### 2024-05-06 data/template.qmd
Initial sketch

# template

We code the studies in ascii format into files titled `authoryearxx.R` stored in `data/` folder.

## Fields

- Initial list, to be modified
- Issues that need to be resolved can be marked after hashtag (#).
- If there are multiple studies/samples in one article, another data can be created and `study_id` can be adjusted by adding a postfix (`_a`,`_b`,`_c`).

```{r}
#| eval: false
#| echo: true
study_id <- 'authorlastnameyeartwoletterfromthetitle'
emotion_type <- c('dimensional','discrete','music-specific','other')
emotion_list <- c('valence','arousal','happy','sad','anger','fear','tender','other')
emotion_locus <- c('perceived','induced','not specified')
stimulus_type <- c('classical','pop','genre','mixed')
stimulus_duration <- 20
stimulus_N <- 24
participant_N <- 35
participant_expertise <- c('non-musician','musician','not specified')
participant_origin <- c('Country','not-specified')
participant_sampling <- c('convenience','not-specified')
participant_task <- c('rating','forced choice','ranking','other')
feature_list <- c('attack rate','pitch height','mode')
feature_validation <- c('annotation','none') # this was done in another study
feature_source <- c('librosa','essentia','MIR toolbox','marsyas','custom','not specified')
model_type <- c('correlation','regression','commonality analysis','classification')
model_measure <- c('rsquared','cor','rmse','classification','other')
model_complexity_parameters <- c(numeric, 'not defined')
model_rate_emotion_list <- c(0.00,0.00)
model_validation <- c('none','cross-validation')
meta_comments <- 'template'
meta_encoder <- 'Initials of the name'
meta_date <- '3/5/2024'
```

### 2024-05-06 index.qmd
Initial sketch

# README

How well we can predict emotions in music? What is the evidence in the published literature for explaining what emotions the listeners can perceive in music when the source consists of audio examples. To what degree the results are dependent on the actual models, emotions, musical/acoustic features, or musical materials or participants?

To obtain answers to these questions, we have set out to record and analyse the current state of the art from the literature using a meta-analysis paradigm. We focus on Music Emotion Recognition and hence the acronym `metaMER`.

## Plan

We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd).

## Study Search and Selection

Search databases and criteria are documented in [studies/search_syntax.qmd](studies/search_syntax.qmd).

## Data Extraction and Coding

Data coding and extraction is described in data template [data/template.qmd](data/template.qmd).

## Analysis

Data analysis is covered in [analysis/analysis.qmd](analysis/analysis.qmd) document.

## Manuscript

The study report is available [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.

### 2024-05-06 manuscript/manuscript.qmd
Initial sketch

---
title             : "Music Emotion Recognition..."
shorttitle        : "XXXXXXXXX"

author: 
  - name          : "TE"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Palace Green, Department of Music, Durham University, DH1 3RL Durham, United Kingdom"
    email         : "tuomas.eerola@durham.ac.uk"
  - name          : "CA"
    affiliation   : "2"
    address       : "XXXXXX"
    email         : "XXX@XXXX"
  - name          : "MS"
    affiliation   : "2"
    address       : "XXXXXX"
    email         : "XXX@XXXX"

affiliation:
  - id            : "1"
    institution   : "Department of Music, Durham University"
  - id            : "2"
    institution   : "XXXX, MacMaster University"

note: ""

author_note: |
  XXX.

abstract: |
 blah blah blah.

keywords          : "music, emotion, recognition, meta-analysis"
wordcount         : "XXXX"

bibliography      : ["references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
csl: apa7.csl

class             : "man"
output            : papaja::apa6_pdf
---

```{r global options, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r include = FALSE, echo=FALSE}
#source('load_libraries.R')
## set options ##
```

# Introduction

blah blah [@anderson2022ex]

## Aims

blah blah

# Methods

blah blah

# Results

blah blah

# Conclusion and Discussion

blah blah

### Funding statement

The authors...

### Competing interests statement

There were no competing interests.

### Open practices statement

XXXX.

### Acknowledgements

xxxxx.

# References

### 2024-05-06 preregistration/preregistration.qmd
Initial sketch

## Meta-analysis title: To what degree music emotion recognition

## Authors: TE + CA + MS ? (to be decided)

## Brief rationale

To assess what degree models are able to predict emotions in music, what models, what emotions, what genres, etc.

## Research objectives

1. How good are MER models?

2. What are the systematic biases of the models?

3. How are models dealing with genres and cultures?

4. How generalisible are the models

5. WEIRD

6. Theory orientations

FINER: feasible, interesting, novel, ethical, relevant [@browner2022de]

## Hypotheses 
We expect that the

## Eligibility criteria
English, peer-reviewed journal articles indexed in X and Y, published between 20xx-20xx

## Database sources

(PubMed, Web of Science, Scopus)

## Search strategy
Music emotion recognition

## Analysis plan

Fixed effects model
Tests of small study/publication bias

### 2024-05-06 studies/search_syntax.qmd
Initial sketch

# Search Syntax

| Database       | Date of search | Results | Search syntax                                                                                                                                                                                                                                                                                                              |
| :--------------| :------------- | :------ | :----------------------------------------------------------------------------------------------------- |
| PsychINFO      | X May 20XX    | XXX     | (emotion OR mood* OR affect*) AND (music OR audio* OR recognition OR percei* OR recogn*) AND (music)   |
| Scopus         | X May 20XX    | XXX     |           |
| Web of Science | X May 20XX    | XXX     |           |

### 2024-05-06 analysis/contents.R

@@ -1,0 +1,3 @@
+#### contents.R
+
+source('read_data.R')

### 2024-05-06 analysis/read_data.R

@@ -1,0 +1,42 @@
+# read_data.R
+
+#### Compile annotated studies ----------
+L <- list.files(path='../data/',pattern = ".R")
+
+df <- data.frame(nro=1:length(L))
+for (k in 1:length(L)) {
+  source(file.path('data/',L[k]))
+  df$study_id[k] <- study_id
+  df$emotion_type[k] <- emotion_type
+  df$emotion_list[k] <- list(emotion_list)
+  df$emotion_locus[k] <- emotion_locus
+  df$stimulus_type[k] <- stimulus_type
+  df$stimulus_duration[k] <- stimulus_duration
+  df$stimulus_N[k] <- stimulus_N
+  df$participant_N[k] <- participant_N
+  df$participant_expertise[k] <- participant_expertise
+  df$participant_origin[k] <- participant_origin
+  df$participant_sampling[k] <- participant_sampling
+  df$feature_list[k] <- list(feature_list)
+  df$feature_validation[k] <- feature_validation
+  df$feature_source[k] <- feature_source
+  df$model_type[k] <- list(model_type)
+  df$model_measure[k] <- model_measure
+  df$model_complexity_parameters[k] <- list(model_complexity_parameters)
+  df$model_rate_emotion_list[k] <- list(model_rate_emotion_list)
+  df$model_validation <- model_validation
+  df$meta_comments[k] <- meta_comments
+  df$meta_encoder[k] <- meta_encoder
+  df$meta_date[k] <- meta_date
+}
+
+# check validity of the data
+
+# numeric variables
+stopifnot(is.numeric(df$stimulus_duration))
+stopifnot(is.numeric(df$stimulus_N))
+stopifnot(is.numeric(df$participant_N))
+
+# specific variables
+stopifnot(df$emotion_type %in% c('dimensional','discrete','music-specific','other'))
+

### 2024-05-06 data/anderson2022ex.R

@@ -1,0 +1,23 @@
+study_id <- 'anderson2020ex'
+emotion_type <- 'dimensional'
+emotion_list <- c('valence','arousal')
+emotion_locus <- 'perceived'
+stimulus_type <- 'classical'
+stimulus_duration <- 20
+stimulus_N <- 24
+participant_N <- 35
+participant_expertise <- 'non-musicians'
+participant_origin <- 'Canada'
+participant_sampling <- 'convenience'
+participant_task <- 'rating'
+feature_list <- c('attack rate','pitch height','mode')
+feature_validation <- c('annotation')
+feature_source <- NA
+model_type <- c('commonality analysis')
+model_measure <- 'rsquared'
+model_complexity_parameters <- 4
+model_rate_emotion_list <- c(0.00,0.00)
+model_validation <- 'none'
+meta_comments <- 'demo study'
+meta_encoder <- 'TE'
+meta_date <- '3/5/2024'

### 2024-05-06 data/battcock2021em.R

@@ -1,0 +1,23 @@
+study_id <- 'battcock2021em'
+emotion_type <- 'dimensional'
+emotion_list <- c('valence','arousal')
+emotion_locus <- 'perceived'
+stimulus_type <- 'classical'
+stimulus_duration <- 20
+stimulus_N <- 48
+participant_N <- 30
+participant_expertise <- 'musicians'
+participant_origin <- 'Canada'
+participant_sampling <- 'convenience'
+participant_task <- 'rating'
+feature_list<- c('attack rate','pitch height','mode')
+feature_validation <- c('annotation')
+feature_source <- NA
+model_type <- c('commonality analysis','regression')
+model_measure <- 'rsquared'
+model_complexity_parameters <- 4
+model_rate_emotion_list <- c(0.8334,0.5429)
+model_validation <- 'none'
+meta_comments <- 'demo study 2'
+meta_encoder <- 'TE'
+meta_date <- '3/5/2024'

### 2024-05-13 studies/search_syntax.qmd
first pass of the study lists

@@
 | Web of Science | X May 20XX    | XXX     |           |
+
+## Scopus
+
+TITLE-ABS-KEY ( valence OR arousal OR classi OR categor OR algorithm AND music AND emotion AND recognition ) AND PUBYEAR > 2013 AND PUBYEAR < 2025 AND ( LIMIT-TO ( DOCTYPE , "ar" ) )
+
+227_ results
+scopus_first_pass.bib
+
+## Web of Science
+
+(DT=(Article) AND PY=(2014-2025)) AND ALL=(music emotion recognition valence arousal)
+
+142 hits
+
+webofscience_142_first_pass.bib
+
+## OpenAlex
+
+https://openalex.org/works?page=1&filter=default.search%3Amusic%20emotion%20recognition%20valence%20arousal,type%3Atypes%2Farticle,publication_year%3A2014-2024,keywords.id%3Akeywords%2Femotion-recognition,keywords.id%3Akeywords%2Faffective-computing,language%3Alanguages%2Fen,open_access.any_repository_has_fulltext%3Atrue
+
+278

### 2024-05-16 studies/search_syntax.qmd
First pass documented

--- 2024-05-06 studies/search_syntax.qmd
@@
 
-| Database       | Date of search | Results | Search syntax                                                                                                                                                                                                                                                                                                              |
+We first performed search through three databases using the following syntax for each.
+
+| Database       | Date  | Results | Search syntax                                                                                                                                                                                                                                                                                                              |
 | :--------------| :------------- | :------ | :----------------------------------------------------------------------------------------------------- |
-| PsychINFO      | X May 20XX    | XXX     | (emotion OR mood* OR affect*) AND (music OR audio* OR recognition OR percei* OR recogn*) AND (music)   |
-| Scopus         | X May 20XX    | XXX     |           |
-| Web of Science | X May 20XX    | XXX     |           |
+| Scopus         | 12 May 2024    | 227     | ```TITLE-ABS-KEY ( valence OR arousal OR classi OR categor OR algorithm AND music AND emotion AND recognition ) AND PUBYEAR > 2013 AND PUBYEAR < 2025 AND ( LIMIT-TO ( DOCTYPE , "ar" ) )```          |
+| Web of Science | 12 May 2024    | 142     | ```(DT=(Article) AND PY=(2014-2025)) AND ALL=(music emotion recognition valence arousal)```          |
+| Open Alex      | 12 May 2024    | 278     | ```https://openalex.org/works?page=1&filter=default.search%3Amusic%20emotion%20recognition%20valence%20arousal,type%3Atypes%2Farticle, publication_year%3A2014-2024, keywords.id%3Akeywords%2Femotion-recognition, keywords.id%3Akeywords%2Faffective-computing, language%3Alanguages%2Fen,open_access.any_repository_has_fulltext%3Atrue```   |
+
+# First Pass: Identification of relevant studies
+
+The first pass was to eliminate non-relevant studies based on our criteria (link to prereg). This round eliminated studies with incomplete or wrong type of information (e.g. conference proceedings).
+
+```{r}
+#| results: asis
+#| warning: false
+library(bib2df)
+library(tidyverse)
+library(stringr)
+library(ggplot2)
+
+#### Read first pass data ---------------------
+d <- bib2df("../studies/metaMER_library_first_pass_year_fixed.bib")
+# Remove extra fields
+d <- dplyr::select(d,-C1,-DATE.ADDED,-DATE.MODIFIED,-LA,-BDSK.URL.1,-BDSK.URL.2,-ISBN)
+# Add explicit source
+d$SOURCE[str_detect(d$UNIQUE.ID,'WOS')] <- 'Web of Science'
+d$SOURCE[is.na(d$SOURCE)] <- 'Open Alex'
+#print(knitr::kable(table(d$SOURCE)))
+
+library(summarytools)
+print(summarytools::freq(d$SOURCE, order = "freq",round.digits = 1,missing = 'NA',headings = FALSE))
+
+```
+
+After this pass, the unique number of studies in the three collections was `r nrow(d)`.
+During the first pass analysis, the studies were manually checked for relevance based on title and classified into low, moderate, and high relevance based on our focus.
+
+```{r}
+#| results: asis
+d$PRIORITY<-factor(d$PRIORITY,levels = c("prio1","prio2","prio3"), labels = c("High","Moderate","Low"))
+#print(knitr::kable(table(d$PRIORITY)))
+summarytools::freq(d$PRIORITY, order = "freq",round.digits = 1,missing = 'NA',headings = FALSE)
+
+```
+
+The majority of the excluded studies focussed on other aspects such as neuroscience, applied direction (recommendation, therapy) or another modality (visual, video, faces).
+
+```{r}
+#| results: asis
+#| 
+eliminated <- dplyr::filter(d, PRIORITY=='Low')
+eliminated$themes <- NA
+eliminated$themes[str_detect(tolower(eliminated$TITLE),'eeg|parietal|neuro|meg|galvanic|electrodermal|conductanc|heart|ecg|biosignal|brain|physiological|electroenceph|imaging|biomarker|cerebral|cardiovascular|autonomic nervous')]<-'Biosignals'
+eliminated$themes[str_detect(tolower(eliminated$TITLE),'stress|therapy|depress|autis|rehabil|schizoph|alzheime|cochle|interve')]<-'Clinical'
+eliminated$themes[str_detect(tolower(eliminated$TITLE),'infant|childr|childhood|empath|curriculum|amusia|music education|college|singing|young adults|newbor|memory')]<-'Developmental/Educational'
+eliminated$themes[str_detect(tolower(eliminated$TITLE),'tracking|image|wearable|virtual|touch|dance|movie|TV|voice|facial|face|multimodal|body|animat|multimed|video|robot|wireless|visual|sensor|multi-modal')]<-'Multimodal'
+eliminated$themes[str_detect(tolower(eliminated$TITLE),'violence|political|speech|melodies|twins|stage|timbre|tonality|age|paralinguistics|ontologies')]<-'Other'
+
+# and more of these themes identified here
+
+#print(knitr::kable(table(eliminated$themes)))
+print(summarytools::freq(eliminated$themes, order = "freq",round.digits = 1,missing = 'NA',headings = FALSE))
+
+eliminated$TITLE[is.na(eliminated$themes)]
+
+```
+
+## Second pass: Assessment of relevant content
+
+Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established [link to prereg] was carried out.

### 2024-05-19 studies/library_formatter.qmd
add code to merge & clean bibtex files

---
title: "Bib Library"
author: "Cameron Anderson"
format: html
editor: visual
---

## Reading in Biblibrary

## Load libraries

```{r}
# load dplyr
library(dplyr)
```

## Read data

```{r}
# read in bibtex library as data frame
bib_df_ca <- bib2df::bib2df('metaMER_lib_third_pass_ca.bib')
bib_df_te <- bib2df::bib2df(blahblah)

```

## Identify sources

```{r}
# filter open_alex entries and declare source (c1 unique to database)
bib_df_ca %>% 
  filter(!is.na(C1)) %>%
  mutate(SOURCE = 'open_alex') -> oa_entries

# filter wos entries and declare source (unique_id unique to database)
bib_df_ca %>% 
  filter(!is.na(UNIQUE.ID)) %>%
  mutate(SOURCE = 'web_of_science') -> wos_entries

# filter scopus entries
bib_df_ca %>% 
  filter(SOURCE == 'Scopus') -> scopus_entries

# bind sources
bib_df_ca <- rbind(oa_entries, wos_entries)
bib_df_ca <- rbind(bib_df_ca, scopus_entries)

```

## Clean up entries

```{r}
# remove columns only belonging to one database
bib_df_ca$UNIQUE.ID <- NULL
bib_df_ca$C1 <- NULL
# remove unnecessary column
bib_df_ca$HASABSTRACT <- FALSE
# relevel priority column with intuitive names
bib_df_ca$PRIORITY <- as.factor(bib_df_ca$PRIORITY)
levels(bib_df_ca$PRIORITY) <- c('high_priority', 'low_priority')
bib_df_ca$PRIORITY <- plyr::revalue(bib_df_ca$PRIORITY, 
                                    c(prio1 = 'high_priority',
                                      prio3 = 'low_prioirty'))
# make casing consistent
bib_df_ca$SOURCE <- tolower(bib_df_ca$SOURCE)
# consistent names for private notes
names(bib_df_ca)[names(bib_df_ca) == 'comment_camja'] <- 'NOTES.CA'
```

## Clean up field formatting

```{r}
# replace periods and hyphens with underscores, make titles lowercase
# stringr::str_replace(names(bib_df), '\\.|_', '_') %>% 
#   tolower() -> names(bib_df)
```

## Add comments from second reviewer

```{r}
# select bibkey (for merge) and notes from second reviewer
bib_df_te <- bib_df_te %>% select(BIBTEXKEY, NOTES.TE)

bib_df_merged <- merge(bib_df_ca, 
                       bib_df_te, 
                       by = c('BIBTEXKEY'))
```

## Drop empty columns

```{r}
# identify columns entirely empty
empty_cols <- sapply(bib_df_merged, function(x)all(is.na(x))) 
# remove them
bib_df_merged <- bib_df_merged[,!empty_cols]

```

## Rewrite BiBTeX library

```{r}
bib2df::df2bib(bib_df_merged, file = 'metaMER_lib_third_pass_clean.bib')
```

##

### 2024-05-20 studies/library_formatter.qmd
Resolving our pass3 issues

@@
 # read in bibtex library as data frame
-bib_df_ca <- bib2df::bib2df('metaMER_lib_third_pass_ca.bib')
-bib_df_te <- bib2df::bib2df(blahblah)
-
+bib_df_ca <- bib2df::bib2df('metaMER_library_third_pass_ca.bib')
+bib_df_te <- bib2df::bib2df('metaMER_library_third_pass_te.bib')
+bib_df_ca <- dplyr::filter(bib_df_ca,PRIORITY=='prio1')
+bib_df_te <- dplyr::filter(bib_df_te,PRIORITY=='prio1')
+sum(bib_df_ca$BIBTEXKEY %in% bib_df_te$BIBTEXKEY)==nrow(bib_df_ca)
 ```
@@
 # remove unnecessary column
-bib_df_ca$HASABSTRACT <- FALSE
+bib_df_ca$HASABSTRACT <- NULL
 # relevel priority column with intuitive names
-bib_df_ca$PRIORITY <- as.factor(bib_df_ca$PRIORITY)
-levels(bib_df_ca$PRIORITY) <- c('high_priority', 'low_priority')
-bib_df_ca$PRIORITY <- plyr::revalue(bib_df_ca$PRIORITY, 
-                                    c(prio1 = 'high_priority',
-                                      prio3 = 'low_prioirty'))
+# bib_df_ca$PRIORITY <- as.factor(bib_df_ca$PRIORITY)
+#levels(bib_df_ca$PRIORITY) <- c('high_priority', 'low_priority')
+# bib_df_ca$PRIORITY <- plyr::revalue(bib_df_ca$PRIORITY, 
+#                                     c(prio1 = 'high_priority',
+#                                       prio3 = 'low_prioirty'))
 # make casing consistent
@@
 # consistent names for private notes
-names(bib_df_ca)[names(bib_df_ca) == 'comment_camja'] <- 'NOTES.CA'
+names(bib_df_ca)[names(bib_df_ca) == 'COMMENT.CAMJA'] <- 'NOTES.CA'
 ```
@@
 ```{r}
+
 # select bibkey (for merge) and notes from second reviewer
@@
 ```{r}
+# JOURNAL and JOURNALTITLE are the same (latter for scopus)
+
+dim(bib_df_merged)
 bib2df::df2bib(bib_df_merged, file = 'metaMER_lib_third_pass_clean.bib')
+
 ```
+## Next
 
-##
+Compare pass 3 annotations and resolve conflicts (`pass 3 comparison.qmd`)

### 2024-05-20 studies/pass3_comparison.qmd
Resolving our pass3 issues

---
title: "Pass 3 Comparison"
author: "Cameron Anderson"
format: html
---

## Reading in Biblibrary

## Load libraries

```{r}
# load dplyr
library(dplyr)
```

## Read data

```{r}
# read in bibtex library as data frame
bib_df_ca <- bib2df::bib2df('metaMER_lib_third_pass_clean.bib')

```

## Compare

```{r}
dim(bib_df_merged)
library(stringr)

bib_df_merged$NOTES_INDEX.CA<-NA
bib_df_merged$NOTES_INDEX.CA[str_detect(tolower(bib_df_merged$NOTES.CA),'include')]<-'include'
bib_df_merged$NOTES_INDEX.CA[str_detect(tolower(bib_df_merged$NOTES.CA),'exclude')]<-'exclude'
bib_df_merged$NOTES_INDEX.CA[str_detect(tolower(bib_df_merged$NOTES.CA),'unsure')]<-'unsure'

bib_df_merged$NOTES_INDEX.TE<-NA
bib_df_merged$NOTES_INDEX.TE[str_detect(tolower(bib_df_merged$NOTES.TE),'include')]<-'include'
bib_df_merged$NOTES_INDEX.TE[str_detect(tolower(bib_df_merged$NOTES.TE),'exclude')]<-'exclude'
bib_df_merged$NOTES_INDEX.TE[str_detect(tolower(bib_df_merged$NOTES.TE),'unsure')]<-'unsure'
sum(is.na(bib_df_merged$NOTES_INDEX.CA))
sum(is.na(bib_df_merged$NOTES_INDEX.TE))

t<-table(bib_df_merged$NOTES_INDEX.CA,bib_df_merged$NOTES_INDEX.TE)
t2<-round(t/sum(t),2)
sum(diag(t2))
```
## Report annotation reliability/agreement

## Resolve these discrepancies
```{r}
# resolve unsure ones
IND <- which(bib_df_merged$NOTES_INDEX.CA=='unsure')
resolved_index <- bib_df_merged$BIBTEXKEY[IND]
resolved <-c('exclude',
             'exclude',
             'exclude',
             'exclude',
             'exclude',
             'exclude',
             'exclude',
             'exclude',
             'exclude',
             'exclude',
             'exclude',
             'exclude')

# Resolving conflicting exclude/include annotations, part 1
IND <- which(bib_df_merged$NOTES_INDEX.CA=='exclude' & bib_df_merged$NOTES_INDEX.TE=='include')
#IND <- which(bib_df_merged$NOTES_INDEX.TE=='exclude' & bib_df_merged$NOTES_INDEX.CA=='include')
resolved_exclude_index <- bib_df_merged$BIBTEXKEY[IND]
resolved_exclude_index # 8
resolved_exclude <-c('exclude','exclude','exclude','include','exclude','exclude','exclude','exclude')

# Resolving conflicting exclude/include annotations, part 2
IND <- which(bib_df_merged$NOTES_INDEX.TE=='exclude' & bib_df_merged$NOTES_INDEX.CA=='include')
resolved_exclude2_index <- bib_df_merged$BIBTEXKEY[IND]
resolved_exclude2_index # 8
resolved_exclude2 <-c('exclude','exclude','exclude','exclude')

```

## Export bibtex for the annotation

Notes:

For Feature classification, use this one:

https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9229494

Insert the template the annotation fields from googledoc to the bibtex file.

### 2024-05-21 studies/library_formatter.qmd
add template for annotation

@@
 ---
-title: "Bib Library"
+title: "Library Formatter"
 author: "Cameron Anderson"
 format: html
-editor: visual
 ---
@@
 
+scopus_entries$JOURNAL <- scopus_entries$JOURNALTITLE
+scopus_entries$JOURNALTITLE <- NA
+
 # bind sources
@@
 names(bib_df_ca)[names(bib_df_ca) == 'COMMENT.CAMJA'] <- 'NOTES.CA'
-```
-
-## Clean up field formatting
-
-```{r}
-# replace periods and hyphens with underscores, make titles lowercase
-# stringr::str_replace(names(bib_df), '\\.|_', '_') %>% 
-#   tolower() -> names(bib_df)
+# after subsetting out high-priority studies, no longer need priority column
+bib_df_ca$PRIORITY <- NULL
+bib_df_ca$RANKING <- NULL
+bib_df_ca$MODIFICATIONDATE <- NULL
 ```
@@
 ```{r}
-
 # select bibkey (for merge) and notes from second reviewer
@@
 # identify columns entirely empty
-empty_cols <- sapply(bib_df_merged, function(x)all(is.na(x))) 
+empty_cols <- sapply(bib_df_merged, function(x) {
+  all(is.na(x))
+  }
+) 
 # remove them
-bib_df_merged <- bib_df_merged[,!empty_cols]
-
+bib_df_merged <- bib_df_merged[ , !empty_cols]
 ```
@@
 ```{r}
-# JOURNAL and JOURNALTITLE are the same (latter for scopus)
-
 dim(bib_df_merged)
-bib2df::df2bib(bib_df_merged, file = 'metaMER_lib_third_pass_clean.bib')
+bib2df::df2bib(bib_df_merged, file = 'metaMER_library_third_pass_clean.bib')
 
 ```
+
 ## Next

### 2024-05-21 studies/pass3_comparison.qmd
add template for annotation

@@
 ```{r}
-# load dplyr
+# load libraries
 library(dplyr)
+library(stringr)
+library(knitr)
 ```
@@
 # read in bibtex library as data frame
-bib_df_ca <- bib2df::bib2df('metaMER_lib_third_pass_clean.bib')
-
+bib_df_merged <- bib2df::bib2df('metaMER_library_third_pass_clean.bib')
 ```
@@
 ```{r}
+# check dimensions are accurate
 dim(bib_df_merged)
-library(stringr)
 
+# distinguish notes with author initials
+names(bib_df_merged)[names(bib_df_merged) == 'NOTES'] <- 'NOTES.CA'
+names(bib_df_merged)[names(bib_df_merged) == 'NOTES.1'] <- 'NOTES.TE'
+
+# extract decisions less comments
+capture_group <- 'include|exclude|unsure'
+
+# create new index to track entries
 bib_df_merged$NOTES_INDEX.CA<-NA
-bib_df_merged$NOTES_INDEX.CA[str_detect(tolower(bib_df_merged$NOTES.CA),'include')]<-'include'
-bib_df_merged$NOTES_INDEX.CA[str_detect(tolower(bib_df_merged$NOTES.CA),'exclude')]<-'exclude'
-bib_df_merged$NOTES_INDEX.CA[str_detect(tolower(bib_df_merged$NOTES.CA),'unsure')]<-'unsure'
 
-bib_df_merged$NOTES_INDEX.TE<-NA
-bib_df_merged$NOTES_INDEX.TE[str_detect(tolower(bib_df_merged$NOTES.TE),'include')]<-'include'
-bib_df_merged$NOTES_INDEX.TE[str_detect(tolower(bib_df_merged$NOTES.TE),'exclude')]<-'exclude'
-bib_df_merged$NOTES_INDEX.TE[str_detect(tolower(bib_df_merged$NOTES.TE),'unsure')]<-'unsure'
+# create new column tracking decisions
+bib_df_merged$NOTES_INDEX.CA <- str_extract(tolower(bib_df_merged$NOTES.CA),
+                                         capture_group)
+bib_df_merged$NOTES_INDEX.TE <- str_extract(tolower(bib_df_merged$NOTES.TE),
+                                     capture_group)
+
+# check entries are consistent
 sum(is.na(bib_df_merged$NOTES_INDEX.CA))
@@
 
-t<-table(bib_df_merged$NOTES_INDEX.CA,bib_df_merged$NOTES_INDEX.TE)
-t2<-round(t/sum(t),2)
-sum(diag(t2))
 ```
+
 ## Report annotation reliability/agreement
 
-## Resolve these discrepancies
+```{r}
+# compare raters' decisions with confusion matrix
+t<-table(bib_df_merged$NOTES_INDEX.CA,
+         bib_df_merged$NOTES_INDEX.TE)
+
+# get agreement
+t2<-round(t/sum(t),2)
+ag_before <- sum(diag(t2))
+
+# make table
+knitr::kable(t,  
+             caption = paste('Votes before discussion. \n
+             Rows: CA votes; cols: TE votes, Agreement = ', ag_before)
+             )
+```
+
+## CA: unsure
+
 ```{r}
@@
 IND <- which(bib_df_merged$NOTES_INDEX.CA=='unsure')
-resolved_index <- bib_df_merged$BIBTEXKEY[IND]
-resolved <-c('exclude',
-             'exclude',
-             'exclude',
-             'exclude',
-             'exclude',
-             'exclude',
-             'exclude',
-             'exclude',
-             'exclude',
-             'exclude',
-             'exclude',
-             'exclude')
+resolved_index <- bib_df_merged$BIBTEXKEY[IND] # 12
+# CA updates ratings:
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'deng2024an'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'hao2022re'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'he2022al'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'huang2023th'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'priscillajoy2023mu'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'shen2024re'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'wang2021mu'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'wang2021re'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'wang2022mua'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'zhang2016rea'] <- 'exclude'
 
-# Resolving conflicting exclude/include annotations, part 1
-IND <- which(bib_df_merged$NOTES_INDEX.CA=='exclude' & bib_df_merged$NOTES_INDEX.TE=='include')
-#IND <- which(bib_df_merged$NOTES_INDEX.TE=='exclude' & bib_df_merged$NOTES_INDEX.CA=='include')
-resolved_exclude_index <- bib_df_merged$BIBTEXKEY[IND]
-resolved_exclude_index # 8
-resolved_exclude <-c('exclude','exclude','exclude','include','exclude','exclude','exclude','exclude')
+# both CA and TE update ratings:
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'na2022mu'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'na2022mu'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'tian2023mu'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'tian2023mu'] <- 'exclude'
 
-# Resolving conflicting exclude/include annotations, part 2
-IND <- which(bib_df_merged$NOTES_INDEX.TE=='exclude' & bib_df_merged$NOTES_INDEX.CA=='include')
-resolved_exclude2_index <- bib_df_merged$BIBTEXKEY[IND]
-resolved_exclude2_index # 8
-resolved_exclude2 <-c('exclude','exclude','exclude','exclude')
+# resolved <-c('deng2024an' = 'exclude',
+#              'hao2022re' = 'exclude',
+#              'he2022al' = 'exclude',
+#              'huang2023th' = 'exclude',
+#              'na2022mu' = 'exclude',
+#              'priscillajoy2023mu' = 'exclude',
+#              'shen2024re' = 'exclude',
+#              'tian2023mu' = 'exclude',
+#              'wang2021mu' = 'exclude',
+#              'wang2021re' = 'exclude',
+#              'wang2022mua' = 'exclude',
+#              'zhang2016rea' = 'exclude')
 
@@
 
+## TE: unsure (in progress)
+
+```{r}
+# update TE decision
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'tang2023ap'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'xing2015em'] <- 'exclude'
+
+# update TE and CA decisions
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'wang2022mu'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'wang2022mu'] <- 'exclude'
+
+```
+## Summary
+|Study|CA|TE||Resolution/Decision|
+|---|---|---|---|
+|tang2023ap|uses image features|No relevant features, lack of stimulus detail|Exclude|
+|xing2015em|includes classification task|No N of musical excerpts, missing information regarding data processing|Exclude|
+|wang2022mu|only reports DET and equal error rate|Although they report correlation coefficients, emotions are not valence or arousal. Do report MSE of classification task|Exclude|
+
+## Tabulate results after resolving unsures
+
+```{r}
+# compare raters' decisions with confusion matrix
+t<-table(bib_df_merged$NOTES_INDEX.CA,
+         bib_df_merged$NOTES_INDEX.TE)
+
+# get agreement
+t2<-round(t/sum(t),2)
+ag_before <- sum(diag(t2))
+
+# make table
+knitr::kable(t,  
+             caption = paste('Votes after resolving unsure discrepancies. \n
+             Rows: CA votes; cols: TE votes, Agreement = ', ag_before)
+             )
+```
+
+# Resolving exclude/include disagreements
+
+## CA: exclude, TE: include
+
+```{r}
+# Resolving conflicting exclude/include annotations, part 1
+IND <- which(bib_df_merged$NOTES_INDEX.CA=='exclude' & 
+  bib_df_merged$NOTES_INDEX.TE=='include')
+# check discrepant entries
+resolved_exclude_index <- bib_df_merged$BIBTEXKEY[IND]
+resolved_exclude_index # 8
+
+# update TE votes to exclude
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'aljanaki2017de'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'li2024im'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'pandeya2024gl'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'sanmillancastillo2022an'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'wang2015mo'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'wang2016af'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.TE[bib_df_merged$BIBTEXKEY == 'yang2023ex'] <- 'exclude'
+# update CA votes to include
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'saizclar2022pr'] <- 'include'
+
+# resolved_exclude <-c('aljanaki2017de' = 'exclude',
+#                      'li2024im' = 'exclude',
+#                      'pandeya2024gl' = 'exclude',
+#                      'saizclar2022pr' = 'include',
+#                      'sanmillancastillo2022an' = 'exclude',
+#                      'wang2015mo' = 'exclude',
+#                      'wang2016af' = 'exclude',
+#                      'yang2023ex' = 'exclude')
+
+```
+
+## Summary
+
+### CA: exclude, TE: include
+
+| Study                       | CA                                    | TE                                                                   | Resolution/Decision                                                                                  |
+|------------------|------------------|------------------|------------------|
+| **aljanaki2017de**          | Multiple teams' performance reported  | Possible to report teams as substudies                               | **Exclude**: Benchmark, does not contain original study details from reporting team                  |
+| **li2024im**                | No relevant task                      | Reports classification accuracy and DEAM results                     | **Exclude**: No audio features reported                                                              |
+| **pandeya2024gl**           | Insufficient detail for meta-analysis | Includes timbre and global audio features, confusion matrix included | **Exclude**: Reporting on music videos; quality issues in data set                                   |
+| **saizclar2022pr**          | No modeling task                      | Modeling is based on onsets                                          | **Include**: although no cross-validation, still performed task                                      |
+| **sanmillancastillo2022an** | No music                              | Task present                                                         | **Exclude**: No music                                                                                |
+| **wang2015mo**              | No relevant task                      | Not sure of outcome measures                                         | **Exclude**: No translation of distances into VA accuracy                                            |
+| **wang2016af**              | Chapter                               | Includes relevant task                                               | **Exclude**: Meets exclusion criteria (not an article)                                               |
+| **yang2023ex**              | No relevant task                      | Final metrics missing                                                | **Exclude**: Collected VA emotion ratings, but don't use audio features to predict VA (not reported) |
+
+## TE: exclude, CA: include
+
+```{r}
+# Resolving conflicting exclude/include annotations, part 2
+IND <- which(bib_df_merged$NOTES_INDEX.TE=='exclude' & 
+               bib_df_merged$NOTES_INDEX.CA=='include')
+
+# check discrepant entries
+resolved_exclude2_index <- bib_df_merged$BIBTEXKEY[IND]
+resolved_exclude2_index # 4
+
+# update CA votes
+
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'cunningham2021su'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'eyben2015em'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'tian2023mua'] <- 'exclude'
+bib_df_merged$NOTES_INDEX.CA[bib_df_merged$BIBTEXKEY == 'tiple2022mu'] <- 'exclude'
+
+# resolved_exclude2 <-c('cunningham2021su' = 'exclude',
+#                       'eyben2015em' = 'exclude',
+#                       'tian2023mua' = 'exclude',
+#                       'tiple2022mu' = 'exclude')
+
+```
+
+## Summary
+
+| Study                | TE                                               | CA                                               | Resolution/Decision                                          |
+|------------------|------------------|------------------|------------------|
+| **cunningham2021su** | Reports on IADS (not music)                      | Relevant task                                    | **Exclude**: No music                                        |
+| **eyben2015em**      | Focused on laboratory singing                    | Relevant task                                    | **Exclude**: Laboratory singing of a scale                   |
+| **tiple2022mu**      | Data set just includes annotation of tonic pitch | Relevant task, but only reports overall accuracy | **Exclude**: Data set not sufficiently detailed for MER task |
+
+## Update table after resolving disagreements
+
+```{r}
+# compare raters' decisions with confusion matrix
+t<-table(bib_df_merged$NOTES_INDEX.CA,
+         bib_df_merged$NOTES_INDEX.TE)
+
+# get agreement
+t2<-round(t/sum(t),2)
+ag_before <- sum(diag(t2))
+
+# make table
+knitr::kable(t,  
+             caption = paste('Votes after resolving include vs. exclude discrepancies. \n
+             Rows: CA votes; cols: TE votes, Agreement = ', ag_before)
+             )
+```
+
+## Track task types
+
+```{r}
+# add column tracking task type
+bib_df_merged$PARADIGM <- 'regression'
+bib_df_merged[str_detect(bib_df_merged$NOTES.CA, 'classification'),]$PARADIGM <- 'classification'
+
+# sort by task
+bib_df_merged <- bib_df_merged[order(bib_df_merged$PARADIGM),]
+```
+
+## Add fields for annotation
+
+```{r}
+# add new fields for annotating bibtex library
+bib_df_merged %>% mutate(emotions = ' ',
+                         emotion_locus = ' ',
+                         stimulus_type = ' ',
+                         stimulus_duration = ' ',
+                         stimulus_duration_unit = ' ',
+                         stimulus_N = ' ',
+                         feature_N = ' ',
+                         participant_N = ' ',
+                         participant_expertise = ' ',
+                         participant_origin = ' ',
+                         participant_sampling = ' ',
+                         participant_task = ' ',
+                         feature_N = ' ',
+                         feature_categories = ' ',
+                         feature_source = ' ',
+                         feature_reduction_method = ' ',
+                         model_category = ' ',
+                         model_detail = ' ',
+                         model_measure = ' ',
+                         model_complexity_parameters = ' ',
+                         model_rate_emotion_names = ' ',
+                         model_rate_emotion_values = ' ',
+                         model_validation = ' ',
+                         final_decision = NOTES_INDEX.CA) -> bib_df_merged
+```
+
 ## Export bibtex for the annotation
+
+```{r}
+bib_df_merged$NOTES_INDEX.CA <- NULL
+bib_df_merged$NOTES_INDEX.TE <- NULL
+```
+
+## Write resulting bibtex library
+
+```{r}
+bib2df::df2bib(bib_df_merged, file = 'metaMER_library_template.bib')
+```
 

### 2024-05-21 studies/pass3_comparison.qmd
remove excluded studies from bib template

@@
 bib_df_merged <- bib_df_merged[order(bib_df_merged$PARADIGM),]
+
+# put rater notes side-by-side
+NOTES.CA <- bib_df_merged$NOTES.CA
+NOTES.TE <- bib_df_merged$NOTES.TE
+bib_df_merged$NOTES.CA <- NULL
+bib_df_merged$NOTES.TE <- NULL
+bib_df_merged$NOTES_CA<-NOTES.CA
+bib_df_merged$NOTES_TE<-NOTES.TE
+
 ```
@@
 bib_df_merged$NOTES_INDEX.TE <- NULL
+bib_df_merged$CATEGORY <- NULL
+```
+
+## Get included studies
+
+```{R}
+bib_df_merged <- subset(bib_df_merged, final_decision == 'include')
+bib_df_merged$final_decision <- NULL
 ```

### 2024-05-28 studies/extraction_details.qmd
add draft doc for extraction fields

---
title: "Extraction Details"
---

To capture relevant information from studies, we expanded BiBTeX fields for each study with additional fields. For reproducibility, these instructions provide information on the process followed for each field.

# Fields

## IDENTIFIER

Unique identifier of article. Contains last name of lead author, year of publication and first two letters of article title. Hyphenated last names collapsed.

## AUTHOR

Names of all authors. Last name precedes first name and separated by comma. For multiple authors "and" precedes each listed subsequent author. E.g., Sorussa, Kanawat and Choksuriwong, Anant and Karnjanadecha, Montri

## JOURNAL

Title of journal containing article.

## NOTE

Includes number of citing articles and open access details. E.g., Cited by: 4; All Open Access, Gold Open Access, Green Open Access

## TITLE

Title of article.

## TYPE

**TODO**: Remove? All are articles

## VOLUME

Volume number of publication.

## YEAR

Publication year.

## DOI

Digital object identifier of article.

## ABSTRACT

Complete text of article abstract.

## PUBLICATION_STAGE

**TODO:** Remove? All final.

## SOURCE

Database article was sourced from. Scopus, Web of Science (WoS) or OpenAlex.

## AUTHOR_KEYWORDS

Corresponding keywords for article indicated by author.

## PARADIGM

Paradigm used for MER task. Either classification or regression.

## NOTES_AUTHORINITIALS

Decision and comments by respective author

## EMOTIONS

List of emotion names or labels separated by commas. **TODO:** Discuss potential redundancies with `MODEL_RATE_EMOTION_NAMES`

## EMOTION_LOCUS

Perceived or felt **TODO:** Remove? All appear to be perceived

## STIMULUS_TYPE

Metadata pertaining to stimuli employed in paradigm. Can be listed as genres of music stimuli employed, or if stimuli come from a standard database, name of standard.

## STIMULUS_DURATION

Duration of stimuli, if applicable. Unit of measurement (seconds, measures) specified in `STIMULUS_DURATION_UNIT`

## STIMULUS_DURATION_UNIT

Unit of measurement pertaining to `STIMULUS_DURATION`. E.g., seconds, measures, etc.

## STIMULUS_N

Number of stimuli employed in experiment.\
**TODO** Discuss handling of subset selection, train, test, etc

## FEATURE_N

Number of features included in model. **TODO** Discuss handling of subset selection, train, test, etc

## PARTICIPANT_N

Total number of participants in experiment. **TODO** Discuss handling of secondary information. E.g., MediaEval

## PARTICIPANT_EXPERTISE

Expertise of annotators. E.g., experts, non-experts, not specified.

## PARTICIPANT_ORIGIN

Origin country of participants, or online platform participants were recruited from (e.g., MTurk)

## PARTICIPANT_SAMPLING

How participants were recruited (e.g., convenience, random sampling, crowdsourcing)

## PARTICIPANT_TASK

Nature of rating/classification task undertaken by participants. E.g., rate, annotate. **TODO** discuss multi-stage studies. E.g., MediaEval categories validated by participants using AV ratings.

## FEATURE_CATEGORIES

Names of categories analyzed features pertain to, based on names in Panda (2021). Includes names of all pertinent categories: *Melody*, *Rhythm*, *Timbre*, *Pitch*, *Tonality*, *Expressivity*, *Texture*, *Form*, *Vocal*, *High-Level* **TODO** Discuss feasibility of this approach. Other nominalizations/categories not covered (e.g., spectral, temporal, lyric)

## FEATURE_SOURCE

Name(s) of feature analysis toolboxes. **TODO** Discuss original features (as in `Panda2020no`)

## FEATURE_REDUCTION_METHOD

Name(s) of feature reduction or feature selection methods employed.

## MODEL_CATEGORY

Name of model type. One of regression, classification *TODO* Discuss redundancy with `PARADIGM`. Consider cases where regression and classification employed; or regression approach to classification (e.g., `sorussa2020em`)

## MODEL_DETAIL

Additional information pertaining to predictive model, such as the name of algorithm used and other pertinent parameters. E.g., RandomForest, Commonality Analysis, Multiple Regression, Neural Networks, LDSM, etc. *TODO* Discuss how much information to include.

## MODEL_MEASURE

Metric used in model evaluation. E.g., 'R2' for $R^2$, MSE, CCC, Classification accuracy, etc.

## MODEL_COMPLEXITY_PARAMETERS

Additional information pertaining to predictive model. Format as R code when encoding multiple pertinent parameters. E.g., `c(training_epochs = 100, layer_n = c(1,2), lstm_units = c(124, 248))`

## MODEL_RATE_EMOTION_NAMES

Names of predicted emotions. E.g., valence, arousal, happy, sad, angry, fearful, etc.

## MODEL_RATE_EMOTION_VALUES

Pertinent prediction of model summaries. Report as *R* arrays, including summary statistics in variables. When reporting results of multiple models, concatenate multiple entries with `rbind`. When reporting results for different toolboxes or feature subsets, assign each to a new BiBTeX field with relevant identifier following final underscore.

\### EXAMPLES:

#### Regression

Report relevant summary statistics in R code. Different feature distinguished through BiBTeX fields (`MODEL_RATE_EMOTION_VALUES_MFCC`, `MODEL_RATE_EMOTION_VALUES_ESSENTIA` ). Fitted models concatenated with `rbind` (`linear.regression`, `SMOreg`, `RNN1.124LSTM`, etc.). Model results reported with names in first array (`R2_arousal`, `MAE_arosal`, `R2_valence`, `MAE_valence`), and recycled in each subsequent model.

```         
MODEL_RATE_EMOTION_VALUES_MFCC = {
  rbind(
    linear.regression = c(R2_arousal = 0.61, MAE_arousal = 0.13, R2_valence = 0.07, MAE_valence = 0.17),
    SMOreg = c(0.6,0.13,0.10,0.17),
    RNN1.124LSTM = c(0.58,0.14,0.14,0.17),
    RNN2.124.124LSTM = c(0.66,0.12,0.11,0.16),
    RNN3.248LSTM = c(0.61,0.13,0.13,0.16),
    RNN4.248.248LSTM = c(0.64,0.12,0.14,0.15)
  )
},
MODEL_RATE_EMOTION_VALUES_ESSENTIA = {
  rbind(
    linear.regression = c(R2_arousal = 0.07, MAE_arousal = 0.25, R2_valence = 0.06, MAE_valence = 0.19),
    SMOreg = c(0.48,0.18,0.27,0.17),
    RNN1.124LSTM = c(0.54,0.14,0.21,0.16),
    RNN2.124.124LSTM = c(0.67,0.12,0.32,0.13),
    RNN3.248LSTM = c(0.58,0.14,0.32,0.14),
    RNN4.248.248LSTM = c(0.69,0.11,0.40,0.13),
    RNN5.529LSTM = c(0.61,0.13,0.29,0.15),
    RNN6.529.529LSTM = c(0.68,0.12,0.36,0.14)
  )
}
```

#### Classification

Report confusion matrices as *R* arrays. The following example classifies emotions into five categories for multiple feature subsets. Different feature distinguished through BiBTeX fields (`MODEL_RATE_EMOTION_VALUES_UNAMBIGUOUS_SMO`, `MODEL_RATE_EMOTION_VALUES_FULL_SMO`, etc.). Confusion matrix classes concatenated with `rbind` (`C1`, `C2`, `C3`, etc.). Classification results reported with names in first array (`C1`, `C2`, `C3`, etc.), and recycled in each subsequent model.

```         
MODEL_RATE_EMOTION_VALUES_UNAMBIGUOUS_SMO = {
rbind(
    C1 = c('C1' = 52.6, 'C2' = 17.1, 'C3' = 0.0, 'C4' = 9.2, 'C5' = 21.1),
    C2 = c(12, 65.2, 7.6, 4.3, 10.9),
    C3 = c(1.1,9.9,73.6,14.3,1.1),
    C4 = c(3.6,10.8,16.9,61.5,7.2),
    C5 = c(21.9,19.2,0,6.8,52.1)
 )
}
MODEL_RATE_EMOTION_VALUES_FULL_SMO = {
rbind(
    C1 = c('C1' = 56.0, 'C2' = 19, 'C3' = 0.0, 'C4' = 7, 'C5' = 18),
    C2 = c(11.3,58.9,13.7,4,12.1),
    C3 = c(0,13.2,68.6,18.2,0),
    C4 = c(4.9,11.7,22.5,54.2,6.7),
    C5 = c(18.5,12.2,1,12.2,56.1)
  )
},
MODEL_RATE_EMOTION_VALUES_FULL_FULLPOLYGONAL = { rbind(
  C1 = c('C1' = 65, 'C2' = 11, 'C3' = 12, 'C4' = 0, 'C5' = 12),
  C2 = c(14.5, 62.1, 22.6, 0.8, 0),
  C3 = c(0, 13.2, 68.6, 18.2, 0),
  C4 = c(0.8, 0, 20.8, 54.2, 24.2),
  C5 = c(38.8, 1, 0, 8.2, 52)
)
},
MODEL_RATE_EMOTION_VALUES_FULL_REDUCEDPOLYGONAL = { 
rbind(
  C1 = c('C1' = 67, 'C2' = 16, 'C3' = 4, 'C4' = 0, 'C5' = 13),
  C2 = c(21.8,55.6,22.6,0,0),
  C3 = c(0,9.1,77.7,13.2,0),
  C4 = c(0,0,23.3,55,21.6),
  C5 = c(27.5,0,0,10.2,62.3)
)
}
```

## MODEL_VALIDATION

Validation method used (if applicable). E.g., 10-fold cross validation. Leave one out cross validation. **TODO**: Discuss train/test/validation formatting. When using external validation set, report name? E.g., AcousticBrainz (`alvarez2023ri`)

### 2024-05-31 analysis/analysis.qmd
added preregistration text nearly complete

# Analysis

Initial work to build the data parser from the bibTeX files.

## Read annotated data

```{r}
# preprocessing step for list fields in bibtex files:
source('stripLFFromList.R') # helper function
stripLFFromList(fn = "../studies/test_orig.bib")
library(bib2df) # this parser seems to be give a lot warnings/errors with this data
#anno <- bib2df("../studies/metaMER_library_extraction_first_pass.bib")
anno <- bib2df("../studies/test_orig_strip.bib")
anno
anno<-data.frame(anno)
#anno$MODEL_RATE_EMOTION_VALUES
x <- eval(parse(text = anno$MODEL_RATE_EMOTION_VALUES))
x
anno$MODEL_LIST<-list(x)
anno$MODEL_LIST

length(anno$MODEL_LIST[[1]])

# select two regression studies: grekow2021mu and chen2017co
#anno_ex <- dplyr::filter(anno,BIBTEXKEY=='grekow2021mu'|BIBTEXKEY=='chen2017co')
```

Use paradigm field to process regression and classification studies separately.

We need to identify the core values:
- correlation (obtained from $R^2$)
- n (we use STIMULUS_N rather than participant n)

## Convert / Extract fields

```{r}
# create parser that gets the R2 measures out of the nested data

```

## Analyse

### Regression studies

### Valence

```{r}
# eval: false
library(dmetar)
library(tidyverse)
library(meta)

# select regression studies

m.cor <- metacor(cor = valence, 
                 n = stimulus_N,
                 studlab = study_id,
                 data = df,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 method.random.ci = "HK",
                 title = "MER: Regression: Valence: All")

```

### 2024-05-31 preregistration/preregistration.qmd
added preregistration text nearly complete

@@
-## Meta-analysis title: To what degree music emotion recognition
+This preregistration is made with `preregr` package from [https://preregr.opens.science/](https://preregr.opens.science/) that implements the BMJ published guidance for meta-analysis protocols ([Shamseer et al., 2015](https://doi.org/10.1136/bmj.g7647)).
 
-## Authors: TE + CA + MS ? (to be decided)
+```{r}
+#| echo: false
+#| output: false
+# prereg_metaMER.R
+# One option to register meta-analysis (rigorous one)
+# T.E. 15/5/2024
+#
+# see
+# https://preregr.opens.science/index.html (package)
+# https://www.bmj.com/content/349/bmj.g7647 (instructions from BMJ for PRISMA-P
 
-## Brief rationale
+#### Initialize ----------
 
-To assess what degree models are able to predict emotions in music, what models, what emotions, what genres, etc.
+metamer_prereg <-
+  preregr::prereg_initialize(
+    "genSysRev_v1"
+  );
 
-## Research objectives
+metamer_prereg$form$metadata$content[1]<-'Meta-analysis Pre-registration: Music Emotion Recognition'
 
-1. How good are MER models?
+preregr::prereg_next_item(
+  metamer_prereg,
+  nrOfItems = 4
+);
 
-2. What are the systematic biases of the models?
+#### Meta-data ----------
 
-3. How are models dealing with genres and cultures?
+metamer_prereg <-
+  metamer_prereg |>
+  preregr::prereg_specify(
+    title = "Music emotion recognition: Meta-analysis of regression and classification success of valence and arousal ratings from audio",
+    authors = "Eerola, T., Anderson, C.",
+    start_date = "2024-05-15",
+    tasks_and_roles = "equal contribution",
+    target_discipline = "music cognition, music information retrieval, music psychology"
+  ) |>
+  preregr::prereg_show_item_completion(
+    section="metadata"
+  );
+# validate
+metamer_prereg |>
+  preregr::prereg_show_item_content(
+    section="metadata"
+  );
 
-4. How generalisible are the models
+# show all
+metamer_prereg |>
+  preregr::prereg_show_item_completion(
+  );
 
-5. WEIRD
+metamer_prereg <-
+  metamer_prereg |>
+  preregr::prereg_specify(
+    type_of_review = "Meta-analysis",
+    review_stages = "Search, Screening, Extraction, Synthesis",
+    current_stage = "Screening",
+    start_date = "2024-05-15",
+    end_date = "2024-06-30",
+    background ="The aim is to establish the current state of the model success in predicting emotions expressed by music from audio.
+We will focus on the last 10 years of research and especially the research that has predicted valence and arousal ratings from music audio.
+No such analysis exists and there are interesting challenges in predicting emotional content of music that relates to specificity of the music and the type of emotions and features used that would benefit from a systematic analysis.",
+    primary_research_question = "To what degree can arousal and valence ratings of emotions expressed by music be predicted from audio?
+How are the prediction rates related to genres of music, the type of models used, the type of features, modelling design and cross-validation utilised, and the model complexity and parsimony?",
+    secondary_research_question = "What is the prediction rate related to classification of quadrants in the affective circumplex?",
+    expectations_hypotheses = "Prediction of arousal ratings is generally high and robust, and in terms of the model outcome metrics (correlation), achieves at least r = 0.77 (R square of 0.60).
+Prediction of valence ratings from audio is more challenging and more context dependent and will achieve generally a lower prediction rate, r = 0.63 (R square 0.40)",
+    dvs_outcomes_main_vars = "Regression model performance will be converted to pearson correlation coefficients and classification model performance will be converted to Matthews correlation coefficient (MCC) when possible.",
+    ivs_intervention_treatment = "Music genre, prediction type (linear or classification), feature type (based on prior work by Panda et al., 2020), model complexity (high, medium, low), model validation (exist or not)",
+    software = "R and Github repository",
+    funding = "Mitacs Globalink Research Award (Mitacs & British High Commission - Ottawa, Canada)",
+    cois = "There are no identified conflicts of interests.",
+    overlapping_authorships = "Not applicable"
+  )
 
-6. Theory orientations
+#### Search strategy --------
 
-FINER: feasible, interesting, novel, ethical, relevant [@browner2022de]
+metamer_prereg <-
+  metamer_prereg |>
+  preregr::prereg_specify(
+    databases = "Web of Science, Scopus, and Open Alex",
+    interfaces = "Web of Science, Scopus, and Open Alex",
+    grey_literature = "Not included",
+    inclusions_exclusion_criteria = "Sample, Phenomenon of Interest, Design, Evaluation, Research type",
+    query_strings = "<B>Scopus</B>: <code>TITLE-ABS-KEY ( valence OR arousal OR classi OR categor OR algorithm AND music <BR> AND emotion AND recognition ) AND PUBYEAR > 2013 AND PUBYEAR < 2025 AND <BR> ( LIMIT-TO ( DOCTYPE , \"ar\" ) ) </code><BR>
+    <B>Web of science</B>: <code> (DT=(Article) AND PY=(2014-2025)) AND ALL=(music <BR>emotion recognition valence arousal) </code>
+    <BR><B>Open Alex</B>: <code> https://openalex.org/works?page=1&filter=default.search%3A<BR>music%20emotion%20recognition%20valence%20arousal, <BR>type%3Atypes%2Farticle,publication_year%3A2014-2024,<BR> keywords.id%3Akeywords%2Femotion-recognition,<BR> keywords.id%3Akeywords%2Faffective-computing, language%3Alanguages%2Fen,<BR> open_access.any_repository_has_fulltext%3Atrue </code>",
+    search_validation_procedure = "Manual checking, separate keywords searches"
+  )
 
-## Hypotheses 
-We expect that the
+#### Screening --------
 
-## Eligibility criteria
-English, peer-reviewed journal articles indexed in X and Y, published between 20xx-20xx
+metamer_prereg <-
+  metamer_prereg |>
+  preregr::prereg_specify(
+    screening_stages = "We completed screening using custom fields inserted to the bibtex file and managed with citation managers (jabref and bibdesk).
+To filter relevant studies, we followed a three-stage screening procedure.
+<BR> <B>In stage 1</B>, we screened the 553 studies’ titles for relevance, removing irrelevant studies and recording exclusion criteria (see Used exclusion criteria).
+CA assigned 63 studies to the High Priority based on titles’ relevance, assigned 338 studies to Low Priority based on irrelevant titles, 152 studies to Medium Priority for additional screening.
+<BR><B>In stage 2</B>, CA assessed the 152 Medium Priority studies for relevance by screening abstracts.
+105 studies’ status changed to Low Priority, whereas 30 studies’ status changed to High Priority.
+27 studies remained in the Medium priority category.
+TE and CA evaluated the remaining 27 studies’, moving X to the High Priority Category and Y to the Medium Priority Category.
+For studies moved to Low Priority, brief BiBTex comments summarized the rationale for exclusion.
+<BR><B>In stage 3</B>, TE and CA independently screened Priority 1 studies for relevance, including an <I>include</I>, <I>exclude</I>, or <I>unsure</I> decision in a user-comment BiBTeX field.",
+    screened_fields_masking = "We left authors, titles, publication years, and journal names unmasked.",
+    used_exclusion_criteria = "We excluded studies according to the following exclusion criteria: soundscapes/vocalisations, non-music audio, video clips, physiological markers, dance, video/movie, physiological/EEG/ECG/MEG/GSR/brain imaging/heart rate/neuroscience/brain studies, sensor data, multimodal, autism, ageing, review/systematic review/overview/survey, face emotion recognition, mental health, music therapy, schizophrenia, memory/emotion factors as IVs, recommender systems, or systems that identify the location of emotional excerpts.",
+    screener_instructions = "As described above.",
+    screening_reliability = "In the pass 1 and 2, we will have a quality control check after the pass to discuss the identified categories.
+In the third pass, we double-coded decisions, resolving discrepancies through discussion.",
+    screening_reconciliation_procedure = "We reconciled discrepancies through discussion, resolving “unsure” votes first, followed by discrepancies in include/exclude decisions between authors Results of this updating procedure are available in the <A HREF=https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html>Pass 3 comparison document</A>.",
+    sampling_and_sample_size = "We identified and retained 553 articles from Scopus, Web of Science, and Open Alex based on the search strategy outlined above.
+See table at the end that details the cumulative exclusions.",
+screening_procedure_justification = "To offer a broad summary of music emotion recognition tasks, we attempted to include all studies involving prediction with acoustic features.
+We performed screening unblinded and determined inclusion/exclusion criteria based on studies’ relevance to the task explored.",
+screening_data_management_and_sharing = "Sources will be shared as (a) BibTeX library(ies) including reviewer notes."
+)
 
-## Database sources
+#### Section: Extraction ------
+metamer_prereg <-
+  metamer_prereg |>
+  preregr::prereg_specify(
+    entities_to_extract = "These are listed and defined in 
+    <A HREF=https://tuomaseerola.github.io/metaMER/studies/Extraction_details.html>Extraction details</A>.",
+    extraction_stages = "The data extraction done is stages.
+In the first stage, an extraction pass of the collection is done by ca using our initial entities to extract document.
+The challenges are discussed and the entities are revised.",
+    extractor_instructions = "See Extraction details.",
+    extractor_blinding = "Blinding was not used.",
+    extraction_reliability = "CA will perform extractions; TE will verify extractions for quality assurance.",
+    extraction_reconciliation_procedure = "NA",
+    extraction_procedure_justification = "TO BE DETAILED",
+    extraction_data_management_and_sharing = "We retain the information of the studies in shared bibtex files, extraction data will be stored in ascii data files (.R), and the analysis and manuscript will be available in quarto/markdown files, and all these are managed, structured, shared and documented in Github repository according to FAIR principles.",
+    misc_extraction_details = "NA"
+  )
 
-(PubMed, Web of Science, Scopus)
+#### Section: Synthesis and Quality Assessment -------
 
-## Search strategy
-Music emotion recognition
+metamer_prereg <-
+  metamer_prereg |>
+  preregr::prereg_specify(
+planned_data_transformations = "For regression studies, we convert all metrics to Pearson correlation coefficients.
+For classification studies, we convert the outcomes of classification to Matthews Correlation Coefficient (MCC) from the  precision, accuracy, specificity, F1 scores.
+Alternatively, we use Cohen’s kappa for multiple classes.",
+missing_data = "If no main outcome variables are available, we exclude the study.",
+data_validation = "None planned beyond the staged approached already documented in extraction process.",
+quality_assessment = "Not all the bias assessment tools for clinical studies are relevant for our purposes, we adapt the overall approached advocated in https://doi.org/10.1136/bmj.d5928 especially concerning #4.
+making our own risk of bias judgements transparent.",
+synthesis_plan = "We analyse regression and classification studies separately, and depending on the quantity of the studies forming suitable sub-groupings, we may further synthesise the results across groupings that are formed along feature sets or music genres",
+criteria_for_conclusions = "NA",
+synthesis_masking = "NA",
+synthesis_reliability = "NA",
+synthesis_reconciliation_procedure = "NA",
+publication_bias = "We utilise Egger's test to assess the publication bias and potentially correct the effect size bias by selecting 10% most precise effect sizes as recommended by Van Aert, Wicherts, & Van Assen (2019).",
+sensitivity_analysis = "Within regression and classificiation tasks, we will carry out sensitivity analysis using sub-groups of studied based on type of models, and the type of journal the studies were published in.",
+synthesis_procedure_justification = "TO BE DETAILED",
+synthesis_data_management_and_sharing = "We share the data, procedures, definitions, the analysis scripts with the outcomes as R code in Quarto notes at Github.",
+misc_synthesis_details = FALSE
+)
 
-## Analysis plan
+```
 
-Fixed effects model
-Tests of small study/publication bias
+```{r}
+#| echo: false
+#| output: true
+ preregr::prereg_knit_item_content(
+   metamer_prereg,
+)
+# Not needed now
+# export to html file
+# preregr::prereg_spec_to_html(
+#   metamer_prereg,file='preregistration.html',silent = TRUE
+# )
+```
+
+|                     | Cumulative Exclusions | Remaining Studies |
+| ------------------- | --------------------- | ----------------- |
+| Database Search     | NA                    | 553               |
+| Pass 1              | 338                   | 215               |
+| Pass 2              | 433                   | 120               |
+| Pass 2 (Discussion) | 457                   | 96                |
+| Pass 3 (Discussion) | 507                   | 46                |

### 2024-05-31 studies/extraction_details.qmd
update todos in extraction_details
added preregistration text nearly complete

@@
 
-## TYPE
-
-**TODO**: Remove? All are articles
-
 ## VOLUME
@@
 
-## PUBLICATION_STAGE
-
-**TODO:** Remove? All final.
-
 ## SOURCE
@@
 
-Paradigm used for MER task. Either classification or regression.
+Paradigm used for MER task. Either `classification` or `regression`.
 
@@
 List of emotion names or labels separated by commas. **TODO:** Discuss potential redundancies with `MODEL_RATE_EMOTION_NAMES`
-
-## EMOTION_LOCUS
-
-Perceived or felt **TODO:** Remove? All appear to be perceived
 
@@
 Names of categories analyzed features pertain to, based on names in Panda (2021).
-Includes names of all pertinent categories: *Melody*, *Rhythm*, *Timbre*, *Pitch*, *Tonality*, *Expressivity*, *Texture*, *Form*, *Vocal*, *High-Level* **TODO** Discuss feasibility of this approach.
-Other nominalizations/categories not covered (e.g., spectral, temporal, lyric)
+Includes names of all pertinent categories: *Melody*, *Rhythm*, *Timbre*, *Pitch*, *Tonality*, *Expressivity*, *Texture*, *Form*, *Vocal*, *High-Level*
+
+**TODO** Discuss feasibility of this approach. Other nominalizations/categories not covered (e.g., spectral, temporal, lyric)
 

### 2024-05-31 analysis/stripLFFromList.R

@@ -1,0 +1,19 @@
+stripLFFromList <- function(fn = NULL){
+  # T.E. 30/5/2024 for metaMER
+  fn_out <- stringr::str_replace(fn,'.bib','_strip.bib')
+  x <- readr::read_lines(fn)
+
+  # get the part we wish to modify, this will need to address multiple cases in the next version!
+  section_start <- which(stringr::str_detect(x,"list"))-1
+  section_end <- which(stringr::str_detect(x,"\\},"))  
+  section_end_index <- section_end > section_start
+  section_end<-section_end[section_end_index]
+  
+  # write back the file but with this section without separator
+  x2<-x[section_start:section_end]
+  readr::write_lines(x[1:(section_start-1)],file = fn_out)
+  readr::write_lines(x2,file = fn_out,sep = "",append = TRUE)
+  readr::write_lines("\n",file = fn_out,append = TRUE)
+  readr::write_lines(x[(section_end+1):length(x)],file = fn_out,append = TRUE)
+ 
+}

### 2024-06-04 studies/library_parser.qmd
add library parser

---
title: "Library Parser"
---

**Status** in progress.

# Pre-processing

## Preparing data

The follow code extracts information from the .bib library to format it as a `data.frame` for further processing. The code makes use of the stringr package and uses regular expressions to extract relevant parameters. First we read in the .bib file and use some string manipulations to retrieve the citation keys.

```{r results = 'hide'}
require(stringr)
```

```{r}
bib_file <- read.delim('metaMER_library_extraction_first_pass.bib',
           sep = '@', header = F)

# get citekeys from bibtex file:
citekeys <- unique(bib_file$V2)
# improve formatting
citekeys <- str_remove(citekeys, '\\{')
citekeys <- str_remove(citekeys, ',')
citekeys <- str_remove(citekeys, '%%.*$')
citekeys <- str_remove(citekeys, 'Article')
citekeys[citekeys ==''] <- NA
citekeys <- na.omit(citekeys)

```

*R* reads the .bib file as a two column data.frame, with the citation key appearing in the second column and the remaining metadata appearing in the first column. When the citation key appears in the second column, the corresponding row in the first column is blank. Because of this quirk, we can index metadata matching each citation key by keeping track of blank rows in the first column. We'll append each to a new entry of a list. The name of each list entry is the citation key; the corresponding value is the remaining unprocessed metadata.

```{r}
# find where new entries begin:
new_entries = which(bib_file$V2 != '')

# loop across unique indices for each entry
meta_list = list()
# loop across unique indices for each entry
meta_list = list()
for(this_entry in 1:(length(new_entries)-1))
{
  # get unique citekey
  this_cite_key <- citekeys[this_entry]
  # capture lines following citekey
  corresponding_lines <- bib_file[new_entries[this_entry]:new_entries[this_entry+1]-1,]$V1
  # store matching lines as data frame
  corresponding_lines <- data.frame(corresponding_lines)
  # assign lines distinct name
  names(corresponding_lines) <- this_cite_key
  # add to a list for further processing
  meta_list <- append(meta_list, corresponding_lines)
}

```

## Extracting Relevant .bib Fields

Not every bibtex field is equally useful for analysis. To facilitate data manipulation, we can save the names of the target fields separately in a .txt file, and use a regular expression to create a new column each time *R* finds one of the target fields in a string containing the bibtex metadata.

```{r}
# read in target bibtex fields
search_fields <- field_names <- readLines('bibtex_fields.txt')

# match casing in bibtex file
field_names <- toupper(field_names)
# add a pattern allowing us to find text between two adjacent bibtex fields
rep_pattern <- paste0(field_names[1:length(field_names)-1], '\\s*(.*?)\\s')
# apply this same pattern to all but the last of the field names                  
field_names[1:length(field_names)-1] <- rep_pattern
# collapse all the new field names into a single string for string manipulation with stringr
field_names[length(field_names)] <- paste0(field_names[length(field_names)], '.*')
field_names <- paste0(field_names, collapse = '')
```

## Prepare dataframe

Now we can convert our list into a data frame with the target bibtex fields. For the last field `MODEL_VALIDATION`, we will apply a different regex pattern which matches all characters following the field name `(?<=MODEL_VALIDATION).*` .

```{r}
# create new column containing information between two adjacent target fields for all entries in list
meta_df <- lapply(meta_list, function(x) str_match(toString(x), field_names))
# collapse list entries into rows
meta_df <- do.call('rbind', meta_df)
# format as a data.frame
meta_df <- data.frame(meta_df)
# match text after final column name
meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) str_match(toString(x), '(?<=MODEL_VALIDATION).*'))
# replace first column with citationkeys
meta_df[,1] <- names(meta_list)
names(meta_df) <- c('citekey', search_fields)
```

## Formatting

Finally, we'll perform some formatting to remove unwanted characters left over following the conversion (in progress)

```{r}
## remove bibtext field formatting
# remove curly braces
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\{')) 
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\}'))
# remove first '=' (from bibtex field )
meta_df <- apply(meta_df, 2, function(x) str_remove(x, '='))
# remove double-commas
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ',,'))
# remove comments
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '%%.*'))
meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ' , '))
meta_df <- as.data.frame(meta_df)
```

```{r}
knitr::kable(meta_df)
```

### 2024-06-04 studies/library_parser.qmd
update library parser

@@
 # create new column containing information between two adjacent target fields for all entries in list
-meta_df <- lapply(meta_list, function(x) str_match(toString(x), field_names))
+meta_df <- lapply(meta_list, function(x) str_match(paste0(x, collapse = ' '), field_names))
+meta_df <- lapply(meta_list, function(x) str_match(paste0(x, collapse = ' '), field_names))
+
 # collapse list entries into rows
@@
 # match text after final column name
-meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) str_match(toString(x), '(?<=MODEL_VALIDATION).*'))
+meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) str_match(paste0(x, collapse = ' '), '(?<=MODEL_VALIDATION).*'))
 # replace first column with citationkeys
@@
 meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\{')) 
-meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\}'))
+meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '\\},'))
 # remove first '=' (from bibtex field )
@@
 # remove double-commas
-meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ',,'))
+#meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ',,'))
 # remove comments
 meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, '%%.*'))
-meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ' , '))
+#meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ' , '))
 meta_df <- as.data.frame(meta_df)
@@
 ```
+Evaluate cell as r code example
+```{r}
+eval(parse(text = meta_df$model_rate_emotion_values[12]))
+```

### 2024-06-04 studies/library_parser.qmd
update parser

@@
 ```{r}
-eval(parse(text = meta_df$model_rate_emotion_values[12]))
+eval(parse(text = meta_df$model_rate_emotion_values[4]))
 ```
+
+# Dealing with nested bibtex fields.
+
+Some studies include multiple bibtex fields for substudies/evaluations of different feature sets. E.g., `MODEL_RATE_EMOTION_VALUES_A` and `MODEL_RATE_EMOTION_VALUES_B`.
+We need to apply special operations to separate these values for further analysis.
+
+```{r}
+## function to parse output of multiple models nested within a single cell
+parse_model_output = function(df)
+{ # loop across rows
+  # apply function to replace NAs with empty string
+  sapply(1:nrow(df), function(x) {
+    df$model_rate_emotion_values <- tidyr::replace_na(df$model_rate_emotion_values, '') # detect cells with rbind in them
+    if(str_count(df$model_rate_emotion_values[x], "rbind") > 1) {
+     # print(x)
+      # match first model (name between first underscore and rbind)
+      model_1_name <- str_match(df$model_rate_emotion_values[x], 
+                                "(?<=_).*?(?=rbind)")
+      # match subsequent models (name between MODEL_RATE_EMOTION_VALUES_ and rbind)
+      model_names <- str_extract_all(df$model_rate_emotion_values[x], 
+                                     "(?<=MODEL_RATE_EMOTION_VALUES_).*?(?=rbind)")
+      # combine names
+      model_names <- unlist(c(model_1_name, model_names))
+      # remove special characters
+      model_names <- gsub("[^[:alnum:]]", "", model_names)
+      # get corresponding values for each model
+      model_results <- str_split(df$model_rate_emotion_values[x], 
+                "MODEL_RATE_EMOTION_VALUES")
+      # get rid of everything up to "rbind"
+      model_results <- lapply(model_results, function(x) str_remove(x, 
+                                                          '.+?(?=rbind)'))
+      # now unlist the models and give them names to add later
+      model_results <- unlist(model_results)
+
+      # doesn't seem to work:
+       model_results <- paste(model_names, '=', model_results)
+      names(model_results) <- model_names
+     # return(model_results)
+    }
+    else { # otherwise, if dealing with non-listed, just return the existing value
+      model_results <- df$model_rate_emotion_values[x]
+    }
+    return(model_results)
+  }
+    )
+  # see whether rbind appears multiple times
+
+}
+
+# get results from nested models:
+model_outputs <- parse_model_output(meta_df)
+# assign unique names
+model_names <- lapply(model_outputs, names)
+
+```
+
+## Data Frame Expansion
+
+Next we want to duplicate the number of rows for each of the bibtex cells requiring
+special nesting
+
+```{r}
+# count the numbers 
+n_entries <- unlist(lapply(model_outputs, function(x) length(x)))
+# for those returning 0, change value to 1
+n_entries[n_entries == 0]<- 1
+# replicate rows based on number of models reported
+meta_df_unpacked <- meta_df[rep(seq_len(nrow(meta_df)), n_entries), ]
+# now overwrite model_rate_emotion_values with the output of parse_model_output
+meta_df_unpacked$model_rate_emotion_values <- unlist(model_outputs)
+
+```
+
+## Sanity check
+
+```{r}
+ex_substudy_1 <- eval(parse(text = meta_df_unpacked[7, 'model_rate_emotion_values']))
+ex_substudy_2 <- eval(parse(text = meta_df_unpacked[8, 'model_rate_emotion_values']))
+
+knitr::kable(rbind(ex_substudy_1, ex_substudy_2),
+             caption = sum(ex_substudy_1))
+```

### 2024-06-05 studies/library_parser.qmd
add functional version of parser

--- 2024-06-04 studies/library_parser.qmd
@@
 ```
+
 Evaluate cell as r code example
+
 ```{r}
-eval(parse(text = meta_df$model_rate_emotion_values[12]))
+eval(parse(text = meta_df$model_rate_emotion_values[4]))
 ```
+
+# Dealing with nested bibtex fields.
+
+Some studies include multiple bibtex fields for substudies/evaluations of different feature sets.
+E.g., `MODEL_RATE_EMOTION_VALUES_A` and `MODEL_RATE_EMOTION_VALUES_B`.
+We need to apply special operations to separate these values for further analysis.
+
+```{r}
+## function to parse output of multiple models nested within a single cell
+parse_model_output = function(df)
+{ # loop across rows
+  # apply function to replace NAs with empty string
+  sapply(1:nrow(df), function(x) {
+    df$model_rate_emotion_values <- tidyr::replace_na(df$model_rate_emotion_values, '') # detect cells with rbind in them
+    if(str_count(df$model_rate_emotion_values[x], "rbind") > 1) {
+      print('yes')
+      # match first model (name between first underscore and rbind)
+      model_1_name <- str_match(df$model_rate_emotion_values[x], 
+                                "(?<=_).*?(?=rbind)")
+      # match subsequent models (name between MODEL_RATE_EMOTION_VALUES_ and rbind)
+      model_names <- str_extract_all(df$model_rate_emotion_values[x], 
+                                     "(?<=MODEL_RATE_EMOTION_VALUES_).*?(?=rbind)")
+      # combine names
+      model_names <- unlist(c(model_1_name, model_names))
+      # remove special characters
+      model_names <- gsub("[^[:alnum:]]", "", model_names)
+      # get corresponding values for each model
+      model_results <- str_split(df$model_rate_emotion_values[x], 
+                "MODEL_RATE_EMOTION_VALUES")
+      # get rid of everything up to "rbind"
+      model_results <- lapply(model_results, function(x) str_remove(x, 
+                                                          '.+?(?=rbind)'))
+      # now unlist the models and give them names to add later
+      model_results <- unlist(model_results)
+       model_results <- paste(model_names, '=', model_results)
+      names(model_results) <- model_names
+     # return(model_results)
+    }
+    else { # otherwise, if dealing with non-listed, just return the existing value
+      model_results <- df$model_rate_emotion_values[x]
+    }
+    return(model_results)
+  }
+    )
+  # see whether rbind appears multiple times
+
+}
+
+# get results from nested models:
+model_outputs <- parse_model_output(meta_df)
+# assign unique names
+model_names <- lapply(model_outputs, names)
+
+```
+
+## Data Frame Expansion
+
+Next we want to copy the number of rows for each of the bibtex cells requiring special nesting
+
+```{r}
+# count the numbers 
+n_entries <- unlist(lapply(model_outputs, function(x) length(x)))
+# for those returning 0, change value to 1
+n_entries[n_entries == 0]<- 1
+# replicate rows based on number of models reported
+meta_df_unpacked <- meta_df[rep(seq_len(nrow(meta_df)), n_entries), ]
+# now overwrite model_rate_emotion_values with the output of parse_model_output
+meta_df_unpacked$model_rate_emotion_values <- unlist(model_outputs)
+
+```
+
+## Sanity check
+
+```{r}
+ex_substudy_1 <- eval(parse(text = meta_df_unpacked[7, 'model_rate_emotion_values']))
+ex_substudy_2 <- eval(parse(text = meta_df_unpacked[8, 'model_rate_emotion_values']))
+
+knitr::kable(rbind(ex_substudy_1, ex_substudy_2),
+             caption = sum(ex_substudy_1))
+```
+
+## Print output of all studies:
+
+```{r}
+sapply(1:nrow(meta_df_unpacked), function(i) {
+  print(i) 
+  print(eval(parse(text = meta_df_unpacked$model_rate_emotion_values[i])))
+}
+)
+```

### 2024-06-05 etc/scratchpad.R

@@ -1,0 +1,19 @@
+
+
+dimension_score_CV_testSet
+
+rbind(internal_validation_model = c('valence' = 0.34, 'arousal' = 0.79) ,
+      external_validation_model = c('valence' = 0.61, 'arousal' = 0.69)) -> temp
+
+
+# 1. rownames -> column [models tested]
+
+# parser: get (for example) arousal values for all studies, subpopulate models & n, etc.
+
+# from bibtex: create function that lets you retrieve target properties
+## return: study|model|outcomeMeasure|stimulusNumber... (compact version)
+
+temp[,stringr::str_detect(colnames(temp), 'valence|valence_R2')]
+temp[,stringr::str_detect(colnames(temp), 'arousal|arousal_R2')]
+
+temp[,'valence']

### 2024-06-07 studies/library_parser.qmd
add working regression example to library parser

@@
 
-**Status** in progress.
+**Status:** in progress.
+
+**TODO**: - Separate scripts and functions into separate .qmd files/directories. - Update `model_rate_emotion_values` nomenclature process for classification papers.
 
@@
 ```
+
+```{r}
+classification_studies = subset(meta_df_unpacked, paradigm == " classification  ")
+
+sapply(1:nrow(classification_studies), function(i) {
+  print(i) 
+  print(eval(parse(text = classification_studies$model_rate_emotion_values[i])))
+}
+)
+```
+
+```{r eval = F}
+regression_studies = subset(meta_df_unpacked, paradigm == " regression  ")
+
+sapply(1:nrow(regression_studies), function(i) {
+  print(i) 
+  print(eval(parse(text = regression_studies$model_rate_emotion_values[i])))
+}
+)
+```
+
+```{r}
+# low-level function to extract relevant values from named array
+model_result_2_df <- function(x) {
+  # get algorithm name from variable at beginning of string (before parsing)
+  toolbox <- trimws(stringr::str_extract(x, pattern = "[^\\=]+"))
+  print(toolbox)
+  # now evaluate the expression
+  x <- rlang::eval_tidy(rlang::parse_expr(x))
+  # get name of fitted models from column names
+  model_names <- colnames(x)
+  # print(model_names)
+  # split across model name for summary statistic (e.g., mean, sd, etc.)
+  model_statistic <- str_split(model_names, '\\.')
+  model_statistic <- unlist(lapply(model_statistic, function(x) x[2]))
+  # get values
+  model_values <- as.numeric(x)
+  # names(model_values) <- 'score'
+  print(model_values)
+  # get additional attributes (feature.data.exp)
+  model_attributes <- rownames(x)
+  print(model_attributes)
+  data.frame(model_attributes)
+  # get additional model details
+  model_attributes <- str_split_1(model_attributes, '\\.')
+  names(model_attributes) <- c('feature_id', 'data_id', 'experiment_id')
+  # split across '_' to 
+  model_measures <- data.frame(do.call('rbind', str_split(colnames(x), '_')))
+  print(model_measures)
+  names(model_measures) <- c('dimension', 'measure')
+  model_measures_split <- str_split(model_measures[,'measure'], '\\.')
+  model_measures[,'measure'] <- unlist(lapply(model_measures_split, 
+                                              function(x) x[1]))
+  return(data.frame(toolbox, 
+             t(model_attributes), 
+             model_measures, 
+             values = model_values,
+             statistic = model_statistic))
+}
+
+# high level function to apply model_result_2_df to multiple studies
+get_study_summaries <- function(df) {
+  do.call(rbind,
+          lapply(df$model_rate_emotion_values, 
+                 FUN = function(x) {
+                   study_id <- unique(df$citekey[which(df$model_rate_emotion_values == x)])
+                   model_results <- model_result_2_df(x)
+                   return(cbind(study_id, model_results))
+                   }
+                 )
+          )
+}
+
+```
+
+# Parsing Regression Studies
+
+The following functions provide a working example for converting the r code contained in `model_rate_emotion_values` to a data frame for further analysis (currently working for regression studies).
+
+### Template
+
+Encoded values should use the following nomenclature:
+
+```         
+library = rbind(features.data.exp = c(dim_measure.summary = 0.5, dim_measure.summary = 0.1), features.data.exp = c(dim_measure.summary = 0.2, dim_measure.summary = 0.5))
+
+# e.g.
+
+librosa = rbind(mfcc.msd.1 = c(valence_r2.mean = 0.5, arousal_r2.mean = 0.1), 
+temporal.msd.1 = c(valence_r2.mean = 0.2, arousal_r2.mean = 0.5,
+valence_r2.sd = 0.1, arousal_r2.sd = 0.1))
+```
+
+### Working example
+
+```{r}
+this_study <- data.frame(citekey = c('testStudy2023ab','testStudy2023ab', 'testStudy2020of'),
+  model_rate_emotion_values = c("marsyas = rbind(mfcc.msd.1 = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
+                                  valence_r2.sd = 0.4, arousal_r2.sd = 0.3,
+  valence_mse.mean = 0.3, arousal_mse.mean = 9.1))",
+  "librosa = rbind(mfcc.ismir.1 = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3,
+                                  valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
+  euclid_euclid.mean = 0.32, euclid_euclid.sd = 0.1))",
+  "mirtoolbox = rbind(pitch.filmMusic.2 = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
+)
+```
+
+### Summary data frame
+
+```{r}
+knitr::kable(get_study_summaries(this_study))
+```

### 2024-06-13 studies/library_parser.qmd
upload first pass extractions

--- 2024-06-05 studies/library_parser.qmd
@@
 ```
+
+```{r}
+classification_studies = subset(meta_df_unpacked, paradigm == " classification  ")
+
+sapply(1:nrow(classification_studies), function(i) {
+  print(i) 
+  print(eval(parse(text = classification_studies$model_rate_emotion_values[i])))
+}
+)
+```
+
+```{r eval = F}
+regression_studies = subset(meta_df_unpacked, paradigm == " regression  ")
+
+sapply(1:nrow(regression_studies), function(i) {
+  print(i) 
+  print(eval(parse(text = regression_studies$model_rate_emotion_values[i])))
+}
+)
+```
+
+```{r}
+# low-level function to extract relevant values from named array
+model_result_2_df <- function(x) {
+  # get algorithm name from variable at beginning of string (before parsing)
+  toolbox <- trimws(stringr::str_extract(x, pattern = "[^\\=]+"))
+  print(toolbox)
+  # now evaluate the expression
+  x <- rlang::eval_tidy(rlang::parse_expr(x))
+  # get name of fitted models from column names
+  model_names <- colnames(x)
+  # print(model_names)
+  # split across model name for summary statistic (e.g., mean, sd, etc.)
+  model_statistic <- str_split(model_names, '\\.')
+  model_statistic <- unlist(lapply(model_statistic, function(x) x[2]))
+  # get values
+  model_values <- as.numeric(x)
+  # names(model_values) <- 'score'
+  print(model_values)
+  # get additional attributes (feature.data.exp)
+  model_attributes <- rownames(x)
+  data.frame(model_attributes)
+  # get additional model details
+  model_attributes <- data.frame(do.call('rbind', str_split(model_attributes, '\\.')))
+  names(model_attributes) <- c('model_id', 'feature_id', 'data_id', 'experiment_id')
+  print(names(model_attributes))
+  # split across '_' to 
+  model_measures <- data.frame(do.call('rbind', stringr::str_split(colnames(x), '_')))
+  print(model_measures)
+  names(model_measures) <- c('dimension', 'measure')
+  model_measures_split <- stringr::str_split(model_measures[,'measure'], '\\.')
+  model_measures[,'measure'] <- unlist(lapply(model_measures_split, 
+                                              function(x) x[1]))
+  return(data.frame(toolbox, 
+             model_attributes, 
+             model_measures, 
+             values = model_values,
+             statistic = model_statistic))
+}
+
+# high level function to apply model_result_2_df to multiple studies
+get_study_summaries <- function(df) {
+  do.call(rbind,
+          lapply(df$model_rate_emotion_values, 
+                 FUN = function(x) {
+                   study_id <- unique(df$citekey[which(df$model_rate_emotion_values == x)])
+                   model_results <- model_result_2_df(x)
+                   return(cbind(study_id, model_results))
+                   }
+                 )
+          )
+}
+
+```
+
+# Parsing Regression Studies
+
+The following functions provide a working example for converting the r code contained in `model_rate_emotion_values` to a data frame for further analysis (currently working for regression studies).
+
+### Template
+
+Encoded values should use the following nomenclature:
+
+```         
+library = rbind(model.features.data.exp = c(dim_measure.summary = 0.5, dim_measure.summary = 0.1), model.features.data.exp = c(dim_measure.summary = 0.2, dim_measure.summary = 0.5))
+
+# e.g.
+
+librosa = rbind(randomforest.mfcc.msd.1 = c(valence_r2.mean = 0.5, arousal_r2.mean = 0.1), 
+temporal.msd.1 = c(valence_r2.mean = 0.2, arousal_r2.mean = 0.5,
+valence_r2.sd = 0.1, arousal_r2.sd = 0.1))
+```
+
+### Working example
+
+```{r}
+this_study <- data.frame(citekey = c('testStudy2023ab','testStudy2023ab', 'testStudy2020of'),
+  model_rate_emotion_values = c("marsyas = rbind('random forest.mfcc.msd.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
+                                  valence_r2.sd = 0.4, arousal_r2.sd = 0.3,
+  valence_mse.mean = 0.3, arousal_mse.mean = 9.1),
+  'random forest.mfcc.deam.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5))",
+  "librosa = rbind('linear regression.mfcc.ismir.1' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3,
+                                  valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
+  euclid_euclid.mean = 0.32, euclid_euclid.sd = 0.1))",
+  "mirtoolbox = rbind('neural net.pitch.filmMusic.2' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
+)
+```
+
+### Summary data frame
+
+```{r}
+knitr::kable(get_study_summaries(this_study))
+write.csv(get_study_summaries(this_study), "~/testcsv.csv")
+```

### 2024-06-14 preregistration/preregistration.qmd
update

@@
     <BR><B>Open Alex</B>: <code> https://openalex.org/works?page=1&filter=default.search%3A<BR>music%20emotion%20recognition%20valence%20arousal, <BR>type%3Atypes%2Farticle,publication_year%3A2014-2024,<BR> keywords.id%3Akeywords%2Femotion-recognition,<BR> keywords.id%3Akeywords%2Faffective-computing, language%3Alanguages%2Fen,<BR> open_access.any_repository_has_fulltext%3Atrue </code>",
-    search_validation_procedure = "Manual checking, separate keywords searches"
+    search_validation_procedure = "Manual checking, separate keywords searches",
+    other_search_strategies = "Not applied",
+    results_of_contacting_authors = "Not carried out",
+    search_expiration_and_repetition = "Searches were done during the active search period in late May early June 2024 and no repetition is planned.",
+    search_strategy_justification = "The three major databases should be able yield a robust picture of the topic",
+    misc_search_strategy_details = "No alternative searches were articulated or envisaged."
   )
@@
 27 studies remained in the Medium priority category.
-TE and CA evaluated the remaining 27 studies’, moving X to the High Priority Category and Y to the Medium Priority Category.
+TE and CA evaluated the remaining 27 studies’, moving 15 to the High Priority Category and 12 to the Medium Priority Category.
 For studies moved to Low Priority, brief BiBTex comments summarized the rationale for exclusion.
@@
 In the third pass, we double-coded decisions, resolving discrepancies through discussion.",
-    screening_reconciliation_procedure = "We reconciled discrepancies through discussion, resolving “unsure” votes first, followed by discrepancies in include/exclude decisions between authors Results of this updating procedure are available in the <A HREF=https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html>Pass 3 comparison document</A>.",
+    screening_reconciliation_procedure = "We reconcile discrepancies through discussion, resolving “unsure” votes first, followed by discrepancies in include/exclude decisions between authors Results of this updating procedure are available in the <A HREF=https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html>Pass 3 comparison document</A>.",
     sampling_and_sample_size = "We identified and retained 553 articles from Scopus, Web of Science, and Open Alex based on the search strategy outlined above.
@@
     entities_to_extract = "These are listed and defined in 
-    <A HREF=https://tuomaseerola.github.io/metaMER/studies/Extraction_details.html>Extraction details</A>.",
+    <A HREF=https://tuomaseerola.github.io/metaMER/studies/extraction_details.html>extraction details</A>.",
     extraction_stages = "The data extraction done is stages.
@@
 The challenges are discussed and the entities are revised.",
-    extractor_instructions = "See Extraction details.",
+    extractor_instructions = "See <A HREF=https://tuomaseerola.github.io/metaMER/studies/extraction_details.html>extraction details</A>.",
     extractor_blinding = "Blinding was not used.",
     extraction_reliability = "CA will perform extractions; TE will verify extractions for quality assurance.",
-    extraction_reconciliation_procedure = "NA",
-    extraction_procedure_justification = "TO BE DETAILED",
-    extraction_data_management_and_sharing = "We retain the information of the studies in shared bibtex files, extraction data will be stored in ascii data files (.R), and the analysis and manuscript will be available in quarto/markdown files, and all these are managed, structured, shared and documented in Github repository according to FAIR principles.",
+    extraction_reconciliation_procedure = "Discussion and joint decision for studies where extraction proves to be challenging and issues of interpretation arise.",
+    extraction_procedure_justification = "These are documented in the extraction details.",
+    extraction_data_management_and_sharing = "We retain the information of the studies in shared bibtex files, extraction data will be stored in ascii data files (.bibtex), and the parser for reading the data from .bibtex files to R for the analysis will be available (as quarto/markdown/R files), and all these are managed, structured, shared and documented in Github repository according to FAIR principles.",
     misc_extraction_details = "NA"
@@
 data_validation = "None planned beyond the staged approached already documented in extraction process.",
-quality_assessment = "Not all the bias assessment tools for clinical studies are relevant for our purposes, we adapt the overall approached advocated in https://doi.org/10.1136/bmj.d5928 especially concerning #4.
-making our own risk of bias judgements transparent.",
-synthesis_plan = "We analyse regression and classification studies separately, and depending on the quantity of the studies forming suitable sub-groupings, we may further synthesise the results across groupings that are formed along feature sets or music genres",
+quality_assessment = "Not all the bias assessment tools for clinical studies are relevant for our purposes, we adapt the overall approached advocated in <A [https://doi.org/10.1136/bmj.d5928](https://doi.org/10.1136/bmj.d5928) especially concerning #4.
+Making our own risk of bias judgements transparent.",
+synthesis_plan = "We analyse regression and classification studies separately, and depending on the quantity of the studies forming suitable sub-groupings based on techniques, materials or music collections/genres, we may further synthesise the results across groupings that are formed along these subsets.",
 criteria_for_conclusions = "NA",
@@
 sensitivity_analysis = "Within regression and classificiation tasks, we will carry out sensitivity analysis using sub-groups of studied based on type of models, and the type of journal the studies were published in.",
-synthesis_procedure_justification = "TO BE DETAILED",
+synthesis_procedure_justification = "We share our justification of the synthesis and the subsetting carried out in the manuscript but we have not formulated these in advance except for synthesizing classiciation and regression approaches separately and creating subsets within these approaches according to techniques and datasets utilised.",
 synthesis_data_management_and_sharing = "We share the data, procedures, definitions, the analysis scripts with the outcomes as R code in Quarto notes at Github.",

### 2024-06-14 manuscript/manuscript.qmd
prereg updated

@@
 ---
-title             : "Music Emotion Recognition..."
+title             : "Music Emotion Recognition: Meta-analysis"
 shorttitle        : "XXXXXXXXX"
@@
   - name          : "CA"
-    affiliation   : "2"
-    address       : "XXXXXX"
-    email         : "XXX@XXXX"
-  - name          : "MS"
     affiliation   : "2"
@@
 
+We preregistered our meta-analysis plan (OSF URL here and available also at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).
+
 # Results

### 2024-06-14 preregistration/preregistration.qmd
prereg updated

@@
   preregr::prereg_specify(
-    title = "Music emotion recognition: Meta-analysis of regression and classification success of valence and arousal ratings from audio",
+    title = "Music emotion recognition: Meta-analysis of regression and classification success of emotion ratings from audio",
     authors = "Eerola, T., Anderson, C.",
@@
 data_validation = "None planned beyond the staged approached already documented in extraction process.",
-quality_assessment = "Not all the bias assessment tools for clinical studies are relevant for our purposes, we adapt the overall approached advocated in <A [https://doi.org/10.1136/bmj.d5928](https://doi.org/10.1136/bmj.d5928) especially concerning #4.
-Making our own risk of bias judgements transparent.",
+quality_assessment = "Not all the bias assessment tools for clinical studies are relevant for our purposes, we adapt the overall approached advocated in [Higgins et al.
+(2011)]  (https://doi.org/10.1136/bmj.d5928).",
 synthesis_plan = "We analyse regression and classification studies separately, and depending on the quantity of the studies forming suitable sub-groupings based on techniques, materials or music collections/genres, we may further synthesise the results across groupings that are formed along these subsets.",
@@
 | Pass 3 (Discussion) | 507                   | 46                |
+
+## References
+
+- Higgins, J.
+P.
+T., Altman, D.
+G., Gøtzsche, P.
+C., Jüni, P., Moher, D., Oxman, A.
+D., Savović, J., Schulz, K.
+F., Weeks, L., & Sterne, J.
+A.
+C.
+(2011).
+The Cochrane Collaboration tool for assessing risk of bias in randomised trials.
+_BMJ, 343_.
+[https://www.bmj.com/content/343/bmj.d5928](https://www.bmj.com/content/343/bmj.d5928)
+
+- Shamseer, L., Moher, D., Clarke, M., Ghersi, D., Liberati, A., Petticrew, M., Shekelle, P., & Stewart, L.
+A.
+(2015).
+Preferred reporting items for systematic review and meta-analysis protocols (PRISMA-P) 2015: elaboration and explanation.
+_BMJ, 349_.
+[https://www.bmj.com/content/349/bmj.g7647](https://www.bmj.com/content/349/bmj.g7647)

### 2024-06-15 preregistration/preregistration.qmd
update prereg, extraction details

@@
     title = "Music emotion recognition: Meta-analysis of regression and classification success of emotion ratings from audio",
-    authors = "Eerola, T., Anderson, C.",
+    authors = "Eerola, T., Anderson, C. J.",
     start_date = "2024-05-15",
@@
 Prediction of valence ratings from audio is more challenging and more context dependent and will achieve generally a lower prediction rate, r = 0.63 (R square 0.40)",
-    dvs_outcomes_main_vars = "Regression model performance will be converted to pearson correlation coefficients and classification model performance will be converted to Matthews correlation coefficient (MCC) when possible.",
-    ivs_intervention_treatment = "Music genre, prediction type (linear or classification), feature type (based on prior work by Panda et al., 2020), model complexity (high, medium, low), model validation (exist or not)",
+    dvs_outcomes_main_vars = "Regression model performance will be converted to Pearson correlation coefficients and classification model performance will be converted to Matthews correlation coefficient (MCC) when possible.",
+    ivs_intervention_treatment = "Music genre, prediction type (linear or classification), feature type (based on prior work by Panda et al., 2020), model complexity (high, medium, low), model validation (exists or not)",
     software = "R and Github repository",
@@
 <BR> <B>In stage 1</B>, we screened the 553 studies’ titles for relevance, removing irrelevant studies and recording exclusion criteria (see Used exclusion criteria).
-CA assigned 63 studies to the High Priority based on titles’ relevance, assigned 338 studies to Low Priority based on irrelevant titles, 152 studies to Medium Priority for additional screening.
+CA assigned 63 studies to the High Priority based on titles’ relevance, assigned 338 studies to Low Priority based on irrelevant titles, and 152 studies to Medium Priority for additional screening.
 <BR><B>In stage 2</B>, CA assessed the 152 Medium Priority studies for relevance by screening abstracts.
-105 studies’ status changed to Low Priority, whereas 30 studies’ status changed to High Priority.
+95 studies’ status changed to Low Priority, whereas 30 studies’ status changed to High Priority.
 27 studies remained in the Medium priority category.
@@
     screened_fields_masking = "We left authors, titles, publication years, and journal names unmasked.",
-    used_exclusion_criteria = "We excluded studies according to the following exclusion criteria: soundscapes/vocalisations, non-music audio, video clips, physiological markers, dance, video/movie, physiological/EEG/ECG/MEG/GSR/brain imaging/heart rate/neuroscience/brain studies, sensor data, multimodal, autism, ageing, review/systematic review/overview/survey, face emotion recognition, mental health, music therapy, schizophrenia, memory/emotion factors as IVs, recommender systems, or systems that identify the location of emotional excerpts.",
+    used_exclusion_criteria = "We excluded studies according to the following exclusion criteria: soundscapes/vocalisations, non-music audio, video clips, physiological markers, dance, video/movie, physiological/EEG/ECG/MEG/GSR/brain imaging/heart rate/neuroscience/brain studies, sensor data, multimodal, autism, ageing, review/systematic review/overview/survey, face emotion recognition, mental health, music therapy, schizophrenia, memory/emotion factors as IVs, recommender systems, or systems that identify the location of emotional excerpts.
+We included results from some studies meeting exclusion criteria (e.g., multimodal studies involving physiological measurements) if they reported separately on acoustic-only models.",
     screener_instructions = "As described above.",
-    screening_reliability = "In the pass 1 and 2, we will have a quality control check after the pass to discuss the identified categories.
+    screening_reliability = "In the pass 1 and 2, we included a quality control check after the pass to discuss the identified categories.
 In the third pass, we double-coded decisions, resolving discrepancies through discussion.",
@@
     <A HREF=https://tuomaseerola.github.io/metaMER/studies/extraction_details.html>extraction details</A>.",
-    extraction_stages = "The data extraction done is stages.
-In the first stage, an extraction pass of the collection is done by ca using our initial entities to extract document.
+    extraction_stages = "The data extraction will be completed in stages.
+In the first stage, CA will complete a pass of the collection using our initial entities to extract document.
 The challenges are discussed and the entities are revised.",
@@
 
+- Panda, R., Malheiro, R., & Paiva, R. P. (2020). Audio features for music emotion recognition: a survey. IEEE Transactions on Affective Computing, 14(1), 68-88.
+[https://doi.org/10.1109/TAFFC.2020.3032373](https://doi.org/10.1109/TAFFC.2020.3032373)
+
 - Shamseer, L., Moher, D., Clarke, M., Ghersi, D., Liberati, A., Petticrew, M., Shekelle, P., & Stewart, L.

### 2024-06-15 studies/extraction_details.qmd
update prereg, extraction details

@@
 
-## PARADIGM
-
-Paradigm used for MER task. Either `classification` or `regression`.
-
 ## NOTES_AUTHORINITIALS
@@
 Decision and comments by respective author
-
-## EMOTIONS
-
-List of emotion names or labels separated by commas. **TODO:** Discuss potential redundancies with `MODEL_RATE_EMOTION_NAMES`
 
@@
 
-Number of stimuli employed in experiment.\
-**TODO** Discuss handling of subset selection, train, test, etc
+Number of stimuli employed in experiment. If multiple experimental conditions reported, separate $n$ by conditions where possible.
 
@@
 
-Number of features included in model. **TODO** Discuss handling of subset selection, train, test, etc
+Number of features included in data modeling (if available).
 
@@
 
-Total number of participants in experiment. **TODO** Discuss handling of secondary information. E.g., MediaEval
+Total number of participants in experiment.
 
@@
 
-Nature of rating/classification task undertaken by participants. E.g., rate, annotate. **TODO** discuss multi-stage studies. E.g., MediaEval categories validated by participants using AV ratings.
+Nature of rating/classification task undertaken by participants. E.g., rate, annotate.
 
@@
 
-**TODO** Discuss feasibility of this approach. Other nominalizations/categories not covered (e.g., spectral, temporal, lyric)
-
 ## FEATURE_SOURCE
 
-Name(s) of feature analysis toolboxes. **TODO** Discuss original features (as in `Panda2020no`)
+Name(s) of feature analysis toolbox(es).
 
@@
 
-Name of model type.
-One of regression, classification *TODO* Discuss redundancy with `PARADIGM`.
-Consider cases where regression and classification employed; or regression approach to classification (e.g., `sorussa2020em`)
+Name of model type (regression, classification, or both).
 
@@
 Additional information pertaining to predictive model, such as the name of algorithm used and other pertinent parameters.
-E.g., RandomForest, Commonality Analysis, Multiple Regression, Neural Networks, LDSM, etc.
-*TODO* Discuss how much information to include.
+E.g., Random Forest, Commonality Analysis, Multiple Regression, Neural Networks, LDSM.
 
@@
 
-Metric used in model evaluation. E.g., 'R2' for $R^2$, MSE, CCC, Classification accuracy, etc.
+Metric used in model evaluation. E.g., $R^2$, $MSE$, $CCC$, Classification accuracy, etc.
 
@@
 
-Additional information pertaining to predictive model. Format as R code when encoding multiple pertinent parameters. E.g., `c(training_epochs = 100, layer_n = c(1,2), lstm_units = c(124, 248))`
+Additional information pertaining to predictive model. E.g., `training epochs: 100; n layers: 1, 2; LSTM units: 124,248.`
 
@@
 Pertinent prediction of model summaries.
-Report as *R* arrays, including summary statistics in variables.
-When reporting results of multiple models, concatenate multiple entries with `rbind`.
+Report as *R* named arrays, including summary statistics in variables.
+When reporting results of multiple models, concatenate multiple entries with `mrbind`.
 When reporting results for different toolboxes or feature subsets, assign each to a new BiBTeX field with relevant identifier following final underscore.
-
-\### EXAMPLES:
-
-#### Regression
-
-Report relevant summary statistics in R code.
-Different feature distinguished through BiBTeX fields (`MODEL_RATE_EMOTION_VALUES_MFCC`, `MODEL_RATE_EMOTION_VALUES_ESSENTIA` ).
-Fitted models concatenated with `rbind` (`linear.regression`, `SMOreg`, `RNN1.124LSTM`, etc.).
-Model results reported with names in first array (`R2_arousal`, `MAE_arosal`, `R2_valence`, `MAE_valence`), and recycled in each subsequent model.
-
-```         
-MODEL_RATE_EMOTION_VALUES_MFCC = {
-  rbind(
-    linear.regression = c(R2_arousal = 0.61, MAE_arousal = 0.13, R2_valence = 0.07, MAE_valence = 0.17),
-    SMOreg = c(0.6,0.13,0.10,0.17),
-    RNN1.124LSTM = c(0.58,0.14,0.14,0.17),
-    RNN2.124.124LSTM = c(0.66,0.12,0.11,0.16),
-    RNN3.248LSTM = c(0.61,0.13,0.13,0.16),
-    RNN4.248.248LSTM = c(0.64,0.12,0.14,0.15)
-  )
-},
-MODEL_RATE_EMOTION_VALUES_ESSENTIA = {
-  rbind(
-    linear.regression = c(R2_arousal = 0.07, MAE_arousal = 0.25, R2_valence = 0.06, MAE_valence = 0.19),
-    SMOreg = c(0.48,0.18,0.27,0.17),
-    RNN1.124LSTM = c(0.54,0.14,0.21,0.16),
-    RNN2.124.124LSTM = c(0.67,0.12,0.32,0.13),
-    RNN3.248LSTM = c(0.58,0.14,0.32,0.14),
-    RNN4.248.248LSTM = c(0.69,0.11,0.40,0.13),
-    RNN5.529LSTM = c(0.61,0.13,0.29,0.15),
-    RNN6.529.529LSTM = c(0.68,0.12,0.36,0.14)
-  )
-}
-```
-
-#### Classification
-
-Report confusion matrices as *R* arrays.
-The following example classifies emotions into five categories for multiple feature subsets.
-Different feature distinguished through BiBTeX fields (`MODEL_RATE_EMOTION_VALUES_UNAMBIGUOUS_SMO`, `MODEL_RATE_EMOTION_VALUES_FULL_SMO`, etc.).
-Confusion matrix classes concatenated with `rbind` (`C1`, `C2`, `C3`, etc.).
-Classification results reported with names in first array (`C1`, `C2`, `C3`, etc.), and recycled in each subsequent model.
-
-```         
-MODEL_RATE_EMOTION_VALUES_UNAMBIGUOUS_SMO = {
-rbind(
-    C1 = c('C1' = 52.6, 'C2' = 17.1, 'C3' = 0.0, 'C4' = 9.2, 'C5' = 21.1),
-    C2 = c(12, 65.2, 7.6, 4.3, 10.9),
-    C3 = c(1.1,9.9,73.6,14.3,1.1),
-    C4 = c(3.6,10.8,16.9,61.5,7.2),
-    C5 = c(21.9,19.2,0,6.8,52.1)
- )
-}
-MODEL_RATE_EMOTION_VALUES_FULL_SMO = {
-rbind(
-    C1 = c('C1' = 56.0, 'C2' = 19, 'C3' = 0.0, 'C4' = 7, 'C5' = 18),
-    C2 = c(11.3,58.9,13.7,4,12.1),
-    C3 = c(0,13.2,68.6,18.2,0),
-    C4 = c(4.9,11.7,22.5,54.2,6.7),
-    C5 = c(18.5,12.2,1,12.2,56.1)
-  )
-},
-MODEL_RATE_EMOTION_VALUES_FULL_FULLPOLYGONAL = { rbind(
-  C1 = c('C1' = 65, 'C2' = 11, 'C3' = 12, 'C4' = 0, 'C5' = 12),
-  C2 = c(14.5, 62.1, 22.6, 0.8, 0),
-  C3 = c(0, 13.2, 68.6, 18.2, 0),
-  C4 = c(0.8, 0, 20.8, 54.2, 24.2),
-  C5 = c(38.8, 1, 0, 8.2, 52)
-)
-},
-MODEL_RATE_EMOTION_VALUES_FULL_REDUCEDPOLYGONAL = { 
-rbind(
-  C1 = c('C1' = 67, 'C2' = 16, 'C3' = 4, 'C4' = 0, 'C5' = 13),
-  C2 = c(21.8,55.6,22.6,0,0),
-  C3 = c(0,9.1,77.7,13.2,0),
-  C4 = c(0,0,23.3,55,21.6),
-  C5 = c(27.5,0,0,10.2,62.3)
-)
-}
-```
+See additional details below.
 
@@
 
-Validation method used (if applicable).
-E.g., 10-fold cross validation.
-Leave one out cross validation.
-**TODO**: Discuss train/test/validation formatting.
-When using external validation set, report name?
-E.g., AcousticBrainz (`alvarez2023ri`)
+Validation method used (if applicable). E.g., 10-fold cross validation, leave one out cross validation.
+
+# Encoding study results:
+
+### Regression
+
+Report relevant summary statistics in the `MODEL_RATE_EMOTION_VALUES` field in R code using the following format.
+Parameters delimited by spaces are later assigned to separate columns in the resulting dataframe.
+
+```         
+bind_field(
+library.model.features.data.experiment = c(dimension_measure.summaryStat = 0, ...),
+...
+)
+```
+
+## Classification
+
+Confusion matrices can be encoded similarly through a function that assigns relevant meta-parameters to the `model_parameters` attribute of the output matrix.
+The row names are then replaced with the column names for clearer output.
+This assumes row names and column names of the confusion matrix are listed in the same order.
+
+```         
+confusion_matrix(
+library.model.features.data.experiment =  c(class_1 = 0, class_2 = 0, ..., class_n = 0),
+class_2 = c(0, 0, ..., 0),
+...
+)
+```
+
+When confusion matrices are not available, encode available parameters (accuracy, precision, recall, $F$ scores, etc.) using the standard nomenclature to distinguish relevant outcomes for each class:
+
+```         
+bind_field(
+library.model.features.data.experiment = c(class_measure.summaryStat = 0, ...),
+...
+)
+```

### 2024-06-15 studies/library_parser.qmd
update prereg, extraction details

@@
 ```{r}
-bib_file <- read.delim('metaMER_library_extraction_first_pass.bib',
+bib_file <- read.delim('bib/extractions.bib',
            sep = '@', header = F)
@@
 #meta_df <- apply(meta_df, 2, function(x) str_remove_all(x, ' , '))
+# remove extra characters in final column
+meta_df[, ncol(meta_df)] = str_remove_all(meta_df[, ncol(meta_df)], '\\}')
 meta_df <- as.data.frame(meta_df)
+
 ```
@@
 ```{r}
-eval(parse(text = meta_df$model_rate_emotion_values[4]))
+eval(parse(text = meta_df$model_rate_emotion_values[22]))
 ```
@@
     if(str_count(df$model_rate_emotion_values[x], "rbind") > 1) {
-      print('yes')
       # match first model (name between first underscore and rbind)
@@
 knitr::kable(get_study_summaries(this_study))
-write.csv(get_study_summaries(this_study), "~/testcsv.csv")
 ```

### 2024-06-15 etc/scratchpad.R

@@ -1,19 +1,0 @@
-
-
-dimension_score_CV_testSet
-
-rbind(internal_validation_model = c('valence' = 0.34, 'arousal' = 0.79) ,
-      external_validation_model = c('valence' = 0.61, 'arousal' = 0.69)) -> temp
-
-
-# 1. rownames -> column [models tested]
-
-# parser: get (for example) arousal values for all studies, subpopulate models & n, etc.
-
-# from bibtex: create function that lets you retrieve target properties
-## return: study|model|outcomeMeasure|stimulusNumber... (compact version)
-
-temp[,stringr::str_detect(colnames(temp), 'valence|valence_R2')]
-temp[,stringr::str_detect(colnames(temp), 'arousal|arousal_R2')]
-
-temp[,'valence']

### 2024-06-17 studies/library_parser.qmd
add functionality for tracking extraction progress

@@
 
-**TODO**: - Separate scripts and functions into separate .qmd files/directories. - Update `model_rate_emotion_values` nomenclature process for classification papers.
+**TODO**: \
+- Separate scripts and functions into separate .qmd files/directories. \
+- Update `model_rate_emotion_values` nomenclature process for classification papers.\
+- Replace rbind with custom bind function throughout
 
@@
 ```{r results = 'hide'}
-require(stringr)
+library(stringr)
+library(knitr, include.only = 'kable')
 ```
@@
 # match text after final column name
-meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) str_match(paste0(x, collapse = ' '), '(?<=MODEL_VALIDATION).*'))
+meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) str_match(paste0(x, collapse = ' '), '(?<=FINAL_NOTES).*'))
 # replace first column with citationkeys
@@
 names(meta_df) <- c('citekey', search_fields)
+names(meta_df) <- trimws(names(meta_df))
 ```
@@
 
+# Track Excluded Studies (During Extraction)
+
+```{r}
+meta_df[which(str_detect(meta_df$final_notes, '!EXCL!')),] |> kable()
+```
+
+```{r}
+meta_df[-which(str_detect(meta_df$final_notes, '!EXCL!')),] -> included_studies
+
+included_studies |> kable()
+```
+
+# Track Incomplete Extractions
+
+Count studies where there are empty fields (exclude `final_notes` in count)
+
+```{r}
+check_missing <- function(n_empty_fields = 1) 
+{
+  included_studies[which(
+    rowSums(
+      sapply(
+        included_studies[,1:ncol(included_studies) - 1],
+        function(x) grepl("^\\s*$", x))) > n_empty_fields - 1),]
+}
+```
+
+```{r}
+## AT LEAST 1 MISSING FIELD
+check_missing() -> missing_1
+
+missing_1 |> kable()
+```
+
+```{r}
+## AT LEAST 2 MISSING FIELDS
+check_missing(2) -> missing_2
+
+missing_2 |> kable()
+```
+
+```{r}
+## AT LEAST 3 MISSING FIELDS
+check_missing(3) |> kable()
+```
+
 ```{r}
@@
 
-# Dealing with nested bibtex fields.
+# Outdated: Dealing with nested bibtex fields.
 
@@
 
-```{r}
+```{r eval = F}
 sapply(1:nrow(meta_df_unpacked), function(i) {
@@
 model_result_2_df <- function(x) {
-  # get algorithm name from variable at beginning of string (before parsing)
-  toolbox <- trimws(stringr::str_extract(x, pattern = "[^\\=]+"))
-  print(toolbox)
-  # now evaluate the expression
+  # evaluate the expression
   x <- rlang::eval_tidy(rlang::parse_expr(x))
@@
   model_attributes <- data.frame(do.call('rbind', str_split(model_attributes, '\\.')))
-  names(model_attributes) <- c('model_id', 'feature_id', 'data_id', 'experiment_id')
+  names(model_attributes) <- c('library_id', 'model_id', 'feature_id', 'data_id', 'experiment_id')
   print(names(model_attributes))
@@
                                               function(x) x[1]))
-  return(data.frame(toolbox, 
+  return(data.frame(
              model_attributes, 
@@
 ```         
-library = rbind(model.features.data.exp = c(dim_measure.summary = 0.5, dim_measure.summary = 0.1), model.features.data.exp = c(dim_measure.summary = 0.2, dim_measure.summary = 0.5))
+library = rbind(library.model.features.data.exp = c(dim_measure.summary = 0.5, dim_measure.summary = 0.1), library.model.features.data.exp = c(dim_measure.summary = 0.2, dim_measure.summary = 0.5))
 
@@
 
-librosa = rbind(randomforest.mfcc.msd.1 = c(valence_r2.mean = 0.5, arousal_r2.mean = 0.1), 
-temporal.msd.1 = c(valence_r2.mean = 0.2, arousal_r2.mean = 0.5,
+rbind(librosa.randomforest.mfcc.msd.1 = c(valence_r2.mean = 0.5, arousal_r2.mean = 0.1), 
+librosa.randomforest.temporal.msd.1 = c(valence_r2.mean = 0.2, arousal_r2.mean = 0.5,
 valence_r2.sd = 0.1, arousal_r2.sd = 0.1))
@@
 this_study <- data.frame(citekey = c('testStudy2023ab','testStudy2023ab', 'testStudy2020of'),
-  model_rate_emotion_values = c("marsyas = rbind('random forest.mfcc.msd.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
+  model_rate_emotion_values = c("rbind('marsyas.random forest.mfcc.msd.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
                                   valence_r2.sd = 0.4, arousal_r2.sd = 0.3,
@@
   'random forest.mfcc.deam.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5))",
-  "librosa = rbind('linear regression.mfcc.ismir.1' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3,
-                                  valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
+  "rbind('librosa.linear regression.mfcc.ismir.1' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3, valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
   euclid_euclid.mean = 0.32, euclid_euclid.sd = 0.1))",
-  "mirtoolbox = rbind('neural net.pitch.filmMusic.2' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
+  "rbind('mirtoolbox.neural net.pitch.filmMusic.2' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
 )

### 2024-06-17 studies/library_parser.qmd
add functionality for tracking extraction progress

@@
 
-# Track Excluded Studies (During Extraction)
+Example: Evaluate `model_rate_emotion_values` as *R* code
 
 ```{r}
-meta_df[which(str_detect(meta_df$final_notes, '!EXCL!')),] |> kable()
+eval(parse(text = meta_df$model_rate_emotion_values[22]))
+```
+
+## Track Excluded Studies (During Extraction)
+
+```{r}
+meta_df[which(str_detect(meta_df$final_notes, '!EXCL!')),] |> dplyr::tibble()
 ```
@@
 
-included_studies |> kable()
+included_studies |> dplyr::tibble()
 ```
@@
 
-missing_1 |> kable()
+missing_1 |> dplyr::tibble()
 ```
@@
 
-missing_2 |> kable()
+missing_2 |> dplyr::tibble()
 ```
@@
 ## AT LEAST 3 MISSING FIELDS
-check_missing(3) |> kable()
-```
-
-```{r}
-knitr::kable(meta_df)
-```
-
-Evaluate cell as r code example
-
-```{r}
-eval(parse(text = meta_df$model_rate_emotion_values[22]))
+check_missing(3) |> dplyr::tibble()
 ```
@@
 
-```{r}
+```{r eval = F, echo = F}
 ## function to parse output of multiple models nested within a single cell
@@
 
-```{r}
+```{r eval = F, echo = F}
 # count the numbers 
@@
 
-```{r}
-ex_substudy_1 <- eval(parse(text = meta_df_unpacked[7, 'model_rate_emotion_values']))
-ex_substudy_2 <- eval(parse(text = meta_df_unpacked[8, 'model_rate_emotion_values']))
-
-knitr::kable(rbind(ex_substudy_1, ex_substudy_2),
-             caption = sum(ex_substudy_1))
+```{r eval = F, echo = F}
+# ex_substudy_1 <- eval(parse(text = meta_df_unpacked[7, 'model_rate_emotion_values']))
+# ex_substudy_2 <- eval(parse(text = meta_df_unpacked[8, 'model_rate_emotion_values']))
 ```
@@
 
-```{r eval = F}
+```{r eval = F, echo = F}
 sapply(1:nrow(meta_df_unpacked), function(i) {
@@
 
-```{r}
+```{r eval = F, echo = F}
 classification_studies = subset(meta_df_unpacked, paradigm == " classification  ")
@@
 
-```{r eval = F}
+```{r eval = F, echo = F}
 regression_studies = subset(meta_df_unpacked, paradigm == " regression  ")
@@
 ```{r}
-knitr::kable(get_study_summaries(this_study))
+dplyr::tibble(get_study_summaries(this_study))
 ```

### 2024-06-18 manuscript/manuscript.qmd
deleted unnecessary css files

--- 2024-05-06 manuscript/manuscript.qmd
@@
 ---
-title             : "Music Emotion Recognition..."
-shorttitle        : "XXXXXXXXX"
+title             : "Meta-analysis of regression and classification success of emotion ratings from audio"
+shorttitle        : "Meta-analysis of music emotion recognition"
 
 author: 
-  - name          : "TE"
+  - name          : "Tuomas Eerola"
     affiliation   : "1"
@@
     email         : "tuomas.eerola@durham.ac.uk"
-  - name          : "CA"
+  - name          : "Cameron J. Anderson"
     affiliation   : "2"
-    address       : "XXXXXX"
-    email         : "XXX@XXXX"
-  - name          : "MS"
-    affiliation   : "2"
-    address       : "XXXXXX"
-    email         : "XXX@XXXX"
+    address       : "Department of Psychology, Neuroscience & Behaviour, McMaster University, Hamilton, ON, Canada"
+    email         : "andersoc@mcmaster.ca"
 
@@
   - id            : "2"
-    institution   : "XXXX, MacMaster University"
-
-note: ""
+    institution   : "Department of Psychology, Neuroscience & Behaviour, McMaster University"
 
 author_note: |
-  XXX.
+  Tuomas Eerola is at the Department of Music, Durham University, UK.
+  Cameron J. Anderson is at the Department of Psychology, Neuroscience & Behaviour, McMaster University, Canada.
 
 abstract: |
- blah blah blah.
+ This is a meta-analysis of music emotion recognition.
+An analysis of the articles published between 2014-2024 containing models predicting either valence and arousal or emotion categories was carried out.
+A total of xx studies were included
 
 keywords          : "music, emotion, recognition, meta-analysis"
-wordcount         : "XXXX"
+wordcount         : "5555"
 
@@
 
-blah blah [@anderson2022ex]
+- Emotional expression is one of the central reasons why people engage with music.
+
+- Great advances in music information retrieval have been made in recent years.
+
+- Numerous studies over the last 25 years have established what emotions listeners perceive and recognise in music [@gomez2021].
+In the last 15 years, it has become possible to trace the recognised emotions to musical contents such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013;@anderson2022ex;@grimaud_eerola_2022], or acoustic features [@yang2008;@panda2013multi;@saari_et_al_2015;@eerola2011c] or emergent properties identified through deep learning [@er2019music;@sarkar2020recognition].
+
+However, there is no consensus on to what degree emotions can be recognised by computational models and the literature to date paints a diverse picture of success for concepts in affective circumplex -- valence and arousal-- [@Russell1980] and classifying various emotion categories [@fu2010survey].
 
@@
 
-blah blah
+- Our aim is to establish the level of predictive accuracy for both continuous models of emotional expression (valence and arousal) and classification of emotion categories based on available and recent studies.
+- We seek to identify the types of issues (modelling techniques, features, and musical qualities used) that significantly influence the prediction rates.
+- To achieve these aims, we carry out a meta-analysis focused on journal articles published in the last 10 years.
+- We outline broad hypotheses such as arousal being predicted to a higher degree than valence, which is more challenging and more context dependent than arousal.
+For classification, simple utilitarian emotions (e.g., fear, anger) will be easier to predict than complex social emotions (e.g., sadness, nostalgia).
 
@@
 
-blah blah
+We preregistered our meta-analysis plan (OSF URL here, also available at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).
+
+In the search stage, we used three databases, _Web of Science_, _Scopus_, and _Open Alex_ to identify journal articles published between 2014 and 2024 containing keywords/title `valence OR arousal OR classi OR categor OR algorithm AND music
+ AND emotion AND recognition` (see specific search strings for each database in [SI](http://)). All searches were done in May 2024.
+
+The initial search yielded 553 potential studies, which were interactively screened for relevance in three stages by both authors, resulting in 46 studies that passed our inclusion criteria (define here: has included some form of emotion modelling with a set of features, and outcome measures such as $R^2$ or classification accuracy ($F1$ score or _precision_ or _recall_) and overall quality control; see [SI](http://) for a breakdown).
+After the screening stage, we define a set of entities to extract characterising music (genre, stimulus number [N], duration), features extracted (number, type, source, defined by [@panda2020audio]), model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, _MSE_, _MCC_), model complexity (???
+model architecture?), and type of model cross-validation.
+We converted all regression results into $R^2$ values for valence and arousal and classification results into Matthews correlation coefficient [_MCC_, @chicco2020advantages].
 
@@
 
-blah blah
+First we could describe the overall pattern of data (modelling techniques, cross-validation, popular datasets, etc).
+
+We first report regression studies that predict valence and arousal.
+
+## Prediction success for valence and arousal
+
+Out of XX studies reporting this task, the majority (xx%) ...
+
+| Concept | N    | Md $R^2$|
+|:--------|:-----|:--------|
+| Valence | ??   | ??      |
+| Arousal | ??   | ??      |
+
+TABLE: xxxx
 
@@
 
-blah blah
+To be done.
 
@@
 
-The authors...
+CA was funded by Mitacs Globalink Research Award (Mitacs & British High Commission - Ottawa, Canada).
 
@@
 
-XXXX.
+Study preregistration, data, analysis scripts and supporting information is available at Github, [https://tuomaseerola.github.io/metaMER](https://tuomaseerola.github.io/metaMER).
 
@@
 
-xxxxx.
+We thank Greggs food-on-the-go retailer for sustaining the work with affordable sandwiches and coffee.
 

### 2024-06-18 data/anderson2022ex.R

@@ -1,23 +1,0 @@
-study_id <- 'anderson2020ex'
-emotion_type <- 'dimensional'
-emotion_list <- c('valence','arousal')
-emotion_locus <- 'perceived'
-stimulus_type <- 'classical'
-stimulus_duration <- 20
-stimulus_N <- 24
-participant_N <- 35
-participant_expertise <- 'non-musicians'
-participant_origin <- 'Canada'
-participant_sampling <- 'convenience'
-participant_task <- 'rating'
-feature_list <- c('attack rate','pitch height','mode')
-feature_validation <- c('annotation')
-feature_source <- NA
-model_type <- c('commonality analysis')
-model_measure <- 'rsquared'
-model_complexity_parameters <- 4
-model_rate_emotion_list <- c(0.00,0.00)
-model_validation <- 'none'
-meta_comments <- 'demo study'
-meta_encoder <- 'TE'
-meta_date <- '3/5/2024'

### 2024-06-18 data/battcock2021em.R

@@ -1,23 +1,0 @@
-study_id <- 'battcock2021em'
-emotion_type <- 'dimensional'
-emotion_list <- c('valence','arousal')
-emotion_locus <- 'perceived'
-stimulus_type <- 'classical'
-stimulus_duration <- 20
-stimulus_N <- 48
-participant_N <- 30
-participant_expertise <- 'musicians'
-participant_origin <- 'Canada'
-participant_sampling <- 'convenience'
-participant_task <- 'rating'
-feature_list<- c('attack rate','pitch height','mode')
-feature_validation <- c('annotation')
-feature_source <- NA
-model_type <- c('commonality analysis','regression')
-model_measure <- 'rsquared'
-model_complexity_parameters <- 4
-model_rate_emotion_list <- c(0.8334,0.5429)
-model_validation <- 'none'
-meta_comments <- 'demo study 2'
-meta_encoder <- 'TE'
-meta_date <- '3/5/2024'

### 2024-06-18 index.qmd
links added to index

@@
 
+The public-facing version of the repository is available at
+[https://tuomaseerola.github.io/metaMER/](https://tuomaseerola.github.io/metaMER/)
+
 ## Plan
 
-We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd).
+We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has beeb preregistered at [OSF]().
 
@@
 
-Data coding and extraction is described in data template [data/template.qmd](data/template.qmd).
+Data extraction is described in [extraction details](studies/extraction_details.qmd). See also [pass3 comparison ](studies/pass3_comparison.qmd).
+
+The data will be parsed to tabular format using a custom [library_parser.qmd](studies/library_parser.qmd).
 

### 2024-06-19 analysis/analysis.qmd
add scripts for analyzing studies

@@
 
-Initial work to build the data parser from the bibTeX files.
+This assumes that the data has been parsed from the BibTeX files into table and exported as CSV file.
 
@@
 
+## Read annotated data
+
+- Update 2024-06-19
+- TODO: find better way to read in functions
+
 ```{r}
-# preprocessing step for list fields in bibtex files:
-source('stripLFFromList.R') # helper function
-stripLFFromList(fn = "../studies/test_orig.bib")
-library(bib2df) # this parser seems to be give a lot warnings/errors with this data
-#anno <- bib2df("../studies/metaMER_library_extraction_first_pass.bib")
-anno <- bib2df("../studies/test_orig_strip.bib")
-anno
-anno<-data.frame(anno)
-#anno$MODEL_RATE_EMOTION_VALUES
-x <- eval(parse(text = anno$MODEL_RATE_EMOTION_VALUES))
-x
-anno$MODEL_LIST<-list(x)
-anno$MODEL_LIST
-
-length(anno$MODEL_LIST[[1]])
-
-# select two regression studies: grekow2021mu and chen2017co
-#anno_ex <- dplyr::filter(anno,BIBTEXKEY=='grekow2021mu'|BIBTEXKEY=='chen2017co')
+require(here)
+source(here::here('R/build-df.R'))
+source(here::here('R/format-study-results.R'))
+source(here::here('R/parse-model-output.R'))
 ```
 
-Use paradigm field to process regression and classification studies separately.
+```{r}
+# get metaMER df:
 
-We need to identify the core values:
-- correlation (obtained from $R^2$)
+meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))
+
+# get included studies
+
+included_studies <- meta_df[which(
+  !stringr::str_detect(meta_df$final_notes, '!EXCL!')),] |> 
+  dplyr::tibble()
+
+```
+
+```{r}
+# get studies re-coded (currently identifiable by presence of bind_field.)
+recoded_studies <- included_studies[which(stringr::str_detect(
+  included_studies$model_rate_emotion_values,
+                                     'bind_field')),]
+
+```
+
+```{r}
+metaMER_results <- do.call(rbind,
+lapply(recoded_studies$model_rate_emotion_values, 
+       parse_model_output)
+)
+
+metaMER_results |> dplyr::tibble()
+
+```
+
+```{r}
+#| eval: false
+d <- read.csv('data/meta-analysis_data.csv')
+```
+
+We need to identify the core metrics:
+
+- _correlation coefficient_ (obtained from $R^2$) for regression studies.
+
+- _Matthew's correlation coefficient_ for classification studies.
+
 - n (we use STIMULUS_N rather than participant n)
 
-## Convert / Extract fields
-
-```{r}
-# create parser that gets the R2 measures out of the nested data
-
-```
+- Subsetting base on model and music qualities
 
@@
 
-### Valence
+#### Valence
 
 ```{r}
-# eval: false
+#| warning: false
+#| eval: false
 library(dmetar)

### 2024-06-19 R/build-df.R

@@ -1,0 +1,94 @@
+
+# Build database ----------------------------------------------------------
+
+## TODO: figure out why 4 studies don't read, document
+
+get_metaMER_df <- function(path_2_studies = here::here('studies')) {
+
+bib_file <- read.delim(paste0(path_2_studies, '/bib/extractions.bib'),
+                       sep = '@', header = F)
+
+# get citekeys from bibtex file:
+citekeys <- unique(bib_file$V2)
+# improve formatting
+citekeys <- stringr::str_remove(citekeys, '\\{')
+citekeys <- stringr::str_remove(citekeys, ',')
+citekeys <- stringr::str_remove(citekeys, '%%.*$')
+citekeys <- stringr::str_remove(citekeys, 'Article')
+citekeys[citekeys ==''] <- NA
+citekeys <- na.omit(citekeys)
+
+# find where new entries begin:
+new_entries = which(bib_file$V2 != '')
+
+# loop across unique indices for each entry
+meta_list = list()
+# loop across unique indices for each entry
+meta_list = list()
+for(this_entry in 1:(length(new_entries)-1))
+{
+  # get unique citekey
+  this_cite_key <- citekeys[this_entry]
+  # capture lines following citekey
+  corresponding_lines <- bib_file[new_entries[this_entry]:new_entries[this_entry+1]-1,]$V1
+  # store matching lines as data frame
+  corresponding_lines <- data.frame(corresponding_lines)
+  # assign lines distinct name
+  names(corresponding_lines) <- this_cite_key
+  # add to a list for further processing
+  meta_list <- append(meta_list, corresponding_lines)
+}
+
+# read in target bibtex fields
+search_fields <- field_names <- readLines(paste0(path_2_studies, '/bibtex_fields.txt'))
+
+# match casing in bibtex file
+field_names <- toupper(field_names)
+# add a pattern allowing us to find text between two adjacent bibtex fields
+rep_pattern <- paste0(field_names[1:length(field_names)-1], '\\s*(.*?)\\s')
+# apply this same pattern to all but the last of the field names                  
+field_names[1:length(field_names)-1] <- rep_pattern
+# collapse all the new field names into a single string for string manipulation with stringr
+field_names[length(field_names)] <- paste0(field_names[length(field_names)], '.*')
[…]

### 2024-06-19 R/parse-model-output.R

@@ -1,0 +1,42 @@
+## TODO: document
+
+# low-level function to extract relevant values from named array
+parse_model_output <- function(x) {
+  # evaluate the expression
+  x <- rlang::eval_tidy(rlang::parse_expr(x))
+  # get name of fitted models from column names
+  model_names <- colnames(x)
+  # print(model_names)
+  # split across model name for summary statistic (e.g., mean, sd, etc.)
+  model_statistic <- stringr::str_split(model_names, '\\.')
+  model_statistic <- unlist(lapply(model_statistic, function(x) x[2]))
+  # get values
+  model_values <- as.numeric(x)
+  # names(model_values) <- 'score'
+  print(model_values)
+  # get additional attributes (feature.data.exp)
+  model_attributes <- rownames(x)
+  data.frame(model_attributes)
+  # get additional model details
+  model_attributes <- data.frame(do.call('rbind', stringr::str_split(model_attributes, '\\.')))
+  names(model_attributes) <- c('library_id', 'model_id', 'feature_id', 'data_id', 'experiment_id')
+  print(names(model_attributes))
+  # split across '_' to 
+  model_measures <- data.frame(do.call('rbind', stringr::str_split(colnames(x), '_')))
+  print(model_measures)
+  names(model_measures) <- c('dimension', 'measure')
+  model_measures_split <- stringr::str_split(model_measures[,'measure'], '\\.')
+  model_measures[,'measure'] <- unlist(lapply(model_measures_split, 
+                                              function(x) x[1]))
+  return(data.frame(
+    model_attributes, 
+    model_measures, 
+    values = model_values,
+    statistic = model_statistic))
+}
+
+
+build_study_summary <- function(df) {
+  do.call(rbind, lapply(df[,'model_rate_emotion_values'], 
+                        parse_model_output))
+} 

### 2024-06-19 analysis/analysis.qmd
Revert "add scripts for analyzing studies"
This reverts commit 3084d02d6801829214a90e2b7cbeaa6daf7c9640.

@@
 ## Read annotated data
-
-## Read annotated data
-
-- Update 2024-06-19
-- TODO: find better way to read in functions
-
-```{r}
-require(here)
-source(here::here('R/build-df.R'))
-source(here::here('R/format-study-results.R'))
-source(here::here('R/parse-model-output.R'))
-```
-
-```{r}
-# get metaMER df:
-
-meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))
-
-# get included studies
-
-included_studies <- meta_df[which(
-  !stringr::str_detect(meta_df$final_notes, '!EXCL!')),] |> 
-  dplyr::tibble()
-
-```
-
-```{r}
-# get studies re-coded (currently identifiable by presence of bind_field.)
-recoded_studies <- included_studies[which(stringr::str_detect(
-  included_studies$model_rate_emotion_values,
-                                     'bind_field')),]
-
-```
-
-```{r}
-metaMER_results <- do.call(rbind,
-lapply(recoded_studies$model_rate_emotion_values, 
-       parse_model_output)
-)
-
-metaMER_results |> dplyr::tibble()
-
-```
 

### 2024-06-19 R/build-df.R

@@ -1,94 +1,0 @@
-
-# Build database ----------------------------------------------------------
-
-## TODO: figure out why 4 studies don't read, document
-
-get_metaMER_df <- function(path_2_studies = here::here('studies')) {
-
-bib_file <- read.delim(paste0(path_2_studies, '/bib/extractions.bib'),
-                       sep = '@', header = F)
-
-# get citekeys from bibtex file:
-citekeys <- unique(bib_file$V2)
-# improve formatting
-citekeys <- stringr::str_remove(citekeys, '\\{')
-citekeys <- stringr::str_remove(citekeys, ',')
-citekeys <- stringr::str_remove(citekeys, '%%.*$')
-citekeys <- stringr::str_remove(citekeys, 'Article')
-citekeys[citekeys ==''] <- NA
-citekeys <- na.omit(citekeys)
-
-# find where new entries begin:
-new_entries = which(bib_file$V2 != '')
-
-# loop across unique indices for each entry
-meta_list = list()
-# loop across unique indices for each entry
-meta_list = list()
-for(this_entry in 1:(length(new_entries)-1))
-{
-  # get unique citekey
-  this_cite_key <- citekeys[this_entry]
-  # capture lines following citekey
-  corresponding_lines <- bib_file[new_entries[this_entry]:new_entries[this_entry+1]-1,]$V1
-  # store matching lines as data frame
-  corresponding_lines <- data.frame(corresponding_lines)
-  # assign lines distinct name
-  names(corresponding_lines) <- this_cite_key
-  # add to a list for further processing
-  meta_list <- append(meta_list, corresponding_lines)
-}
-
-# read in target bibtex fields
-search_fields <- field_names <- readLines(paste0(path_2_studies, '/bibtex_fields.txt'))
-
-# match casing in bibtex file
-field_names <- toupper(field_names)
-# add a pattern allowing us to find text between two adjacent bibtex fields
-rep_pattern <- paste0(field_names[1:length(field_names)-1], '\\s*(.*?)\\s')
-# apply this same pattern to all but the last of the field names                  
-field_names[1:length(field_names)-1] <- rep_pattern
-# collapse all the new field names into a single string for string manipulation with stringr
-field_names[length(field_names)] <- paste0(field_names[length(field_names)], '.*')
[…]

### 2024-06-19 R/parse-model-output.R

@@ -1,42 +1,0 @@
-## TODO: document
-
-# low-level function to extract relevant values from named array
-parse_model_output <- function(x) {
-  # evaluate the expression
-  x <- rlang::eval_tidy(rlang::parse_expr(x))
-  # get name of fitted models from column names
-  model_names <- colnames(x)
-  # print(model_names)
-  # split across model name for summary statistic (e.g., mean, sd, etc.)
-  model_statistic <- stringr::str_split(model_names, '\\.')
-  model_statistic <- unlist(lapply(model_statistic, function(x) x[2]))
-  # get values
-  model_values <- as.numeric(x)
-  # names(model_values) <- 'score'
-  print(model_values)
-  # get additional attributes (feature.data.exp)
-  model_attributes <- rownames(x)
-  data.frame(model_attributes)
-  # get additional model details
-  model_attributes <- data.frame(do.call('rbind', stringr::str_split(model_attributes, '\\.')))
-  names(model_attributes) <- c('library_id', 'model_id', 'feature_id', 'data_id', 'experiment_id')
-  print(names(model_attributes))
-  # split across '_' to 
-  model_measures <- data.frame(do.call('rbind', stringr::str_split(colnames(x), '_')))
-  print(model_measures)
-  names(model_measures) <- c('dimension', 'measure')
-  model_measures_split <- stringr::str_split(model_measures[,'measure'], '\\.')
-  model_measures[,'measure'] <- unlist(lapply(model_measures_split, 
-                                              function(x) x[1]))
-  return(data.frame(
-    model_attributes, 
-    model_measures, 
-    values = model_values,
-    statistic = model_statistic))
-}
-
-
-build_study_summary <- function(df) {
-  do.call(rbind, lapply(df[,'model_rate_emotion_values'], 
-                        parse_model_output))
-} 

### 2024-06-19 studies/library_parser.qmd
undo previous commit

@@
 
-**TODO**: \
+**TODO**: 
 - Separate scripts and functions into separate .qmd files/directories. \
@@
 Now we can convert our list into a data frame with the target bibtex fields.
-For the last field `MODEL_VALIDATION`, we will apply a different regex pattern which matches all characters following the field name `(?<=MODEL_VALIDATION).*` .
+For the last field `FINAL_NOTES`, we will apply a different regex pattern which matches all characters following the field name `(?<=FINAL_NOTES).*` .
 
 ```{r}
+Sys.sleep(1)
 # create new column containing information between two adjacent target fields for all entries in list
@@
 ```{r}
+Sys.sleep(1)
 ## remove bibtext field formatting
@@
 
-included_studies |> dplyr::tibble()
+included_studies |> dplyr::tibble() #|> View()
+```
+# Track studies to discuss
+```{r}
+included_studies[str_detect(included_studies$final_notes, 'DISCUSS|Discuss|discuss'),] 
+```
+
+## Updates following discussion
+```{r}
+included_studies[str_detect(included_studies$final_notes, 'DISCUSS|Discuss|discuss'),]
+
+resolution_comments <- c(
+  'Report total # of features 8904',
+  'Report available statistics (new nomenclature solves issue)',
+  'Report as many features are there are in MEM n = 260',
+  'Report best model results (Rprop)',
+  'Report available statistics (new nomenclature solves issue)',
+  'Report on proposed model',
+  'Report 50 PCA features'
+)
+
+included_studies[str_detect(included_studies$final_notes, 'DISCUSS|Discuss|discuss'),]$final_notes <- resolution_comments
+
+```
+
+# Track Reformatted Extractions
+
+```{r}
+included_studies[which(stringr::str_detect(included_studies$model_rate_emotion_values,
+                                     'bind_field')),] -> reencoded
+
+message('Completed re-encodings for ', nrow(reencoded), ' studies')
+
+reencoded
+
 ```
@@
 ```{r}
-check_missing <- function(n_empty_fields = 1) 
+check_missing_fields <- function(n_empty_fields = 1) 
 {
@@
 ## function to parse output of multiple models nested within a single cell
-parse_model_output = function(df)
+get_nested_studies = function(df)
 { # loop across rows
@@
 # low-level function to extract relevant values from named array
-model_result_2_df <- function(x) {
+parse_model_output <- function(x) {
   # evaluate the expression

### 2024-06-19 analysis/format_study_results.R

@@ -1,150 +1,0 @@
-# ============================================================================ #
-#' Match names and lengths of one-dimensional data, padding with NAs.
-#' 
-#' @usage match_named_values(c('a' = 1, 'b' = 2, 'c' = 3), c('a' = 2, 'c' = 4))
-#' @param ... Inputs of named arrays, data frames, or lists of named arrays. All classes must be the same.
-#' 
-#' @return Matrix array of input with matched names
-#' 
-#' @examples
-#' 
-#' a = c(
-#'  name1 = 0.48, name2 = 0.32, name3 = 0.22)
-#' b = 1:3
-#' c = 5:7
-#' x <- c('a' = 1, 'b' = 2, 'c' = 2)
-#' y <- c('a' = 5, 'c' = 4)
-#' z <- c('b' = 1)
-#' list_arrays(list(x),list(y),list(z))
-#' list_arrays(a,z) 
-#'
-#'
-# input same for each
-#' match_input_dims(x,y,z)
-#' match_input_dims(data.frame(x),data.frame(y),data.frame(z))
-#' match_input_dims(list(x), list(y), list(z))
-#' match_input_dims(list(x,y,z))
-#' match_input_dims(list(x,y), list(z))
-#' match_input_dims(list(x), list(y,z))
-#' # sensitive to input order (row-wise but not col-wise):
-#' match_input_dims(list(z,y,x))
-#'
-#'
-#'
-#' match_named_values(c,a)
-#' match_named_values(a,c)
-#' match_named_values(a,z)
-#' match_named_values(x,y,z)
-#'                   
-#'     
-#' 
-list_arrays <- function(...) {
-  input <- list(...)
-  if(length(unique(sapply(input, mode))) > 1) {
-    stop('All inputs must be of same data type.')
-  } else if(all(sapply(input, is.data.frame))) { # check if all inputs are dfs
-    # check if combining dataframes with more than one dimension
-    if(any(sapply(input, function(x) dim(x)[2]) > 1)) { 
-      stop('All input dataframes must be one dimensional.')
-    }
-    # convert dataframes to named arrays
-    input <- lapply(input, function(x) {
-      x_names <- rownames(x)
-      x <- unlist(x)
-      names(x) <- x_names
-      return(x)
-    }
-    )
-  }
-  # check if inputs are all lists
-  else if(all(sapply(input, is.list))) {
-    # if so, unlist each list separately (convert to arrays)
-    input <- unlist(input, recursive = F)
-  }
-  return(input)
-}
[…]

### 2024-06-19 R/format-study-results.R
update extractions

@@ -1,0 +1,150 @@
+# ============================================================================ #
+#' Match names and lengths of one-dimensional data, padding with NAs.
+#' 
+#' @usage match_named_values(c('a' = 1, 'b' = 2, 'c' = 3), c('a' = 2, 'c' = 4))
+#' @param ... Inputs of named arrays, data frames, or lists of named arrays. All classes must be the same.
+#' 
+#' @return Matrix array of input with matched names
+#' 
+#' @examples
+#' 
+#' a = c(
+#'  name1 = 0.48, name2 = 0.32, name3 = 0.22)
+#' b = 1:3
+#' c = 5:7
+#' x <- c('a' = 1, 'b' = 2, 'c' = 2)
+#' y <- c('a' = 5, 'c' = 4)
+#' z <- c('b' = 1)
+#' list_arrays(list(x),list(y),list(z))
+#' list_arrays(a,z) 
+#'
+#'
+# input same for each
+#' match_input_dims(x,y,z)
+#' match_input_dims(data.frame(x),data.frame(y),data.frame(z))
+#' match_input_dims(list(x), list(y), list(z))
+#' match_input_dims(list(x,y,z))
+#' match_input_dims(list(x,y), list(z))
+#' match_input_dims(list(x), list(y,z))
+#' # sensitive to input order (row-wise but not col-wise):
+#' match_input_dims(list(z,y,x))
+#'
+#'
+#'
+#' match_named_values(c,a)
+#' match_named_values(a,c)
+#' match_named_values(a,z)
+#' match_named_values(x,y,z)
+#'                   
+#'     
+#' 
+list_arrays <- function(...) {
+  input <- list(...)
+  if(length(unique(sapply(input, mode))) > 1) {
+    stop('All inputs must be of same data type.')
+  } else if(all(sapply(input, is.data.frame))) { # check if all inputs are dfs
+    # check if combining dataframes with more than one dimension
+    if(any(sapply(input, function(x) dim(x)[2]) > 1)) { 
+      stop('All input dataframes must be one dimensional.')
+    }
+    # convert dataframes to named arrays
+    input <- lapply(input, function(x) {
+      x_names <- rownames(x)
+      x <- unlist(x)
+      names(x) <- x_names
+      return(x)
+    }
+    )
+  }
+  # check if inputs are all lists
+  else if(all(sapply(input, is.list))) {
+    # if so, unlist each list separately (convert to arrays)
+    input <- unlist(input, recursive = F)
+  }
+  return(input)
+}
[…]

### 2024-06-19 R/parse-model-output.R
update analysis functions

@@ -36,7 +36,15 @@ parse_model_output <- function(x) {
 }
 
 
-build_study_summary <- function(df) {
-  do.call(rbind, lapply(df[,'model_rate_emotion_values'], 
-                        parse_model_output))
-} 
+get_study_results <- function(study) {
+  citekey <- unique(as.character(study[,'citekey']))
+  #print(citekey)
+  #print(as.character(study[,'model_rate_emotion_values']))
+  results <- parse_model_output(as.character(study[,'model_rate_emotion_values']))
+  return(
+    dplyr::tibble(citekey,
+            results)
+    )
+}
+
+

### 2024-06-19 analysis/analysis.qmd
update extractions
update analysis functions

--- 2024-06-19 analysis/analysis.qmd
@@
 
-## Read annotated data
+# Analysis
+
+Initial work to build the data parser from the bibTeX files.
 
@@
 ```{r}
-metaMER_results <- do.call(rbind,
-lapply(recoded_studies$model_rate_emotion_values, 
-       parse_model_output)
+metaMER_results <-
+do.call(
+  rbind,
+    lapply(1:nrow(recoded_studies),
+       function(x) get_study_results(recoded_studies[x,])
+       )
 )
@@
 ```
+
+## Read annotated data
 

### 2024-06-20 R/parse-model-output.R
fix issues with parse-model-output.R (spotcheck pending)

@@ -11,19 +11,17 @@ parse_model_output <- function(x) {
   model_statistic <- stringr::str_split(model_names, '\\.')
   model_statistic <- unlist(lapply(model_statistic, function(x) x[2]))
   # get values
-  model_values <- as.numeric(x)
+  model_values <- as.numeric(t(x))
   # names(model_values) <- 'score'
-  print(model_values)
+  #print(model_values)
   # get additional attributes (feature.data.exp)
-  model_attributes <- rownames(x)
-  data.frame(model_attributes)
+  model_attributes <- rep(rownames(x), each = ncol(x))
   # get additional model details
   model_attributes <- data.frame(do.call('rbind', stringr::str_split(model_attributes, '\\.')))
   names(model_attributes) <- c('library_id', 'model_id', 'feature_id', 'data_id', 'experiment_id')
   print(names(model_attributes))
   # split across '_' to 
   model_measures <- data.frame(do.call('rbind', stringr::str_split(colnames(x), '_')))
-  print(model_measures)
   names(model_measures) <- c('dimension', 'measure')
   model_measures_split <- stringr::str_split(model_measures[,'measure'], '\\.')
   model_measures[,'measure'] <- unlist(lapply(model_measures_split, 
@@ -31,8 +29,8 @@ parse_model_output <- function(x) {
   return(data.frame(
     model_attributes, 
     model_measures, 
-    values = model_values,
-    statistic = model_statistic))
+    statistic = model_statistic,
+    values = model_values))
 }
 
 

### 2024-06-20 analysis/analysis.qmd

@@
 
-# Analysis
-
-Initial work to build the data parser from the bibTeX files.
-
 ## Read annotated data
@@
 - Update 2024-06-19
-- TODO: find better way to read in functions
+- [ ] CA TODO: find better way to read in functions
 
@@
 
+- [ ] CA ToDo: Check the warning reported here
+
 ```{r}
 # get metaMER df:
-
 meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))
@@
 # get included studies
-
 included_studies <- meta_df[which(
@@
 ```
+### Recoded
 
@@
 ```
+
+Maybe limit the verbosity of `get_study_results` below
 
@@
 
-## Read annotated data
+## Summarise annotated data
 
 ```{r}
-#| eval: false
-d <- read.csv('data/meta-analysis_data.csv')
+#| eval: true
+#| output: asis
+
+print(knitr::kable(table(metaMER_results$citekey,metaMER_results$dimension)))
+print(knitr::kable(table(metaMER_results$citekey,metaMER_results$model_id)))
+print(knitr::kable(table(metaMER_results$citekey,metaMER_results$feature_id)))
+print(knitr::kable(table(metaMER_results$citekey,metaMER_results$data_id)))
+
 ```
 
-We need to identify the core metrics:
+## Analysis notes
 
-- _correlation coefficient_ (obtained from $R^2$) for regression studies.
-
-- _Matthew's correlation coefficient_ for classification studies.
-
-- n (we use STIMULUS_N rather than participant n)
-
-- Subsetting base on model and music qualities
-
-## Analyse
+- [ ] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
+- [ ] Issue 2: We `stimulus_N`
+- [ ] Issue 3: measure vs statistic?
+- [ ] Issue 4: We need to classify the modelling techniques into fewer number of techniques
+- [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)
 
@@
 #| warning: false
-#| eval: false
+#| eval: true
 library(dmetar)
@@
 
-# select regression studies
+# select regression studies with r2
+tmp <- dplyr::filter(metaMER_results,dimension=="valence" & measure=="r2")
+#sqrt(tmp$values) # convert from R^2 to r
+tmp$stimulus_n <- 100 # ad-hoc for now
 
-m.cor <- metacor(cor = valence, 
-                 n = stimulus_N,
-                 studlab = study_id,
-                 data = df,
+m.cor <- metacor(cor = sqrt(values), 
+                 n = stimulus_n,
+                 studlab = citekey,
+                 data = tmp,
                  fixed = FALSE,
                  random = TRUE,
-                 method.tau = "REML",
+                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                  method.random.ci = "HK", 
@@
 
+print(m.cor)
 ```
+
+## Explore qualities
+
+```{r}
+meta <- metagen(values, sqrt(values), 
+                data = tmp, 
+                studlab = tmp$citekey, 
+                comb.fixed = FALSE, 
+                method.tau = "PM")
+find.outliers(meta)
+infan <- InfluenceAnalysis(meta)
+print(eggers.test(meta))
+
+```
+
+## Sub-group analysis (based on model type)
+
+```{r}
+
+meta <- metagen(values, sqrt(values), # Fix the TE.se 
+                data = tmp, 
+                studlab = tmp$citekey, 
+                comb.fixed = FALSE, 
+                method.tau = "PM")
+
+subgroup.analysis.mixed.effects(x = meta, 
+                                subgroups = tmp$model_id)
+```
+
+## Visualise
+
+```{r}
+plot(m.cor)
+plot(eggers.test(meta))
+
+```

### 2024-06-20 index.qmd

@@
 
-We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has beeb preregistered at [OSF]().
+We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has beeb preregistered at [https://osf.io/6y3dr/](https://osf.io/6y3dr/).
 
-## Study Search and Selection
+### Study Search and Selection
 
@@
 
-## Data Extraction and Coding
+### Data Extraction and Coding
 
@@
 
-The data will be parsed to tabular format using a custom [library_parser.qmd](studies/library_parser.qmd).
+The data will be parsed to a tabular format using a custom [library_parser.qmd](studies/library_parser.qmd).
 
-## Analysis
+### Analysis
 
@@
 
-## Manuscript
+### Manuscript
 

### 2024-06-24 analysis/analysis.qmd
added updated analysis
update get_study_results, add unique ids to analysis.Qmd

@@
 - Update 2024-06-19
-- [ ] CA TODO: find better way to read in functions
+- [ ] CA TODO later (if at all): find better way to read in functions
 
@@
 )
+
+# add unique identifiers
+
+unique_id <- apply(metaMER_results[,c('citekey',
+                        'library_id',
+                         'model_id',
+                         'feature_id',
+                         'data_id',
+                         'experiment_id')],
+                      1, 
+                      paste0, 
+                      collapse = '-'
+) 
+metaMER_results$unique_id <- stringr::str_remove_all(unique_id, 
+                                                     ' ')
+
+metaMER_results <- metaMER_results |> dplyr::select(unique_id, 
+                                 dplyr::everything())
 

### 2024-06-24 R/parse-model-output.R

@@ -19,14 +19,14 @@ parse_model_output <- function(x) {
   # get additional model details
   model_attributes <- data.frame(do.call('rbind', stringr::str_split(model_attributes, '\\.')))
   names(model_attributes) <- c('library_id', 'model_id', 'feature_id', 'data_id', 'experiment_id')
-  print(names(model_attributes))
+  #print(names(model_attributes))
   # split across '_' to 
   model_measures <- data.frame(do.call('rbind', stringr::str_split(colnames(x), '_')))
   names(model_measures) <- c('dimension', 'measure')
   model_measures_split <- stringr::str_split(model_measures[,'measure'], '\\.')
   model_measures[,'measure'] <- unlist(lapply(model_measures_split, 
                                               function(x) x[1]))
-  return(data.frame(
+  invisible(data.frame(
     model_attributes, 
     model_measures, 
     statistic = model_statistic,
@@ -36,13 +36,26 @@ parse_model_output <- function(x) {
 
 get_study_results <- function(study) {
   citekey <- unique(as.character(study[,'citekey']))
+  stimulus_n <- unique(as.character(study[,'stimulus_n']))
+  feature_n <- unique(as.character(study[,'feature_n']))
+  participant_n <- unique(as.character(study[,'participant_n']))
+  
   #print(citekey)
   #print(as.character(study[,'model_rate_emotion_values']))
-  results <- parse_model_output(as.character(study[,'model_rate_emotion_values']))
+  results <- parse_model_output(as.character(
+    study[,'model_rate_emotion_values'])
+    )
+  
   return(
-    dplyr::tibble(citekey,
-            results)
+    dplyr::tibble(
+      citekey,
+      stimulus_n,
+      feature_n,
+      participant_n,
+      results)
     )
 }
+
+
 
 

### 2024-06-25 analysis/analysis.qmd
New analysis pilot

@@
 
-- [ ] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
-- [ ] Issue 2: We `stimulus_N`
-- [ ] Issue 3: measure vs statistic?
-- [ ] Issue 4: We need to classify the modelling techniques into fewer number of techniques
+- [x] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
+- [x] Issue 2: We `stimulus_N`
+- [x] Issue 3: measure vs statistic?
+- [x] Issue 4: We need to classify the modelling techniques into fewer number of techniques (example given, but no principles defined)
 - [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)
+
+- [ ] If the _number of stimuli_ varies, divide either to separate experiments or use the largest value (see below for ad-hoc solution).
 
@@
 tmp <- dplyr::filter(metaMER_results,dimension=="valence" & measure=="r2")
+
+# Temporary clarification of N
+tmp$stimulus_n[tmp$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "]<-1000
+tmp$stimulus_n[tmp$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "]<-2372
+tmp$stimulus_n[tmp$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "]<-40
+tmp$stimulus_n <- as.numeric(tmp$stimulus_n)
+
 #sqrt(tmp$values) # convert from R^2 to r
-tmp$stimulus_n <- 100 # ad-hoc for now
+#tmp$stimulus_n <- 100 # ad-hoc for now
 
@@
 ```{r}
+#| eval: true
 
+# divide models into random forests, SVM and MLR
+tmp$model_class_id <- 'MLR/PLS'
+tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression')]<-'RF'
+tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR')]<-'SVM'
+table(tmp$model_class_id)
 meta <- metagen(values, sqrt(values), # Fix the TE.se 
@@
 subgroup.analysis.mixed.effects(x = meta, 
-                                subgroups = tmp$model_id)
+                                subgroups = tmp$model_class_id)
 ```

### 2024-06-26 R/parse-model-output.R
add function for summarizing confusion matrices

@@ -34,6 +34,35 @@ parse_model_output <- function(x) {
 }
 
 
+
+summarize_matrix = function(matrix) {
+  # convert named array to table
+  class_table <- as.table(matrix)
+  # make row and column names consistent
+  rownames(class_table) <- colnames(class_table)
+  # get confusion matrix output from caret
+  confusion_results <- caret::confusionMatrix(class_table)
+  # calculate mcc
+  confusion_mcc <- yardstick::mcc(confusion_results$table)$.estimate
+  names(confusion_mcc) <- 'mcc'
+  # combine data summaries
+  confusion_summary <- append(confusion_results$overall,
+                              confusion_mcc)
+  # make nomenclature consistent with regression studies
+  names(confusion_summary) <- paste0('classification_', 
+                                     names(confusion_summary))
+  # for two consecutive capitalized words, delimit with '.' and lowercase
+  # e.g. Classification_AccuracyPvalue becomes classification_accuracy.pvalue
+  names(confusion_summary) <- tolower(
+    gsub("([a-z])([A-Z])", "\\1.\\2", 
+         names(confusion_summary)
+    )
+  )
+  
+  return(confusion_summary)
+}
+
+
 get_study_results <- function(study) {
   citekey <- unique(as.character(study[,'citekey']))
   stimulus_n <- unique(as.character(study[,'stimulus_n']))

### 2024-06-26 R/format-study-results.R
add helper function for concise classification matrix formatting

@@ -140,11 +140,36 @@ bind_field <- function(...) {
   else return(recycled_names)
 }
 
-confusion_matrix <- function(..., class_names) {
-  confusion_matrix <- bind_field(...) 
-  class_names <- colnames(confusion_matrix)
-  attributes(confusion_matrix)$meta_details <- rownames(confusion_matrix)
-  rownames(confusion_matrix) <- class_names
-  return(confusion_matrix)
+
+## function to make n x n matrix from partially named array
+# d: optional argument specifying n x n dimensionality
+unflatten <- function(..., d) {
+  # put inputs into array
+  x <- c(...)
+  # check if blanks within names
+  if('' %in% names(x)) {
+    # if so, find them, and repeat existing non-blank names (assumed recycling)
+    x_names <- names(x)[!names(x) %in% '']
+    names(x) <- rep(x_names, length.out = length(x))
+  }
+  # if user doesn't specify dimensionality, infer it from n unique names
+  if(missing(d)) {
+    d <- length(unique(names(x)))
+  }
+  # convert to n x n matrix
+  mat <- matrix(x, nrow = d, ncol = d)
+  # make sure names of rows and columns identical
+  rownames(mat) <- colnames(mat) <- unique(names(x))
+  return(mat)
 }
+
+
+
+# confusion_matrix <- function(..., class_names) {
+#   confusion_matrix <- bind_field(...) 
+#   class_names <- colnames(confusion_matrix)
+#   attributes(confusion_matrix)$meta_details <- rownames(confusion_matrix)
+#   rownames(confusion_matrix) <- class_names
+#   return(confusion_matrix)
+# }
 

### 2024-06-26 R/format-study-results.R
update unflatten function
- (1) Make function stop if n elements does not match n rows * n cols. (2) Return transpose of matrix to ensure actual and predicted classes correctly formatted

@@ -157,9 +157,13 @@ unflatten <- function(..., d) {
     d <- length(unique(names(x)))
   }
   # convert to n x n matrix
+  #print(length(x))
+  if(length(x) != d*d) stop('Length of elements not equal to nrow * ncol of matrix')
   mat <- matrix(x, nrow = d, ncol = d)
   # make sure names of rows and columns identical
   rownames(mat) <- colnames(mat) <- unique(names(x))
+  # transpose matrix 
+  mat <- t(mat)
   return(mat)
 }
 

### 2024-06-26 R/format-study-results.R
rename argument in unflatten function

@@ -143,7 +143,7 @@ bind_field <- function(...) {
 
 ## function to make n x n matrix from partially named array
 # d: optional argument specifying n x n dimensionality
-unflatten <- function(..., d) {
+unflatten <- function(..., dim_length) {
   # put inputs into array
   x <- c(...)
   # check if blanks within names
@@ -153,13 +153,13 @@ unflatten <- function(..., d) {
     names(x) <- rep(x_names, length.out = length(x))
   }
   # if user doesn't specify dimensionality, infer it from n unique names
-  if(missing(d)) {
-    d <- length(unique(names(x)))
+  if(missing(dim_length)) {
+    dim_length <- length(unique(names(x)))
   }
   # convert to n x n matrix
   #print(length(x))
-  if(length(x) != d*d) stop('Length of elements not equal to nrow * ncol of matrix')
-  mat <- matrix(x, nrow = d, ncol = d)
+  if(length(x) != dim_length*dim_length) stop('Length of elements not equal to nrow * ncol of matrix')
+  mat <- matrix(x, nrow = dim_length, ncol = dim_length)
   # make sure names of rows and columns identical
   rownames(mat) <- colnames(mat) <- unique(names(x))
   # transpose matrix 

### 2024-07-01 analysis/analysis.qmd
analysis ideas updated

@@
 ```
-
-- [ ] CA ToDo: Check the warning reported here
 
@@
 - [x] Issue 3: measure vs statistic?
-- [x] Issue 4: We need to classify the modelling techniques into fewer number of techniques (example given, but no principles defined)
-- [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)
+- [ ] Issue 4: We need to classify the modelling techniques into fewer number of techniques (example given, but no principles defined)
+  - Possible solution from "Dive into Deep Learning" by Zhang et al., 2024
+    1. Linear Neural Networks
+    2. Recurrent Neural Networks
+    3. Convolutional Neural Networks
+    4. Attention mechanisms (probably not applicable here, these are LMMs)
+
+- [x] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)
+
+```{r}
+#| echo: false
+#| eval: true
+library(stringr)
+metaMER_results$studyREF <- substr(metaMER_results$citekey,1,nchar(metaMER_results$citekey)-2)
+metaMER_results$studyREF <- str_replace_all(metaMER_results$studyREF,'([0-9]+)',' et al \\1')
+metaMER_results$studyREF <- str_to_sentence(metaMER_results$studyREF)
+```
 
@@
 
-#### Valence
+#### Valence: all models, datasets, features
 
@@
 # Temporary clarification of N
-tmp$stimulus_n[tmp$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "]<-1000
-tmp$stimulus_n[tmp$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "]<-2372
-tmp$stimulus_n[tmp$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "]<-40
+tmp$stimulus_n[tmp$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "] <- 1000
+tmp$stimulus_n[tmp$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372
+tmp$stimulus_n[tmp$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40
+tmp$stimulus_n[tmp$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 818
 tmp$stimulus_n <- as.numeric(tmp$stimulus_n)
@@
                  n = stimulus_n,
-                 studlab = citekey,
+                 studlab = studyREF,
                  data = tmp,
@@
 
+# Classify techniques according Hastie, Tibshirani, Friedman (2008)
+#
+# https://www.sas.upenn.edu/~fdiebold/NoHesitations/BookAdvanced.pdf
+#
+# 3. Linear Methods for Regression
+# 4. Linear Methods for Classification 
+# 5. Basis Expansions and Regularization
+# 6. Kernel Smoothing Methods
+# 7. Model Assessment and Selection
+# 8. Model Inference and Averaging 
+# 9. Additive Models, Trees, and Related Methods
+# 10. Boosting and Additive Trees
+# 11. Neural Networks
+# 12. Support Vector Machines and Flexible Discriminants
+# 15. Random Forests
+# 16. Ensemble Learning
+
 # divide models into random forests, SVM and MLR
-tmp$model_class_id <- 'MLR/PLS'
-tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression')]<-'RF'
-tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR')]<-'SVM'
-table(tmp$model_class_id)
+table(tmp$model_id)
+tmp$model_class_id <- 'Unclassified'
+tmp$model_class_id[str_detect(tmp$model_id,'lr|lm')] <- 'LR' # CAM?
+tmp$model_class_id[str_detect(tmp$model_id,'PLS|MLR|gaussian|gmm|GMM|mlr|PLSR|sparse|variational bayesian')]<-'MLR/PLS'
+tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression|forest|rfr')]<-'RF'
+tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR|svr')]<-'SVM'
+tmp$model_class_id[str_detect(tmp$model_id,'rnn')]<-'RNN'
+tmp$model_class_id[str_detect(tmp$model_id,'bee|backprop|knn|mars|rbf|smoreg')]<-'NN other'
+table(tmp$model_id,tmp$model_class_id)
+tmp$model_class_id<-factor(tmp$model_class_id)
+
 meta <- metagen(values, sqrt(values), # Fix the TE.se 
                 data = tmp, 
-                studlab = tmp$citekey, 
+                studlab = tmp$studyREF, 
                 comb.fixed = FALSE, 
@@
 ```
+
+## Take the max from each study
+
+Also max and min.
+
+Idea: visualise the distributions of the model successes within studies
+
+```{r}
+
+g <- ggplot(tmp,aes(y=values,fill=model_class_id))+
+  geom_histogram(show.legend = T)+
+  facet_wrap(.~studyREF)+
+  coord_flip()+
+  theme_bw()
+g
+
+# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
+# g<-ggplot(S,aes(y=maxvalue))+
+#   geom_histogram(bins = 14)+
+#   #facet_wrap(.~studyREF)+
+#   coord_flip()+
+#   theme_bw()
+# g
+
+```
+
+## Plot success across the years

### 2024-07-01 analysis/contents.R

@@ -1,3 +1,0 @@
-#### contents.R
-
-source('read_data.R')

### 2024-07-01 analysis/read_data.R

@@ -1,42 +1,0 @@
-# read_data.R
-
-#### Compile annotated studies ----------
-L <- list.files(path='../data/',pattern = ".R")
-
-df <- data.frame(nro=1:length(L))
-for (k in 1:length(L)) {
-  source(file.path('data/',L[k]))
-  df$study_id[k] <- study_id
-  df$emotion_type[k] <- emotion_type
-  df$emotion_list[k] <- list(emotion_list)
-  df$emotion_locus[k] <- emotion_locus
-  df$stimulus_type[k] <- stimulus_type
-  df$stimulus_duration[k] <- stimulus_duration
-  df$stimulus_N[k] <- stimulus_N
-  df$participant_N[k] <- participant_N
-  df$participant_expertise[k] <- participant_expertise
-  df$participant_origin[k] <- participant_origin
-  df$participant_sampling[k] <- participant_sampling
-  df$feature_list[k] <- list(feature_list)
-  df$feature_validation[k] <- feature_validation
-  df$feature_source[k] <- feature_source
-  df$model_type[k] <- list(model_type)
-  df$model_measure[k] <- model_measure
-  df$model_complexity_parameters[k] <- list(model_complexity_parameters)
-  df$model_rate_emotion_list[k] <- list(model_rate_emotion_list)
-  df$model_validation <- model_validation
-  df$meta_comments[k] <- meta_comments
-  df$meta_encoder[k] <- meta_encoder
-  df$meta_date[k] <- meta_date
-}
-
-# check validity of the data
-
-# numeric variables
-stopifnot(is.numeric(df$stimulus_duration))
-stopifnot(is.numeric(df$stimulus_N))
-stopifnot(is.numeric(df$participant_N))
-
-# specific variables
-stopifnot(df$emotion_type %in% c('dimensional','discrete','music-specific','other'))
-

### 2024-07-01 analysis/stripLFFromList.R

@@ -1,19 +1,0 @@
-stripLFFromList <- function(fn = NULL){
-  # T.E. 30/5/2024 for metaMER
-  fn_out <- stringr::str_replace(fn,'.bib','_strip.bib')
-  x <- readr::read_lines(fn)
-
-  # get the part we wish to modify, this will need to address multiple cases in the next version!
-  section_start <- which(stringr::str_detect(x,"list"))-1
-  section_end <- which(stringr::str_detect(x,"\\},"))  
-  section_end_index <- section_end > section_start
-  section_end<-section_end[section_end_index]
-  
-  # write back the file but with this section without separator
-  x2<-x[section_start:section_end]
-  readr::write_lines(x[1:(section_start-1)],file = fn_out)
-  readr::write_lines(x2,file = fn_out,sep = "",append = TRUE)
-  readr::write_lines("\n",file = fn_out,append = TRUE)
-  readr::write_lines(x[(section_end+1):length(x)],file = fn_out,append = TRUE)
- 
-}

### 2024-07-02 analysis/analysis.qmd
Edits of the preprocessing

@@
 
-## Sub-group analysis (based on model type)
+## Organise modelling techniques used
 
@@
 #
+# Replace with Cam's ## Linear Methods classes
 # 3. Linear Methods for Regression
@@
 # divide models into random forests, SVM and MLR
-table(tmp$model_id)
-tmp$model_class_id <- 'Unclassified'
-tmp$model_class_id[str_detect(tmp$model_id,'lr|lm')] <- 'LR' # CAM?
-tmp$model_class_id[str_detect(tmp$model_id,'PLS|MLR|gaussian|gmm|GMM|mlr|PLSR|sparse|variational bayesian')]<-'MLR/PLS'
-tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression|forest|rfr')]<-'RF'
-tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR|svr')]<-'SVM'
-tmp$model_class_id[str_detect(tmp$model_id,'rnn')]<-'RNN'
-tmp$model_class_id[str_detect(tmp$model_id,'bee|backprop|knn|mars|rbf|smoreg')]<-'NN other'
+metaMER_results$model_id <- tolower(metaMER_results$model_id)
+table(metaMER_results$model_id)
+length(table(metaMER_results$model_id))
+metaMER_results$model_class_id <- 'Unclassified'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Methods' # Class name from Elements of Stat.."
+#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Classification'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods' #
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|gmm|local|polynomial|polygonal')]<-'Kernel Smoothing'
+#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'adaboost|gradient')]<-'Boosting'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'nn|gru|lstm|ltsm|long short term memory|rprop|mcan')]<-'Neural Nets'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Flexible Discriminants'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient')]<-'Random Forests'
+#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf')]<-'Ensemble Learning'
+
+table(metaMER_results$model_class_id)
+round(table(metaMER_results$model_class_id)/nrow(metaMER_results),2)
+table(metaMER_results$model_id[metaMER_results$model_class_id=='Unclassified'],metaMER_results$model_class_id[metaMER_results$model_class_id=='Unclassified'])
+
+table(metaMER_results$model_class_id,metaMER_results$citekey)
+
+table(metaMER_results$model_class_id,metaMER_results$model_category)
+
+## simplify regression dimensions
+metaMER_results$dimension[str_detect(metaMER_results$dimension,'xxxx')]<-'arousal'
+
+table(metaMER_results$model_class_id,metaMER_results$dimension_category)
+table(metaMER_results$model_class_id,metaMER_results$dimension)
+
+View(metaMER_results)
+
+mcan
+
 table(tmp$model_id,tmp$model_class_id)

### 2024-07-02 R/parse-model-output.R

@@ -68,7 +68,10 @@ get_study_results <- function(study) {
   stimulus_n <- unique(as.character(study[,'stimulus_n']))
   feature_n <- unique(as.character(study[,'feature_n']))
   participant_n <- unique(as.character(study[,'participant_n']))
-  
+  model_category <- unique(as.character(study[,'model_category']))
+  feature_source <- unique(as.character(study[,'feature_source']))
+  feature_reduction_method <- unique(as.character(study[,'feature_reduction_method']))
+
   #print(citekey)
   #print(as.character(study[,'model_rate_emotion_values']))
   results <- parse_model_output(as.character(
@@ -78,9 +81,12 @@ get_study_results <- function(study) {
   return(
     dplyr::tibble(
       citekey,
+      model_category,
       stimulus_n,
       feature_n,
       participant_n,
+      feature_source,
+      feature_reduction_method,
       results)
     )
 }

### 2024-07-02 R/format-study-results.R
update parse-model-output

@@ -91,7 +91,7 @@ fill_missing_names <- function(...) {
       ) 
       return(do.call(rbind, input))
     } else {
-    message('Mismatch in input lengths.')
+    warning('Mismatch in input lengths.')
     invisible(0)
   }
 }

### 2024-07-02 R/parse-model-output.R

@@ -78,17 +78,19 @@ get_study_results <- function(study) {
     study[,'model_rate_emotion_values'])
     )
   
-  return(
-    dplyr::tibble(
+  
+    clean_df <- dplyr::tibble(
       citekey,
-      model_category,
+      model_categoey = trimws(model_category, which = 'both'), 
       stimulus_n,
       feature_n,
       participant_n,
       feature_source,
       feature_reduction_method,
-      results)
-    )
+      results) 
+    
+    
+    return(clean_df)
 }
 
 

### 2024-07-02 analysis/analysis.qmd
divided analysis into preprocessing and analysis

--- 2024-06-25 analysis/analysis.qmd
@@
 
-This assumes that the data has been parsed from the BibTeX files into table and exported as CSV file.
-
-## Read annotated data
-
-- Update 2024-06-19
-- [ ] CA TODO later (if at all): find better way to read in functions
-
-```{r}
-require(here)
-source(here::here('R/build-df.R'))
-source(here::here('R/format-study-results.R'))
-source(here::here('R/parse-model-output.R'))
-```
-
-- [ ] CA ToDo: Check the warning reported here
-
-```{r}
-# get metaMER df:
-meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))
-
-# get included studies
-included_studies <- meta_df[which(
-  !stringr::str_detect(meta_df$final_notes, '!EXCL!')),] |> 
-  dplyr::tibble()
-
-```
-### Recoded
-
-```{r}
-# get studies re-coded (currently identifiable by presence of bind_field.)
-recoded_studies <- included_studies[which(stringr::str_detect(
-  included_studies$model_rate_emotion_values,
-                                     'bind_field')),]
-
-```
-
-Maybe limit the verbosity of `get_study_results` below
-
-```{r}
-metaMER_results <-
-do.call(
-  rbind,
-    lapply(1:nrow(recoded_studies),
-       function(x) get_study_results(recoded_studies[x,])
-       )
-)
-
-# add unique identifiers
-
-unique_id <- apply(metaMER_results[,c('citekey',
-                        'library_id',
-                         'model_id',
-                         'feature_id',
-                         'data_id',
-                         'experiment_id')],
-                      1, 
-                      paste0, 
-                      collapse = '-'
-) 
-metaMER_results$unique_id <- stringr::str_remove_all(unique_id, 
-                                                     ' ')
-
-metaMER_results <- metaMER_results |> dplyr::select(unique_id, 
-                                 dplyr::everything())
-
-metaMER_results |> dplyr::tibble()
-
-```
-
-## Summarise annotated data
-
-```{r}
-#| eval: true
-#| output: asis
-
-print(knitr::kable(table(metaMER_results$citekey,metaMER_results$dimension)))
-print(knitr::kable(table(metaMER_results$citekey,metaMER_results$model_id)))
-print(knitr::kable(table(metaMER_results$citekey,metaMER_results$feature_id)))
-print(knitr::kable(table(metaMER_results$citekey,metaMER_results$data_id)))
-
-```
-
-## Analysis notes
-
-- [x] Issue 1: We need unique identifiers for each input component (combine: `study` + `model` + `feature` + `data` + `experiment` that would have be unique id)
-- [x] Issue 2: We `stimulus_N`
-- [x] Issue 3: measure vs statistic?
-- [x] Issue 4: We need to classify the modelling techniques into fewer number of techniques (example given, but no principles defined)
-- [ ] Issue 5: We could polish citekey into ref (xu2021us to Xu 2021 et al., ) for nicer plotting output (can be done with `str_replace`)
-
-- [ ] If the _number of stimuli_ varies, divide either to separate experiments or use the largest value (see below for ad-hoc solution).
+This assumes that the data has been parsed (`parse-model-output.R`, `format-study-results.R`) and preprocessed (`processing.qmd`).
 
@@
 
-## Sub-group analysis (based on model type)
-
-```{r}
-#| eval: true
-
-# divide models into random forests, SVM and MLR
-tmp$model_class_id <- 'MLR/PLS'
-tmp$model_class_id[str_detect(tmp$model_id,'RFR|extremely randomized tree regression')]<-'RF'
-tmp$model_class_id[str_detect(tmp$model_id,'svm|SVR')]<-'SVM'
-table(tmp$model_class_id)
-meta <- metagen(values, sqrt(values), # Fix the TE.se 
-                data = tmp, 
-                studlab = tmp$citekey, 
-                comb.fixed = FALSE, 
-                method.tau = "PM")
-
-subgroup.analysis.mixed.effects(x = meta, 
-                                subgroups = tmp$model_class_id)
-```
-
 ## Visualise
@@
 ```
+
+## Take the max from each study
+
+- Also think of max, median/mean and min?
+
+- Idea: visualise the distributions of the model successes within studies
+
+```{r}
+g1 <- ggplot(tmp,aes(y=values,fill=model_class_id))+
+  geom_histogram(show.legend = T)+
+  facet_wrap(.~studyREF)+
+  coord_flip()+
+  theme_bw()
+g1
+
+# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
+# g<-ggplot(S,aes(y=maxvalue))+
+#   geom_histogram(bins = 14)+
+#   #facet_wrap(.~studyREF)+
+#   coord_flip()+
+#   theme_bw()
+# g
+```
+
+## Plot success across the years
+
+```{r}
+#| eval: false
+g2 <- ggplot(tmp,aes(y=values,fill=model_class_id))+
+  geom_histogram(show.legend = T)+
+  facet_wrap(.~studyREF)+
+  coord_flip()+
+  theme_bw()
+g2
+```

### 2024-07-02 analysis/preprocessing.qmd
divided analysis into preprocessing and analysis

# Preprocessing

This assumes that the data has been parsed from the BibTeX files into table and exported as CSV file.

## Read annotated data

```{r}
#| warning: false
require(here)
source(here::here('R/build-df.R'))
source(here::here('R/format-study-results.R'))
source(here::here('R/parse-model-output.R'))
```

```{r}
#| warning: false
# get metaMER df:
meta_df <- get_metaMER_df(path_2_studies = here::here('studies'))

# get included studies
included_studies <- meta_df[which(
  !stringr::str_detect(meta_df$final_notes, '!EXCL!')),] |> 
  dplyr::tibble()

```

### Recoded

```{r}
#| warning: false
# get studies re-coded (currently identifiable by presence of bind_field.)
recoded_studies <- included_studies[which(stringr::str_detect(
  included_studies$model_rate_emotion_values,
                                     'bind_field')),]

```

### Add unique identifiers

```{r}
#| warning: false

metaMER_results <-
do.call(
  rbind,
    lapply(1:nrow(recoded_studies),
       function(x) get_study_results(recoded_studies[x,])
       )
)

# add unique identifiers

unique_id <- apply(metaMER_results[,c('citekey',
                        'library_id',
                         'model_id',
                         'feature_id',
                         'data_id',
                         'experiment_id')],
                      1, 
                      paste0, 
                      collapse = '-'
) 
metaMER_results$unique_id <- stringr::str_remove_all(unique_id, 
                                                     ' ')

metaMER_results <- metaMER_results |> dplyr::select(unique_id, 
                                 dplyr::everything())

metaMER_results |> dplyr::tibble()

```

### Summarise annotated data (optional)

```{r}
#| eval: false
#| output: asis

print(knitr::kable(table(metaMER_results$citekey,metaMER_results$dimension)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$model_id)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$feature_id)))
print(knitr::kable(table(metaMER_results$citekey,metaMER_results$data_id)))

```

### Add human readable author+date field

```{r}
#| echo: false
#| eval: true
library(stringr)
metaMER_results$studyREF <- substr(metaMER_results$citekey,1,nchar(metaMER_results$citekey)-2)
metaMER_results$studyREF <- str_replace_all(metaMER_results$studyREF,'([0-9]+)',' et al \\1')
metaMER_results$studyREF <- str_to_sentence(metaMER_results$studyREF)
```

### Classify modelling techniques used

```{r}
#| eval: true
# Classify techniques according Hastie, Tibshirani, Friedman (2008)
# https://www.sas.upenn.edu/~fdiebold/NoHesitations/BookAdvanced.pdf
#
metaMER_results$model_id <- tolower(metaMER_results$model_id)
metaMER_results$model_class_id <- 'Unclassified'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Methods' # Class name from Elements of Stat.."
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Classification'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods' #
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|gmm|local|polynomial|polygonal')]<-'Kernel Smoothing'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'adaboost|gradient')]<-'Boosting'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'nn|gru|lstm|ltsm|long short term memory|rprop|mcan')]<-'Neural Nets'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Flexible Discriminants'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient')]<-'Random Forests'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf')]<-'Ensemble Learning'

```

## Summarise

```{r}
#| eval: true
#| output: asis
print(knitr::kable(table(metaMER_results$model_class_id)))
print(knitr::kable(table(metaMER_results$model_class_id,metaMER_results$model_category)))

print(paste("We have", nrow(metaMER_results), "observations"))

print(paste("We have", length(unique(metaMER_results$citekey)), "studies"))

print(paste("Where", length(unique(metaMER_results$citekey[metaMER_results$model_category=='regression'])), "are regression studies"))

print(paste("Where", length(unique(metaMER_results$citekey[metaMER_results$model_category=='classification'])), "are classification studies"))

```

### 2024-07-08 analysis/preprocessing.qmd
separate process and analysis

@@
 #
+library(stringr)
 metaMER_results$model_id <- tolower(metaMER_results$model_id)
@@
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Classification'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods' #
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|gmm|local|polynomial|polygonal')]<-'Kernel Smoothing'
+#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods' #
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|gmm|local|polynomial|polygonal|knn|mars|gam')]<-'Kernel Smoothing, Additive and KNN'
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'adaboost|gradient')]<-'Boosting'
@@
 metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Flexible Discriminants'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
+#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
 metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient')]<-'Random Forests'
@@
 print(paste("Where", length(unique(metaMER_results$citekey[metaMER_results$model_category=='classification'])), "are classification studies"))
+# note that we have some classification studies that also do regression and vice versa?
 
 ```
+
+### Pull data to analyse regression studies
+
+```{r}
+R_studies <- dplyr::filter(metaMER_results,model_category=='regression' & str_detect(measure,'r|cc|r2|R2')) #  
+dim(R_studies)
+
+# eliminate measures that we don't need now
+R_studies <- dplyr::filter(R_studies,!str_detect(statistic,'r2-95l|r2-95u|pvalue|upper|lower|sd|null|rmse'))
+R_studies <- dplyr::filter(R_studies,!str_detect(measure,'nFeatures|rmse|jensen shannon divergence|accuracy|ccc|vector distance'))
+
+table(R_studies$measure)
+
+table(R_studies$measure, R_studies$statistic)
+
+dim(R_studies)
+R_studies$values[R_studies$measure=='R2']<-sqrt(R_studies$values[R_studies$measure=='R2']) # recode R2 into r
+R_studies$values[R_studies$measure=='r2']<-sqrt(R_studies$values[R_studies$measure=='r2']) # recode R2 into r
+
+```
+
+### Diagnostics
+
+```{r}
+library(ggplot2)
+
+g1<-ggplot(R_studies,aes(x=values,fill=citekey))+
+             geom_histogram()+
+  facet_wrap(.~model_class_id)+
+           theme_bw()+
+scale_x_continuous(breaks = seq(0,1,by=.1))
+           g1
+```

### 2024-07-08 R/parse-model-output.R

@@ -81,7 +81,7 @@ get_study_results <- function(study) {
   
     clean_df <- dplyr::tibble(
       citekey,
-      model_categoey = trimws(model_category, which = 'both'), 
+      model_category = trimws(model_category, which = 'both'), 
       stimulus_n,
       feature_n,
       participant_n,

### 2024-07-08 studies/extraction_details.qmd
update extraction details

@@
 Report as *R* named arrays, including summary statistics in variables.
-When reporting results of multiple models, concatenate multiple entries with `mrbind`.
+When reporting results of multiple models, concatenate multiple entries with `bind_field`.
 When reporting results for different toolboxes or feature subsets, assign each to a new BiBTeX field with relevant identifier following final underscore.
@@
 
-Confusion matrices can be encoded similarly through a function that assigns relevant meta-parameters to the `model_parameters` attribute of the output matrix.
-The row names are then replaced with the column names for clearer output.
-This assumes row names and column names of the confusion matrix are listed in the same order.
+Confusion matrices can be encoded using the `unflatten` function, which assigns relevant meta-parameters to the `model_parameters` attribute of the output matrix.
+The function automatically builds a $n$ by $n$ matrix and takes individual values as arguments.
+Values can be specified for the first row, and are recycled in subsequent rows.
 
 ```
-confusion_matrix(
-library.model.features.data.experiment =  c(class_1 = 0, class_2 = 0, ..., class_n = 0),
-class_2 = c(0, 0, ..., 0),
-...
+unflatten(A = .5, B = .2, C = .3,
+          .3, .5, .2,
+          .1, .1, .8)
+```
+Summary parameters can be extracted from the resulting matrix by calling the `summarize_matrix` function.
+This function calls on `caret` to extract several summary statistics at once.
+Including `bind_field` in the call ensures consistent nomenclature with other study encodings.
+```
+bind_field(
+  'library.model.features.data.exp' = summarize_matrix(
+    unflatten(Q1=185.85,Q2=14.4,Q3=8.6,Q4=18.15,
+              23.95,190.55,7,3.5,
+              14.2,8.4,157.25,45.15,
+              24.35,1.65,45.85,153.15)
+  )
+)
+```
+Multiple matrices in a study can be summarized by putting them in a list and using the `lapply` function to extract relevant statistics:
+
+```
+bind_field(
+  lapply(
+    list(
+      'library.model.features.data.exp1' = unflatten(
+        Angry=.984,Happy=.007,Relax=.007,Sad=0,
+        0,.987,0,.007,
+        .008,.007,.987,0,
+        .008,0,.007,.993
+        ),
+      'library.model.features.data.exp2' = unflatten(
+        Angry=.976,Happy=.013,Relax=.014,Sad=0,
+        .008,.967,0,.02,
+        .008,.013,.98,.007,
+        .008,.007,.007,.974
+       )
+      ),
+    summarize_matrix
+  )
 )

### 2024-07-10 analysis/analysis.qmd
Regression update

@@
 
-### Regression studies
+## Regression studies
 
-#### Valence: all models, datasets, features
+### Valence: Best model
 
@@
 
+R_studies <- read.csv("R_studies.csv")
+R_summary <- read.csv("R_summary.csv")
+
 # select regression studies with r2
-tmp <- dplyr::filter(metaMER_results,dimension=="valence" & measure=="r2")
-
-# Temporary clarification of N
-tmp$stimulus_n[tmp$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "] <- 1000
-tmp$stimulus_n[tmp$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372
-tmp$stimulus_n[tmp$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40
-tmp$stimulus_n[tmp$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 818
-tmp$stimulus_n <- as.numeric(tmp$stimulus_n)
-
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp <- dplyr::filter(R_studies,dimension=="valence")
+tmp<-drop_na(tmp)
 #sqrt(tmp$values) # convert from R^2 to r
@@
 
-m.cor <- metacor(cor = sqrt(values), 
+m.cor <- metacor(cor = values, 
+                 n = stimulus_n,
+                 studlab = unique_id,
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+
+print(m.cor)
+```
+
+#### Visualise (forest and funnel plots)
+
+```{r}
+forest(m.cor,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "g", "SE"),studlab = citekey)
+plot(eggers.test(m.cor))
+```
+
+#### Explore qualities (in progress)
+
+```{r}
+O <- find.outliers(m.cor)
+# 6 datasets identified as outliers, without them the r drops to 0.5781
+infan <- InfluenceAnalysis(m.cor)
+print(eggers.test(m.cor))
+
+```
+#### Re-run the analysis without the outliers
+
+```{r}
+outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")
+
+tmp2<-tmp[!tmp$unique_id %in% outliers,]
+m.cor <- metacor(cor = values, 
+                 n = stimulus_n,
+                 studlab = unique_id, # unique_id
+                 data = tmp2,
+                 fixed = FALSE,
+                 random = TRUE,
+                 sm = "ZCOR",
+                 prediction = TRUE,
+                 backtransf = TRUE,
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+
+print(m.cor)
+
+fp <- funnel(m.cor, common = TRUE,studlab=FALSE)
+
+```
+
+#### Custom funnel plot
+
+To show the quality differences between core and eliminated studies (in progress).
+
+```{r}
+tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE)
+estimate = m.cor$TE.common
+se = m.cor$seTE.common
+se.seq=seq(0, max(m.cor$cor), 0.001)
+ll95 = estimate-(1.96*se.seq)
+ul95 = estimate+(1.96*se.seq)
+ll99 = estimate-(3.29*se.seq)
+ul99 = estimate+(3.29*se.seq)
+meanll95 = estimate-(1.96*se)
+meanul95 = estimate+(1.96*se)
+dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
+
+fp = ggplot(aes(x = SE, y = Zr), data = tmpdata) +
+  geom_point(shape = 1) +
+  xlab('Standard Error') + ylab('Zr')+
+  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
+  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
+   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
+  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
+#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
+#at the top of the figure once we swap the x- and y-axes...
+  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
+#Specify the range and interval for the tick-marks of the y-axis (Zr);
+#Choose values that work for you based on your data
+  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
+#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
+#And now we flip the axes so that SE is on y- and Zr is on x-
+  coord_flip()+
+#Finally, apply my APA-format theme (see code at end of post).
+#You could, alternatively, specify theme_bw() instead.
+  theme_bw()
+
+```
+
+#### Subgroup analysis according to techniques
+
+```{r}
+m.cor_subgroups <- update(m.cor, 
+       subgroup = model_class_id, 
+       tau.common = FALSE,
+       prediction = TRUE)
+
+print(m.cor_subgroups)
+#forest(m.cor_subgroups,subgroup=TRUE)
+```
+
+- Idea: visualise the distributions of the model successes within studies (done in preprocessing)
+
+### Arousal: Best model
+
+```{r}
+#| warning: false
+#| eval: true
+
+# select regression studies with r2
+tmp <- dplyr::filter(R_summary,dimension=="arousal")
+m.cor <- metacor(cor = valuesMedian, 
                  n = stimulus_n,
@@
                  method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: All")
+                 title = "MER: Regression: Arousal: Summary")
 
@@
 
-## Explore qualities
+#### Visualise (forest and funnel plots)
 
 ```{r}
-meta <- metagen(values, sqrt(values), 
+forest(m.cor,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "g", "SE"))
+plot(eggers.test(m.cor))
+```
+
+#### Explore qualities (in progress)
+
+```{r}
+#| eval: false
+meta <- metagen(valuesMax, sqrt(valuesMax), 
                 data = tmp, 
@@
 
-## Visualise
+#### Subgroup analysis according to techniques
 
 ```{r}
-plot(m.cor)
-plot(eggers.test(meta))
+update(m.cor, 
+       subgroup = model_class_id, 
+       tau.common = FALSE)
+m.cor_subgroups <- update(m.cor, 
+       subgroup = model_class_id, 
+       tau.common = FALSE)
 
+forest(m.cor_subgroups,subgroup=TRUE)
 ```
 
-## Take the max from each study
-
-- Also think of max, median/mean and min?
-
-- Idea: visualise the distributions of the model successes within studies
+- Idea: visualise the distributions of the model successes within studies (done in preprocessing)
 
 ```{r}
-g1 <- ggplot(tmp,aes(y=values,fill=model_class_id))+
+#| eval: false
+g1 <- ggplot(tmp,aes(y=valuesMax,fill=model_class_id))+
    geom_histogram(show.legend = T)+
@@
 ```
-
-## Plot success across the years
-
-```{r}
-#| eval: false
-g2 <- ggplot(tmp,aes(y=values,fill=model_class_id))+
-  geom_histogram(show.legend = T)+
-  facet_wrap(.~studyREF)+
-  coord_flip()+
-  theme_bw()
-g2
-```

### 2024-07-10 analysis/preprocessing.qmd
Regression update

@@
 ```
+### Homogenise the outcome variable names to valence and arousal
+
+```{r}
+R_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal'
+R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
+R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av')) # relates to distances, can be omitted
+
+table(R_studies$dimension)
+
+table(R_studies$stimulus_n)
+
+# Deal with four studies involving multiple datasets: 
+R_studies$stimulus_n[R_studies$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "] <- 938 #resolved from the paper
+R_studies$stimulus_n[R_studies$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372 # resolved
+R_studies$stimulus_n[R_studies$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40 # decided to take this from validation
+# REDO with a clearer function
+eliminate <- str_detect(R_studies$unique_id,"hu2017cr") & !str_detect(R_studies$unique_id,"all")
+R_studies <- R_studies[!eliminate,]
+R_studies$stimulus_n[R_studies$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 60+818+1608 #
+R_studies$stimulus_n <- as.numeric(R_studies$stimulus_n)
+
+```
 
@@
 
-g1<-ggplot(R_studies,aes(x=values,fill=citekey))+
+g1<-ggplot(R_studies,aes(x=values,fill=citekey,color=dimension))+
   geom_histogram()+
   facet_wrap(.~model_class_id)+
-           theme_bw()+
+  scale_color_manual(values = c('black','white'))+
+  theme_dark()+
   scale_x_continuous(breaks = seq(0,1,by=.1))
+
 g1
 ```
+
+### Select a summary measure for valence and arousal separately
+
+```{r}
+library(tidyverse)
+R_studies$citekey <- factor(R_studies$citekey)
+R_studies$dimension <- factor(R_studies$dimension)
+
+R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=T),valuesMedian=median(values,na.rm=T),valuesMax=max(values,na.rm=T),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id))
+
+```
+
+### Visualise Summary on two dimensions
+
+Add variation from within the studies (alternative models)
+
+```{r}
+R_summary_split <- pivot_wider(R_summary,id_cols = citekey, names_from = c(dimension), values_from = valuesMax)
+
+g2 <- ggplot(R_summary_split,aes(x=valence,y=arousal,label=citekey))+
+  geom_label()+
+  theme_bw()+
+  scale_x_continuous(breaks = seq(0,1,by=.1))+
+  scale_y_continuous(breaks = seq(0,1,by=.1))
+
+g2
+
+## could be more informative when done with the full data
+R_studies$citekey<-factor(R_studies$citekey)
+R_studies$dimension<-factor(R_studies$dimension)
+
+R_studies_split <- pivot_wider(R_studies,id_cols = c(unique_id,citekey,model_class_id), names_from = c(dimension), values_from = c(values),values_fn = mean)
+R_studies_split<-drop_na(R_studies_split)
+
+library(ggrepel)
+
+g3 <- ggplot(R_studies_split,aes(x=valence,y=arousal,label=citekey,color=model_class_id,fill=model_class_id))+
+  geom_point(size=4)+
+  geom_label_repel(size=3, max.overlaps=50,show.legend = T,color='white')+
+  scale_x_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
+  scale_y_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
+  theme_bw()
+g3
+
+```
+
+### Plot success across the years
+
+```{r}
+#| eval: true
+# Add year!
+R_studies$year <- as.numeric(str_match(R_studies$citekey,'[0-9]+'))
+
+g3 <- ggplot(R_studies,aes(x=year,y=values,colour=model_class_id))+
+  geom_point(show.legend = T)+
+  facet_wrap(.~dimension)+
+  theme_bw()
+g3
+```
+### Simple model complexity metric
+
+Ratio of obs./features or just a classification based on feature n (quintiles).
+
+```{r}
+R_studies$feature_n==" 15; 23 in table, but 15 reported "
+
+R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved from the paper
+
+R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved
+R_studies$feature_n[R_studies$feature_n==" before_selection = 45, after_selection = 6  "] <- 45 #resolved
+R_studies$feature_n[R_studies$feature_n==" model 1: 52, model 2 = 68, model 3 = 260, model 4 = 388 "] <- 388 #resolved
+R_studies$feature_n[R_studies$feature_n==" variable, 557 before feature selection "] <- 557 #resolved
+
+R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 50 #resolved
+#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
+#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
+
+R_studies$feature_n<-as.numeric(R_studies$feature_n)
+
+print(quantile(R_studies$feature_n,c(0.333,0.666),na.rm = T))
+#quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)
+
+# Assign
+R_studies$feature_n_complexity <- cut(R_studies$feature_n,
+                                      breaks = c(0,
+                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
+                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
+                                                 1000),
+                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
+table(R_studies$feature_n_complexity)
+```
+
+### Explore feature_n_complexity and model success
+
+Needs to be done from the unsummarised data (`R_studies`).
+
+```{r}
+tmp <- drop_na(R_studies)
+library(ggdist)
+
+tmp$dimension<-str_to_title(tmp$dimension)
+tmp$model_class_id<-factor(tmp$model_class_id,
+                           levels = c("Neural Nets","Flexible Discriminants", "Kernel Smoothing, Additive and KNN", "Random Forests","Linear Methods"),
+                           labels = c("Neural\nNets","Flexible\nDiscriminants", "KS\n & KNN", "Random\nForests", "Linear\nMethods"))
+
+g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey))+
+  stat_halfeye(aes(fill=citekey),point_interval="mean_qi", trim=FALSE, expand=FALSE, show.legend = FALSE,adjust = 1.25, density="bounded", point_size=3,scale = 1,alpha=0.5) + 
+  geom_point(alpha=0.5,show.legend = F,position = position_jitter(width = .3))+
+  #geom_label_repel(size=2,max.overlaps = 50)+
+  facet_wrap(dimension~feature_n_complexity)+
+  ylab("Correlation Coefficient")+
+  xlab("Model Technique")+
+#  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
+  geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
+             stat = "summary", fun = mean,show.legend = F)+
+  theme_bw()
+g
+#ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
+```
+
+## Export as csv
+
+```{r}
+write.csv(x = R_studies,file = 'R_studies.csv')
+write.csv(x = R_summary,file = 'R_summary.csv')
+```

### 2024-07-10 manuscript/manuscript.qmd
Regression update

@@
 
+- Report all models or the best model?
+
 Out of XX studies reporting this task, the majority (xx%) ...
 
-| Concept | N    | Md $R^2$|
-|:--------|:-----|:--------|
-| Valence | ??   | ??      |
-| Arousal | ??   | ??      |
+This is for diagnostic purposes
+
+| Concept     | N,obs     | $r$ 95%-CI              | $t$ | $p$  |$\tau^2$|$I^2$|
+|:------------|:----------|:--------|:--------------|:----|:-----|:-----|:------|
+| Valence All | 49,42648  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
+| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1% [0.0%; 58.2%]|
+| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
+| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
+| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% |
+| N Features  |           |                         |     |      |      |       |
+| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+| Techniques  |           |                         |     |      |      |       |
+|   KS        | 1          | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+
+| Arousal | 14,9035  | 0.8139 [0.7147; 0.8810] |10.17|.0001 | 0.165| 97.3% |
+|   KS    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   LM    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   FD    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   NN    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   RF    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
 
 TABLE: xxxx
+
+model complexity issue
+
+https://ishanjainoffical.medium.com/model-complexity-explained-intuitively-e179e38866b6
+
+https://www.sciencedirect.com/science/article/pii/S0925231220317525
+
+bake in number of features, + N + success
+AIC =
 

### 2024-07-11 analysis/preprocessing.qmd
minor updates morning

@@
 
-## Summarise
+## Summarise all
 
@@
 
-### Pull data to analyse regression studies
+## Pull data to analyse regression studies
 
@@
 
-## Export as csv
+### Create descriptive table for the manuscript
+
+```{r}
+TR <- NULL
+TR$study_n <- length(unique(R_studies$citekey))
+TR$model_n <- nrow(R_studies)
+t<-table(R_studies$model_class_id)
+t2 <- paste0(names(t),': ', as.numeric(t))
+TR$model_types_n <- str_c(t2,collapse = "\n")
+TR$feature_Desc <- paste0('Min=',min(R_studies$feature_n,na.rm = TRUE),', Md=',median(R_studies$feature_n,na.rm = TRUE),', Max=', max(R_studies$feature_n,na.rm = TRUE))
+TR$stimulus_Desc <- paste0('Min=',min(R_studies$stimulus_n,na.rm = TRUE),', Md=',median(R_studies$stimulus_n,na.rm = TRUE),', Max=', max(R_studies$stimulus_n,na.rm = TRUE))
+print(TR)
+
+```
+
+### Export as csv
 
@@
 ```
+
+## Pull data to analyse classification studies
+
+```{r}
+C_studies <- dplyr::filter(metaMER_results,model_category=='classification' & str_detect(measure,'accuracy|r2|mcc')) #  
+dim(C_studies)
+
+# eliminate measures that we don't need now
+C_studies <- dplyr::filter(C_studies,values>0)
+C_studies$statistic[is.na(C_studies$statistic)]<-'Not defined'
+C_studies <- dplyr::filter(C_studies,!str_detect(statistic,'pvalue|upper|lower'))
+C_studies <- dplyr::filter(C_studies,str_detect(measure,'accuracy|mcc|r2'))
+dim(C_studies)
+
+table(C_studies$measure,C_studies$statistic)
+
+dim(C_studies)
+# Conversion into mcc (==r), do we need
+
+```
+### Homogenise the outcome variable names to valence and arousal
+
+```{r}
+#C_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal'
+#R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
+#R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av')) # relates to distances, can be omitted
+
+table(C_studies$stimulus_n)
+
+# Deal with four studies involving multiple datasets: 
+C_studies$stimulus_n[C_studies$stimulus_n==" 429; 350 popular songs + 79 songs from the Beatles (Mirex 2009 collection)  "] <- 429 # resolved from the paper
+C_studies$stimulus_n[C_studies$stimulus_n==" 5192; 12 per user in user validation (not included here due to little information),   AcousticBrainz validation: 60000  "] <- 5192 # resolved
+C_studies$stimulus_n[C_studies$stimulus_n==" ISMIR2012: 2886, NJU_V1: 777, Hindi: 1037  "] <- 2886+777+1037 # decided to take this from validation
+C_studies<-C_studies[!str_detect(C_studies$stimulus_n,'not specified'),]
+C_studies<-C_studies[!str_detect(C_studies$stimulus_n,'Specified elsewhere'),]
+C_studies$stimulus_n <- as.numeric(C_studies$stimulus_n)
+
+```
+
+### Diagnostics
+
+```{r}
+library(ggplot2)
+
+g1<-ggplot(R_studies,aes(x=values,fill=citekey,color=dimension))+
+  geom_histogram()+
+  facet_wrap(.~model_class_id)+
+  scale_color_manual(values = c('black','white'))+
+  theme_dark()+
+  scale_x_continuous(breaks = seq(0,1,by=.1))
+
+g1
+```
+
+### Select a summary measure for valence and arousal separately
+
+```{r}
+library(tidyverse)
+R_studies$citekey <- factor(R_studies$citekey)
+R_studies$dimension <- factor(R_studies$dimension)
+
+R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=T),valuesMedian=median(values,na.rm=T),valuesMax=max(values,na.rm=T),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id))
+
+```
+
+### Visualise Summary on two dimensions
+
+Add variation from within the studies (alternative models)
+
+```{r}
+R_summary_split <- pivot_wider(R_summary,id_cols = citekey, names_from = c(dimension), values_from = valuesMax)
+
+g2 <- ggplot(R_summary_split,aes(x=valence,y=arousal,label=citekey))+
+  geom_label()+
+  theme_bw()+
+  scale_x_continuous(breaks = seq(0,1,by=.1))+
+  scale_y_continuous(breaks = seq(0,1,by=.1))
+
+g2
+
+## could be more informative when done with the full data
+R_studies$citekey<-factor(R_studies$citekey)
+R_studies$dimension<-factor(R_studies$dimension)
+
+R_studies_split <- pivot_wider(R_studies,id_cols = c(unique_id,citekey,model_class_id), names_from = c(dimension), values_from = c(values),values_fn = mean)
+R_studies_split<-drop_na(R_studies_split)
+
+library(ggrepel)
+
+g3 <- ggplot(R_studies_split,aes(x=valence,y=arousal,label=citekey,color=model_class_id,fill=model_class_id))+
+  geom_point(size=4)+
+  geom_label_repel(size=3, max.overlaps=50,show.legend = T,color='white')+
+  scale_x_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
+  scale_y_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
+  theme_bw()
+g3
+
+```
+
+### Plot success across the years
+
+```{r}
+#| eval: true
+# Add year!
+R_studies$year <- as.numeric(str_match(R_studies$citekey,'[0-9]+'))
+
+g3 <- ggplot(R_studies,aes(x=year,y=values,colour=model_class_id))+
+  geom_point(show.legend = T)+
+  facet_wrap(.~dimension)+
+  theme_bw()
+g3
+```
+### Simple model complexity metric
+
+Ratio of obs./features or just a classification based on feature n (quintiles).
+
+```{r}
+R_studies$feature_n==" 15; 23 in table, but 15 reported "
+
+R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved from the paper
+
+R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved
+R_studies$feature_n[R_studies$feature_n==" before_selection = 45, after_selection = 6  "] <- 45 #resolved
+R_studies$feature_n[R_studies$feature_n==" model 1: 52, model 2 = 68, model 3 = 260, model 4 = 388 "] <- 388 #resolved
+R_studies$feature_n[R_studies$feature_n==" variable, 557 before feature selection "] <- 557 #resolved
+
+R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 50 #resolved
+#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
+#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
+
+R_studies$feature_n<-as.numeric(R_studies$feature_n)
+
+print(quantile(R_studies$feature_n,c(0.333,0.666),na.rm = T))
+#quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)
+
+# Assign
+R_studies$feature_n_complexity <- cut(R_studies$feature_n,
+                                      breaks = c(0,
+                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
+                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
+                                                 1000),
+                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
+table(R_studies$feature_n_complexity)
+```
+
+### Explore feature_n_complexity and model success
+
+Needs to be done from the unsummarised data (`R_studies`).
+
+```{r}
+tmp <- drop_na(R_studies)
+library(ggdist)
+
+tmp$dimension<-str_to_title(tmp$dimension)
+tmp$model_class_id<-factor(tmp$model_class_id,
+                           levels = c("Neural Nets","Flexible Discriminants", "Kernel Smoothing, Additive and KNN", "Random Forests","Linear Methods"),
+                           labels = c("Neural\nNets","Flexible\nDiscriminants", "KS\n & KNN", "Random\nForests", "Linear\nMethods"))
+
+g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey))+
+  stat_halfeye(aes(fill=citekey),point_interval="mean_qi", trim=FALSE, expand=FALSE, show.legend = FALSE,adjust = 1.25, density="bounded", point_size=3,scale = 1,alpha=0.5) + 
+  geom_point(alpha=0.5,show.legend = F,position = position_jitter(width = .3))+
+  #geom_label_repel(size=2,max.overlaps = 50)+
+  facet_wrap(dimension~feature_n_complexity)+
+  ylab("Correlation Coefficient")+
+  xlab("Model Technique")+
+#  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
+  geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
+             stat = "summary", fun = mean,show.legend = F)+
+  theme_bw()
+g
+#ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
+```
+
+### Create descriptive table for the manuscript
+
+```{r}
+TR <- NULL
+TR$study_n <- length(unique(R_studies$citekey))
+TR$model_n <- nrow(R_studies)
+t<-table(R_studies$model_class_id)
+t2 <- paste0(names(t),': ', as.numeric(t))
+TR$model_types_n <- str_c(t2,collapse = "\n")
+TR$feature_Desc <- paste0('Min=',min(R_studies$feature_n,na.rm = TRUE),', Md=',median(R_studies$feature_n,na.rm = TRUE),', Max=', max(R_studies$feature_n,na.rm = TRUE))
+TR$stimulus_Desc <- paste0('Min=',min(R_studies$stimulus_n,na.rm = TRUE),', Md=',median(R_studies$stimulus_n,na.rm = TRUE),', Max=', max(R_studies$stimulus_n,na.rm = TRUE))
+print(TR)
+
+```
+
+### Export as csv
+
+```{r}
+write.csv(x = R_studies,file = 'R_studies.csv')
+write.csv(x = R_summary,file = 'R_summary.csv')
+```

### 2024-07-11 manuscript/manuscript.qmd
minor updates morning

--- 2024-06-18 manuscript/manuscript.qmd
@@
 - Great advances in music information retrieval have been made in recent years.
+The available features, modelling techniques and datasets have given scholars opportunities to refine the accuracy and reliability of predicting annotated emotions from audio.
 
@@
 
-- Our aim is to establish the level of predictive accuracy for both continuous models of emotional expression (valence and arousal) and classification of emotion categories based on available and recent studies.
+- Our aim is to establish the level of predictive accuracy for both models of emotional expression that can account for track-specific coordinates in affective circumple space (valence and arousal) and classification of emotion categories based on available and recent studies.
 - We seek to identify the types of issues (modelling techniques, features, and musical qualities used) that significantly influence the prediction rates.
@@
 
-We preregistered our meta-analysis plan (OSF URL here, also available at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).
+We preregistered our meta-analysis plan on 21 June 2024 at OSF, [https://osf.io/c5wgd](https://osf.io/c5wgd), and the plan is also available at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).
 
@@
 
+[optional Figure: flowchart of the study inclusions/eliminations]
+
+- Devote some sentences to quality control issues (what were the most common reasons for eliminating studies).
+
 # Results
 
-First we could describe the overall pattern of data (modelling techniques, cross-validation, popular datasets, etc).
+First we could describe the overall pattern of data (regression vs classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
+
+TABLE 1: Summary of data (part of `analysis/preprocessing.qmd`)
+
+Talk about the stimuli and
 
@@
 
-## Prediction success for valence and arousal
+## Prediction success for valence and arousal (or affect dimensions)
 
-Out of XX studies reporting this task, the majority (xx%) ...
+See `analysis/analysis.qmd`
 
-| Concept | N    | Md $R^2$|
-|:--------|:-----|:--------|
-| Valence | ??   | ??      |
-| Arousal | ??   | ??      |
+- Decision: Report all models or the best model?
+  * Possible solution: Report all models, trimmed models, and but mainly rely on Max
 
-TABLE: xxxx
+- Report issues of heterogeneity right here (can be visualised with funnel plots, see below)
+
+- Optional Figure X: Funnel plot that combines valence and arousal (separate panels) with FULL/TRIMMED data shown with markers"
+
+Table 2. Meta-analytic diagnostic for all regression studies predicting valence from audio.
+
+| Concept     | Models, obs|$r$ [95%-CI]              | $t$ | $p$  |$\tau^2$|$I^2$|
+|:------------|:----------|:--------|:--------------|:----|:-----|:-----|:------|
+| Valence All | 49,42648  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
+| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1% [0.0%; 58.2%]|
+| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
+| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
+| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% |
+| *N Features*|           |                         |     |      |      |       |
+| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+| *Techniques*|           |                         |     |      |      |       |
+|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+
+Figure 1. Forest plot of valence prediction (Max?)
+`analysis/figure1.qmd`
+
+Summarise the results here briefly
+
+Moving on the arousal, ...
+
+Table 3. Meta-analytic diagnostic for all regression studies predicting arousal from audio.
+
+| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
+|:------------|:-----------|:---------|:-------------|:----|:-----|:-----|:------|
+| Arousal     | 14,9035    |          |              |     |      |      |       |
+| Arousal Trim| 27,18402   |          |              |     |      |      |       |
+| Arousal M   | 14,10641   |          |              |     |      |      |       |
+| Arousal Md  | 14,10641   |          |              |     |      |      |       |
+| Arousal Max | 14,10641   |          |              |     |      |      |       |
+| *N Features*|            |          |              |     |      |      |       |   
+| <18 F       |            |          |              |     |      |      |       |
+| 18-260 F    |            |          |              |     |      |      |       |
+| 260+ F      |            |          |              |     |      |      |       |
+| *Techniques*|            |          |              |     |      |      |       |  
+|   KS        |            |          |              |     |      |      |       |
+|   LM        |            |          |              |     |      |      |       |
+|   FD        |            |          |              |     |      |      |       |
+|   NN        |            |          |              |     |      |      |       |
+|   RF        |            |          |              |     |      |      |       |
+
+Figure 2. Forest plot of arousal prediction (using Max?)
+
+Summarise here the pattern of results
+
+## Classification studies
+
+Summary of details contained in Table 1, but summarise at least the categories predicted before moving onto the main findings.
+
+Table 4. Meta-analytic diagnostic for all classification studies predicting emotion categories from audio.
+
+Heterogeneity issues
+
+Figure 3. Forest plot of arousal prediction (Max?) (Unless we do some custom plotting)
+
+- Figure Optional: Funnel plot (I haven't seen this yet)
 
@@
 
-To be done.
+## Concise summary of what we did and found
+
+## Main outcomes 
+- Arousal is easier to predict (r = 0.7627) than valence (r = 0.6236), as we predicted. The glass ceiling seems to be at ...
+- Classification ...
+- Model accuracy is surprisingly little affected by the number of features (?) or modelling technique (?). 
+- Some of the complex state-of-the-art techniques (e.g., NNs) do not deliver impressive improvements over older techniques (e.g., SVR, RF)
+- Variation in study/model/data quality is large and can be seen in heterogenuity and the amount of studies eliminated
+
+## Calls for action/points to improve in such studies
+- *Documentation* the details in full (features, stimuli, model details, cross-validation)
+- *Quality* of the underlying data (emotion ratings, classes, or even stimulus properties?
+- *Generalisibility* of the models (some studies such as X and Y address this by applying the models across several datasets)
+- Diversity in the evaluative aspects of studies: *overfitting*, numerous ways of cross-validating, not sharing data or analysis scripts, not reporting in the same way
+- What proportion of stimuli are Western music, and what genres tend to dominate?
 

### 2024-07-11 analysis/analysis.qmd
working on preprocessing and analysis

@@
 tmp <- dplyr::filter(R_studies,dimension=="valence")
-tmp<-drop_na(tmp)
+dim(tmp)
+tmp <- tmp[!is.na(tmp$values),]
+dim(tmp)
+
 #sqrt(tmp$values) # convert from R^2 to r
@@
 
-m.cor <- metacor(cor = values, 
+m.cor <- metacor(cor = values,     # values 
                  n = stimulus_n,
-                 studlab = unique_id,
+                 studlab = unique_id, # unique_id
                  data = tmp,
@@
                  random = TRUE,
+                 prediction = TRUE,
+                 backtransf = TRUE,
                  sm = "ZCOR",
@@
 
-print(m.cor)
+#print(m.cor)
+
+m.cor_backtransformed <- m.cor
+m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
+print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
+
+```
+#### Custom plot
+
+```{r}
+tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
+
+tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
+tmpdata$citekey<-factor(tmpdata$citekey)
+
+g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
+  geom_point(show.legend = FALSE) +
+  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
+  ylab('Standard Error') + 
+  xlab('r')+
+  scale_y_reverse()+
+  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
+#  coord_flip()+
+  theme_bw()
+print(g)
 ```
@@
              leftlabs = c("Author", "g", "SE"),studlab = citekey)
-plot(eggers.test(m.cor))
+
+funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
 ```
@@
 ```
+
 #### Re-run the analysis without the outliers
@@
   theme_bw()
-
+print(fp)
 ```
@@
 tmp <- dplyr::filter(R_summary,dimension=="arousal")
-m.cor <- metacor(cor = valuesMedian, 
+tmp <- dplyr::filter(R_studies,dimension=="arousal")
+dim(tmp)
+tmp <- tmp[!is.na(tmp$values),]
+dim(tmp)
+#tmp<-drop_na(tmp)
+
+m.cor <- metacor(cor = values, 
                  n = stimulus_n,
-                 studlab = studyREF,
+                 studlab = unique_id,
                  data = tmp,
@@
 print(m.cor)
+```
+### Trimmed analysis
+```{r}
+O <- find.outliers(m.cor)
 ```

### 2024-07-11 analysis/preprocessing.qmd
working on preprocessing and analysis

@@
 ```{r}
-#C_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal'
-#R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
-#R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av')) # relates to distances, can be omitted
-
 table(C_studies$stimulus_n)

### 2024-07-11 manuscript/manuscript.qmd
working on preprocessing and analysis

@@
 | Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$|
-|:------------|:----------|:--------|:--------------|:----|:-----|:-----|:------|
-| Valence All | 49,42648  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
-| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1% [0.0%; 58.2%]|
+|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
+| Valence All | 49,42480  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
+| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
 | Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
@@
 | Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% |
+| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% |
 | *N Features*|           |                         |     |      |      |       |
@@
 | Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
-|:------------|:-----------|:---------|:-------------|:----|:-----|:-----|:------|
-| Arousal     | 14,9035    |          |              |     |      |      |       |
-| Arousal Trim| 27,18402   |          |              |     |      |      |       |
-| Arousal M   | 14,10641   |          |              |     |      |      |       |
-| Arousal Md  | 14,10641   |          |              |     |      |      |       |
-| Arousal Max | 14,10641   |          |              |     |      |      |       |
+|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
+| Arousal     | 55,43160   | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
+| Arousal Trim| 27,18402   | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
+| Arousal M   | 14,10641   | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
+| Arousal Md  | 14,10641   | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
+| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  |
+| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  |
+
 | *N Features*|            |          |              |     |      |      |       |   

### 2024-07-11 R/build-df.R
Revert "add genre and journal info"
This reverts commit 3f6cf7b74b3d8ce57b0d09544eaadefd8240d951.

@@ -7,9 +7,7 @@ get_metaMER_df <- function(path_2_studies = here::here('studies')) {
 
 bib_file <- read.delim(paste0(path_2_studies, '/bib/extractions.bib'),
                        sep = '@', header = F)
-journal <- bib_file[str_detect(tolower(bib_file$V1), 'journal = '),]$V1
-journal <- journal[1:length(journal)-1]
-journal <- stringr::str_remove(journal, "JOURNAL ")
+
 # get citekeys from bibtex file:
 citekeys <- unique(bib_file$V2)
 # improve formatting
@@ -71,7 +69,6 @@ meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) stringr::str_match(
 # replace first column with citationkeys
 meta_df[,1] <- names(meta_list)
 names(meta_df) <- c('citekey', search_fields)
-meta_df$journal <- journal
 names(meta_df) <- trimws(names(meta_df))
 
 Sys.sleep(0.25)
@@ -89,7 +86,6 @@ meta_df <- apply(meta_df, 2, function(x) stringr::str_remove_all(x, '%%.*'))
 # remove extra characters in final column
 meta_df[, ncol(meta_df)] = stringr::str_remove_all(meta_df[, ncol(meta_df)], '\\}')
 meta_df <- as.data.frame(meta_df)
-
 
 return(meta_df)
 

### 2024-07-11 R/parse-model-output.R

@@ -65,14 +65,12 @@ summarize_matrix = function(matrix) {
 
 get_study_results <- function(study) {
   citekey <- unique(as.character(study[,'citekey']))
-  journal <- unique(as.character(study[,'journal']))
   stimulus_n <- unique(as.character(study[,'stimulus_n']))
   feature_n <- unique(as.character(study[,'feature_n']))
   participant_n <- unique(as.character(study[,'participant_n']))
   model_category <- unique(as.character(study[,'model_category']))
   feature_source <- unique(as.character(study[,'feature_source']))
   feature_reduction_method <- unique(as.character(study[,'feature_reduction_method']))
-  stimulus_genre <- unique(as.character(study[,'stimulus_genre']))
 
   #print(citekey)
   #print(as.character(study[,'model_rate_emotion_values']))
@@ -83,8 +81,6 @@ get_study_results <- function(study) {
   
     clean_df <- dplyr::tibble(
       citekey,
-      journal,
-      stimulus_genre,
       model_category = trimws(model_category, which = 'both'), 
       stimulus_n,
       feature_n,

### 2024-07-11 R/build-df.R
add journal and genre info

@@ -7,7 +7,9 @@ get_metaMER_df <- function(path_2_studies = here::here('studies')) {
 
 bib_file <- read.delim(paste0(path_2_studies, '/bib/extractions.bib'),
                        sep = '@', header = F)
-
+journal <- bib_file[str_detect(tolower(bib_file$V1), 'journal = '),]$V1
+journal <- journal[1:length(journal)-1]
+journal <- stringr::str_remove(journal, "JOURNAL ")
 # get citekeys from bibtex file:
 citekeys <- unique(bib_file$V2)
 # improve formatting
@@ -69,6 +71,7 @@ meta_df[,ncol(meta_df)+1] <- sapply(meta_df[,1], function(x) stringr::str_match(
 # replace first column with citationkeys
 meta_df[,1] <- names(meta_list)
 names(meta_df) <- c('citekey', search_fields)
+meta_df$journal <- journal
 names(meta_df) <- trimws(names(meta_df))
 
 Sys.sleep(0.25)
@@ -86,6 +89,7 @@ meta_df <- apply(meta_df, 2, function(x) stringr::str_remove_all(x, '%%.*'))
 # remove extra characters in final column
 meta_df[, ncol(meta_df)] = stringr::str_remove_all(meta_df[, ncol(meta_df)], '\\}')
 meta_df <- as.data.frame(meta_df)
+
 
 return(meta_df)
 

### 2024-07-11 R/parse-model-output.R

@@ -65,12 +65,14 @@ summarize_matrix = function(matrix) {
 
 get_study_results <- function(study) {
   citekey <- unique(as.character(study[,'citekey']))
+  journal <- unique(as.character(study[,'journal']))
   stimulus_n <- unique(as.character(study[,'stimulus_n']))
   feature_n <- unique(as.character(study[,'feature_n']))
   participant_n <- unique(as.character(study[,'participant_n']))
   model_category <- unique(as.character(study[,'model_category']))
   feature_source <- unique(as.character(study[,'feature_source']))
   feature_reduction_method <- unique(as.character(study[,'feature_reduction_method']))
+  stimulus_genre <- unique(as.character(study[,'stimulus_genre']))
 
   #print(citekey)
   #print(as.character(study[,'model_rate_emotion_values']))
@@ -81,6 +83,8 @@ get_study_results <- function(study) {
   
     clean_df <- dplyr::tibble(
       citekey,
+      journal,
+      stimulus_genre,
       model_category = trimws(model_category, which = 'both'), 
       stimulus_n,
       feature_n,

### 2024-07-11 analysis/analysis.qmd
updated analysis heterogenuity issues

@@
 tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp <- dplyr::filter(R_studies,dimension=="valence")
-dim(tmp)
-tmp <- tmp[!is.na(tmp$values),]
-dim(tmp)
+#tmp <- dplyr::filter(R_studies,dimension=="valence")
+#dim(tmp)
+
+#if all studies, remove two
+#tmp <- tmp[!is.na(tmp$values),]
+#dim(tmp)
 
@@
 
-m.cor <- metacor(cor = values,     # values 
+m.cor <- metacor(cor = valuesMax,     # values 
                  n = stimulus_n,
-                 studlab = unique_id, # unique_id
+                 studlab = citekey, # unique_id
                  data = tmp,
@@
 tmp <- dplyr::filter(R_summary,dimension=="arousal")
-tmp <- dplyr::filter(R_studies,dimension=="arousal")
+#tmp <- dplyr::filter(R_studies,dimension=="arousal")
 dim(tmp)
-tmp <- tmp[!is.na(tmp$values),]
+#tmp <- tmp[!is.na(tmp$values),]
 dim(tmp)
@@
 
-m.cor <- metacor(cor = values, 
+m.cor <- metacor(cor = valuesMax, 
                  n = stimulus_n,
-                 studlab = unique_id,
+                 studlab = citekey,
                  data = tmp,

### 2024-07-11 analysis/preprocessing.qmd
updated analysis heterogenuity issues

@@
 
-## Pull data to analyse regression studies
+# Pull data to analyse regression studies
 
@@
 ```
-### Homogenise the outcome variable names to valence and arousal
+
+## Homogenise the outcome variable names to valence and arousal
 
@@
 
-### Diagnostics
+## Diagnostics
 
@@
 
-### Select a summary measure for valence and arousal separately
+## Select a summary measure for valence and arousal separately
 
@@
 
-### Visualise Summary on two dimensions
+## Visualise Summary on two dimensions
 
@@
 
-### Plot success across the years
+## Plot success across the years
 
@@
 ```
-### Simple model complexity metric
+
+## Simple model complexity metric
 
@@
 
-### Explore feature_n_complexity and model success
+## Explore feature_n_complexity and model success
 
@@
 
-### Create descriptive table for the manuscript
+## Create descriptive table for the manuscript
 
@@
 
-### Export as csv
+## Export as csv
 
@@
 
-## Pull data to analyse classification studies
+# Pull data to analyse classification studies
 
@@
 ```
-### Homogenise the outcome variable names to valence and arousal
+## Homogenise the outcome variable names to valence and arousal
 
@@
 
-g1<-ggplot(R_studies,aes(x=values,fill=citekey,color=dimension))+
+g1<-ggplot(C_studies,aes(x=values,fill=citekey,color=dimension))+
   geom_histogram()+
@@
 ```
-### Simple model complexity metric
+## Simple model complexity metric
 
@@
 
-### Export as csv
+## Export as csv
 
 ```{r}
-write.csv(x = R_studies,file = 'R_studies.csv')
-write.csv(x = R_summary,file = 'R_summary.csv')
+#write.csv(x = R_studies,file = 'R_studies.csv')
+#write.csv(x = R_summary,file = 'R_summary.csv')
 ```

### 2024-07-11 manuscript/manuscript.qmd
updated analysis heterogenuity issues

@@
 
-| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$|
+| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$| Prediction interval
 |:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
@@
 | Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
-| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% |
-| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% |
+| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% | -0.0719; 0.9260
+| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% | 0.4470; 0.7396
 | *N Features*|           |                         |     |      |      |       |
@@
 |   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+
+OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION,
+
+see this to ignore I^2 and rely on prediction interval: 
+https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678
 
@@
 | Arousal Md  | 14,10641   | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
-| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  |
-| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  |
+| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
+| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047
 

### 2024-07-12 R/build-df.R
update df build

@@ -7,7 +7,7 @@ get_metaMER_df <- function(path_2_studies = here::here('studies')) {
 
 bib_file <- read.delim(paste0(path_2_studies, '/bib/extractions.bib'),
                        sep = '@', header = F)
-journal <- bib_file[str_detect(tolower(bib_file$V1), 'journal = '),]$V1
+journal <- bib_file[stringr::str_detect(tolower(bib_file$V1), 'journal = '),]$V1
 journal <- journal[1:length(journal)-1]
 journal <- stringr::str_remove(journal, "JOURNAL ")
 # get citekeys from bibtex file:

### 2024-07-12 analysis/preprocessing.qmd
created classification preprocessing and analysis parts

@@
 #| warning: false
+library(stringr) 
 # get metaMER df:
@@
 
+### Classify stimulus genres
+
+```{r}
+#| eval: true
+metaMER_results$stimulus_genre_mixed <- 'SingleGenre'
+metaMER_results$stimulus_genre_mixed[str_detect(metaMER_results$stimulus_genre,',|multi')] <- 'MultiGenre' # Class name from Elements of Stat.."
+#table(metaMER_results$stimulus_genre_mixed)
+```
+
+### Classify journals
+
+```{r}
+metaMER_results$journal_type <- "Engineering"
+metaMER_results$journal_type[str_detect(metaMER_results$journal,'Quarterly Journal of Experimental Psychology|PSYCHOLOGY OF MUSIC|PLOS ONE|JOURNAL OF NEW MUSIC RESEARCH|IEEE-ACM TRANSACTIONS ON AUDIO SPEECH AND LANGUAGE PROCESSING|FRONTIERS IN PSYCHOLOGY|Frontiers in Psychology')] <- 'Psychology' # Class name from Elements of Stat.."
+
+#table(metaMER_results$journal_type)
+```
+
 ## Summarise all
@@
 # note that we have some classification studies that also do regression and vice versa?
+# THIS IS CORRECT:
+# [1] "We have 1192 observations"
+# [1] "We have 37 studies"
+# [1] "Where 25 are regression studies"
+# [1] "Where 12 are classification studies"
 
@@
 ```{r}
-R_studies <- dplyr::filter(metaMER_results,model_category=='regression' & str_detect(measure,'r|cc|r2|R2')) #  
+
+unique(metaMER_results$citekey[metaMER_results$model_category=="regression"])
+
+R_studies <- dplyr::filter(metaMER_results, measure %in% c('r','ccc','pcc','cc','r2','R2')) #  
+R_studies$statistic
 dim(R_studies)
 
-# eliminate measures that we don't need now
-R_studies <- dplyr::filter(R_studies,!str_detect(statistic,'r2-95l|r2-95u|pvalue|upper|lower|sd|null|rmse'))
-R_studies <- dplyr::filter(R_studies,!str_detect(measure,'nFeatures|rmse|jensen shannon divergence|accuracy|ccc|vector distance'))
+# explicit NA coding
+R_studies$statistic[is.na(R_studies$statistic)]<-'r2'
 
+# include measures we need 
+R_studies <- dplyr::filter(R_studies,str_detect(statistic,'adjusted|ccc|pcc|cc|globalOptimal|localOptimal|mean|r2|r'))
+dim(R_studies)
 table(R_studies$measure)
@@
 R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
-R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av')) # relates to distances, can be omitted
+R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av|resonance')) # relates to distances, can be omitted
 
@@
 # Deal with four studies involving multiple datasets: 
-R_studies$stimulus_n[R_studies$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "] <- 938 #resolved from the paper
+R_studies$stimulus_n[R_studies$stimulus_n==" emoMusic: 744, soundtracks: 360, chinese: 500 "] <- 938 # resolved from the paper
 R_studies$stimulus_n[R_studies$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372 # resolved
@@
 ```
+## Check studies included
+
+```{r}
+#| eval: false
+included_in_summary <- R_summary$citekey[R_summary$dimension=='arousal']
+
+included_originally <- unique(metaMER_results$citekey[metaMER_results$model_category=='regression'])
+
+included_originally[!included_originally %in% included_in_summary]
+
+```
 
@@
 
-R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=T),valuesMedian=median(values,na.rm=T),valuesMax=max(values,na.rm=T),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id))
+R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),journal_type=first(journal_type),stimulus_genre_mixed=first(stimulus_genre_mixed))
 
@@
 ```{r}
-C_studies <- dplyr::filter(metaMER_results,model_category=='classification' & str_detect(measure,'accuracy|r2|mcc')) #  
+C_studies<-metaMER_results
+sum(is.na(C_studies$measure)) # 0
+sum(is.na(C_studies$statistic)) # 426
+
+C_studies$statistic[is.na(C_studies$statistic)]<-'acc'
+
+C_studies <- dplyr::filter(C_studies, str_detect(measure,'mcc|accuracy|auc|classification|f1|fscore|fvalue|kappa|precision|recall')) #
+table(C_studies$measure)
 dim(C_studies)
+table(C_studies$statistic)
 
-# eliminate measures that we don't need now
-C_studies <- dplyr::filter(C_studies,values>0)
-C_studies$statistic[is.na(C_studies$statistic)]<-'Not defined'
-C_studies <- dplyr::filter(C_studies,!str_detect(statistic,'pvalue|upper|lower'))
-C_studies <- dplyr::filter(C_studies,str_detect(measure,'accuracy|mcc|r2'))
+C_studies <- dplyr::filter(C_studies, str_detect(statistic,'mean|median|acc')) #  
 dim(C_studies)
+length(unique(C_studies$citekey))
 
 table(C_studies$measure,C_studies$statistic)
+table(C_studies$measure,C_studies$citekey)
+table(C_studies$statistic,C_studies$citekey)
 
+# ToDo
+# how to convert accuracy (precision, recall, f) into kappa or mcc
+# There IS NO solution unfortunately, accuracy and mcc can vary independently, but
+# see Chicco and Jurman, 2020, https://doi.org/10.1186/s12864-019-6413-7
+# which shows that MCC is the best. The paer compares accuracy and F1 to MCC 
+# and shows high correlations between accuracy and MCC (r=0.90-0.92). 
+# It is only the exceptions (unbalanced datasets with binary classification) that deliver major discrepancies. Our dataset does not seem to be having these, so
+# perhaps we can equate accuracy with MCC in a minority of cases.
+
+# Conversion
+# convert one 'classification' into accuracy (bai2017mu)
+# convert one 'f1' into accuracy (hu2022de)
+C_studies$measure[C_studies$citekey=='bai2017mu'] <- 'accuracy'
+C_studies$measure[C_studies$citekey=='hu2022de' & C_studies$measure=='f1']<-'accuracy'
 dim(C_studies)
-# Conversion into mcc (==r), do we need
+C_studies <- dplyr::filter(C_studies, str_detect(measure,'mcc|accuracy')) #  
+dim(C_studies)
+table(C_studies$measure,C_studies$citekey)
+
+# take accuracy as MCC in those studies that have not specified mcc
+C_studies$accuracy_converted_to_mcc <- 0
+C_studies$accuracy_converted_to_mcc[C_studies$citekey=='bai2016di' | 
+                  C_studies$citekey=='bai2017mu' | 
+                  C_studies$citekey=='hizlisoy2021mu' |
+                  C_studies$citekey=='hu2022de' |    
+                  C_studies$citekey=='yeh2014po' |
+                  C_studies$citekey=='zhang2016br' |
+                  C_studies$citekey=='zhang2017fe' 
+                  & C_studies$measure=='accuracy']<-1
+
+C_studies$measure[C_studies$citekey=='bai2016di' | 
+                  C_studies$citekey=='bai2017mu' | 
+                  C_studies$citekey=='hizlisoy2021mu' |
+                  C_studies$citekey=='hu2022de' |    
+                  C_studies$citekey=='yeh2014po' |
+                  C_studies$citekey=='zhang2016br' |
+                  C_studies$citekey=='zhang2017fe' 
+                  & C_studies$measure=='accuracy']<-'mcc'
+table(C_studies$measure,C_studies$citekey)
+C_studies <- dplyr::filter(C_studies, str_detect(measure,'mcc')) #  
+dim(C_studies)
+table(C_studies$measure,C_studies$accuracy_converted_to_mcc)
+t.test(C_studies$values,y = C_studies$accuracy_converted_to_mcc) # There is a difference
 
 ```
-## Homogenise the outcome variable names to valence and arousal
+## Homogenise the stimulus N
 
@@
 C_studies$stimulus_n[C_studies$stimulus_n==" ISMIR2012: 2886, NJU_V1: 777, Hindi: 1037  "] <- 2886+777+1037 # decided to take this from validation
-C_studies<-C_studies[!str_detect(C_studies$stimulus_n,'not specified'),]
-C_studies<-C_studies[!str_detect(C_studies$stimulus_n,'Specified elsewhere'),]
+C_studies$stimulus_n[C_studies$stimulus_n==" total: 564; unambiguous: 416, circular validation: 39 "] <- 564 # 
 C_studies$stimulus_n <- as.numeric(C_studies$stimulus_n)
@@
 ```{r}
+#| eval: false
 library(ggplot2)
@@
   facet_wrap(.~model_class_id)+
-  scale_color_manual(values = c('black','white'))+
   theme_dark()+
@@
 
+- [ ] Ask Cameron whether it is OK to treat dimension contents as they are all classification studies (the exceptions are `av` and `valence` and `arousal`).
+
 ```{r}
 library(tidyverse)
-R_studies$citekey <- factor(R_studies$citekey)
-R_studies$dimension <- factor(R_studies$dimension)
+C_studies$citekey <- factor(C_studies$citekey)
 
-R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=T),valuesMedian=median(values,na.rm=T),valuesMax=max(values,na.rm=T),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id))
+C_summary <- summarise(group_by(C_studies,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id), stimulus_genre_mixed=first(stimulus_genre_mixed),journal_type = first(journal_type))
 
@@
 
-## Visualise Summary on two dimensions
-
-Add variation from within the studies (alternative models)
+## Visualise Summary
 
 ```{r}
-R_summary_split <- pivot_wider(R_summary,id_cols = citekey, names_from = c(dimension), values_from = valuesMax)
 
-g2 <- ggplot(R_summary_split,aes(x=valence,y=arousal,label=citekey))+
-  geom_label()+
-  theme_bw()+
-  scale_x_continuous(breaks = seq(0,1,by=.1))+
-  scale_y_continuous(breaks = seq(0,1,by=.1))
-
+g2 <- ggplot(C_summary,aes(x=stimulus_n,y=valuesMax,label=citekey,color=stimulus_genre_mixed))+
+  geom_point()+
+  geom_label_repel(size=1.5)+
+#  coord_flip()+
+  theme_bw()
 g2
 
+g3 <- ggplot(C_summary,aes(x=stimulus_n,y=valuesMax,label=citekey,color=model_class_id))+
+  geom_point()+
+  geom_label_repel(size=1.2)+
+#  coord_flip()+
+  theme_bw()
+g3
+
 ## could be more informative when done with the full data
-R_studies$citekey<-factor(R_studies$citekey)
-R_studies$dimension<-factor(R_studies$dimension)
-
-R_studies_split <- pivot_wider(R_studies,id_cols = c(unique_id,citekey,model_class_id), names_from = c(dimension), values_from = c(values),values_fn = mean)
-R_studies_split<-drop_na(R_studies_split)
+C_studies$citekey<-factor(C_studies$citekey)
 
@@
 
-g3 <- ggplot(R_studies_split,aes(x=valence,y=arousal,label=citekey,color=model_class_id,fill=model_class_id))+
+g4 <- ggplot(C_studies,aes(x=stimulus_n,y=values,label=citekey,color=model_class_id,fill=model_class_id))+
   geom_point(size=4)+
-  geom_label_repel(size=3, max.overlaps=50,show.legend = T,color='white')+
-  scale_x_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
-  scale_y_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
+  geom_label_repel(size=1.2, max.overlaps=50,show.legend = T,color='white')+
+#  scale_x_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
+#  scale_y_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
   theme_bw()
-g3
+g4
 
@@
 
-## Plot success across the years
+## Simple model complexity metric based on feature_n
 
 ```{r}
-#| eval: true
-# Add year!
-R_studies$year <- as.numeric(str_match(R_studies$citekey,'[0-9]+'))
+table(C_studies$feature_n)
+C_studies$feature_n[str_detect(C_studies$feature_n,'eight different ')]<-600 # arbitrary!
+C_studies$feature_n[str_detect(C_studies$feature_n,'126, retained 97')]<-126 
+C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  arbitrary!
+C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')]<-548 
+C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')]<-548 
+C_studies$feature_n[str_detect(C_studies$feature_n,'8; 3 after')]<-8 
+C_studies$feature_n[str_detect(C_studies$feature_n,'between 9 and 10')]<-10 
+C_studies$feature_n[str_detect(C_studies$feature_n,'summarize feature')]<-600 # arbitrary
+table(C_studies$feature_n)
 
-g3 <- ggplot(R_studies,aes(x=year,y=values,colour=model_class_id))+
-  geom_point(show.legend = T)+
-  facet_wrap(.~dimension)+
-  theme_bw()
-g3
-```
-## Simple model complexity metric
+C_studies$feature_n<-as.numeric(C_studies$feature_n)
 
-Ratio of obs./features or just a classification based on feature n (quintiles).
-
-```{r}
-R_studies$feature_n==" 15; 23 in table, but 15 reported "
-
-R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved from the paper
-
-R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved
-R_studies$feature_n[R_studies$feature_n==" before_selection = 45, after_selection = 6  "] <- 45 #resolved
-R_studies$feature_n[R_studies$feature_n==" model 1: 52, model 2 = 68, model 3 = 260, model 4 = 388 "] <- 388 #resolved
-R_studies$feature_n[R_studies$feature_n==" variable, 557 before feature selection "] <- 557 #resolved
-
-R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 50 #resolved
-#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
-#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
-
-R_studies$feature_n<-as.numeric(R_studies$feature_n)
-
-print(quantile(R_studies$feature_n,c(0.333,0.666),na.rm = T))
+print(quantile(C_studies$feature_n,c(0.333,0.666),na.rm = TRUE))
 #quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)
@@
 # Assign
-R_studies$feature_n_complexity <- cut(R_studies$feature_n,
+C_studies$feature_n_complexity <- cut(C_studies$feature_n,
                                       breaks = c(0,
-                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
-                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
+                                                 as.numeric(quantile(C_studies$feature_n,c(0.333),na.rm = TRUE)),
+                                                 as.numeric(quantile(C_studies$feature_n,c(0.666),na.rm = TRUE)),
                                                  1000),
-                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
-table(R_studies$feature_n_complexity)
+                                      labels = c("Feature n < 119","Feature n > 119 & < 548","Feature n > 548"))
+table(C_studies$feature_n_complexity)
 ```
@@
 
-Needs to be done from the unsummarised data (`R_studies`).
+Needs to be done from the unsummarised data (`C_studies`).
 
 ```{r}
-tmp <- drop_na(R_studies)
+#| eval: true
+tmp <- drop_na(C_studies)
 library(ggdist)
@@
   #geom_label_repel(size=2,max.overlaps = 50)+
-  facet_wrap(dimension~feature_n_complexity)+
+  facet_wrap(.~feature_n_complexity)+
   ylab("Correlation Coefficient")+
   xlab("Model Technique")+
-#  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
+  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
   geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
@@
   theme_bw()
-g
+print(g)
 #ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
@@
 ```{r}
-TR <- NULL
-TR$study_n <- length(unique(R_studies$citekey))
-TR$model_n <- nrow(R_studies)
-t<-table(R_studies$model_class_id)
+TC <- NULL
+TC$study_n <- length(unique(C_studies$citekey))
+TC$model_n <- nrow(C_studies)
+t<-table(C_studies$model_class_id)
 t2 <- paste0(names(t),': ', as.numeric(t))
-TR$model_types_n <- str_c(t2,collapse = "\n")
-TR$feature_Desc <- paste0('Min=',min(R_studies$feature_n,na.rm = TRUE),', Md=',median(R_studies$feature_n,na.rm = TRUE),', Max=', max(R_studies$feature_n,na.rm = TRUE))
-TR$stimulus_Desc <- paste0('Min=',min(R_studies$stimulus_n,na.rm = TRUE),', Md=',median(R_studies$stimulus_n,na.rm = TRUE),', Max=', max(R_studies$stimulus_n,na.rm = TRUE))
-print(TR)
+TC$model_types_n <- str_c(t2,collapse = "\n")
+TC$feature_Desc <- paste0('Min=',min(C_studies$feature_n,na.rm = TRUE),', Md=',median(C_studies$feature_n,na.rm = TRUE),', Max=', max(C_studies$feature_n,na.rm = TRUE))
+TC$stimulus_Desc <- paste0('Min=',min(C_studies$stimulus_n,na.rm = TRUE),', Md=',median(C_studies$stimulus_n,na.rm = TRUE),', Max=', max(C_studies$stimulus_n,na.rm = TRUE))
+print(TC)
 
@@
 ```{r}
-#write.csv(x = R_studies,file = 'R_studies.csv')
-#write.csv(x = R_summary,file = 'R_summary.csv')
+write.csv(x = C_studies,file = 'C_studies.csv')
+write.csv(x = C_summary,file = 'C_summary.csv')
 ```

### 2024-07-12 manuscript/manuscript.qmd
created classification preprocessing and analysis parts

@@
 
+| Model       | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
+|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
+| All         | 89,87347   | 0.8074 [0.7681; 0.8407] |21.4 |0.0001|0.2415|99.7%  |
+| All Trim    | 29,6499    | 0.8185 [0.8046; 0.8314] | 58.3|0.0001|0.0066| 60.4%  |
+| Max         | 14,17184   | 0.8564 [0.7386; 0.9234] | 10.3|0.0001|0.329 | 99.8% |
+| Max Trim    | 6,3653     | 0.8689 [0.7760; 0.9249] | 11.6|0.0001|0.0749| 97.5% |
+
 Heterogeneity issues

### 2024-07-12 analysis/preprocessing.qmd
preprocessing updates

@@
 
-print(paste("We have", nrow(metaMER_results), "observations"))
+cat(paste("We have", nrow(metaMER_results), "observations"))
 
-print(paste("We have", length(unique(metaMER_results$citekey)), "studies"))
+cat(paste("\nWe have", length(unique(metaMER_results$citekey)), "studies"))
 
-print(paste("Where", length(unique(metaMER_results$citekey[metaMER_results$model_category=='regression'])), "are regression studies"))
+cat(paste("\nWhere", length(unique(metaMER_results$citekey[metaMER_results$model_category=='regression'])), "are regression studies"))
 
-print(paste("Where", length(unique(metaMER_results$citekey[metaMER_results$model_category=='classification'])), "are classification studies"))
+cat(paste("\nWhere", length(unique(metaMER_results$citekey[metaMER_results$model_category=='classification'])), "are classification studies"))
 # note that we have some classification studies that also do regression and vice versa?
-# THIS IS CORRECT:
-# [1] "We have 1192 observations"
+# THIS IS CORRECT (updated 12 July 2024):
+# [1] "We have 1238 observations"
 # [1] "We have 37 studies"
-# [1] "Where 25 are regression studies"
-# [1] "Where 12 are classification studies"
+# [1] "Where 23 are regression studies"
+# [1] "Where 14 are classification studies"
+
+# Add a check for these properties ToDo
 
@@
 R_studies <- dplyr::filter(metaMER_results, measure %in% c('r','ccc','pcc','cc','r2','R2')) #
-R_studies$statistic
-dim(R_studies)
 
@@
 
-dim(R_studies)
 R_studies$values[R_studies$measure=='R2']<-sqrt(R_studies$values[R_studies$measure=='R2']) # recode R2 into r
@@
 
-table(R_studies$stimulus_n)
+#table(R_studies$stimulus_n)
 
 # Deal with four studies involving multiple datasets:
+
 R_studies$stimulus_n[R_studies$stimulus_n==" emoMusic: 744, soundtracks: 360, chinese: 500 "] <- 938 # resolved from the paper
@@
 R_studies$stimulus_n[R_studies$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40 # decided to take this from validation
+R_studies$stimulus_n[R_studies$stimulus_n==" study 1: 100; study 2: 20"] <- 20 #
+
+R_studies$stimulus_n[R_studies$stimulus_n==" DEAM: 744, PMEmo: 206  "] <- 744 # we have encoded this based on stronger results on DEAM compared to PMEmo.
+
+R_studies$stimulus_n[R_studies$stimulus_n==" NTUMIR: 60, MediaEval2013: 744  "] <- 60 # we have encoded this based on stronger results on NTUMIR compared to MediaEval
+
+R_studies$stimulus_n[R_studies$stimulus_n==" 1020; MediaEval2014: 1000: music perception database 1: 6, music perception database 2: 9, music perception database 3: 8, music perception database 4: 7   "] <- 1020
+
 # REDO with a clearer function
@@
 R_studies$stimulus_n[R_studies$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 60+818+1608 #
+
+table(R_studies$stimulus_n)
+
 R_studies$stimulus_n <- as.numeric(R_studies$stimulus_n)
@@
   facet_wrap(.~model_class_id)+
-  scale_color_manual(values = c('black','white'))+
+#  scale_color_manual(values = c('black','white'))+
   theme_dark()+
@@
 ```{r}
-R_studies$feature_n==" 15; 23 in table, but 15 reported "
 
@@
                                                  1000),
-                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
+                                      labels = c("Feature n < 130","Feature n > 130 & < 653","Feature n > 653"))
 table(R_studies$feature_n_complexity)
@@
 ```{r}
-tmp <- drop_na(R_studies)
+#tmp <- drop_na(R_studies)
+tmp <- R_studies[!is.na(R_studies$values),]
+
 library(ggdist)
@@
 ```
+#### Get the number of categories in the classification task
+
+```{r}
+tmp <- metaMER_results
+tmp2 <- tmp[which(tmp$statistic=='n'),]
+no_of_classes <- summarise(group_by(tmp2,citekey),first(values))
+print(no_of_classes)
+rm(tmp,tmp2)
+```
+
 ## Homogenise the stimulus N
@@
 
-g1<-ggplot(C_studies,aes(x=values,fill=citekey,color=dimension))+
+g1<-ggplot(C_studies,aes(x=values,fill=citekey))+
   geom_histogram()+
@@
 ## Select a summary measure for valence and arousal separately
-
-- [ ] Ask Cameron whether it is OK to treat dimension contents as they are all classification studies (the exceptions are `av` and `valence` and `arousal`).
 
@@
 C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  arbitrary!
-C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')]<-548 
-C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')]<-548 
+C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')] <- 548 
+C_studies$feature_n[str_detect(C_studies$feature_n,'548 dimensions')] <- 548 
+C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')] <- 548 
 C_studies$feature_n[str_detect(C_studies$feature_n,'8; 3 after')]<-8 
@@
 
-C_studies$feature_n<-as.numeric(C_studies$feature_n)
+C_studies$feature_n <- as.numeric(C_studies$feature_n)
 

### 2024-07-12 R/parse-model-output.R
update summarize_matrix
add classification n

@@ -58,6 +58,7 @@ summarize_matrix = function(matrix) {
          names(confusion_summary)
     )
   )
+  confusion_summary$classification_class.n = ncol(class_table)
   
   return(confusion_summary)
 }

### 2024-07-12 analysis/analysis.qmd

@@
 library(meta)
-
-R_studies <- read.csv("R_studies.csv")
+library(DescTools)
+library(ggrepel)
+#R_studies <- read.csv("R_studies.csv")
 R_summary <- read.csv("R_summary.csv")
@@
 ```{r}
+#| eval: false
 outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")
@@
 
+add `journal_type` and `stimulus_genre_mixed` as a grouping option
+
 ```{r}
@@
        subgroup = model_class_id, 
+#       subgroup = journal_type, 
+#       subgroup = stimulus_genre_mixed, 
        tau.common = FALSE,
@@
 ```
+
+## Classification studies
+
+```{r}
+#| warning: false
+#| eval: true
+
+C_studies <- read.csv("C_studies.csv")
+C_studies <- C_studies[!is.na(C_studies$values),]
+
+C_summary <- read.csv("C_summary.csv")
+
+m.cor <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = C_summary,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 backtransf = TRUE,
+                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Classification: Summary")
+
+#print(m.cor)
+
+#m.cor_backtransformed <- m.cor
+#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
+print(funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE))
+
+```
+#### Custom plot
+
+```{r}
+library(ggrepel)
+tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
+
+tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
+tmpdata$citekey<-factor(tmpdata$citekey)
+
+g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
+  geom_point(show.legend = FALSE) +
+  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
+  ylab('Standard Error') + 
+  xlab('r')+
+  scale_y_reverse()+
+#  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
+#  coord_flip()+
+  theme_bw()
+print(g)
+```
+
+#### Visualise (forest and funnel plots)
+
+```{r}
+forest(m.cor,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "g", "SE"),studlab = citekey)
+
+funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+```
+
+#### Explore qualities (in progress)
+
+```{r}
+O <- find.outliers(m.cor)
+# 6 datasets identified as outliers, without them the r drops to 0.5781
+#infan <- InfluenceAnalysis(m.cor)
+#print(eggers.test(m.cor))
+
+```
+
+#### Re-run the analysis without the outliers
+
+```{r}
+#| eval: false
+outliers <- c("")
+
+tmp2<-tmp[!tmp$unique_id %in% outliers,]
+m.cor <- metacor(cor = values, 
+                 n = stimulus_n,
+                 studlab = unique_id, # unique_id
+                 data = tmp2,
+                 fixed = FALSE,
+                 random = TRUE,
+                 sm = "ZCOR",
+                 prediction = TRUE,
+                 backtransf = TRUE,
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+
+print(m.cor)
+
+fp <- funnel(m.cor, common = TRUE,studlab=FALSE)
+
+```
+
+#### Custom funnel plot
+
+To show the quality differences between core and eliminated studies (in progress).
+
+```{r}
+#| eval: false
+tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE)
+estimate = m.cor$TE.common
+se = m.cor$seTE.common
+se.seq=seq(0, max(m.cor$cor), 0.001)
+ll95 = estimate-(1.96*se.seq)
+ul95 = estimate+(1.96*se.seq)
+ll99 = estimate-(3.29*se.seq)
+ul99 = estimate+(3.29*se.seq)
+meanll95 = estimate-(1.96*se)
+meanul95 = estimate+(1.96*se)
+dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
+
+fp = ggplot(aes(x = SE, y = Zr), data = tmpdata) +
+  geom_point(shape = 1) +
+  xlab('Standard Error') + ylab('Zr')+
+  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
+  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
+   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
+  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
+#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
+#at the top of the figure once we swap the x- and y-axes...
+  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
+#Specify the range and interval for the tick-marks of the y-axis (Zr);
+#Choose values that work for you based on your data
+  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
+#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
+#And now we flip the axes so that SE is on y- and Zr is on x-
+  coord_flip()+
+#Finally, apply my APA-format theme (see code at end of post).
+#You could, alternatively, specify theme_bw() instead.
+  theme_bw()
+print(fp)
+```
+
+#### Subgroup analysis according to techniques
+
+add `journal_type` and `stimulus_genre_mixed` as a grouping option
+
+```{r}
+#| eval: false
+m.cor_subgroups <- update(m.cor, 
+       subgroup = model_class_id, 
+#       subgroup = journal_type, 
+#       subgroup = stimulus_genre_mixed, 
+       tau.common = FALSE,
+       prediction = TRUE)
+
+print(m.cor_subgroups)
+#forest(m.cor_subgroups,subgroup=TRUE)
+```
+
+- Idea: visualise the distributions of the model successes within studies (done in preprocessing)

### 2024-07-12 R/parse-model-output.R
update encodings; add class_n to confusion matrix processing

@@ -58,7 +58,8 @@ summarize_matrix = function(matrix) {
          names(confusion_summary)
     )
   )
-  confusion_summary$classification_class.n = ncol(class_table)
+  confusion_n <- c('classification_class.n' =  ncol(class_table))
+  confusion_summary <- append(confusion_summary, confusion_n)
   
   return(confusion_summary)
 }

### 2024-07-15 analysis/analysis.qmd
updates from our last working together in person

@@
                  n = stimulus_n,
-                 studlab = citekey, # unique_id
+                 studlab = studyREF, # unique_id
                  data = C_summary,

### 2024-07-15 analysis/preprocessing.qmd
updates from our last working together in person

@@
 ```
-## Check studies included
-
-```{r}
-#| eval: false
-included_in_summary <- R_summary$citekey[R_summary$dimension=='arousal']
-
-included_originally <- unique(metaMER_results$citekey[metaMER_results$model_category=='regression'])
-
-included_originally[!included_originally %in% included_in_summary]
-
-```
-
 ## Select a summary measure for valence and arousal separately
@@
 
-R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 50 #resolved
-#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
-#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
+R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 499 #resolved
+
+R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting = 21')] <- 21
+R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions')] <- 548
+R_studies$feature_n[str_detect(R_studies$feature_n,'548; after reduct')] <- 548
+R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and filter bank')] <- 3600
+R_studies$feature_n[str_detect(R_studies$feature_n,'Features deep-learned from audio (not specified) but 1802 in DEAM')] <- 260
+
+R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')] <- 3000 # under-estimation based openSmile features and the paper arguing that they have 15 stat moments
 
@@
                                                  as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
-                                                 1000),
-                                      labels = c("Feature n < 130","Feature n > 130 & < 653","Feature n > 653"))
+                                                 10000),
+                                      labels = c("Feature n < 236","Feature n > 236 & < 653","Feature n > 653"))
+
+R_studies$feature_n_complexity <- cut(R_studies$feature_n,
+                                      breaks = c(0,30,300,10000),
+                                      labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))
+
 table(R_studies$feature_n_complexity)
@@
 
-g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey))+
+g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey,shape=stimulus_genre_mixed))+
   stat_halfeye(aes(fill=citekey),point_interval="mean_qi", trim=FALSE, expand=FALSE, show.legend = FALSE,adjust = 1.25, density="bounded", point_size=3,scale = 1,alpha=0.5) + 
@@
   xlab("Model Technique")+
-#  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
+  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
   geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
@@
 print(no_of_classes)
+hist(no_of_classes$`first(values)`)
+
 rm(tmp,tmp2)
@@
 C_studies$stimulus_n[C_studies$stimulus_n==" total: 564; unambiguous: 416, circular validation: 39 "] <- 564 # 
+#table(C_studies$stimulus_n)
 C_studies$stimulus_n <- as.numeric(C_studies$stimulus_n)
@@
 
-print(quantile(C_studies$feature_n,c(0.333,0.666),na.rm = TRUE))
+ggplot(C_studies,aes(x=feature_n))+geom_histogram()
+
+#print(quantile(C_studies$feature_n,c(0.333,0.666),na.rm = TRUE))
 #quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)
@@
 C_studies$feature_n_complexity <- cut(C_studies$feature_n,
-                                      breaks = c(0,
-                                                 as.numeric(quantile(C_studies$feature_n,c(0.333),na.rm = TRUE)),
-                                                 as.numeric(quantile(C_studies$feature_n,c(0.666),na.rm = TRUE)),
-                                                 1000),
-                                      labels = c("Feature n < 119","Feature n > 119 & < 548","Feature n > 548"))
+                                      breaks = c(0,30,300,
+                                                 10000),
+                                      labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))
 table(C_studies$feature_n_complexity)

### 2024-07-15 manuscript/manuscript.qmd
updates from our last working together in person

--- 2024-07-11 manuscript/manuscript.qmd
@@
 
-We preregistered our meta-analysis plan on 21 June 2024 at OSF, [https://osf.io/c5wgd](https://osf.io/c5wgd), and the plan is also available at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).
+We preregistered the meta-analysis plan on 21 June 2024 at OSF, [https://osf.io/c5wgd](https://osf.io/c5wgd), and the plan is also available at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).
 
@@
 
-First we could describe the overall pattern of data (regression vs classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
+First we describe the overall pattern of data (regression vs classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
 
 TABLE 1: Summary of data (part of `analysis/preprocessing.qmd`)
+
+|            | Regression                   | Classification |
+|:-----------|:-----------------------------|:---------------|
+| Study N    | 24                           | 14             |
+| Model N    | 258                          | 108            |
+| Techniques | Flexible Discriminants: 64   | 37 |
+| Techniques | KS, Add. & KNN: 24           | 8 |
+| Techniques | Linear Methods: 74           | 24 |
+| Techniques | Neural Nets: 74              | 27 |
+| Techniques | Random Forests: 22           | 12 |
+| Feature N  | Min=3, Md=472.5, Max=654     | Min=3, Md=231, Max=8904 |
+| Stimulus N | Min=40, Md=324, Max=2486     |Min=124, Md=387, Max=5192 |
 
@@
 |:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
-| Valence All | 49,42480  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
-| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
-| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
-| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
-| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% | -0.0719; 0.9260
-| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% | 0.4470; 0.7396
+| Valence All |           | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
+| Valence Trim|           | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
+| Valence M   |           | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
+| Valence Md  |           | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
+| Valence Max | 24,15660  | 0.6585 [0.5574; 0.7404] | 7.44|.0001 | 0.142| 97.9% |
+| Val. MaxTrim|   13,7363 | 0.6489 [0.5980; 0.6945] | 18.5|.0001 | 0.008| 88.5% |
 | *N Features*|           |                         |     |      |      |       |
@@
 |:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
-| Arousal     | 55,43160   | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
-| Arousal Trim| 27,18402   | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
-| Arousal M   | 14,10641   | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
-| Arousal Md  | 14,10641   | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
-| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
-| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047
+| Arousal     |            | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
+| Arousal Trim|            | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
+| Arousal M   |            | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
+| Arousal Md  |            | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
+| Arousal Max | 24,15660   | 0.8070 [0.7453; 0.8550] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
+| Aro.Max.Trm | 14,12061   | 0.8182 [0.8021; 0.8331] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047
 
@@
 Table 4. Meta-analytic diagnostic for all classification studies predicting emotion categories from audio.
+
+| Model       | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
+|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
+| All         | 89,87347   | 0.8074 [0.7681; 0.8407] |21.4 |0.0001|0.2415|99.7%  |
+| All Trim    | 29,6499    | 0.8185 [0.8046; 0.8314] | 58.3|0.0001|0.0066| 60.4%  |
+| Max         | 14,17184   | 0.8564 [0.7386; 0.9234] | 8.32|0.0001|0.329 | 99.8% |
+| Max Trim    | 6,3653     | 0.8689 [0.7760; 0.9249] | 11.6|0.0001|0.0749| 97.5% |
 

### 2024-07-15 manuscript/manuscript.qmd
updated MS

@@
 
-| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$| Prediction interval
-|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
+| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$|
+|:------------|:----------|:------------------------|:----|:-----|:-----|:------|
 | Valence All |           | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
@@
 | Arousal Md  |            | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
-| Arousal Max | 24,15660   | 0.8070 [0.7453; 0.8550] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
-| Aro.Max.Trm | 14,12061   | 0.8182 [0.8021; 0.8331] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047
-
+| Arousal Max | 24,15660   | 0.8070 [0.7453; 0.8550] | 10.3|0.0001|0.155 | 96.8% | 
+| Aro.Max.Trm | 14,12061   | 0.8182 [0.8021; 0.8331] | 25.6|0.0001|0.0132| 96.8% | 
 | *N Features*|            |          |              |     |      |      |       |   

### 2024-09-15 manuscript/manuscript.qmd
add flowchart to methods

--- 2024-07-12 manuscript/manuscript.qmd
@@
 -   Numerous studies over the last 25 years have established what emotions listeners perceive and recognise in music [@gomez2021].
-In the last 15 years, it has become possible to trace the recognised emotions to musical contents such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013;@anderson2022ex;@grimaud_eerola_2022], or acoustic features [@yang2008;@panda2013multi;@saari_et_al_2015;@eerola2011c] or emergent properties identified through deep learning [@er2019music;@sarkar2020recognition].
+In the last 15 years, it has become possible to trace the recognised emotions to musical contents such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013; @anderson2022ex; @grimaud_eerola_2022], or acoustic features [@yang2008; @panda2013multi; @saari_et_al_2015; @eerola2011c] or emergent properties identified through deep learning [@er2019music; @sarkar2020recognition].
 
@@
 
-We preregistered our meta-analysis plan on 21 June 2024 at OSF, [https://osf.io/c5wgd](https://osf.io/c5wgd), and the plan is also available at [https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html)).
+We preregistered the meta-analysis plan on 21 June 2024 at OSF, <https://osf.io/c5wgd>, and the plan is also available at <https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html>).
 
-In the search stage, we used three databases, _Web of Science_, _Scopus_, and _Open Alex_ to identify journal articles published between 2014 and 2024 containing keywords/title `valence OR arousal OR classi OR categor OR algorithm AND music
- AND emotion AND recognition` (see specific search strings for each database in [SI](http://)). All searches were done in May 2024.
+In the search stage, we used three databases, *Web of Science*, *Scopus*, and *Open Alex* to identify journal articles published between 2014 and 2024 containing keywords/title `valence OR arousal OR classi* OR categor* OR algorithm AND music AND emotion AND recognition` (see specific search strings for each database in [SI](http://)).
+All searches were done in May 2024.
 
-The initial search yielded 553 potential studies, which were interactively screened for relevance in three stages by both authors, resulting in 46 studies that passed our inclusion criteria (define here: has included some form of emotion modelling with a set of features, and outcome measures such as $R^2$ or classification accuracy ($F1$ score or _precision_ or _recall_) and overall quality control; see [SI](http://) for a breakdown).
-After the screening stage, we define a set of entities to extract characterising music (genre, stimulus number [N], duration), features extracted (number, type, source, defined by [@panda2020audio]), model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, _MSE_, _MCC_), model complexity (???
+The initial search yielded 553 potential studies, which were interactively screened for relevance in three stages by both authors, resulting in 46 studies that passed our inclusion criteria (define here: has included some form of emotion modelling with a set of features, and outcome measures such as $R^2$ or classification accuracy ($F1$ score or *precision* or *recall*) and overall quality control; see [SI](http://) for a breakdown).
+After the screening stage, we define a set of entities to extract characterising music (genre, stimulus number \[N\], duration), features extracted (number, type, source, defined by [@panda2020audio]), model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), model complexity (???
 model architecture?), and type of model cross-validation.
-We converted all regression results into $R^2$ values for valence and arousal and classification results into Matthews correlation coefficient [_MCC_, @chicco2020advantages].
+We converted all regression results into $R^2$ values for valence and arousal and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].
 
-[optional Figure: flowchart of the study inclusions/eliminations]
+\[Figure 1: flowchart of the study inclusions/eliminations\]
+
+```{r echo=FALSE}
+library(glue)
+library(DiagrammeR)
+
+a_label <- glue('Records identified from:
+                Web of Science (n = 142)
+                Scopus (n = 227)
+                OpenALEX (n = 278)')
+b_label <- glue('Records removed before screening: 
+                Duplicates entries/errors (n = 94)')
+e_label <- glue('Records removed: 
+                Irrelevant titles/themes (n = 338)
+                Abstract screening (n = 95)
+                Discussion (n = 24)')
+h_label <- glue('Full text articles excluded
+             (n = 50)')
+grViz("
+digraph cohort_flow_chart
+{
+node [fontname = Helvetica, fontsize = 12, shape = box, width = 4]
+a[label = '@@1']
+b[label = '@@2']
+c[label = 'Records after duplicates removed (n = 553)']
+d[label = 'Records screened (n = 553)']
+e[label = '@@3']
+f[label = 'Full text articles assessed (n = 96)']
+g[label = 'Studies included (n = 46)']
+h[label = '@@4']
+
+{ rank = same; a b}
+{ rank = same; d, e}
+{ rank = same; f, h}
+
+a -> b;
+a -> c;
+c -> d;
+d -> e [ minlen = 3 ];
+d -> f;
+f -> h [ minlen = 3 ];
+f -> g;
+}
+
+[1]: a_label
+[2]: b_label
+[3]: e_label
+[4]: h_label
+
+")
+```
 
@@
 
-First we could describe the overall pattern of data (regression vs classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
+First we describe the overall pattern of data (regression vs classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
 
 TABLE 1: Summary of data (part of `analysis/preprocessing.qmd`)
+
+|            | Regression                 | Classification            |
+|:-----------|:---------------------------|:--------------------------|
+| Study N    | 24                         | 14                        |
+| Model N    | 258                        | 108                       |
+| Techniques | Flexible Discriminants: 64 | 37                        |
+| Techniques | KS, Add. & KNN: 24         | 8                         |
+| Techniques | Linear Methods: 74         | 24                        |
+| Techniques | Neural Nets: 74            | 27                        |
+| Techniques | Random Forests: 22         | 12                        |
+| Feature N  | Min=3, Md=472.5, Max=654   | Min=3, Md=231, Max=8904   |
+| Stimulus N | Min=40, Md=324, Max=2486   | Min=124, Md=387, Max=5192 |
 
@@
 -   Decision: Report all models or the best model?
-  * Possible solution: Report all models, trimmed models, and but mainly rely on Max
+
+    -   Possible solution: Report all models, trimmed models, and but mainly rely on Max
 
@@
 
-| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$| Prediction interval
-|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
-| Valence All | 49,42480  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
-| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
-| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
-| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
-| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% | -0.0719; 0.9260
-| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% | 0.4470; 0.7396
-| *N Features*|           |                         |     |      |      |       |
-| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
-| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
-| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
-| *Techniques*|           |                         |     |      |      |       |
-|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
-|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
-|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
-|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
-|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
+| Concept      | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$   | $\tau^2$ | $I^2$ |
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+| Valence All  |             | 0.6137 \[0.5540; 0.6672\] | 15.9 | .0001 | 0.092    | 98.1% |
+| Valence Trim |             | 0.6048 \[0.5920; 0.6172\] | 72.4 | .0001 | 0.0007   | 33.1% |
+| Valence M    |             | 0.6038 \[0.4671; 0.7124\] | 7.83 | .0001 | 0.100    | 97.8% |
+| Valence Md   |             | 0.6018 \[0.4659; 0.7099\] | 7.87 | .0001 | 0.098    | 97.7% |
+| Valence Max  | 24,15660    | 0.6585 \[0.5574; 0.7404\] | 7.44 | .0001 | 0.142    | 97.9% |
+| Val. MaxTrim | 13,7363     | 0.6489 \[0.5980; 0.6945\] | 18.5 | .0001 | 0.008    | 88.5% |
+| *N Features* |             |                           |      |       |          |       |
+| \<18 F       |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| 18-260 F     |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| 260+ F       |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| *Techniques* |             |                           |      |       |          |       |
+| KS           |             | 0.3606 \[0.3201; 0.3997\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| LM           |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| FD           |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| NN           |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| RF           |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
 
@@
 
-see this to ignore I^2 and rely on prediction interval: 
-https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678
+see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678
 
-Figure 1. Forest plot of valence prediction (Max?)
-`analysis/figure1.qmd`
+Figure 1. Forest plot of valence prediction (Max?) `analysis/figure1.qmd`
 
@@
 
-| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
-|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
-| Arousal     | 55,43160   | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
-| Arousal Trim| 27,18402   | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
-| Arousal M   | 14,10641   | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
-| Arousal Md  | 14,10641   | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
-| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
-| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047
-
-| *N Features*|            |          |              |     |      |      |       |   
-| <18 F       |            |          |              |     |      |      |       |
-| 18-260 F    |            |          |              |     |      |      |       |
-| 260+ F      |            |          |              |     |      |      |       |
-| *Techniques*|            |          |              |     |      |      |       |  
-|   KS        |            |          |              |     |      |      |       |
-|   LM        |            |          |              |     |      |      |       |
-|   FD        |            |          |              |     |      |      |       |
-|   NN        |            |          |              |     |      |      |       |
-|   RF        |            |          |              |     |      |      |       |
+| Concept      | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+| Arousal      |             | 0.7959 \[0.7666; 0.8218\] | 29.0 | 0.0001 | 0.0676   | 95.6% |
+| Arousal Trim |             | 0.7932 \[0.7846; 0.8014\] | 96.5 | 0.0001 | 0.0030   | 73.3% |
+| Arousal M    |             | 0.7567 \[0.6752; 0.8199\] | 12.7 | 0.0001 | 0.0739   | 95.6% |
+| Arousal Md   |             | 0.7627 \[0.6819; 0.8252\] | 12.7 | 0.0001 | 0.0757   | 95.3% |
+| Arousal Max  | 24,15660    | 0.8070 \[0.7453; 0.8550\] | 10.3 | 0.0001 | 0.155    | 96.8% |
+| Aro.Max.Trm  | 14,12061    | 0.8182 \[0.8021; 0.8331\] | 25.6 | 0.0001 | 0.0132   | 96.8% |
+| *N Features* |             |                           |      |        |          |       |
+| \<18 F       |             |                           |      |        |          |       |
+| 18-260 F     |             |                           |      |        |          |       |
+| 260+ F       |             |                           |      |        |          |       |
+| *Techniques* |             |                           |      |        |          |       |
+| KS           |             |                           |      |        |          |       |
+| LM           |             |                           |      |        |          |       |
+| FD           |             |                           |      |        |          |       |
+| NN           |             |                           |      |        |          |       |
+| RF           |             |                           |      |        |          |       |
 
@@
 
-| Model       | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
-|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
-| All         | 89,87347   | 0.8074 [0.7681; 0.8407] |21.4 |0.0001|0.2415|99.7%  |
-| All Trim    | 29,6499    | 0.8185 [0.8046; 0.8314] | 58.3|0.0001|0.0066| 60.4%  |
-| Max         | 14,17184   | 0.8564 [0.7386; 0.9234] | 10.3|0.0001|0.329 | 99.8% |
-| Max Trim    | 6,3653     | 0.8689 [0.7760; 0.9249] | 11.6|0.0001|0.0749| 97.5% |
+| Model    | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+| All      | 89,87347    | 0.8074 \[0.7681; 0.8407\] | 21.4 | 0.0001 | 0.2415   | 99.7% |
+| All Trim | 29,6499     | 0.8185 \[0.8046; 0.8314\] | 58.3 | 0.0001 | 0.0066   | 60.4% |
+| Max      | 14,17184    | 0.8564 \[0.7386; 0.9234\] | 8.32 | 0.0001 | 0.329    | 99.8% |
+| Max Trim | 6,3653      | 0.8689 \[0.7760; 0.9249\] | 11.6 | 0.0001 | 0.0749   | 97.5% |
 
@@
 ## Main outcomes
+
 -   Arousal is easier to predict (r = 0.7627) than valence (r = 0.6236), as we predicted. The glass ceiling seems to be at ...
@@
 ## Calls for action/points to improve in such studies
+
 -   *Documentation* the details in full (features, stimuli, model details, cross-validation)
@@
 
-Study preregistration, data, analysis scripts and supporting information is available at Github, [https://tuomaseerola.github.io/metaMER](https://tuomaseerola.github.io/metaMER).
+Study preregistration, data, analysis scripts and supporting information is available at Github, <https://tuomaseerola.github.io/metaMER>.
 

### 2024-09-20 manuscript/manuscript.qmd
update methods
add additional detail to method, including quality control subsection

@@
 
-The initial search yielded 553 potential studies, which were interactively screened for relevance in three stages by both authors, resulting in 46 studies that passed our inclusion criteria (define here: has included some form of emotion modelling with a set of features, and outcome measures such as $R^2$ or classification accuracy ($F1$ score or *precision* or *recall*) and overall quality control; see [SI](http://) for a breakdown).
-After the screening stage, we define a set of entities to extract characterising music (genre, stimulus number \[N\], duration), features extracted (number, type, source, defined by [@panda2020audio]), model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), model complexity (???
-model architecture?), and type of model cross-validation.
+The initial search yielded 553 potential studies after excluding duplicate entries.
+We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $R^2$ or $MCC$ values see [SI](http://) for a breakdown).
+After the screening stage, we defined a set of entities to extract characterising (i) music (genre, stimulus number \[N\], duration), (ii) features extracted (number, type, source, defined by [@panda2020audio]), (iii) model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), (iv) model complexity (i.e., approximate number of features used to predict ratings), and (v) type of model cross-validation.
 We converted all regression results into $R^2$ values for valence and arousal and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].
@@
 
--   Devote some sentences to quality control issues (what were the most common reasons for eliminating studies).
+## Quality Control
+
+The search yielded studies of variable (and occasionally questionable) quality.
+To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](include approx # for each?).
+Additionally, we excluded results comprising algorithms trained on image features such as spectrograms (affecting two studies, one of which was eliminated).Finally, we excluded one study published in two journals of questionable relevance to MER.
+This includes *Mathematical Problems in Engineering* which ceased publication following a large number of retractions in September 2024.
 

### 2024-09-25 analysis/analysis.qmd
small edits to analysis

@@
 ### Valence: Best model
+
+For creating Table 2
 
@@
 
-#sqrt(tmp$values) # convert from R^2 to r
-#tmp$stimulus_n <- 100 # ad-hoc for now
-
 m.cor <- metacor(cor = valuesMax,     # values 
@@
                  prediction = TRUE,
-                 backtransf = TRUE,
-                 sm = "ZCOR",
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
                  method.tau = "REML",# could be PM (Paule-Mandel) as well
@@
 
-m.cor_backtransformed <- m.cor
-m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
+print(FisherZInv(m.cor$TE.random))
+print(FisherZInv(m.cor$upper.random))
+print(FisherZInv(m.cor$lower.random))
+
+#m.cor_backtransformed <- m.cor
+#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
+#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
 
 ```
+
+sub-division based on journals (engineering vs psych)
+
+```{r}
+m.cor2 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  journal_type,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+```
+
 #### Custom plot
@@
 #| eval: false
+#| echo: false
 outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")
@@
 
-To show the quality differences between core and eliminated studies (in progress).
+To show the quality differences between core and eliminated studies.
 
 ```{r}
-tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE)
+tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)
+
+tmpdata$studyREF <- substr(tmpdata$studies,1,nchar(tmpdata$studies)-2)
+tmpdata$studyREF <- str_replace_all(tmpdata$studyREF,'([0-9]+)',' et al \\1')
+tmpdata$studyREF <- str_to_sentence(tmpdata$studyREF)
+tmpdata$studyREF
+
 estimate = m.cor$TE.common
@@
 
-fp = ggplot(aes(x = SE, y = Zr), data = tmpdata) +
-  geom_point(shape = 1) +
-  xlab('Standard Error') + ylab('Zr')+
+fp = ggplot(NULL) +
+  geom_point(aes(x = SE, y = Zr), color='grey50',data=tmpdata) +
+  geom_text_repel(aes(x = SE, y = Zr, label=studyREF), data=tmpdata,size=2.5,max.overlaps = 40)+
+  xlab('Standard Error') + ylab('Fisher\'s z transformed correlation')+
   geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
@@
   geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-#at the top of the figure once we swap the x- and y-axes...
-  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
-#Specify the range and interval for the tick-marks of the y-axis (Zr);
-#Choose values that work for you based on your data
-  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
-#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
-#And now we flip the axes so that SE is on y- and Zr is on x-
+#  scale_x_reverse()+
+  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
+  scale_y_continuous(breaks=seq(0.3,1.25,0.20),limits=c(0.3,1.23))+
   coord_flip()+
-#Finally, apply my APA-format theme (see code at end of post).
-#You could, alternatively, specify theme_bw() instead.
   theme_bw()
@@
 #| eval: false
+#| echo: false
 outliers <- c("")
@@
 ```{r}
-#| eval: false
-tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE)
+#| eval: true
+tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)
+
+tmpdata$studyREF <- substr(tmpdata$studies,1,nchar(tmpdata$studies)-2)
+tmpdata$studyREF <- str_replace_all(tmpdata$studyREF,'([0-9]+)',' et al \\1')
+tmpdata$studyREF <- str_to_sentence(tmpdata$studyREF)
+tmpdata$studyREF
+
 estimate = m.cor$TE.common
@@
   geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-#at the top of the figure once we swap the x- and y-axes...
-  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
-#Specify the range and interval for the tick-marks of the y-axis (Zr);
-#Choose values that work for you based on your data
-  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
-#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
-#And now we flip the axes so that SE is on y- and Zr is on x-
+#  scale_x_reverse()+
+  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
+  scale_y_continuous(breaks=seq(0.3,1.25,0.20),limits=c(0.3,1.23))+
   coord_flip()+
-#Finally, apply my APA-format theme (see code at end of post).
-#You could, alternatively, specify theme_bw() instead.
   theme_bw()
 print(fp)
+
 ```

### 2024-09-25 analysis/preprocessing.qmd
small edits to analysis

@@
 
+Note: Before adding feature_n to the summary, they need to be cleaned!
+
 ```{r}
@@
 
-R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),journal_type=first(journal_type),stimulus_genre_mixed=first(stimulus_genre_mixed))
+R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),stimulus_genre_mixed=first(stimulus_genre_mixed))
 
@@
 
-Ratio of obs./features or just a classification based on feature n (quintiles).
+Ratio of obs./features or just a classification based on feature n (quantiles).
 

### 2024-09-25 manuscript/manuscript.qmd
summary text written before the actual analysis

@@
 The search yielded studies of variable (and occasionally questionable) quality.
-To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](include approx # for each?).
+To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](include approx # for each?
+This would be good since the rest of this para already mentions counts.
+If this take a long time, we could save this for an additional analysis).
 Additionally, we excluded results comprising algorithms trained on image features such as spectrograms (affecting two studies, one of which was eliminated).Finally, we excluded one study published in two journals of questionable relevance to MER.
@@
 
-|            | Regression                 | Classification            |
-|:-----------|:---------------------------|:--------------------------|
-| Study N    | 24                         | 14                        |
-| Model N    | 258                        | 108                       |
-| Techniques | Flexible Discriminants: 64 | 37                        |
-| Techniques | KS, Add. & KNN: 24         | 8                         |
-| Techniques | Linear Methods: 74         | 24                        |
-| Techniques | Neural Nets: 74            | 27                        |
-| Techniques | Random Forests: 22         | 12                        |
-| Feature N  | Min=3, Md=472.5, Max=654   | Min=3, Md=231, Max=8904   |
-| Stimulus N | Min=40, Md=324, Max=2486   | Min=124, Md=387, Max=5192 |
+|            | Regression                 | Classification            |Total|
+|:-----------|:---------------------------|:--------------------------|:----|
+| Study N    | 24                         | 14                        | 38  |
+| Model N    | 258                        | 108                       | 366 |
+| Techniques | Flexible Discriminants: 64 | 37                        | 101 |
+| Techniques | Neural Nets: 74            | 27                        | 101 |
+| Techniques | Linear Methods: 74         | 24                        | 98  |
+| Techniques | Random Forests: 22         | 12                        | 34  |
+| Techniques | KS, Add. & KNN: 24         | 8                         | 32  |
+| Feature N  | Min=3, Md=472.5, Max=654   | Min=3, Md=231, Max=8904   | NA  |
+| Stimulus N | Min=40, Md=324, Max=2486   | Min=124, Md=387, Max=5192 | NA  |
 
-Talk about the stimuli and
+Although the total number of studies meeting the criteria described in the previous section is modest (38 in total), they encompass a large array of models (366 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
+The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 9000 features [@zhang2023mo].
+The median number of features differs between regression (473) and classification (231) studies, primarily reflecting the nature of the datasets used in each approach.
+The number of stimuli is typically around 300-400 (with a median of 324 for regression and 387 for classification), though there is substantial variation, with the extremes from 40 stimuli in @saizclar2022pr to 5192 stimuli in @alvarez2023ri.
+There are also additional dimensions to consider, such as the type of cross-validation used, the music genres analyzed (whether a single genre, multiple genres, or a mix), the type of journal in which the studies were published, and the source of the extracted features.
+However, these variables do not lend themselves to a simple summary, so we will revisit them during the interpretation and discussion stages.
+[COMMENT: IT MIGHT BE WORTWHILE TO SUMMARISE SOME OF THESE HERE].
 
@@
 -   Decision: Report all models or the best model?
-
     -   Possible solution: Report all models, trimmed models, and but mainly rely on Max
-
 -   Report issues of heterogeneity right here (can be visualised with funnel plots, see below)
-
 -   Optional Figure X: Funnel plot that combines valence and arousal (separate panels) with FULL/TRIMMED data shown with markers"
@@
 | Concept      | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$   | $\tau^2$ | $I^2$ |
-|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+|:-------------|:------------|:--------------------------|:-----|:------|:---------|:------|
 | Valence All  |             | 0.6137 \[0.5540; 0.6672\] | 15.9 | .0001 | 0.092    | 98.1% |

### 2024-09-25 manuscript/manuscript.qmd
Start of results

@@
              (n = 50)')
-grViz("
+fig1 <- DiagrammeR::grViz("
 digraph cohort_flow_chart
@@
 ")
+
+# Does not print this, but could this be done directly with dot syntax?
+# see https://quarto.org/docs/authoring/diagrams.html
+
 ```
@@
 
--   Decision: Report all models or the best model?
-    -   Possible solution: Report all models, trimmed models, and but mainly rely on Max
--   Report issues of heterogeneity right here (can be visualised with funnel plots, see below)
--   Optional Figure X: Funnel plot that combines valence and arousal (separate panels) with FULL/TRIMMED data shown with markers"
+Since there are many models contained within the studies, we will report the results in a two parts; We first give an overview of the results for all models, and then we focus on the best performing models of each study.
+The focus on best performing model is carried out by taking the model with the highest correlation coefficient and using this model for the study.
+This is done to avoid the issue of multiple models from the same study deflating the results as majority of the models included are relative modest baseline models and alternative techniques that do not represent the novelty and content of the article.
+Table 2 summarises the results for all models (All) as well as best performing models (Max) for each study.
+The summary includes the number of models and observations, the correlation coefficient and its 95% confidence interval, the t-value and p-value for the correlation, the heterogeneity statistics $\tau^2$ and $I^2$, calculated through appropriate transformations (Fisher's Z) for the correlation coefficient, and a random-effects model using `meta` library [@balduzzi2019].
 
@@
 |:-------------|:------------|:--------------------------|:-----|:------|:---------|:------|
-| Valence All  |             | 0.6137 \[0.5540; 0.6672\] | 15.9 | .0001 | 0.092    | 98.1% |
-| Valence Trim |             | 0.6048 \[0.5920; 0.6172\] | 72.4 | .0001 | 0.0007   | 33.1% |
-| Valence M    |             | 0.6038 \[0.4671; 0.7124\] | 7.83 | .0001 | 0.100    | 97.8% |
-| Valence Md   |             | 0.6018 \[0.4659; 0.7099\] | 7.87 | .0001 | 0.098    | 97.7% |
-| Valence Max  | 24,15660    | 0.6585 \[0.5574; 0.7404\] | 7.44 | .0001 | 0.142    | 97.9% |
-| Val. MaxTrim | 13,7363     | 0.6489 \[0.5980; 0.6945\] | 18.5 | .0001 | 0.008    | 88.5% |
+| Valence All  |             | 0.614 \[0.554; 0.667\] | 15.9 | .0001 | 0.092    | 98.1% |
+| Valence Trim |             | 0.605 \[0.592; 0.617\] | 72.4 | .0001 | 0.0007   | 33.1% |
+| Valence M    |             | 0.604 \[0.467; 0.712\] | 7.83 | .0001 | 0.100    | 97.8% |
+| Valence Md   |             | 0.602 \[0.466; 0.710\] | 7.87 | .0001 | 0.098    | 97.7% |
+| Valence Max  | 24,15660    | 0.659 \[0.557; 0.740\] | 7.44 | .0001 | 0.142    | 97.9% |
+| Val. MaxTrim | 13,7363     | 0.649 \[0.598; 0.695\] | 18.5 | .0001 | 0.008    | 88.5% |
 | *N Features* |             |                           |      |       |          |       |

### 2024-09-25 manuscript/manuscript.qmd
Start of results

@@
 
-Since there are many models contained within the studies, we will report the results in a two parts; We first give an overview of the results for all models, and then we focus on the best performing models of each study.
-The focus on best performing model is carried out by taking the model with the highest correlation coefficient and using this model for the study.
-This is done to avoid the issue of multiple models from the same study deflating the results as majority of the models included are relative modest baseline models and alternative techniques that do not represent the novelty and content of the article.
+Since there are many models contained within each of the studies, we will report the results in two parts; We first give an overview of the results for all models, and then we focus on the best performing models of each study.
+The best performing model is the model within each study with the highest correlation coefficient.
+This reduction is done to avoid the issue of multiple models from the same study deflating the results as majority of the models included are relative modest baseline or alternative models that do not represent the novelty or content of the article.
 Table 2 summarises the results for all models (All) as well as best performing models (Max) for each study.
-The summary includes the number of models and observations, the correlation coefficient and its 95% confidence interval, the t-value and p-value for the correlation, the heterogeneity statistics $\tau^2$ and $I^2$, calculated through appropriate transformations (Fisher's Z) for the correlation coefficient, and a random-effects model using `meta` library [@balduzzi2019].
+The summary includes the number of models and observations, the correlation coefficient and its 95% confidence interval, the t-value and p-value for the correlation, the heterogeneity statistics $\tau^2$ and $I^2$, calculated through appropriate transformations (Fisher's Z) for the correlation coefficient as part of a random-effects model using `meta` library [@balduzzi2019].
 

### 2024-09-25 analysis/analysis.qmd
Updated Table 2 and Figure 2

@@
 library(ggrepel)
+```
+
+#### Using all models
+
+```{r}
+R_studies <- read.csv("R_studies.csv")
+#R_summary <- read.csv("R_summary.csv")
+
+# select regression studies with r2
+#tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp <- dplyr::filter(R_studies,dimension=="valence")
+#dim(tmp)
+
+#if all studies, remove two with NA values
+tmp <- tmp[!is.na(tmp$values),]
+#dim(tmp)
+
+# Take all models
+m.cor <- metacor(cor = values,     # values 
+                 n = stimulus_n,
+                 studlab = unique_id,
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+
+print(m.cor)
+
+print(FisherZInv(m.cor$TE.random))
+print(FisherZInv(m.cor$upper.random))
+print(FisherZInv(m.cor$lower.random))
+
+#m.cor_backtransformed <- m.cor
+#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
+#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
+
+```
+
+#### Using the best model out of each study
+
+```{r}
 #R_studies <- read.csv("R_studies.csv")
@@
 
+## Disambiguate the studies
+tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
+
+# Max values
 m.cor <- metacor(cor = valuesMax,     # values 
                  n = stimulus_n,
-                 studlab = citekey, # unique_id
+                 studlab = studyREF,#citekey, # unique_id
                  data = tmp,
@@
 
-#print(m.cor)
+print(m.cor)
 
@@
 
-sub-division based on journals (engineering vs psych)
+### Sub-division based on techniques
+
+```{r}
+m.cor1 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  model_class_id,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor1)
+
+S<-summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
+print(S)
+```
+
+### Sub-division based on journals (engineering vs psych)
 
@@
 
-#### Custom plot
+### Sub-division based on N features
 
 ```{r}
-tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
+dim(tmp)
+m.cor3 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  feature_n_categories,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor3)
+S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+print(S)
 
-tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
-tmpdata$citekey<-factor(tmpdata$citekey)
-
-g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
-  geom_point(show.legend = FALSE) +
-  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
-  ylab('Standard Error') + 
-  xlab('r')+
-  scale_y_reverse()+
-  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
-#  coord_flip()+
-  theme_bw()
-print(g)
 ```
@@
              print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"),studlab = citekey)
+             leftlabs = c("Author", "g", "SE"),studlab = studyREF)
 
-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+#funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
 
@@
 print(eggers.test(m.cor))
-
 ```
@@
 ```{r}
-tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)
-
-tmpdata$studyREF <- substr(tmpdata$studies,1,nchar(tmpdata$studies)-2)
-tmpdata$studyREF <- str_replace_all(tmpdata$studyREF,'([0-9]+)',' et al \\1')
-tmpdata$studyREF <- str_to_sentence(tmpdata$studyREF)
-tmpdata$studyREF
+tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
+#tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)
 
@@
   geom_point(aes(x = SE, y = Zr), color='grey50',data=tmpdata) +
-  geom_text_repel(aes(x = SE, y = Zr, label=studyREF), data=tmpdata,size=2.5,max.overlaps = 40)+
-  xlab('Standard Error') + ylab('Fisher\'s z transformed correlation')+
+  geom_text_repel(aes(x = SE, y = Zr, label=studies), data=tmpdata,size=2.5,max.overlaps = 40)+
+  xlab('Standard Error') + ylab('Correlation')+
   geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
   geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
-  geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-#  scale_x_reverse()+
+  geom_hline(yintercept = estimate, linetype='solid', color='grey50',linewidth=0.2) +
   scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
-  scale_y_continuous(breaks=seq(0.3,1.25,0.20),limits=c(0.3,1.23))+
+  scale_y_continuous(breaks=seq(0.0,1.00,0.20),limits=c(0.0,1.00),expand=c(0.00,0.00))+
   coord_flip()+

### 2024-09-25 analysis/preprocessing.qmd
Updated Table 2 and Figure 2

@@
 
+#### Clean feature N field
+
+```{r}
+
+R_studies$feature_n[R_studies$feature_n==" 548; after reduction, 139 for PCA and 276 for ReliefF   "] <- 548
+
+R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting')] <- 21
+R_studies$feature_n[str_detect(R_studies$feature_n,'but 15 reported')]<-15
+R_studies$feature_n[str_detect(R_studies$feature_n,'50 PCA features')]<-50
+R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions. Pos')]<-548
+R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and')]<-60 # this should be 14400+60!
+R_studies$feature_n[str_detect(R_studies$feature_n,'before_selection = 45')]<-45
+R_studies$feature_n[str_detect(R_studies$feature_n,'model 4 = 388')]<-388
+R_studies$feature_n[str_detect(R_studies$feature_n,'6670 in MediaEval')]<-6670
+R_studies$feature_n[str_detect(R_studies$feature_n,'557 before feature')]<-557
+R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')]<-NA
+R_studies$feature_n<-as.numeric(R_studies$feature_n)
+
+quantile(R_studies$feature_n,c(0.333,0.666),na.rm = TRUE)
+quantile(R_studies$feature_n,c(0.25,0.500,0.750),na.rm = TRUE)
+quantile(R_studies$feature_n,c(0.1,0.500,0.90),na.rm = TRUE)
+
+R_studies$feature_n_categories <-cut(R_studies$feature_n,
+                                      breaks = c(0,18,260,
+                                                 10000),
+                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
+
+```
+
 ## Diagnostics
@@
 
-R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),stimulus_genre_mixed=first(stimulus_genre_mixed))
+R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed))
 

### 2024-09-25 manuscript/_figure1.qmd
Updated Table 2 and Figure 2

--- 2024-07-15 analysis/analysis.qmd
@@
-# Analysis
+```{r}
+#| label: fig1
+#| fig.height: 7
+#| echo: false
+#| fig.cap: > 
+#|   Forest plot of valence predictions from the MER models.
 
-This assumes that the data has been parsed (`parse-model-output.R`, `format-study-results.R`) and preprocessed (`processing.qmd`).
+library(metafor)
+library(dmetar)
+library(meta)
 
-## Regression studies
+R_summary <- read.csv("../analysis/R_summary.csv")
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
 
-### Valence: Best model
-
-```{r}
-#| warning: false
-#| eval: true
-library(dmetar)
-library(tidyverse)
-library(meta)
-library(DescTools)
-library(ggrepel)
-#R_studies <- read.csv("R_studies.csv")
-R_summary <- read.csv("R_summary.csv")
-
-# select regression studies with r2
-tmp <- dplyr::filter(R_summary,dimension=="valence")
-#tmp <- dplyr::filter(R_studies,dimension=="valence")
-#dim(tmp)
-
-#if all studies, remove two
-#tmp <- tmp[!is.na(tmp$values),]
-#dim(tmp)
-
-#sqrt(tmp$values) # convert from R^2 to r
-#tmp$stimulus_n <- 100 # ad-hoc for now
-
+# Max values
 m.cor <- metacor(cor = valuesMax,     # values 
                  n = stimulus_n,
-                 studlab = citekey, # unique_id
+                 studlab = studyREF,#citekey, # unique_id
                  data = tmp,
@@
                  prediction = TRUE,
-                 backtransf = TRUE,
-                 sm = "ZCOR",
+                 #                 backtransf = TRUE,
+                 #                 sm = "ZCOR",
                  method.tau = "REML",# could be PM (Paule-Mandel) as well
@@
 
-#print(m.cor)
-
-m.cor_backtransformed <- m.cor
-m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
+forest(m.cor,
+       sortvar = TE,
+       fontfamily = "Times",
+       hetstat =FALSE,
+       prediction = FALSE, 
+       print.tau2 = FALSE,
+       leftlabs = c("Author", "g", "SE"),layout = "meta",addrows =0,rows.gr=0,col.diamond='black') # RevMan5
 
 ```
-#### Custom plot
-
-```{r}
-tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
-
-tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
-tmpdata$citekey<-factor(tmpdata$citekey)
-
-g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
-  geom_point(show.legend = FALSE) +
-  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
-  ylab('Standard Error') + 
-  xlab('r')+
-  scale_y_reverse()+
-  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
-#  coord_flip()+
-  theme_bw()
-print(g)
-```
-
-#### Visualise (forest and funnel plots)
-
-```{r}
-forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"),studlab = citekey)
-
-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
-
-```
-
-#### Explore qualities (in progress)
-
-```{r}
-O <- find.outliers(m.cor)
-# 6 datasets identified as outliers, without them the r drops to 0.5781
-infan <- InfluenceAnalysis(m.cor)
-print(eggers.test(m.cor))
-
-```
-
-#### Re-run the analysis without the outliers
-
-```{r}
-#| eval: false
-outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")
-
-tmp2<-tmp[!tmp$unique_id %in% outliers,]
-m.cor <- metacor(cor = values, 
-                 n = stimulus_n,
-                 studlab = unique_id, # unique_id
-                 data = tmp2,
-                 fixed = FALSE,
-                 random = TRUE,
-                 sm = "ZCOR",
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-
-print(m.cor)
-
-fp <- funnel(m.cor, common = TRUE,studlab=FALSE)
-
-```
-
-#### Custom funnel plot
-
-To show the quality differences between core and eliminated studies (in progress).
-
-```{r}
-tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE)
-estimate = m.cor$TE.common
-se = m.cor$seTE.common
-se.seq=seq(0, max(m.cor$cor), 0.001)
-ll95 = estimate-(1.96*se.seq)
-ul95 = estimate+(1.96*se.seq)
-ll99 = estimate-(3.29*se.seq)
-ul99 = estimate+(3.29*se.seq)
-meanll95 = estimate-(1.96*se)
-meanul95 = estimate+(1.96*se)
-dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
-
-fp = ggplot(aes(x = SE, y = Zr), data = tmpdata) +
-  geom_point(shape = 1) +
-  xlab('Standard Error') + ylab('Zr')+
-  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
-  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
-   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-#at the top of the figure once we swap the x- and y-axes...
-  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
-#Specify the range and interval for the tick-marks of the y-axis (Zr);
-#Choose values that work for you based on your data
-  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
-#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
-#And now we flip the axes so that SE is on y- and Zr is on x-
-  coord_flip()+
-#Finally, apply my APA-format theme (see code at end of post).
-#You could, alternatively, specify theme_bw() instead.
-  theme_bw()
-print(fp)
-```
-
-#### Subgroup analysis according to techniques
-
-add `journal_type` and `stimulus_genre_mixed` as a grouping option
-
-```{r}
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-#       subgroup = journal_type, 
-#       subgroup = stimulus_genre_mixed, 
-       tau.common = FALSE,
-       prediction = TRUE)
-
-print(m.cor_subgroups)
-#forest(m.cor_subgroups,subgroup=TRUE)
-```
-
-- Idea: visualise the distributions of the model successes within studies (done in preprocessing)
-
-### Arousal: Best model
-
-```{r}
-#| warning: false
-#| eval: true
-
-# select regression studies with r2
-tmp <- dplyr::filter(R_summary,dimension=="arousal")
-#tmp <- dplyr::filter(R_studies,dimension=="arousal")
-dim(tmp)
-#tmp <- tmp[!is.na(tmp$values),]
-dim(tmp)
-#tmp<-drop_na(tmp)
-
-m.cor <- metacor(cor = valuesMax, 
-                 n = stimulus_n,
-                 studlab = citekey,
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Arousal: Summary")
-
-print(m.cor)
-```
-### Trimmed analysis
-```{r}
-O <- find.outliers(m.cor)
-```
-
-#### Visualise (forest and funnel plots)
-
-```{r}
-forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"))
-plot(eggers.test(m.cor))
-```
-
-#### Explore qualities (in progress)
-
-```{r}
-#| eval: false
-meta <- metagen(valuesMax, sqrt(valuesMax), 
-                data = tmp, 
-                studlab = tmp$citekey, 
-                comb.fixed = FALSE, 
-                method.tau = "PM")
-find.outliers(meta)
-infan <- InfluenceAnalysis(meta)
-print(eggers.test(meta))
-
-```
-
-#### Subgroup analysis according to techniques
-
-```{r}
-update(m.cor, 
-       subgroup = model_class_id, 
-       tau.common = FALSE)
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-       tau.common = FALSE)
-
-forest(m.cor_subgroups,subgroup=TRUE)
-```
-
-- Idea: visualise the distributions of the model successes within studies (done in preprocessing)
-
-```{r}
-#| eval: false
-g1 <- ggplot(tmp,aes(y=valuesMax,fill=model_class_id))+
-   geom_histogram(show.legend = T)+
-  facet_wrap(.~studyREF)+
-   coord_flip()+
-   theme_bw()
-g1
-
-# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
-# g<-ggplot(S,aes(y=maxvalue))+
-#   geom_histogram(bins = 14)+
-#   #facet_wrap(.~studyREF)+
-#   coord_flip()+
-#   theme_bw()
-# g
-```
-
-## Classification studies
-
-```{r}
-#| warning: false
-#| eval: true
-
-C_studies <- read.csv("C_studies.csv")
-C_studies <- C_studies[!is.na(C_studies$values),]
-
-C_summary <- read.csv("C_summary.csv")
-
-m.cor <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = studyREF, # unique_id
-                 data = C_summary,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Classification: Summary")
-
-#print(m.cor)
-
-#m.cor_backtransformed <- m.cor
-#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-print(funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE))
-
-```
-#### Custom plot
-
-```{r}
-library(ggrepel)
-tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
-
-tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
-tmpdata$citekey<-factor(tmpdata$citekey)
-
-g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
-  geom_point(show.legend = FALSE) +
-  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
-  ylab('Standard Error') + 
-  xlab('r')+
-  scale_y_reverse()+
-#  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
-#  coord_flip()+
-  theme_bw()
-print(g)
-```
-
-#### Visualise (forest and funnel plots)
-
-```{r}
-forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"),studlab = citekey)
-
-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
-
-```
-
-#### Explore qualities (in progress)
-
-```{r}
-O <- find.outliers(m.cor)
-# 6 datasets identified as outliers, without them the r drops to 0.5781
-#infan <- InfluenceAnalysis(m.cor)
-#print(eggers.test(m.cor))
-
-```
-
-#### Re-run the analysis without the outliers
-
-```{r}
-#| eval: false
-outliers <- c("")
-
-tmp2<-tmp[!tmp$unique_id %in% outliers,]
-m.cor <- metacor(cor = values, 
-                 n = stimulus_n,
-                 studlab = unique_id, # unique_id
-                 data = tmp2,
-                 fixed = FALSE,
-                 random = TRUE,
-                 sm = "ZCOR",
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-
-print(m.cor)
-
-fp <- funnel(m.cor, common = TRUE,studlab=FALSE)
-
-```
-
-#### Custom funnel plot
-
-To show the quality differences between core and eliminated studies (in progress).
-
-```{r}
-#| eval: false
-tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE)
-estimate = m.cor$TE.common
-se = m.cor$seTE.common
-se.seq=seq(0, max(m.cor$cor), 0.001)
-ll95 = estimate-(1.96*se.seq)
-ul95 = estimate+(1.96*se.seq)
-ll99 = estimate-(3.29*se.seq)
-ul99 = estimate+(3.29*se.seq)
-meanll95 = estimate-(1.96*se)
-meanul95 = estimate+(1.96*se)
-dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
-
-fp = ggplot(aes(x = SE, y = Zr), data = tmpdata) +
-  geom_point(shape = 1) +
-  xlab('Standard Error') + ylab('Zr')+
-  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
-  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
-   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
-#at the top of the figure once we swap the x- and y-axes...
-  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
-#Specify the range and interval for the tick-marks of the y-axis (Zr);
-#Choose values that work for you based on your data
-  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
-#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
-#And now we flip the axes so that SE is on y- and Zr is on x-
-  coord_flip()+
-#Finally, apply my APA-format theme (see code at end of post).
-#You could, alternatively, specify theme_bw() instead.
-  theme_bw()
-print(fp)
-```
-
-#### Subgroup analysis according to techniques
-
-add `journal_type` and `stimulus_genre_mixed` as a grouping option
-
-```{r}
-#| eval: false
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-#       subgroup = journal_type, 
-#       subgroup = stimulus_genre_mixed, 
-       tau.common = FALSE,
-       prediction = TRUE)
-
-print(m.cor_subgroups)
-#forest(m.cor_subgroups,subgroup=TRUE)
-```
-
-- Idea: visualise the distributions of the model successes within studies (done in preprocessing)

### 2024-09-25 manuscript/manuscript.qmd
Updated Table 2 and Figure 2

@@
 | Concept      | Models, obs | $r$ \[95%-CI\]         | $t$  | $p$   | $\tau^2$ | $I^2$ |
-|:-------------|:------------|:--------------------------|:-----|:------|:---------|:------|
-| Valence All  |             | 0.614 \[0.554; 0.667\] | 15.9 | .0001 | 0.092    | 98.1% |
-| Valence Trim |             | 0.605 \[0.592; 0.617\] | 72.4 | .0001 | 0.0007   | 33.1% |
-| Valence M    |             | 0.604 \[0.467; 0.712\] | 7.83 | .0001 | 0.100    | 97.8% |
-| Valence Md   |             | 0.602 \[0.466; 0.710\] | 7.87 | .0001 | 0.098    | 97.7% |
-| Valence Max  | 24,15660    | 0.659 \[0.557; 0.740\] | 7.44 | .0001 | 0.142    | 97.9% |
-| Val. MaxTrim | 13,7363     | 0.649 \[0.598; 0.695\] | 18.5 | .0001 | 0.008    | 88.5% |
+|:-------------|:------------|:-----------------------|:-----|:------|:---------|:------|
+| Valence All  |  120,73685  | 0.567 \[0.530; 0.603\] | 23.7 | .0001 | 0.083    | 97.5% |
+| Valence Max  | 24,15660    | 0.659 \[0.557; 0.740\] | 10.14| .0001 | 0.138    | 98.2% |
 | *N Features* |             |                        |      |       |          |       |
-| \<18 F       |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
-| 18-260 F     |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
-| 260+ F       |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| \<18 F       |  5,3036     | 0.811 \[0.566; 0.775\] | -    | -     | 0.182    | 98.9% |
+| 18-260 F     |  11,7318    | 0.548 \[0.343; 0.703\] | -    | -     | 0.133    | 97.6% |
+| 260+ F       |  7,4562     | 0.685 \[0.566; 0.775\] | -    | -     | 0.044    | 97.2% |
 | *Techniques* |             |                        |      |       |          |       |
-| KS           |             | 0.3606 \[0.3201; 0.3997\] | xxxx | .xxxx | 0.xxx    | XXXX% |
-| LM           |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
-| FD           |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
-| NN           |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
-| RF           |             | 0.xxxx \[0.xxxx; 0.xxxx\] | xxxx | .xxxx | 0.xxx    | XXXX% |
+| KS           |  2,2582     | 0.466 \[-0.634; 0.942\]| -    | -     | 0.0185   | 95.1% |
+| LM           |  8,1762     | 0.784 \[0.625; 0.881\] | -    | -     | 0.1370   | 96.4% |
+| FD           |  6,4993     | 0.656 \[0.484; 0.779\] | -    | -     | 0.0574   | 96.9% |
+| NN           |  4,2249     | 0.340 \[-0.097; 0.668\]| -    | -     | 0.0761   | 97.1% |
+| RF           |  4,4074     | 0.702 \[0.391; 0.869\] | -    | -     | 0.057    | 98.5% |
 
-OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION,
+<!-- | Val. MaxTrim | 13,7363     | 0.649 \[0.598; 0.695\] | 18.5 | .0001 | 0.008    | 88.5% | -->
+<!-- | Valence Trim |             | 0.605 \[0.592; 0.617\] | 72.4 | .0001 | 0.0007   | 33.1% | -->
+<!-- | Valence M    |             | 0.604 \[0.467; 0.712\] | 7.83 | .0001 | 0.100    | 97.8% | -->
+<!-- | Valence Md   |             | 0.602 \[0.466; 0.710\] | 7.87 | .0001 | 0.098    | 97.7% | -->
 
-see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678
+- [OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION](to explore?)
 
-Figure 1. Forest plot of valence prediction (Max?) `analysis/figure1.qmd`
+<!-- see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678 -->
+
+{{< include _figure1.qmd >}}
 
@@
 | Arousal      |             | 0.7959 \[0.7666; 0.8218\] | 29.0 | 0.0001 | 0.0676   | 95.6% |
-| Arousal Trim |             | 0.7932 \[0.7846; 0.8014\] | 96.5 | 0.0001 | 0.0030   | 73.3% |
-| Arousal M    |             | 0.7567 \[0.6752; 0.8199\] | 12.7 | 0.0001 | 0.0739   | 95.6% |
-| Arousal Md   |             | 0.7627 \[0.6819; 0.8252\] | 12.7 | 0.0001 | 0.0757   | 95.3% |
 | Arousal Max  | 24,15660    | 0.8070 \[0.7453; 0.8550\] | 10.3 | 0.0001 | 0.155    | 96.8% |
-| Aro.Max.Trm  | 14,12061    | 0.8182 \[0.8021; 0.8331\] | 25.6 | 0.0001 | 0.0132   | 96.8% |
 | *N Features* |             |                           |      |        |          |       |
@@
 
+<!-- | Arousal Trim |             | 0.7932 \[0.7846; 0.8014\] | 96.5 | 0.0001 | 0.0030   | 73.3% | -->
+<!-- | Arousal M    |             | 0.7567 \[0.6752; 0.8199\] | 12.7 | 0.0001 | 0.0739   | 95.6% | -->
+<!-- | Arousal Md   |             | 0.7627 \[0.6819; 0.8252\] | 12.7 | 0.0001 | 0.0757   | 95.3% | -->
+<!-- | Aro.Max.Trm  | 14,12061    | 0.8182 \[0.8021; 0.8331\] | 25.6 | 0.0001 | 0.0132   | 96.8% | -->
+
 Summarise here the pattern of results
@@
 | All      | 89,87347    | 0.8074 \[0.7681; 0.8407\] | 21.4 | 0.0001 | 0.2415   | 99.7% |
-| All Trim | 29,6499     | 0.8185 \[0.8046; 0.8314\] | 58.3 | 0.0001 | 0.0066   | 60.4% |
 | Max      | 14,17184    | 0.8564 \[0.7386; 0.9234\] | 8.32 | 0.0001 | 0.329    | 99.8% |
-| Max Trim | 6,3653      | 0.8689 \[0.7760; 0.9249\] | 11.6 | 0.0001 | 0.0749   | 97.5% |
+
+<!-- | All Trim | 29,6499     | 0.8185 \[0.8046; 0.8314\] | 58.3 | 0.0001 | 0.0066   | 60.4% | -->
+<!-- | Max Trim | 6,3653      | 0.8689 \[0.7760; 0.9249\] | 11.6 | 0.0001 | 0.0749   | 97.5% | -->
 

### 2024-10-01 manuscript/manuscript.qmd
docs(manuscript): update cohort flowchart
Use Graphviz syntax for flow chart

@@
 
-```{r echo=FALSE}
-library(glue)
-library(DiagrammeR)
+```{dot}
 
-a_label <- glue('Records identified from:
+digraph sub {
+  node [fontname = Helvetica, fontsize = 14, shape = box, width = 4]
+  A [label = "Records identified from:
                 Web of Science (n = 142)
                 Scopus (n = 227)
-                OpenALEX (n = 278)')
-b_label <- glue('Records removed before screening: 
-                Duplicates entries/errors (n = 94)')
-e_label <- glue('Records removed: 
+                OpenALEX (n = 278)" ]
+  B [label = "Records removed before screening: 
+                Duplicates entries/errors (n = 94)" ]
+  C [label = "Records after duplicates removed (n = 553)"]
+  D [label = "Records screened (n = 553)"]
+  E [label = "Records removed: 
                 Irrelevant titles/themes (n = 338)
                 Abstract screening (n = 95)
-                Discussion (n = 24)')
-h_label <- glue('Full text articles excluded
-             (n = 50)')
-fig1 <- DiagrammeR::grViz("
-digraph cohort_flow_chart
-{
-node [fontname = Helvetica, fontsize = 12, shape = box, width = 4]
-a[label = '@@1']
-b[label = '@@2']
-c[label = 'Records after duplicates removed (n = 553)']
-d[label = 'Records screened (n = 553)']
-e[label = '@@3']
-f[label = 'Full text articles assessed (n = 96)']
-g[label = 'Studies included (n = 46)']
-h[label = '@@4']
+                Discussion (n = 24)"]
+  F [label = "Full text articles assessed (n = 96)"]
+  G [label = "Studies included in final review (n = 46)"]
+  H [label = "Full text articles excluded
+             (n = 50)"]
+  I [label = "Studies excluded in final review (n = 8)"]
+  J [label = "Final selection (n = 38)"]
+  A->B
+  A->C
+  C->D
+  D->E [ minlen = 3 ]
+  D->F
+  F->H [ minlen = 3 ]
+  F->G
+  G->I
+  G->J
 
-{ rank = same; a b}
-{ rank = same; d, e}
-{ rank = same; f, h}
-
-a -> b;
-a -> c;
-c -> d;
-d -> e [ minlen = 3 ];
-d -> f;
-f -> h [ minlen = 3 ];
-f -> g;
+  { rank = same; A B}
+  { rank = same; D, E}
+  { rank = same; F, H}
+  { rank = same; G, I}
 }
-
-[1]: a_label
-[2]: b_label
-[3]: e_label
-[4]: h_label
-
-")
-
-# Does not print this, but could this be done directly with dot syntax?
-# see https://quarto.org/docs/authoring/diagrams.html
 
@@
 The search yielded studies of variable (and occasionally questionable) quality.
-To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](include approx # for each?
-This would be good since the rest of this para already mentions counts.
-If this take a long time, we could save this for an additional analysis).
+To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](include%20approx%20#%20for%20each?%20This%20would%20be%20good%20since%20the%20rest%20of%20this%20para%20already%20mentions%20counts.%20If%20this%20take%20a%20long%20time,%20we%20could%20save%20this%20for%20an%20additional%20analysis).
 Additionally, we excluded results comprising algorithms trained on image features such as spectrograms (affecting two studies, one of which was eliminated).Finally, we excluded one study published in two journals of questionable relevance to MER.
@@
 
-|            | Regression                 | Classification            |Total|
-|:-----------|:---------------------------|:--------------------------|:----|
+|            | Regression                 | Classification            | Total |
+|:-----------|:---------------------------|:--------------------------|:------|
 | Study N    | 24                         | 14                        | 38    |
@@
 However, these variables do not lend themselves to a simple summary, so we will revisit them during the interpretation and discussion stages.
-[COMMENT: IT MIGHT BE WORTWHILE TO SUMMARISE SOME OF THESE HERE].
+\[COMMENT: IT MIGHT BE WORTWHILE TO SUMMARISE SOME OF THESE HERE\].
 
@@
 | Concept      | Models, obs | $r$ \[95%-CI\]          | $t$   | $p$   | $\tau^2$ | $I^2$ |
-|:-------------|:------------|:-----------------------|:-----|:------|:---------|:------|
+|:---------|:---------|:------------|:---------|:---------|:---------|:---------|
 | Valence All  | 120,73685   | 0.567 \[0.530; 0.603\]  | 23.7  | .0001 | 0.083    | 97.5% |
-| Valence Max  | 24,15660    | 0.659 \[0.557; 0.740\] | 10.14| .0001 | 0.138    | 98.2% |
+| Valence Max  | 24,15660    | 0.659 \[0.557; 0.740\]  | 10.14 | .0001 | 0.138    | 98.2% |
 | *N Features* |             |                         |       |       |          |       |
-| \<18 F       |  5,3036     | 0.811 \[0.566; 0.775\] | -    | -     | 0.182    | 98.9% |
-| 18-260 F     |  11,7318    | 0.548 \[0.343; 0.703\] | -    | -     | 0.133    | 97.6% |
-| 260+ F       |  7,4562     | 0.685 \[0.566; 0.775\] | -    | -     | 0.044    | 97.2% |
+| \<18 F       | 5,3036      | 0.811 \[0.566; 0.775\]  | \-    | \-    | 0.182    | 98.9% |
+| 18-260 F     | 11,7318     | 0.548 \[0.343; 0.703\]  | \-    | \-    | 0.133    | 97.6% |
+| 260+ F       | 7,4562      | 0.685 \[0.566; 0.775\]  | \-    | \-    | 0.044    | 97.2% |
 | *Techniques* |             |                         |       |       |          |       |
-| KS           |  2,2582     | 0.466 \[-0.634; 0.942\]| -    | -     | 0.0185   | 95.1% |
-| LM           |  8,1762     | 0.784 \[0.625; 0.881\] | -    | -     | 0.1370   | 96.4% |
-| FD           |  6,4993     | 0.656 \[0.484; 0.779\] | -    | -     | 0.0574   | 96.9% |
-| NN           |  4,2249     | 0.340 \[-0.097; 0.668\]| -    | -     | 0.0761   | 97.1% |
-| RF           |  4,4074     | 0.702 \[0.391; 0.869\] | -    | -     | 0.057    | 98.5% |
+| KS           | 2,2582      | 0.466 \[-0.634; 0.942\] | \-    | \-    | 0.0185   | 95.1% |
+| LM           | 8,1762      | 0.784 \[0.625; 0.881\]  | \-    | \-    | 0.1370   | 96.4% |
+| FD           | 6,4993      | 0.656 \[0.484; 0.779\]  | \-    | \-    | 0.0574   | 96.9% |
+| NN           | 4,2249      | 0.340 \[-0.097; 0.668\] | \-    | \-    | 0.0761   | 97.1% |
+| RF           | 4,4074      | 0.702 \[0.391; 0.869\]  | \-    | \-    | 0.057    | 98.5% |
 
 <!-- | Val. MaxTrim | 13,7363     | 0.649 \[0.598; 0.695\] | 18.5 | .0001 | 0.008    | 88.5% | -->
+
 <!-- | Valence Trim |             | 0.605 \[0.592; 0.617\] | 72.4 | .0001 | 0.0007   | 33.1% | -->
+
 <!-- | Valence M    |             | 0.604 \[0.467; 0.712\] | 7.83 | .0001 | 0.100    | 97.8% | -->
+
 <!-- | Valence Md   |             | 0.602 \[0.466; 0.710\] | 7.87 | .0001 | 0.098    | 97.7% | -->
 
-- [OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION](to explore?)
+-   [OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION](to%20explore?)
 
@@
 <!-- | Arousal Trim |             | 0.7932 \[0.7846; 0.8014\] | 96.5 | 0.0001 | 0.0030   | 73.3% | -->
+
 <!-- | Arousal M    |             | 0.7567 \[0.6752; 0.8199\] | 12.7 | 0.0001 | 0.0739   | 95.6% | -->
+
 <!-- | Arousal Md   |             | 0.7627 \[0.6819; 0.8252\] | 12.7 | 0.0001 | 0.0757   | 95.3% | -->
+
 <!-- | Aro.Max.Trm  | 14,12061    | 0.8182 \[0.8021; 0.8331\] | 25.6 | 0.0001 | 0.0132   | 96.8% | -->
@@
 | Model | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
-|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+|:------|:------------|:--------------------------|:-----|:-------|:---------|:------|
 | All   | 89,87347    | 0.8074 \[0.7681; 0.8407\] | 21.4 | 0.0001 | 0.2415   | 99.7% |
@@
 <!-- | All Trim | 29,6499     | 0.8185 \[0.8046; 0.8314\] | 58.3 | 0.0001 | 0.0066   | 60.4% | -->
+
 <!-- | Max Trim | 6,3653      | 0.8689 \[0.7760; 0.9249\] | 11.6 | 0.0001 | 0.0749   | 97.5% | -->

### 2024-10-01 manuscript/manuscript.qmd
docs(manuscript): correct graphViz figure

@@
              (n = 50)"]
-  I [label = "Studies excluded in final review (n = 8)"]
-  J [label = "Final selection (n = 38)"]
+  I [label = "Studies excluded in final review (n = 9)"]
+  J [label = "Final selection (n = 37)"]
   A->B
@@
   C->D
-  D->E [ minlen = 3 ]
+  D->E
   D->F
-  F->H [ minlen = 3 ]
+  F->H 
   F->G
@@
 | Concept      | Models, obs | $r$ \[95%-CI\]          | $t$   | $p$   | $\tau^2$ | $I^2$ |
-|:---------|:---------|:------------|:---------|:---------|:---------|:---------|
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
 | Valence All  | 120,73685   | 0.567 \[0.530; 0.603\]  | 23.7  | .0001 | 0.083    | 97.5% |

### 2024-10-04 studies/library_formatter.qmd
fix(site): fix links in qmd files
correct cross-referencing in library-parser, pass 3 comparison, and search syntax

@@
 # read in bibtex library as data frame
-bib_df_ca <- bib2df::bib2df('metaMER_library_third_pass_ca.bib')
-bib_df_te <- bib2df::bib2df('metaMER_library_third_pass_te.bib')
+bib_df_ca <- bib2df::bib2df(paste0(here::here(),
+                                   "/studies/bib/Passes/", 
+                                   "metaMER_library_third_pass_ca.bib")
+)
+bib_df_te <- bib2df::bib2df(paste0(here::here(),
+                                   "/studies/bib/Passes/", 
+                                   "metaMER_library_third_pass_te.bib")
+)
 bib_df_ca <- dplyr::filter(bib_df_ca,PRIORITY=='prio1')

### 2024-10-04 studies/library_parser.qmd
fix(site): fix links in qmd files
correct cross-referencing in library-parser, pass 3 comparison, and search syntax

--- 2024-06-17 studies/library_parser.qmd
@@
 ```{r}
+source(paste0(here::here(), "/R/format-study-results.R"))
 eval(parse(text = meta_df$model_rate_emotion_values[22]))
@@
 
+```{r eval = F, echo = F}
+
 # Outdated: Dealing with nested bibtex fields.
 
-Some studies include multiple bibtex fields for substudies/evaluations of different feature sets.
-E.g., `MODEL_RATE_EMOTION_VALUES_A` and `MODEL_RATE_EMOTION_VALUES_B`.
-We need to apply special operations to separate these values for further analysis.
+# Some studies include multiple bibtex fields for 
+# substudies/evaluations of different feature sets. E.g., 
+# `MODEL_RATE_EMOTION_VALUES_A` and `MODEL_RATE_EMOTION_VALUES_B`. 
+# We need to apply special operations to separate these values for 
+# further analysis.
 
-```{r eval = F, echo = F}
 ## function to parse output of multiple models nested within a single cell
@@
   valence_mse.mean = 0.3, arousal_mse.mean = 9.1),
-  'random forest.mfcc.deam.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5))",
+  'essentia.random forest.mfcc.deam.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5))",
   "rbind('librosa.linear regression.mfcc.ismir.1' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3, valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
@@
 ```{r}
-dplyr::tibble(get_study_summaries(this_study))
+dplyr::tibble(get_study_summaries(this_study)) |>
+  knitr::kable()
 ```

### 2024-10-04 studies/search_syntax.qmd
fix(site): fix links in qmd files
correct cross-referencing in library-parser, pass 3 comparison, and search syntax

@@
 #### Read first pass data ---------------------
-d <- bib2df("../studies/metaMER_library_first_pass_year_fixed.bib")
+d <- bib2df::bib2df(paste0(here::here(),
+                                   "/studies/bib/Passes/", 
+                                   "metaMER_library_first_pass.bib")
+)
 # Remove extra fields

### 2024-10-04 manuscript/manuscript.qmd
docs(manuscript): update methods

@@
 After the screening stage, we defined a set of entities to extract characterising (i) music (genre, stimulus number \[N\], duration), (ii) features extracted (number, type, source, defined by [@panda2020audio]), (iii) model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), (iv) model complexity (i.e., approximate number of features used to predict ratings), and (v) type of model cross-validation.
+
 We converted all regression results into $R^2$ values for valence and arousal and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].
+To increase consistency in our analyses, we excluded studies using incompatible features (e.g., spectrograms of audio files [@nag2022]), or dependent variables (e.g., one regression study analyzed valence and arousal together, but not separately [@chin2018]).
 
@@
              (n = 50)"]
-  I [label = "Studies excluded in final review (n = 9)"]
-  J [label = "Final selection (n = 37)"]
+  I [label = "Studies excluded in final review (n = 10)"]
+  J [label = "Final selection (n = 36)"]
   A->B
@@
 To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](include%20approx%20#%20for%20each?%20This%20would%20be%20good%20since%20the%20rest%20of%20this%20para%20already%20mentions%20counts.%20If%20this%20take%20a%20long%20time,%20we%20could%20save%20this%20for%20an%20additional%20analysis).
-Additionally, we excluded results comprising algorithms trained on image features such as spectrograms (affecting two studies, one of which was eliminated).Finally, we excluded one study published in two journals of questionable relevance to MER.
-This includes *Mathematical Problems in Engineering* which ceased publication following a large number of retractions in September 2024.
+Finally, we excluded studies published in journals of questionable relevance/quality, (e.g., *Mathematical Problems in Engineering* ceased publication following 17 retractions published between July and September 2024).
+
+## Study Encoding
+
+To capture key details of each study, we added additional fields to BibTeX entries for each study.
+Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type, validation procedure and output measures.
+Additionally, we included study results using executable *R* code containing custom functions for meta-analysis.
+For complete details about our encoding procedure, see `studies/extraction_details.qmd` .
 

### 2024-10-07 manuscript/manuscript.qmd
feat: add intro subsection, correct one model encoded in studies/bib/extractions
update to introduction subsections and corresponding references, along with a correction to name of one model in zhang2017fe

@@
 
-bibliography      : ["references.bib"]
+#bibliography      : ["references.bib"]
 
@@
 output            : papaja::apa6_pdf
+bibliography: references.bib
 ---
@@
 However, there is no consensus on to what degree emotions can be recognised by computational models and the literature to date paints a diverse picture of success for concepts in affective circumplex -- valence and arousal-- [@Russell1980] and classifying various emotion categories [@fu2010survey].
+
+# A brief history of MER
+
+Emotion has been widely discussed since the earliest artificial intelligence (AI) applications to music in the 1950s.
+Whereas early discourse largely focused on generative composition using computers [@zaripov1969], attention later shifted to creating methods to predict emotion using music's structural cues.
+Novel techniques for information retrieval emerged in the 1950s and 1960s [@fairthorne1968], inspiring analogous developments for automated music analysis (@kassler1966toward; @mendel1969some).
+These developments would set the stage for early work in music emotion recognition (MER).
+Katayose et al.
+(1988) conducted the first study of this nature, creating an algorithm that associated emotions with analyzed chords to generate descriptions like "there is hopeful mood on chord from 69 to 97 \[*sic*\]." [@katayose_sentiment_1988, p.
+1087].
+
+In the early 2000s, several research groups conducted studies using regression [@friberg_automatic_2002; @liu_automatic_2003] and classification [@lu_automatic_2005; @feng_popular_2003; @mandel_support_2006] techniques to predict emotion in music audio or MIDI.
+Citing "MIR researchers' growing interest in classifying music by moods" [@downie_music_2008, p.
+1], the Music Information Retrieval EXchange (MIREX) introduced Audio Mood Classification (AMC) to their rotation of tasks in 2007.
+In the first year, nine systems classified mood labels in a common data set, reaching 52.65% accuracy (SD = 11.19%).
+These events, along with growing interest in the burgeoning field of affective computing, would lead to an explosion of interest in MER research.[^1]
+
+[^1]: The best-performing model to date reached 69.83 % in the 2017 competition (Park et al., 2017)[\@park2017representation](https://scholar.google.com/scholar?q=Representation%20learning%20using%20artist%20labels%20for%20audio%20classification%20tasks%2C%20Park).
+
+Researchers have assessed regression and classification techniques on diverse corpora with features drawn from music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
+In one widely-cited study, Yang (2008) approached MER as a regression task, predicting the valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) of 195 Chinese pop songs, achieving 62% accuracy for arousal but only 28% for valence [@yang2008].
+This difference in prediction accuracy between dimensions has reappeared in several subsequent studies [e.g., @bai2016dimensional; @coutinho2013psychoacoustic], with some research suggesting this challenge reflects fewer well-established predictors and more individual differences for valence than arousal [@yang2007music].
+
+# The semantic gap in MER
+
+The difficulty in predicting valence reflects a broader challenge in information retrieval.
+Specifically, relations between low-level predictors from music and text and the perceptual phenomena they model remain poorly understood, reaching a ceiling in prediction accuracy [@celma_foafing_2006].
+To address this so-called *semantic gap*, researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang_bridge_2016].
+Through these approaches, MER researchers attempt to shatter a so-called *glass ceiling* [@downie_music_2008] by establishing strong emotion predictors.
+To date, however, no study has systematically compared results of these diverse approaches.
 
@@
 | Concept      | Models, obs | $r$ \[95%-CI\]          | $t$   | $p$   | $\tau^2$ | $I^2$ |
-|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+|:-------------|:------------|:------------------------|:------|:------|:---------|:------|
 | Valence All  | 120,73685   | 0.567 \[0.530; 0.603\]  | 23.7  | .0001 | 0.083    | 97.5% |
@@
 
--   [OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION](to%20explore?)
+-   OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION
 
@@
 | Concept      | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
-|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+|:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
 | Arousal      |             | 0.7959 \[0.7666; 0.8218\] | 29.0 | 0.0001 | 0.0676   | 95.6% |

### 2024-10-07 etc/identifying_duplicate_measurements.R

@@ -1,0 +1,52 @@
+## This script works after running preprocessing.qmd
+
+
+# some models have multiple summary measures. This script makes identifying them easier ----------------------
+
+# Find studies where models are summarized by multiple measures
+R_studies |> group_by(unique_id, dimension) |> dplyr::summarize(
+  measure_n = length(unique(measure)),
+  summary_stat_n = length(unique(statistic))
+  ) -> r_summary_measures
+
+C_studies |> group_by(unique_id, dimension) |> dplyr::summarize(
+  measure_n = length(unique(measure)),
+  summary_stat_n = length(unique(statistic))
+) -> c_summary_measures
+
+nrow(r_summary_measures[r_summary_measures$summary_stat_n == 1,])
+nrow(c_summary_measures[c_summary_measures$summary_stat_n == 1,])
+
+r_summary_measures[r_summary_measures$measure_n > 1,]
+r_summary_measures[r_summary_measures$summary_stat_n > 1,]
+
+
+R_studies[stringr::str_detect(R_studies$unique_id, 
+                     c('gingras2014be|wang2022co|coutinho2017')),] |> 
+  dplyr::select(unique_id, dimension, measure, statistic, values) -> R_multiple
+
+
+
+
+
+
+
+c_summary_measures[c_summary_measures$measure_n > 1,]
+c_summary_measures[c_summary_measures$summary_stat_n > 1,]
+
+
+C_studies[stringr::str_detect(C_studies$unique_id, c('zhang2016br|zhang2017fe')),] |> 
+  dplyr::select(unique_id, dimension, measure, statistic, values) -> C_multiple
+print(C_multiple, n = nrow(C_multiple))
+
+print(C_multiple)
+print(R_multiple)
+
+
+# After omitting NAs ------------------------------------------------------
+
+
+na.omit(C_multiple)
+na.omit(R_multiple)
+
+

### 2024-10-10 analysis/analysis.qmd
reporting valence results (text)

@@
 #                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.tau = "PM",# was REML, but we switch to Paule-Mandel because Langan et al., 2019
                  method.random.ci = "HK", 

### 2024-10-10 manuscript/manuscript.qmd
reporting valence results (text)

@@
 
--   Emotional expression is one of the central reasons why people engage with music.
+Emotional engagement is one of the central reasons why people engage with music in their every day activities and why music is being implicated in various health applications [@juslin2022emotions;@agres2021music].
+Significant advances in music information retrieval relating to music emotion recognition (MER) tasks have been made in recent years [@gomez2021;@panda2020audio].
+The available features, modelling techniques and datasets have given the field opportunities to refine the accuracy and reliability of predicting annotated emotions from audio.
+Numerous studies over the last 25 years have established what emotions listeners perceive and recognise in music.
+In the last 15 years, it has become possible to trace the recognised emotions to musical contents such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013; @anderson2022ex; @grimaud_eerola_2022], or acoustic features [@yang2008; @panda2013multi; @saari_et_al_2015; @eerola2011c; @panda2020audio] or emergent properties identified through deep learning [@er2019music; @sarkar2020recognition].
 
--   Great advances in music information retrieval have been made in recent years.
-The available features, modelling techniques and datasets have given scholars opportunities to refine the accuracy and reliability of predicting annotated emotions from audio.
-
--   Numerous studies over the last 25 years have established what emotions listeners perceive and recognise in music [@gomez2021].
-In the last 15 years, it has become possible to trace the recognised emotions to musical contents such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013; @anderson2022ex; @grimaud_eerola_2022], or acoustic features [@yang2008; @panda2013multi; @saari_et_al_2015; @eerola2011c] or emergent properties identified through deep learning [@er2019music; @sarkar2020recognition].
-
-However, there is no consensus on to what degree emotions can be recognised by computational models and the literature to date paints a diverse picture of success for concepts in affective circumplex -- valence and arousal-- [@Russell1980] and classifying various emotion categories [@fu2010survey].
+However, there is no consensus on to what degree emotions can be recognised by computational models, and the literature to date paints a diverse picture of success for concepts in affective circumplex -- valence and arousal-- [@Russell1980] and classifying various emotion categories [@fu2010survey].
 
@@
 In one widely-cited study, Yang (2008) approached MER as a regression task, predicting the valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) of 195 Chinese pop songs, achieving 62% accuracy for arousal but only 28% for valence [@yang2008].
-This difference in prediction accuracy between dimensions has reappeared in several subsequent studies [e.g., @bai2016dimensional; @coutinho2013psychoacoustic], with some research suggesting this challenge reflects fewer well-established predictors and more individual differences for valence than arousal [@yang2007music].
+This difference in prediction accuracy between dimensions has reappeared in several subsequent studies [e.g., @bai2016dimensional; @coutinho2013psychoacoustic], with some research suggesting this challenge reflects fewer well-established predictors and more individual differences for valence than arousal [@yang2007music; @eerola2011c].
 
@@
 To address this so-called *semantic gap*, researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang_bridge_2016].
-Through these approaches, MER researchers attempt to shatter a so-called *glass ceiling* [@downie_music_2008] by establishing strong emotion predictors.
+Through these approaches, MER researchers attempt to shatter a so-called *glass ceiling* [@downie_music_2008] by establishing central predictors for emotions.
 To date, however, no study has systematically compared results of these diverse approaches.
@@
 
--   Our aim is to establish the level of predictive accuracy for both models of emotional expression that can account for track-specific coordinates in affective circumple space (valence and arousal) and classification of emotion categories based on available and recent studies.
--   We seek to identify the types of issues (modelling techniques, features, and musical qualities used) that significantly influence the prediction rates.
--   To achieve these aims, we carry out a meta-analysis focused on journal articles published in the last 10 years.
--   We outline broad hypotheses such as arousal being predicted to a higher degree than valence, which is more challenging and more context dependent than arousal.
+Our aim is to establish the level of predictive accuracy for both models of emotional expression that can account for track-specific coordinates in (a) affective circumple space (valence and arousal) and (b) classification of emotion categories based on available and recent studies.
+We seek to identify the types of issues (modelling techniques, features, and musical qualities used) that significantly influence the prediction rates.
+To achieve these aims, we carry out a meta-analysis focused on journal articles published in the last 10 years.
+Based on literature, we articulate broad hypotheses such as arousal being predicted to a higher degree than valence, which is more challenging and more context dependent than arousal.
 For classification, simple utilitarian emotions (e.g., fear, anger) will be easier to predict than complex social emotions (e.g., sadness, nostalgia).
@@
 |            | Regression                      | Classification            | Total |
-|:-----------|:---------------------------|:--------------------------|:------|
+|:-----------|:--------------------------------|:--------------------------|:------|
 | Study N    | 24                              | 14                        | 38    |
 | Model N    | 258                             | 108                       | 366   |
-| Techniques | Flexible Discriminants: 64 | 37                        | 101   |
-| Techniques | Neural Nets: 74            | 27                        | 101   |
-| Techniques | Linear Methods: 74         | 24                        | 98    |
-| Techniques | Random Forests: 22         | 12                        | 34    |
-| Techniques | KS, Add. & KNN: 24         | 8                         | 32    |
+| Techniques | Flexible Discriminants (FD): 64 | 37                        | 101   |
+| Techniques | Neural Nets (NN): 74            | 27                        | 101   |
+| Techniques | Linear Methods (LM): 74         | 24                        | 98    |
+| Techniques | Random Forests (RF): 22         | 12                        | 34    |
+| Techniques | KS, Add. & KNN (KS): 24         | 8                         | 32    |
 | Feature N  | Min=3, Md=472.5, Max=654        | Min=3, Md=231, Max=8904   | NA    |
@@
 The summary includes the number of models and observations, the correlation coefficient and its 95% confidence interval, the t-value and p-value for the correlation, the heterogeneity statistics $\tau^2$ and $I^2$, calculated through appropriate transformations (Fisher's Z) for the correlation coefficient as part of a random-effects model using `meta` library [@balduzzi2019].
+We used Paule-Mandel estimator for between-study heterogeneity [@langan2019comparison] and Knapp-Hartung [@knapp2003improved] adjustments for confidence intervals.
+In this table we also report two subgroup analyses.
+One where we have divided the studies according to the number of features they contain (three categories based on quantiles to keep the group size comparable) and into five modelling techniques introduced earlier (Table 1).
 
-Table 2. Meta-analytic diagnostic for all regression studies predicting valence from audio.
+Table 2. Meta-analytic diagnostic for all regression studies predicting valence from audio. See Table 1 for the acronyms of the modelling techniques.
 
@@
 
-<!-- | Val. MaxTrim | 13,7363     | 0.649 \[0.598; 0.695\] | 18.5 | .0001 | 0.008    | 88.5% | -->
-
-<!-- | Valence Trim |             | 0.605 \[0.592; 0.617\] | 72.4 | .0001 | 0.0007   | 33.1% | -->
-
-<!-- | Valence M    |             | 0.604 \[0.467; 0.712\] | 7.83 | .0001 | 0.100    | 97.8% | -->
-
-<!-- | Valence Md   |             | 0.602 \[0.466; 0.710\] | 7.87 | .0001 | 0.098    | 97.7% | -->
-
 -   OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION
@@
 
-Summarise the results here briefly
+The results indicate the valence can be accounted generally moderately well, _r_ = 0.658 (95%CI 0.557-0.740) for valence Max (the best model from each of the 24 studies), while all models (n=120) encoded in these studies yield significantly lower overall prediction rate ( _r_ = 0.567).
+We argue that the lower correlation is due to inclusion of baselines these studies report and therefore not a true measure of the success in the task for our analysis.
+Further on, looking at the between-study heterogeneity as indexed by $\tau^2$ (0.138) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] for 98.2%, which captures the percentage of variability in the effect size, both indicate substantial heterogeneity.
+Since $I^2$ is heavily influenced by the size of the studies (large N having low sampling error), the index is perhaps not so insightful here whereas $\tau^2$ less insentive to the size and the number of studies and directly related to the outcome variable (_r_) size, we draw our interpretations about heteregeneity from the latter.
+To understand the observed effects across the studies and the type of heterogeneity evident in the data, we provide Figure 2 showing a forest plot of the random effects model across all studies using the best model.
+[TO BE CONTINUED]
 

### 2024-10-10 manuscript/manuscript.qmd
reporting valence results (text) revision

@@
 
-Emotional engagement is one of the central reasons why people engage with music in their every day activities and why music is being implicated in various health applications [@juslin2022emotions;@agres2021music].
-Significant advances in music information retrieval relating to music emotion recognition (MER) tasks have been made in recent years [@gomez2021;@panda2020audio].
-The available features, modelling techniques and datasets have given the field opportunities to refine the accuracy and reliability of predicting annotated emotions from audio.
-Numerous studies over the last 25 years have established what emotions listeners perceive and recognise in music.
-In the last 15 years, it has become possible to trace the recognised emotions to musical contents such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013; @anderson2022ex; @grimaud_eerola_2022], or acoustic features [@yang2008; @panda2013multi; @saari_et_al_2015; @eerola2011c; @panda2020audio] or emergent properties identified through deep learning [@er2019music; @sarkar2020recognition].
+Emotional engagement is a key reason why people engage with music in their every day activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions;@agres2021music].
+In recent years, significant advances have been made in music information retrieval, particularly in music emotion recognition (MER) tasks [@gomez2021;@panda2020audio].
+Improvements in available features, modeling techniques, and datasets have provided the field with opportunities to enhance the accuracy and reliability of predicting annotated emotions from audio.
+Over the past 25 years, numerous studies have established the types of emotions that listeners perceive and recognize in music.
+In the last 15 years, research has increasingly focused on tracing these recognized emotions back to specific musical components, such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013; @anderson2022ex; @grimaud_eerola_2022], acoustic features [@yang2008; @panda2013multi; @saari_et_al_2015; @eerola2011c; @panda2020audio], or emergent properties revealed through deep learning techniques [@er2019music; @sarkar2020recognition].
 
-However, there is no consensus on to what degree emotions can be recognised by computational models, and the literature to date paints a diverse picture of success for concepts in affective circumplex -- valence and arousal-- [@Russell1980] and classifying various emotion categories [@fu2010survey].
+However, there is no consensus on the extent to which emotions can be accurately recognized by computational models.
+The current literature presents a diverse and mixed picture regarding the success of models in predicting emotions within the affective circumplex -- valence and arousal-- [@Russell1980] and in classifying distinct emotion categories [@fu2010survey].
 
@@
 
-Our aim is to establish the level of predictive accuracy for both models of emotional expression that can account for track-specific coordinates in (a) affective circumple space (valence and arousal) and (b) classification of emotion categories based on available and recent studies.
-We seek to identify the types of issues (modelling techniques, features, and musical qualities used) that significantly influence the prediction rates.
-To achieve these aims, we carry out a meta-analysis focused on journal articles published in the last 10 years.
-Based on literature, we articulate broad hypotheses such as arousal being predicted to a higher degree than valence, which is more challenging and more context dependent than arousal.
-For classification, simple utilitarian emotions (e.g., fear, anger) will be easier to predict than complex social emotions (e.g., sadness, nostalgia).
+Our aim is to evaluate the predictive accuracy of two models of emotional expression in music: (a) models that predict track-specific coordinates in affective circumplex space (valence and arousal), and (b) models that classify discrete emotion categories.
+We focus on recent to identify key factors such as modeling techniques and features that significantly affect  prediction accuracy.
+To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years.
+Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model.
+For emotion classification, we expect simple utilitarian emotions (e.g., fear, anger) will be easier to predict than more complex social emotions (e.g., sadness, nostalgia).
 
@@
 
-The results indicate the valence can be accounted generally moderately well, _r_ = 0.658 (95%CI 0.557-0.740) for valence Max (the best model from each of the 24 studies), while all models (n=120) encoded in these studies yield significantly lower overall prediction rate ( _r_ = 0.567).
-We argue that the lower correlation is due to inclusion of baselines these studies report and therefore not a true measure of the success in the task for our analysis.
-Further on, looking at the between-study heterogeneity as indexed by $\tau^2$ (0.138) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] for 98.2%, which captures the percentage of variability in the effect size, both indicate substantial heterogeneity.
-Since $I^2$ is heavily influenced by the size of the studies (large N having low sampling error), the index is perhaps not so insightful here whereas $\tau^2$ less insentive to the size and the number of studies and directly related to the outcome variable (_r_) size, we draw our interpretations about heteregeneity from the latter.
-To understand the observed effects across the studies and the type of heterogeneity evident in the data, we provide Figure 2 showing a forest plot of the random effects model across all studies using the best model.
+The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 24 studies achieving an average correlation of _r_ = 0.658 (95% CI: 0.557-0.740), called "valence Max" in Table 2.
+However, when considering all models across these studies (n = 120), the overall prediction rate drops significantly to _r_ = 0.567.
+We argue that this lower correlation is likely due to the inclusion of baseline models reported in these studies, which may not reflect the true success of the task for the purposes of our analysis.
+
+Further analysis of between-study heterogeneity, as indexed by the $\tau^2$ (0.138) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] at 98.2%, reveals substantial heterogeneity.
+Since $I^2$ is heavily influenced by study size (with larger N leading to lower sampling error), its value may be less insightful in this context.
+In contrast, $\tau^2$, which is less sentive to the number of studies and directly linked to the outcome metric (_r_), provides a more reliable measure of heterogeneity in this case.
+
+To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents a forest plot of the random-effects model based on the best-performing models from all studies.
+
 [TO BE CONTINUED]

### 2024-10-11 manuscript/manuscript.qmd
reporting valence results (text) splits

@@
 
-## Prediction success for valence and arousal (or affect dimensions)
+## Prediction success for affect dimensions
 
@@
 | *N Features* |             |                         |       |       |          |       |
-| \<18 F       | 5,3036      | 0.811 \[0.566; 0.775\]  | \-    | \-    | 0.182    | 98.9% |
+| \<18 F       | 5,3036      | 0.811 \[0.566; 0.???\]  | \-    | \-    | 0.182    | 98.9% |
 | 18-260 F     | 11,7318     | 0.548 \[0.343; 0.703\]  | \-    | \-    | 0.133    | 97.6% |
@@
 -   OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION
-
 <!-- see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678 -->
@@
 
-To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents a forest plot of the random-effects model based on the best-performing models from all studies.
+To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents a forest plot of the random-effects model, based on the best-performing models from all studies.
+The range of prediction values (correlations) is broad, spanning from 0.13 to 0.92, with all studies except Koh et al.
+(2023) demonstrating evidence of positive correlations.
+A mean estimate of 0.66 is achieved by 15 out of the 24 models.
+While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), @saizclar2022pr (n = 40), and in @griffiths2021am (n = 40).
 
-[TO BE CONTINUED]
+To gain insights into the factors contributing to the wide range of model success, we explored several ways of splitting the data.
+Table 2 presents two key splits: one based on the number of features used, which we hypothesized might influence model performance, and another based on the modeling techniques employed.
+In terms of feature sets, we categorized them into three groups: few features (<18), a large number of features (18–260), and massive feature sets (260+).
+Interestingly, models using a relatively small number of features (<18) performed best (_r_ = 0.881, 95% CI: 0.566–0.???) compared to those utilizing larger feature sets.
+However, it is worth noting that the models using massive feature sets (260+) also performed well (_r_ = 0.685), achieving better and more consistent results than the overall prediction rate (_r_ = 0.659).
+This observation is supported by the lowest heterogeneity index for the massive feature set group ($\tau^2$ = 0.044), indicating more consistent results across studies.
 
-Moving on the arousal, ...
+When analyzing the data by modeling techniques, we identified five sub-groups.
+Notably, linear models (LM) and flexible discriminants (FD) were the most common, with 8 and 6 studies, respectively, allowing for more confident interpretations.
+Linear models achieved the highest prediction rate (_r_ = 0.784, 95% CI: 0.625–0.881), though this may be influenced by the smaller datasets typically used in these studies.
+These studies also exhibited substantially higher heterogeneity ($\tau^2$ = 0.137) compared to other techniques, where $\tau^2$ values were less than half of this.
+Flexible discriminants performed at a similar level to the overall model average (_r_ = 0.656, 95% CI: 0.484–0.779).
+The relatively poor performance of neural network (NN) models (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
+
+These comparisons of sub-groupings are also influenced by other factors, such as the type of stimuli used in the studies and whether the objective is to explain or predict emotions.
+Although the sub-groupings result in an uneven distribution of studies and observations, they still offer valuable insights.
+Despite these caveats, the current sub-groupings enable us to identify interesting differences related to model success across the studies.
+
+Moving on the arousal, we carry out the same meta-analytical analysis applying the random-effects model to arousal.
+Table 3 and Figure 2 shows the same outputs as was done for valence describing the broad pattern of results in tabular and in forest plot formats.
+Table 3 give
 

### 2024-10-17 analysis/analysis.qmd
reporting valence results (text) revision
new figures in a separate quarto docs

@@
 #| eval: true
-library(dmetar)
-library(tidyverse)
+library(dmetar,quietly = TRUE)
+library(tidyverse,quietly = TRUE)
 library(meta)
@@
 
+### Sub-division based on N features and genres
+
+```{r}
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
+dim(tmp)
+m.cor4 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  feature_n_complexity_genre,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor4)
+S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
+print(S)
+
+```
+
 #### Visualise (forest and funnel plots)
@@
 ```{r}
-forest(m.cor,
+#| fig-width: 12
+#| fig-height: 6
+fig2a <- forest(m.cor,
        sortvar = TE,
@@
 
-#funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+fig2b<-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
 
+library(forestplot)
+data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
+data<-dplyr::arrange(data,mean)
+
+fp1 <- grid.grabExpr(print(data |>
+  forestplot(labeltext = c(study, n, cor),
+             xlab = "Correlation",
+             xticks = c(0, .25,.5,.75, 1),
+             clip = c(0, 1))|>
+    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
+    fp_append_row(mean  = m.cor$TE.common,
+                lower = m.cor$lower.common,
+                upper = m.cor$upper.common,
+                study = "Summary",
+                n = sum(m.cor$n),
+                cor = round(m.cor$TE.common,2),
+                is.summary = TRUE) |>
+  fp_set_style(box = "grey50",
+               line = "grey20",
+               summary = "black",
+                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
+                                ticks = gpar(cex = 0.80),
+                                xlab  = gpar(cex = 0.80)))|>
+    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
+)
+)
+
+source('../etc/custom_funnel_plot.R')
+fp2 <- custom_funnel_plot(m.cor)
+
+gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1),heights=c(2,1))
 ```

### 2024-10-17 analysis/preprocessing.qmd
new figures in a separate quarto docs

@@
 
-R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed))
+R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))
 
@@
 table(R_studies$feature_n_complexity)
+```
+## Feature N and genre split
+
+```{r}
+quantile(subset(R_studies,stimulus_genre_mixed=='SingleGenre')$feature_n,probs = seq(0,1,0.333))
+quantile(subset(R_studies,stimulus_genre_mixed=='MultiGenre')$feature_n,na.rm=TRUE,probs = seq(0,1,0.333))
+
+# a combination of the two
+R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
+                                      breaks = c(0,15,501,653,10000),
+                                      labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
+table(R_studies$feature_n_complexity_genre)
 ```

### 2024-10-17 manuscript/_figure1.qmd
new figures in a separate quarto docs

@@
-```{r}
-#| label: fig1
-#| fig.height: 7
-#| echo: false
-#| fig.cap: > 
-#|   Forest plot of valence predictions from the MER models.
+```{dot}
+//| label: fig1
+//| fig-cap: "Flowchart of the study inclusions/eliminations."
 
-library(metafor)
-library(dmetar)
-library(meta)
+digraph sub {
+  node [fontname = Helvetica, fontsize = 14, shape = box, width = 4]
+  A [label = "Records identified from:
+                Web of Science (n = 142)
+                Scopus (n = 227)
+                OpenALEX (n = 278)" ]
+  B [label = "Records removed before screening: 
+                Duplicates entries/errors (n = 94)" ]
+  C [label = "Records after duplicates removed (n = 553)"]
+  D [label = "Records screened (n = 553)"]
+  E [label = "Records removed: 
+                Irrelevant titles/themes (n = 338)
+                Abstract screening (n = 95)
+                Discussion (n = 24)"]
+  F [label = "Full text articles assessed (n = 96)"]
+  G [label = "Studies included in final review (n = 46)"]
+  H [label = "Full text articles excluded
+             (n = 50)"]
+  I [label = "Studies excluded in final review (n = 10)"]
+  J [label = "Final selection (n = 36)"]
+  A->B
+  A->C
+  C->D
+  D->E
+  D->F
+  F->H 
+  F->G
+  G->I
+  G->J
 
-R_summary <- read.csv("../analysis/R_summary.csv")
-tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
-
-# Max values
-m.cor <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = studyREF,#citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 #                 backtransf = TRUE,
-                 #                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-
-forest(m.cor,
-       sortvar = TE,
-       fontfamily = "Times",
-       hetstat =FALSE,
-       prediction = FALSE, 
-       print.tau2 = FALSE,
-       leftlabs = c("Author", "g", "SE"),layout = "meta",addrows =0,rows.gr=0,col.diamond='black') # RevMan5
-
+  { rank = same; A B}
+  { rank = same; D, E}
+  { rank = same; F, H}
+  { rank = same; G, I}
+}
 ```

### 2024-10-17 manuscript/_figure2.qmd
new figures in a separate quarto docs

--- 2024-09-25 analysis/analysis.qmd
@@
-# Analysis
+```{r}
+#| label: fig2
+#| fig-width: 16
+#| fig-height: 6
+#| echo: false
+#| fig.cap: > 
+#|   Forest and funnel plots of valence predictions from the MER models.
 
-This assumes that the data has been parsed (`parse-model-output.R`, `format-study-results.R`) and preprocessed (`processing.qmd`).
+library(metafor, warn.conflicts = FALSE)
+library(dmetar,warn.conflicts = FALSE)
+library(meta,warn.conflicts = FALSE)
+library(DescTools,warn.conflicts = FALSE)
+library(ggplot2,quietly = TRUE)
+library(ggrepel,quietly = TRUE)
 
-## Regression studies
-
-### Valence: Best model
-
-For creating Table 2
-
-```{r}
-#| warning: false
-#| eval: true
-library(dmetar)
-library(tidyverse)
-library(meta)
-library(DescTools)
-library(ggrepel)
-```
-
-#### Using all models
-
-```{r}
-R_studies <- read.csv("R_studies.csv")
-#R_summary <- read.csv("R_summary.csv")
-
-# select regression studies with r2
-#tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp <- dplyr::filter(R_studies,dimension=="valence")
-#dim(tmp)
-
-#if all studies, remove two with NA values
-tmp <- tmp[!is.na(tmp$values),]
-#dim(tmp)
-
-# Take all models
-m.cor <- metacor(cor = values,     # values 
-                 n = stimulus_n,
-                 studlab = unique_id,
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-
-print(m.cor)
-
-print(FisherZInv(m.cor$TE.random))
-print(FisherZInv(m.cor$upper.random))
-print(FisherZInv(m.cor$lower.random))
-
-#m.cor_backtransformed <- m.cor
-#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
-
-```
-
-#### Using the best model out of each study
-
-```{r}
-#R_studies <- read.csv("R_studies.csv")
-R_summary <- read.csv("R_summary.csv")
-
-# select regression studies with r2
+R_summary <- read.csv("../analysis/R_summary.csv")
 tmp <- dplyr::filter(R_summary,dimension=="valence")
-#tmp <- dplyr::filter(R_studies,dimension=="valence")
-#dim(tmp)
-
-#if all studies, remove two
-#tmp <- tmp[!is.na(tmp$values),]
-#dim(tmp)
-
-## Disambiguate the studies
 tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
@@
 
-print(m.cor)
+#### Forest plot using forestplot
+library(forestplot)
+data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
+data<-dplyr::arrange(data,mean)
 
-print(FisherZInv(m.cor$TE.random))
-print(FisherZInv(m.cor$upper.random))
-print(FisherZInv(m.cor$lower.random))
+fp1 <- grid.grabExpr(print(data |>
+  forestplot(labeltext = c(study, n, cor),
+             xlab = "Correlation",
+             xticks = c(0, .25,.5,.75, 1),
+             clip = c(0, 1))|>
+    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
+    fp_append_row(mean  = m.cor$TE.common,
+                lower = m.cor$lower.common,
+                upper = m.cor$upper.common,
+                study = "Summary",
+                n = sum(m.cor$n),
+                cor = round(m.cor$TE.common,2),
+                is.summary = TRUE) |>
+  fp_set_style(box = "grey50",
+               line = "grey20",
+               summary = "black",
+                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
+                                ticks = gpar(cex = 0.80),
+                                xlab  = gpar(cex = 0.80)))|>
+    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
+)
+)
 
-#m.cor_backtransformed <- m.cor
-#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
+#### Funnel plot using a custom function
+source('../etc/custom_funnel_plot.R')
+fp2 <- suppressWarnings(custom_funnel_plot(m.cor))
+
+gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
 
 ```
-
-### Sub-division based on techniques
-
-```{r}
-m.cor1 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  model_class_id,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor1)
-
-S<-summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
-print(S)
-```
-
-### Sub-division based on journals (engineering vs psych)
-
-```{r}
-m.cor2 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  journal_type,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-```
-
-### Sub-division based on N features
-
-```{r}
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
-dim(tmp)
-m.cor3 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  feature_n_categories,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor3)
-S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
-print(S)
-
-```
-
-#### Visualise (forest and funnel plots)
-
-```{r}
-forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"),studlab = studyREF)
-
-#funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
-
-```
-
-#### Explore qualities (in progress)
-
-```{r}
-O <- find.outliers(m.cor)
-# 6 datasets identified as outliers, without them the r drops to 0.5781
-infan <- InfluenceAnalysis(m.cor)
-print(eggers.test(m.cor))
-```
-
-#### Re-run the analysis without the outliers
-
-```{r}
-#| eval: false
-#| echo: false
-outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")
-
-tmp2<-tmp[!tmp$unique_id %in% outliers,]
-m.cor <- metacor(cor = values, 
-                 n = stimulus_n,
-                 studlab = unique_id, # unique_id
-                 data = tmp2,
-                 fixed = FALSE,
-                 random = TRUE,
-                 sm = "ZCOR",
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-
-print(m.cor)
-
-fp <- funnel(m.cor, common = TRUE,studlab=FALSE)
-
-```
-
-#### Custom funnel plot
-
-To show the quality differences between core and eliminated studies.
-
-```{r}
-tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
-#tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)
-
-estimate = m.cor$TE.common
-se = m.cor$seTE.common
-se.seq=seq(0, max(m.cor$cor), 0.001)
-ll95 = estimate-(1.96*se.seq)
-ul95 = estimate+(1.96*se.seq)
-ll99 = estimate-(3.29*se.seq)
-ul99 = estimate+(3.29*se.seq)
-meanll95 = estimate-(1.96*se)
-meanul95 = estimate+(1.96*se)
-dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
-
-fp = ggplot(NULL) +
-  geom_point(aes(x = SE, y = Zr), color='grey50',data=tmpdata) +
-  geom_text_repel(aes(x = SE, y = Zr, label=studies), data=tmpdata,size=2.5,max.overlaps = 40)+
-  xlab('Standard Error') + ylab('Correlation')+
-  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
-  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
-  geom_hline(yintercept = estimate, linetype='solid', color='grey50',linewidth=0.2) +
-  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
-  scale_y_continuous(breaks=seq(0.0,1.00,0.20),limits=c(0.0,1.00),expand=c(0.00,0.00))+
-  coord_flip()+
-  theme_bw()
-print(fp)
-```
-
-#### Subgroup analysis according to techniques
-
-add `journal_type` and `stimulus_genre_mixed` as a grouping option
-
-```{r}
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-#       subgroup = journal_type, 
-#       subgroup = stimulus_genre_mixed, 
-       tau.common = FALSE,
-       prediction = TRUE)
-
-print(m.cor_subgroups)
-#forest(m.cor_subgroups,subgroup=TRUE)
-```
-
-- Idea: visualise the distributions of the model successes within studies (done in preprocessing)
-
-### Arousal: Best model
-
-```{r}
-#| warning: false
-#| eval: true
-
-# select regression studies with r2
-tmp <- dplyr::filter(R_summary,dimension=="arousal")
-#tmp <- dplyr::filter(R_studies,dimension=="arousal")
-dim(tmp)
-#tmp <- tmp[!is.na(tmp$values),]
-dim(tmp)
-#tmp<-drop_na(tmp)
-
-m.cor <- metacor(cor = valuesMax, 
-                 n = stimulus_n,
-                 studlab = citekey,
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Arousal: Summary")
-
-print(m.cor)
-```
-### Trimmed analysis
-```{r}
-O <- find.outliers(m.cor)
-```
-
-#### Visualise (forest and funnel plots)
-
-```{r}
-forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"))
-plot(eggers.test(m.cor))
-```
-
-#### Explore qualities (in progress)
-
-```{r}
-#| eval: false
-meta <- metagen(valuesMax, sqrt(valuesMax), 
-                data = tmp, 
-                studlab = tmp$citekey, 
-                comb.fixed = FALSE, 
-                method.tau = "PM")
-find.outliers(meta)
-infan <- InfluenceAnalysis(meta)
-print(eggers.test(meta))
-
-```
-
-#### Subgroup analysis according to techniques
-
-```{r}
-update(m.cor, 
-       subgroup = model_class_id, 
-       tau.common = FALSE)
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-       tau.common = FALSE)
-
-forest(m.cor_subgroups,subgroup=TRUE)
-```
-
-- Idea: visualise the distributions of the model successes within studies (done in preprocessing)
-
-```{r}
-#| eval: false
-g1 <- ggplot(tmp,aes(y=valuesMax,fill=model_class_id))+
-   geom_histogram(show.legend = T)+
-  facet_wrap(.~studyREF)+
-   coord_flip()+
-   theme_bw()
-g1
-
-# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
-# g<-ggplot(S,aes(y=maxvalue))+
-#   geom_histogram(bins = 14)+
-#   #facet_wrap(.~studyREF)+
-#   coord_flip()+
-#   theme_bw()
-# g
-```
-
-## Classification studies
-
-```{r}
-#| warning: false
-#| eval: true
-
-C_studies <- read.csv("C_studies.csv")
-C_studies <- C_studies[!is.na(C_studies$values),]
-
-C_summary <- read.csv("C_summary.csv")
-
-m.cor <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = studyREF, # unique_id
-                 data = C_summary,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Classification: Summary")
-
-#print(m.cor)
-
-#m.cor_backtransformed <- m.cor
-#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-print(funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE))
-
-```
-#### Custom plot
-
-```{r}
-library(ggrepel)
-tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
-
-tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
-tmpdata$citekey<-factor(tmpdata$citekey)
-
-g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
-  geom_point(show.legend = FALSE) +
-  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
-  ylab('Standard Error') + 
-  xlab('r')+
-  scale_y_reverse()+
-#  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
-#  coord_flip()+
-  theme_bw()
-print(g)
-```
-
-#### Visualise (forest and funnel plots)
-
-```{r}
-forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"),studlab = citekey)
-
-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
-
-```
-
-#### Explore qualities (in progress)
-
-```{r}
-O <- find.outliers(m.cor)
-# 6 datasets identified as outliers, without them the r drops to 0.5781
-#infan <- InfluenceAnalysis(m.cor)
-#print(eggers.test(m.cor))
-
-```
-
-#### Re-run the analysis without the outliers
-
-```{r}
-#| eval: false
-#| echo: false
-outliers <- c("")
-
-tmp2<-tmp[!tmp$unique_id %in% outliers,]
-m.cor <- metacor(cor = values, 
-                 n = stimulus_n,
-                 studlab = unique_id, # unique_id
-                 data = tmp2,
-                 fixed = FALSE,
-                 random = TRUE,
-                 sm = "ZCOR",
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-
-print(m.cor)
-
-fp <- funnel(m.cor, common = TRUE,studlab=FALSE)
-
-```
-
-#### Custom funnel plot
-
-To show the quality differences between core and eliminated studies (in progress).
-
-```{r}
-#| eval: true
-tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)
-
-tmpdata$studyREF <- substr(tmpdata$studies,1,nchar(tmpdata$studies)-2)
-tmpdata$studyREF <- str_replace_all(tmpdata$studyREF,'([0-9]+)',' et al \\1')
-tmpdata$studyREF <- str_to_sentence(tmpdata$studyREF)
-tmpdata$studyREF
-
-estimate = m.cor$TE.common
-se = m.cor$seTE.common
-se.seq=seq(0, max(m.cor$cor), 0.001)
-ll95 = estimate-(1.96*se.seq)
-ul95 = estimate+(1.96*se.seq)
-ll99 = estimate-(3.29*se.seq)
-ul99 = estimate+(3.29*se.seq)
-meanll95 = estimate-(1.96*se)
-meanul95 = estimate+(1.96*se)
-dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
-
-fp = ggplot(NULL) +
-  geom_point(aes(x = SE, y = Zr), color='grey50',data=tmpdata) +
-  geom_text_repel(aes(x = SE, y = Zr, label=studyREF), data=tmpdata,size=2.5,max.overlaps = 40)+
-  xlab('Standard Error') + ylab('Fisher\'s z transformed correlation')+
-  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
-  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
-  geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
-  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
-#  scale_x_reverse()+
-  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
-  scale_y_continuous(breaks=seq(0.3,1.25,0.20),limits=c(0.3,1.23))+
-  coord_flip()+
-  theme_bw()
-print(fp)
-
-```
-
-#### Subgroup analysis according to techniques
-
-add `journal_type` and `stimulus_genre_mixed` as a grouping option
-
-```{r}
-#| eval: false
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-#       subgroup = journal_type, 
-#       subgroup = stimulus_genre_mixed, 
-       tau.common = FALSE,
-       prediction = TRUE)
-
-print(m.cor_subgroups)
-#forest(m.cor_subgroups,subgroup=TRUE)
-```
-
-- Idea: visualise the distributions of the model successes within studies (done in preprocessing)

### 2024-10-17 manuscript/manuscript.qmd
new figures in a separate quarto docs

@@
 
-\[Figure 1: flowchart of the study inclusions/eliminations\]
-
-```{dot}
-
-digraph sub {
-  node [fontname = Helvetica, fontsize = 14, shape = box, width = 4]
-  A [label = "Records identified from:
-                Web of Science (n = 142)
-                Scopus (n = 227)
-                OpenALEX (n = 278)" ]
-  B [label = "Records removed before screening: 
-                Duplicates entries/errors (n = 94)" ]
-  C [label = "Records after duplicates removed (n = 553)"]
-  D [label = "Records screened (n = 553)"]
-  E [label = "Records removed: 
-                Irrelevant titles/themes (n = 338)
-                Abstract screening (n = 95)
-                Discussion (n = 24)"]
-  F [label = "Full text articles assessed (n = 96)"]
-  G [label = "Studies included in final review (n = 46)"]
-  H [label = "Full text articles excluded
-             (n = 50)"]
-  I [label = "Studies excluded in final review (n = 10)"]
-  J [label = "Final selection (n = 36)"]
-  A->B
-  A->C
-  C->D
-  D->E
-  D->F
-  F->H 
-  F->G
-  G->I
-  G->J
-
-  { rank = same; A B}
-  { rank = same; D, E}
-  { rank = same; F, H}
-  { rank = same; G, I}
-}
-
-```
+{{< include _figure1.qmd >}}
 
@@
 
--   OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION
-<!-- see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678 -->
-
-{{< include _figure1.qmd >}}
-
 The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 24 studies achieving an average correlation of _r_ = 0.658 (95% CI: 0.557-0.740), called "valence Max" in Table 2.
@@
 While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), @saizclar2022pr (n = 40), and in @griffiths2021am (n = 40).
+
+{{< include _figure2.qmd >}}
 
@@
 
-These comparisons of sub-groupings are also influenced by other factors, such as the type of stimuli used in the studies and whether the objective is to explain or predict emotions.
+We also ran the sub-grouping analyses across a combination of stimulus genres (single vs mixed) and number of the features to explore where the differences in model success might lie.
+For this purpose, we grouped the studies into small single genre/multigenre studies (1), medium single genre/multigenre studies (2), and medium-large single genre/multigenre studies (3), and huge multigenre studies (4).
+The small single genre/multigenre studies generally performed best (_r_ = 0.836, 95% CI: -0.197-0.989), followed by huge multi-genre studies (_r_ = 0.720, 95% CI: -0.189-0.965) while the medium and medium-large sized studies performance was between close the overall average (medium-large, _r_ = 0.669, 95% CI: 0.347-0.850 and medium _r_ = 0.587, 95% CI: 0.433-0.708).
+The heterogeneity was lowest in the huge multigenre studies ($\tau^2$ = 0.013) and highest in the small single genre/multigenre studies ($\tau^2$ = 0.318).
+
+<!-- However, these analyses did not reveal any clear patterns, likely due to the small number of studies in each subgroup.  -->
+
+<!-- see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678 -->
+
+These comparisons of sub-groupings are also influenced by other factors, such as the type of journal (psychology vs engineering) or whether the objective is to explain or predict emotions.
 Although the sub-groupings result in an uneven distribution of studies and observations, they still offer valuable insights.
-Despite these caveats, the current sub-groupings enable us to identify interesting differences related to model success across the studies.
+Despite these caveats, the  two main sub-groupings portrayed in Table 2 enable us to identify valuable differences related to model success across the studies.
 
@@
 
-Figure 2. Forest plot of arousal prediction (using Max?)
-
-<!-- | Arousal Trim |             | 0.7932 \[0.7846; 0.8014\] | 96.5 | 0.0001 | 0.0030   | 73.3% | -->
-
-<!-- | Arousal M    |             | 0.7567 \[0.6752; 0.8199\] | 12.7 | 0.0001 | 0.0739   | 95.6% | -->
-
-<!-- | Arousal Md   |             | 0.7627 \[0.6819; 0.8252\] | 12.7 | 0.0001 | 0.0757   | 95.3% | -->
-
-<!-- | Aro.Max.Trm  | 14,12061    | 0.8182 \[0.8021; 0.8331\] | 25.6 | 0.0001 | 0.0132   | 96.8% | -->
+<!-- {{< include _figure3.qmd >}} -->
 

### 2024-10-17 etc/custom_funnel_plot.R

@@ -1,0 +1,52 @@
+custom_funnel_plot <- function(data) {
+  # Function to plot a funnel plot with 95% and 99% confidence intervals
+  # assumes data from dmetar::metacor function
+  
+  tmpdata <- data.frame(
+    SE = FisherZInv(data$seTE),
+    Zr = FisherZInv(data$TE),
+    studies = data$studlab
+  )
+  
+  estimate = data$TE.common
+  se = data$seTE.common
+  se.seq = seq(0, max(data$cor), 0.001)
+  ll95 = estimate - (1.96 * se.seq)
+  ul95 = estimate + (1.96 * se.seq)
+  ll99 = estimate - (3.29 * se.seq)
+  ul99 = estimate + (3.29 * se.seq)
+  meanll95 = estimate - (1.96 * se)
+  meanul95 = estimate + (1.96 * se)
+  dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
+  
+  fp = ggplot(NULL) +
+    geom_point(aes(x = SE, y = Zr), color = 'grey50', data = tmpdata) +
+    geom_text_repel(
+      aes(x = SE, y = Zr, label = studies),
+      data = tmpdata,
+      size = 2.5,
+      max.overlaps = 45
+    ) +
+    xlab('Standard Error') + ylab('Correlation') +
+    geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
+    geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
+    geom_hline(
+      yintercept = estimate,
+      linetype = 'solid',
+      color = 'grey50',
+      linewidth = 0.2
+    ) +
+    scale_x_reverse(
+      breaks = seq(0, 0.2, 0.05),
+      limits = c(max(tmpdata$SE), 0),
+      expand = c(0.001, 0.001)
+    ) +
+    scale_y_continuous(
+      breaks = seq(0.0, 1.00, 0.25),
+      limits = c(0.0, 1.00),
+      expand = c(0.005, 0.005)
+    ) +
+    coord_flip() +
+    theme_bw()
+  return <- fp
+}

### 2024-10-20 analysis/analysis.qmd
figure 3

@@
 ```{r}
-O <- find.outliers(m.cor)
+#| eval: false
+#| echo: false
+O <- find.outliers(m.cor) # 13 remaining out of 24
 # 6 datasets identified as outliers, without them the r drops to 0.5781
@@
 print(eggers.test(m.cor))
+
+# 10% most precise studies (Stanley, Jarrel, Doucouliagos 2010)
+thres<-quantile(m.cor$seTE,0.1)
+ind<-m.cor$seTE<=as.numeric(thres)
+
+m.cor10pct <- update(m.cor, subset = which(ind))
+
 ```

### 2024-10-20 manuscript/_figure3.qmd
figure 3

--- 2024-10-17 manuscript/_figure2.qmd
@@
 ```{r}
-#| label: fig2
+#| label: fig3
 #| fig-width: 16
@@
 #| fig.cap: > 
-#|   Forest and funnel plots of valence predictions from the MER models.
+#|   Forest (A) and funnel (B) plots of the best arousal models from all MER studies.
 

### 2024-10-20 manuscript/manuscript.qmd
figure 3

@@
 Since $I^2$ is heavily influenced by study size (with larger N leading to lower sampling error), its value may be less insightful in this context.
-In contrast, $\tau^2$, which is less sentive to the number of studies and directly linked to the outcome metric (_r_), provides a more reliable measure of heterogeneity in this case.
+In contrast, $\tau^2$, which is less sensitive to the number of studies and directly linked to the outcome metric (_r_), provides a more reliable measure of heterogeneity in this case.
+Also, we note that because the overall heterogeneity in the data is high, we are cautious in our interpretation of the publication bias [@van-aertwicherts_2016].
 
-To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents a forest plot of the random-effects model, based on the best-performing models from all studies.
-The range of prediction values (correlations) is broad, spanning from 0.13 to 0.92, with all studies except Koh et al.
+To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents (A) a forest and (B) funnel plot of the random-effects model, based on the best-performing models from all studies.
+In terms of the forest plot, the range of prediction values (correlations) is broad, spanning from 0.13 to 0.92, with all studies except Koh et al.
 (2023) demonstrating evidence of positive correlations.
@@
 While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), @saizclar2022pr (n = 40), and in @griffiths2021am (n = 40).
+The funnel plot in panel B of Figure 2 shows clustering at the top of the plot (studies with low standard error) and no assumed larger diversity in the correlations when the error rates increase.
+However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$=5.00, CI95% -0.78-10.78, _t_ = 1.70, _p_ = 0.104, @eggersmith_1997).
+Coming back to the mean of valence correlation of 0.66 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect.
+This left 13 studies in the data and resulted in the meta-analytical pooled correlation of 0.649 (CI95% 0.598-0.695).
+In other words, despite the large variation in the correlations and standard errors across the studies, this variation in itself does not seem to be a significant driver behind the overall effect.
 
@@
 
-When analyzing the data by modeling techniques, we identified five sub-groups.
+When analyzing the studies across the five modeling techniques used.
 Notably, linear models (LM) and flexible discriminants (FD) were the most common, with 8 and 6 studies, respectively, allowing for more confident interpretations.
@@
 Flexible discriminants performed at a similar level to the overall model average (_r_ = 0.656, 95% CI: 0.484–0.779).
-The relatively poor performance of neural network (NN) models (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
+The relatively poor performance of the neural network (NN) models (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
 
-We also ran the sub-grouping analyses across a combination of stimulus genres (single vs mixed) and number of the features to explore where the differences in model success might lie.
-For this purpose, we grouped the studies into small single genre/multigenre studies (1), medium single genre/multigenre studies (2), and medium-large single genre/multigenre studies (3), and huge multigenre studies (4).
+We also ran the sub-grouping analyses across a combination of stimulus genres (single vs mixed) and number of the features to explore where the differences in the model prediction rates might lie.
+For this purpose, we grouped the studies into small single genre/multigenre studies, medium single genre/multigenre studies, and medium-large single genre/multigenre studies, and huge multigenre studies.
 The small single genre/multigenre studies generally performed best (_r_ = 0.836, 95% CI: -0.197-0.989), followed by huge multi-genre studies (_r_ = 0.720, 95% CI: -0.189-0.965) while the medium and medium-large sized studies performance was between close the overall average (medium-large, _r_ = 0.669, 95% CI: 0.347-0.850 and medium _r_ = 0.587, 95% CI: 0.433-0.708).
@@
 Moving on the arousal, we carry out the same meta-analytical analysis applying the random-effects model to arousal.
-Table 3 and Figure 2 shows the same outputs as was done for valence describing the broad pattern of results in tabular and in forest plot formats.
-Table 3 give
+Table 3 and Figure 3 show the same outputs as was done for valence describing the broad pattern of results in tabular format, and visually illustrate the spread and heterogeneity of all studies.
+
+Table 3 indicates that the overall correlation across the studies using the best performing model out of each study (Max) is 0.807 (CI95% 0.745-0.855).
+If we examine all the models, the correlation drops to 0.796, only marginally lower.
+
+The indicators of heterogeneity ($\tau^2$ = 0.155 and $I^2$=96.8%) suggest high
 

### 2024-10-21 analysis/analysis.qmd
arousal analysis included

--- 2024-10-17 analysis/analysis.qmd
@@
 
-### Valence: Best model
+### Valence
 
@@
 print(FisherZInv(m.cor$lower.random))
-
-#m.cor_backtransformed <- m.cor
-#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
-
 ```
@@
 ```{r}
-#R_studies <- read.csv("R_studies.csv")
 R_summary <- read.csv("R_summary.csv")
@@
 print(FisherZInv(m.cor$lower.random))
-
-#m.cor_backtransformed <- m.cor
-#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-#print(funnel(m.cor_backtransformed, common = FALSE, studlab=TRUE,backtransf=TRUE))
-
 ```
 
-### Sub-division based on techniques
+### Explore heterogeneity
 
 ```{r}
-m.cor1 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  model_class_id,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor1)
+#| eval: true
+#| echo: true
+# Method 1: Give us the Egger's test about beta coefficient from funnel
+print(eggers.test(m.cor))
 
-S<-summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
-print(S)
+# Method 2: Find the impact to the results when removing those outside the 95CI
+O <- find.outliers(m.cor) # 13 remaining out of 24
+print(O)
+# Method 3: Leave-out-out analysis etc for individual influence (not useful here)
+#infan <- InfluenceAnalysis(m.cor)
+
+# Method 4: Focus on 10% of most precise studies (Stanley, Jarrel, Doucouliagos 2010)
+thres<-quantile(m.cor$seTE,0.1)
+ind<-m.cor$seTE<=as.numeric(thres)
+m.cor10pct <- update(m.cor, subset = which(ind))
+
+# Method 5: P curve analysis (Simonsohn, Simmons & Nelson, 2015)
+pcurve(m.cor)
 ```
 
-### Sub-division based on journals (engineering vs psych)
-
-```{r}
-m.cor2 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  journal_type,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-```
-
-### Sub-division based on N features
-
-```{r}
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
-dim(tmp)
-m.cor3 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  feature_n_categories,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor3)
-S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
-print(S)
-
-```
-
-### Sub-division based on N features and genres
-
-```{r}
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
-dim(tmp)
-m.cor4 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  feature_n_complexity_genre,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor4)
-S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
-print(S)
-
-```
-
-#### Visualise (forest and funnel plots)
+### Visualise (forest and funnel plots)
 
@@
 
-#### Explore qualities (in progress)
+### Sub-divisions
+
+#### Sub-division based on techniques
+
+```{r,results='asis'}
+S <- summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
 
 ```{r}
-O <- find.outliers(m.cor)
-# 6 datasets identified as outliers, without them the r drops to 0.5781
-infan <- InfluenceAnalysis(m.cor)
-print(eggers.test(m.cor))
-```
-
-#### Re-run the analysis without the outliers
-
-```{r}
-#| eval: false
-#| echo: false
-outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")
-
-tmp2<-tmp[!tmp$unique_id %in% outliers,]
-m.cor <- metacor(cor = values, 
+m.cor1 <- metacor(cor = valuesMax,     # values 
                  n = stimulus_n,
-                 studlab = unique_id, # unique_id
-                 data = tmp2,
-                 fixed = FALSE,
-                 random = TRUE,
-                 sm = "ZCOR",
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-
-print(m.cor)
-
-fp <- funnel(m.cor, common = TRUE,studlab=FALSE)
-
-```
-
-#### Custom funnel plot
-
-To show the quality differences between core and eliminated studies.
-
-```{r}
-tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
-#tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)
-
-estimate = m.cor$TE.common
-se = m.cor$seTE.common
-se.seq=seq(0, max(m.cor$cor), 0.001)
-ll95 = estimate-(1.96*se.seq)
-ul95 = estimate+(1.96*se.seq)
-ll99 = estimate-(3.29*se.seq)
-ul99 = estimate+(3.29*se.seq)
-meanll95 = estimate-(1.96*se)
-meanul95 = estimate+(1.96*se)
-dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
-
-fp = ggplot(NULL) +
-  geom_point(aes(x = SE, y = Zr), color='grey50',data=tmpdata) +
-  geom_text_repel(aes(x = SE, y = Zr, label=studies), data=tmpdata,size=2.5,max.overlaps = 40)+
-  xlab('Standard Error') + ylab('Correlation')+
-  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
-  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
-  geom_hline(yintercept = estimate, linetype='solid', color='grey50',linewidth=0.2) +
-  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
-  scale_y_continuous(breaks=seq(0.0,1.00,0.20),limits=c(0.0,1.00),expand=c(0.00,0.00))+
-  coord_flip()+
-  theme_bw()
-print(fp)
-```
-
-#### Subgroup analysis according to techniques
-
-add `journal_type` and `stimulus_genre_mixed` as a grouping option
-
-```{r}
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-#       subgroup = journal_type, 
-#       subgroup = stimulus_genre_mixed, 
-       tau.common = FALSE,
-       prediction = TRUE)
-
-print(m.cor_subgroups)
-#forest(m.cor_subgroups,subgroup=TRUE)
-```
-
-- Idea: visualise the distributions of the model successes within studies (done in preprocessing)
-
-### Arousal: Best model
-
-```{r}
-#| warning: false
-#| eval: true
-
-# select regression studies with r2
-tmp <- dplyr::filter(R_summary,dimension=="arousal")
-#tmp <- dplyr::filter(R_studies,dimension=="arousal")
-dim(tmp)
-#tmp <- tmp[!is.na(tmp$values),]
-dim(tmp)
-#tmp<-drop_na(tmp)
-
-m.cor <- metacor(cor = valuesMax, 
-                 n = stimulus_n,
-                 studlab = citekey,
+                 studlab = citekey, # unique_id
                  data = tmp,
@@
                  prediction = TRUE,
-                 backtransf = TRUE,
-                 sm = "ZCOR",
+                 subgroup =  model_class_id,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor1)
+```
+
+#### Sub-division based on journals (engineering vs psych)
+
+```{r,results='asis'}
+S <- summarise(group_by(tmp,journal_type),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
+
+```{r}
+m.cor2 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  journal_type,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor2)
+```
+
+#### Sub-division based on N features
+
+```{r,results='asis'}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
+S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
+
+```{r}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
+m.cor3 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  feature_n_categories,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor3)
+S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+print(S)
+
+```
+
+#### Sub-division based on N features and genres
+
+```{r, results='asis'}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values
+
+S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+
+m.cor4 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  feature_n_complexity_genre,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor4)
+```
+
+### Arousal
+
+#### Using all models
+
+```{r}
+R_studies <- read.csv("R_studies.csv")
+tmp <- dplyr::filter(R_studies,dimension=="arousal")
+#if all studies, remove two with NA values
+tmp <- tmp[!is.na(tmp$values),]
+#dim(tmp)
+
+# Take all models
+m.cor <- metacor(cor = values,     # values 
+                 n = stimulus_n,
+                 studlab = unique_id,
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "PM",# was REML, but we switch to Paule-Mandel because Langan et al., 2019
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Arousal: Summary")
+
+print(m.cor)
+
+print(FisherZInv(m.cor$TE.random))
+print(FisherZInv(m.cor$upper.random))
+print(FisherZInv(m.cor$lower.random))
+```
+
+#### Using the best model out of each study
+
+```{r}
+R_summary <- read.csv("R_summary.csv")
+
+# select regression studies with r2
+tmp <- dplyr::filter(R_summary,dimension=="arousal")
+#tmp <- dplyr::filter(R_studies,dimension=="valence")
+#dim(tmp)
+
+#if all studies, remove two
+#tmp <- tmp[!is.na(tmp$values),]
+#dim(tmp)
+
+## Disambiguate the studies
+tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
+
+# Max values
+m.cor <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = studyREF,#citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
                  method.tau = "REML",# could be PM (Paule-Mandel) as well
@@
 print(m.cor)
-```
-### Trimmed analysis
-```{r}
-O <- find.outliers(m.cor)
+
+print(FisherZInv(m.cor$TE.random))
+print(FisherZInv(m.cor$upper.random))
+print(FisherZInv(m.cor$lower.random))
 ```
 
-#### Visualise (forest and funnel plots)
+### Explore heterogeneity
 
 ```{r}
-forest(m.cor,
+#| eval: true
+#| echo: true
+# Method 1: Give us the Egger's test about beta coefficient from funnel
+print(eggers.test(m.cor))
+
+# Method 2: Find the impact to the results when removing those outside the 95CI
+O <- find.outliers(m.cor) # 13 remaining out of 24
+print(O)
+# Method 3: Leave-out-out analysis etc for individual influence (not useful here)
+#infan <- InfluenceAnalysis(m.cor)
+
+# Method 4: Focus on 10% of most precise studies (Stanley, Jarrel, Doucouliagos 2010)
+thres<-quantile(m.cor$seTE,0.1)
+ind<-m.cor$seTE<=as.numeric(thres)
+m.cor10pct <- update(m.cor, subset = which(ind))
+
+# Method 5: P curve analysis (Simonsohn, Simmons & Nelson, 2015)
+pcurve(m.cor)
+```
+
+### Visualise (forest and funnel plots)
+
+```{r}
+#| fig-width: 12
+#| fig-height: 6
+fig2a <- forest(m.cor,
        sortvar = TE,
@@
              print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"))
-plot(eggers.test(m.cor))
+             leftlabs = c("Author", "g", "SE"),studlab = studyREF)
+
+fig2b<-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+library(forestplot)
+data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
+data<-dplyr::arrange(data,mean)
+
+fp1 <- grid.grabExpr(print(data |>
+  forestplot(labeltext = c(study, n, cor),
+             xlab = "Correlation",
+             xticks = c(0, .25,.5,.75, 1),
+             clip = c(0, 1))|>
+    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
+    fp_append_row(mean  = m.cor$TE.common,
+                lower = m.cor$lower.common,
+                upper = m.cor$upper.common,
+                study = "Summary",
+                n = sum(m.cor$n),
+                cor = round(m.cor$TE.common,2),
+                is.summary = TRUE) |>
+  fp_set_style(box = "grey50",
+               line = "grey20",
+               summary = "black",
+                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
+                                ticks = gpar(cex = 0.80),
+                                xlab  = gpar(cex = 0.80)))|>
+    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
+)
+)
+
+source('../etc/custom_funnel_plot.R')
+fp2 <- custom_funnel_plot(m.cor)
+
+gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1),heights=c(2,1))
 ```
 
-#### Explore qualities (in progress)
+### Sub-divisions
+
+#### Sub-division based on techniques
+
+```{r,results='asis'}
+S <- summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
 
 ```{r}
-#| eval: false
-meta <- metagen(valuesMax, sqrt(valuesMax), 
+m.cor1 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
                  data = tmp,
-                studlab = tmp$citekey, 
-                comb.fixed = FALSE, 
-                method.tau = "PM")
-find.outliers(meta)
-infan <- InfluenceAnalysis(meta)
-print(eggers.test(meta))
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  model_class_id,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor1)
+```
+
+#### Sub-division based on journals (engineering vs psych)
+
+```{r,results='asis'}
+S <- summarise(group_by(tmp,journal_type),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
+
+```{r}
+m.cor2 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  journal_type,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor2)
+```
+
+#### Sub-division based on N features
+
+```{r,results='asis'}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
+S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
+
+```{r}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
+m.cor3 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  feature_n_categories,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor3)
+S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+print(S)
 
@@
 
-#### Subgroup analysis according to techniques
+#### Sub-division based on N features and genres
 
-```{r}
-update(m.cor, 
-       subgroup = model_class_id, 
-       tau.common = FALSE)
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-       tau.common = FALSE)
+```{r, results='asis'}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values
 
-forest(m.cor_subgroups,subgroup=TRUE)
-```
+S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
 
-- Idea: visualise the distributions of the model successes within studies (done in preprocessing)
-
-```{r}
-#| eval: false
-g1 <- ggplot(tmp,aes(y=valuesMax,fill=model_class_id))+
-   geom_histogram(show.legend = T)+
-  facet_wrap(.~studyREF)+
-   coord_flip()+
-   theme_bw()
-g1
-
-# S <- summarise(group_by(tmp,citekey),maxvalue=max(values))
-# g<-ggplot(S,aes(y=maxvalue))+
-#   geom_histogram(bins = 14)+
-#   #facet_wrap(.~studyREF)+
-#   coord_flip()+
-#   theme_bw()
-# g
+m.cor4 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  feature_n_complexity_genre,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor4)
 ```

### 2024-10-21 manuscript/_figure2.qmd
arousal analysis included

@@
 #| fig.cap: > 
-#|   Forest and funnel plots of valence predictions from the MER models.
+#|   Forest (A) and funnel (B) plots of the best valence models from all MER studies.
 
@@
 library(ggrepel,quietly = TRUE)
+library(forestplot)
 
@@
 #### Forest plot using forestplot
-library(forestplot)
-data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
+data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=format(round(m.cor$cor, digits=3), nsmall = 3))
 data<-dplyr::arrange(data,mean)
@@
     fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
-    fp_append_row(mean  = m.cor$TE.common,
-                lower = m.cor$lower.common,
-                upper = m.cor$upper.common,
+    fp_append_row(mean  = FisherZInv(m.cor$TE.random),
+                lower = FisherZInv(m.cor$lower.random),
+                upper = FisherZInv(m.cor$upper.random),
                 study = "Summary",
                 n = sum(m.cor$n),
-                cor = round(m.cor$TE.common,2),
+                cor = round(FisherZInv(m.cor$TE.random),3),
                 is.summary = TRUE) |>

### 2024-10-21 manuscript/_figure3.qmd
arousal analysis included

@@
 R_summary <- read.csv("../analysis/R_summary.csv")
-tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp <- dplyr::filter(R_summary,dimension=="arousal")
 tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
@@
                  method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+                 title = "MER: Regression: Arousal: Summary")
 
@@
 library(forestplot)
-data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
+data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=format(round(m.cor$cor, digits=3), nsmall = 3))
 data<-dplyr::arrange(data,mean)

### 2024-10-21 manuscript/manuscript.qmd
arousal analysis included

@@
 This reduction is done to avoid the issue of multiple models from the same study deflating the results as majority of the models included are relative modest baseline or alternative models that do not represent the novelty or content of the article.
-Table 2 summarises the results for all models (All) as well as best performing models (Max) for each study.
+
+### Results for valence
+
+Table 2 summarises the results for all models (All) as well as best performing models (Max) for each study for valence.
 The summary includes the number of models and observations, the correlation coefficient and its 95% confidence interval, the t-value and p-value for the correlation, the heterogeneity statistics $\tau^2$ and $I^2$, calculated through appropriate transformations (Fisher's Z) for the correlation coefficient as part of a random-effects model using `meta` library [@balduzzi2019].
@@
 
+### Results for arousal
+
 Moving on the arousal, we carry out the same meta-analytical analysis applying the random-effects model to arousal.
-Table 3 and Figure 3 show the same outputs as was done for valence describing the broad pattern of results in tabular format, and visually illustrate the spread and heterogeneity of all studies.
-
-Table 3 indicates that the overall correlation across the studies using the best performing model out of each study (Max) is 0.807 (CI95% 0.745-0.855).
-If we examine all the models, the correlation drops to 0.796, only marginally lower.
-
-The indicators of heterogeneity ($\tau^2$ = 0.155 and $I^2$=96.8%) suggest high
+Table 3 describes the broad pattern of results in tabular format, and Figure 3 illustrates the spread and heterogeneity of all studies for arousal.
+The overall correlation across the studies using the best performing model out of each study (Max) is 0.807 (CI95% 0.745-0.855).
+If we examine all the models reported in each study, the correlation drops marginally, to 0.784 (CI95% 0.765-0.801), despite this analysis includes about five times as many models as taking the best model out of each study.
+For arousal, even the baseline models seem to be performing on a relative high level.
+However, the indicators of heterogeneity are again high ($\tau^2$ = 0.155 and $I^2$=96.8%), which suggests that summary may be misleading.
+However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.787 95%CI -4.61-6.18, _t_ = 0.286, _p_ = 0.778).
+If we remove the studies that are outside the 95%CI in heterogeneity, leaves this 14 studies in the summary that has _r_ = 0.8182 (95%CI 0.802-0.833) with $\tau^2$ = 0.0038 and $I^2$ = 76.0%.
+In other words, no material difference to the results obtained with all 24 studies.
 
@@
 |:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
-| Arousal      |             | 0.7959 \[0.7666; 0.8218\] | 29.0 | 0.0001 | 0.0676   | 95.6% |
-| Arousal Max  | 24,15660    | 0.8070 \[0.7453; 0.8550\] | 10.3 | 0.0001 | 0.155    | 96.8% |
+| Arousal All  | 126, 74365  | 0.7837 \[0.7652-0.8009\]  | 45.2 | 0.0001 | 0.064    | 96.3% |
+| Arousal Max  | 24, 15660   | 0.8070 \[0.7453-0.8550\]  | 14.8 | 0.0001 | 0.128    | 97.7% |
 | *N Features* |             |                           |      |        |          |       |
-| \<18 F       |             |                           |      |        |          |       |
-| 18-260 F     |             |                           |      |        |          |       |
-| 260+ F       |             |                           |      |        |          |       |
+| \<18 F       | 5, 3036     | 0.8111 \[0.5342-0.9308\]  |      |        | 0.1815   | 98.9% |
+| 18-260 F     | 11, 7318    | 0.5477 \[0.3434-0.7025\]  |      |        | 0.1331   | 97.6% |
+| 260+ F       | 7, 4562     | 0.6845 \[0.5660-0.7752\]  |      |        | 0.0435   | 97.2% |
 | *Techniques* |             |                           |      |        |          |       |
-| KS           |             |                           |      |        |          |       |
-| LM           |             |                           |      |        |          |       |
-| FD           |             |                           |      |        |          |       |
-| NN           |             |                           |      |        |          |       |
-| RF           |             |                           |      |        |          |       |
+| KS           | 2, 2582     | 0.8068 \[0.5493-0.9244\]  |      |        | 0.0022   | 70.0% |
+| LM           | 8, 1762     | 0.8812 \[0.8079-0.9277\]  |      |        | 0.0846   | 93.3% |
+| FD           | 6, 4993     | 0.8077 \[0.6437-0.9008\]  |      |        | 0.1125   | 98.0% |
+| NN           | 4, 2249     | 0.5339 \[0.3281-0.6912\]  |      |        | 0.0190   | 85.8% |
+| RF           | 4, 4074     | 0.8024 \[0.7672-0.8327\]  |      |        | 0.0012   | 52.7% |
 
-<!-- {{< include _figure3.qmd >}} -->
+The forest plot in Figure 3 reveals
 
-Summarise here the pattern of results
+The subdivision of studies shows...
+
+{{< include _figure3.qmd >}}
 

### 2024-10-22 analysis/preprocessing.qmd
arousal analysis included
feat(preprocessing): update R_studies build
Drop resonance(deng2015em), tension arousal (wang2022cr, wang2021ac), Remove NAs from values column (zhang2017fe, zhang2016br, gingras2014be). Fix unique_ids for hu2016cr

@@
 ```
+2024-10-21: Update studies with multiple unique_ids due to multiple stats reported
+```{r}
+metaMER_results <- metaMER_results |> 
+  dplyr::filter(!(citekey == "zhang2017fe" & statistic == "mean"),
+         !(citekey == "zhang2016br" & statistic == "mean"),
+         !(citekey == "zhang2016br" & is.na(values)),
+         !(citekey == "coutinho2017sh" & statistic == "ccc"),
+         # Include only results for energy arousal
+         !(citekey == "wang2022cr" & dimension == "tension arousal"),
+         !(citekey == "wang2021ac" & dimension == "tension arousal"),
+         !(citekey == "deng2015em" & dimension == "resonance"))
+```
+Deal with repeated experiment IDs in `hu2017cr`
+```{r}
+
+# get citation keys (all currently say experiment 1)
+hu2017models <- metaMER_results[str_detect(metaMER_results$citekey, 
+                                           "hu2017cr"),]$unique_id
+
+# replace the last digit with 1:4 (representing each experiment)
+hu2017models_replacement <- paste0(
+substr(hu2017models, 
+       1, 
+       nchar(hu2017models) - 1),
+1:4
+)
+
+# overwrite original values
+metaMER_results[metaMER_results$unique_id %in% 
+                  hu2017models,]$unique_id <- hu2017models_replacement
+```
 
@@
 ```
+## Remove NAs
+
+```{r}
+R_studies <- R_studies[!is.na(R_studies$values),]
+
+```
+
+## Check models aren't double-counted
+
+```{r}
+length(unique(paste0(R_studies$unique_id, R_studies$dimension)))
+
+ez::ezDesign(data = R_studies, x = unique_id, y = citekey)
+
+```
 
@@
 ```{r}
-R_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal'
+R_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal' # note: there is no longer "tension arousal" based on decision to include only energy
 R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
@@
 ```
+
+## Feature N and genre split
+
+```{r}
+quantile(subset(R_studies,stimulus_genre_mixed=='SingleGenre')$feature_n,probs = seq(0,1,0.333))
+quantile(subset(R_studies,stimulus_genre_mixed=='MultiGenre')$feature_n,na.rm=TRUE,probs = seq(0,1,0.333))
+
+# a combination of the two
+R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
+                                      breaks = c(0,15,501,653,10000),
+                                      labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
+table(R_studies$feature_n_complexity_genre)
+```
+
 ## Select a summary measure for valence and arousal separately
@@
 
+R_studies$feature_n[str_detect(R_studies$feature_n,'150 PCA features')] <- 3000
 R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting = 21')] <- 21
@@
 
-R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')] <- 3000 # under-estimation based openSmile features and the paper arguing that they have 15 stat moments
+# 2024-10-21: I changed the encoding for this one to "150 PCA features", so updated above.
+# R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')] <- 3000 # under-estimation based openSmile features and the paper arguing that they have 15 stat moments
 
@@
 ```
+
 ## Feature N and genre split

### 2024-10-24 manuscript/manuscript.qmd
checking the number of models and studies table 1

@@
 |:-----------|:--------------------------------|:--------------------------|:------|
-| Study N    | 24                              | 14                        | 38    |
-| Model N    | 258                             | 108                       | 366   |
-| Techniques | Flexible Discriminants (FD): 64 | 37                        | 101   |
-| Techniques | Neural Nets (NN): 74            | 27                        | 101   |
-| Techniques | Linear Methods (LM): 74         | 24                        | 98    |
-| Techniques | Random Forests (RF): 22         | 12                        | 34    |
+| Study N    | 23                              | 14                        | 37    |
+| Model N    | 236                             | 119                       | 355   |
+| Techniques | Flexible Discriminants (FD): 58 | 37                        | 101   |
+| Techniques | Neural Nets (NN): 70            | 29                        | 101   |
+| Techniques | Linear Methods (LM): 62         | 17                        | 98    |
+| Techniques | Random Forests (RF): 22         | 15                        | 34    |
 | Techniques | KS, Add. & KNN (KS): 24         | 8                         | 32    |
-| Feature N  | Min=3, Md=472.5, Max=654        | Min=3, Md=231, Max=8904   | NA    |
-| Stimulus N | Min=40, Md=324, Max=2486        | Min=124, Md=387, Max=5192 | NA    |
+| Feature N  | Min=3, Md=548, Max=6670         | Min=3, Md=126, Max=8904   | NA    |
+| Stimulus N | Min=20, Md=330, Max=2486        | Min=124, Md=387, Max=5192 | NA    |
 
-Although the total number of studies meeting the criteria described in the previous section is modest (38 in total), they encompass a large array of models (366 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
+Although the total number of studies meeting the criteria described in the previous section is modest (37 in total), they encompass a large array of models (366 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
 The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 9000 features [@zhang2023mo].

### 2024-10-25 analysis/preprocessing.qmd
checking the number of models and studies table 1
feat(preprocessing): average V and A accuracy classification
update encoding for alvarez to include validation model in mcc conversion. take average of valence and arousal classification for hu2022de, zhang2016br

@@
 library(stringr)
+library(tidyverse)
+library(ggrepel)
+library(ez)
+library(ggdist)
+
 # get metaMER df:
@@
 #| eval: true
-library(stringr)
 metaMER_results$studyREF <- substr(metaMER_results$citekey,1,nchar(metaMER_results$citekey)-2)
@@
 #
-library(stringr)
 metaMER_results$model_id <- tolower(metaMER_results$model_id)
@@
 # note that we have some classification studies that also do regression and vice versa?
-# THIS IS CORRECT (updated 12 July 2024):
-# [1] "We have 1238 observations"
-# [1] "We have 37 studies"
-# [1] "Where 23 are regression studies"
+# THIS IS CORRECT (updated 24 October 2024):
+# [1] "We have 1284 observations"
+# [1] "We have 36 studies"
+# [1] "Where 22 are regression studies"
 # [1] "Where 14 are classification studies"
@@
 
-ez::ezDesign(data = R_studies, x = unique_id, y = citekey)
+ez::ezDesign(data = R_studies, x = unique_id, y = citekey)+
+  theme(axis.text.x = element_blank(),
+        axis.title.x = element_blank())
 
@@
 ```{r}
-library(ggplot2)
 
@@
 ```{r}
-library(tidyverse)
 R_studies$citekey <- factor(R_studies$citekey)
@@
 R_studies_split<-drop_na(R_studies_split)
-
-library(ggrepel)
 
@@
 
-library(ggdist)
-
 tmp$dimension<-str_to_title(tmp$dimension)
@@
 
-## Create descriptive table for the manuscript
+## Create descriptive table for the manuscript  (Table 1, column 1)
 
@@
 C_studies$accuracy_converted_to_mcc <- 0
-C_studies$accuracy_converted_to_mcc[C_studies$citekey=='bai2016di' | 
+C_studies$accuracy_converted_to_mcc[
+                  C_studies$unique_id==
+'alvarez2023ri-spotify-randomforest-spotify-acousticBrainz-modelvalidation'|
+                  C_studies$citekey=='bai2016di' | 
                   C_studies$citekey=='bai2017mu' | 
@@
 
-C_studies$measure[C_studies$citekey=='bai2016di' | 
+C_studies$measure[C_studies$unique_id==
+'alvarez2023ri-spotify-randomforest-spotify-acousticBrainz-modelvalidation'|
+                  C_studies$citekey=='bai2016di' | 
                   C_studies$citekey=='bai2017mu' | 
@@
 dim(C_studies)
+
+C_studies <- C_studies[!is.na(C_studies$values),]
+
 table(C_studies$measure,C_studies$accuracy_converted_to_mcc)
@@
 ```
+
+# Average across valence and arousal for VA classification
+
+```{r}
+
+length(unique(paste0(C_studies$unique_id, C_studies$dimension)))
+
+ez::ezDesign(data = C_studies, x = unique_id, y = citekey)+
+  theme(axis.text.x = element_blank(),
+        axis.title.x = element_blank())
+
+```
+
+```{r}
+va_studies <- c("zhang2016br", "hu2022de")
+
+va_acc <- C_studies |> 
+  filter(citekey %in% va_studies) |> 
+  group_by(unique_id, measure, statistic) |> 
+  mutate(values = mean(values), 
+         accuracy_converted_to_mcc = mean(accuracy_converted_to_mcc))
+
+va_acc$dimension <- "classification"
+
+va_acc <- va_acc |> distinct()
+
+C_studies <- C_studies[!C_studies$citekey %in% va_studies,]
+
+C_studies <- rbind(C_studies, va_acc)
+
+```
+
+### Revisualize studies
+```{r}
+
+length(unique(paste0(C_studies$unique_id, C_studies$dimension)))
+
+ez::ezDesign(data = C_studies, x = unique_id, y = citekey)+
+  theme(axis.text.x = element_blank(),
+        axis.title.x = element_blank())
+
+```
+
 #### Get the number of categories in the classification task
@@
 #| eval: false
-library(ggplot2)
 
@@
 ```{r}
-library(tidyverse)
 C_studies$citekey <- factor(C_studies$citekey)
@@
 C_studies$citekey<-factor(C_studies$citekey)
-
-library(ggrepel)
 
@@
 tmp <- drop_na(C_studies)
-library(ggdist)
 
@@
 
-## Create descriptive table for the manuscript
+## Create descriptive table for the manuscript (Table 1, column 2)
+
+CA: I think this should be correct, though may need to update after averaging across VA for some classification studies (zhang2016, hu2022)
 

### 2024-10-27 manuscript/manuscript.qmd
Minor tweaks
preprocessing simplified

@@
 |:-----------|:--------------------------------|:--------------------------|:------|
-| Study N    | 23                              | 14                        | 37    |
-| Model N    | 236                             | 119                       | 355   |
-| Techniques | Flexible Discriminants (FD): 58 | 37                        | 101   |
-| Techniques | Neural Nets (NN): 70            | 29                        | 101   |
-| Techniques | Linear Methods (LM): 62         | 17                        | 98    |
-| Techniques | Random Forests (RF): 22         | 15                        | 34    |
+| Study N    | 21                              | 14                        | 36    |
+| Model N    | 236                             | 103                       | 339   |
+| Techniques | Flexible Discriminants (FD): 58 | 30                        | 86    |
+| Techniques | Neural Nets (NN): 70            | 28                        | 98    |
+| Techniques | Linear Methods (LM): 62         | 13                        | 75    |
+| Techniques | Random Forests (RF): 22         | 14                        | 36    |
 | Techniques | KS, Add. & KNN (KS): 24         | 8                         | 32    |
-| Feature N  | Min=3, Md=548, Max=6670         | Min=3, Md=126, Max=8904   | NA    |
+| Feature N  | Min=3, Md=548, Max=6670         | Min=3, Md=397, Max=8904   | NA    |
 | Stimulus N | Min=20, Md=330, Max=2486        | Min=124, Md=387, Max=5192 | NA    |
 
-Although the total number of studies meeting the criteria described in the previous section is modest (37 in total), they encompass a large array of models (366 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
+Although the total number of studies meeting the criteria described in the previous section is modest (36 in total), they encompass a large array of models (339 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
 The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 9000 features [@zhang2023mo].
-The median number of features differs between regression (473) and classification (231) studies, primarily reflecting the nature of the datasets used in each approach.
-The number of stimuli is typically around 300-400 (with a median of 324 for regression and 387 for classification), though there is substantial variation, with the extremes from 40 stimuli in @saizclar2022pr to 5192 stimuli in @alvarez2023ri.
+The median number of features differs between regression (548) and classification (397) studies, primarily reflecting the nature of the datasets used in each approach.
+The number of stimuli is typically around 300-400 (with a median of 330 for regression and 387 for classification), though there is substantial variation, with the extremes from 40 stimuli in @saizclar2022pr to 5192 stimuli in @alvarez2023ri.
 There are also additional dimensions to consider, such as the type of cross-validation used, the music genres analyzed (whether a single genre, multiple genres, or a mix), the type of journal in which the studies were published, and the source of the extracted features.
 However, these variables do not lend themselves to a simple summary, so we will revisit them during the interpretation and discussion stages.
-\[COMMENT: IT MIGHT BE WORTWHILE TO SUMMARISE SOME OF THESE HERE\].
 
@@
 |:-------------|:------------|:------------------------|:------|:------|:---------|:------|
-| Valence All  | 120,73685   | 0.567 \[0.530; 0.603\]  | 23.7  | .0001 | 0.083    | 97.5% |
-| Valence Max  | 24,15660    | 0.659 \[0.557; 0.740\]  | 10.14 | .0001 | 0.138    | 98.2% |
+| Valence All  | 90,61733    | 0.609 \[0.570-0.650\]   | 23.3  | .0001 | 0.079    | 97.3% |
+| Valence Max  | 21,13572    | 0.680 \[0.575-0.762\]   | 9.96  | .0001 | 0.136    | 98.2% |
 | *N Features* |             |                         |       |       |          |       |
-| \<18 F       | 5,3036      | 0.811 \[0.566; 0.???\]  | \-    | \-    | 0.182    | 98.9% |
-| 18-260 F     | 11,7318     | 0.548 \[0.343; 0.703\]  | \-    | \-    | 0.133    | 97.6% |
-| 260+ F       | 7,4562      | 0.685 \[0.566; 0.775\]  | \-    | \-    | 0.044    | 97.2% |
+| \<18 F       | 5,3036      | 0.811 \[0.542-0.823\]  | \-    | \-    | 0.182    | 98.9% |
+| 18-260 F     | 11,7042     | 0.584 \[0.534-0.931\]  | \-    | \-    | 0.133    | 97.6% |
+| 260+ F       | 5,3494      | 0.710 \[0.542-0.823\]  | \-    | \-    | 0.044    | 97.2% |
 | *Techniques* |             |                         |       |       |          |       |
-| KS           | 2,2582      | 0.466 \[-0.634; 0.942\] | \-    | \-    | 0.0185   | 95.1% |
-| LM           | 8,1762      | 0.784 \[0.625; 0.881\]  | \-    | \-    | 0.1370   | 96.4% |
-| FD           | 6,4993      | 0.656 \[0.484; 0.779\]  | \-    | \-    | 0.0574   | 96.9% |
-| NN           | 4,2249      | 0.340 \[-0.097; 0.668\] | \-    | \-    | 0.0761   | 97.1% |
-| RF           | 4,4074      | 0.702 \[0.391; 0.869\]  | \-    | \-    | 0.057    | 98.5% |
+| KS           | 2,2582      | 0.466 \[-0.634-0.942\]  | \-    | \-    | 0.0185   | 95.1% |
+| LM           | 7,1438      | 0.797 \[0.614-0.899\]   | \-    | \-    | 0.1370   | 96.4% |
+| FD           | 6,4993      | 0.656 \[0.484-0.779\]  | \-    | \-     | 0.0574   | 96.9% |
+| NN           | 3,1229      | 0.393 \[-0.355-0.835\] | \-    | \-     | 0.0761   | 97.1% |
+| RF           | 3,3330      | 0.750 \[0.292-0.928\]  | \-    | \-     | 0.093    | 98.5% |
 
@@
 |:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
-| Arousal All  | 126, 74365  | 0.7837 \[0.7652-0.8009\]  | 45.2 | 0.0001 | 0.064    | 96.3% |
-| Arousal Max  | 24, 15660   | 0.8070 \[0.7453-0.8550\]  | 14.8 | 0.0001 | 0.128    | 97.7% |
+| Arousal All  | 90, 61733   | 0.795 \[0.774-0.814\]     | 39.4 | 0.0001 | 0.064    | 96.3% |
+| Arousal Max  | 21, 13572   | 0.815 \[0.749-0.865\]     | 14.0 | 0.0001 | 0.131    | 97.7% |
 | *N Features* |             |                           |      |        |          |       |
-| \<18 F       | 5, 3036     | 0.8111 \[0.5342-0.9308\]  |      |        | 0.1815   | 98.9% |
-| 18-260 F     | 11, 7318    | 0.5477 \[0.3434-0.7025\]  |      |        | 0.1331   | 97.6% |
-| 260+ F       | 7, 4562     | 0.6845 \[0.5660-0.7752\]  |      |        | 0.0435   | 97.2% |
+| \<18 F       | 5, 3036     | 0.811 \[0.534-0.931\]     |      |        | 0.1815   | 98.9% |
+| 18-260 F     | 11, 7042    | 0.584 \[0.534-0.931\]     |      |        | 0.1331   | 97.6% |
+| 260+ F       | 5, 3494     | 0.710 \[0.542-0.823\]     |      |        | 0.0435   | 97.2% |
 | *Techniques* |             |                           |      |        |          |       |
-| KS           | 2, 2582     | 0.8068 \[0.5493-0.9244\]  |      |        | 0.0022   | 70.0% |
-| LM           | 8, 1762     | 0.8812 \[0.8079-0.9277\]  |      |        | 0.0846   | 93.3% |
-| FD           | 6, 4993     | 0.8077 \[0.6437-0.9008\]  |      |        | 0.1125   | 98.0% |
-| NN           | 4, 2249     | 0.5339 \[0.3281-0.6912\]  |      |        | 0.0190   | 85.8% |
-| RF           | 4, 4074     | 0.8024 \[0.7672-0.8327\]  |      |        | 0.0012   | 52.7% |
+| KS           | 2, 2582     | 0.807 \[0.549-0.924\]     |      |        | 0.0022   | 70.0% |
+| LM           | 7, 1438     | 0.885 \[0.796-0.936\]     |      |        | 0.0846   | 93.3% |
+| FD           | 6, 4993     | 0.808 \[0.644-0.901\]    |      |        | 0.1125   | 98.0% |
+| NN           | 3, 1229     | 0.533 \[0.082-0.803\]     |      |        | 0.0190   | 85.8% |
+| RF           | 3, 3330     | 0.809 \[0.733-0.864\]  |      |        | 0.0012   | 52.7% |
 
@@
 -   Figure Optional: Funnel plot (I haven't seen this yet)
+
+###
+
+secondary datasets, include a table, with an index of which studies/counts
+
+TABLE
 

### 2024-11-06 analysis/analysis.qmd
feat(analysis): indicate class_n in classification studies
feat(analysis): begin analysis by class n

@@
 C_summary <- read.csv("C_summary.csv")
+C_classes <- read.csv("C_study_class_n.csv")
+
+C_summary <- merge(C_summary, C_classes)
 
@@
 ```{r}
+forest(m.cor,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "g", "SE"),studlab = citekey)
+
+funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+```
+#### By class n = 2 vs. > 2
+```{r}
+C_summary$classes <- 0
+C_summary[C_summary$n_classes < 3,]$classes <- "2"
+C_summary[C_summary$n_classes >= 3,]$classes <- ">2"
+
+m.cor <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n, # could also change to n_classes
+                 studlab = studyREF, # unique_id
+                 data = C_summary,
+                 subgroup = classes,
+                 fixed = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 backtransf = TRUE,
+                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Classification: Summary")
+
 forest(m.cor,

### 2024-11-25 analysis/preprocessing.qmd
fix(preprocessing): recover coutinho2017sh in r_studies

@@
          !(citekey == "zhang2016br" & is.na(values)),
-         !(citekey == "coutinho2017sh" & statistic == "ccc"),
+         !(citekey == "coutinho2017sh" & measure == "ccc"),
          # Include only results for energy arousal

### 2024-11-25 analysis/preprocessing.qmd
Revert "fix(preprocessing): recover coutinho2017sh in r_studies"
This reverts commit f43eababf288cbdb9e9a8ad36d89a2c3b1a1ccdb.

@@
 
+```{r}
+#| warning: false
+#| echo: false
+#| eval: true
+# Set parameters and libraries
+export_decision <- TRUE
+verbose <- FALSE
+require(here)
+library(stringr)
+library(tidyverse)
+library(ggrepel)
+library(ez)
+library(ggdist)
+```
+
 ## Read annotated data
@@
 ```{r}
-#| warning: false
-require(here)
+#| echo: true
 source(here::here('R/build-df.R'))
@@
 ```{r}
-#| warning: false
-library(stringr)
-library(tidyverse)
-library(ggrepel)
-library(ez)
-library(ggdist)
-
+#| echo: true
 # get metaMER df:
@@
   dplyr::tibble()
-
 ```
@@
 # add unique identifiers
-
 unique_id <- apply(metaMER_results[,c('citekey',
@@
 metaMER_results |> dplyr::tibble()
-
 ```
@@
 #| eval: true
+#| echo: false
 # Classify techniques according Hastie, Tibshirani, Friedman (2008)
@@
 #| eval: true
+#| echo: false
 metaMER_results$stimulus_genre_mixed <- 'SingleGenre'
@@
 ```{r}
+#| echo: false
+#| eval: true
 metaMER_results$journal_type <- "Engineering"
@@
 2024-10-21: Update studies with multiple unique_ids due to multiple stats reported
+
 ```{r}
+#| echo: true
+#| eval: true
+
 metaMER_results <- metaMER_results |> 
@@
          !(citekey == "zhang2016br" & is.na(values)),
-         !(citekey == "coutinho2017sh" & measure == "ccc"),
+         !(citekey == "coutinho2017sh" & statistic == "ccc"),
          # Include only results for energy arousal
@@
 ```{r}
+#| echo: true
+#| eval: true
 
@@
 ```{r}
+#| echo: false
+#| eval: true
 
@@
 
-R_studies <- dplyr::filter(metaMER_results, measure %in% c('r','ccc','pcc','cc','r2','R2')) #
+length(unique(metaMER_results$citekey[metaMER_results$model_category=='regression']))
+
+R_studies <- dplyr::filter(metaMER_results, measure %in% c('r','ccc','pcc','cc','r2','R2') & model_category=="regression") # brings some classification studies!
+I have added an additional filter for model category
+# Cameron: Can you check that this is correct now?
 
@@
 R_studies <- dplyr::filter(R_studies,str_detect(statistic,'adjusted|ccc|pcc|cc|globalOptimal|localOptimal|mean|r2|r'))
-dim(R_studies)
-table(R_studies$measure)
+#dim(R_studies)
+#table(R_studies$measure)
 
-table(R_studies$measure, R_studies$statistic)
+#table(R_studies$measure, R_studies$statistic)
 
@@
 ```{r}
+#| echo: true
+#| eval: true
 R_studies <- R_studies[!is.na(R_studies$values),]
-
 ```
@@
 ```{r}
+#| echo: true
+#| eval: true
+
 length(unique(paste0(R_studies$unique_id, R_studies$dimension)))
@@
 ```{r}
+#| echo: false
+#| eval: true
+
 R_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal' # note: there is no longer "tension arousal" based on decision to include only energy
@@
 
-table(R_studies$dimension)
+#table(R_studies$dimension)
 
@@
 
-table(R_studies$stimulus_n)
+#table(R_studies$stimulus_n)
 
 R_studies$stimulus_n <- as.numeric(R_studies$stimulus_n)
+
+length(unique(metaMER_results$citekey[metaMER_results$model_category=='regression']))
 
@@
 ```{r}
-
+#| echo: false
+#| eval: false
 g1<-ggplot(R_studies,aes(x=values,fill=citekey,color=dimension))+
@@
   facet_wrap(.~model_class_id)+
-#  scale_color_manual(values = c('black','white'))+
   theme_dark()+
   scale_x_continuous(breaks = seq(0,1,by=.1))
-
-g1
+print(g1)
 ```
@@
 ```{r}
+#| echo: false
+#| eval: true
+
 quantile(subset(R_studies,stimulus_genre_mixed=='SingleGenre')$feature_n,probs = seq(0,1,0.333))
@@
                                       labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
-table(R_studies$feature_n_complexity_genre)
+#table(R_studies$feature_n_complexity_genre)
 ```
@@
 ```{r}
-R_studies$citekey <- factor(R_studies$citekey)
+#| echo: true
+#| eval: true
+R_studies$citekey <- factor(R_studies$citekey) # 21 unique values
 R_studies$dimension <- factor(R_studies$dimension)
@@
 
+print(dim(R_summary))
 ```
@@
 ```{r}
+#| echo: false
+#| eval: false
+
 R_summary_split <- pivot_wider(R_summary,id_cols = citekey, names_from = c(dimension), values_from = valuesMax)
@@
   scale_y_continuous(breaks = seq(0,1,by=.1))
-
-g2
+print(g2)
 
@@
   theme_bw()
-g3
-
+print(g3)
 ```
@@
 ```{r}
-#| eval: true
+#| eval: false
+#| echo: false
 # Add year!
@@
   theme_bw()
-g3
+print(g3)
 ```
@@
 
-table(R_studies$feature_n_complexity)
+#table(R_studies$feature_n_complexity)
 ```
@@
 ```{r}
+#| echo: false
+#| eval: true
 quantile(subset(R_studies,stimulus_genre_mixed=='SingleGenre')$feature_n,probs = seq(0,1,0.333))
@@
 ```{r}
+#| echo: false
+#| eval: false
+
 #tmp <- drop_na(R_studies)
@@
 ```{r}
+#| echo: true
+#| eval: true
+
 TR <- NULL
@@
 ```{r}
+#| echo: true
+#| eval: true
+if (export_decision == TRUE){
   write.csv(x = R_studies,file = 'R_studies.csv')
   write.csv(x = R_summary,file = 'R_summary.csv')
+}
 ```
@@
 ```{r}
+#| echo: false
+#| eval: true
+
 C_studies<-metaMER_results
-sum(is.na(C_studies$measure)) # 0
-sum(is.na(C_studies$statistic)) # 426
+sum(is.na(C_studies$measure)) 
+sum(is.na(C_studies$statistic))
 
@@
 C_studies <- dplyr::filter(C_studies, str_detect(statistic,'mean|median|acc')) #  
-dim(C_studies)
+#dim(C_studies)
 length(unique(C_studies$citekey))
 
-table(C_studies$measure,C_studies$statistic)
-table(C_studies$measure,C_studies$citekey)
-table(C_studies$statistic,C_studies$citekey)
+#table(C_studies$measure,C_studies$statistic)
+#table(C_studies$measure,C_studies$citekey)
+#table(C_studies$statistic,C_studies$citekey)
 
@@
 C_studies$measure[C_studies$citekey=='hu2022de' & C_studies$measure=='f1']<-'accuracy'
-dim(C_studies)
+#dim(C_studies)
 C_studies <- dplyr::filter(C_studies, str_detect(measure,'mcc|accuracy')) #  
-dim(C_studies)
-table(C_studies$measure,C_studies$citekey)
+#dim(C_studies)
+#table(C_studies$measure,C_studies$citekey)
 
@@
                   & C_studies$measure=='accuracy']<-'mcc'
-table(C_studies$measure,C_studies$citekey)
+#table(C_studies$measure,C_studies$citekey)
 C_studies <- dplyr::filter(C_studies, str_detect(measure,'mcc')) #  
-dim(C_studies)
+#dim(C_studies)
 
@@
 
-table(C_studies$measure,C_studies$accuracy_converted_to_mcc)
-t.test(C_studies$values,y = C_studies$accuracy_converted_to_mcc) # There is a difference
+#table(C_studies$measure,C_studies$accuracy_converted_to_mcc)
+#t.test(C_studies$values,y = C_studies$accuracy_converted_to_mcc) # There is a difference
+
+length(unique(C_studies$citekey))
 
@@
 
-# Average across valence and arousal for VA classification
+## Average across valence and arousal for VA classification
 
 ```{r}
+#| echo: true
+#| eval: true
 
-length(unique(paste0(C_studies$unique_id, C_studies$dimension)))
+#length(unique(paste0(C_studies$unique_id, C_studies$dimension)))
 
@@
 ```{r}
+#| echo: true
+#| eval: true
+
 va_studies <- c("zhang2016br", "hu2022de")
@@
 C_studies <- C_studies[!C_studies$citekey %in% va_studies,]
-
 C_studies <- rbind(C_studies, va_acc)
@@
 ### Revisualize studies
+
 ```{r}
+#| echo: true
+#| eval: true
 
@@
         axis.title.x = element_blank())
-
 ```
@@
 ```{r}
+#| echo: true
+#| eval: true
+
 tmp <- metaMER_results
@@
 ```{r}
-table(C_studies$stimulus_n)
+#| echo: false
+#| eval: true
+
+#table(C_studies$stimulus_n)
 
@@
 ```{r}
+#| echo: false
 #| eval: false
@@
   scale_x_continuous(breaks = seq(0,1,by=.1))
-
-g1
+print(g1)
 ```
@@
 ```{r}
+#| echo: true
+#| eval: true
+
 C_studies$citekey <- factor(C_studies$citekey)
@@
 ```{r}
+#| echo: false
+#| eval: false
 
@@
 ```{r}
-table(C_studies$feature_n)
+#| echo: false
+#| eval: true
+
+#table(C_studies$feature_n)
 C_studies$feature_n[str_detect(C_studies$feature_n,'eight different ')]<-600 # arbitrary!
@@
 C_studies$feature_n[str_detect(C_studies$feature_n,'summarize feature')]<-600 # arbitrary
-table(C_studies$feature_n)
+#table(C_studies$feature_n)
 
@@
 
-ggplot(C_studies,aes(x=feature_n))+geom_histogram()
+#ggplot(C_studies,aes(x=feature_n))+geom_histogram()
 
@@
                                       labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))
-table(C_studies$feature_n_complexity)
+#table(C_studies$feature_n_complexity)
 ```
@@
 ```{r}
-#| eval: true
+#| echo: false
+#| eval: false
+
 tmp <- drop_na(C_studies)
-
 tmp$dimension<-str_to_title(tmp$dimension)
@@
 ```{r}
+#| echo: true
+#| eval: true
+
 TC <- NULL
@@
 ```{r}
+#| echo: true
+#| eval: true
+if (export_decision == TRUE){
   write.csv(x = C_studies,file = 'C_studies.csv')
   write.csv(x = C_summary,file = 'C_summary.csv')
+}
 ```

### 2024-12-12 studies/library_parser.qmd
fix(library_parser): update examples, remove outdated code

--- 2024-06-17 studies/library_parser.qmd
@@
 ---
-
-**Status:** in progress.
-
-**TODO**: \
-- Separate scripts and functions into separate .qmd files/directories. \
-- Update `model_rate_emotion_values` nomenclature process for classification papers.\
-- Replace rbind with custom bind function throughout
 
@@
 library(knitr, include.only = 'kable')
+source(paste0(here::here(), "/R/format-study-results.R"))
+source(paste0(here::here(), "/R/parse-model-output.R"))
+
 ```
@@
 ## AT LEAST 2 MISSING FIELDS
-check_missing(2) -> missing_2
-
-missing_2 |> dplyr::tibble()
-```
-
-```{r}
+check_missing(2) |> dplyr::tibble()
 ## AT LEAST 3 MISSING FIELDS
@@
 
-# Outdated: Dealing with nested bibtex fields.
+# Parsing Studies
 
-Some studies include multiple bibtex fields for substudies/evaluations of different feature sets.
-E.g., `MODEL_RATE_EMOTION_VALUES_A` and `MODEL_RATE_EMOTION_VALUES_B`.
-We need to apply special operations to separate these values for further analysis.
-
-```{r eval = F, echo = F}
-## function to parse output of multiple models nested within a single cell
-parse_model_output = function(df)
-{ # loop across rows
-  # apply function to replace NAs with empty string
-  sapply(1:nrow(df), function(x) {
-    df$model_rate_emotion_values <- tidyr::replace_na(df$model_rate_emotion_values, '') # detect cells with rbind in them
-    if(str_count(df$model_rate_emotion_values[x], "rbind") > 1) {
-      # match first model (name between first underscore and rbind)
-      model_1_name <- str_match(df$model_rate_emotion_values[x], 
-                                "(?<=_).*?(?=rbind)")
-      # match subsequent models (name between MODEL_RATE_EMOTION_VALUES_ and rbind)
-      model_names <- str_extract_all(df$model_rate_emotion_values[x], 
-                                     "(?<=MODEL_RATE_EMOTION_VALUES_).*?(?=rbind)")
-      # combine names
-      model_names <- unlist(c(model_1_name, model_names))
-      # remove special characters
-      model_names <- gsub("[^[:alnum:]]", "", model_names)
-      # get corresponding values for each model
-      model_results <- str_split(df$model_rate_emotion_values[x], 
-                "MODEL_RATE_EMOTION_VALUES")
-      # get rid of everything up to "rbind"
-      model_results <- lapply(model_results, function(x) str_remove(x, 
-                                                          '.+?(?=rbind)'))
-      # now unlist the models and give them names to add later
-      model_results <- unlist(model_results)
-       model_results <- paste(model_names, '=', model_results)
-      names(model_results) <- model_names
-     # return(model_results)
-    }
-    else { # otherwise, if dealing with non-listed, just return the existing value
-      model_results <- df$model_rate_emotion_values[x]
-    }
-    return(model_results)
-  }
-    )
-  # see whether rbind appears multiple times
-
-}
-
-# get results from nested models:
-model_outputs <- parse_model_output(meta_df)
-# assign unique names
-model_names <- lapply(model_outputs, names)
-
-```
-
-## Data Frame Expansion
-
-Next we want to copy the number of rows for each of the bibtex cells requiring special nesting
-
-```{r eval = F, echo = F}
-# count the numbers 
-n_entries <- unlist(lapply(model_outputs, function(x) length(x)))
-# for those returning 0, change value to 1
-n_entries[n_entries == 0]<- 1
-# replicate rows based on number of models reported
-meta_df_unpacked <- meta_df[rep(seq_len(nrow(meta_df)), n_entries), ]
-# now overwrite model_rate_emotion_values with the output of parse_model_output
-meta_df_unpacked$model_rate_emotion_values <- unlist(model_outputs)
-
-```
-
-## Sanity check
-
-```{r eval = F, echo = F}
-# ex_substudy_1 <- eval(parse(text = meta_df_unpacked[7, 'model_rate_emotion_values']))
-# ex_substudy_2 <- eval(parse(text = meta_df_unpacked[8, 'model_rate_emotion_values']))
-```
-
-## Print output of all studies:
-
-```{r eval = F, echo = F}
-sapply(1:nrow(meta_df_unpacked), function(i) {
-  print(i) 
-  print(eval(parse(text = meta_df_unpacked$model_rate_emotion_values[i])))
-}
-)
-```
-
-```{r eval = F, echo = F}
-classification_studies = subset(meta_df_unpacked, paradigm == " classification  ")
-
-sapply(1:nrow(classification_studies), function(i) {
-  print(i) 
-  print(eval(parse(text = classification_studies$model_rate_emotion_values[i])))
-}
-)
-```
-
-```{r eval = F, echo = F}
-regression_studies = subset(meta_df_unpacked, paradigm == " regression  ")
-
-sapply(1:nrow(regression_studies), function(i) {
-  print(i) 
-  print(eval(parse(text = regression_studies$model_rate_emotion_values[i])))
-}
-)
-```
+The following functions provide a working example for converting the *R* code contained in `model_rate_emotion_values` to a data frame for further analysis.
+`get_study_summaries` is a simple function to demonstrate how the preprocessing routines work in the following examples
 
 ```{r}
-# low-level function to extract relevant values from named array
-model_result_2_df <- function(x) {
-  # evaluate the expression
-  x <- rlang::eval_tidy(rlang::parse_expr(x))
-  # get name of fitted models from column names
-  model_names <- colnames(x)
-  # print(model_names)
-  # split across model name for summary statistic (e.g., mean, sd, etc.)
-  model_statistic <- str_split(model_names, '\\.')
-  model_statistic <- unlist(lapply(model_statistic, function(x) x[2]))
-  # get values
-  model_values <- as.numeric(x)
-  # names(model_values) <- 'score'
-  print(model_values)
-  # get additional attributes (feature.data.exp)
-  model_attributes <- rownames(x)
-  data.frame(model_attributes)
-  # get additional model details
-  model_attributes <- data.frame(do.call('rbind', str_split(model_attributes, '\\.')))
-  names(model_attributes) <- c('library_id', 'model_id', 'feature_id', 'data_id', 'experiment_id')
-  print(names(model_attributes))
-  # split across '_' to 
-  model_measures <- data.frame(do.call('rbind', stringr::str_split(colnames(x), '_')))
-  print(model_measures)
-  names(model_measures) <- c('dimension', 'measure')
-  model_measures_split <- stringr::str_split(model_measures[,'measure'], '\\.')
-  model_measures[,'measure'] <- unlist(lapply(model_measures_split, 
-                                              function(x) x[1]))
-  return(data.frame(
-             model_attributes, 
-             model_measures, 
-             values = model_values,
-             statistic = model_statistic))
-}
-
-# high level function to apply model_result_2_df to multiple studies
+# high level function to apply parse_model_output to multiple studies
 get_study_summaries <- function(df) {
@@
            study_id <- unique(df$citekey[which(df$model_rate_emotion_values == x)])
-                   model_results <- model_result_2_df(x)
+           model_results <- parse_model_output(x)
            return(cbind(study_id, model_results))
@@
 
-# Parsing Regression Studies
+## Regression studies
 
-The following functions provide a working example for converting the r code contained in `model_rate_emotion_values` to a data frame for further analysis (currently working for regression studies).
+Encoded values should use the following nomenclature.
+In this synthetic example, dim_measure.summary2 exists for the study in the second row, but not the first, so an NA is encoded for summary2 in row 1.
 
-### Template
-
-Encoded values should use the following nomenclature:
-
-```         
-library = rbind(library.model.features.data.exp = c(dim_measure.summary = 0.5, dim_measure.summary = 0.1), library.model.features.data.exp = c(dim_measure.summary = 0.2, dim_measure.summary = 0.5))
-
-# e.g.
-
-rbind(librosa.randomforest.mfcc.msd.1 = c(valence_r2.mean = 0.5, arousal_r2.mean = 0.1), 
-librosa.randomforest.temporal.msd.1 = c(valence_r2.mean = 0.2, arousal_r2.mean = 0.5,
-valence_r2.sd = 0.1, arousal_r2.sd = 0.1))
-```
-
-### Working example
-
-```{r}
-this_study <- data.frame(citekey = c('testStudy2023ab','testStudy2023ab', 'testStudy2020of'),
-  model_rate_emotion_values = c("rbind('marsyas.random forest.mfcc.msd.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
-                                  valence_r2.sd = 0.4, arousal_r2.sd = 0.3,
-  valence_mse.mean = 0.3, arousal_mse.mean = 9.1),
-  'random forest.mfcc.deam.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5))",
-  "rbind('librosa.linear regression.mfcc.ismir.1' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3, valence_r2.sd = 0.2, arousal_r2.sd = 0.4,
-  euclid_euclid.mean = 0.32, euclid_euclid.sd = 0.1))",
-  "rbind('mirtoolbox.neural net.pitch.filmMusic.2' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
+```{r warning=FALSE}
+bind_field(
+  'library.model.features.data.exp1' = c(dim_measure1.summary = 0.5, dim_measure2.summary = 0.1), 
+  'library.model.features.data.exp2' = c(dim_measure1.summary = 0.2, dim_measure2.summary = 0.5, dim_measure.summary2 = 0.3)
 )
@@
 
-### Summary data frame
+### Example 2
+
+This example is more extensive, and shows how this procedure can work with multiple studies:
 
 ```{r}
-dplyr::tibble(get_study_summaries(this_study))
+regression_example <- data.frame(citekey = c('testStudy2023aa','testStudy2023bb', 'testStudy2020cc'),
+  model_rate_emotion_values = c("bind_field('marsyas.random forest.mfcc.msd.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5,
+ valence_r2.sd = 0.4, arousal_r2.sd = 0.3),
+  'essentia.random forest.mfcc.deam.1' = c(valence_r2.mean = 0.9, arousal_r2.mean = 0.5))",
+  "bind_field('librosa.linear regression.mfcc.ismir.1' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3, euclid_euclid.mean = 0.32))",
+  "bind_field('mirtoolbox.neural net.pitch.filmMusic.2' = c(valence_r2.mean = 0.1, arousal_r2.mean = 0.3))")
+)
+
+dplyr::tibble(get_study_summaries(regression_example)) |>
+  knitr::kable()
 ```
+
+## Classification studies
+
+For classification studies, we can extract results from a matrix-like representation.
+
+`unflatten` is a convenience function for preparing a confusion matrix, and `summarize_matrix` calls on the *caret* package to compute summary statistics for the matrix.
+
+```{r warning = FALSE}
+bind_field(
+  lapply(
+    list(
+      'library.model.features.data.exp' = unflatten(
+      "Class_A" = 0.8, "Class_B" = 0.2,
+      0.2, 0.8
+      ),
+      'library.model.features.data.exp' = unflatten(
+      "Class_A" = 0.4, "Class_B" = 0.6,
+      0.6, 0.4
+      )
+    ),
+    summarize_matrix
+  )
+)
+```
+
+```{r warning = FALSE}
+
+classification_example <- data.frame(
+  citekey = "classificationStudy2020aa",
+  model_rate_emotion_values = 
+  "bind_field(
+    lapply(
+      list(
+        'marsyas.smo unambiguous.mixed.new.1' = unflatten(
+          'A' = 52.6, 'B' = 17.1, 'C' = 0.0,
+          12, 65.2, 7.6, 
+          1.1,9.9,73.6),
+        'marsyas.smo full.mixed.new.1' = unflatten(
+          'C1' = 56.0, 'C2' = 19, 'C3' = 0.0, 'C4' = 2, 
+          11.3,58.9,13.7,15,
+          0,13.2,68.6, 3,
+          15,1,4, 6)
+      ),
+      summarize_matrix
+    )
+  )"
+)
+
+dplyr::tibble(get_study_summaries(classification_example)) |>
+  knitr::kable()
+```

### 2025-01-16 analysis/preprocessing.qmd
chore(preprocessing): update feature_n
- feature_n encodings now reflect changes to bib/extractions.bib -exclusions updated - grekow2021mu now appears in regression studies

@@
 #| eval: true
-
-R_studies$feature_n[R_studies$feature_n==" 548; after reduction, 139 for PCA and 276 for ReliefF   "] <- 548
-
+# this entry no longer appears due to exclusion:
+# R_studies$feature_n[R_studies$feature_n==" 548; after reduction, 139 for PCA and 276 for ReliefF   "] <- 548
+# R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions. Pos')]<-548
 R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting')] <- 21
-R_studies$feature_n[str_detect(R_studies$feature_n,'but 15 reported')]<-15
-R_studies$feature_n[str_detect(R_studies$feature_n,'50 PCA features')]<-50
-R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions. Pos')]<-548
-R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and')]<-60 # this should be 14400+60!
-R_studies$feature_n[str_detect(R_studies$feature_n,'before_selection = 45')]<-45
-R_studies$feature_n[str_detect(R_studies$feature_n,'model 4 = 388')]<-388
-R_studies$feature_n[str_detect(R_studies$feature_n,'6670 in MediaEval')]<-6670
-R_studies$feature_n[str_detect(R_studies$feature_n,'557 before feature')]<-557
-R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')]<-NA
+R_studies$feature_n[str_detect(R_studies$feature_n,'but 15 reported')]<-15 #resolved from the paper
+R_studies$feature_n[str_detect(R_studies$feature_n,'150 PCA features')]<-3000 #discuss
+R_studies$feature_n[str_detect(R_studies$feature_n,' 50 PCA features')]<-  499 #resolved
+R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and')]<-60 # this should be 14400+60! discuss
+R_studies$feature_n[str_detect(R_studies$feature_n,'before_selection = 45')]<-45 #resolved
+R_studies$feature_n[str_detect(R_studies$feature_n,'model 4 = 388')]<-388 #resolved
+R_studies$feature_n[str_detect(R_studies$feature_n,'6670 in MediaEval')]<-6670 #discuss
+R_studies$feature_n[str_detect(R_studies$feature_n,'557 before feature')]<-557 #resolved
+# this seems to refer to yang2021an, which is handled above with "6670 in mediaeval"
+# R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')]<-NA
+# 2025-01-15
+# beveridge2018po. This one is worth discussing as the two studies might be worth differentiating. 
+# Using higher value for now. DISCUSS
+R_studies$feature_n[str_detect(R_studies$feature_n,'study 1: 26, study 2: 28')] <- 28
 R_studies$feature_n<-as.numeric(R_studies$feature_n)
@@
 #| eval: true
-R_studies$citekey <- factor(R_studies$citekey) # 21 unique values
+R_studies$citekey <- factor(R_studies$citekey) # 22 unique values
 R_studies$dimension <- factor(R_studies$dimension)
@@
 #| eval: true
-
-R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved from the paper
-
-R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved
-R_studies$feature_n[R_studies$feature_n==" before_selection = 45, after_selection = 6  "] <- 45 #resolved
-R_studies$feature_n[R_studies$feature_n==" model 1: 52, model 2 = 68, model 3 = 260, model 4 = 388 "] <- 388 #resolved
-R_studies$feature_n[R_studies$feature_n==" variable, 557 before feature selection "] <- 557 #resolved
-
-R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 499 #resolved
-
-R_studies$feature_n[str_detect(R_studies$feature_n,'150 PCA features')] <- 3000
-R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting = 21')] <- 21
-R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions')] <- 548
-R_studies$feature_n[str_detect(R_studies$feature_n,'548; after reduct')] <- 548
-R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and filter bank')] <- 3600
-R_studies$feature_n[str_detect(R_studies$feature_n,'Features deep-learned from audio (not specified) but 1802 in DEAM')] <- 260
-
-# 2024-10-21: I changed the encoding for this one to "150 PCA features", so updated above.
-# R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')] <- 3000 # under-estimation based openSmile features and the paper arguing that they have 15 stat moments
-
-R_studies$feature_n<-as.numeric(R_studies$feature_n)
-
 print(quantile(R_studies$feature_n,c(0.333,0.666),na.rm = T))
@@
 C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  arbitrary!
-C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')] <- 548 
-C_studies$feature_n[str_detect(C_studies$feature_n,'548 dimensions')] <- 548 
-C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')] <- 548 
+# these seem to refer to the excluded bai studies
+# C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')] <- 548 
+#C_studies$feature_n[str_detect(C_studies$feature_n,'548 dimensions')] <- 548 
+# C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')] <- 548 
 C_studies$feature_n[str_detect(C_studies$feature_n,'8; 3 after')]<-8 

### 2025-01-17 analysis/analysis.qmd
update analysis
updated analysis and manuscript

--- 2024-10-21 analysis/analysis.qmd
@@
                  data = tmp,
-                 fixed = FALSE,
+                 common = FALSE,
                  random = TRUE,
@@
 #| fig-height: 6
+fig2a <- meta::forest(m.cor,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "N"),studlab = studyREF)
+
+fig2b <- funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+library(forestplot)
+data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
+data<-dplyr::arrange(data,mean)
+
+fp1 <- grid.grabExpr(print(data |>
+  forestplot(labeltext = c(study, n, cor),
+             xlab = "Correlation",
+             xticks = c(0, .25,.5,.75, 1),
+             clip = c(0, 1))|>
+    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
+    fp_append_row(mean  = m.cor$TE.common,
+                lower = m.cor$lower.common,
+                upper = m.cor$upper.common,
+                study = "Summary",
+                n = sum(m.cor$n),
+                cor = round(m.cor$TE.common,2),
+                is.summary = TRUE) |>
+  fp_set_style(box = "grey50",
+               line = "grey20",
+               summary = "black",
+                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
+                                ticks = gpar(cex = 0.80),
+                                xlab  = gpar(cex = 0.80)))|>
+    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
+)
+)
+
+source('../etc/custom_funnel_plot.R')
+fp2 <- custom_funnel_plot(m.cor)
+
+gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1),heights=c(2,1))
+```
+
+### Sub-divisions
+
+#### Sub-division based on techniques
+
+```{r,results='asis'}
+S <- summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
+
+```{r}
+m.cor1 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  model_class_id,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor1)
+```
+
+#### Sub-division based on journals (engineering vs psych)
+
+```{r,results='asis'}
+S <- summarise(group_by(tmp,journal_type),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
+
+```{r}
+m.cor2 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  journal_type,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor2)
+```
+
+#### Sub-division based on N features
+
+```{r,results='asis'}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
+S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+```
+
+```{r}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
+m.cor3 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  feature_n_categories,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor3)
+S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+print(S)
+
+```
+
+#### Sub-division based on N features and genres
+
+```{r, results='asis'}
+tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values
+
+S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
+print(knitr::kable(S))
+
+m.cor4 <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = citekey, # unique_id
+                 data = tmp,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 subgroup =  feature_n_complexity_genre,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Valence: Summary")
+print(m.cor4)
+```
+
+### Arousal
+
+#### Using all models
+
+```{r}
+R_studies <- read.csv("R_studies.csv")
+tmp <- dplyr::filter(R_studies,dimension=="arousal")
+#if all studies, remove two with NA values
+tmp <- tmp[!is.na(tmp$values),]
+#dim(tmp)
+
+# Take all models
+m.cor <- metacor(cor = values,     # values 
+                 n = stimulus_n,
+                 studlab = unique_id,
+                 data = tmp,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "PM",# was REML, but we switch to Paule-Mandel because Langan et al., 2019
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Arousal: Summary")
+
+print(m.cor)
+
+print(FisherZInv(m.cor$TE.random))
+print(FisherZInv(m.cor$upper.random))
+print(FisherZInv(m.cor$lower.random))
+```
+
+#### Using the best model out of each study
+
+```{r}
+R_summary <- read.csv("R_summary.csv")
+
+# select regression studies with r2
+tmp <- dplyr::filter(R_summary,dimension=="arousal")
+#tmp <- dplyr::filter(R_studies,dimension=="valence")
+#dim(tmp)
+
+#if all studies, remove two
+#tmp <- tmp[!is.na(tmp$values),]
+#dim(tmp)
+
+## Disambiguate the studies
+tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
+
+# Max values
+m.cor <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = studyREF,#citekey, # unique_id
+                 data = tmp,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+#                 backtransf = TRUE,
+#                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Regression: Arousal: Summary")
+
+print(m.cor)
+
+print(FisherZInv(m.cor$TE.random))
+print(FisherZInv(m.cor$upper.random))
+print(FisherZInv(m.cor$lower.random))
+```
+
+### Explore heterogeneity
+
+```{r}
+#| eval: true
+#| echo: true
+# Method 1: Give us the Egger's test about beta coefficient from funnel
+print(eggers.test(m.cor))
+
+# Method 2: Find the impact to the results when removing those outside the 95CI
+O <- find.outliers(m.cor) # 13 remaining out of 24
+print(O)
+# Method 3: Leave-out-out analysis etc for individual influence (not useful here)
+#infan <- InfluenceAnalysis(m.cor)
+
+# Method 4: Focus on 10% of most precise studies (Stanley, Jarrel, Doucouliagos 2010)
+thres<-quantile(m.cor$seTE,0.1)
+ind<-m.cor$seTE<=as.numeric(thres)
+m.cor10pct <- update(m.cor, subset = which(ind))
+
+# Method 5: P curve analysis (Simonsohn, Simmons & Nelson, 2015)
+pcurve(m.cor)
+```
+
+### Visualise (forest and funnel plots)
+
+```{r}
+#| fig-width: 12
+#| fig-height: 6
 fig2a <- forest(m.cor,
@@
              print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"),studlab = studyREF)
+             leftlabs = c("Author", "N"),studlab = studyREF)
 
@@
                  data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  feature_n_complexity_genre,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor4)
-```
-
-### Arousal
-
-#### Using all models
-
-```{r}
-R_studies <- read.csv("R_studies.csv")
-tmp <- dplyr::filter(R_studies,dimension=="arousal")
-#if all studies, remove two with NA values
-tmp <- tmp[!is.na(tmp$values),]
-#dim(tmp)
-
-# Take all models
-m.cor <- metacor(cor = values,     # values 
-                 n = stimulus_n,
-                 studlab = unique_id,
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "PM",# was REML, but we switch to Paule-Mandel because Langan et al., 2019
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Arousal: Summary")
-
-print(m.cor)
-
-print(FisherZInv(m.cor$TE.random))
-print(FisherZInv(m.cor$upper.random))
-print(FisherZInv(m.cor$lower.random))
-```
-
-#### Using the best model out of each study
-
-```{r}
-R_summary <- read.csv("R_summary.csv")
-
-# select regression studies with r2
-tmp <- dplyr::filter(R_summary,dimension=="arousal")
-#tmp <- dplyr::filter(R_studies,dimension=="valence")
-#dim(tmp)
-
-#if all studies, remove two
-#tmp <- tmp[!is.na(tmp$values),]
-#dim(tmp)
-
-## Disambiguate the studies
-tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
-
-# Max values
-m.cor <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = studyREF,#citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Arousal: Summary")
-
-print(m.cor)
-
-print(FisherZInv(m.cor$TE.random))
-print(FisherZInv(m.cor$upper.random))
-print(FisherZInv(m.cor$lower.random))
-```
-
-### Explore heterogeneity
-
-```{r}
-#| eval: true
-#| echo: true
-# Method 1: Give us the Egger's test about beta coefficient from funnel
-print(eggers.test(m.cor))
-
-# Method 2: Find the impact to the results when removing those outside the 95CI
-O <- find.outliers(m.cor) # 13 remaining out of 24
-print(O)
-# Method 3: Leave-out-out analysis etc for individual influence (not useful here)
-#infan <- InfluenceAnalysis(m.cor)
-
-# Method 4: Focus on 10% of most precise studies (Stanley, Jarrel, Doucouliagos 2010)
-thres<-quantile(m.cor$seTE,0.1)
-ind<-m.cor$seTE<=as.numeric(thres)
-m.cor10pct <- update(m.cor, subset = which(ind))
-
-# Method 5: P curve analysis (Simonsohn, Simmons & Nelson, 2015)
-pcurve(m.cor)
-```
-
-### Visualise (forest and funnel plots)
-
-```{r}
-#| fig-width: 12
-#| fig-height: 6
-fig2a <- forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"),studlab = studyREF)
-
-fig2b<-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
-
-library(forestplot)
-data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
-data<-dplyr::arrange(data,mean)
-
-fp1 <- grid.grabExpr(print(data |>
-  forestplot(labeltext = c(study, n, cor),
-             xlab = "Correlation",
-             xticks = c(0, .25,.5,.75, 1),
-             clip = c(0, 1))|>
-    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
-    fp_append_row(mean  = m.cor$TE.common,
-                lower = m.cor$lower.common,
-                upper = m.cor$upper.common,
-                study = "Summary",
-                n = sum(m.cor$n),
-                cor = round(m.cor$TE.common,2),
-                is.summary = TRUE) |>
-  fp_set_style(box = "grey50",
-               line = "grey20",
-               summary = "black",
-                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
-                                ticks = gpar(cex = 0.80),
-                                xlab  = gpar(cex = 0.80)))|>
-    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
-)
-)
-
-source('../etc/custom_funnel_plot.R')
-fp2 <- custom_funnel_plot(m.cor)
-
-gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1),heights=c(2,1))
-```
-
-### Sub-divisions
-
-#### Sub-division based on techniques
-
-```{r,results='asis'}
-S <- summarise(group_by(tmp,model_class_id),n=n(),obs=sum(stimulus_n))
-print(knitr::kable(S))
-```
-
-```{r}
-m.cor1 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  model_class_id,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor1)
-```
-
-#### Sub-division based on journals (engineering vs psych)
-
-```{r,results='asis'}
-S <- summarise(group_by(tmp,journal_type),n=n(),obs=sum(stimulus_n))
-print(knitr::kable(S))
-```
-
-```{r}
-m.cor2 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  journal_type,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor2)
-```
-
-#### Sub-division based on N features
-
-```{r,results='asis'}
-tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
-S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
-print(knitr::kable(S))
-```
-
-```{r}
-tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
-m.cor3 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  feature_n_categories,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
-print(m.cor3)
-S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
-print(S)
-
-```
-
-#### Sub-division based on N features and genres
-
-```{r, results='asis'}
-tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values
-
-S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
-print(knitr::kable(S))
-
-m.cor4 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 fixed = FALSE,
+                 common = FALSE,
                  random = TRUE,
@@
 
+# yang2021an needs to be encoded for classification (currently just regression)
 C_summary <- read.csv("C_summary.csv")
+C_classes <- read.csv("C_study_class_n.csv")
+
+C_summary <- merge(C_summary, C_classes)
 
@@
                  data = C_summary,
-                 fixed = FALSE,
+                 common = FALSE,
                  random = TRUE,
@@
              print.tau2 = FALSE,
-             leftlabs = c("Author", "g", "SE"),studlab = citekey)
+             leftlabs = c("Author", "N"),studlab = citekey)
+
+funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+```
+#### By class n = 2 vs. > 2
+```{r}
+C_summary$classes <- 0
+C_summary[C_summary$n_classes < 3,]$classes <- "2"
+C_summary[C_summary$n_classes >= 3,]$classes <- ">2"
+
+m.cor <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n, # could also change to n_classes
+                 studlab = studyREF, # unique_id
+                 data = C_summary,
+                 subgroup = classes,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 backtransf = TRUE,
+                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Classification: Summary")
+
+forest(m.cor,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "N"),studlab = citekey)
 
@@
                  data = tmp2,
-                 fixed = FALSE,
+                 common = FALSE,
                  random = TRUE,

### 2025-01-17 analysis/preprocessing.qmd
updated analysis and manuscript

@@
 # THIS IS CORRECT (updated 24 October 2024):
-# [1] "We have 1284 observations"
-# [1] "We have 36 studies"
+# THIS IS CORRECT (updated 17 January 2025):
+# [1] "We have 1114 observations"
+# [1] "We have 34 studies"
 # [1] "Where 22 are regression studies"
-# [1] "Where 14 are classification studies"
+# [1] "Where 12 are classification studies"
 

### 2025-01-17 manuscript/manuscript.qmd
updated analysis and manuscript

@@
 
-Although the total number of studies meeting the criteria described in the previous section is modest (36 in total), they encompass a large array of models (339 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
+Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (339 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
 The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 9000 features [@zhang2023mo].
@@
 
+There has been a considerable number of studies published involving MER models (N=96/46 full text articles considered), but in many cases the reporting standards or other quality issues or the lack of dedicated focus on music led us to reject a substantial proportion of studies.
+At the end, 34 studies remained in the analysis that overall reported xxxxx models.
+
 ## Concise summary of what we did and found
@@
 -   Variation in study/model/data quality is large and can be seen in heterogenuity and the amount of studies eliminated
+
+[this is the discussion section]
 

### 2025-01-22 analysis/preprocessing.qmd

@@
 # Set parameters and libraries
-export_decision <- TRUE
+export_decision <- FALSE
 verbose <- FALSE
@@
 R_studies$feature_n[str_detect(R_studies$feature_n,'but 15 reported')]<-15 #resolved from the paper
-R_studies$feature_n[str_detect(R_studies$feature_n,'150 PCA features')]<-3000 #discuss
+R_studies$feature_n[str_detect(R_studies$feature_n,'150 PCA features')]<-3000 #resolved
 R_studies$feature_n[str_detect(R_studies$feature_n,' 50 PCA features')]<-  499 #resolved
-R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and')]<-60 # this should be 14400+60! discuss
+R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and')]<-14400+60 # this should be 14400+60! resolved
 R_studies$feature_n[str_detect(R_studies$feature_n,'before_selection = 45')]<-45 #resolved
 R_studies$feature_n[str_detect(R_studies$feature_n,'model 4 = 388')]<-388 #resolved
-R_studies$feature_n[str_detect(R_studies$feature_n,'6670 in MediaEval')]<-6670 #discuss
+# yang2021an appears there are nine unique features based on table 1
+R_studies$feature_n[str_detect(R_studies$feature_n,'6669 in MediaEval')]<-6669 # resolved. 9 reported in table 1, but likely used full mediaeval feature set. 
 R_studies$feature_n[str_detect(R_studies$feature_n,'557 before feature')]<-557 #resolved
-# this seems to refer to yang2021an, which is handled above with "6670 in mediaeval"
+# this seems to refer to yang2021an, which is handled above with "6669 in mediaeval"
 # R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')]<-NA
 # 2025-01-15
-# beveridge2018po. This one is worth discussing as the two studies might be worth differentiating. 
-# Using higher value for now. DISCUSS
-R_studies$feature_n[str_detect(R_studies$feature_n,'study 1: 26, study 2: 28')] <- 28
+R_studies$feature_n[str_detect(R_studies$feature_n,'study 1: 26, study 2: 28')] <- 54 # resolved used audio and midi features. study 2 was external validation
 R_studies$feature_n<-as.numeric(R_studies$feature_n)
@@
 #table(C_studies$feature_n)
-C_studies$feature_n[str_detect(C_studies$feature_n,'eight different ')]<-600 # arbitrary!
+C_studies$feature_n[str_detect(C_studies$feature_n,'eight different ')]<-21+12+4+14+39+1+1+6 # estimated from feature subsection 4.1.2 (encoded in reverse order from h to a)
 C_studies$feature_n[str_detect(C_studies$feature_n,'126, retained 97')]<-126 
-C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  arbitrary!
+C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  resolved
 # these seem to refer to the excluded bai studies
@@
 C_studies$feature_n[str_detect(C_studies$feature_n,'between 9 and 10')]<-10 
-C_studies$feature_n[str_detect(C_studies$feature_n,'summarize feature')]<-600 # arbitrary
+C_studies$feature_n[str_detect(C_studies$feature_n,'summarize feature')]<-2+2+2 # estimated from 3.2.1 to 3.2.3
 #table(C_studies$feature_n)

### 2025-01-22 manuscript/_figure1.qmd

@@
              (n = 50)"]
-  I [label = "Studies excluded in final review (n = 10)"]
-  J [label = "Final selection (n = 36)"]
+  I [label = "Studies excluded in final review (n = 12)"]
+  J [label = "Final selection (n = 34)"]
   A->B

### 2025-01-22 manuscript/manuscript.qmd

@@
 ---
-title             : "Meta-analysis of regression and classification success of emotion ratings from audio"
+title             : "A Meta-Analysis of Music Emotion Recognition Studies"
 shorttitle        : "Meta-analysis of music emotion recognition"
@@
 The initial search yielded 553 potential studies after excluding duplicate entries.
-We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $R^2$ or $MCC$ values see [SI](http://) for a breakdown).
+We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $r$ or $MCC$ values see [SI](http://) for a breakdown).
 After the screening stage, we defined a set of entities to extract characterising (i) music (genre, stimulus number \[N\], duration), (ii) features extracted (number, type, source, defined by [@panda2020audio]), (iii) model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), (iv) model complexity (i.e., approximate number of features used to predict ratings), and (v) type of model cross-validation.
 
-We converted all regression results into $R^2$ values for valence and arousal and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].
+We converted all regression results from $R^2$ values into $r$ values for valence and arousal, and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].
 To increase consistency in our analyses, we excluded studies using incompatible features (e.g., spectrograms of audio files [@nag2022]), or dependent variables (e.g., one regression study analyzed valence and arousal together, but not separately [@chin2018]).
@@
 Finally, we excluded studies published in journals of questionable relevance/quality, (e.g., *Mathematical Problems in Engineering* ceased publication following 17 retractions published between July and September 2024).
+Overall this step eliminated 12 studies, leaving us with 34 studies in total.
 
@@
 
-TABLE 1: Summary of data (part of `analysis/preprocessing.qmd`)
+TABLE 1: Summary of data (part of `analysis/preprocessing.qmd` updated 21/1/2025)
 
@@
 |:-----------|:--------------------------------|:--------------------------|:------|
-| Study N    | 21                              | 14                        | 36    |
-| Model N    | 236                             | 103                       | 339   |
-| Techniques | Flexible Discriminants (FD): 58 | 30                        | 86    |
-| Techniques | Neural Nets (NN): 70            | 28                        | 98    |
+| Study N    | 22                              | 12                        | 34    |
+| Model N    | 204                             | 86                        | 290   |
+| Techniques | Neural Nets (NN): 66            | 25                        | 91    |
+| Techniques | Flexible Discriminants (FD): 50 | 26                        | 76    |
 | Techniques | Linear Methods (LM): 62         | 13                        | 75    |
-| Techniques | Random Forests (RF): 22         | 14                        | 36    |
-| Techniques | KS, Add. & KNN (KS): 24         | 8                         | 32    |
-| Feature N  | Min=3, Md=548, Max=6670         | Min=3, Md=397, Max=8904   | NA    |
-| Stimulus N | Min=20, Md=330, Max=2486        | Min=124, Md=387, Max=5192 | NA    |
+| Techniques | Random Forests (RF): 14         | 10                        | 34    |
+| Techniques | KS, Add. & KNN (KS): 12         | 12                        | 24    |
+| Feature N  | Min=3, Md=605, Max=6670         | Min=8, Md=126, Max=8904   | NA    |
+| Stimulus N | Min=20, Md=324, Max=2486        | Min=124, Md=300, Max=5192 | NA    |
 
-Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (339 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
+Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (290 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
 The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 9000 features [@zhang2023mo].
-The median number of features differs between regression (548) and classification (397) studies, primarily reflecting the nature of the datasets used in each approach.
-The number of stimuli is typically around 300-400 (with a median of 330 for regression and 387 for classification), though there is substantial variation, with the extremes from 40 stimuli in @saizclar2022pr to 5192 stimuli in @alvarez2023ri.
-There are also additional dimensions to consider, such as the type of cross-validation used, the music genres analyzed (whether a single genre, multiple genres, or a mix), the type of journal in which the studies were published, and the source of the extracted features.
+The median number of features differs between regression (605) and classification (126) studies, primarily reflecting the nature of the datasets used in each approach.
+The number of stimuli is typically around 300-400 (with a median of 324 for regression and 300 for classification), though there is substantial variation, with the extremes from 20 stimuli in @beveridge2018po to 5192 stimuli in @alvarez2023ri.
+There are also additional dimensions to consider, such as the type of cross-validation used, the music genres analyzed (whether a single genre, multiple genres, or a mix), the type of journal in which the studies were published, and the extraction tool used to extract features.
 However, these variables do not lend themselves to a simple summary, so we will revisit them during the interpretation and discussion stages.
@@
 
-See `analysis/analysis.qmd`
+See `analysis/analysis.qmd` (updated 17/1/2025)
 
@@
 |:-------------|:------------|:------------------------|:------|:------|:---------|:------|
-| Valence All  | 90,61733    | 0.609 \[0.570-0.650\]   | 23.3  | .0001 | 0.079    | 97.3% |
-| Valence Max  | 21,13572    | 0.680 \[0.575-0.762\]   | 9.96  | .0001 | 0.136    | 98.2% |
+| Valence All  | 102,60017   | 0.583 \[0.541-0.623\]   | 21.40 | .0001 | 0.094    | 97.7% |
+| Valence Max  | 22,14172    | 0.669 \[0.560-0.755\]   | 9.58  | .0001 | 0.148    | 98.4% |
 | *N Features* |             |                         |       |       |          |       |
@@
 | *Techniques* |             |                         |       |       |          |       |
-| KS           | 2,2582      | 0.466 \[-0.634-0.942\]  | \-    | \-    | 0.0185   | 95.1% |
-| LM           | 7,1438      | 0.797 \[0.614-0.899\]   | \-    | \-    | 0.1370   | 96.4% |
+| KS           | 1,1838      | 0.466 \[-0.634-0.942\]  | \-    | \-    | 0.0185   | 95.1% |
+| LM           | 8,1762      | 0.797 \[0.614-0.899\]   | \-    | \-    | 0.1370   | 96.4% |
 | FD           | 6,4993      | 0.656 \[0.484-0.779\]   | \-    | \-     | 0.0574  | 96.9% |
-| NN           | 3,1229      | 0.393 \[-0.355-0.835\] | \-    | \-     | 0.0761   | 97.1% |
+| NN           | 4,2249      | 0.393 \[-0.355-0.835\]  | \-    | \-     | 0.0761  | 97.1% |
 | RF           | 3,3330      | 0.750 \[0.292-0.928\]   | \-    | \-     | 0.093   | 98.5% |
 
-The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 24 studies achieving an average correlation of _r_ = 0.658 (95% CI: 0.557-0.740), called "valence Max" in Table 2.
-However, when considering all models across these studies (n = 120), the overall prediction rate drops significantly to _r_ = 0.567.
+<!-- table updated TE 21/1/2025 -->
+
+The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 22 studies achieving an average correlation of _r_ = 0.669 (95% CI: 0.560-0.755), called "valence Max" in Table 2.
+However, when considering all models across these studies (n = 102), the overall prediction rate drops significantly to _r_ = 0.583.
 We argue that this lower correlation is likely due to the inclusion of baseline models reported in these studies, which may not reflect the true success of the task for the purposes of our analysis.
 
-Further analysis of between-study heterogeneity, as indexed by the $\tau^2$ (0.138) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] at 98.2%, reveals substantial heterogeneity.
+Further analysis of between-study heterogeneity, as indexed by the $\tau^2$ (0.148) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] at 98.4%, reveals substantial heterogeneity.
 Since $I^2$ is heavily influenced by study size (with larger N leading to lower sampling error), its value may be less insightful in this context.
@@
 (2023) demonstrating evidence of positive correlations.
-A mean estimate of 0.66 is achieved by 15 out of the 24 models.
-While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), @saizclar2022pr (n = 40), and in @griffiths2021am (n = 40).
+A mean estimate of 0.67 is achieved by 15 out of the 22 models.
+While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), and in @griffiths2021am (n = 40).
 The funnel plot in panel B of Figure 2 shows clustering at the top of the plot (studies with low standard error) and no assumed larger diversity in the correlations when the error rates increase.
-However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$=5.00, CI95% -0.78-10.78, _t_ = 1.70, _p_ = 0.104, @eggersmith_1997).
-Coming back to the mean of valence correlation of 0.66 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect.
-This left 13 studies in the data and resulted in the meta-analytical pooled correlation of 0.649 (CI95% 0.598-0.695).
+However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$=5.05, CI95% -0.99-11.09, _t_ = 1.64, _p_ = 0.112, @eggersmith_1997).
+Coming back to the mean of valence correlation of 0.67 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect.
+This left 12 studies in the data and resulted in the meta-analytical pooled correlation of 0.686 (CI95% 0.635-0.731).
 In other words, despite the large variation in the correlations and standard errors across the studies, this variation in itself does not seem to be a significant driver behind the overall effect.
+
+<!-- numbers in the text updated up to here, TE 21/1/2025 -->
 
@@
 In terms of feature sets, we categorized them into three groups: few features (<18), a large number of features (18–260), and massive feature sets (260+).
-Interestingly, models using a relatively small number of features (<18) performed best (_r_ = 0.881, 95% CI: 0.566–0.???) compared to those utilizing larger feature sets.
-However, it is worth noting that the models using massive feature sets (260+) also performed well (_r_ = 0.685), achieving better and more consistent results than the overall prediction rate (_r_ = 0.659).
-This observation is supported by the lowest heterogeneity index for the massive feature set group ($\tau^2$ = 0.044), indicating more consistent results across studies.
+Interestingly, models (4 in total) using a relatively small number of features (<18) performed best (_r_ = 0.817, 95% CI: 0.361–0.958) compared to those utilizing larger feature sets.
+However, it is worth noting that the models using massive feature sets (260+, 7 studies in total) also performed well (_r_ = 0.702), achieving better and more consistent results than the overall prediction rate (_r_ = 0.669).
+This observation is supported by the lowest heterogeneity index for the massive feature set group ($\tau^2$ = 0.029), indicating more consistent results across studies.
+Studies with large number of features (18-260 features, 10 studies in total) delivered the worst results, _r_ = 0.586 (95% CI: 0.360–0.748).
+Despite the fluctuation in the overall model accuracy between the number of features, the differences are not substantially large to pass the test of statistical significance (_Q_(2) = 3.47, _p_=.176).
 
-When analyzing the studies across the five modeling techniques used.
+<!-- numbers in the text updated up to here, TE 21/1/2025 -->
+
+When analyzing the studies across the five modeling techniques used, the prediction do differ significantly (_Q_(4) = 45.7, _p_ < .0001).
 Notably, linear models (LM) and flexible discriminants (FD) were the most common, with 8 and 6 studies, respectively, allowing for more confident interpretations.
@@
 Flexible discriminants performed at a similar level to the overall model average (_r_ = 0.656, 95% CI: 0.484–0.779).
-The relatively poor performance of the neural network (NN) models (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
+While there were only 3 studies involving random forests, these performed well, achieving _r_ = 0.750, 95% CI: 0.292–0.928), and the relatively poor performance of the neural network models represented in four studies (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
+Kernel smoothing and KNN models (with only 1 study represented) achieved relatively poor success as well, _r_ = 0.383, 95% CI: 0.348–0.426).
 
@@
 For this purpose, we grouped the studies into small single genre/multigenre studies, medium single genre/multigenre studies, and medium-large single genre/multigenre studies, and huge multigenre studies.
-The small single genre/multigenre studies generally performed best (_r_ = 0.836, 95% CI: -0.197-0.989), followed by huge multi-genre studies (_r_ = 0.720, 95% CI: -0.189-0.965) while the medium and medium-large sized studies performance was between close the overall average (medium-large, _r_ = 0.669, 95% CI: 0.347-0.850 and medium _r_ = 0.587, 95% CI: 0.433-0.708).
+The small single genre/multigenre studies generally performed best (_r_ = 0.836), followed by huge multi-genre studies (_r_ = 0.693) while the medium and medium-large sized studies performance was between close the overall average (medium-large, _r_ = 0.768 and medium _r_ = 0.607).
 The heterogeneity was lowest in the huge multigenre studies ($\tau^2$ = 0.013) and highest in the small single genre/multigenre studies ($\tau^2$ = 0.318).
@@
 Despite these caveats, the two main sub-groupings portrayed in Table 2 enable us to identify valuable differences related to model success across the studies.
+
+<!-- numbers in the text updated up to here, TE 21/1/2025 -->
 

### 2025-01-22 analysis/analysis.qmd
updated manuscript up to arousal. A mod to renv.lock added ggpubr package

@@
 ```{r,results='asis'}
-tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp <- dplyr::filter(R_summary,dimension=="arousal")
 tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
@@
 ```{r}
-tmp <- dplyr::filter(R_summary,dimension=="valence")
+tmp <- dplyr::filter(R_summary,dimension=="arousal")
 tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
@@
 ```{r, results='asis'}
-tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values
+tmp <- dplyr::filter(R_summary,dimension=="arousal")
+tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
 

### 2025-01-22 manuscript/_figure2.qmd
updated manuscript up to arousal. A mod to renv.lock added ggpubr package

@@
 library(forestplot)
-
+library(ggpubr)
 R_summary <- read.csv("../analysis/R_summary.csv")
@@
 
-gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
+#gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
+
+ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
 

### 2025-01-22 manuscript/_figure3.qmd
updated manuscript up to arousal. A mod to renv.lock added ggpubr package

@@
 #### Forest plot using forestplot
-library(forestplot)
 data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=format(round(m.cor$cor, digits=3), nsmall = 3))
@@
                                 xlab  = gpar(cex = 0.80)))|>
-    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
+    fp_decorate_graph(grid = structure(FisherZInv(m.cor$TE.random),gp = gpar(lty = 2, col = "grey30")))
 )
@@
 
-gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
+#gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
+ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
 

### 2025-01-22 manuscript/manuscript.qmd
updated manuscript up to arousal. A mod to renv.lock added ggpubr package

@@
 Table 3 describes the broad pattern of results in tabular format, and Figure 3 illustrates the spread and heterogeneity of all studies for arousal.
-The overall correlation across the studies using the best performing model out of each study (Max) is 0.807 (CI95% 0.745-0.855).
-If we examine all the models reported in each study, the correlation drops marginally, to 0.784 (CI95% 0.765-0.801), despite this analysis includes about five times as many models as taking the best model out of each study.
+The overall correlation across the studies using the best performing model out of each study (Max) is 0.809 (CI95% 0.740-0.860).
+If we examine all the models reported in each study, the correlation drops marginally, to 0.791 (CI95% 0.770-0.810), despite this analysis includes about four times as many models as taking the best model out of each study.
 For arousal, even the baseline models seem to be performing on a relative high level.
-However, the indicators of heterogeneity are again high ($\tau^2$ = 0.155 and $I^2$=96.8%), which suggests that summary may be misleading.
-However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.787 95%CI -4.61-6.18, _t_ = 0.286, _p_ = 0.778).
-If we remove the studies that are outside the 95%CI in heterogeneity, leaves this 14 studies in the summary that has _r_ = 0.8182 (95%CI 0.802-0.833) with $\tau^2$ = 0.0038 and $I^2$ = 76.0%.
-In other words, no material difference to the results obtained with all 24 studies.
+However, the indicators of heterogeneity are again high ($\tau^2$ = 0.141 and $I^2$=97.9%), which suggests that summary may be misleading.
+However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.789 95%CI -4.87-6.45, _t_ = 0.273, _p_ = 0.788).
+If we remove the studies that are outside the 95%CI in heterogeneity, leaves this 13 studies in the summary that has _r_ = 0.826 (95%CI 0.806-0.845) with $\tau^2$ = 0.0042 and $I^2$ = 76.8%.
+In other words, no material difference to the results obtained with all 22 studies.
 
@@
 |:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
-| Arousal All  | 90, 61733   | 0.795 \[0.774-0.814\]     | 39.4 | 0.0001 | 0.064    | 96.3% |
-| Arousal Max  | 21, 13572   | 0.815 \[0.749-0.865\]     | 14.0 | 0.0001 | 0.131    | 97.7% |
+| Arousal All  | 102, 60017  | 0.791 \[0.770-0.810\]     | 39.9 | 0.0001 | 0.069    | 96.2% |
+| Arousal Max  | 22, 14172   | 0.809 \[0.740-0.860\]     | 13.6 | 0.0001 | 0.141    | 97.9% |
 | *N Features* |             |                           |      |        |          |       |
-| \<18 F       | 5, 3036     | 0.811 \[0.534-0.931\]     |      |        | 0.1815   | 98.9% |
-| 18-260 F     | 11, 7042    | 0.584 \[0.534-0.931\]     |      |        | 0.1331   | 97.6% |
-| 260+ F       | 5, 3494     | 0.710 \[0.542-0.823\]     |      |        | 0.0435   | 97.2% |
+| \<18 F       | 4, 3016     | 0.817 \[0.361-0.958\]     |      |        | 0.2295   | 99.2% |
+| 18-260 F     | 10, 4222    | 0.586 \[0.356-0.748\]     |      |        | 0.1542   | 96.9% |
+| 260+ F       | 7, 6190     | 0.702 \[0.612-0.774\]     |      |        | 0.0285   | 96.6% |
 | *Techniques* |             |                           |      |        |          |       |
-| KS           | 2, 2582     | 0.807 \[0.549-0.924\]     |      |        | 0.0022   | 70.0% |
-| LM           | 7, 1438     | 0.885 \[0.796-0.936\]     |      |        | 0.0846   | 93.3% |
+| KS           | 1, 1838     | 0.819 \[0.803-0.833\]     |      |        |  -       | -     |
+| LM           | 8, 1762     | 0.881 \[0.808-0.928\]     |      |        | 0.0846   | 93.3% |
 | FD           | 6, 4993     | 0.808 \[0.644-0.901\]     |      |        | 0.1125   | 98.0% |
-| NN           | 3, 1229     | 0.533 \[0.082-0.803\]     |      |        | 0.0190   | 85.8% |
-| RF           | 3, 3330     | 0.809 \[0.733-0.864\]  |      |        | 0.0012   | 52.7% |
+| NN           | 4, 2249     | 0.533 \[0.328-0.691\]     |      |        | 0.0190   | 85.8% |
+| RF           | 3, 3330     | 0.809 \[0.733-0.864\]     |      |        | 0.0025   | 65.4% |
 
-The forest plot in Figure 3 reveals
+<!-- numbers in the text updated up to here, TE 22/1/2025 -->
 
-The subdivision of studies shows...
+<!-- Schwarzer and colleagues (Schwarzer, Carpenter, and Rücker 2015, chap. 4.3) mention, as a general rule of thumb, that subgroup analyses only make sense when your meta-analysis contains at least 
+K= 10 studies.-->
+
+Figure 3 presents (A) a forest and (B) funnel plot of the random-effects model of the best-performing models from all studies.
+Similarly to valence, the range of correlations is also wide for arousal, ranging from 0.35 to 0.95, with all studies demonstrating evidence of positive correlations.
+A mean estimate of 0.81 or higher is achieved by the majority (15 out of the 22 models).
+Due to large sample in ost studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am;@koh2023me; @saizclar2022pr; @wang2021ac].
+The funnel plot in panel B illustrates the limited range of the correlations and show heavy clustering at the top of the plot (studies with low standard error).
+There is no clear asymmetry in the plot, verified by non-significant Egger's test reported above.
+
+The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (_Q_(2) = 3.47, _p_ = .176) despite the differing means (_r_ = 0.817 for studies with less than 18 features, _r_ = 0.586 for 18 to 260 features, and _r_ = 0.702 for studies utilising over 260 features).
+The differences in the techniques, however, does show variance between subgroups that is statistically significant (_Q_(4) = 50.47, _p_ < .0001), where at least Neural Nets achieve poor prediction of arousal (_r_ = 0.533) in comparison to other techniques.
+The caveat of this subgroup analysis is the small number of observations for five techniques.
+When other subgroupings were explored, such as the type of journal (Engineering with 13 studies vs Psychology with 9 studies), no significant differences were observed (_Q_(1) = 0.94, _p_ = .333).
 

### 2025-01-22 version.R

@@ -1,0 +1,9 @@
+# show package version (these are controlled by renv)
+print(paste("meta:",packageVersion("meta")))
+print(paste("metafor:",packageVersion("metafor")))
+print(paste("dmetar:",packageVersion("dmetar")))
+print(paste("knitr:",packageVersion("knitr")))
+
+print(sessionInfo())
+
+# run me in terminal: R -e 'source("version.R")'

### 2025-01-24 analysis/analysis.qmd
fix(analysis): aggregate performance across models:  bhuvanakumar2023em and nguyen2017an

@@
 C_summary <- read.csv("C_summary.csv")
+
+# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
+C_summary[C_summary$citekey == "nguyen2017an",]$valuesMax <- C_summary[C_summary$citekey == "nguyen2017an",]$valuesMean
+
+# 2025-01-24: averaging across quadrants for bhuvanakumar study
+# subset study
+bhuvanakumar <- subset(
+  C_studies, 
+  stringr::str_detect(
+    C_studies$citekey,
+    "bhuvanakumar"
+    )
+)
+# group by algorithm to average across the four quadrants
+bhuvanakumar$model_algorithm <- substr(
+  bhuvanakumar$model_id, 
+  1, 
+  4
+)
+# take the average for each algorithm
+bhuvanakumar |> 
+  group_by(model_algorithm) |>
+  mutate(values = mean(values)) -> bhuvanakumar
+# overwrite values in C_summary
+C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMean <- mean(unique(bhuvanakumar$values))
+C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMedian <- median(unique(bhuvanakumar$values))
+C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMax <- max(unique(bhuvanakumar$values))
+
+remove(bhuvanakumar)
+
 C_classes <- read.csv("C_study_class_n.csv")
@@
 m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
+#       subgroup = model_class_id, 
 #       subgroup = journal_type, 

### 2025-01-26 analysis/preprocessing.qmd
chore(preprocessing): update classification output
-aggregate model performance across valence and arousal for bhuvanakumar2023em &  nguyen20172017an -update model categories for zhang2017fe

@@
 metaMER_results$model_class_id <- 'Unclassified'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Methods' # Class name from Elements of Stat.."
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis|linear discriminant|quadratic discriminant')] <- 'Linear Methods' # Class name from Elements of Stat.."
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Classification'
@@
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient')]<-'Random Forests'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient|tree|bag|boost')]<-'Random Forests'
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf')]<-'Ensemble Learning'
@@
 # note that we have some classification studies that also do regression and vice versa?
-# THIS IS CORRECT (updated 24 October 2024):
 # THIS IS CORRECT (updated 17 January 2025):
@@
 R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
-                                      breaks = c(0,15,501,653,10000),
+                                      breaks = c(0,15,501,653,20000),
                                       labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
@@
 
-## Select a summary measure for valence and arousal separately
-
-```{r}
-#| echo: true
-#| eval: true
-
-C_studies$citekey <- factor(C_studies$citekey)
-
-C_summary <- summarise(group_by(C_studies,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id), stimulus_genre_mixed=first(stimulus_genre_mixed),journal_type = first(journal_type))
-
-```
-
-## Visualise Summary
-
-```{r}
-#| echo: false
-#| eval: false
-
-g2 <- ggplot(C_summary,aes(x=stimulus_n,y=valuesMax,label=citekey,color=stimulus_genre_mixed))+
-  geom_point()+
-  geom_label_repel(size=1.5)+
-#  coord_flip()+
-  theme_bw()
-g2
-
-g3 <- ggplot(C_summary,aes(x=stimulus_n,y=valuesMax,label=citekey,color=model_class_id))+
-  geom_point()+
-  geom_label_repel(size=1.2)+
-#  coord_flip()+
-  theme_bw()
-g3
-
-## could be more informative when done with the full data
-C_studies$citekey<-factor(C_studies$citekey)
-
-g4 <- ggplot(C_studies,aes(x=stimulus_n,y=values,label=citekey,color=model_class_id,fill=model_class_id))+
-  geom_point(size=4)+
-  geom_label_repel(size=1.2, max.overlaps=50,show.legend = T,color='white')+
-#  scale_x_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
-#  scale_y_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
-  theme_bw()
-g4
-
-```
-
 ## Simple model complexity metric based on feature_n
@@
 #| eval: false
-
+C_studies$citekey <- factor(C_studies$citekey)
 tmp <- drop_na(C_studies)
@@
 #ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
+```
+
+## Aggregate valence and arousal results for nguygen2017, bhuvanakumar2023
+
+```{r}
+C_summary <- summarise(group_by(C_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
+                        #feature_n_complexity_genre=first(feature_n_complexity_genre)
+                        )
+# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
+C_summary[C_summary$citekey == "nguyen2017an",]$valuesMax <- C_summary[C_summary$citekey == "nguyen2017an",]$valuesMean
+
+# 2025-01-24: averaging across quadrants for bhuvanakumar study
+# subset study
+bhuvanakumar <- subset(
+  C_studies, 
+  stringr::str_detect(
+    C_studies$citekey,
+    "bhuvanakumar"
+    )
+)
+# group by algorithm to average across the four quadrants
+bhuvanakumar$model_algorithm <- substr(
+  bhuvanakumar$model_id, 
+  1, 
+  4
+)
+# take the average for each algorithm
+bhuvanakumar |> 
+  group_by(model_algorithm) |>
+  mutate(values = mean(values)) -> bhuvanakumar
+# overwrite values in C_summary
+C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMean <- mean(unique(bhuvanakumar$values))
+C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMedian <- median(unique(bhuvanakumar$values))
+C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMax <- max(unique(bhuvanakumar$values))
+
+remove(bhuvanakumar)
+
+```
+
+## Visualise Summary
+
+```{r}
+#| echo: false
+#| eval: false
+
+g2 <- ggplot(C_summary,aes(x=stimulus_n,y=valuesMax,label=citekey,color=stimulus_genre_mixed))+
+  geom_point()+
+  geom_label_repel(size=1.5)+
+#  coord_flip()+
+  theme_bw()
+g2
+
+g3 <- ggplot(C_summary,aes(x=stimulus_n,y=valuesMax,label=citekey,color=model_class_id))+
+  geom_point()+
+  geom_label_repel(size=1.2)+
+#  coord_flip()+
+  theme_bw()
+g3
+
+## could be more informative when done with the full data
+C_studies$citekey<-factor(C_studies$citekey)
+
+g4 <- ggplot(C_studies,aes(x=stimulus_n,y=values,label=citekey,color=model_class_id,fill=model_class_id))+
+  geom_point(size=4)+
+  geom_label_repel(size=1.2, max.overlaps=50,show.legend = T,color='white')+
+#  scale_x_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
+#  scale_y_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
+  theme_bw()
+g4
+
 ```

### 2025-01-26 analysis/analysis.qmd
fix(summaries): update model_class_id to reflect best performing model class

--- 2025-01-22 analysis/analysis.qmd
@@
 C_summary <- read.csv("C_summary.csv")
+
 C_classes <- read.csv("C_study_class_n.csv")
@@
 C_summary$classes <- 0
-C_summary[C_summary$n_classes < 3,]$classes <- "2"
-C_summary[C_summary$n_classes >= 3,]$classes <- ">2"
+C_summary[C_summary$n_classes == 2,]$classes <- "Binary"
+C_summary[C_summary$n_classes >= 3,]$classes <- "Multiclass"
 
@@
 ```
+```{r}
+m.cor <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n, # could also change to n_classes
+                 studlab = studyREF, # unique_id
+                 data = C_summary,
+                 subgroup = model_class_id,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 backtransf = TRUE,
+                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Classification: Summary")
+
+m.cor
+forest(m.cor,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "N"),studlab = citekey)
+
+funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+```
+
+```{r}
+#| fig-width: 12
+#| fig-height: 6
+forest(m.cor,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "N"),studlab = studyREF)
+
+fig2b<-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+library(forestplot)
+data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
+data<-dplyr::arrange(data,mean)
+
+fp1 <- grid.grabExpr(print(data |>
+  forestplot(labeltext = c(study, n, cor),
+             xlab = "Correlation",
+             xticks = c(0, .25,.5,.75, 1),
+             clip = c(0, 1))|>
+    fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
+    fp_append_row(mean  = m.cor$TE.common,
+                lower = m.cor$lower.common,
+                upper = m.cor$upper.common,
+                study = "Summary",
+                n = sum(m.cor$n),
+                cor = round(m.cor$TE.common,2),
+                is.summary = TRUE) |>
+  fp_set_style(box = "grey50",
+               line = "grey20",
+               summary = "black",
+                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
+                                ticks = gpar(cex = 0.80),
+                                xlab  = gpar(cex = 0.80)))|>
+    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
+)
+)
+
+source('../etc/custom_funnel_plot.R')
+fp2 <- custom_funnel_plot(m.cor)
+
+gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1),heights=c(2,1))
+
+```
 
@@
 #print(eggers.test(m.cor))
+
+O
 
@@
 m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
+#       subgroup = model_class_id, 
 #       subgroup = journal_type, 
-#       subgroup = stimulus_genre_mixed, 
+       subgroup = stimulus_genre_mixed, 
        tau.common = FALSE,

### 2025-01-26 analysis/preprocessing.qmd
fix(summaries): update model_class_id to reflect best performing model class

@@
                                       breaks = c(0,18,260,
-                                                 10000),
+                                                 14460),
                                       labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
@@
 R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
-                                      breaks = c(0,15,501,653,20000),
+                                      breaks = c(0,15,501,653,14460),
                                       labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
@@
 
-R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))
+R_summary <- summarise(group_by(R_studies,dimension,citekey,model_class_id),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))
+
+### Now filter out best model
+R_summary |> 
+  ungroup() |> 
+  filter(
+    valuesMax == max(valuesMax), 
+    .by = c(citekey, dimension)
+  ) -> R_summary
 
@@
 
-R_summary_split <- pivot_wider(R_summary,id_cols = citekey, names_from = c(dimension), values_from = valuesMax)
+R_summary_split <- pivot_wider(R_summary,id_cols = c(citekey, model_class_id), names_from = c(dimension), values_from = valuesMax)
 
@@
                                                  as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
-                                                 10000),
+                                                 14460),
                                       labels = c("Feature n < 236","Feature n > 236 & < 653","Feature n > 653"))
@@
 R_studies$feature_n_complexity <- cut(R_studies$feature_n,
-                                      breaks = c(0,30,300,10000),
+                                      breaks = c(0,30,300,14460),
                                       labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))
@@
 R_studies$feature_n_complexity_genre <- cut(R_studies$feature_n,
-                                      breaks = c(0,15,501,653,10000),
+                                      breaks = c(0,15,501,653,14460),
                                       labels = c("Small single genre study","Medium single genre/multigenre study","Medium-large single genre/multigenre study","Huge multigenre study"))
@@
 ```{r}
-C_summary <- summarise(group_by(C_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
+C_summary <- summarise(group_by(C_studies,dimension,citekey,model_class_id),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
                         #feature_n_complexity_genre=first(feature_n_complexity_genre)
@@
 remove(bhuvanakumar)
+
+C_summary |> 
+  ungroup() |> 
+  filter(
+    valuesMax == max(valuesMax), 
+    .by = c(citekey, dimension)
+) -> C_summary
 

### 2025-01-28 manuscript/manuscript.qmd
updated manuscript terms

@@
 To capture key details of each study, we added additional fields to BibTeX entries for each study.
-Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type, validation procedure and output measures.
+Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM), Linear Methods (LM), Tree-based Methods (TM), KS, Add.
+and KNN Methods (KM) -- validation procedure and output measures.
 Additionally, we included study results using executable *R* code containing custom functions for meta-analysis.
@@
 | Model N    | 204                             | 86                        | 290   |
-| Techniques | Neural Nets (NN): 66            | 25                        | 91    |
-| Techniques | Flexible Discriminants (FD): 50 | 26                        | 76    |
-| Techniques | Linear Methods (LM): 62         | 13                        | 75    |
-| Techniques | Random Forests (RF): 14         | 10                        | 34    |
-| Techniques | KS, Add. & KNN (KS): 12         | 12                        | 24    |
+| Techniques | Neural Nets: 66                 | 25                        | 91    |
+| Techniques | Support Vector Machines: 50     | 26                        | 76    |
+| Techniques | Linear Methods: 62              | 13                        | 75    |
+| Techniques | Tree-based methods: 14          | 10                        | 34    |
+| Techniques | KS, Add. & KNN: 12              | 12                        | 24    |
 | Feature N  | Min=3, Md=605, Max=6670         | Min=8, Md=126, Max=8904   | NA    |
@@
 
-Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (290 in total) with a relatively even distribution among the three most popular techniques: flexible discriminants, neural nets, and linear methods.
+Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (290 in total) with a relatively even distribution among the three most popular techniques: Neural Nets, SVMs, and Linear Methods.
 The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 9000 features [@zhang2023mo].
@@
 | LM           | 8,1762      | 0.797 \[0.614-0.899\]   | \-    | \-    | 0.1370   | 96.4% |
-| FD           | 6,4993      | 0.656 \[0.484-0.779\]   | \-    | \-     | 0.0574  | 96.9% |
+| SVM          | 6,4993      | 0.656 \[0.484-0.779\]   | \-    | \-     | 0.0574  | 96.9% |
 | NN           | 4,2249      | 0.393 \[-0.355-0.835\]  | \-    | \-     | 0.0761  | 97.1% |
-| RF           | 3,3330      | 0.750 \[0.292-0.928\]   | \-    | \-     | 0.093   | 98.5% |
+| TM           | 3,3330      | 0.750 \[0.292-0.928\]   | \-    | \-     | 0.093   | 98.5% |
 
-<!-- table updated TE 21/1/2025 -->
+<!-- table updated TE 21/1/2025, revised terms 28/1/2025 -->
 
@@
 When analyzing the studies across the five modeling techniques used, the prediction do differ significantly (_Q_(4) = 45.7, _p_ < .0001).
-Notably, linear models (LM) and flexible discriminants (FD) were the most common, with 8 and 6 studies, respectively, allowing for more confident interpretations.
+Notably, linear models (LM) and Support Vector Machines (SVM) were the most common, with 8 and 6 studies, respectively, allowing for more confident interpretations.
 Linear models achieved the highest prediction rate (_r_ = 0.784, 95% CI: 0.625–0.881), though this may be influenced by the smaller datasets typically used in these studies.
@@
 | LM           | 8, 1762     | 0.881 \[0.808-0.928\]     |      |        | 0.0846   | 93.3% |
-| FD           | 6, 4993     | 0.808 \[0.644-0.901\]     |      |        | 0.1125   | 98.0% |
+| SVM          | 6, 4993     | 0.808 \[0.644-0.901\]     |      |        | 0.1125   | 98.0% |
 | NN           | 4, 2249     | 0.533 \[0.328-0.691\]     |      |        | 0.0190   | 85.8% |
-| RF           | 3, 3330     | 0.809 \[0.733-0.864\]     |      |        | 0.0025   | 65.4% |
+| TM           | 3, 3330     | 0.809 \[0.733-0.864\]     |      |        | 0.0025   | 65.4% |
 

### 2025-01-29 analysis/preprocessing.qmd
fix(summaries): show  mean and median for all models
When correcting the best model_class_id, the previous commit grouped by best model type before summarizing the mean, max, and median. This commit updates valuesMean and valuesMedian columns to reflect all model classes  used in each study rather than only the best model class.

@@
 
-R_summary <- summarise(group_by(R_studies,dimension,citekey,model_class_id),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))
+# get best model class
+R_studies |> 
+  group_by(citekey, dimension, model_class_id) |> 
+  summarize(best_model = max(values)) |> 
+  filter(best_model == max(best_model)) -> best_model_class
 
-### Now filter out best model
-R_summary |> 
-  ungroup() |> 
-  filter(
-    valuesMax == max(valuesMax), 
-    .by = c(citekey, dimension)
-  ) -> R_summary
+best_model_class <- best_model_class[,c("citekey", "dimension", "model_class_id")]
+
+R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))
+
+R_summary <- left_join(R_summary, best_model_class)
 
@@
 
+# These are encoded slightly differently, so need to use a different approach
+
+# 2025-01-24: averaging across quadrants for bhuvanakumar study
+# subset study
+bhuvanakumar <- subset(
+  C_studies, 
+  stringr::str_detect(
+    C_studies$citekey,
+    "bhuvanakumar"
+    )
+)
+# group by algorithm to average across the four quadrants
+bhuvanakumar$model_algorithm <- substr(
+  bhuvanakumar$model_id, 
+  1, 
+  4
+)
+# take the average for each algorithm
+bhuvanakumar |> 
+  group_by(model_algorithm) |>
+  mutate(values = mean(values)) -> bhuvanakumar
+
+C_studies <-C_studies |> filter(citekey != "bhuvanakumar2023em")
+bhuvanakumar$model_algorithm <- NULL
+C_studies <- rbind(C_studies, bhuvanakumar)
+
+remove(bhuvanakumar)
+
+# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
+C_studies[C_studies$citekey == "nguyen2017an",]$values <- mean(C_studies[C_studies$citekey == "nguyen2017an",]$values)
+
 ```
@@
 ```{r}
-C_summary <- summarise(group_by(C_studies,dimension,citekey,model_class_id),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
+# get best model class
+C_studies |> 
+  group_by(citekey, dimension, model_class_id) |> 
+  summarize(best_model = max(values)) |> 
+  filter(best_model == max(best_model)) -> best_model_class_C
+
+best_model_class_C <- best_model_class_C[,c("citekey", "dimension", "model_class_id")]
+
+```
+
+```{r}
+C_summary <- summarise(group_by(C_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed)#,
                         #feature_n_complexity_genre=first(feature_n_complexity_genre)
                         )
-# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
-C_summary[C_summary$citekey == "nguyen2017an",]$valuesMax <- C_summary[C_summary$citekey == "nguyen2017an",]$valuesMean
 
-# 2025-01-24: averaging across quadrants for bhuvanakumar study
-# subset study
-bhuvanakumar <- subset(
-  C_studies, 
-  stringr::str_detect(
-    C_studies$citekey,
-    "bhuvanakumar"
-    )
-)
-# group by algorithm to average across the four quadrants
-bhuvanakumar$model_algorithm <- substr(
-  bhuvanakumar$model_id, 
-  1, 
-  4
-)
-# take the average for each algorithm
-bhuvanakumar |> 
-  group_by(model_algorithm) |>
-  mutate(values = mean(values)) -> bhuvanakumar
-# overwrite values in C_summary
-C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMean <- mean(unique(bhuvanakumar$values))
-C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMedian <- median(unique(bhuvanakumar$values))
-C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMax <- max(unique(bhuvanakumar$values))
-
-remove(bhuvanakumar)
-
-C_summary |> 
-  ungroup() |> 
-  filter(
-    valuesMax == max(valuesMax), 
-    .by = c(citekey, dimension)
-) -> C_summary
+C_summary <- left_join(C_summary, best_model_class_C)
 

### 2025-02-03 analysis/preprocessing.qmd
refactor(preprocessing): refactor model_class_id
rename random forests to tree-based methods and flexible discriminants to svm

@@
 # Set parameters and libraries
-export_decision <- FALSE
+export_decision <- TRUE
 verbose <- FALSE
@@
 metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'nn|gru|lstm|ltsm|long short term memory|rprop|mcan')]<-'Neural Nets'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Flexible Discriminants'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Support Vector Machines'
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient|tree|bag|boost')]<-'Random Forests'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient|tree|bag|boost')]<-'Tree-based Methods'
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf')]<-'Ensemble Learning'
@@
 tmp$model_class_id<-factor(tmp$model_class_id,
-                           levels = c("Neural Nets","Flexible Discriminants", "Kernel Smoothing, Additive and KNN", "Random Forests","Linear Methods"),
+                           levels = c("Neural Nets","Support Vector Machines", "Kernel Smoothing, Additive and KNN", "Tree-based Methods","Linear Methods"),
                            labels = c("Neural\nNets","Flexible\nDiscriminants", "KS\n & KNN", "Random\nForests", "Linear\nMethods"))

### 2025-02-09 manuscript/_datasets.qmd
updated the manuscript discussion, added dataset table

```{r}
#| label: datasets
```

<!-- This is a reduced table from /etc/Secondary Databases.md -->

| Index | Database                                                                                                                       | Stim. Type                    | Stim. Dur.                                  | Stim. N                                          | Feature N.                                                                 | Ppt. N                        | Feature Source                                        | In studies                                                                                                               |
| ----- | ------------------------------------------------------------------------------------------------------------------------------ | ----------------------------- | ------------------------------------------- | ------------------------------------------------ | -------------------------------------------------------------------------- | ----------------------------- | ----------------------------------------------------- | ------------------------------------------------------------------------------------------------------------------------ |
| 1     | [**MediaEval**](https://cvml.unige.ch/databases/emoMusic/)                                                                     | Western pop of various genres | 45                                          | 744                                              | 6669                                                                       | 10/track                      | OpenSMILE                                             | @bai2016di, @bai2017mu, @yang2021an, @chin2018pr, @coutinho2017sh, @markov2014mu, @medina2020em, @wang2022co, @xie2020mu |
| 2     | [**DEAM**](https://cvml.unige.ch/databases/DEAM/)                                                                              | Pop                           | 58 full-length and 1744 45-second excerpts  | 1802                                             | 260                                                                        | 5-10/track                    | OpenSMILE                                             | @sorussa2020em, @orjesek2022en, @panwar2019ar, @zhang2023mo                                                              |
| 3     | [**AMG1608**](https://github.com/loichan-tw/AMG1608_release)                                                                   | Pop                           | 30                                          | 1608                                             | 72                                                                         | 643 MTurk, 22 Taiwan subjects | MIRToolbox, YAAFE                                     | @chen2017co, @hu2017cr, @wang2022cr                                                                                      |
| 4     | [**EMOPIA**](https://annahung31.github.io/EMOPIA/)                                                                             | Piano Solo (pop music)        | 30 to 40                                    | 387                                              | 24                                                                         | 1 annotation/track            | MIDI Toolbox                                          | @bhuvanakumar2023em                                                                                                      |
| 5     | [**NTUMIR**](https://web.archive.org/web/20170510081611/mac.citi.sinica.edu.tw/~yang/MER/NTUMIR-60)                            | Famous pop songs              | 25                                          | 60                                               | 46                                                                         | 40 annotations/track.         | MIRToolbox, Sound Description Toolbox, MA Toolbox     | @chin2018pr                                                                                                              |
| 6     | [**Soundtracks**](https://osf.io/p6vkg/wiki/home/)                                                                             | Obscure film soundtracks      | 15                                          | 110                                              | NA                                                                         | 116 university students       | NA                                                    | @wang2022co                                                                                                              |
| 7     | [**PSIC3839**](https://github.com/xl2218066/PSIC3839)                                                                          | Chinese popular               | full? 180 s excerpts extracted for analyses | 3839                                             | NA                                                                         | 87                            | Librosa                                               | @xu2021us                                                                                                                |
| 8     | [**CH818**](ccmir.cite.hku.hk/data/)                                                                                           | Chinese pop                   | 30                                          | 818                                              | 15                                                                         | 3                             | MIRToolbox, PsySound, ChromaToolbox,Tempogram Toolbox | @hu2017cr                                                                                                                |
| 9     | [**Zhang et al. (2015)**](LINK)                                                                                                | Chinese pop                   | 30                                          | 171                                              | 84 dimensions                                                              | 10                            | MAToolbox, MIRToolbox, Coversongs                     | @zhang2016br                                                                                                             |
| 10    | [**PMEmo**](http://huisblog.cn/PMEmo/)                                                                                         | Choruses of top pop songs     | variable                                    | 794                                              | 6373 static; 260 acoustic low-level features                               | 457                           | ComParE 2013 baseline feature set                     | @zhang2023mo                                                                                                             |
| 11    | [**NJU-V1**](https://cs.nju.edu.cn/sufeng/data/musicmood.htm)                                                                  | Music clips (limited detail)  | variable                                    | 777                                              | Not reported                                                               | NA (lastfm tags)              | NA                                                    | @agarwal2021an                                                                                                           |
| 12    | [**ISMIR-2012**](http://yadingsong.blogspot.com/2015/03/popular-music-emotion-dataset-ismir2012.html)                          | Popular music                 | 30 or 60                                    | 2904                                             | 54                                                                         | NA (lastfm tags)              | MIRToolbox                                            | @agarwal2021an                                                                                                           |
| 13    | [**Spotify API**](https://developer.spotify.com/documentation/web-api)                                                         | Various                       | Variable                                    | 5192 used in @alvarez2023ri                      | 12                                                                         | NA                            | EchoNest                                              | @alvarez2023ri                                                                                                           |
| 14    | [**Acoustic Brainz**](https://acousticbrainz.org/)                                                                             | Various                       | Variable                                    | 60,000 used in @alvarez2023ri                    | Not reported                                                               | NA (lastfm tags)              | Essentia                                              | @alvarez2023ri                                                                                                           |
| 15    | [**MIREX2009**](https://www.music-ir.org/mirex/wiki/2009:Music_Structure_Segmentation_Results)                                 | Popular                       | Full?                                       | 297                                              | 3                                                                          | NA                            | Paulus & Klapuri (2009)                               | @yeh2014po                                                                                                               |
| 16    | [**Million Songs Dataset**](http://millionsongdataset.com/pages/getting-dataset/)                                              | Pop                           | Full                                        | 1,000,000                                        | 55                                                                         | None                          | EchoNest                                              | @cao2023th                                                                                                               |
| 17    | [**Free Music Archive**](https://freemusicarchive.org/home)                                                                    | Various                       | Variable                                    | >100,000                                         | NA                                                                         | NA                            | NA                                                    | @koh2023me                                                                                                               |
| 18    | [**Jamendo**](https://www.music-ir.org/mirex/wiki/2015:Main_Page) | Various                       | Variable                                    | 10,000                                           | 24                                                                         | NA                            | Metadata                                              | @hu2022de                                                                                                                |
| 19    | **Chinese Classical Music Dataset**                                                                                            | Chinese classical             | ~30s                                        | 500                                              | 557                                                                        | 20                            | Essentia, MIRToolbox                                  | @wang2022co                                                                                                              |

### 2025-02-09 manuscript/manuscript.qmd
updated the manuscript discussion, added dataset table

@@
 | Techniques | Linear Methods: 62              | 13                        | 75    |
-| Techniques | Tree-based methods: 14          | 10                        | 34    |
+| Techniques | Tree-based Methods: 14          | 10                        | 34    |
 | Techniques | KS, Add. & KNN: 12              | 12                        | 24    |
@@
 The funnel plot in panel B of Figure 2 shows clustering at the top of the plot (studies with low standard error) and no assumed larger diversity in the correlations when the error rates increase.
-However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$=5.05, CI95% -0.99-11.09, _t_ = 1.64, _p_ = 0.112, @eggersmith_1997).
-Coming back to the mean of valence correlation of 0.67 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect.
+However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$ = 5.05, CI95% -0.99-11.09, _t_ = 1.64, _p_ = 0.112, @eggersmith_1997).
+Coming back to the mean of valence correlation of 0.669 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect.
 This left 12 studies in the data and resulted in the meta-analytical pooled correlation of 0.686 (CI95% 0.635-0.731).
@@
 These studies also exhibited substantially higher heterogeneity ($\tau^2$ = 0.137) compared to other techniques, where $\tau^2$ values were less than half of this.
-Flexible discriminants performed at a similar level to the overall model average (_r_ = 0.656, 95% CI: 0.484–0.779).
-While there were only 3 studies involving random forests, these performed well, achieving _r_ = 0.750, 95% CI: 0.292–0.928), and the relatively poor performance of the neural network models represented in four studies (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
+While there were only 3 studies involving tree-based model (TM), these performed well, achieving _r_ = 0.750, 95% CI: 0.292–0.928), and the relatively poor performance of the neural network (NN) models represented in four studies (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
 Kernel smoothing and KNN models (with only 1 study represented) achieved relatively poor success as well, _r_ = 0.383, 95% CI: 0.348–0.426).
@@
 A mean estimate of 0.81 or higher is achieved by the majority (15 out of the 22 models).
-Due to large sample in ost studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am;@koh2023me; @saizclar2022pr; @wang2021ac].
+Due to large sample in most studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am;@koh2023me; @saizclar2022pr; @wang2021ac].
 The funnel plot in panel B illustrates the limited range of the correlations and show heavy clustering at the top of the plot (studies with low standard error).
@@
 The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (_Q_(2) = 3.47, _p_ = .176) despite the differing means (_r_ = 0.817 for studies with less than 18 features, _r_ = 0.586 for 18 to 260 features, and _r_ = 0.702 for studies utilising over 260 features).
-The differences in the techniques, however, does show variance between subgroups that is statistically significant (_Q_(4) = 50.47, _p_ < .0001), where at least Neural Nets achieve poor prediction of arousal (_r_ = 0.533) in comparison to other techniques.
+The differences in the techniques, however, does show statistically significant variance between subgroups (_Q_(4) = 50.47, _p_ < .0001).
+The Neural Nets (NN) achieve poor prediction of arousal (_r_ = 0.533) in comparison to other techniques.
 The caveat of this subgroup analysis is the small number of observations for five techniques.
@@
 
-###
+## Datasets
 
-secondary datasets, include a table, with an index of which studies/counts
+<!-- Note: this might take too much space in the main text, perhaps need to be moved to Supporting Information -->
 
-TABLE
+As we noted that several studies rely on the same datasets, summarising these could aid interpretation of the results.
+
+Table 5. Summary of datasets and studies utilising them.
+
+{{< include _datasets.qmd >}}
+
+The most frequently used 3 datasets are MediaEval [@soleymani20131000], DEAM[@aljanaki2017developing], and AMG1608[@chen2015amg1608].
+These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by relative large number of participants (either by experts, students, or crowdsourced workers).
+Two of the most popular datasets offer a large number (260 to 6669) features extracted with OpenSMILE [@eyben2010opensmile].
+Looking at the datasets more broadly, the diversity in size of the datasets (the number of tracks and features) is notable.
+While there are
 
@@
 
-There has been a considerable number of studies published involving MER models (N=96/46 full text articles considered), but in many cases the reporting standards or other quality issues or the lack of dedicated focus on music led us to reject a substantial proportion of studies.
-At the end, 34 studies remained in the analysis that overall reported xxxxx models.
+<!-- first para is your text from ICMPC paper -->
 
-## Concise summary of what we did and found
+Research on Music Emotion Recognition has steadily increased in popularity since the early 2000s, with technological advancements facilitating sharing of data sets, analysis tools, and music stimuli.
+Public forums like the Music Information Retrieval Exchange (MIREX) have facilitated collaborations between computer scientists, musicologists, and psychologists alike—spurring improvements in performance.
+Despite increasing complexity in the types of models and data sets used, no extant study has evaluated the relative merits of the tools, stimuli, and feature sets employed in MER studies.
+To provide a benchmark to guide future research, we present the first meta-analysis of music emotion recognition.
 
-## Main outcomes
+<!-- Concise summary of what we did and found -->
 
--   Arousal is easier to predict (r = 0.7627) than valence (r = 0.6236), as we predicted. The glass ceiling seems to be at ...
--   Classification ...
--   Model accuracy is surprisingly little affected by the number of features (?) or modelling technique (?).
--   Some of the complex state-of-the-art techniques (e.g., NNs) do not deliver impressive improvements over older techniques (e.g., SVR, RF)
--   Variation in study/model/data quality is large and can be seen in heterogenuity and the amount of studies eliminated
+We initially identified 96 studies involving MER models, but in many cases the reporting standards or other quality issues or the lack of dedicated focus on music led us to include 34 studies in the analysis that overall reported 290 models, 204 of them related to regression and 86 in classification studies.
+Comparing the most accurate model in each study, we observed reasonably accurate prediction of valence (r = 0.67 [0.56, 0.76]), and arousal (r = 0.81 [0.74, 0.86]) in regression studies.
+For both affective dimensions of the circumplex model, linear methods (valence r = 0.78, arousal r = 0.88) and tree-based models (valence = 0.75, arousal r = 0.81) outperformed neural networks (valence = 0.47, arousal = 0.66) and support vector machines (SVMs) (valence r = 0.58, arousal r = 0.79).
+In contrast, neural networks performed most accurately in classification studies (MCC = 0.93), followed by SVMs (MCC = 0.87) and tree-based models (MCC = 0.85).
+The models are applied to a variety of datasets that differ substantially in terms of size, annotation principles, and acoustic features counts and sources.
 
-[this is the discussion section]
+These results offer several important insights.
+First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from _r_ = 0.51 to 0.67.
+Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at _r_ = 0.83).
+For classification, studies reached variable classification rates from 0.497 F1 score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in 2013, whereas now the accuracy is XX.
 
-## Calls for action/points to improve in such studies
+<!-- These numbers above could be reinterpreted here, they are not comparable with our MCC -->
 
--   *Documentation* the details in full (features, stimuli, model details, cross-validation)
--   *Quality* of the underlying data (emotion ratings, classes, or even stimulus properties?
--   *Generalisibility* of the models (some studies such as X and Y address this by applying the models across several datasets)
--   Diversity in the evaluative aspects of studies: *overfitting*, numerous ways of cross-validating, not sharing data or analysis scripts, not reporting in the same way
--   What proportion of stimuli are Western music, and what genres tend to dominate?
+There is no single modelling technique that seems to arise on top although linear models and random forests perform best in regression studies, and neural networks and support vector machines excelling in classification tasks.
+We note that the model accuracy is surprisingly little affected by the number of features or the dataset size, likely the result of  cross-validation techniques used to avoid overfitting, but the heterogeneity of the materials used in different studies may also mask substantial differences.
+For instance, the smaller datasets tend to use linear models and deliver higher model accuracy than larger datasets and those with large amount of features.
+We surmise that this might relate to disciplinary difference, where the smaller datasets come from music psychology which put premium on data quality (quality control of the ground truth data and features) rather than on data size and modelling tecniques.
+If the quality control is succesful, it decreases the random error inherent in the human judgements.
+Also feature relevance and precision impacts the accuracy of the models.
+Unfortunately in many cases it is impossible to attribute the sources of error as the studies so far have not compared the feature sets systematically, nor a comparison of the datasets with identical features has been carried out.
+In future, it would be advantageous to systematically assess these sources of error in MER studies to allow to focus on where significant improvements can be made.
+
+More broadly, the present study revealed uncomfortable large variation in overall quality control and reporting in MER studies.
+In many cases, the reporting was insufficient to determine the features or their sources used in the models, and a high number of studies were discarded due to insufficient information about the data, model architectures, or the outcome measures.
+
+<!-- recommendations 1: reporting --> 
+Future reporting should contain the minimal information about the data, models, and success metrics.
+The modelling process should include the description of cross-validation, feature extraction techniques, feature reduction, and the actual accuracy measures.
+We would recommend future studies to utilise Matthews correlation coefficient for classification studies as currently there are numerous metrics (F1, F precision, recall, F average, classification rate), which are not mutually comparable.
+
+<!-- feature validation? -->
+
+Feature validation...?
+(Two extreme positions: a limited number of features that are perceptual validated (psychology) vs a large number of features where the models identify what is needed (deep learning/engineering).
+
+<!-- recommendations 2: sharing -->
+
+It would be highly beneficial to share the models and features transparently.
+If a study relies on published datasets, as most do, sharing the actual model (as code) and features would allow more direct comparison of model techniques for the same dataset.
+Also, not all datasets are shared or at least the sharing is only done partially.
+The copyright restrictions will limit the sharing of some datasets, but at least features and examples should be available.
+
+<!-- size, type of data --> 
+We also note that the majority of the dataset used in MER studies are relatively small in comparison to studies carried out in other fields of emotion recognition (refs here).
+
+The majority of the datasets are Western pop ... Music and annotators that represent the Global North do dominate the studies at the moment, ....
+
+Are the emotion recognition targets valid from the psychological and application point of view?
+Prediction of valence and arousal is popular, but has limited usefulness in practical applications that aim to capture experiences with music that are more aligned with models of music-induced emotions (such as GEMS etc.).
+
+Future efforts prioritizing feature validation, standardized reporting, and transparent sharing of research materials will lead to further improvements in MER.
 
@@
 
-We thank Greggs food-on-the-go retailer for sustaining the work with affordable sandwiches and coffee.
+We thank the _Institute of Advanced Study_ at Durham University for creating the environment in which this study was created.
 

### 2025-02-09 manuscript/manuscript.qmd
updated manuscript and added abstract

@@
 abstract: |
- This is a meta-analysis of music emotion recognition.
-An analysis of the articles published between 2014-2024 containing models predicting either valence and arousal or emotion categories was carried out.
-A total of xx studies were included
-
+ This meta-analysis examines music emotion recognition (MER) models published between 2014 and 2024, focusing on predictions of valence, arousal, and categorical emotions.
+A total of 553 studies were identified, of which 96 full-text articles were assessed, resulting in a final review of 34 studies.
+These studies reported 204 models, including 86 for emotion classification and 204 for regression.
+Using the best-performing model from each study, we found that valence and arousal were predicted with reasonable accuracy (r = 0.67 and r = 0.81, respectively), while classification models achieved an accuracy of 0.xx.
+Across modeling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed superior performance in classification tasks.
+We highlight key recommendations for future MER research, emphasizing the need for greater transparency, feature validation, and standardized reporting to improve comparability across studies.
 keywords          : "music, emotion, recognition, meta-analysis"
@@
 
-[^1]: The best-performing model to date reached 69.83 % in the 2017 competition (Park et al., 2017)[\@park2017representation](https://scholar.google.com/scholar?q=Representation%20learning%20using%20artist%20labels%20for%20audio%20classification%20tasks%2C%20Park).
+[^1]: The best-performing model to date reached 69.83 % in the 2017 competition [@park2017representation].
 
@@
 
+#### Notes to results: In the pre-registration, we promised the following:
+
+- groupings based on genre, model complexity (high, medium, low), model validation (exists or not)
+- we promised to carry out sensitivity analyses based on type of journal the studies were published in.
+
 ## Datasets
@@
 
-The most frequently used 3 datasets are MediaEval [@soleymani20131000], DEAM[@aljanaki2017developing], and AMG1608[@chen2015amg1608].
+The most frequently used 3 datasets are MediaEval [@soleymani20131000], DEAM [@aljanaki2017developing], and AMG1608 [@chen2015amg1608].
 These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by relative large number of participants (either by experts, students, or crowdsourced workers).
 Two of the most popular datasets offer a large number (260 to 6669) features extracted with OpenSMILE [@eyben2010opensmile].
-Looking at the datasets more broadly, the diversity in size of the datasets (the number of tracks and features) is notable.
-While there are
+Looking at the datasets more broadly, the diversity in the size and the features of the datasets is notable.
+Only two feature extraction tools are used across multiple datasets (OpenSMILE and MIR Toolbox, @lartillot2007matlab).
+However, despite this diversity, there does not seem to be a direct link between the model success rates and the features themselves, or at least separating the features from variation created by the dataset size, annotation accuracy and genre is not possible.
 
@@
 
-We initially identified 96 studies involving MER models, but in many cases the reporting standards or other quality issues or the lack of dedicated focus on music led us to include 34 studies in the analysis that overall reported 290 models, 204 of them related to regression and 86 in classification studies.
-Comparing the most accurate model in each study, we observed reasonably accurate prediction of valence (r = 0.67 [0.56, 0.76]), and arousal (r = 0.81 [0.74, 0.86]) in regression studies.
-For both affective dimensions of the circumplex model, linear methods (valence r = 0.78, arousal r = 0.88) and tree-based models (valence = 0.75, arousal r = 0.81) outperformed neural networks (valence = 0.47, arousal = 0.66) and support vector machines (SVMs) (valence r = 0.58, arousal r = 0.79).
-In contrast, neural networks performed most accurately in classification studies (MCC = 0.93), followed by SVMs (MCC = 0.87) and tree-based models (MCC = 0.85).
-The models are applied to a variety of datasets that differ substantially in terms of size, annotation principles, and acoustic features counts and sources.
+We initially identified 96 studies involving MER models, but in many cases the reporting standards or other quality issues or the lack of dedicated focus on music led us to include 34 studies in the analysis that overall reported 290 models, 204 related to regression and 86 classification.
+Comparing the most accurate model in each study, we observed reasonably accurate prediction of valence (_r_ = 0.67 [0.56, 0.76]), and arousal (_r_ = 0.81 [0.74, 0.86]) in regression studies.
+For both affective dimensions of the circumplex model, linear methods (valence _r_ = 0.78, arousal _r_ = 0.88) and tree-based models (valence _r_ = 0.75, arousal _r_ = 0.81) outperformed neural networks (valence = 0.47, arousal = 0.66) and support vector machines (SVMs) (valence _r_ = 0.58, arousal _r_ = 0.79).
+In contrast, neural networks performed most accurately in classification studies (_MCC_ = 0.93), followed by SVMs (_MCC_ = 0.87) and tree-based models (_MCC_ = 0.85).
+The models applied to a variety of datasets differ substantially in terms of size, annotation principles, and the number of features and sources of these features.
 
@@
 Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at _r_ = 0.83).
-For classification, studies reached variable classification rates from 0.497 F1 score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in 2013, whereas now the accuracy is XX.
+For classification, studies reached variable classification rates from 0.497 using _F~1~_ score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is 0.930 (?).
 
@@
 
-There is no single modelling technique that seems to arise on top although linear models and random forests perform best in regression studies, and neural networks and support vector machines excelling in classification tasks.
+Second, there is no single modelling technique that seems to arise on top, although linear models and random forests perform best in regression studies, and neural networks and support vector machines excel in classification tasks.
 We note that the model accuracy is surprisingly little affected by the number of features or the dataset size, likely the result of cross-validation techniques used to avoid overfitting, but the heterogeneity of the materials used in different studies may also mask substantial differences.
-For instance, the smaller datasets tend to use linear models and deliver higher model accuracy than larger datasets and those with large amount of features.
-We surmise that this might relate to disciplinary difference, where the smaller datasets come from music psychology which put premium on data quality (quality control of the ground truth data and features) rather than on data size and modelling tecniques.
-If the quality control is succesful, it decreases the random error inherent in the human judgements.
-Also feature relevance and precision impacts the accuracy of the models.
-Unfortunately in many cases it is impossible to attribute the sources of error as the studies so far have not compared the feature sets systematically, nor a comparison of the datasets with identical features has been carried out.
-In future, it would be advantageous to systematically assess these sources of error in MER studies to allow to focus on where significant improvements can be made.
+For instance, the smaller datasets tend to use linear models and deliver higher model accuracy than larger datasets and those with a large number of features.
+We surmise that this might relate to disciplinary difference, where the smaller datasets come from music psychology, which puts a premium on data quality (quality control of the ground-truth data and features) rather than on data size and modelling techniques.
+If quality control is succesful, it decreases the random error inherent in human judgements.
+Furthermore, the relevance and the precision of the features impacts the accuracy of the models.
+Unfortunately, in many cases, it is impossible to attribute the sources of error, as the studies so far have not compared the feature sets systematically, nor a comparison of the datasets with identical features has been carried out.
+In the future, it would be advantageous to systematically assess these sources of error in MER studies to allow us to focus on where significant improvements can be made.
 
-More broadly, the present study revealed uncomfortable large variation in overall quality control and reporting in MER studies.
-In many cases, the reporting was insufficient to determine the features or their sources used in the models, and a high number of studies were discarded due to insufficient information about the data, model architectures, or the outcome measures.
+More broadly, the present study revealed an uncomfortable large variation in overall quality control and reporting in MER studies.
+In many cases, the reporting was insufficient to determine the features or their sources used in the models, and a large number of studies were discarded due to insufficient information about the data, model architectures, or outcome measures.
 
 <!-- recommendations 1: reporting -->
-Future reporting should contain the minimal information about the data, models, and success metrics.
-The modelling process should include the description of cross-validation, feature extraction techniques, feature reduction, and the actual accuracy measures.
-We would recommend future studies to utilise Matthews correlation coefficient for classification studies as currently there are numerous metrics (F1, F precision, recall, F average, classification rate), which are not mutually comparable.
+
+Future reports should contain viable information about the data, models, and success metrics.
+The modelling process should include a description of cross-validation, feature extraction technique, feature reduction (if used), and actual accuracy measures.
+We would recommend future studies to use Matthews correlation coefficient for classification studies as currently there are numerous metrics (_F~1~_, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
 
@@
 Feature validation...?
-(Two extreme positions: a limited number of features that are perceptual validated (psychology) vs a large number of features where the models identify what is needed (deep learning/engineering).
+(Two extreme positions: a limited number of features that are perceptual validated (psychology) -- domain knowledge –– vs a large number of features where the models identify what is needed (deep learning/engineering).
 
@@
 
-It would be highly beneficial to share the models and features transparently.
-If a study relies on published datasets, as most do, sharing the actual model (as code) and features would allow more direct comparison of model techniques for the same dataset.
-Also, not all datasets are shared or at least the sharing is only done partially.
-The copyright restrictions will limit the sharing of some datasets, but at least features and examples should be available.
+It would be beneficial to share models and features transparently.
+If a study relies on published datasets, as most do, sharing the actual model (as code/notebooks) and features would allow for more direct comparison of model techniques for the same dataset.
+Also, not all datasets are shared, or at least the sharing is only done partially.
+The copyright restrictions may limit the sharing of some datasets, but at least features and examples should be available.
 
 <!-- size, type of data --> 
-We also note that the majority of the dataset used in MER studies are relatively small in comparison to studies carried out in other fields of emotion recognition (refs here).
+We also note that the majority of the datasets used in MER studies are relatively small, but comparable to datasets for modeling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
+However, annotated datasets for visual scenes and objects tend to be much larger, often exceeding 100,000 annotated examples [@deng2009imagenet; @krishna2017visual].
+Datasets of these magnitudes seem to be required for appropriate utilisation of deep learning algorithms, which may explain the modest results observed in the music emotion recognition studies.
 
-The majority of the datasets are Western pop ... Music and annotators that represent the Global North do dominate the studies at the moment, ....
+The majority of the datasets are Western pop ... Music and annotators that represent the Global North do dominate the studies at the moment, and ... [@bornDiversifyingMIRKnowledge2020].
 
 Are the emotion recognition targets valid from the psychological and application point of view?
-Prediction of valence and arousal is popular, but has limited usefulness in practical applications that aim to capture experiences with music that are more aligned with models of music-induced emotions (such as GEMS etc.).
+Prediction of valence and arousal is popular, but has limited usefulness in practical applications that aim to capture experiences with music that are more aligned with models of music-induced emotions (such as GEMS by @zentner2008emotions).
 
-Future efforts prioritizing feature validation, standardized reporting, and transparent sharing of research materials will lead to further improvements in MER.
+Future efforts to prioritize feature validation, standardized reporting, and transparent sharing of research materials are needed for consistent improvements in MER.
 
@@
 
-### Acknowledgements
-
-We thank the _Institute of Advanced Study_ at Durham University for creating the environment in which this study was created.
-
 # References

### 2025-02-09 analysis/analysis.qmd
feat(analysis.qmd): update classification analyses

--- 2025-01-22 analysis/analysis.qmd
@@
 
-## Classification studies
+## Classification studies: overall success
 
@@
 
-m.cor <- metacor(cor = valuesMax,     # values 
+m.cor.c.all <- metacor(cor = values,     # values 
+                 n = stimulus_n,
+                 studlab = studyREF, # unique_id
+                 data = C_studies,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 backtransf = TRUE,
+                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Classification: Summary")
+
+m.cor.c.all
+
+#m.cor_backtransformed <- m.cor
+#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
+print(funnel(m.cor.c.all, common = FALSE, studlab=TRUE,backtransf=TRUE))
+
+```
+## Define splits for genre & stimulus n combinations
+
+```{r}
+# get stimulus and genre metadata for classification studies:
+C_studies |>
+  group_by(citekey) |>
+  summarize(feature_n = unique(feature_n),
+            feature_n_complexity = unique(feature_n_complexity),
+            stimulus_genre_mixed = unique(stimulus_genre_mixed)) -> C_splits
+
+# create feature_n_complexity_genre column:
+C_splits$feature_n_complexity_genre <- ""
+
+# define splits
+C_splits[C_splits$feature_n_complexity %in% "Feature n > 30 & < 300" &
+        C_splits$stimulus_genre_mixed == "MultiGenre",]$feature_n_complexity_genre <- "Medium multi-genre study"
+C_splits[C_splits$stimulus_genre_mixed %in% "SingleGenre" &
+                             C_splits$feature_n_complexity %in% "Feature n < 30" ,]$feature_n_complexity_genre <- "Small single-genre study"
+C_splits[C_splits$feature_n_complexity == "Feature n > 300",]$feature_n_complexity_genre <- "Huge single or multigenre study"
+C_splits[C_splits$citekey == "alvarez2023ri",]$feature_n_complexity_genre <- "Small, multi-genre study"
+C_splits[C_splits$citekey == "zhang2016br",]$feature_n_complexity_genre <- "Medium, single-genre study"
+# add splits to summary:
+C_summary <- left_join(C_summary, C_splits)
+
+```
+
+### Define splits for binary vs. multiclass
+
+```{r}
+C_summary$classes <- 0
+C_summary[C_summary$n_classes < 3,]$classes <- "Binary"
+C_summary[C_summary$n_classes >= 3,]$classes <- "Multiclass"
+
+```
+
+## Classification models: best models
+
+```{r}
+m.cor.c <- metacor(cor = valuesMax,     # values 
                  n = stimulus_n,
@@
 
-print(m.cor)
+```
 
-#m.cor_backtransformed <- m.cor
-#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-print(funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE))
+### Custom funnel for classification studies
+
+```{r}
+#| fig-width: 12
+#| fig-height: 6
+fig3a <- forest(m.cor.c,
+                sortvar = TE,
+                prediction = FALSE, 
+                print.tau2 = FALSE,
+                leftlabs = c("Author", "N"),studlab = studyREF)
+
+fig3b<-funnel(m.cor.c, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+library(forestplot)
+data<-tibble::tibble(mean=m.cor.c$cor,lower=FisherZInv(m.cor.c$lower),upper=FisherZInv(m.cor.c$upper),study=m.cor.c$studlab,n=m.cor.c$n,cor=round(m.cor.c$cor,2))
+data<-dplyr::arrange(data,mean)
+
+fp3 <- grid.grabExpr(print(data |>
+                             forestplot(labeltext = c(study, n, cor),
+                                        xlab = "Correlation",
+                                        xticks = c(0, .25,.5,.75, 1),
+                                        clip = c(0, 1))|>
+                             fp_add_header(study = "Study",n = "N",cor = expression(italic(r))) |>
+                             fp_append_row(mean  = m.cor.c$TE.common,
+                                           lower = m.cor.c$lower.common,
+                                           upper = m.cor.c$upper.common,
+                                           study = "Summary",
+                                           n = sum(m.cor.c$n),
+                                           cor = round(m.cor.c$TE.common,2),
+                                           is.summary = TRUE) |>
+                             fp_set_style(box = "grey50",
+                                          line = "grey20",
+                                          summary = "black",
+                                          txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
+                                                           ticks = gpar(cex = 0.80),
+                                                           xlab  = gpar(cex = 0.80)))|>
+                             fp_decorate_graph(grid = structure( m.cor.c$TE.common,gp = gpar(lty = 2, col = "grey30")))
+)
+)
+
+source('../etc/custom_funnel_plot.R')
+fp4 <- custom_funnel_plot(m.cor.c)
+
+gridExtra::grid.arrange(fp3, fp4, ncol=2, widths=c(2,1),heights=c(2,1))
 
 ```
+
 #### Custom plot
@@
 library(ggrepel)
-tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)
+tmpdata <- data.frame(SE = FisherZInv(m.cor.c$seTE), Zr = FisherZInv(m.cor.c$TE),studies=m.cor.c$studlab)
 
@@
 
-#### Visualise (forest and funnel plots)
+## Exploring heterogeneity
 
 ```{r}
-forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "N"),studlab = citekey)
+#| eval: true
+#| echo: true
+# Method 1: Give us the Egger's test about beta coefficient from funnel
+print(eggers.test(m.cor.c))
 
-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+# Method 2: Find the impact to the results when removing those outside the 95CI
+O <- find.outliers(m.cor.c) # 13 remaining out of 24
+print(O)
+# Method 3: Leave-out-out analysis etc for individual influence (not useful here)
+#infan <- InfluenceAnalysis(m.cor)
 
+# Method 4: Focus on 10% of most precise studies (Stanley, Jarrel, Doucouliagos 2010)
+thres<-quantile(m.cor.c$seTE,0.1)
+ind<-m.cor.c$seTE<=as.numeric(thres)
+m.cor10pct <- update(m.cor.c, subset = which(ind))
+
+# Method 5: P curve analysis (Simonsohn, Simmons & Nelson, 2015)
+pcurve(m.cor.c)
 ```
-#### By class n = 2 vs. > 2
-```{r}
-C_summary$classes <- 0
-C_summary[C_summary$n_classes < 3,]$classes <- "2"
-C_summary[C_summary$n_classes >= 3,]$classes <- ">2"
-
-m.cor <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n, # could also change to n_classes
-                 studlab = studyREF, # unique_id
-                 data = C_summary,
-                 subgroup = classes,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 backtransf = TRUE,
-                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Classification: Summary")
-
-forest(m.cor,
-       sortvar = TE,
-       prediction = FALSE, 
-             print.tau2 = FALSE,
-             leftlabs = c("Author", "N"),studlab = citekey)
-
-funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
-
-```
-
-#### Explore qualities (in progress)
+### Re-run the analysis without outliers
 
 ```{r}
-O <- find.outliers(m.cor)
-# 6 datasets identified as outliers, without them the r drops to 0.5781
-#infan <- InfluenceAnalysis(m.cor)
-#print(eggers.test(m.cor))
+#| eval: true
+#| echo: false
+outliers <- O$out.study.random
 
-```
-
-#### Re-run the analysis without the outliers
-
-```{r}
-#| eval: false
-#| echo: false
-outliers <- c("")
-
-tmp2<-tmp[!tmp$unique_id %in% outliers,]
-m.cor <- metacor(cor = values, 
+tmp2<-C_summary[!C_summary$studyREF %in% outliers,]
+m.cor.c.o <- metacor(cor = valuesMax, 
                  n = stimulus_n,
-                 studlab = unique_id, # unique_id
+                 studlab = tmp2$studyREF,
                  data = tmp2,
@@
 
-print(m.cor)
+```
 
-fp <- funnel(m.cor, common = TRUE,studlab=FALSE)
+#### Visualise (forest and funnel plots)
 
+```{r}
+forest(m.cor.c.o,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "N"),studlab = citekey)
+
+funnel(m.cor.c.o, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+```
+## Subgroup analyses
+
+### By binary vs. multi-class classification
+
+```{r}
+m.cor_classes <- update(m.cor.c, 
+       subgroup = C_summary$classes, 
+       tau.common = FALSE,
+       prediction = TRUE)
+
+forest(m.cor_classes,
+       sortvar = TE,
+       prediction = FALSE, 
+             print.tau2 = FALSE,
+             leftlabs = c("Author", "N"),studlab = citekey)
+
+funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+```
+
+### By single vs. multi-genre
+
+```{r}
+#| eval: false
+m.cor_subgroups <- update(m.cor.c, 
+       subgroup = stimulus_genre_mixed, 
+       tau.common = FALSE,
+       prediction = TRUE)
+
+print(m.cor_subgroups)
+#forest(m.cor_subgroups,subgroup=TRUE)
+```
+
+### By genre + feature complexity
+
+```{r}
+m.cor_complexity <- update(m.cor.c, 
+       subgroup = C_summary$feature_n_complexity_genre, 
+       tau.common = FALSE,
+       prediction = TRUE)
+
+print(m.cor_complexity)
+```
+### By model type
+
+```{r}
+#| eval: false
+m.cor_subgroups <- update(m.cor.c, 
+       subgroup = model_class_id, 
+       tau.common = FALSE,
+       prediction = TRUE)
+
+print(m.cor_subgroups)
+#forest(m.cor_subgroups,subgroup=TRUE)
 ```
@@
 #| eval: true
-tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE, studies=m.cor$studlab)
+tmpdata <- data.frame(SE = m.cor.c$seTE, Zr = m.cor.c$TE, studies=m.cor.c$studlab)
 
@@
 
-estimate = m.cor$TE.common
-se = m.cor$seTE.common
-se.seq=seq(0, max(m.cor$cor), 0.001)
+estimate = m.cor.c$TE.common
+se = m.cor.c$seTE.common
+se.seq=seq(0, max(m.cor.c$cor), 0.001)
 ll95 = estimate-(1.96*se.seq)
@@
   scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.15,0),expand=c(0.00,0.00))+
-  scale_y_continuous(breaks=seq(0.3,1.25,0.20),limits=c(0.3,1.23))+
+ # scale_y_continuous(breaks=seq(0.3,1.25,0.20),limits=c(0.3,1.23))+
   coord_flip()+
@@
 
-#### Subgroup analysis according to techniques
-
-add `journal_type` and `stimulus_genre_mixed` as a grouping option
-
-```{r}
-#| eval: false
-m.cor_subgroups <- update(m.cor, 
-       subgroup = model_class_id, 
-#       subgroup = journal_type, 
-#       subgroup = stimulus_genre_mixed, 
-       tau.common = FALSE,
-       prediction = TRUE)
-
-print(m.cor_subgroups)
-#forest(m.cor_subgroups,subgroup=TRUE)
-```
-
 - Idea: visualise the distributions of the model successes within studies (done in preprocessing)

### 2025-02-18 analysis/preprocessing.qmd
chore(preprocessing): update model categorizations

@@
 metaMER_results$model_class_id <- 'Unclassified'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis|linear discriminant|quadratic discriminant')] <- 'Linear Methods' # Class name from Elements of Stat.."
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis|linear discriminant|quadratic discriminant|polygonal')] <- 'Linear Methods' # Class name from Elements of Stat.."
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Classification'
-#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods' #
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|gmm|local|polynomial|polygonal|knn|mars|gam')]<-'Kernel Smoothing, Additive and KNN'
+#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods'
+
+# make sure nn gets classified before knn
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'nn|gru|lstm|ltsm|long short term memory|rprop|mcan')]<-'Neural Nets'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|local|knn|mars|gam')]<-'Kernel Smoothing, Additive and KNN'
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'adaboost|gradient')]<-'Boosting'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'nn|gru|lstm|ltsm|long short term memory|rprop|mcan')]<-'Neural Nets'
-metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Support Vector Machines'
+metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'gmm|svm|svr|support vector regression|smoreg|smo ')]<-'Support Vector Machines'
 #metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
@@
 
-R_studies$feature_n_categories <-cut(R_studies$feature_n,
-                                      breaks = c(0,18,260,
-                                                 14460),
-                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
+# R_studies$feature_n_categories <-cut(R_studies$feature_n,
+#                                       breaks = c(0,18,260,
+#                                                  14460),
+#                                       labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
+
+R_studies$feature_n_complexity <- cut(R_studies$feature_n,
+                                      breaks = c(0,30,300,14460),
+                                      labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))
 
@@
 
-R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_categories=first(feature_n_categories),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))
+R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=TRUE),valuesMedian=median(values,na.rm=TRUE),valuesMax=max(values,na.rm=TRUE),stimulus_n=first(stimulus_n),studyREF=first(studyREF),feature_n=first(feature_n),journal_type=first(journal_type),feature_n=first(feature_n),feature_n_complexity=first(feature_n_complexity),stimulus_genre_mixed=first(stimulus_genre_mixed),feature_n_complexity_genre=first(feature_n_complexity_genre))
 
@@
 # Assign
-R_studies$feature_n_complexity <- cut(R_studies$feature_n,
-                                      breaks = c(0,
-                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
-                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
-                                                 14460),
-                                      labels = c("Feature n < 236","Feature n > 236 & < 653","Feature n > 653"))
-
-R_studies$feature_n_complexity <- cut(R_studies$feature_n,
-                                      breaks = c(0,30,300,14460),
-                                      labels = c("Feature n < 30","Feature n > 30 & < 300","Feature n > 300"))
+# R_studies$feature_n_complexity <- cut(R_studies$feature_n,
+#                                       breaks = c(0,
+#                                                  as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
+#                                                  as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
+#                                                  14460),
+#                                       labels = c("Feature n < 236","Feature n > 236 & < 653","Feature n > 653"))
 

### 2025-02-18 analysis/analysis.qmd
feat(analysis): update analysis based on main branch file
- simplify splits - update feature_n_complexity

@@
 tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
-S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove 
+S <- summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
 print(knitr::kable(S))
@@
 tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
+tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
 m.cor3 <- metacor(cor = valuesMax,     # values 
@@
                  prediction = TRUE,
-                 subgroup =  feature_n_categories,
+                 subgroup =  feature_n_complexity,
 #                 backtransf = TRUE,
@@
 print(m.cor3)
-S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+S<-summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
 print(S)
@@
 tmp <- dplyr::filter(R_summary,dimension=="valence")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values
+tmp<-tmp[!is.na(tmp$feature_n_complexity),] # removemissing values
 
-S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
+S<-summarise(group_by(tmp,stimulus_genre_mixed),n=n(),obs=sum(stimulus_n))
 print(knitr::kable(S))
@@
                  prediction = TRUE,
-                 subgroup =  feature_n_complexity_genre,
+                 subgroup =  stimulus_genre_mixed,
 #                 backtransf = TRUE,
@@
 tmp <- dplyr::filter(R_summary,dimension=="arousal")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
-S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
+tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove 
+S <- summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
 print(knitr::kable(S))
@@
 tmp <- dplyr::filter(R_summary,dimension=="arousal")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
+tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
 m.cor3 <- metacor(cor = valuesMax,     # values 
@@
 tmp <- dplyr::filter(R_summary,dimension=="arousal")
-tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
+tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
 
-S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
+S<-summarise(group_by(tmp,stimulus_genre_mixed),n=n(),obs=sum(stimulus_n))
 print(knitr::kable(S))
@@
 ```{r}
-m.cor_complexity <- update(m.cor.c, 
-       subgroup = C_summary$feature_n_complexity_genre, 
-       tau.common = FALSE,
-       prediction = TRUE)
-
-print(m.cor_complexity)
+# m.cor_complexity <- update(m.cor.c, 
+#        subgroup = C_summary$feature_n_complexity_genre, 
+#        tau.common = FALSE,
+#        prediction = TRUE)
+# 
+# print(m.cor_complexity)
 ```

### 2025-02-18 manuscript/_datasets.qmd

@@
 
-| Index | Database                                                                                                                       | Stim.
+| Dataset                                                                                                | Stim.
 Type                 | Stim.
 Dur.
-| Stim.
-N                                          | Feature N.
-| Ppt.
+(s)  | Stim.
+N          | Feature N    | Ppt.
 N          | Feature Source                                        | In studies                                                                                                               |
-| ----- | ------------------------------------------------------------------------------------------------------------------------------ | ----------------------------- | ------------------------------------------- | ------------------------------------------------ | -------------------------------------------------------------------------- | ----------------------------- | ----------------------------------------------------- | ------------------------------------------------------------------------------------------------------------------------ |
-| 1     | [**MediaEval**](https://cvml.unige.ch/databases/emoMusic/)                                                                     | Western pop of various genres | 45                                          | 744                                              | 6669                                                                       | 10/track                      | OpenSMILE                                             | @bai2016di, @bai2017mu, @yang2021an, @chin2018pr, @coutinho2017sh, @markov2014mu, @medina2020em, @wang2022co, @xie2020mu |
-| 2     | [**DEAM**](https://cvml.unige.ch/databases/DEAM/)                                                                              | Pop                           | 58 full-length and 1744 45-second excerpts  | 1802                                             | 260                                                                        | 5-10/track                    | OpenSMILE                                             | @sorussa2020em, @orjesek2022en, @panwar2019ar, @zhang2023mo                                                              |
-| 3     | [**AMG1608**](https://github.com/loichan-tw/AMG1608_release)                                                                   | Pop                           | 30                                          | 1608                                             | 72                                                                         | 643 MTurk, 22 Taiwan subjects | MIRToolbox, YAAFE                                     | @chen2017co, @hu2017cr, @wang2022cr                                                                                      |
-| 4     | [**EMOPIA**](https://annahung31.github.io/EMOPIA/)                                                                             | Piano Solo (pop music)        | 30 to 40                                    | 387                                              | 24                                                                         | 1 annotation/track            | MIDI Toolbox                                          | @bhuvanakumar2023em                                                                                                      |
-| 5     | [**NTUMIR**](https://web.archive.org/web/20170510081611/mac.citi.sinica.edu.tw/~yang/MER/NTUMIR-60)                            | Famous pop songs              | 25                                          | 60                                               | 46                                                                         | 40 annotations/track.
-| MIRToolbox, Sound Description Toolbox, MA Toolbox     | @chin2018pr                                                                                                              |
-| 6     | [**Soundtracks**](https://osf.io/p6vkg/wiki/home/)                                                                             | Obscure film soundtracks      | 15                                          | 110                                              | NA                                                                         | 116 university students       | NA                                                    | @wang2022co                                                                                                              |
-| 7     | [**PSIC3839**](https://github.com/xl2218066/PSIC3839)                                                                          | Chinese popular               | full?
-180 s excerpts extracted for analyses | 3839                                             | NA                                                                         | 87                            | Librosa                                               | @xu2021us                                                                                                                |
-| 8     | [**CH818**](ccmir.cite.hku.hk/data/)                                                                                           | Chinese pop                   | 30                                          | 818                                              | 15                                                                         | 3                             | MIRToolbox, PsySound, ChromaToolbox,Tempogram Toolbox | @hu2017cr                                                                                                                |
-| 9     | [**Zhang et al.
-(2015)**](LINK)                                                                                                | Chinese pop                   | 30                                          | 171                                              | 84 dimensions                                                              | 10                            | MAToolbox, MIRToolbox, Coversongs                     | @zhang2016br                                                                                                             |
-| 10    | [**PMEmo**](http://huisblog.cn/PMEmo/)                                                                                         | Choruses of top pop songs     | variable                                    | 794                                              | 6373 static; 260 acoustic low-level features                               | 457                           | ComParE 2013 baseline feature set                     | @zhang2023mo                                                                                                             |
-| 11    | [**NJU-V1**](https://cs.nju.edu.cn/sufeng/data/musicmood.htm)                                                                  | Music clips (limited detail)  | variable                                    | 777                                              | Not reported                                                               | NA (lastfm tags)              | NA                                                    | @agarwal2021an                                                                                                           |
-| 12    | [**ISMIR-2012**](http://yadingsong.blogspot.com/2015/03/popular-music-emotion-dataset-ismir2012.html)                          | Popular music                 | 30 or 60                                    | 2904                                             | 54                                                                         | NA (lastfm tags)              | MIRToolbox                                            | @agarwal2021an                                                                                                           |
-| 13    | [**Spotify API**](https://developer.spotify.com/documentation/web-api)                                                         | Various                       | Variable                                    | 5192 used in @alvarez2023ri                      | 12                                                                         | NA                            | EchoNest                                              | @alvarez2023ri                                                                                                           |
-| 14    | [**Acoustic Brainz**](https://acousticbrainz.org/)                                                                             | Various                       | Variable                                    | 60,000 used in @alvarez2023ri                    | Not reported                                                               | NA (lastfm tags)              | Essentia                                              | @alvarez2023ri                                                                                                           |
-| 15    | [**MIREX2009**](https://www.music-ir.org/mirex/wiki/2009:Music_Structure_Segmentation_Results)                                 | Popular                       | Full?
-| 297                                              | 3                                                                          | NA                            | Paulus & Klapuri (2009)                               | @yeh2014po                                                                                                               |
-| 16    | [**Million Songs Dataset**](http://millionsongdataset.com/pages/getting-dataset/)                                              | Pop                           | Full                                        | 1,000,000                                        | 55                                                                         | None                          | EchoNest                                              | @cao2023th                                                                                                               |
-| 17    | [**Free Music Archive**](https://freemusicarchive.org/home)                                                                    | Various                       | Variable                                    | >100,000                                         | NA                                                                         | NA                            | NA                                                    | @koh2023me                                                                                                               |
-| 18    | [**Jamendo**](https://www.music-ir.org/mirex/wiki/2015:Main_Page) | Various                       | Variable                                    | 10,000                                           | 24                                                                         | NA                            | Metadata                                              | @hu2022de                                                                                                                |
-| 19    | **Chinese Classical Music Dataset**                                                                                            | Chinese classical             | ~30s                                        | 500                                              | 557                                                                        | 20                            | Essentia, MIRToolbox                                  | @wang2022co                                                                                                              |
+| ------------------------------------------------------------------------------------------------------ | -------------------------- | --------------- | ---------------- | ------------ | --------------- | ----------------------------------------------------- | ------------------------------------------------------------------------------------------------------------------------ |
+| [**MediaEval**](https://cvml.unige.ch/databases/emoMusic/)                                             | Western pop                | 45              | 744              | 6669         | 10/track        | OpenSMILE                                             | @bai2016di, @bai2017mu, @yang2021an, @chin2018pr, @coutinho2017sh, @markov2014mu, @medina2020em, @wang2022co, @xie2020mu |
+| [**DEAM**](https://cvml.unige.ch/databases/DEAM/)                                                      | Pop                        | 45              | 1802             | 260          | 5-10/track      | OpenSMILE                                             | @sorussa2020em, @orjesek2022en, @panwar2019ar, @zhang2023mo                                                              |
+| [**AMG1608**](https://github.com/loichan-tw/AMG1608_release)                                           | Pop                        | 30              | 1608             | 72           | 643             | MIR Toolbox, YAAFE                                     | @chen2017co, @hu2017cr, @wang2022cr                                                                                      |
+| [**EMOPIA**](https://annahung31.github.io/EMOPIA/)                                                     | Piano Solo (pop music)     | 30-40           | 387              | 24           | 1 annot./track  | MIDI Toolbox                                          | @bhuvanakumar2023em                                                                                                      |
+| [**NTUMIR**](https://web.archive.org/web/20170510081611/mac.citi.sinica.edu.tw/~yang/MER/NTUMIR-60)    | Famous pop songs           | 25              | 60               | 46           | 40 annot./track | MIR Toolbox, Sound Description Toolbox, MA Toolbox     | @chin2018pr                                                                                                              |
+| [**Soundtracks**](https://osf.io/p6vkg/wiki/home/)                                                     | Obscure film soundtracks   | 15              | 110              | NA           | 116             | NA                                                    | @wang2022co                                                                                                              |
+| [**PSIC3839**](https://github.com/xl2218066/PSIC3839)                                                  | Chinese popular            | 180             | 3839             | NA           | 87              | Librosa                                               | @xu2021us                                                                                                                |
+| [**CH818**](ccmir.cite.hku.hk/data/)                                                                   | Chinese pop                | 30              | 818              | 15           | 3               | MIR Toolbox, PsySound, Chroma Toolbox, Tempogram Toolbox| @hu2017cr                                                                                                                |
+| [**Zhang et al.
+(2015)**](LINK)                                                                        | Chinese pop                | 30              | 171              | 84           | 10              | MA Toolbox, MIR Toolbox, Coversongs                     | @zhang2016br                                                                                                             |
+| [**PMEmo**](http://huisblog.cn/PMEmo/)                                                                 | Pop songs                  | Variable        | 794              | 6373         | 457             | ComParE 2013 baseline feature set                     | @zhang2023mo                                                                                                             |
+| [**NJU-V1**](https://cs.nju.edu.cn/sufeng/data/musicmood.htm)                                          | Limited detail             | Variable        | 777              | Not reported | NA (tags)       | NA                                                    | @agarwal2021an                                                                                                           |
+| [**ISMIR-2012**](http://yadingsong.blogspot.com/2015/03/popular-music-emotion-dataset-ismir2012.html)  | Popular music              | 30 or 60        | 2904             | 54           | NA (tags)       | MIR Toolbox                                            | @agarwal2021an                                                                                                           |
+| [**MIREX2009**](https://www.music-ir.org/mirex/wiki/2009:Music_Structure_Segmentation_Results)         | Popular                    | Full            | 297              | 3            | NA              | Paulus & Klapuri (2009)                               | @yeh2014po                                                                                                               |
+| [**Million Songs Dataset**](http://millionsongdataset.com/pages/getting-dataset/)                      | Pop                        | Full            | 1,000,000        | 55           | None            | EchoNest                                              | @cao2023th                                                                                                               |
+| [**Free Music Archive**](https://freemusicarchive.org/home)                                            | Various                    | Variable        | >100,000         | NA           | NA              | NA                                                    | @koh2023me                                                                                                               |
+| [**Jamendo**](https://www.music-ir.org/mirex/wiki/2015:Main_Page)                                      | Various                    | Variable        | 10,000           | 24           | NA              | Metadata                                              | @hu2022de                                                                                                                |
+| **Chinese Classical Music Dataset**                                                                    | Chinese classical          | ~30s            | 500              | 557          | 20              | Essentia, MIR Toolbox                                  | @wang2022co                                                                                                              |
+Notes: $\dagger$ Used in @alvarez2023ri
+
+<!-- I TOOK THESE OUT FOR NOW
+| [**Spotify API**](https://developer.spotify.com/documentation/web-api)                                 | Various                    | Variable        | 5192$\dagger$    | 12           | NA              | EchoNest                                              | @alvarez2023ri                                                                                                           |
+| [**Acoustic Brainz**](https://acousticbrainz.org/)                                                     | Various                    | Variable        | 60,000$\dagger$  | Not reported | NA (tags)       | Essentia                                              | @alvarez2023ri                                                                                                           |
+-->

### 2025-02-19 manuscript/manuscript.qmd
Took out datasets and created Supporting Information document

@@
 
-## Datasets
-
-<!-- Note: this might take too much space in the main text, perhaps need to be moved to Supporting Information -->
-
-As we noted that several studies rely on the same datasets, summarising these could aid interpretation of the results.
-
-Table 5. Summary of datasets and studies utilising them.
-
-{{< include _datasets.qmd >}}
-
-The most frequently used 3 datasets are MediaEval [@soleymani20131000], DEAM [@aljanaki2017developing], and AMG1608 [@chen2015amg1608].
-These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by relative large number of participants (either by experts, students, or crowdsourced workers).
-Two of the most popular datasets offer a large number (260 to 6669) features extracted with OpenSMILE [@eyben2010opensmile].
-Looking at the datasets more broadly, the diversity in the size and the features of the datasets is notable.
-Only two feature extraction tools are used across multiple datasets (OpenSMILE and MIR Toolbox, @lartillot2007matlab).
-However, despite this diversity, there does not seem to be a direct link between the model success rates and the features themselves, or at least separating the features from variation created by the dataset size, annotation accuracy and genre is not possible.
-
 # Conclusion and Discussion

### 2025-02-19 manuscript/supporting_information.qmd
Took out datasets and created Supporting Information document

---
title             : "Supporting Information"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
csl: apa7.csl
class             : "man"
output            : papaja::apa6_pdf
bibliography      : references.bib
---

Supporting Information related to "A Meta-Analysis of Music Emotion Recognition Studies".

## Datasets

As several studies rely on the same datasets, Table S1 provides a summary of these.

Table S1. Summary of datasets and studies utilising them.

{{< include _datasets.qmd >}}

The most frequently used 3 datasets are MediaEval [@soleymani20131000], DEAM [@aljanaki2017developing], and AMG1608 [@chen2015amg1608]. These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by relative large number of participants (either by experts, students, or crowdsourced workers). Two of the most popular datasets offer a large number (260 to 6669) features extracted with OpenSMILE [@eyben2010opensmile]. Looking at the datasets more broadly, the diversity in the size and the features of the datasets is notable. Only two feature extraction tools are used across multiple datasets (OpenSMILE and MIR Toolbox, @lartillot2007matlab). However, despite this diversity, there does not seem to be a direct link between the model success rates and the features themselves, or at least separating the features from variation created by the dataset size, annotation accuracy and genre is not possible.

# References

### 2025-02-20 analysis/analysis.qmd

@@
 
-### By genre + feature complexity
+### By feature complexity
 
 ```{r}
-# m.cor_complexity <- update(m.cor.c, 
-#        subgroup = C_summary$feature_n_complexity_genre, 
-#        tau.common = FALSE,
-#        prediction = TRUE)
-# 
-# print(m.cor_complexity)
+m.cor_complexity <- update(m.cor.c,
+       subgroup = C_summary$feature_n_complexity,
+       tau.common = FALSE,
+       prediction = TRUE)
+
+print(m.cor_complexity)
+
 ```

### 2025-02-20 manuscript/manuscript.qmd
feat(manuscript): update results following merge cc98abi

@@
 
-TABLE 1: Summary of data (part of `analysis/preprocessing.qmd` updated 21/1/2025)
+TABLE 1: Summary of data (part of `analysis/preprocessing.qmd` updated 20/2/2025)
 
@@
 | Model N    | 204                             | 86                        | 290   |
-| Techniques | Neural Nets: 66                 | 25                        | 91    |
-| Techniques | Support Vector Machines: 50     | 26                        | 76    |
-| Techniques | Linear Methods: 62              | 13                        | 75    |
-| Techniques | Tree-based Methods: 14          | 10                        | 34    |
-| Techniques | KS, Add. & KNN: 12              | 12                        | 24    |
-| Feature N  | Min=3, Md=605, Max=6670         | Min=8, Md=126, Max=8904   | NA    |
+| Techniques | Neural Nets: 64                 | 21                        | 85    |
+| Techniques | Support Vector Machines: 62     | 26                        | 88    |
+| Techniques | Linear Methods: 62              | 19                        | 81    |
+| Techniques | Tree-based Methods: 14          | 16                        | 30    |
+| Techniques | KS, Add. & KNN:  2              | 4                         | 6     |
+| Feature N  | Min=3, Md=653, Max=14460        | Min=6, Md=98, Max=8904    | NA    |
 | Stimulus N | Min=20, Md=324, Max=2486        | Min=124, Md=300, Max=5192 | NA    |
@@
 Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (290 in total) with a relatively even distribution among the three most popular techniques: Neural Nets, SVMs, and Linear Methods.
-The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 9000 features [@zhang2023mo].
-The median number of features differs between regression (605) and classification (126) studies, primarily reflecting the nature of the datasets used in each approach.
+The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 14,500 features [@zhang2023mo].
+The median number of features differs between regression (653) and classification (98) studies, primarily reflecting the nature of the datasets used in each approach.
 The number of stimuli is typically around 300-400 (with a median of 324 for regression and 300 for classification), though there is substantial variation, with the extremes from 20 stimuli in @beveridge2018po to 5192 stimuli in @alvarez2023ri.
@@
 |:-------------|:------------|:------------------------|:------|:------|:---------|:------|
-| Valence All  | 102,60017   | 0.583 \[0.541-0.623\]   | 21.40 | .0001 | 0.094    | 97.7% |
+| Valence All  | 102,60017   | 0.583 \[0.541-0.623\]   | 21.41 | .0001 | 0.094    | 97.7% |
 | Valence Max  | 22,14172    | 0.669 \[0.560-0.755\]   | 9.58  | .0001 | 0.148    | 98.4% |
 | *N Features* |             |                         |       |       |          |       |
-| \<18 F       | 5,3036      | 0.811 \[0.542-0.823\]   | \-    | \-    | 0.182    | 98.9% |
-| 18-260 F     | 11,7042     | 0.584 \[0.534-0.931\]   | \-    | \-    | 0.133    | 97.6% |
-| 260+ F       | 5,3494      | 0.710 \[0.542-0.823\]   | \-    | \-    | 0.044    | 97.2% |
+| \<30 F       | 6,3140      | 0.766 \[0.488-0.903\]   | \-    | \-    | 0.198    | 98.6% |
+| 30-300 F     | 8,4098      | 0.580 \[0.276-0.778\]   | \-    | \-    | 0.188    | 97.4% |
+| 300+ F       | 8,6934      | 0.666 \[0.531-0.767\]   | \-    | \-    | 0.062    | 98.0% |
 | *Techniques* |             |                         |       |       |          |       |
-| KS           | 1,1838      | 0.466 \[-0.634-0.942\]  | \-    | \-    | 0.0185   | 95.1% |
-| LM           | 8,1762      | 0.797 \[0.614-0.899\]   | \-    | \-    | 0.1370   | 96.4% |
-| SVM          | 6,4993      | 0.656 \[0.484-0.779\]   | \-    | \-     | 0.0574  | 96.9% |
-| NN           | 4,2249      | 0.393 \[-0.355-0.835\]  | \-    | \-     | 0.0761  | 97.1% |
-| TM           | 3,3330      | 0.750 \[0.292-0.928\]   | \-    | \-     | 0.093   | 98.5% |
+| LM           | 9,2457      | 0.784 \[0.652-0.870\]   | \-    | \-    | 0.1194   | 96.3% |
+| SVM          | 4,5068      | 0.539 \[0.171-0.774\]   | \-    | \-    | 0.0702   | 97.1% |
+| NN           | 6,3317      | 0.473 \[0.167-0.696\]   | \-    | \-    | 0.1029   | 98.2% |
+| TM           | 3,3330      | 0.750 \[0.292-0.928\]   | \-    | \-    | 0.0740   | 98.8% |
 
-<!-- table updated TE 21/1/2025, revised terms 28/1/2025 -->
+<!-- table updated CA 20/2/2025, revised terms 28/1/2025 -->
 
@@
 
-<!-- numbers in the text updated up to here, TE 21/1/2025 -->
+<!-- numbers in the text updated up to here, CA 20/2/2025 -->
 
@@
 Table 2 presents two key splits: one based on the number of features used, which we hypothesized might influence model performance, and another based on the modeling techniques employed.
-In terms of feature sets, we categorized them into three groups: few features (<18), a large number of features (18–260), and massive feature sets (260+).
-Interestingly, models (4 in total) using a relatively small number of features (<18) performed best (_r_ = 0.817, 95% CI: 0.361–0.958) compared to those utilizing larger feature sets.
-However, it is worth noting that the models using massive feature sets (260+, 7 studies in total) also performed well (_r_ = 0.702), achieving better and more consistent results than the overall prediction rate (_r_ = 0.669).
-This observation is supported by the lowest heterogeneity index for the massive feature set group ($\tau^2$ = 0.029), indicating more consistent results across studies.
-Studies with large number of features (18-260 features, 10 studies in total) delivered the worst results, _r_ = 0.586 (95% CI: 0.360–0.748).
-Despite the fluctuation in the overall model accuracy between the number of features, the differences are not substantially large to pass the test of statistical significance (_Q_(2) = 3.47, _p_=.176).
+In terms of feature sets, we categorized them into three groups: few features (<30), a large number of features (30–300), and massive feature sets (300+).
+Interestingly, models (6 in total) using a relatively small number of features (<30) performed best (_r_ = 0.766, 95% CI: 0.488–0.903) compared to those utilizing larger feature sets.
+However, it is worth noting that the models using massive feature sets (300+, 8 studies in total) also performed reasonably well (_r_ = 0.666), achieving more consistent results than the overall prediction rate (_r_ = 0.669).
+This observation is supported by the lowest heterogeneity index for the massive feature set group ($\tau^2$ = 0.062), indicating more consistent results across studies.
+Studies with large number of features (30-300 features, 8 studies in total) delivered the worst results, _r_ = 0.580 (95% CI: 0.276–0.778).
+Despite the fluctuation in the overall model accuracy between the number of features, the differences are not substantially large to pass the test of statistical significance (_Q_(2) = 2.03, _p_=.363).
 
-<!-- numbers in the text updated up to here, TE 21/1/2025 -->
+<!-- numbers in the text updated up to here, CA 20/2/2025 -->
 
-When analyzing the studies across the five modeling techniques used, the prediction do differ significantly (_Q_(4) = 45.7, _p_ < .0001).
-Notably, linear models (LM) and Support Vector Machines (SVM) were the most common, with 8 and 6 studies, respectively, allowing for more confident interpretations.
-Linear models achieved the highest prediction rate (_r_ = 0.784, 95% CI: 0.625–0.881), though this may be influenced by the smaller datasets typically used in these studies.
-These studies also exhibited substantially higher heterogeneity ($\tau^2$ = 0.137) compared to other techniques, where $\tau^2$ values were less than half of this.
-While there were only 3 studies involving tree-based model (TM), these performed well, achieving _r_ = 0.750, 95% CI: 0.292–0.928), and the relatively poor performance of the neural network (NN) models represented in four studies (_r_ = 0.340, 95% CI: -0.097–0.668) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
-Kernel smoothing and KNN models (with only 1 study represented) achieved relatively poor success as well, _r_ = 0.383, 95% CI: 0.348–0.426).
+When analyzing the studies across the four modeling techniques used, the prediction do differ significantly (_Q_(3) = 12.43, _p_ = .0061).
+Notably, linear models (LM) and neural networks (NN) were the most common, with 9 and 6 studies, respectively, allowing for more confident interpretations.
+Linear models achieved the highest prediction rate (_r_ = 0.784, 95% CI: 0.652–0.870), though this may be influenced by the smaller datasets typically used in these studies.
+These studies also exhibited higher heterogeneity ($\tau^2$ = 0.119) compared to other techniques.
+While there were only 3 studies involving tree-based model (TM), these performed well, achieving _r_ = 0.750, 95% CI: 0.292–0.928), and the relatively poor performance of the neural network (NN) models represented in six studies (_r_ = 0.473, 95% CI: 0.167–0.696) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
 
-We also ran the sub-grouping analyses across a combination of stimulus genres (single vs mixed) and number of the features to explore where the differences in the model prediction rates might lie.
-For this purpose, we grouped the studies into small single genre/multigenre studies, medium single genre/multigenre studies, and medium-large single genre/multigenre studies, and huge multigenre studies.
-The small single genre/multigenre studies generally performed best (_r_ = 0.836), followed by huge multi-genre studies (_r_ = 0.693) while the medium and medium-large sized studies performance was between close the overall average (medium-large, _r_ = 0.768 and medium _r_ = 0.607).
-The heterogeneity was lowest in the huge multigenre studies ($\tau^2$ = 0.013) and highest in the small single genre/multigenre studies ($\tau^2$ = 0.318).
+We also ran the sub-grouping analyses across stimulus genres (single vs mixed), finding no significant difference (_Q_(1) = 0.01, _p_ = .9158).
+Both single-genre (_r_ = 0.675 95% CI: 0.465, 0.813, _n_ = 8) and multi-genre (_r_ = 0.665, 95% CI: 0.508-0.779, _n_ = 14) achieved similar results, although multi-genre studies exhibited slightly higher heterogeneity ($\tau^2$ = 0.167) than single-genre studies ($\tau^2$ = 0.137).
 
@@
 The overall correlation across the studies using the best performing model out of each study (Max) is 0.809 (CI95% 0.740-0.860).
-If we examine all the models reported in each study, the correlation drops marginally, to 0.791 (CI95% 0.770-0.810), despite this analysis includes about four times as many models as taking the best model out of each study.
-For arousal, even the baseline models seem to be performing on a relative high level.
+If we examine all the models reported in each study, the correlation drops marginally, to 0.791 (CI95% 0.770-0.810), despite this analysis including about four times as many models as taking the best model out of each study.
+For arousal, even the baseline models seem to perform at a relatively high level.
 However, the indicators of heterogeneity are again high ($\tau^2$ = 0.141 and $I^2$=97.9%), which suggests that summary may be misleading.
@@
 | *N Features* |             |                           |      |        |          |       |
-| \<18 F       | 4, 3016     | 0.817 \[0.361-0.958\]     |      |        | 0.2295   | 99.2% |
-| 18-260 F     | 10, 4222    | 0.586 \[0.356-0.748\]     |      |        | 0.1542   | 96.9% |
-| 260+ F       | 7, 6190     | 0.702 \[0.612-0.774\]     |      |        | 0.0285   | 96.6% |
+| \<30 F       | 6, 3140     | 0.885 \[0.782-0.940\]     |      |        | 0.0948   | 93.5% |
+| 30-300 F     | 8, 4098     | 0.735 \[0.501-0.868\]     |      |        | 0.1971   | 98.2% |
+| 300+ F       | 8, 6934     | 0.804 \[0.716-0.867\]     |      |        | 0.0612   | 97.4% |
 | *Techniques* |             |                           |      |        |          |       |
-| KS           | 1, 1838     | 0.819 \[0.803-0.833\]     |      |        |  -       | -     |
-| LM           | 8, 1762     | 0.881 \[0.808-0.928\]     |      |        | 0.0846   | 93.3% |
-| SVM          | 6, 4993     | 0.808 \[0.644-0.901\]     |      |        | 0.1125   | 98.0% |
-| NN           | 4, 2249     | 0.533 \[0.328-0.691\]     |      |        | 0.0190   | 85.8% |
+| LM           | 8, 1713     | 0.882 \[0.809-0.928\]     |      |        | 0.0846   | 93.3% |
+| SVM          | 5, 5812     | 0.796 \[0.559-0.913\]     |      |        | 0.1325   | 98.3% |
+| NN           | 6, 3317     | 0.660 \[0.395-0.823\]     |      |        | 0.1209   | 98.1% |
 | TM           | 3, 3330     | 0.809 \[0.733-0.864\]     |      |        | 0.0025   | 65.4% |
 
-<!-- numbers in the text updated up to here, TE 22/1/2025 -->
+<!-- numbers in the text updated up to here, CA 20/2/2025 -->
 
@@
 Similarly to valence, the range of correlations is also wide for arousal, ranging from 0.35 to 0.95, with all studies demonstrating evidence of positive correlations.
-A mean estimate of 0.81 or higher is achieved by the majority (15 out of the 22 models).
+A mean estimate of 0.82 or higher is achieved by the majority (14 out of the 22 models).
 Due to large sample in most studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am;@koh2023me; @saizclar2022pr; @wang2021ac].
@@
 
-The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (_Q_(2) = 3.47, _p_ = .176) despite the differing means (_r_ = 0.817 for studies with less than 18 features, _r_ = 0.586 for 18 to 260 features, and _r_ = 0.702 for studies utilising over 260 features).
-The differences in the techniques, however, does show statistically significant variance between subgroups (_Q_(4) = 50.47, _p_ < .0001).
-The Neural Nets (NN) achieve poor prediction of arousal (_r_ = 0.533) in comparison to other techniques.
-The caveat of this subgroup analysis is the small number of observations for five techniques.
+The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (_Q_(2) = 5.20, _p_ = .074) despite the differing means (_r_ = 0.885 for studies with less than 30 features, _r_ = 0.735 for 30 to 300 features, and _r_ = 0.804 for studies utilising over 300 features).
+The differences in the techniques, however, does show statistically significant variance between subgroups (_Q_(3) = 10.83, _p_ = .0127).
+The Neural Nets (NN) achieve poor prediction of arousal (_r_ = 0.660) in comparison to other techniques.
+The caveat of this subgroup analysis is the small number of observations for four techniques.
 When other subgroupings were explored, such as the type of journal (Engineering with 13 studies vs Psychology with 9 studies), no significant differences were observed (_Q_(1) = 0.94, _p_ = .333).
@@
 {{< include _figure3.qmd >}}
+<!-- numbers in the text updated up to here, CA 20/2/2025 -->
 

### 2025-02-20 manuscript/_figure4.qmd
manuscript: update results, add classification
update results following pull request from model-updates; add classification write-up and figure

--- 2025-01-22 manuscript/_figure3.qmd
@@
 #| fig.cap: > 
-#|   Forest (A) and funnel (B) plots of the best arousal models from all MER studies.
+#|   Forest (A) and funnel (B) plots of the best classification models from all MER studies.
 
@@
 
-R_summary <- read.csv("../analysis/R_summary.csv")
-tmp <- dplyr::filter(R_summary,dimension=="arousal")
-tmp$studyREF[tmp$studyREF=="Wang et al 2022"] <- c("Wang et al. 2022a","Wang et al. 2022b")
+C_summary <- read.csv("../analysis/C_summary.csv")
+tmp <- C_summary
 
@@
                  n = stimulus_n,
-                 studlab = studyREF,#citekey, # unique_id
-                 data = tmp,
+                 studlab = studyREF, # unique_id
+                 data = C_summary,
                  common = FALSE,
@@
                  prediction = TRUE,
-                 #                 backtransf = TRUE,
-                 #                 sm = "ZCOR",
+                 backtransf = TRUE,
+                 sm = "ZCOR",
                  method.tau = "REML",# could be PM (Paule-Mandel) as well
                  method.random.ci = "HK", 
-                 title = "MER: Regression: Arousal: Summary")
+                 title = "MER: Classification: Summary")
 

### 2025-02-20 manuscript/manuscript.qmd
manuscript: update results, add classification
update results following pull request from model-updates; add classification write-up and figure

@@
 
-Summary of details contained in Table 1, but summarise at least the categories predicted before moving onto the main findings.
+We next evaluated classification studies.
+The number of emotion classes predicted varied between studies, ranging from two to eight.
+Across studies, most operationalizations corresponded to either affective dimensions of the circumplex model or discrete emotion labels mapping to those dimensions [e.g., happy, sad, nervous, and calm and similar variants used in @agarwal2021an; @alvarez2023ri; @yeh2014po].
+Despite common adoption of the circumplex quadrants, studies differed in modeling dcisions: one study predicted quadrants in a multi-class problem [@panda2020no], whereas another predicted them in a series of binary classification tasks [@bhuvanakumar2023em].
+Others predicted valence and arousal in separate tasks [@hu2022de; @zhang2016br], and some of the models analyzed only predicted arousal [e.g., all models in @zhang2017fe; the CART model in @zhang2016br].
+Finally, some studies excluded specific quadrants [@hizlisoy2021mu] due to a lack of relevant stimuli, whereas others divided quadrants into multiple levels of valence and arousal [@nguyen2017an; @sorussa2020em].
+Because only a few studies separately reported valence and arousal or quadrant classification, we averaged prediction success across them for each model to increase comaparability with other studies.
+
+Figure 4 shows forest and funnel plot visualizations from the random-effects model of the best-performing models in classification studies.
+_MCC_s vary across a wide range, reporting _MCC_s between 0.55 to 0.98.
+Table 4 indicates that using the best model from each study increases performance relative to all models ($MCC$ = 0.8684 95%CI: 0.7475-0.9336), yet slightly increases heterogeneity ($\tau^2$ = 0.3180, $I^2$ = 99.8%).
+
+{{< include _figure4.qmd >}}
+
+| Concept      | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
+|:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
+| All Models   | 86, 80544   | 0.8245 \[0.7904-0.8535\]  | 23.7 | 0.0001 | 0.2082   | 99.7% |
+| Best Models  | 12, 15696   | 0.8684  \[0.7475-0.9336\] | 8.13 | 0.0001 | 0.3180   | 99.8% |
+| *N Features* |             |                           |      |        |          |       |
+| \<30 F       | 4, 6179     | 0.9293 \[0.8160-0.9738\]  |      |        | 0.0978   | 96.2% |
+| 30-300 F     | 5, 8193     | 0.8458 \[0.3613-0.9707\]  |      |        | 0.4822   | 99.9% |
+| 300+ F       | 3, 1324     | 0.7754 \[-0.2709-0.9818\] |      |        | 0.2724   | 97.7% |
+| *Techniques* |             |                           |      |        |          |       |
+| LM           | 2, 735      | 0.7280 \[-0.9957-0.9999\] |      |        | 0.1935   | 98.0% |
+| SVM          | 3, 6556     | 0.8699 \[-0.7268-0.9985\] |      |        | 0.8233   | 99.9% |
+| NN           | 3, 2313     | 0.9307  \[0.6523-0.9878\] |      |        | 0.1250   | 98.8% |
+| TM           | 4, 6092     | 0.8534 \[0.4464-0.9679\]  |      |        | 0.2430   | 99.1% |
+
+### Outlier analysis
+
+Accounting for outliers among the classifications results removes 6 studie, affecting both performance ($MCC$ = 0.8941, 95%CI: 0.8282-0.9356) and heterogeneity scores ($\tau^2$ = 0.0569, $I^2$ = 97.7%).
+However, Eggers' test does not indicate an asymmetric funnel plot ($\beta$ = -19.769, 95%CI: -39.29--0.24).
+After aggregating across dimensions, some of the best models included only classified arousal (@zhang2016; @zhang2017).
+To assess these studies' impact on overall performance, we conducted the same meta-analytic procedure after excluding them.
+Classification accuracy ($MCC$ = 0.8758, 95%CI: 0.7235-0.9468) does not change notably, nor does the rank order of model classes in terms of performance.
+Conseqeuntly, we report on all 12 in subsequent analyses.
+
+### Reporting splits
+
+The number of features analyzed does not significantly impact results (_Q_(2) = 3.91, _p_ = 0.1419), though $MCC$ shows differences on averages based on the number of features (< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; >300 F: $MCC$ = 0.7754).
+Conversely, model classes differ significantly (_Q_(3) = 4.22, _p_ = 0.239).
+Specifiaclly, neural networks outperform all other model types ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728).
+Studies did not differ based on whether stimuli comprised one or multiple genres (_Q_(1) = 0.12, _p_ = 0.7324), or whether studies employed binary or multi-class models (_Q_(1) = 0.03, _p_ = 0.8694).
 
 Table 4. Meta-analytic diagnostic for all classification studies predicting emotion categories from audio.
-
-| Model | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
-|:------|:------------|:--------------------------|:-----|:-------|:---------|:------|
-| All   | 89,87347    | 0.8074 \[0.7681; 0.8407\] | 21.4 | 0.0001 | 0.2415   | 99.7% |
-| Max   | 14,17184    | 0.8564 \[0.7386; 0.9234\] | 8.32 | 0.0001 | 0.329    | 99.8% |
 

### 2025-02-22 manuscript/_figure4.qmd
Fixed Fig 4 id and x label. Added missing references and moved table 4 caption.

@@
 ```{r}
-#| label: fig3
+#| label: fig4
 #| fig-width: 16
@@
   forestplot(labeltext = c(study, n, cor),
-             xlab = "Correlation",
+             xlab = "Matthews Correlation Coefficient",
              xticks = c(0, .25,.5,.75, 1),
@@
 source('../etc/custom_funnel_plot.R')
-fp2 <- suppressWarnings(custom_funnel_plot(m.cor))
+fp2 <- suppressWarnings(custom_funnel_plot(m.cor, metric = "MCC"))
 

### 2025-02-22 manuscript/manuscript.qmd
Fixed Fig 4 id and x label. Added missing references and moved table 4 caption.

@@
 
+Table 4. Meta-analytic diagnostic for all classification studies predicting emotion categories from audio.
+
 | Concept      | Models, obs | $r$ \[95%-CI\]            | $t$  | $p$    | $\tau^2$ | $I^2$ |
@@
 However, Eggers' test does not indicate an asymmetric funnel plot ($\beta$ = -19.769, 95%CI: -39.29--0.24).
-After aggregating across dimensions, some of the best models included only classified arousal (@zhang2016; @zhang2017).
+After aggregating across dimensions, some of the best models included only classified arousal (@zhang2016br; @zhang2017fe).
 To assess these studies' impact on overall performance, we conducted the same meta-analytic procedure after excluding them.
@@
 
-Table 4. Meta-analytic diagnostic for all classification studies predicting emotion categories from audio.
-
-<!-- | All Trim | 29,6499     | 0.8185 \[0.8046; 0.8314\] | 58.3 | 0.0001 | 0.0066   | 60.4% | -->
-
-<!-- | Max Trim | 6,3653      | 0.8689 \[0.7760; 0.9249\] | 11.6 | 0.0001 | 0.0749   | 97.5% | -->
-
 Heterogeneity issues
-
-Figure 3. Forest plot of arousal prediction (Max?) (Unless we do some custom plotting)
-
--   Figure Optional: Funnel plot (I haven't seen this yet)
 

### 2025-02-22 etc/custom_funnel_plot.R

@@ -1,4 +1,4 @@
-custom_funnel_plot <- function(data) {
+custom_funnel_plot <- function(data, metric = "cor") {
   # Function to plot a funnel plot with 95% and 99% confidence intervals
   # assumes data from dmetar::metacor function
   
@@ -18,7 +18,17 @@ custom_funnel_plot <- function(data) {
   meanll95 = estimate - (1.96 * se)
   meanul95 = estimate + (1.96 * se)
   dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
-  
+
+  if(metric=="cor"){
+    metric_label <- "Correlation"
+  }
+  if(metric=="MCC"){
+      metric_label <- "Matthews Correlation Coefficient"
+    }
+  else {
+    metric_label <- 'Not defined!'
+  }
+
   fp = ggplot(NULL) +
     geom_point(aes(x = SE, y = Zr), color = 'grey50', data = tmpdata) +
     geom_text_repel(
@@ -27,7 +37,7 @@ custom_funnel_plot <- function(data) {
       size = 2.5,
       max.overlaps = 45
     ) +
-    xlab('Standard Error') + ylab('Correlation') +
+    xlab('Standard Error') + ylab(metric_label) +
     geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
     geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
     geom_hline(

### 2025-02-26 manuscript/manuscript.qmd
references updated and conclusions revised. Some structural changes as well.

@@
 These studies reported 204 models, including 86 for emotion classification and 204 for regression.
-Using the best-performing model from each study, we found that valence and arousal were predicted with reasonable accuracy (r = 0.67 and r = 0.81, respectively), while classification models achieved an accuracy of 0.xx.
+Using the best-performing model from each study, we found that valence and arousal were predicted with reasonable accuracy (r = 0.67 and r = 0.81, respectively), while classification models achieved an accuracy of 0.87 as measured with Matthews correlation coefficient.
 Across modeling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed superior performance in classification tasks.
@@
 
-# A brief history of MER
+## A brief history of MER
 
@@
 
-# The semantic gap in MER
+## The semantic gap in MER
 
@@
 Specifically, relations between low-level predictors from music and text and the perceptual phenomena they model remain poorly understood, reaching a ceiling in prediction accuracy [@celma_foafing_2006].
-To address this so-called *semantic gap*, researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang_bridge_2016].
+To address this so-called *semantic gap*, researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang2016br].
 Through these approaches, MER researchers attempt to shatter a so-called *glass ceiling* [@downie_music_2008] by establishing central predictors for emotions.
@@
 We preregistered the meta-analysis plan on 21 June 2024 at OSF, <https://osf.io/c5wgd>, and the plan is also available at <https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html>).
+
+## Study identification
 
@@
 
+#### Outlier analysis
+
 Further analysis of between-study heterogeneity, as indexed by the $\tau^2$ (0.148) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] at 98.4%, reveals substantial heterogeneity.
@@
 {{< include _figure2.qmd >}}
+
+#### Reporting splits
 
@@
 For arousal, even the baseline models seem to perform at a relatively high level.
+
+#### Outlier analysis
+
 However, the indicators of heterogeneity are again high ($\tau^2$ = 0.141 and $I^2$=97.9%), which suggests that summary may be misleading.
@@
 
+#### Reporting splits
+
 The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (_Q_(2) = 5.20, _p_ = .074) despite the differing means (_r_ = 0.885 for studies with less than 30 features, _r_ = 0.735 for 30 to 300 features, and _r_ = 0.804 for studies utilising over 300 features).
@@
 The caveat of this subgroup analysis is the small number of observations for four techniques.
-When other subgroupings were explored, such as the type of journal (Engineering with 13 studies vs Psychology with 9 studies), no significant differences were observed (_Q_(1) = 0.94, _p_ = .333).
+When other sub-groupings were explored, such as the type of journal (Engineering with 13 studies vs Psychology with 9 studies), no significant differences were observed (_Q_(1) = 0.94, _p_ = .333).
 
@@
 
-## Classification studies
+## Results for classification studies
 
@@
 Across studies, most operationalizations corresponded to either affective dimensions of the circumplex model or discrete emotion labels mapping to those dimensions [e.g., happy, sad, nervous, and calm and similar variants used in @agarwal2021an; @alvarez2023ri; @yeh2014po].
-Despite common adoption of the circumplex quadrants, studies differed in modeling dcisions: one study predicted quadrants in a multi-class problem [@panda2020no], whereas another predicted them in a series of binary classification tasks [@bhuvanakumar2023em].
+Despite common adoption of the circumplex quadrants, studies differed in modeling decisions: one study predicted quadrants in a multi-class problem [@panda2020no], whereas another predicted them in a series of binary classification tasks [@bhuvanakumar2023em].
 Others predicted valence and arousal in separate tasks [@hu2022de; @zhang2016br], and some of the models analyzed only predicted arousal [e.g., all models in @zhang2017fe; the CART model in @zhang2016br].
 Finally, some studies excluded specific quadrants [@hizlisoy2021mu] due to a lack of relevant stimuli, whereas others divided quadrants into multiple levels of valence and arousal [@nguyen2017an; @sorussa2020em].
-Because only a few studies separately reported valence and arousal or quadrant classification, we averaged prediction success across them for each model to increase comaparability with other studies.
+Because only a few studies separately reported valence and arousal or quadrant classification, we averaged prediction success across them for each model to increase comparability with other studies.
 
@@
 
-Accounting for outliers among the classifications results removes 6 studie, affecting both performance ($MCC$ = 0.8941, 95%CI: 0.8282-0.9356) and heterogeneity scores ($\tau^2$ = 0.0569, $I^2$ = 97.7%).
+Accounting for outliers among the classifications results removes 6 studies, affecting both performance ($MCC$ = 0.8941, 95%CI: 0.8282-0.9356) and heterogeneity scores ($\tau^2$ = 0.0569, $I^2$ = 97.7%).
 However, Eggers' test does not indicate an asymmetric funnel plot ($\beta$ = -19.769, 95%CI: -39.29--0.24).
@@
 Classification accuracy ($MCC$ = 0.8758, 95%CI: 0.7235-0.9468) does not change notably, nor does the rank order of model classes in terms of performance.
-Conseqeuntly, we report on all 12 in subsequent analyses.
+Consequently, we report on all 12 in subsequent analyses.
+
+Heterogeneity issues
 
@@
 Conversely, model classes differ significantly (_Q_(3) = 4.22, _p_ = 0.239).
-Specifiaclly, neural networks outperform all other model types ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728).
+Specifically, neural networks outperform all other model types ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728).
 Studies did not differ based on whether stimuli comprised one or multiple genres (_Q_(1) = 0.12, _p_ = 0.7324), or whether studies employed binary or multi-class models (_Q_(1) = 0.03, _p_ = 0.8694).
 
-Heterogeneity issues
+Brief summary
 
-#### Notes to results: In the pre-registration, we promised the following:
+<!--
+Notes to results: In the pre-registration, we promised the following:
 
@@
 
-# Conclusion and Discussion
+-->
+
+# Discussion and conclusions
 
@@
 
-These results offer several important insights.
+## Moderate but systematic increases in accuracy
+
+The results of the meta-analysis offer several important insights.
 First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from _r_ = 0.51 to 0.67.
 Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at _r_ = 0.83).
-For classification, studies reached variable classification rates from 0.497 using _F~1~_ score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is 0.930 (?).
+For classification, studies reached variable classification rates from 0.497 using _F~1~_ score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is generally notably better, here _MCC_=0.87, albeit the differences in metrics.
 
-<!-- These numbers above could be reinterpreted here, they are not comparable with our MCC -->
+<!-- Note. there is no clear conversion from Average precision to MCC, although we could estimate this from our data -->
 
@@
 We surmise that this might relate to disciplinary difference, where the smaller datasets come from music psychology, which puts a premium on data quality (quality control of the ground-truth data and features) rather than on data size and modelling techniques.
-If quality control is succesful, it decreases the random error inherent in human judgements.
-Furthermore, the relevance and the precision of the features impacts the accuracy of the models.
-Unfortunately, in many cases, it is impossible to attribute the sources of error, as the studies so far have not compared the feature sets systematically, nor a comparison of the datasets with identical features has been carried out.
-In the future, it would be advantageous to systematically assess these sources of error in MER studies to allow us to focus on where significant improvements can be made.
+If quality control is successful, it decreases the random error inherent in human judgements.
 
-More broadly, the present study revealed an uncomfortable large variation in overall quality control and reporting in MER studies.
-In many cases, the reporting was insufficient to determine the features or their sources used in the models, and a large number of studies were discarded due to insufficient information about the data, model architectures, or outcome measures.
+Third, there is little work on the relevance of the features and how these impact the accuracy of the models.
+Unfortunately, in many cases, it is impossible to attribute the sources of error to features (as opposed to target emotions obtained from participants), as the studies so far have not compared the feature sets systematically, nor a comparison of the datasets with identical features has been carried out.
+In the future, it would be advantageous to systematically assess these sources of error in MER studies to allow us to focus on where and how significant improvements can be made.
 
-<!-- recommendations 1: reporting -->
+## Recommendations for future MER studies
+
+Broadly speaking, the present study revealed an uncomfortably large variation in overall quality control and reporting in MER studies.
+In many cases, the reporting was insufficient to determine the features used in the models or their sources.
+Additionally, a significant number of studies had to be discarded due to a lack of information about the data, model architectures, or outcome measures.
+We summarize these issues below as recommendations for improving (1) reporting and transparency, (2) feature definition, (3) dataset scale and content, and (4) the selection of emotion frameworks.
+
+<!-- ### Reporting and transparency -->
 
@@
 The modelling process should include a description of cross-validation, feature extraction technique, feature reduction (if used), and actual accuracy measures.
-We would recommend future studies to use Matthews correlation coefficient for classification studies as currently there are numerous metrics (_F~1~_, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
-
-<!-- feature validation? -->
-
-Feature validation...?
-(Two extreme positions: a limited number of features that are perceptual validated (psychology) -- domain knowledge –– vs a large number of features where the models identify what is needed (deep learning/engineering).
-
-<!-- recommendations 2: sharing -->
+We would recommend future studies to use Matthews correlation coefficient (_MCC_) for classification studies as currently there are numerous metrics (_F~1~_, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
+The situation is regression studies tends to be less volatile, but model accuracy may be reported with error measures (Mean Squared Error, Root Mean Squared Error, or Mean Absolute Error, or MSE, RMSE, MAE), which cannot be converted to relative measure such as _R^2_ without knowing the variance of the data.
 
 It would be beneficial to share models and features transparently.
-If a study relies on published datasets, as most do, sharing the actual model (as code/notebooks) and features would allow for more direct comparison of model techniques for the same dataset.
-Also, not all datasets are shared, or at least the sharing is only done partially.
+If a study relies on published datasets, as most do, sharing the actual model (as code/notebooks) and features would allow for a more direct comparison of model techniques for the same dataset.
+Also, not all datasets are shared [@akiki2021; @santana2020], or at least the sharing is only done partially.
 The copyright restrictions may limit the sharing of some datasets, but at least features and examples should be available.
 
-<!-- size, type of data --> 
+<!-- ### Feature definition -->
+
+One of the crucial aspects of modeling is the choice of features, their quantity, and their validation.
+In the present materials, we observe a continuum defined by two extremes: one approach relies on domain knowledge, starting with a limited number of features that are assumed to be perceptually relevant, while the other employs a large number of features, allowing the model to determine which are most relevant for prediction.
+The former is typically favored in music psychology studies, whereas the latter is more common in engineering and machine learning fields.
+Our results suggest that the domain knowledge-driven approach leads to the highest model accuracy across all studies and techniques.
+However, as our sample includes studies from the past 10 years, it is important to note that deep learning models have only gained prominence in this field since 2021.
+Consequently, it is too early to generalize that models based on domain knowledge, with a limited number of features and classical techniques, will continue to outperform machine learning approaches that utilize a large (300+) feature set.
+We believe that the relatively modest size of datasets available so far has prevented deep learning approaches from fully leveraging their potential to learn generalizable patterns in the data.
+
+<!-- ### Dataset scale and content -->
+
 We also note that the majority of the datasets used in MER studies are relatively small, but comparable to datasets for modeling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
@@
 
-The majority of the datasets are Western pop ... Music and annotators that represent the Global North do dominate the studies at the moment, and ... [@bornDiversifyingMIRKnowledge2020].
+<!-- Western bias -->
 
-Are the emotion recognition targets valid from the psychological and application point of view?
-Prediction of valence and arousal is popular, but has limited usefulness in practical applications that aim to capture experiences with music that are more aligned with models of music-induced emotions (such as GEMS by @zentner2008emotions).
+The majority of the datasets are Western pop, which represent only a fraction of the musical styles consumed globally.
+Also, the annotators represent the Global North do dominate the studies at the moment with some exceptions [@gomez-canon2023; @zhangPMEmo2018].
+This lack of diversity may contribute the success of the task but presents a significant limitation in our understanding of MER more broadly [@bornDiversifyingMIRKnowledge2020].
 
-Future efforts to prioritize feature validation, standardized reporting, and transparent sharing of research materials are needed for consistent improvements in MER.
+<!-- ### Emotion frameworks chosen -->
+
+Finally, we note that the relevance of of the emotion frameworks used in MER is not always explicitly discussed.
+The majority of studies rely either on valence and arousal or some combination of basic emotion categories.
+However, the relevance of quadrants of the affective circumplex or basic emotions for music consumers can have limited usefulness in practical applications that aim to capture experiences with music that are more aligned with models of music-induced emotions such as GEMS by @zentner2008emotions or what emotions music are thought to express [@eerola2025what].
+
+The present meta-analysis demonstrates that significant progress has been made toward developing accurate and scalable MER models over the past decade.
+Future efforts should prioritize feature validation, standardized reporting, the construction of larger and more diverse datasets, and the transparent sharing of research materials to ensure further consistent improvements in MER.
 

### 2025-02-26 manuscript/manuscript.qmd
text edits to results and conclusions

@@
 
-#### Outlier analysis
+#### Study heterogeneity
 
@@
 Figure 4 shows forest and funnel plot visualizations from the random-effects model of the best-performing models in classification studies.
-_MCC_s vary across a wide range, reporting _MCC_s between 0.55 to 0.98.
+$MCC$s vary across a wide range, reporting $MCC$s between 0.55 to 0.98.
 Table 4 indicates that using the best model from each study increases performance relative to all models ($MCC$ = 0.8684 95%CI: 0.7475-0.9336), yet slightly increases heterogeneity ($\tau^2$ = 0.3180, $I^2$ = 99.8%).
@@
 
-Heterogeneity issues
+More heterogeneity issues?
 
@@
 
-The number of features analyzed does not significantly impact results (_Q_(2) = 3.91, _p_ = 0.1419), though $MCC$ shows differences on averages based on the number of features (< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; >300 F: $MCC$ = 0.7754).
+The number of features (as classified into under 30, between 30 and 300, and above 300 features) analyzed does not significantly impact results (_Q_(2) = 3.91, _p_ = 0.1419), though $MCC$ shows differences on averages based on the number of features (< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; >300 F: $MCC$ = 0.7754).
 Conversely, model classes differ significantly (_Q_(3) = 4.22, _p_ = 0.239).
@@
 
-Brief summary
+NOTE. Model classes do not seem to differ significantly!?
 
@@
 Notes to results: In the pre-registration, we promised the following:
-
 - groupings based on genre, model complexity (high, medium, low), model validation (exists or not)
 - we promised to carry out sensitivity analyses based on type of journal the studies were published in.
+-->
 
--->
+Anything missing?
+
+- Leave-one-out sensitivity analyses?
 
@@
 For both affective dimensions of the circumplex model, linear methods (valence _r_ = 0.78, arousal _r_ = 0.88) and tree-based models (valence _r_ = 0.75, arousal _r_ = 0.81) outperformed neural networks (valence = 0.47, arousal = 0.66) and support vector machines (SVMs) (valence _r_ = 0.58, arousal _r_ = 0.79).
-In contrast, neural networks performed most accurately in classification studies (_MCC_ = 0.93), followed by SVMs (_MCC_ = 0.87) and tree-based models (_MCC_ = 0.85).
+In contrast, neural networks performed most accurately in classification studies ($MCC$ = 0.93), followed by SVMs ($MCC$ = 0.87) and tree-based models ($MCC$ = 0.85).
 The models applied to a variety of datasets differ substantially in terms of size, annotation principles, and the number of features and sources of these features.
@@
 Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at _r_ = 0.83).
-For classification, studies reached variable classification rates from 0.497 using _F~1~_ score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is generally notably better, here _MCC_=0.87, albeit the differences in metrics.
+For classification, studies reached variable classification rates from 0.497 using _F~1~_ score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is generally notably better, here $MCC$ = 0.87, albeit the differences in metrics.
 
@@
 The modelling process should include a description of cross-validation, feature extraction technique, feature reduction (if used), and actual accuracy measures.
-We would recommend future studies to use Matthews correlation coefficient (_MCC_) for classification studies as currently there are numerous metrics (_F~1~_, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
-The situation is regression studies tends to be less volatile, but model accuracy may be reported with error measures (Mean Squared Error, Root Mean Squared Error, or Mean Absolute Error, or MSE, RMSE, MAE), which cannot be converted to relative measure such as _R^2_ without knowing the variance of the data.
+We would recommend future studies to use Matthews correlation coefficient ($MCC$) for classification studies as currently there are numerous metrics (_F~1~_, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
+The situation is regression studies tends to be less volatile, but model accuracy may be reported with error measures (Mean Squared Error, Root Mean Squared Error, or Mean Absolute Error, or $MSE$, $RMSE$, $MAE$), which cannot be converted to relative measure such as $R^2$ without knowing the variance of the data.
 
@@
 
+## Implications and Conclusion
+
 The present meta-analysis demonstrates that significant progress has been made toward developing accurate and scalable MER models over the past decade.

### 2025-02-26 manuscript/manuscript.qmd
live editing the MS

@@
 Using the best-performing model from each study, we found that valence and arousal were predicted with reasonable accuracy (r = 0.67 and r = 0.81, respectively), while classification models achieved an accuracy of 0.87 as measured with Matthews correlation coefficient.
-Across modeling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed superior performance in classification tasks.
+Across modeling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed highest performance in classification tasks.
 We highlight key recommendations for future MER research, emphasizing the need for greater transparency, feature validation, and standardized reporting to improve comparability across studies.
@@
 
-#### Study heterogeneity
+#### Quantifying study heterogeneity
 
@@
 
-### Outlier analysis
+### Quantifying study heterogeneity
 
@@
 However, Eggers' test does not indicate an asymmetric funnel plot ($\beta$ = -19.769, 95%CI: -39.29--0.24).
-After aggregating across dimensions, some of the best models included only classified arousal (@zhang2016br; @zhang2017fe).
+After aggregating across dimensions, some of the best models included only classified arousal [@zhang2016br; @zhang2017fe].
 To assess these studies' impact on overall performance, we conducted the same meta-analytic procedure after excluding them.
@@
 Consequently, we report on all 12 in subsequent analyses.
-
-More heterogeneity issues?
 
@@
 -->
-
-Anything missing?
-
-- Leave-one-out sensitivity analyses?
 
@@
 
-## Moderate but systematic increases in accuracy
+## Improvements to predictive accuracy
 

### 2025-02-26 manuscript/manuscript.qmd
live editing the MS
manuscript: update classification reporting
fix issue in reporting of splits

@@
 
-The number of features (as classified into under 30, between 30 and 300, and above 300 features) analyzed does not significantly impact results (_Q_(2) = 3.91, _p_ = 0.1419), though $MCC$ shows differences on averages based on the number of features (< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; >300 F: $MCC$ = 0.7754).
-Conversely, model classes differ significantly (_Q_(3) = 4.22, _p_ = 0.239).
-Specifically, neural networks outperform all other model types ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728).
-Studies did not differ based on whether stimuli comprised one or multiple genres (_Q_(1) = 0.12, _p_ = 0.7324), or whether studies employed binary or multi-class models (_Q_(1) = 0.03, _p_ = 0.8694).
-
-NOTE. Model classes do not seem to differ significantly!?
+The number of features (as classified into under 30, between 30 and 300, and above 300 features) analyzed does not significantly impact results (_Q_(2) = 3.91, _p_ = 0.1419), despite $MCC$s showing average differences according to the number of features (< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; >300 F: $MCC$ = 0.7754).
+Similarly, the class of model did not differ significantly (_Q_(3) = 4.22, _p_ = 0.239) despite neural networks attaining highest average performance ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728).
+Finally, neither single- vs.
+multigenre studies (_Q_(1) = 0.12, _p_ = 0.7324), nor binary vs.
+multi-class models (_Q_(1) = 0.03, _p_ = 0.8694) differed significantly.
 
@@
 
-<!-- ### Feature definition -->
+<!-- ### Feature definition/validations -->
 

### 2025-02-26 etc/heat_map_figure.R
feat(etc): add heat map figure

@@ -1,0 +1,69 @@
+
+# Load libraries --------------------------------------------------
+
+library(ggplot2)
+
+
+# Read in best models ---------------------------------------------
+
+
+
+R_summary <- read.csv("analysis/R_summary.csv")
+C_summary <- read.csv("analysis/C_summary.csv")
+
+
+# Select relevant columns for plotting ----------------------------
+
+Rtmp <- R_summary |> dplyr::select(
+  model_class_id,
+  feature_n_complexity,
+  valuesMax,
+  dimension,
+  stimulus_n,
+  citekey
+)
+
+Ctmp <- C_summary |> dplyr::select(
+  model_class_id,
+  feature_n_complexity,
+  valuesMax,
+  dimension,
+  stimulus_n,
+  citekey
+)
+
+
+tmp <- rbind(Rtmp, Ctmp)
+
+tmp <- tmp |> dplyr::group_by(
+  dimension,
+  model_class_id,
+  feature_n_complexity
+)|>
+  dplyr::mutate(
+    study_n = length(citekey),
+    stim_mid = median(stimulus_n),
+    label = paste0("n=",study_n,"\n(", stim_mid, ")")
+  )
+
+# Combine C and R studies, then facet based on type.
+# Simplify labels for x and y axes
+# Median number of stimulus n
+tmp$dimension <- factor(tmp$dimension,
+                        levels = c("valence", 
+                                   "arousal", 
+                                   "classification"))
+
+tmp |>
+  ggplot(aes(x = model_class_id, 
+             y = feature_n_complexity,
+             fill = valuesMax
+         )) +
+  geom_raster()+
+  facet_wrap(facets = vars(dimension))+
+  scale_fill_gradient2(name = "Accuracy")+
+  scale_x_discrete(labels = c("LM", "NN", "SVM", "TM"))+
+  scale_y_discrete(labels = c("<30", "30-300", ">300"))+
+  geom_text(aes(label = label))+
+  labs(x = "Model Class Type", y = "Feature N Category")+
+  theme_classic()

### 2025-02-27 manuscript/_figure2.qmd
Fixed Fig 4 id and x label. Added missing references and moved table 4 caption.
live editing the MS

@@
 #| label: fig2
-#| fig-width: 16
+#| fig-width: 12
 #| fig-height: 6
@@
 #| fig.cap: > 
-#|   Forest (A) and funnel (B) plots of the best valence models from all MER studies.
+#|   Forest plot of the best valence models from all MER studies.
 
@@
 #### Funnel plot using a custom function
-source('../etc/custom_funnel_plot.R')
-fp2 <- suppressWarnings(custom_funnel_plot(m.cor))
+#source('../etc/custom_funnel_plot.R')
+#fp2 <- suppressWarnings(custom_funnel_plot(m.cor, metric = "cor"))
 
@@
 
-ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
+#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
+
+gridExtra::grid.arrange(fp1)
 

### 2025-02-27 manuscript/_figure3.qmd
Fixed Fig 4 id and x label. Added missing references and moved table 4 caption.
live editing the MS

@@
 #| label: fig3
-#| fig-width: 16
+#| fig-width: 12
 #| fig-height: 6
@@
 #| fig.cap: > 
-#|   Forest (A) and funnel (B) plots of the best arousal models from all MER studies.
+#|   Forest plot of the best arousal models from all MER studies.
 
@@
 #### Funnel plot using a custom function
-source('../etc/custom_funnel_plot.R')
-fp2 <- suppressWarnings(custom_funnel_plot(m.cor))
+#source('../etc/custom_funnel_plot.R')
+#fp2 <- suppressWarnings(custom_funnel_plot(m.cor, metric = "cor"))
 
 #gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
-ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
-
+#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
+ggarrange(fp1) #  
 ```

### 2025-02-27 manuscript/_figure4.qmd
live editing the MS

@@
 #| label: fig4
-#| fig-width: 16
+#| fig-width: 12
 #| fig-height: 6
@@
 #| fig.cap: > 
-#|   Forest (A) and funnel (B) plots of the best classification models from all MER studies.
+#|   Forest plot of the best classification models from all MER studies.
 
@@
 #### Funnel plot using a custom function
-source('../etc/custom_funnel_plot.R')
-fp2 <- suppressWarnings(custom_funnel_plot(m.cor, metric = "MCC"))
+#source('../etc/custom_funnel_plot.R')
+#fp2 <- suppressWarnings(custom_funnel_plot(m.cor, metric = "MCC"))
 
 #gridExtra::grid.arrange(fp1, fp2, ncol=2, widths=c(2,1))
-ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
+#ggarrange(fp1,fp2, ncol = 2, labels = c("A","B"),widths=c(2,1)) # added labels A and B
+ggarrange(fp1)
 

### 2025-02-27 manuscript/manuscript.qmd
live editing the MS

@@
 
-To capture key details of each study, we added additional fields to BibTeX entries for each study.
+To capture key details of each study, we added extra fields to BibTeX entries for each study.
 Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM), Linear Methods (LM), Tree-based Methods (TM), KS, Add.
@@
 
-Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (290 in total) with a relatively even distribution among the three most popular techniques: Neural Nets, SVMs, and Linear Methods.
+Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (290 in total) with a relatively even distribution among the three most popular techniques: Neural Nets (85 models in total), SVMs (88), and Linear Methods (81).
+Tree-based models are less frequently used (30 in total), and there is a small number (6) of other model techniques such as kernel smoothing or K-nearest neighbors (KNN) techniques used in the models.
+However, these techniques will not be visible in the breakdown of the results as these models were not among the strongest models per study (see reporting principles in the results).
 The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 14,500 features [@zhang2023mo].

### 2025-02-27 etc/heat_map_figure.R

@@ -61,9 +61,13 @@ tmp |>
          )) +
   geom_raster()+
   facet_wrap(facets = vars(dimension))+
-  scale_fill_gradient2(name = "Accuracy")+
+  scale_fill_distiller(name = "Accuracy", palette = "Spectral")+
+#  scale_fill_gradient2(name = "Accuracy")+
   scale_x_discrete(labels = c("LM", "NN", "SVM", "TM"))+
   scale_y_discrete(labels = c("<30", "30-300", ">300"))+
   geom_text(aes(label = label))+
   labs(x = "Model Class Type", y = "Feature N Category")+
   theme_classic()
+
+
+ggsave("heat_map_figure.png", width = 14, height = 4, units = "in")

### 2025-02-27 manuscript/manuscript.qmd
Notes to MS and additional references

@@
 
-## Quality Control
+## Quality control
 
@@
 
-## Study Encoding
+## Study encoding
 
@@
 
-TABLE 1: Summary of data (part of `analysis/preprocessing.qmd` updated 20/2/2025)
+<!-- table 1 is part of `analysis/preprocessing.qmd` updated 20/2/2025) -->
+
+TABLE 1: Summary of data
 
@@
 
-## Prediction success for affect dimensions
+## Results for regression studies
 
-See `analysis/analysis.qmd` (updated 17/1/2025)
+<!-- See `analysis/analysis.qmd` (updated 17/1/2025) -->
 
@@
 
-<!--
-Notes to results: In the pre-registration, we promised the following:
+<!-- TODO @Cameron: could you also check whether the journal type made a difference to classification results?
+We report these in the regression section (a had talked about this in the pre-registration so it might be worth 1 sentence).
+-->
+
+<!-- Notes to results: In the pre-registration, we promised the following:
 - groupings based on genre, model complexity (high, medium, low), model validation (exists or not)
@@
 Despite increasing complexity in the types of models and data sets used, no extant study has evaluated the relative merits of the tools, stimuli, and feature sets employed in MER studies.
-To provide a benchmark to guide future research, we present the first meta-analysis of music emotion recognition.
+The present study offers the first meta-analysis of music emotion recognition.
 
@@
 In contrast, neural networks performed most accurately in classification studies ($MCC$ = 0.93), followed by SVMs ($MCC$ = 0.87) and tree-based models ($MCC$ = 0.85).
-The models applied to a variety of datasets differ substantially in terms of size, annotation principles, and the number of features and sources of these features.
+Despite the high overall success of the research in this topic, the models applied to a variety of datasets differ substantially in terms of size, feature extraction methods, the number of features and their reduction, the actual modeling architecture, and the way the model outcomes are cross-validated.
 
@@
 
-<!-- Note. there is no clear conversion from Average precision to MCC, although we could estimate this from our data -->
+<!-- Note. there is no clear conversion from Average precision to MCC, although we could estimate this from our data using regression? or to calculate both metrics from the confusion matrix. -->
 
@@
 For instance, the smaller datasets tend to use linear models and deliver higher model accuracy than larger datasets and those with a large number of features.
-We surmise that this might relate to disciplinary difference, where the smaller datasets come from music psychology, which puts a premium on data quality (quality control of the ground-truth data and features) rather than on data size and modelling techniques.
+We surmise that this might relate to disciplinary difference, where the smaller datasets come from music psychology, which puts a premium on data quality (quality control of the ground-truth data and features) rather than on data size and model techniques.
 If quality control is successful, it decreases the random error inherent in human judgements.
+This argument is largely consistent with the analysis of the studies divided across journal types (psychology vs engineering).
 
 Third, there is little work on the relevance of the features and how these impact the accuracy of the models.
-Unfortunately, in many cases, it is impossible to attribute the sources of error to features (as opposed to target emotions obtained from participants), as the studies so far have not compared the feature sets systematically, nor a comparison of the datasets with identical features has been carried out.
+Unfortunately, in many cases, it is impossible to attribute the sources of error to features (as opposed to target emotions obtained from participants or from the modelling architecture, cross-validation or the size of data), as the studies so far have not compared the feature sets systematically, nor a comparison of the datasets with identical features has been carried out.
 In the future, it would be advantageous to systematically assess these sources of error in MER studies to allow us to focus on where and how significant improvements can be made.
+
+<!-- Question to @Cameron: We are a bit coy here as we don't really mention the tools by name (e.g.
+MIR toolbox, psysound, essentia, librosa, etc.).
+We have the information and should we write about them?
+Another gem to the supporting information as the space does not allow expansion.
+-->
 
@@
 
-It would be beneficial to share models and features transparently.
+It would be also highly beneficial to share models and features transparently.
 If a study relies on published datasets, as most do, sharing the actual model (as code/notebooks) and features would allow for a more direct comparison of model techniques for the same dataset.
@@
 The copyright restrictions may limit the sharing of some datasets, but at least features and examples should be available.
+
+<!-- Question to @Cameron: Could you add some of the studies included in the meta-analysis in the references to those studies that do not share datasets to make this more relevant.
+I just copied two references that I know are examples of datasets that require extra steps, but we have studies where we just don't even know whether the data is available, right?
+-->
 
@@
 However, as our sample includes studies from the past 10 years, it is important to note that deep learning models have only gained prominence in this field since 2021.
-Consequently, it is too early to generalize that models based on domain knowledge, with a limited number of features and classical techniques, will continue to outperform machine learning approaches that utilize a large (300+) feature set.
+Consequently, it is too early to generalize that models based on domain knowledge, with a limited number of features and classical techniques, will continue to outperform machine learning approaches that utilize a large (300+) feature sets.
 We believe that the relatively modest size of datasets available so far has prevented deep learning approaches from fully leveraging their potential to learn generalizable patterns in the data.
-
-<!-- ### Dataset scale and content -->
-
-We also note that the majority of the datasets used in MER studies are relatively small, but comparable to datasets for modeling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
+For reference, the size of the datasets in MER are currently comparable to dataset sizes for modeling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
 However, annotated datasets for visual scenes and objects tend to be much larger, often exceeding 100,000 annotated examples [@deng2009imagenet; @krishna2017visual].
@@
 
-The majority of the datasets are Western pop, which represent only a fraction of the musical styles consumed globally.
+At present, the majority of the datasets are Western pop, which represent only a fraction of the musical styles consumed globally.
 Also, the annotators represent the Global North do dominate the studies at the moment with some exceptions [@gomez-canon2023; @zhangPMEmo2018].
@@
 
-Finally, we note that the relevance of of the emotion frameworks used in MER is not always explicitly discussed.
+Finally, we note that the relevance of the emotion frameworks used in MER is not always explicitly discussed.
 The majority of studies rely either on valence and arousal or some combination of basic emotion categories.
-However, the relevance of quadrants of the affective circumplex or basic emotions for music consumers can have limited usefulness in practical applications that aim to capture experiences with music that are more aligned with models of music-induced emotions such as GEMS by @zentner2008emotions or what emotions music are thought to express [@eerola2025what].
+However, these frameworks may have limited usefulness for some practical applications that aim to capture experiences with music that are more aligned with models of music-induced emotions such as GEMS by @zentner2008emotions or AESTHEMOS [@schindler2017me], or what emotions music are shown to be able to express [@eerola2025what], or what are assumed to be worthwhile clusters of concepts (moods, emotions, tags) from crowdsourced, non-theory driven data [@saari_et_al_2015].
 
-## Implications and Conclusion
+## Implications and conclusion
 
@@
 Future efforts should prioritize feature validation, standardized reporting, the construction of larger and more diverse datasets, and the transparent sharing of research materials to ensure further consistent improvements in MER.
+
+<!-- This last section needs to be expanded. Or text moved from above to here? -->
 

### 2025-03-07 analysis/analysis.qmd
chore(analysis): summarize feature n for study summaries and small code tweaks

@@
 library(ggrepel)
+library(forestplot)
 ```
@@
 R_summary <- read.csv("R_summary.csv")
+
+# print a summary of features
+
+R_summary |> 
+  group_by(feature_n_complexity) |> 
+  summarize(min = min(feature_n), 
+            max = max(feature_n), 
+            mean = mean(feature_n), 
+            mdn = median(feature_n))
 
@@
 
-library(forestplot)
 data<-tibble::tibble(mean=m.cor$cor,lower=FisherZInv(m.cor$lower),upper=FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=round(m.cor$cor,2))
@@
 ```{r}
-m.cor1 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  model_class_id,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+m.cor1 <- update(m.cor,
+       subgroup = model_class_id)
 print(m.cor1)
@@
 ```{r}
-m.cor2 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  journal_type,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+m.cor2 <- update(m.cor,
+       subgroup = journal_type)
 print(m.cor2)
@@
 tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
-m.cor3 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  feature_n_complexity,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+m.cor3 <- update(m.cor,
+       subgroup = feature_n_complexity)
 print(m.cor3)
@@
 
-m.cor4 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  stimulus_genre_mixed,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+m.cor4 <- update(m.cor,
+       subgroup = stimulus_genre_mixed)
+
 print(m.cor4)
@@
 ```{r}
-m.cor1 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  model_class_id,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+m.cor1 <- update(m.cor,
+                 subgroup = model_class_id
+)
 print(m.cor1)
@@
 ```{r}
-m.cor2 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  journal_type,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+m.cor2 <- update(
+  m.cor,
+  subgroup = journal_type
+)
 print(m.cor2)
@@
 tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
-m.cor3 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  feature_n_complexity,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+m.cor3 <- update(
+  m.cor,
+  subgroup = feature_n_complexity
+)
 print(m.cor3)
@@
 
-m.cor4 <- metacor(cor = valuesMax,     # values 
-                 n = stimulus_n,
-                 studlab = citekey, # unique_id
-                 data = tmp,
-                 common = FALSE,
-                 random = TRUE,
-                 prediction = TRUE,
-                 subgroup =  stimulus_genre_mixed,
-#                 backtransf = TRUE,
-#                 sm = "ZCOR",
-                 method.tau = "REML",# could be PM (Paule-Mandel) as well
-                 method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+m.cor4 <- update(
+  m.cor,
+  subgroup = stimulus_genre_mixed
+)
+
 print(m.cor4)
@@
 C_summary <- merge(C_summary, C_classes)
+
+# print a summary of features
+
+C_summary |> 
+  group_by(feature_n_complexity) |> 
+  summarize(min = min(feature_n), 
+            max = max(feature_n), 
+            mean = mean(feature_n), 
+            mdn = median(feature_n))
 
@@
 
+print(m.cor.c)
+
 ```
@@
 
-library(forestplot)
 data<-tibble::tibble(mean=m.cor.c$cor,lower=FisherZInv(m.cor.c$lower),upper=FisherZInv(m.cor.c$upper),study=m.cor.c$studlab,n=m.cor.c$n,cor=round(m.cor.c$cor,2))
@@
 ```{r}
-library(ggrepel)
 tmpdata <- data.frame(SE = FisherZInv(m.cor.c$seTE), Zr = FisherZInv(m.cor.c$TE),studies=m.cor.c$studlab)
@@
                  n = stimulus_n,
-                 studlab = tmp2$studyREF,
+                 studlab = studyREF,
                  data = tmp2,
@@
                  method.random.ci = "HK", 
-                 title = "MER: Regression: Valence: Summary")
+                 title = "MER: Classification: Summary")
 
@@
 ```{r}
-m.cor_classes <- update(m.cor.c, 
-       subgroup = C_summary$classes, 
-       tau.common = FALSE,
-       prediction = TRUE)
+m.cor_classes <- update(
+  m.cor.c, 
+  subgroup = classes)
+
+print(m.cor_classes)
 
@@
              print.tau2 = FALSE,
-             leftlabs = c("Author", "N"),studlab = citekey)
+             leftlabs = c("Author", "N"),
+       studlab = citekey)
 
 funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE)
+
+```
+
+### By journal type
+
+```{r}
+m.cor_journal <- update(
+  m.cor.c, 
+  subgroup = journal_type
+)
+
+print(m.cor_journal)
 
@@
 #| eval: false
-m.cor_subgroups <- update(m.cor.c, 
-       subgroup = stimulus_genre_mixed, 
-       tau.common = FALSE,
-       prediction = TRUE)
+m.cor_subgroups <- update(
+  m.cor.c, 
+  subgroup = stimulus_genre_mixed
+)
 
@@
 ```{r}
-m.cor_complexity <- update(m.cor.c,
-       subgroup = C_summary$feature_n_complexity,
-       tau.common = FALSE,
-       prediction = TRUE)
+m.cor_complexity <- update(
+  m.cor.c,
+  subgroup = feature_n_complexity
+)
 
@@
 #| eval: false
-m.cor_subgroups <- update(m.cor.c, 
+m.cor_subgroups <- update(
+  m.cor.c, 
   subgroup = model_class_id, 
-       tau.common = FALSE,
-       prediction = TRUE)
+)
 

### 2025-03-07 manuscript/manuscript.qmd
Notes to MS and additional references
manuscript: update tables, work on TODOs

@@
 
-Emotional engagement is a key reason why people engage with music in their every day activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions;@agres2021music].
-In recent years, significant advances have been made in music information retrieval, particularly in music emotion recognition (MER) tasks [@gomez2021;@panda2020audio].
+Emotional engagement is a key reason why people engage with music in their every day activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions; @agres2021music].
+In recent years, significant advances have been made in music information retrieval, particularly in music emotion recognition (MER) tasks [@gomez2021; @panda2020audio].
 Improvements in available features, modeling techniques, and datasets have provided the field with opportunities to enhance the accuracy and reliability of predicting annotated emotions from audio.
@@
 
-First we describe the overall pattern of data (regression vs classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
+First we describe the overall pattern of data (regression vs. classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
 
@@
 |            | Regression                  | Classification            | Total |
-|:-----------|:--------------------------------|:--------------------------|:------|
+|:-----------|:----------------------------|:--------------------------|:------|
 | Study N    | 22                          | 12                        | 34    |
@@
 | Concept | Models, obs | $r$ \[95%-CI\] | $t$ | $p$ | $\tau^2$ | $I^2$ |
-|:-------------|:------------|:------------------------|:------|:------|:---------|:------|
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
 | Valence All | 102,60017 | 0.583 \[0.541-0.623\] | 21.41 | .0001 | 0.094 | 97.7% |
@@
 | \<30 F | 6,3140 | 0.766 \[0.488-0.903\] | \- | \- | 0.198 | 98.6% |
+| (Range: 3-22; Mdn = 16.5; *M* = 15.7) |  |  |  |  |  |  |
 | 30-300 F | 8,4098 | 0.580 \[0.276-0.778\] | \- | \- | 0.188 | 97.4% |
+| (Range: 45-260; Mdn = 101; *M* = 136) |  |  |  |  |  |  |
 | 300+ F | 8,6934 | 0.666 \[0.531-0.767\] | \- | \- | 0.062 | 98.0% |
+| (Range: 388-14460; Mdn = 654; *M* = 3360) |  |  |  |  |  |  |
 | *Techniques* |  |  |  |  |  |  |
@@
 
-The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 22 studies achieving an average correlation of _r_ = 0.669 (95% CI: 0.560-0.755), called "valence Max" in Table 2.
-However, when considering all models across these studies (n = 102), the overall prediction rate drops significantly to _r_ = 0.583.
+The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 22 studies achieving an average correlation of *r* = 0.669 (95% CI: 0.560-0.755), called "valence Max" in Table 2.
+However, when considering all models across these studies (n = 102), the overall prediction rate drops significantly to *r* = 0.583.
 We argue that this lower correlation is likely due to the inclusion of baseline models reported in these studies, which may not reflect the true success of the task for the purposes of our analysis.
@@
 Since $I^2$ is heavily influenced by study size (with larger N leading to lower sampling error), its value may be less insightful in this context.
-In contrast, $\tau^2$, which is less sensitive to the number of studies and directly linked to the outcome metric (_r_), provides a more reliable measure of heterogeneity in this case.
+In contrast, $\tau^2$, which is less sensitive to the number of studies and directly linked to the outcome metric (*r*), provides a more reliable measure of heterogeneity in this case.
 Also, we note that because the overall heterogeneity in the data is high, we are cautious in our interpretation of the publication bias [@van-aertwicherts_2016].
@@
 The funnel plot in panel B of Figure 2 shows clustering at the top of the plot (studies with low standard error) and no assumed larger diversity in the correlations when the error rates increase.
-However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$ = 5.05, CI95% -0.99-11.09, _t_ = 1.64, _p_ = 0.112, @eggersmith_1997).
+However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$ = 5.05, CI95% -0.99-11.09, *t* = 1.64, *p* = 0.112, @eggersmith_1997).
 Coming back to the mean of valence correlation of 0.669 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect.
@@
 Table 2 presents two key splits: one based on the number of features used, which we hypothesized might influence model performance, and another based on the modeling techniques employed.
-In terms of feature sets, we categorized them into three groups: few features (<30), a large number of features (30–300), and massive feature sets (300+).
-Interestingly, models (6 in total) using a relatively small number of features (<30) performed best (_r_ = 0.766, 95% CI: 0.488–0.903) compared to those utilizing larger feature sets.
-However, it is worth noting that the models using massive feature sets (300+, 8 studies in total) also performed reasonably well (_r_ = 0.666), achieving more consistent results than the overall prediction rate (_r_ = 0.669).
+In terms of feature sets, we categorized them into three groups: few features (\<30), a large number of features (30–300), and massive feature sets (300+).
+These splits produced reasonably comparable representations of regression and classification studies, though the actual ranges differed.
+For transparency, we report a summary of the actual feature counts in Table 2.
+Models (6 in total) using a relatively small number of features (\<30) performed best (*r* = 0.766, 95% CI: 0.488–0.903) compared to those utilizing larger feature sets.
+However, it is worth noting that the models using massive feature sets (300+, 8 studies in total) also performed reasonably well (*r* = 0.666), achieving more consistent results than the overall prediction rate (*r* = 0.669).
 This observation is supported by the lowest heterogeneity index for the massive feature set group ($\tau^2$ = 0.062), indicating more consistent results across studies.
-Studies with large number of features (30-300 features, 8 studies in total) delivered the worst results, _r_ = 0.580 (95% CI: 0.276–0.778).
-Despite the fluctuation in the overall model accuracy between the number of features, the differences are not substantially large to pass the test of statistical significance (_Q_(2) = 2.03, _p_=.363).
+Studies with large number of features (30-300 features, 8 studies in total) delivered the worst results, *r* = 0.580 (95% CI: 0.276–0.778).
+Despite the fluctuation in the overall model accuracy between the number of features, the differences are not substantially large to pass the test of statistical significance (*Q*(2) = 2.03, *p*=.363).
 
@@
 
-When analyzing the studies across the four modeling techniques used, the prediction do differ significantly (_Q_(3) = 12.43, _p_ = .0061).
+When analyzing the studies across the four modeling techniques used, the prediction do differ significantly (*Q*(3) = 12.43, *p* = .0061).
 Notably, linear models (LM) and neural networks (NN) were the most common, with 9 and 6 studies, respectively, allowing for more confident interpretations.
-Linear models achieved the highest prediction rate (_r_ = 0.784, 95% CI: 0.652–0.870), though this may be influenced by the smaller datasets typically used in these studies.
+Linear models achieved the highest prediction rate (*r* = 0.784, 95% CI: 0.652–0.870), though this may be influenced by the smaller datasets typically used in these studies.
 These studies also exhibited higher heterogeneity ($\tau^2$ = 0.119) compared to other techniques.
-While there were only 3 studies involving tree-based model (TM), these performed well, achieving _r_ = 0.750, 95% CI: 0.292–0.928), and the relatively poor performance of the neural network (NN) models represented in six studies (_r_ = 0.473, 95% CI: 0.167–0.696) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
+While there were only 3 studies involving tree-based model (TM), these performed well, achieving *r* = 0.750, 95% CI: 0.292–0.928), and the relatively poor performance of the neural network (NN) models represented in six studies (*r* = 0.473, 95% CI: 0.167–0.696) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
 
-We also ran the sub-grouping analyses across stimulus genres (single vs mixed), finding no significant difference (_Q_(1) = 0.01, _p_ = .9158).
-Both single-genre (_r_ = 0.675 95% CI: 0.465, 0.813, _n_ = 8) and multi-genre (_r_ = 0.665, 95% CI: 0.508-0.779, _n_ = 14) achieved similar results, although multi-genre studies exhibited slightly higher heterogeneity ($\tau^2$ = 0.167) than single-genre studies ($\tau^2$ = 0.137).
+We also ran the sub-grouping analyses across stimulus genres (single vs mixed), finding no significant difference (*Q*(1) = 0.01, *p* = .9158).
+Both single-genre (*r* = 0.675 95% CI: 0.465, 0.813, *n* = 8) and multi-genre (*r* = 0.665, 95% CI: 0.508-0.779, *n* = 14) achieved similar results, although multi-genre studies exhibited slightly higher heterogeneity ($\tau^2$ = 0.167) than single-genre studies ($\tau^2$ = 0.137).
 
@@
 However, the indicators of heterogeneity are again high ($\tau^2$ = 0.141 and $I^2$=97.9%), which suggests that summary may be misleading.
-However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.789 95%CI -4.87-6.45, _t_ = 0.273, _p_ = 0.788).
-If we remove the studies that are outside the 95%CI in heterogeneity, leaves this 13 studies in the summary that has _r_ = 0.826 (95%CI 0.806-0.845) with $\tau^2$ = 0.0042 and $I^2$ = 76.8%.
+However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.789 95%CI -4.87-6.45, *t* = 0.273, *p* = 0.788).
+If we remove the studies that are outside the 95%CI in heterogeneity, leaves this 13 studies in the summary that has *r* = 0.826 (95%CI 0.806-0.845) with $\tau^2$ = 0.0042 and $I^2$ = 76.8%.
 In other words, no material difference to the results obtained with all 22 studies.
@@
 | Concept | Models, obs | $r$ \[95%-CI\] | $t$ | $p$ | $\tau^2$ | $I^2$ |
-|:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
 | Arousal All | 102, 60017 | 0.791 \[0.770-0.810\] | 39.9 | 0.0001 | 0.069 | 96.2% |
@@
 | \<30 F | 6, 3140 | 0.885 \[0.782-0.940\] |  |  | 0.0948 | 93.5% |
+| (Range: 3-22; Mdn = 16.5; *M* = 15.7) |  |  |  |  |  |  |
 | 30-300 F | 8, 4098 | 0.735 \[0.501-0.868\] |  |  | 0.1971 | 98.2% |
+| (Range: 45-260; Mdn = 101; *M* = 136) |  |  |  |  |  |  |
 | 300+ F | 8, 6934 | 0.804 \[0.716-0.867\] |  |  | 0.0612 | 97.4% |
+| (Range: 388-14460; Mdn = 654; *M* = 3360) |  |  |  |  |  |  |
 | *Techniques* |  |  |  |  |  |  |
@@
 
+```{=html}
 <!-- Schwarzer and colleagues (Schwarzer, Carpenter, and Rücker 2015, chap. 4.3) mention, as a general rule of thumb, that subgroup analyses only make sense when your meta-analysis contains at least 
 K= 10 studies.-->
+```
 
@@
 A mean estimate of 0.82 or higher is achieved by the majority (14 out of the 22 models).
-Due to large sample in most studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am;@koh2023me; @saizclar2022pr; @wang2021ac].
+Due to large sample in most studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am; @koh2023me; @saizclar2022pr; @wang2021ac].
 The funnel plot in panel B illustrates the limited range of the correlations and show heavy clustering at the top of the plot (studies with low standard error).
@@
 
-The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (_Q_(2) = 5.20, _p_ = .074) despite the differing means (_r_ = 0.885 for studies with less than 30 features, _r_ = 0.735 for 30 to 300 features, and _r_ = 0.804 for studies utilising over 300 features).
-The differences in the techniques, however, does show statistically significant variance between subgroups (_Q_(3) = 10.83, _p_ = .0127).
-The Neural Nets (NN) achieve poor prediction of arousal (_r_ = 0.660) in comparison to other techniques.
+The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (*Q*(2) = 5.20, *p* = .074) despite the differing means (*r* = 0.885 for studies with less than 30 features, *r* = 0.735 for 30 to 300 features, and *r* = 0.804 for studies utilising over 300 features).
+The differences in the techniques, however, does show statistically significant variance between subgroups (*Q*(3) = 10.83, *p* = .0127).
+The Neural Nets (NN) achieve poor prediction of arousal (*r* = 0.660) in comparison to other techniques.
 The caveat of this subgroup analysis is the small number of observations for four techniques.
-When other sub-groupings were explored, such as the type of journal (Engineering with 13 studies vs Psychology with 9 studies), no significant differences were observed (_Q_(1) = 0.94, _p_ = .333).
+When other sub-groupings were explored, such as the type of journal (Engineering with 13 studies vs Psychology with 9 studies), no significant differences were observed (*Q*(1) = 0.94, *p* = .333).
 
 {{< include _figure3.qmd >}}
-<!-- numbers in the text updated up to here, CA 20/2/2025 -->
 
@@
 | Concept | Models, obs | $r$ \[95%-CI\] | $t$ | $p$ | $\tau^2$ | $I^2$ |
-|:-------------|:------------|:--------------------------|:-----|:-------|:---------|:------|
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
 | All Models | 86, 80544 | 0.8245 \[0.7904-0.8535\] | 23.7 | 0.0001 | 0.2082 | 99.7% |
@@
 | \<30 F | 4, 6179 | 0.9293 \[0.8160-0.9738\] |  |  | 0.0978 | 96.2% |
+| (Range: 6-11; Mdn = 9; *M* = 8.75) |  |  |  |  |  |  |
 | 30-300 F | 5, 8193 | 0.8458 \[0.3613-0.9707\] |  |  | 0.4822 | 99.9% |
+| (Range: 98-231; Mdn = 122; *M* = 139) |  |  |  |  |  |  |
 | 300+ F | 3, 1324 | 0.7754 \[-0.2709-0.9818\] |  |  | 0.2724 | 97.7% |
+| (Range: 397-8904; Mdn = 1702; *M* = 3668) |  |  |  |  |  |  |
 | *Techniques* |  |  |  |  |  |  |
@@
 
-The number of features (as classified into under 30, between 30 and 300, and above 300 features) analyzed does not significantly impact results (_Q_(2) = 3.91, _p_ = 0.1419), despite $MCC$s showing average differences according to the number of features (< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; >300 F: $MCC$ = 0.7754).
-Similarly, the class of model did not differ significantly (_Q_(3) = 4.22, _p_ = 0.239) despite neural networks attaining highest average performance ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728).
+The number of features (as classified into under 30, between 30 and 300, and above 300 features; see Table 3 for actual ranges) analyzed does not significantly impact results (*Q*(2) = 3.91, *p* = 0.1419), despite $MCC$s showing average differences according to the number of features (\< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; \>300 F: $MCC$ = 0.7754).
+Similarly, the class of model did not differ significantly (*Q*(3) = 4.22, *p* = 0.239) despite neural networks attaining highest average performance ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728).
 Finally, neither single- vs.
-multigenre studies (_Q_(1) = 0.12, _p_ = 0.7324), nor binary vs.
-multi-class models (_Q_(1) = 0.03, _p_ = 0.8694) differed significantly.
+multigenre studies (*Q*(1) = 0.12, *p* = 0.7324), nor binary vs.
+multi-class models (*Q*(1) = 0.03, *p* = 0.8694) differed significantly.
+Unlike regression, no classification studies were published in engineering journals.
 
-<!-- TODO @Cameron: could you also check whether the journal type made a difference to classification results?
-We report these in the regression section (a had talked about this in the pre-registration so it might be worth 1 sentence).
--->
-
+```{=html}
 <!-- Notes to results: In the pre-registration, we promised the following:
@@
 - we promised to carry out sensitivity analyses based on type of journal the studies were published in.
+
+CA: It looks like we've accounted for genre (single- vs.
+multi-genre), complexity (if feature n is a suitable substitute), and subgroup analyses for journal type (though this is not possible for classification studies).
+We have info on validation, though I'm not sure how this will play out depending on model type and whether cross-validation is necessary based on the algorithm.
+We might still be able to do a simple T/F encoding for cross-validation, and report the outcomes regardless of what the actual algorithm is.
 -->
+```
 
@@
 
-We initially identified 96 studies involving MER models, but in many cases the reporting standards or other quality issues or the lack of dedicated focus on music led us to include 34 studies in the analysis that overall reported 290 models, 204 related to regression and 86 classification.
-Comparing the most accurate model in each study, we observed reasonably accurate prediction of valence (_r_ = 0.67 [0.56, 0.76]), and arousal (_r_ = 0.81 [0.74, 0.86]) in regression studies.
-For both affective dimensions of the circumplex model, linear methods (valence _r_ = 0.78, arousal _r_ = 0.88) and tree-based models (valence _r_ = 0.75, arousal _r_ = 0.81) outperformed neural networks (valence = 0.47, arousal = 0.66) and support vector machines (SVMs) (valence _r_ = 0.58, arousal _r_ = 0.79).
+We initially identified 96 studies involving MER models, but narrowed our selection to 34 after filtering studies to ensure consistent quality, reporting standards, and a dedicated focus on music.
+From these studies, we encoded accuracy scores for 290 models, with 204 related to regression and 86 to classification.
+Comparing the most accurate model in each study revealed reasonably accurate prediction of valence (*r* = 0.67 \[0.56, 0.76\]), and arousal (*r* = 0.81 \[0.74, 0.86\]) in regression studies.
+For both affective dimensions of the circumplex model, linear methods (valence *r* = 0.78, arousal *r* = 0.88) and tree-based models (valence *r* = 0.75, arousal *r* = 0.81) outperformed neural networks (valence = 0.47, arousal = 0.66) and support vector machines (SVMs) (valence *r* = 0.58, arousal *r* = 0.79).
 In contrast, neural networks performed most accurately in classification studies ($MCC$ = 0.93), followed by SVMs ($MCC$ = 0.87) and tree-based models ($MCC$ = 0.85).
-Despite the high overall success of the research in this topic, the models applied to a variety of datasets differ substantially in terms of size, feature extraction methods, the number of features and their reduction, the actual modeling architecture, and the way the model outcomes are cross-validated.
+Despite the high overall success of the research in this topic, the models exhibited several differences relating to (i) the scale and quantity of data sets employed, (ii) feature extraction methods, (iii) the number and types of features and reduction methods used, (iv) the actual modeling architecture, and (v) how model outcomes are cross-validated.
 
@@
 The results of the meta-analysis offer several important insights.
-First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from _r_ = 0.51 to 0.67.
-Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at _r_ = 0.83).
-For classification, studies reached variable classification rates from 0.497 using _F~1~_ score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is generally notably better, here $MCC$ = 0.87, albeit the differences in metrics.
+First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from *r* = 0.51 to 0.67.[^2] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
+For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is generally notably better, here $MCC$ = 0.87, albeit the differences in metrics.
 
-<!-- Note. there is no clear conversion from Average precision to MCC, although we could estimate this from our data using regression? or to calculate both metrics from the confusion matrix. -->
+[^2]: Values reported as $R^2$ in original study.
+
+<!-- Note.
+there is no clear conversion from Average precision to MCC, although we could estimate this from our data using regression?
+or to calculate both metrics from the confusion matrix.
+CA: this sounds like an interesting and achievable idea.
+The confusion matrices are encoded and then summarized with the caret and yardstick packages, and we can potentially extract many other useful measures from them with yardstick::summary(), demonstrated here: https://yardstick.tidymodels.org/reference/summary.conf_mat.html -->
 
 Second, there is no single modelling technique that seems to arise on top, although linear models and random forests perform best in regression studies, and neural networks and support vector machines excel in classification tasks.
-We note that the model accuracy is surprisingly little affected by the number of features or the dataset size, likely the result of cross-validation techniques used to avoid overfitting, but the heterogeneity of the materials used in different studies may also mask substantial differences.
+We note that the model accuracy is surprisingly little affected by the number of features or the dataset size—likely the result of cross-validation techniques used to avoid overfitting—but the heterogeneity of the materials used in different studies may also mask substantial differences.
 For instance, the smaller datasets tend to use linear models and deliver higher model accuracy than larger datasets and those with a large number of features.
-We surmise that this might relate to disciplinary difference, where the smaller datasets come from music psychology, which puts a premium on data quality (quality control of the ground-truth data and features) rather than on data size and model techniques.
-If quality control is successful, it decreases the random error inherent in human judgements.
-This argument is largely consistent with the analysis of the studies divided across journal types (psychology vs engineering).
+We surmise that this might relate to disciplinary differences.
+For example, the smaller datasets often come from music psychology studies, which put a premium on data quality (quality control of the ground-truth data and features) rather than on data size and model techniques.
+Successful quality control is thought to decrease random errors inherent in human judgments.
+This argument is largely consistent with the analysis of the studies divided across journal types (psychology vs.
+engineering).
 
 Third, there is little work on the relevance of the features and how these impact the accuracy of the models.
-Unfortunately, in many cases, it is impossible to attribute the sources of error to features (as opposed to target emotions obtained from participants or from the modelling architecture, cross-validation or the size of data), as the studies so far have not compared the feature sets systematically, nor a comparison of the datasets with identical features has been carried out.
+Unfortunately, in many cases, it is impossible to attribute the sources of error to features (as opposed to target emotions obtained from participants or from the modelling architecture, cross-validation, or the size of data), as the studies so far have not compared the feature sets systematically, nor has a comparison of the datasets with identical features has been carried out.
 In the future, it would be advantageous to systematically assess these sources of error in MER studies to allow us to focus on where and how significant improvements can be made.
 
+```{=html}
 <!-- Question to @Cameron: We are a bit coy here as we don't really mention the tools by name (e.g.
@@
 Another gem to the supporting information as the space does not allow expansion.
+
+CA: This is a great idea, and reminds me we also have the Panda categories, which we have encoded, but haven't touched.
+We could explore whether we can find additional patterns about feature categories, and possibly libraries by extending out our new heat map visualization approach.
 -->
+```
 
@@
 The modelling process should include a description of cross-validation, feature extraction technique, feature reduction (if used), and actual accuracy measures.
-We would recommend future studies to use Matthews correlation coefficient ($MCC$) for classification studies as currently there are numerous metrics (_F~1~_, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
-The situation is regression studies tends to be less volatile, but model accuracy may be reported with error measures (Mean Squared Error, Root Mean Squared Error, or Mean Absolute Error, or $MSE$, $RMSE$, $MAE$), which cannot be converted to relative measure such as $R^2$ without knowing the variance of the data.
+We would recommend future studies to use Matthews correlation coefficient ($MCC$) for classification studies as currently there are numerous metrics (*F~1~*, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
+The situation for regression studies tends to be less volatile, but model accuracy may be reported with error measures (Mean Squared Error, Root Mean Squared Error, or Mean Absolute Error, or $MSE$, $RMSE$, $MAE$), which cannot be converted to relative measure such as $R^2$ without knowing the variance of the data.
 
@@
 If a study relies on published datasets, as most do, sharing the actual model (as code/notebooks) and features would allow for a more direct comparison of model techniques for the same dataset.
-Also, not all datasets are shared [@akiki2021; @santana2020], or at least the sharing is only done partially.
-The copyright restrictions may limit the sharing of some datasets, but at least features and examples should be available.
+Also, not all datasets are shared [@akiki2021; @santana2020; @hizlisoy2021mu; @zhang2017fe], or at least the sharing is only done partially.
+Standardizing reporting of datasets to include subsections explaining detailed information about stimuli (including genre, duration, sampling rate, and encoding format), features (types, extraction/analysis software, quantity of features, transformations, reduction methods), and models (types, tuning parameters, cross-validation) will enable more accurate comparisons between studies.
+The reporting in @grekow2018au serves as a useful example by providing enough detail in these areas to facilitate reproducibility.
+Although copyright restrictions may limit the sharing of some datasets, features and examples should be made available.
 
+```{=html}
 <!-- Question to @Cameron: Could you add some of the studies included in the meta-analysis in the references to those studies that do not share datasets to make this more relevant.
 I just copied two references that I know are examples of datasets that require extra steps, but we have studies where we just don't even know whether the data is available, right?
+
+CA: I've added some studies now, though these were excluded from the final meta-analysis.
+I also have a few examples of those which were included in the final results based on scrolling through the articles.
+Many are psychology papers, where it seems less common to share data publicly, but those also tend to have more case-specific goals rather than comparing results to existing benchmarks, so I didn't cite them.
+@hizlisoy2021mu proposes a new turkish music database, but I wasn't able to find the data from the article, so I added that.
+@zhang2017fe uses a dataset but doesn't seem to provide information on how to access it.
 -->
+```
 
@@
 At present, the majority of the datasets are Western pop, which represent only a fraction of the musical styles consumed globally.
-Also, the annotators represent the Global North do dominate the studies at the moment with some exceptions [@gomez-canon2023; @zhangPMEmo2018].
+Also, the annotators representing the Global North dominate the studies at the moment, with some exceptions [@gomez-canon2023; @zhangPMEmo2018].
 This lack of diversity may contribute the success of the task but presents a significant limitation in our understanding of MER more broadly [@bornDiversifyingMIRKnowledge2020].
@@
 
-Study preregistration, data, analysis scripts and supporting information is available at Github, <https://tuomaseerola.github.io/metaMER>.
+Study preregistration, data, analysis scripts and supporting information is available at GitHub, <https://tuomaseerola.github.io/metaMER>.
 

### 2025-03-07 manuscript/manuscript.qmd
Responses to CA and one in-text citation fixed

@@
 CA: this sounds like an interesting and achievable idea.
-The confusion matrices are encoded and then summarized with the caret and yardstick packages, and we can potentially extract many other useful measures from them with yardstick::summary(), demonstrated here: https://yardstick.tidymodels.org/reference/summary.conf_mat.html -->
+The confusion matrices are encoded and then summarized with the caret and yardstick packages, and we can potentially extract many other useful measures from them with yardstick::summary(), demonstrated here: https://yardstick.tidymodels.org/reference/summary.conf_mat.html.
+
+TE: Interesting, it is a potential weakness and it would make our promotion of MCC more valuable when we could demonstrate how these two are linked, but perhaps to limit the workload, we could try identify a small subset to which to apply to this idea.
+-->
 
@@
 We could explore whether we can find additional patterns about feature categories, and possibly libraries by extending out our new heat map visualization approach.
+
+TE: Or if we submit the meta-analysis soon and create a more pragmatic breakdown of what is the state of the art technologies in MER, this could be sufficient for a brief article separately.
+The selling point would not be the prediction rate, but quality control issues and the techniques/tools/crossvals/datasets chosen so far.
 -->
@@
 ```{=html}
-<!-- Question to @Cameron: Could you add some of the studies included in the meta-analysis in the references to those studies that do not share datasets to make this more relevant.
+<!-- Question to Cameron: Could you add some of the studies included in the meta-analysis in the references to those studies that do not share datasets to make this more relevant.
 I just copied two references that I know are examples of datasets that require extra steps, but we have studies where we just don't even know whether the data is available, right?
@@
 @zhang2017fe uses a dataset but doesn't seem to provide information on how to access it.
--->
+TE: great, well done, job done. -->
 ```

### 2025-03-07 manuscript/manuscript.qmd
manuscript: add heatmap figure

@@
 
+### Model success across concepts
+
+To assess how the use of different model types affected performance, we prepared heatmap visualizations depicting differences in success across feature *n* categories.
+We collapsed SVM and Tree-Based categories due to their low representation in the model summary.
+Figure 5 reveals studies using smaller feature sets tend to perform best, whereas the best model class differs depending on the prediction task.
+
+![Heatmap Depicting Success Across Tasks](../heat_map_figure.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Labels indicate the number of studies and the median number of stimuli is shown in parentheses.")
+
 ```{=html}
@@
 
+```{=html}
 <!-- Note.
@@
 -->
+```
 

### 2025-03-07 etc/heat_map_figure.R

@@ -1,20 +1,16 @@
 
-# Load libraries --------------------------------------------------
-
-library(ggplot2)
-
 
 # Read in best models ---------------------------------------------
 
 
 
-R_summary <- read.csv("analysis/R_summary.csv")
-C_summary <- read.csv("analysis/C_summary.csv")
+R_heatmap <- read.csv("analysis/R_summary.csv")
+C_heatmap <- read.csv("analysis/C_summary.csv")
 
 
 # Select relevant columns for plotting ----------------------------
 
-Rtmp <- R_summary |> dplyr::select(
+Rtmp <- R_heatmap |> dplyr::select(
   model_class_id,
   feature_n_complexity,
   valuesMax,
@@ -23,7 +19,7 @@ Rtmp <- R_summary |> dplyr::select(
   citekey
 )
 
-Ctmp <- C_summary |> dplyr::select(
+Ctmp <- C_heatmap |> dplyr::select(
   model_class_id,
   feature_n_complexity,
   valuesMax,
@@ -34,6 +30,12 @@ Ctmp <- C_summary |> dplyr::select(
 
 
 tmp <- rbind(Rtmp, Ctmp)
+
+tmp$model_class_id
+
+tmp[tmp$model_class_id %in% 
+      c("Support Vector Machines",
+        "Tree-based Methods" ),]$model_class_id <-"SVM,TM"
 
 tmp <- tmp |> dplyr::group_by(
   dimension,
@@ -54,7 +56,7 @@ tmp$dimension <- factor(tmp$dimension,
                                    "arousal", 
                                    "classification"))
 
-tmp |>
+heatmap_facets <- tmp |>
   ggplot(aes(x = model_class_id, 
              y = feature_n_complexity,
              fill = valuesMax
@@ -63,11 +65,47 @@ tmp |>
   facet_wrap(facets = vars(dimension))+
   scale_fill_distiller(name = "Accuracy", palette = "Spectral")+
 #  scale_fill_gradient2(name = "Accuracy")+
-  scale_x_discrete(labels = c("LM", "NN", "SVM", "TM"))+
+  scale_x_discrete(labels = c("LM", "NN", "Other"))+
   scale_y_discrete(labels = c("<30", "30-300", ">300"))+
   geom_text(aes(label = label))+
-  labs(x = "Model Class Type", y = "Feature N Category")+
+  labs(x = "Model class type", y = "Feature N category")+
   theme_classic()
 
 
+heatmap_facets
+
[…]

### 2025-03-09 manuscript/manuscript.qmd
manuscript: update discussion
add subsection describing model validation types. add footnote to methods justifying inclusion of chen2017co in SVM

@@
 To capture key details of each study, we added extra fields to BibTeX entries for each study.
-Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM), Linear Methods (LM), Tree-based Methods (TM), KS, Add.
+Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM),[^2] Linear Methods (LM), Tree-based Methods (TM), KS, Add.
 and KNN Methods (KM) -- validation procedure and output measures.
@@
 For complete details about our encoding procedure, see `studies/extraction_details.qmd` .
+
+[^2]: @chen2017co was the only study of those included to use Gaussian Mixture Models.
+We decided to group this with Support Vector Machines as they have been reported to perform similarly on mid-sized data sets [@mashao2003co].
 
@@
 
-![Heatmap Depicting Success Across Tasks](../heat_map_figure.png "Heatmap depicting success across tasks according to Feature N category and model class.
-Labels indicate the number of studies and the median number of stimuli is shown in parentheses.")
+![Heatmap Depicting Success Across Tasks](../manuscript/heat_map_figure.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="892"}
 
@@
 The results of the meta-analysis offer several important insights.
-First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from *r* = 0.51 to 0.67.[^2] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
+First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from *r* = 0.51 to 0.67.[^3] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
 For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is generally notably better, here $MCC$ = 0.87, albeit the differences in metrics.
 
-[^2]: Values reported as $R^2$ in original study.
+[^3]: @chen2017co was the only study in the included studies using Gaussian Mixture Models.
+We decided to group this with SVMs, as they are commonly applied in similar contexts and have been used together in hybrid systems.
 
@@
 
+<!-- ### Validation -->
+
+An encouraging finding is that ~94% of the studies analyzed here reported some form of model validation.
+The majority of studies validated models by splitting the dataset into separate sets for training and testing [e.g., @yang2021an], sometimes including an additional set for validation [@sorussa2020em].
+Most used some form of cross validation (CV), with the most common type being 10-fold CV.
+Other varieties included 3-fold, 5-fold, or 6-fold CV, as well as more complex variants like nested leave-one-out CV [@coutinho2017sh] and 20 x 10-fold CV [@panda2020no].
+Whereas many engineering studies performed model validation using one or more large databases, some psychological studies evaluating smaller datasets validated models by designing new experiments.
+Examples include comparing a model's performance on ground-truth data with annotations from a second experiment [@griffiths2021am; @beveridge2018po], or comparing a model's performance across different versions of the same music pieces [@battcock2021in].
+
 <!-- Western bias -->

### 2025-03-09 manuscript/manuscript.qmd
fix(manuscript): correct footnote 3

@@
 
-[^3]: @chen2017co was the only study in the included studies using Gaussian Mixture Models.
-We decided to group this with SVMs, as they are commonly applied in similar contexts and have been used together in hybrid systems.
+[^3]: Values reported as $R^2$ in original study.
 
@@
 
-An encouraging finding is that ~94% of the studies analyzed here reported some form of model validation.
+An encouraging finding is that \~94% of the studies analyzed here reported some form of model validation.
 The majority of studies validated models by splitting the dataset into separate sets for training and testing [e.g., @yang2021an], sometimes including an additional set for validation [@sorussa2020em].

### 2025-03-10 manuscript/manuscript.qmd
minor wording issue

@@
 shorttitle        : "Meta-analysis of music emotion recognition"
-
 author: 
@@
     email         : "andersoc@mcmaster.ca"
-
 affiliation:
@@
 wordcount         : "5555"
-
-#bibliography      : ["references.bib"]
-
 figsintext        : yes
@@
 csl: apa7.csl
-
 class             : "man"
-output            : papaja::apa6_pdf
 bibliography: references.bib
+format:
+  html: default
 ---

### 2025-03-10 manuscript/_figure2.qmd
Added a template for compiling a pdf version of MS using apaquarto

@@
 #| echo: false
+#| warning: false
+#| message: false
 #| fig.cap: > 

### 2025-03-10 manuscript/_figure3.qmd
Added a template for compiling a pdf version of MS using apaquarto

@@
 #| fig-height: 6
+#| warning: false
+#| message: false
 #| echo: false

### 2025-03-10 manuscript/manuscript-apaquarto.qmd
Added a template for compiling a pdf version of MS using apaquarto

---
title: "A Meta-Analysis of Music Emotion Recognition Studies"
# If blank, the running header is the title in upper case.
shorttitle: "Meta-analysis of music emotion recognition"
# Set names and affiliations.
# It is nice to specify everyone's orcid, if possible.
# There can be only one corresponding author, but declaring one is optional.
author:
  - name: Tuomas Eerola
    corresponding: true
    orcid: 0000-0002-2896-929X
    email: tuomas.eerola@durham.ac.uk
    url: https://tuomaseerola.github.io/
    # Roles are optional. 
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    roles:
      - conceptualization
      - methodology
      - formal Analysis
      - writing
    affiliations:
      - id: id1
        name: "Durham University"
        department: Department of Music
        address: Palace Green
        city: Durham
        region: Durham
        country: United Kingdom
        postal-code: DH1 3DA
  - name: Cameron J. Anderson
    orcid: 0000-0002-4334-5696
    roles:
      - data curation
      - formal analysis
      - writing
    affiliations: 
      - ref: id2
        name: "McMaster University"
        department: "Department of Psychology, Neuroscience & Behaviour"
        city: Hamilton
        region: Ontario
        country: Canada
author-note:
    study-registration: "the meta-analysis plan was pre-registered on 21 June 2024 at OSF, https://osf.io/c5wgd"
    # Acknowledge and cite data/materials to be shared.
    data-sharing: "https://tuomaseerola.github.io/metaMER"
    related-report: ~
    conflict-of-interest: The authors have no conflicts of interest to disclose.
    # Example: This study was supported by Grant [Grant Number] from [Funding Source].
    financial-support: ~
    # Example: The authors are grateful to [Person] for [Reason].
    gratitude: ~
    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
    authorship-agreements: ~
abstract: "This meta-analysis examines music emotion recognition (MER) models published between 2014 and 2024, focusing on predictions of valence, arousal, and categorical emotions. A total of 553 studies were identified, of which 96 full-text articles were assessed, resulting in a final review of 34 studies. These studies reported 204 models, including 86 for emotion classification and 204 for regression. Using the best-performing model from each study, we found that valence and arousal were predicted with reasonable accuracy (r = 0.67 and r = 0.81, respectively), while classification models achieved an accuracy of 0.87 as measured with Matthews correlation coefficient. Across modeling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed highest performance in classification tasks. We highlight key recommendations for future MER research, emphasizing the need for greater transparency, feature validation, and standardized reporting to improve comparability across studies."
# Put as many keywords at you like, separated by commmas (e.g., [reliability, validity, generalizability])
keywords: [music, emotion, recognition, computational, model, meta-analysis]
# If true, tables and figures are mingled with the text instead of listed at the end of the document.
impact-statement: ~
floatsintext: true
# Numbered lines (.pdf and .docx only)
numbered-lines: false
# File with references
bibliography: references.bib
# Suppress title page
suppress-title-page: false
# Link citations to references
link-citations: true
# Masks references that appear in the masked-citations list
mask: false
# If true, adds today's date below author affiliations. If text, can be any value.
# This is not standard APA format, but it is convenient.
# Works with docx, html, and typst. 
draft-date: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  email: "Email"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  title-impact-statement: "Impact Statement"
  references-meta-analysis: "References marked with an asterisk indicate studies included in the meta-analysis."
format:
#  apaquarto-docx: default
#  apaquarto-html: default
  apaquarto-typst: 
    keep-typ: true
    list-of-figures: false
    list-of-tables: false
#    toc: true
#  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
#    documentmode: jou
#    keep-tex: true
---

```{r}
#| label: setup
#| include: false

```

# Introduction

Emotional engagement is a key reason why people engage with music in their every day activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions; @agres2021music].

# Methods

{{< include _figure1.qmd >}}

# Results

```{r}
#| label: tbl-table1
#| tbl-cap: Summary of the models for regression and classification studies.
#| ft.align: left
#| warning: false
#| message: false

library(tidyverse)
library(flextable)

tibble(Info = c("Study N","Model N","Techniques","Techniques","Techniques","Techniques","Techniques","Feature N","Stimulus N"), 
       Regression = c("22","204","Neural Nets: 64","Support Vector Machines: 62","Linear Methods: 62","Tree-based Methods: 14","KS, Add. & KNN: 2","Min=3, Md=653, Max=14460","Min=20, Md=324, Max=2486"),
       Classification = c("12","86","21","26","19","16","4","Min=6, Md=98, Max=8904","Min=124, Md=300, Max=5192"),
       Total = c("34","290","85","88","81","30","6","NA","NA")) %>% 
  flextable(cwidth = c(.7,2.3,2.3,.4)) %>%
  theme_apa() 
```

# Discussion and conclusions

### Funding statement

CA was funded by Mitacs Globalink Research Award (Mitacs & British High Commission - Ottawa, Canada).

### Competing interests statement

There were no competing interests.

### Open practices statement

Study preregistration, data, analysis scripts and supporting information is available at GitHub, <https://tuomaseerola.github.io/metaMER>.

# References

### 2025-03-10 manuscript/manuscript-apaquarto.qmd
Added a template for compiling a pdf version of MS using apaquarto, removed flextable

@@
 #| label: tbl-table1
-#| tbl-cap: Summary of the models for regression and classification studies.
-#| ft.align: left
+#| id: tbl-table1
+#| output: asis
 #| warning: false
 #| message: false
+#| tbl-cap: Summary of the models for regression and classification studies.
+library(tidyverse)
+library(kableExtra)
 
-library(tidyverse)
-library(flextable)
-
-tibble(Info = c("Study N","Model N","Techniques","Techniques","Techniques","Techniques","Techniques","Feature N","Stimulus N"), 
+t <- tibble(Info = c("Study N","Model N","Techniques","Techniques","Techniques","Techniques","Techniques","Feature N","Stimulus N"), 
        Regression = c("22","204","Neural Nets: 64","Support Vector Machines: 62","Linear Methods: 62","Tree-based Methods: 14","KS, Add.
@@
        Classification = c("12","86","21","26","19","16","4","Min=6, Md=98, Max=8904","Min=124, Md=300, Max=5192"),
-       Total = c("34","290","85","88","81","30","6","NA","NA")) %>% 
-  flextable(cwidth = c(.7,2.3,2.3,.4)) %>%
-  theme_apa() 
+       Total = c("34","290","85","88","81","30","6","NA","NA")) 
+print(knitr::kable(t,bookstabs=TRUE))
+#  theme_apa()
+
 ```

### 2025-03-10 manuscript/manuscript.qmd
Heatmap sub-headings in capitals

@@
 
-![Heatmap Depicting Success Across Tasks](../manuscript/heat_map_figure.png "Heatmap depicting success across tasks according to Feature N category and model class.
+![Heatmap Depicting Success Across Tasks](../manuscript/heat_map_figure_R1.png "Heatmap depicting success across tasks according to Feature N category and model class.
 Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="892"}

### 2025-03-10 etc/heat_map_figure.R

@@ -1,4 +1,4 @@
-
+library(ggplot2)
 
 # Read in best models ---------------------------------------------
 
@@ -54,7 +54,10 @@ tmp <- tmp |> dplyr::group_by(
 tmp$dimension <- factor(tmp$dimension,
                         levels = c("valence", 
                                    "arousal", 
-                                   "classification"))
+                                   "classification"),
+                        labels = c("Valence", 
+                                   "Arousal", 
+                                   "Classification"))
 
 heatmap_facets <- tmp |>
   ggplot(aes(x = model_class_id, 
@@ -69,12 +72,12 @@ heatmap_facets <- tmp |>
   scale_y_discrete(labels = c("<30", "30-300", ">300"))+
   geom_text(aes(label = label))+
   labs(x = "Model class type", y = "Feature N category")+
-  theme_classic()
+  theme_classic(base_size = 14,base_family = "Helvetica")
 
 
 heatmap_facets
 
-ggsave("heat_map_figure.png", width = 14, height = 4, units = "in")
+ggsave("heat_map_figure_R1.png", width = 14, height = 4, units = "in",dpi = 300)
 
 
 

### 2025-03-15 etc/model_class_summary.R
feat(etc): add code for model summary figure
visualizes heatmap counting the frequency of models used across model_class_ids for regression and classification studies

@@ -1,0 +1,65 @@
+library(dplyr)
+
+best_mods <- read.csv("etc/pretty-model-ids.csv")
+
+best_mods <- best_mods |> select(
+  citekey, 
+  paradigm, 
+  model_class_id,
+  model_id
+)
+
+
+model_id_summary <- best_mods |>
+  group_by(
+    paradigm,
+    citekey
+  ) |>
+  reframe(
+    model_id = unique(
+      model_id
+    ),
+    model_class_id = unique(
+      model_class_id
+    )
+  ) 
+
+model_id_summary <- model_id_summary |>
+  ungroup() |>
+  group_by(paradigm) |>
+  add_count(model_id)
+
+model_id_summary$paradigm <- factor(
+  model_id_summary$paradigm,
+  levels = c("regression", "classification"),
+  labels = c("Regression", "Classification")
+)
+
+
+
+model_id_summary <- model_id_summary[order(model_id_summary$model_class_id),]
+
+model_id_summary$model_id <- factor(
+  model_id_summary$model_id,
+ levels = unique(model_id_summary$model_id
+                 )
+ )
+
+heatmap_fig <- function(df, dim) {
+  df |> 
+    ggplot(aes(y = model_id, 
+               x = model_class_id,
+               fill = n
+    )) +
+    geom_tile(colour="black")+
+    scale_fill_distiller(name = "Count", palette = "Spectral")+
+    scale_x_discrete(labels = c("LM", "NN", "SVM", "TM"))+
+    #scale_y_discrete(labels = c("<30", "30-300", ">300"))+
+    #geom_text(aes(label = model_id), position = position_jitter())+
+    labs(x = "Model class type", y = "Algorithm")+
+    theme_bw()+
+    facet_wrap(vars(paradigm))
+   # scale_y_discrete(values)
+  
+}
+heatmap_fig(model_id_summary)

### 2025-03-16 manuscript/manuscript.qmd
feat: add model information as panel to figure 5
cleaned pretty-model-ids, added additional information to heatmap figure

--- 2025-03-10 manuscript/manuscript.qmd
@@
 We collapsed SVM and Tree-Based categories due to their low representation in the model summary.
-Figure 5 reveals studies using smaller feature sets tend to perform best, whereas the best model class differs depending on the prediction task.
+Figure 5 summarizes differences in success across categories (a), as well as the algorithms in each model class (b).
+Oveall, studies using smaller feature sets tend to perform best, whereas the best model type largely depends on the nature of the prediction task.
 
-![Heatmap Depicting Success Across Tasks](../manuscript/heat_map_figure.png "Heatmap depicting success across tasks according to Feature N category and model class.
-Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="892"}
+![Heatmaps summarizing models.
+5(a) depicts overall success across tasks according to model type and feature *n* summaries.
+Text labels summarize the number of models belonging to each subgroup, whereas the numbers in parentheses summarize the median number of stimuli used.
+5(b) summarizes the algorithms pertaining to each class, colour-coded by frequency.
+Grey rectangles are visual aids aligning with *x*-axis groupings in 5(a) (white: LM; light grey: NN; dark grey: other).](../manuscript/model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="668"}
 

### 2025-03-16 etc/heat_map_figure.R

@@ -1,16 +1,15 @@
 library(ggplot2)
+library(dplyr)
 
 # Read in best models ---------------------------------------------
-
-
 
 R_heatmap <- read.csv("analysis/R_summary.csv")
 C_heatmap <- read.csv("analysis/C_summary.csv")
 
+# Success Heatmap -------------------------------------------------
 
-# Select relevant columns for plotting ----------------------------
 
-Rtmp <- R_heatmap |> dplyr::select(
+Rtmp <- R_heatmap |> select(
   model_class_id,
   feature_n_complexity,
   valuesMax,
@@ -19,7 +18,7 @@ Rtmp <- R_heatmap |> dplyr::select(
   citekey
 )
 
-Ctmp <- C_heatmap |> dplyr::select(
+Ctmp <- C_heatmap |> select(
   model_class_id,
   feature_n_complexity,
   valuesMax,
@@ -37,12 +36,12 @@ tmp[tmp$model_class_id %in%
       c("Support Vector Machines",
         "Tree-based Methods" ),]$model_class_id <-"SVM,TM"
 
-tmp <- tmp |> dplyr::group_by(
+tmp <- tmp |> group_by(
   dimension,
   model_class_id,
   feature_n_complexity
 )|>
-  dplyr::mutate(
+  mutate(
     study_n = length(citekey),
     stim_mid = median(stimulus_n),
     label = paste0("n=",study_n,"\n(", stim_mid, ")")
@@ -75,40 +74,96 @@ heatmap_facets <- tmp |>
   theme_classic(base_size = 14,base_family = "Helvetica")
 
 
-heatmap_facets
+# Model Types -----------------------------------------------------
 
-ggsave("heat_map_figure_R1.png", width = 14, height = 4, units = "in",dpi = 300)
+# read model summary
+
+best_mods <- read.csv("etc/pretty-model-ids.csv")
+
+# select relevant columns
+
+best_mods <- best_mods |> select(
+  citekey, 
+  paradigm, 
+  model_class_id,
+  model_id
+)
+
+# count the number of models, making sure they aren't doubly
+# represented for VA studies
+
+model_id_summary <- best_mods |>
+  group_by(
+    paradigm,
+    citekey
+  ) |>
+  reframe(
+    model_id = unique(
+      model_id
+    ),
+    model_class_id = unique(
+      model_class_id
+    )
+  ) 
+
+model_id_summary <- model_id_summary |>
+  ungroup() |>
+  group_by(paradigm) |>
[…]

### 2025-03-16 etc/model_class_summary.R

@@ -1,65 +1,0 @@
-library(dplyr)
-
-best_mods <- read.csv("etc/pretty-model-ids.csv")
-
-best_mods <- best_mods |> select(
-  citekey, 
-  paradigm, 
-  model_class_id,
-  model_id
-)
-
-
-model_id_summary <- best_mods |>
-  group_by(
-    paradigm,
-    citekey
-  ) |>
-  reframe(
-    model_id = unique(
-      model_id
-    ),
-    model_class_id = unique(
-      model_class_id
-    )
-  ) 
-
-model_id_summary <- model_id_summary |>
-  ungroup() |>
-  group_by(paradigm) |>
-  add_count(model_id)
-
-model_id_summary$paradigm <- factor(
-  model_id_summary$paradigm,
-  levels = c("regression", "classification"),
-  labels = c("Regression", "Classification")
-)
-
-
-
-model_id_summary <- model_id_summary[order(model_id_summary$model_class_id),]
-
-model_id_summary$model_id <- factor(
-  model_id_summary$model_id,
- levels = unique(model_id_summary$model_id
-                 )
- )
-
-heatmap_fig <- function(df, dim) {
-  df |> 
-    ggplot(aes(y = model_id, 
-               x = model_class_id,
-               fill = n
-    )) +
-    geom_tile(colour="black")+
-    scale_fill_distiller(name = "Count", palette = "Spectral")+
-    scale_x_discrete(labels = c("LM", "NN", "SVM", "TM"))+
-    #scale_y_discrete(labels = c("<30", "30-300", ">300"))+
-    #geom_text(aes(label = model_id), position = position_jitter())+
-    labs(x = "Model class type", y = "Algorithm")+
-    theme_bw()+
-    facet_wrap(vars(paradigm))
-   # scale_y_discrete(values)
-  
-}
-heatmap_fig(model_id_summary)

### 2025-03-19 manuscript/manuscript.qmd
comments on introduction

@@
 
+<!--Paragraph on MER as regression task-->
+
 Researchers have assessed regression and classification techniques on diverse corpora with features drawn from music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
@@
 
+<!--paragraph on models used across regession & classification tasks-->
+```{=html}
+<!-- 
+- Types of classification algorithms employed
+- Popularity of SVMs (for both classification and regression)
+- Algorithms used for personalized and nonpersonalized MER models?
+- Success with regression varieties
+- Introduction of neural networks & deep learning paradigms
+-->
+```
+
+<!--summary of feature sets and quantity-->
+```{=html}
+<!-- 
+- Wide set of features explored
+- Summary of categories commonly used/discussed (Panda)
+- Audio, midi, lyric features
+- Low-, mid-, and high-level features
+- Emphasize focus on audio-based featuers
+- Small, medium, and large data sets 
+- Could emphasize that types of features differ based on type of study
+(psychology, engineering) due to different goals
+-->
+```
+
+<!--MER approaches: psychology, engineering approaches-->
+```{=html}
+<!-- 
+- Summary of findings, success with MER approaches.
+  - Scope of topic areas explored
+  - Annotations: sometimes presented as a game, either experts or participants,
+  sometimes secondary data from web databases (LastFM).
+Treated as "ground truth" (reference standard may be more accurate).
+Training/testing/validation.
+Comparisons with previously collected data/benchmarks
+  - Participants: e.g., 5 experts, MTurk, etc.
+  - Demographics
+  - Common stimuli/genres: predominately pop
+- Summary of findings, success with psychological approaches
+  - Scope of topic areas explored
+  - Annotations: Used to explain variance in participants' responses. Cross-validation rare.
+  - Participants: psychology students, Prolific/MTurk?
+  - Demographics
+  - Common stimuli/genres: predominately classical
+-->
+```
+
 ## The semantic gap in MER
+```{=html}
+<!--
+I'm considering now reworking this paragraph and de-emphasizing the semantic gap given the limited extent to which can address this.
+It might be worth including to show the semantic gap has narrowed, and we can point to the Barthet estimate, or to conclude that "linear methods with small to mid-sized feature sets appear perform best for this dimension".
+-->
+```
 
@@
 ## Aims
-
+<!--This paragraph now is somewhat inconsistent with the analyses we actually perform motivating the journal/feature N/model discussion-->
 Our aim is to evaluate the predictive accuracy of two models of emotional expression in music: (a) models that predict track-specific coordinates in affective circumplex space (valence and arousal), and (b) models that classify discrete emotion categories.

### 2025-03-19 manuscript/manuscript.qmd
updates to manuscript, notes about conversion to pdf

--- 2025-03-16 manuscript/manuscript.qmd
@@
 Whereas early discourse largely focused on generative composition using computers [@zaripov1969], attention later shifted to creating methods to predict emotion using music's structural cues.
-Novel techniques for information retrieval emerged in the 1950s and 1960s [@fairthorne1968], inspiring analogous developments for automated music analysis (@kassler1966toward; @mendel1969some).
+Novel techniques for information retrieval emerged in the 1950s and 1960s [@fairthorne1968], inspiring analogous developments for automated music analysis [@kassler1966toward; @mendel1969some].
 These developments would set the stage for early work in music emotion recognition (MER).
-Katayose et al.
-(1988) conducted the first study of this nature, creating an algorithm that associated emotions with analyzed chords to generate descriptions like "there is hopeful mood on chord from 69 to 97 \[*sic*\]." [@katayose_sentiment_1988, p.
+@katayose_sentiment_1988 conducted the first study of this nature, creating an algorithm that associated emotions with analyzed chords to generate descriptions like "there is hopeful mood on chord from 69 to 97 \[*sic*\]." [@katayose_sentiment_1988, p.
 1087].
@@
 Specifically, relations between low-level predictors from music and text and the perceptual phenomena they model remain poorly understood, reaching a ceiling in prediction accuracy [@celma_foafing_2006].
-To address this so-called *semantic gap*, researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang2016br].
+To address this so-called *semantic gap*, researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang2016br;@alvarez2023ri;@agarwal2021an].
 Through these approaches, MER researchers attempt to shatter a so-called *glass ceiling* [@downie_music_2008] by establishing central predictors for emotions.
 To date, however, no study has systematically compared results of these diverse approaches.
+
+<!-- added more recent references to make the neural network mention more up to date, TE 19/3/2025 -->
 
@@
 Our aim is to evaluate the predictive accuracy of two models of emotional expression in music: (a) models that predict track-specific coordinates in affective circumplex space (valence and arousal), and (b) models that classify discrete emotion categories.
-We focus on recent to identify key factors such as modeling techniques and features that significantly affect prediction accuracy.
+We focus on recent studies to identify the overall success rate in MER tasks and the key factors such as modeling techniques and features that contribute to the prediction accuracy of the models.
 To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years.
@@
 For emotion classification, we expect simple utilitarian emotions (e.g., fear, anger) will be easier to predict than more complex social emotions (e.g., sadness, nostalgia).
+
+<!-- DISCUSS: we have not address this last thought at all, TE 19/3/2025 -->
 
@@
 | Model N    | 204                         | 86                        | 290   |
-| Techniques | Neural Nets: 64             | 21                        | 85    |
-| Techniques | Support Vector Machines: 62 | 26                        | 88    |
-| Techniques | Linear Methods: 62          | 19                        | 81    |
-| Techniques | Tree-based Methods: 14      | 16                        | 30    |
+| Techniques | Neural Nets (NN): 64             | 21                        | 85    |
+| Techniques | Support Vector Machines (SVM): 62 | 26                        | 88    |
+| Techniques | Linear Methods (LM): 62          | 19                        | 81    |
+| Techniques | Tree-based Methods (TM): 14      | 16                        | 30    |
 | Techniques | KS, Add. & KNN: 2           | 4                         | 6     |
@@
 This reduction is done to avoid the issue of multiple models from the same study deflating the results as majority of the models included are relative modest baseline or alternative models that do not represent the novelty or content of the article.
+We also provide a summary of the results with all models included in addition to the chosen strategy, where the best model of each study is considered.
 
@@
 In this table we also report two subgroup analyses.
-One where we have divided the studies according to the number of features they contain (three categories based on quantiles to keep the group size comparable) and into five modelling techniques introduced earlier (Table 1).
+One where we have divided the studies according to the number of features they contain (three categories based on quantiles to keep the group size comparable) and into four modelling techniques introduced earlier (Table 1).
+
+<!-- DISCUSS: I have changed the modelling techniques into FOUR categories, TE 19/3/2025 -->
 
@@
 
-To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents (A) a forest and (B) funnel plot of the random-effects model, based on the best-performing models from all studies.
+To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents a forest of the random-effects model, based on the best-performing models from all studies.
 In terms of the forest plot, the range of prediction values (correlations) is broad, spanning from 0.13 to 0.92, with all studies except Koh et al.
@@
 While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), and in @griffiths2021am (n = 40).
-The funnel plot in panel B of Figure 2 shows clustering at the top of the plot (studies with low standard error) and no assumed larger diversity in the correlations when the error rates increase.
-However, there is no clear asymmetry in the plot, verified by non-significant Egger's test ($\beta$ = 5.05, CI95% -0.99-11.09, *t* = 1.64, *p* = 0.112, @eggersmith_1997).
+If we explore the asymmetry of the model prediction rate across standard error, we do not observe particular asymmetries that would indicate particular bias in the reported studies.
+This is verified by non-significant Egger's test ($\beta$ = 5.05, CI95% -0.99-11.09, *t* = 1.64, *p* = 0.112, @eggersmith_1997).
+
 Coming back to the mean of valence correlation of 0.669 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect.
@@
 <!-- numbers in the text updated up to here, CA 20/2/2025 -->
+<!-- I've removed the reference to the funnel plot, TE 19/3/2025 -->
 
@@
 <!-- numbers in the text updated up to here, CA 20/2/2025 -->
+<!-- DISCUSS: we don't report journal type of explain/predict differences, although we do some of these in arousal, TE 19/3/2025 -->
 
@@
 
-Figure 3 presents (A) a forest and (B) funnel plot of the random-effects model of the best-performing models from all studies.
+Figure 3 presents a forest plot of the random-effects model of the best-performing models from all studies.
 Similarly to valence, the range of correlations is also wide for arousal, ranging from 0.35 to 0.95, with all studies demonstrating evidence of positive correlations.
-A mean estimate of 0.82 or higher is achieved by the majority (14 out of the 22 models).
+A mean estimate of 0.81 or higher is achieved by the majority (14 out of the 22 models).
 Due to large sample in most studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am; @koh2023me; @saizclar2022pr; @wang2021ac].
-The funnel plot in panel B illustrates the limited range of the correlations and show heavy clustering at the top of the plot (studies with low standard error).
-There is no clear asymmetry in the plot, verified by non-significant Egger's test reported above.
+
+<!-- Removed reference to the funnel plot, TE 19/3/2025 -->
 
@@
 
+<! -- DISCUSS: 4 digits is too much, let's make this consistent, 3 in all places?, TE 19/3/2025 -->
+
 ### Quantifying study heterogeneity
@@
 
-### Model success across concepts
+### Model success across concepts, model types and feature counts
+
+<!-- Changed the header slightly, TE 19/3/2025-->
 
@@
 We collapsed SVM and Tree-Based categories due to their low representation in the model summary.
-Figure 5 summarizes differences in success across categories (a), as well as the algorithms in each model class (b).
-Oveall, studies using smaller feature sets tend to perform best, whereas the best model type largely depends on the nature of the prediction task.
+Figure 5 summarizes differences in success (a) across categories, as well as (b) the algorithms in each model class.
+Overall, studies using smaller feature sets tend to perform best, whereas the best model type largely depends on the nature of the prediction task.
 
 ![Heatmaps summarizing models.
-5(a) depicts overall success across tasks according to model type and feature *n* summaries.
+Panel a depicts overall success across tasks according to model type and feature *n* summaries.
 Text labels summarize the number of models belonging to each subgroup, whereas the numbers in parentheses summarize the median number of stimuli used.
-5(b) summarizes the algorithms pertaining to each class, colour-coded by frequency.
-Grey rectangles are visual aids aligning with *x*-axis groupings in 5(a) (white: LM; light grey: NN; dark grey: other).](../manuscript/model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Panel b summarizes the algorithms pertaining to each class, colour-coded by frequency.
+Grey rectangles are visual aids aligning with *x*-axis groupings in panel a (white: LM; light grey: NN; dark grey: other).](../manuscript/model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
 Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="668"}

### 2025-03-19 manuscript/_figure4.qmd
updates to manuscript

@@
 ggarrange(fp1)
-
 ```

### 2025-03-19 manuscript/manuscript-apaquarto.qmd
updates to manuscript

@@
 
-{{< include _figure1.qmd >}}
+![Flowchart of the study inclusions/eliminations.](figure1.svg){width="580"}
 
@@
 ```{r}
-#| label: tbl-table1
-#| id: tbl-table1
+#| id: table1
 #| output: asis
+#| error: false
 #| warning: false
@@
 #| tbl-cap: Summary of the models for regression and classification studies.
-library(tidyverse)
-library(kableExtra)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
+suppressPackageStartupMessages(library(tidyverse))
+suppressPackageStartupMessages(library(kableExtra))
+#suppressPackageStartupMessages(library(flextable))
 
@@
 print(knitr::kable(t,bookstabs=TRUE))
-#  theme_apa()
+#flextable(t) %>% theme_apa()
 
 ```
+
+{{< include _figure2.qmd >}}
+
+{{< include _figure3.qmd >}}
+
+{{< include _figure4.qmd >}}
 

### 2025-03-21 manuscript/manuscript.qmd
changes during our last meeting

@@
 
-## The semantic gap in MER
+<!--paragraph on models used across regession & classification tasks-->
+```{=html}
+<!-- 
+- Types of classification algorithms employed
+- Popularity of SVMs (for both classification and regression)
+- Algorithms used for personalized and nonpersonalized MER models?
+- Success with regression varieties
+- Introduction of neural networks & deep learning paradigms
+-->
+```
+
+<!--summary of feature sets and quantity-->
+```{=html}
+<!-- 
+- Wide set of features explored
+- Summary of categories commonly used/discussed (Panda)
+- Audio, midi, lyric features, tags 
+- Low-, mid-, and high-level features
+- Emphasize focus on audio-based featuers
+- Small, medium, and large data sets (Features: 30, 300, 3000) 
+- Could emphasize that types of features differ based on type of study
+(psychology, engineering) due to different goals
+-->
+```
+
+<!--MER approaches: psychology, engineering approaches-->
+```{=html}
+<!-- 
+- Big picture: explanation vs predicting
+- Summary of findings, success with MER approaches.
+  - Scope of topic areas explored
+  - Annotations: sometimes presented as a game, either experts or participants,
+  sometimes secondary data from web databases (LastFM).
+Treated as "ground truth" (reference standard may be more accurate).
+Training/testing/validation.
+Comparisons with previously collected data/benchmarks
+  - Participants: e.g., 5 experts, MTurk, etc.
+  - Demographics
+  - Common stimuli/genres: predominately pop
+- Summary of findings, success with psychological approaches
+  - Scope of topic areas explored
+  - Annotations: Used to explain variance in participants' responses. Cross-validation rare.
+  - Participants: psychology students, Prolific/MTurk?
+  - Demographics
+  - Common stimuli/genres: predominately classical
+-->
+```
+
+## The semantic gap in MER / What are the reported standards? / ceiling
+```{=html}
+<!--
+I'm considering now reworking this paragraph and de-emphasizing the semantic gap given the limited extent to which can address this.
+It might be worth including to show the semantic gap has narrowed, and we can point to the Barthet estimate, or to conclude that "linear methods with small to mid-sized feature sets appear perform best for this dimension".
+
+- semantic challenge
+- inherent error in all stages (annotation, features, models)
+
+-->
+```
 
@@
 
+<!--This paragraph now is somewhat inconsistent with the analyses we actually perform motivating the journal/feature N/model discussion-->
+
 Our aim is to evaluate the predictive accuracy of two models of emotional expression in music: (a) models that predict track-specific coordinates in affective circumplex space (valence and arousal), and (b) models that classify discrete emotion categories.
-We focus on recent studies to identify the overall success rate in MER tasks and the key factors such as modeling techniques and features that contribute to the prediction accuracy of the models.
+We focus on recent studies to identify the overall success rate in MER tasks and the key factors such as modeling techniques, the number of features, or the inferential goal (explanation vs prediction) that might contribute to the prediction accuracy of the models.
 To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years.
 Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model.
-For emotion classification, we expect simple utilitarian emotions (e.g., fear, anger) will be easier to predict than more complex social emotions (e.g., sadness, nostalgia).
 
-<!-- DISCUSS: we have not address this last thought at all, TE 19/3/2025 -->
+<!-- incorporate splits into above? -->
 
@@
 
-Figure 4 shows forest and funnel plot visualizations from the random-effects model of the best-performing models in classification studies.
+Figure 4 shows forest plot visualization from the random-effects model of the best-performing models in classification studies.
 $MCC$s vary across a wide range, reporting $MCC$s between 0.55 to 0.98.
@@
 
-<! -- DISCUSS: 4 digits is too much, let's make this consistent, 3 in all places?, TE 19/3/2025 -->
+<!-- DISCUSS: 4 digits is too much, let's make this consistent, 2 in all places?, TE 19/3/2025 -->
 

### 2025-03-21 manuscript/_figure2.qmd
rendered figures into pdf files

@@
                summary = "black",
-                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
+                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80, fontfamily="Times")),
                                 ticks = gpar(cex = 0.80),
                                 xlab  = gpar(cex = 0.80)))|>
-    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30")))
+    fp_decorate_graph(grid = structure( m.cor$TE.common,gp = gpar(lty = 2, col = "grey30",fontfamily="libertine")))
 )
@@
 
-gridExtra::grid.arrange(fp1)
+#gridExtra::grid.arrange(fp1)
+# libertine
+ggsave(filename = 'figure2.pdf', width = 12, height = 6, units = 'in',fp1)
 

### 2025-03-21 manuscript/_figure3.qmd
rendered figures into pdf files

@@
                summary = "black",
-                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80)),
+                txt_gp = fpTxtGp(label = list(gpar(cex = 0.80, fontfamily="Times")),
                                 ticks = gpar(cex = 0.80),
@@
 ggarrange(fp1) #  
+ggsave(filename = 'figure3.pdf', width = 12, height = 6, units = 'in',fp1)
+
 ```

### 2025-03-21 manuscript/_figure4.qmd
rendered figures into pdf files

--- 2025-03-10 manuscript/_figure4.qmd
@@
 ggarrange(fp1)
+ggsave(filename = 'figure4.pdf', width = 12, height = 6, units = 'in',fp1)
 

### 2025-03-22 etc/heat_map_figure.R
feat(etc/heat_map_figure): update panel 2

@@ -1,5 +1,6 @@
 library(ggplot2)
 library(dplyr)
+library(ggpubr)
 
 # Read in best models ---------------------------------------------
 
@@ -80,90 +81,67 @@ heatmap_facets <- tmp |>
 
 best_mods <- read.csv("etc/pretty-model-ids.csv")
 
-# select relevant columns
-
-best_mods <- best_mods |> select(
-  citekey, 
-  paradigm, 
-  model_class_id,
-  model_id
+best_mods$model_class_id <- factor(
+  best_mods$model_class_id,
+  labels = c("LM", "NN", "SVM", "TM")
 )
 
-# count the number of models, making sure they aren't doubly
-# represented for VA studies
+best_mods <- best_mods[
+  order(
+    best_mods$model_class_id, 
+    best_mods$model_id),
+] 
 
-model_id_summary <- best_mods |>
-  group_by(
-    paradigm,
-    citekey
-  ) |>
-  reframe(
-    model_id = unique(
-      model_id
-    ),
-    model_class_id = unique(
-      model_class_id
-    )
-  ) 
-
-model_id_summary <- model_id_summary |>
-  ungroup() |>
-  group_by(paradigm) |>
-  add_count(model_id)
-
-# change factor order for regression and classification
-
-model_id_summary$paradigm <- factor(
-  model_id_summary$paradigm,
-  levels = c("regression", "classification"),
-  labels = c("Regression", "Classification")
+best_mods$tally <- 1
+best_mods$ind <- 1:nrow(best_mods)
+best_mods$model_id <- forcats::fct_reorder(
+  best_mods$model_id,
+  best_mods$ind
+)
+best_mods$dimension <- factor(
+  best_mods$dimension,
+  levels = c("valence", "arousal", "classification"),
+  labels = c("Valence", "Arousal", "Classification")
 )
 
-# re-order models so they follow model classes
+best_mods <- best_mods |> group_by(
+  dimension, 
+  model_class_id, 
+  model_id) |>
+  mutate(best_model = sort(best_model))
 
-model_id_summary <- model_id_summary[
-  order(model_id_summary$model_class_id),]
 
-model_id_summary$model_id <- factor(
-  model_id_summary$model_id,
-  levels = unique(model_id_summary$model_id
+best_mods <- best_mods |> 
+  group_by(dimension, model_id) |> 
+  mutate(
[…]

### 2025-03-23 manuscript/manuscript.qmd
manuscript:updates to intro

@@
 
+## Classification and regression approaches
+
 In the early 2000s, several research groups conducted studies using regression [@friberg_automatic_2002; @liu_automatic_2003] and classification [@lu_automatic_2005; @feng_popular_2003; @mandel_support_2006] techniques to predict emotion in music audio or MIDI.
@@
 In the first year, nine systems classified mood labels in a common data set, reaching 52.65% accuracy (SD = 11.19%).
-These events, along with growing interest in the burgeoning field of affective computing, would lead to an explosion of interest in MER research.[^1]
-
-[^1]: The best-performing model to date reached 69.83 % in the 2017 competition [@park2017representation].
+These events, along with growing interest in the burgeoning field of affective computing, would lead to an explosion of interest in MER research.
 
@@
 
-Researchers have assessed regression and classification techniques on diverse corpora with features drawn from music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
-In one widely-cited study, Yang (2008) approached MER as a regression task, predicting the valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) of 195 Chinese pop songs, achieving 62% accuracy for arousal but only 28% for valence [@yang2008].
+- Following one decade of competitions, the AMC task's highest performing model reached 69.83% accuracy [@park2017representation].
+In parallel, other researchers began assessing MER as a regression task.
+The first study to popularize this approach predicted valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) in 195 Chinese pop songs [@yang2008] using audio-extracted features.
+The regression model predicted arousal with 62% accuracy, but only achieved 28% accuracy for valence.
 This difference in prediction accuracy between dimensions has reappeared in several subsequent studies [e.g., @bai2016dimensional; @coutinho2013psychoacoustic], with some research suggesting this challenge reflects fewer well-established predictors and more individual differences for valence than arousal [@yang2007music; @eerola2011c].
@@
 <!--paragraph on models used across regession & classification tasks-->
-```{=html}
-<!-- 
-- Types of classification algorithms employed
-- Popularity of SVMs (for both classification and regression)
-- Algorithms used for personalized and nonpersonalized MER models?
-- Success with regression varieties
-- Introduction of neural networks & deep learning paradigms
--->
-```
 
-<!--summary of feature sets and quantity-->
-```{=html}
-<!-- 
-- Wide set of features explored
-- Summary of categories commonly used/discussed (Panda)
-- Audio, midi, lyric features, tags 
-- Low-, mid-, and high-level features
-- Emphasize focus on audio-based featuers
-- Small, medium, and large data sets (Features: 30, 300, 3000) 
-- Could emphasize that types of features differ based on type of study
-(psychology, engineering) due to different goals
--->
-```
+Since the early days of MER, researchers have adopted a wide range of models to predict emotions, ranging in complexity from linear regression models [@saizclar2022pr; @griffiths2021am; @yang2008] to neural networks [@orjesek2022en; @hizlisoy2021mu].
+Whereas early classification studies commonly employed Gaussian mixture models [@lu_automatic_2005; @liu_automatic_2003] and support vector machines [@mandel2007labrosa; @lin2009eeg; @tzanetakis2007marsyas], convolutional, recurrent, and fully-connected neural networks have become increasingly popular in recent years [@grekow2021music; @song2018audio; @coutinho2017sh].
+In regression tasks, a wide range of algorithms have been tested, including partial least squares [@gingras2014be; @wang2021ac], support vector machines [@grekow2018au; @hu2017cr; @agarwal2021an], random forests [@beveridge2018po; @xu2021us], and convolutional neural networks [@orjesek2022en; @orjesek2022en].
+
+## Large vs. small data
+
+Researchers have assessed regression and classification techniques on diverse datasets with features drawn from music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
+To facilitate model comparison, several databases have been shared publicly, including MediaEval [@soleymani20131000], DEAM[@aljanaki2017developing], and AMG1608[@chen2015amg1608].
+These datasets, represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by a relatively large number of participants (either by experts, students, or crowdsourced workers).
+Many datasets include audio features analyzed with software toolboxes for audio analysis such as OpenSMILE [@] and MIRToolbox [@lartillot2007matlab]---enabling models that predict ratings using tens, or even hundreds, of audio features.
+
+Although MER studies increasingly perform prediction on large-scale datasets, others use small datasets to evaluate models trained for specific contexts.
+For example, @gingras2014be evaluates the effect of amplitude normalization on emotion ratings using 84 six-second classical excerpts rated by two separate groups of 30 participants.
+@griffiths2021am test MER in a multi-genre context using two corpora with 20 and 40 songs across 20 distinct genres.
+@saizclar2022pr predicts the affective dimensions of the circumplex model in 40 short (8-12s) piano excerpts using onset curves (changes in the energy of a note starting from its onset).
 

### 2025-03-26 manuscript/manuscript.qmd
manuscript: updates to introduction

--- 2025-03-19 manuscript/manuscript.qmd
@@
 In the first year, nine systems classified mood labels in a common data set, reaching 52.65% accuracy (SD = 11.19%).
-These events, along with growing interest in the burgeoning field of affective computing, would lead to an explosion of interest in MER research.[^1]
+These events, along with growing interest in the burgeoning field of affective computing, would lead to an explosion of interest in MER research.
 
-[^1]: The best-performing model to date reached 69.83 % in the 2017 competition [@park2017representation].
+<!--Paragraph on MER as regression task-->
 
-Researchers have assessed regression and classification techniques on diverse corpora with features drawn from music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
-In one widely-cited study, Yang (2008) approached MER as a regression task, predicting the valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) of 195 Chinese pop songs, achieving 62% accuracy for arousal but only 28% for valence [@yang2008].
+In the tenth annual AMC task, the highest performing model reached 69.83% accuracy [@park2017representation].
+In parallel, other researchers began assessing MER as a regression task.
+The first study to popularize this approach predicted valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) in 195 Chinese pop songs [@yang2008] using audio-extracted features.
+The regression model predicted arousal with 62% accuracy, but only achieved 28% accuracy for valence.
 This difference in prediction accuracy between dimensions has reappeared in several subsequent studies [e.g., @bai2016dimensional; @coutinho2013psychoacoustic], with some research suggesting this challenge reflects fewer well-established predictors and more individual differences for valence than arousal [@yang2007music; @eerola2011c].
 
-## The semantic gap in MER
+<!--paragraph on models used across regession & classification tasks-->
 
-The difficulty in predicting valence reflects a broader challenge in information retrieval.
-Specifically, relations between low-level predictors from music and text and the perceptual phenomena they model remain poorly understood, reaching a ceiling in prediction accuracy [@celma_foafing_2006].
-To address this so-called *semantic gap*, researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang2016br;@alvarez2023ri;@agarwal2021an].
+Across regression and classification paradigms, a wide range of models have been employed, ranging from linear regression models [@saizclar2022pr; @griffiths2021am; @yang2008] to deep neural networks [@orjesek2022en; @hizlisoy2021mu].
+In classification tasks, early work has commonly employed Gaussian mixture models [@lu_automatic_2005; @liu_automatic_2003] and support vector machines [@mandel2007labrosa; @lin2009eeg; @tzanetakis2007marsyas], whereas convolutional, recurrent, and fully-connected neural networks have become increasingly popular in recent years [@grekow2021music; @song2018audio; @coutinho2017sh].
+In regression tasks, a wide range of algorithms have been tested, including partial least squares [@gingras2014be; @wang2021ac], support vector machines [@grekow2018au; @hu2017cr; @agarwal2021an], random forests [@beveridge2018po; @xu2021us], and convolutional neural networks [@orjesek2022en].
+
+## Large vs. small data
+
+MER tasks commonly apply regression and classification techniques to diverse datasets with features drawn from both music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
+To facilitate model comparison, several databases have been shared publicly, including MediaEval [@soleymani20131000], DEAM [@aljanaki2017developing], and AMG1608[@chen2015amg1608].
+These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by a relatively large number of participants (either by experts, students, or crowdsourced workers).
+Many datasets include audio features analyzed with software toolboxes for audio analysis such as OpenSMILE [@] and MIRToolbox [@lartillot2007matlab]---enabling models that predict ratings using tens, or even hundreds, of audio features.
+Large datasets are ideal for generalizing predictions across diverse musical samples and are commonly employed in machine learning applications focused on maximizing accuracy of a MER system.
+
+Although training MER systems with a wide range of stimuli and features can be useful for generalizable and accurate modeling, small datasets can be more appropriate in explorations that require precise control of stimuli or analyzed features to understand a model's performance.
+For example,  @griffiths2021am evaluated a MER model's performance when predicting 20 tracks different genres, validating the model on another 40 tracks.
+@saizclar2022pr evaluated how onset curves (changes in the energy of a note starting from its onset) can be incorporated into a predictive framework using 40 short (8-12s) piano excerpts.
+Smaller datasets are also useful in studies attempting to explain how stimulus qualities such as amplitude normalization [@gingras2014be] or different performers' interpretations [@battcock2021in] affect ratings of valence and arousal.
+Although these studies are not always designed with MER applications in mind, their similar framework has enabled direct application [e.g., @chowdhury2021perceived].
+
+## The semantic gap in MER / What are the reported standards? / ceiling
+
+```{=html}
+<!--
+- Wide range of MER models attempting to outperform previous benchmarks, comparing performance against baseline models
+- Introduce ceilings for classification, valence, and arousal, citing Barthet study
+- Citing what some researchers attribute limitations to (e.g., lower valence than arousal)
+- MIR discussions of "semantic" challenge
+- inherent error in all stages (annotation, features, models)
+- Due to wide range of approaches, difficult to evaluate how successful attempts to raise glass ceiling have been
+- How do modeling techniques, and the number of features used affect performance? Which combinations perform best?
+
+-->
+```
+
+Researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang2016br;@alvarez2023ri;@agarwal2021an].
 Through these approaches, MER researchers attempt to shatter a so-called *glass ceiling* [@downie_music_2008] by establishing central predictors for emotions.

### 2025-03-26 manuscript/manuscript.qmd
Some bibtex fixes and wrote missing parts in the introduction

@@
 
+<!-- ACM Computing Surveys: Shorter survey papers should be self-contained and not exceed 15 pages in length including references. -->
+
 # Introduction
@@
 MER tasks commonly apply regression and classification techniques to diverse datasets with features drawn from both music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
-To facilitate model comparison, several databases have been shared publicly, including MediaEval [@soleymani20131000], DEAM [@aljanaki2017developing], and AMG1608[@chen2015amg1608].
+To facilitate model comparison, several databases have been shared publicly, including MediaEval [@soleymani2013], DEAM [@aljanaki2017developing], and AMG1608 [@chen2015amg1608].
 These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by a relatively large number of participants (either by experts, students, or crowdsourced workers).
-Many datasets include audio features analyzed with software toolboxes for audio analysis such as OpenSMILE [@] and MIRToolbox [@lartillot2007matlab]---enabling models that predict ratings using tens, or even hundreds, of audio features.
+Many datasets include audio features analyzed with software toolboxes for audio analysis such as OpenSMILE [@eyben2010opensmile] and MIRToolbox [@lartillot2007matlab] -- enabling models that predict ratings using tens, or even hundreds, of audio features.
 Large datasets are ideal for generalizing predictions across diverse musical samples and are commonly employed in machine learning applications focused on maximizing accuracy of a MER system.
@@
 
-## The semantic gap in MER / What are the reported standards? / ceiling
+## The current benchmarks of MER
 
@@
 <!--
-- Wide range of MER models attempting to outperform previous benchmarks, comparing performance against baseline models
-- Introduce ceilings for classification, valence, and arousal, citing Barthet study
-- Citing what some researchers attribute limitations to (e.g., lower valence than arousal)
-- MIR discussions of "semantic" challenge
-- inherent error in all stages (annotation, features, models)
+- Wide range of MER models attempting to outperform previous benchmarks, comparing performance against baseline models [MENTIONED NOW]
+- Introduce ceilings for classification, valence, and arousal, citing Barthet study [MENTIONED]
+- Citing what some researchers attribute limitations to (e.g., lower valence than arousal) [MENTIONED]
+- MIR discussions of "semantic" challenge [LEFT OUT NOW, GLASS-CEILING]
+- inherent error in all stages (annotation, features, models) [MENTIONED]
 - Due to wide range of approaches, difficult to evaluate how successful attempts to raise glass ceiling have been
@@
 
-Researchers have attempted to identify new feature sets with greater relevance to emotion [@panda2020audio; @chowdhury2021perceived], combine low-, mid-, and high-level features using multimodal data [@celma_foafing_2006], or train neural networks to automatically learn features from audio [@zhang2016br;@alvarez2023ri;@agarwal2021an].
-Through these approaches, MER researchers attempt to shatter a so-called *glass ceiling* [@downie_music_2008] by establishing central predictors for emotions.
-To date, however, no study has systematically compared results of these diverse approaches.
+Prediction accuracy in MER tasks has improved as datasets and models have become more sophisticated; The regression models for arousal/valence was 58%/28% in 2008 [@yang2008], 70%/26% in 2010 [@huq2010automated], to 67%/46% in 2021 [@yang2021an].
+The classification rates have similarly increased from 53% [@downie_music_2008] to 70% [@park2017representation] to 83% [@sarkar2020recognition] in the same period.
+Comparing these past efforts is challenging due to inconsistencies in metrics, modelling architectures, datasets, and model evaluation criteria.
+While we assume that overall accuracy has improved significantly over the past decade, predicting valence remains more challenging than predicting arousal.
 
-<!-- added more recent references to make the neural network mention more up to date, TE 19/3/2025 -->
+Researchers have sought to enhance emotion prediction by identifying more relevant feature sets [@panda2020audio; @chowdhury2021perceived], integrating low-, mid-, and high-level features through multimodal data [@celma_foafing_2006], and leveraging neural networks to learn features directly from audio [@zhang2016br; @alvarez2023ri; @agarwal2021an].
+These approaches aim to overcome what has been described as a *glass ceiling* in MER research [@downie_music_2008] -- a limitation sometimes referred to as the *semantic gap* [@wiggins_semantic_2009].
+However, this ceiling may be better understood as an inherent measurement error arising from annotations, feature representations, and model limitations.
+While isolating the sources of these errors remains infeasible at this stage, comparing success rates across modeling techniques, feature set sizes, and other meaningful factors offers a step toward addressing this challenge.
+To date, however, no study has systematically compared the results of the diverse approaches employed in MER research.
 
@@
 
-Our aim is to evaluate the predictive accuracy of two models of emotional expression in music: (a) models that predict track-specific coordinates in affective circumplex space (valence and arousal), and (b) models that classify discrete emotion categories.
+Our aim is to evaluate the predictive accuracy of two types emotional expression in music: (a) models that predict track-specific coordinates in affective circumplex space (valence and arousal), and (b) models that classify discrete emotion categories.
 We focus on recent studies to identify the overall success rate in MER tasks and the key factors such as modeling techniques, the number of features, or the inferential goal (explanation vs prediction) that might contribute to the prediction accuracy of the models.
@@
 Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model.
+In terms of the modelling techniques and the number of features, a reasonable hypothesis is that advanced techniques (e.g., neural networks) and larger amount of features will lead to higher prediction rates than conventional techniques (e.g., logistic regression or linear regression) and smaller amount of features.
+However, this relationship might not be as straightforward as this due to the demands complex models place on dataset size [@alwosheel2018;@sun2017revisiting].
 
@@
 
-```{=html}
-<!-- Question to Cameron: Could you add some of the studies included in the meta-analysis in the references to those studies that do not share datasets to make this more relevant.
-I just copied two references that I know are examples of datasets that require extra steps, but we have studies where we just don't even know whether the data is available, right?
-
-CA: I've added some studies now, though these were excluded from the final meta-analysis.
-I also have a few examples of those which were included in the final results based on scrolling through the articles.
-Many are psychology papers, where it seems less common to share data publicly, but those also tend to have more case-specific goals rather than comparing results to existing benchmarks, so I didn't cite them.
-@hizlisoy2021mu proposes a new turkish music database, but I wasn't able to find the data from the article, so I added that.
-@zhang2017fe uses a dataset but doesn't seem to provide information on how to access it.
-TE: great, well done, job done. -->
-```
-
 <!-- ### Feature definition/validations -->
@@
 Consequently, it is too early to generalize that models based on domain knowledge, with a limited number of features and classical techniques, will continue to outperform machine learning approaches that utilize a large (300+) feature sets.
-We believe that the relatively modest size of datasets available so far has prevented deep learning approaches from fully leveraging their potential to learn generalizable patterns in the data.
+We believe that the relatively modest size of datasets available so far has prevented deep learning approaches from fully leveraging their potential to learn generalizable patterns in the data .
 For reference, the size of the datasets in MER are currently comparable to dataset sizes for modeling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
 However, annotated datasets for visual scenes and objects tend to be much larger, often exceeding 100,000 annotated examples [@deng2009imagenet; @krishna2017visual].
-Datasets of these magnitudes seem to be required for appropriate utilisation of deep learning algorithms, which may explain the modest results observed in the music emotion recognition studies.
+Datasets of these magnitudes seem to be required for appropriate utilisation of deep learning algorithms [@alwosheel2018;@sun2017revisiting], which may explain the modest results observed in the music emotion recognition studies.
 
@@
 
-## Implications and conclusion
-
 The present meta-analysis demonstrates that significant progress has been made toward developing accurate and scalable MER models over the past decade.
 Future efforts should prioritize feature validation, standardized reporting, the construction of larger and more diverse datasets, and the transparent sharing of research materials to ensure further consistent improvements in MER.
-
-<!-- This last section needs to be expanded. Or text moved from above to here? -->
 

### 2025-03-26 etc/heat_map_figure.R

@@ -72,7 +72,7 @@ heatmap_facets <- tmp |>
   scale_y_discrete(labels = c("<30", "30-300", ">300"))+
   geom_text(aes(label = label))+
   labs(x = "Model class type", y = "Feature N category")+
-  theme_classic(base_size = 14,base_family = "Helvetica")
+  theme_classic(base_size = 14,base_family = "Times")
 
 
 # Model Types -----------------------------------------------------

### 2025-03-26 manuscript/manuscript.qmd
MS changes made during the meeting

@@
 
-## Large vs. small data
+## Dataset size and scope
 
@@
 Many datasets include audio features analyzed with software toolboxes for audio analysis such as OpenSMILE [@eyben2010opensmile] and MIRToolbox [@lartillot2007matlab] -- enabling models that predict ratings using tens, or even hundreds, of audio features.
+
+REVISE:
 Large datasets are ideal for generalizing predictions across diverse musical samples and are commonly employed in machine learning applications focused on maximizing accuracy of a MER system.
+
+IDEA: LARGE data requirements for machine-learning/deep learning, but annotating music is resource-intensive.
 
@@
 Smaller datasets are also useful in studies attempting to explain how stimulus qualities such as amplitude normalization [@gingras2014be] or different performers' interpretations [@battcock2021in] affect ratings of valence and arousal.
-Although these studies are not always designed with MER applications in mind, their similar framework has enabled direct application [e.g., @chowdhury2021perceived].
+Although predictive modeling is not always an explicit goal of these studies, MER researchers have been able to adapt them in a MER framework [e.g., @chowdhury2021perceived].
 
@@
 The classification rates have similarly increased from 53% [@downie_music_2008] to 70% [@park2017representation] to 83% [@sarkar2020recognition] in the same period.
-Comparing these past efforts is challenging due to inconsistencies in metrics, modelling architectures, datasets, and model evaluation criteria.
+Comparing these past efforts, however, is challenging due to inconsistencies in metrics, modelling architectures, datasets, and model evaluation criteria.
 While we assume that overall accuracy has improved significantly over the past decade, predicting valence remains more challenging than predicting arousal.
@@
 Researchers have sought to enhance emotion prediction by identifying more relevant feature sets [@panda2020audio; @chowdhury2021perceived], integrating low-, mid-, and high-level features through multimodal data [@celma_foafing_2006], and leveraging neural networks to learn features directly from audio [@zhang2016br; @alvarez2023ri; @agarwal2021an].
-These approaches aim to overcome what has been described as a *glass ceiling* in MER research [@downie_music_2008] -- a limitation sometimes referred to as the *semantic gap* [@wiggins_semantic_2009].
-However, this ceiling may be better understood as an inherent measurement error arising from annotations, feature representations, and model limitations.
+These approaches aim to overcome what has been described as a _glass ceiling_ in MER research [@downie_music_2008] -- a limitation sometimes referred to as the _semantic gap_ [@wiggins_semantic_2009;@celma_foafing_2006].
+However, this prediction ceiling may be better understood as an inherent _measurement error_ arising from annotations, feature representations, and model limitations.
 While isolating the sources of these errors remains infeasible at this stage, comparing success rates across modeling techniques, feature set sizes, and other meaningful factors offers a step toward addressing this challenge.

### 2025-03-26 etc/heat_map_figure.R
feat(etc): update figure 5

@@ -45,7 +45,7 @@ tmp <- tmp |> group_by(
   mutate(
     study_n = length(citekey),
     stim_mid = median(stimulus_n),
-    label = paste0("n=",study_n,"\n(", stim_mid, ")")
+    label = paste0("n = ",study_n,"\n(", stim_mid, ")")
   )
 
 # Combine C and R studies, then facet based on type.
@@ -104,34 +104,39 @@ best_mods$dimension <- factor(
   labels = c("Valence", "Arousal", "Classification")
 )
 
-best_mods <- best_mods |> group_by(
-  dimension, 
-  model_class_id, 
-  model_id) |>
-  mutate(best_model = sort(best_model))
-
-
 best_mods <- best_mods |> 
-  group_by(dimension, model_id) |> 
-  mutate(
-    tally = cumsum(tally)
+  group_by(
+    dimension, 
+    model_class_id,
+    model_id
+    ) |> 
+  reframe(
+    tally = sum(tally),
+    label = paste("n =", max(tally)),
+    best_model = mean(best_model)
   )
 
 
 model_summary <- ggplot(best_mods, 
-       aes(x=tally, 
+       aes(x=dimension, 
            y=model_id, 
            fill=best_model,
        )) + 
   geom_tile(color = "black")+
+  geom_text(aes(label = label))+
   facet_grid(cols = vars(dimension), 
              rows = vars(model_class_id),
-             scales="free_y",
-             space = "free_y"
+             scales="free",
+             space = "free"
   )+
   scale_fill_distiller(palette = "Spectral")+
-  labs(x = "Frequency", y = "Algorithm", fill = "Accuracy")+
-  theme_classic()
+  labs(y = "Algorithm", fill = "Accuracy")+
+  theme_classic()+
+  theme(
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    axis.title.x = element_blank()
+  )
 
 fig5 <- ggarrange(
   heatmap_facets,
@@ -140,8 +145,8 @@ fig5 <- ggarrange(
   labels = c("(a)", "(b)")
 )
 
-
-# ggsave("manuscript/model-summary-fig.png",
-#        plot = fig5,
-#        width = 12, height = 7.5, units = "in")
+fig5
+ggsave("manuscript/model-summary-fig.png",
+       plot = fig5,
+       width = 12, height = 7.5, units = "in")
 

### 2025-03-28 manuscript/manuscript.qmd
Font edits to heatmap and MS edits to introduction

@@
 MER tasks commonly apply regression and classification techniques to diverse datasets with features drawn from both music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
-To facilitate model comparison, several databases have been shared publicly, including MediaEval [@soleymani2013], DEAM [@aljanaki2017developing], and AMG1608 [@chen2015amg1608].
+To facilitate model comparison, several databases have been shared publicly, including _MediaEval_ [@soleymani2013], _DEAM_ [@aljanaki2017developing], and _AMG1608_ [@chen2015amg1608].
 These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by a relatively large number of participants (either by experts, students, or crowdsourced workers).
-Many datasets include audio features analyzed with software toolboxes for audio analysis such as OpenSMILE [@eyben2010opensmile] and MIRToolbox [@lartillot2007matlab] -- enabling models that predict ratings using tens, or even hundreds, of audio features.
+Many datasets include audio features analyzed with software toolboxes for audio analysis such as _OpenSMILE_ [@eyben2010opensmile] and _MIRToolbox_ [@lartillot2007matlab] -- enabling models that predict ratings using tens, or even hundreds, of audio features.
 
-REVISE:
-Large datasets are ideal for generalizing predictions across diverse musical samples and are commonly employed in machine learning applications focused on maximizing accuracy of a MER system.
-
-IDEA: LARGE data requirements for machine-learning/deep learning, but annotating music is resource-intensive.
+Large datasets are needed to generalize predictions across diverse samples, especially for deep learning and complex machine-learning models that require extensive pre-training.
+However, the dataset sizes in MER tend to be modest in comparison, as direct annotation of music examples is resource-intensive.
+In contrast, datasets in the visual domain are often significantly larger (e.g., _EmoSet_ with 118,102 images and _AffectNet_ with 450,000, see @yang2023emoset;@mollahosseini2017affectnet).
+Some efforts have been made to scale up MER datasets by inferring emotions from tags (_MTG-Jamendo_ with 18,486 excerpts @bogdanov2019mtg and _Music4all_ with 109,269 excerpts @santana2020), but these have not found their way into standard emotion prediction or classification tasks yet.
 

### 2025-03-28 etc/heat_map_figure.R

@@ -66,13 +66,14 @@ heatmap_facets <- tmp |>
          )) +
   geom_raster()+
   facet_wrap(facets = vars(dimension))+
-  scale_fill_distiller(name = "Accuracy", palette = "Spectral")+
+  scale_fill_distiller(name = "Accuracy", palette = "Spectral",breaks=seq(0,1,by=.20),limits=c(0,1))+
 #  scale_fill_gradient2(name = "Accuracy")+
   scale_x_discrete(labels = c("LM", "NN", "Other"))+
   scale_y_discrete(labels = c("<30", "30-300", ">300"))+
-  geom_text(aes(label = label))+
+  geom_text(aes(label = label),family='Times')+
   labs(x = "Model class type", y = "Feature N category")+
-  theme_classic(base_size = 14,base_family = "Times")
+  theme_classic(base_size = 14, base_family = "Times")+
+  theme(legend.key.width= unit(2, 'cm'))
 
 
 # Model Types -----------------------------------------------------
@@ -116,37 +117,38 @@ best_mods <- best_mods |>
     best_model = mean(best_model)
   )
 
-
 model_summary <- ggplot(best_mods, 
        aes(x=dimension, 
            y=model_id, 
            fill=best_model,
        )) + 
   geom_tile(color = "black")+
-  geom_text(aes(label = label))+
+  geom_text(aes(label = label,family='Times'))+
   facet_grid(cols = vars(dimension), 
              rows = vars(model_class_id),
              scales="free",
              space = "free"
   )+
-  scale_fill_distiller(palette = "Spectral")+
+  scale_fill_distiller(palette = "Spectral",breaks=seq(0,1,by=.20),limits=c(0,1))+
   labs(y = "Algorithm", fill = "Accuracy")+
-  theme_classic()+
+  theme_classic(base_size = 14, base_family = "Times")+
   theme(
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-    axis.title.x = element_blank()
+    axis.title.x = element_blank(),
+    legend.key.width = unit(2, 'cm')
   )
 
 fig5 <- ggarrange(
   heatmap_facets,
   model_summary,
   common.legend = TRUE,
+  font.label = list(size = 14, color = "black", face = "bold", family = 'Times'),
   labels = c("(a)", "(b)")
 )
 
 fig5
 ggsave("manuscript/model-summary-fig.png",
        plot = fig5,
[…]

### 2025-04-02 manuscript/manuscript.qmd
manuscript: updates to introduction

@@
 Using the best-performing model from each study, we found that valence and arousal were predicted with reasonable accuracy (r = 0.67 and r = 0.81, respectively), while classification models achieved an accuracy of 0.87 as measured with Matthews correlation coefficient.
-Across modeling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed highest performance in classification tasks.
+Across modelling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed highest performance in classification tasks.
 We highlight key recommendations for future MER research, emphasizing the need for greater transparency, feature validation, and standardized reporting to improve comparability across studies.
@@
 
-Emotional engagement is a key reason why people engage with music in their every day activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions; @agres2021music].
+Emotional engagement is a key reason why people engage with music in their everyday activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions; @agres2021music].
 In recent years, significant advances have been made in music information retrieval, particularly in music emotion recognition (MER) tasks [@gomez2021; @panda2020audio].
-Improvements in available features, modeling techniques, and datasets have provided the field with opportunities to enhance the accuracy and reliability of predicting annotated emotions from audio.
-Over the past 25 years, numerous studies have established the types of emotions that listeners perceive and recognize in music.
+Improvements to modelling techniques, datasets, and available features have created new opportunities to improve the accuracy and reliability of MER systems developed to predict emotion labels or ratings in music using audio features.
+Over the past 25 years, these studies have established the types of emotions that listeners perceive and recognize in music.
 In the last 15 years, research has increasingly focused on tracing these recognized emotions back to specific musical components, such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013; @anderson2022ex; @grimaud_eerola_2022], acoustic features [@yang2008; @panda2013multi; @saari_et_al_2015; @eerola2011c; @panda2020audio], or emergent properties revealed through deep learning techniques [@er2019music; @sarkar2020recognition].
 
-However, there is no consensus on the extent to which emotions can be accurately recognized by computational models.
+Despite increased interest in MER studies, there is no consensus on the extent to which emotions can accurately be recognized by computational models.
 The current literature presents a diverse and mixed picture regarding the success of models in predicting emotions within the affective circumplex -- valence and arousal-- [@Russell1980] and in classifying distinct emotion categories [@fu2010survey].
@@
 
-Emotion has been widely discussed since the earliest artificial intelligence (AI) applications to music in the 1950s.
+Music's capacity to convey emotions has been widely discussed since the earliest artificial intelligence (AI) applications in the 1950s.
 Whereas early discourse largely focused on generative composition using computers [@zaripov1969], attention later shifted to creating methods to predict emotion using music's structural cues.
@@
 These developments would set the stage for early work in music emotion recognition (MER).
-@katayose_sentiment_1988 conducted the first study of this nature, creating an algorithm that associated emotions with analyzed chords to generate descriptions like "there is hopeful mood on chord from 69 to 97 \[*sic*\]." [@katayose_sentiment_1988, p.
+@katayose_sentiment_1988 conducted the first study of this nature, creating an algorithm that associated emotions with analyzed chords to generate descriptions like "there is \[a\] hopeful mood on chord\[s\] 69 to 97." [@katayose_sentiment_1988, p.
 1087].
@@
 1], the Music Information Retrieval EXchange (MIREX) introduced Audio Mood Classification (AMC) to their rotation of tasks in 2007.
-In the first year, nine systems classified mood labels in a common data set, reaching 52.65% accuracy (SD = 11.19%).
-These events, along with growing interest in the burgeoning field of affective computing, would lead to an explosion of interest in MER research.
+In the first year, nine systems classified mood labels in a common data set, reaching 52.65% in classification accuracy (SD = 11.19%).
+These annual events, along with growing interest in the burgeoning field of affective computing [@picard_affective_1997], would lead to an explosion of interest in MER research.
 
@@
 In the tenth annual AMC task, the highest performing model reached 69.83% accuracy [@park2017representation].
-In parallel, other researchers began assessing MER as a regression task.
-The first study to popularize this approach predicted valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) in 195 Chinese pop songs [@yang2008] using audio-extracted features.
-The regression model predicted arousal with 62% accuracy, but only achieved 28% accuracy for valence.
+In parallel, research groups began independently evaluating MER using regression algorithms.
+The first study to popularize this approach predicted valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) in 195 Chinese pop songs [@yang2008] using audio-extracted features represented in 114 dimensions.
+Applying support vector regression, the study achieved 58.3% accuracy in predicting arousal and 28.1% in predicting valence.
 This difference in prediction accuracy between dimensions has reappeared in several subsequent studies [e.g., @bai2016dimensional; @coutinho2013psychoacoustic], with some research suggesting this challenge reflects fewer well-established predictors and more individual differences for valence than arousal [@yang2007music; @eerola2011c].
@@
 
-Across regression and classification paradigms, a wide range of models have been employed, ranging from linear regression models [@saizclar2022pr; @griffiths2021am; @yang2008] to deep neural networks [@orjesek2022en; @hizlisoy2021mu].
-In classification tasks, early work has commonly employed Gaussian mixture models [@lu_automatic_2005; @liu_automatic_2003] and support vector machines [@mandel2007labrosa; @lin2009eeg; @tzanetakis2007marsyas], whereas convolutional, recurrent, and fully-connected neural networks have become increasingly popular in recent years [@grekow2021music; @song2018audio; @coutinho2017sh].
-In regression tasks, a wide range of algorithms have been tested, including partial least squares [@gingras2014be; @wang2021ac], support vector machines [@grekow2018au; @hu2017cr; @agarwal2021an], random forests [@beveridge2018po; @xu2021us], and convolutional neural networks [@orjesek2022en].
+Across regression and classification paradigms, a wide range of models have been employed, ranging from multiple linear regression (MLR) [@saizclar2022pr; @griffiths2021am; @yang2008] to deep neural networks [@orjesek2022en; @hizlisoy2021mu].
+In classification tasks, early studies commonly employed Gaussian mixture models [@lu_automatic_2005; @liu_automatic_2003] and support vector machines [@mandel2007labrosa; @lin2009eeg; @tzanetakis2007marsyas], whereas convolutional, recurrent, and fully-connected neural networks are increasingly popular in recent years [@grekow2021music; @song2018audio; @coutinho2017sh].
+In regression tasks, a wide range of algorithms have been tested, including partial least squares (PLS) [@gingras2014be; @wang2021ac], support vector machines (SVMs) [@grekow2018au; @hu2017cr; @agarwal2021an], random forests (RFs) [@beveridge2018po; @xu2021us], and convolutional neural networks [@orjesek2022en].
 
@@
 
-MER tasks commonly apply regression and classification techniques to diverse datasets with features drawn from both music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
-To facilitate model comparison, several databases have been shared publicly, including _MediaEval_ [@soleymani2013], _DEAM_ [@aljanaki2017developing], and _AMG1608_ [@chen2015amg1608].
-These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by a relatively large number of participants (either by experts, students, or crowdsourced workers).
-Many datasets include audio features analyzed with software toolboxes for audio analysis such as _OpenSMILE_ [@eyben2010opensmile] and _MIRToolbox_ [@lartillot2007matlab] -- enabling models that predict ratings using tens, or even hundreds, of audio features.
+MER studies apply regression and classification techniques to predict emotion in diverse datasets, using features derived from both music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
+To facilitate model comparison, several databases have been shared publicly, including *MediaEval* [@soleymani2013], *DEAM* [@aljanaki2017developing], and *AMG1608* [@chen2015amg1608].
+These datasets predominately use Western pop music, are moderate in size (containing from 744 to 1802 music excerpts) and have been manually annotated by a variable numbers of participants (either by experts, students, or crowdsourced workers).
+Several publicly available datasets include features analyzed using audio software suites such as *OpenSMILE* [@eyben2010opensmile] and *MIRToolbox* [@lartillot2007matlab] -- enabling predictions from tens, or even hundreds, of audio features.
 
@@
 However, the dataset sizes in MER tend to be modest in comparison, as direct annotation of music examples is resource-intensive.
-In contrast, datasets in the visual domain are often significantly larger (e.g., _EmoSet_ with 118,102 images and _AffectNet_ with 450,000, see @yang2023emoset;@mollahosseini2017affectnet).
-Some efforts have been made to scale up MER datasets by inferring emotions from tags (_MTG-Jamendo_ with 18,486 excerpts @bogdanov2019mtg and _Music4all_ with 109,269 excerpts @santana2020), but these have not found their way into standard emotion prediction or classification tasks yet.
+In contrast, datasets in the visual domain are often significantly larger (e.g., *EmoSet* with 118,102 images and *AffectNet* with 450,000, see @yang2023emoset;@mollahosseini2017affectnet).
+Some efforts have been made to scale up MER datasets by inferring emotions from tags (*MTG-Jamendo* with 18,486 excerpts @bogdanov2019mtg and *Music4all* with 109,269 excerpts @santana2020), but these have not found their way into standard emotion prediction or classification tasks yet.
 
-Although training MER systems with a wide range of stimuli and features can be useful for generalizable and accurate modeling, small datasets can be more appropriate in explorations that require precise control of stimuli or analyzed features to understand a model's performance.
-For example,  @griffiths2021am evaluated a MER model's performance when predicting 20 tracks different genres, validating the model on another 40 tracks.
-@saizclar2022pr evaluated how onset curves (changes in the energy of a note starting from its onset) can be incorporated into a predictive framework using 40 short (8-12s) piano excerpts.
+Although training MER systems with a wide range of stimuli and features can be useful for generalizable and accurate modelling, smaller datasets can be more appropriate in studies requiring precise control over stimulus parameters.
+For example, @griffiths2021am tested multi-genre MER using multiple linear regression to predict emotion in 20 tracks from different genres (validating the model using a separate set of 40 tracks).
+@saizclar2022pr evaluated how 22 variables derived from an onset curves (changes in the energy of a note starting from its onset) can be used to predict valence and activation in 40 short (8-12s) piano excerpts.
 Smaller datasets are also useful in studies attempting to explain how stimulus qualities such as amplitude normalization [@gingras2014be] or different performers' interpretations [@battcock2021in] affect ratings of valence and arousal.
-Although predictive modeling is not always an explicit goal of these studies, MER researchers have been able to adapt them in a MER framework [e.g., @chowdhury2021perceived].
+Although predictive modelling is not always an explicit goal of these studies, they can be adapted to fit into a MER framework.
+For example, @chowdhury2021perceived adopted data from a previous psychological study of piano performances to compare sets of features analyzed from audio files, musical scores, or deep neural network feature extractors.
 
@@
 - Due to wide range of approaches, difficult to evaluate how successful attempts to raise glass ceiling have been
-- How do modeling techniques, and the number of features used affect performance? Which combinations perform best?
+- How do modelling techniques, and the number of features used affect performance? Which combinations perform best?
 
@@
 
-Prediction accuracy in MER tasks has improved as datasets and models have become more sophisticated; The regression models for arousal/valence was 58%/28% in 2008 [@yang2008], 70%/26% in 2010 [@huq2010automated], to 67%/46% in 2021 [@yang2021an].
-The classification rates have similarly increased from 53% [@downie_music_2008] to 70% [@park2017representation] to 83% [@sarkar2020recognition] in the same period.
-Comparing these past efforts, however, is challenging due to inconsistencies in metrics, modelling architectures, datasets, and model evaluation criteria.
-While we assume that overall accuracy has improved significantly over the past decade, predicting valence remains more challenging than predicting arousal.
+Predictive accuracy in MER tasks has improved as datasets and models have become more sophisticated; Regression models for arousal/valence have been reported to peak at 58%/28% accuracy in 2008 [@yang2008], 70%/26% in 2010 [@huq2010automated], and 67%/46% in 2021 [@yang2021an].
+In the same period, classification rates have increased from 53% [@downie_music_2008] to 70% [@park2017representation] to 83% [@sarkar2020recognition].
+Comparing these past efforts, however, is challenging due to inconsistencies between studies in metrics, modelling architectures, datasets, and evaluation criteria.
+Although we assume that overall accuracy has improved significantly over the past decade, valence remains more challenging to predict than arousal.
 
-Researchers have sought to enhance emotion prediction by identifying more relevant feature sets [@panda2020audio; @chowdhury2021perceived], integrating low-, mid-, and high-level features through multimodal data [@celma_foafing_2006], and leveraging neural networks to learn features directly from audio [@zhang2016br; @alvarez2023ri; @agarwal2021an].
-These approaches aim to overcome what has been described as a _glass ceiling_ in MER research [@downie_music_2008] -- a limitation sometimes referred to as the _semantic gap_ [@wiggins_semantic_2009;@celma_foafing_2006].
-However, this prediction ceiling may be better understood as an inherent _measurement error_ arising from annotations, feature representations, and model limitations.
-While isolating the sources of these errors remains infeasible at this stage, comparing success rates across modeling techniques, feature set sizes, and other meaningful factors offers a step toward addressing this challenge.
+Recent studies have sought to enhance emotion prediction by identifying more relevant feature sets [@panda2020audio; @chowdhury2021perceived], integrating low-, mid-, and high-level features through multimodal data [@celma_foafing_2006], and leveraging neural networks to learn features directly from audio [@zhang2016br; @alvarez2023ri; @agarwal2021an].
+These approaches aim to overcome ceiling effects in predictive accuracy [@downie_music_2008], which some scholars refer to as a *semantic gap* [@wiggins_semantic_2009; @celma_foafing_2006].
+However, this prediction ceiling may be better understood as an inherent *measurement error* arising from annotations, feature representations, and model limitations.
+Although isolating the sources of these errors remains infeasible at this stage, comparing success rates across modelling techniques, feature set sizes, and other meaningful factors offers a step toward addressing this challenge.
 To date, however, no study has systematically compared the results of the diverse approaches employed in MER research.
@@
 Our aim is to evaluate the predictive accuracy of two types emotional expression in music: (a) models that predict track-specific coordinates in affective circumplex space (valence and arousal), and (b) models that classify discrete emotion categories.
-We focus on recent studies to identify the overall success rate in MER tasks and the key factors such as modeling techniques, the number of features, or the inferential goal (explanation vs prediction) that might contribute to the prediction accuracy of the models.
-To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years.
-Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model.
-In terms of the modelling techniques and the number of features, a reasonable hypothesis is that advanced techniques (e.g., neural networks) and larger amount of features will lead to higher prediction rates than conventional techniques (e.g., logistic regression or linear regression) and smaller amount of features.
-However, this relationship might not be as straightforward as this due to the demands complex models place on dataset size [@alwosheel2018;@sun2017revisiting].
+We focus on recent studies to identify the overall success rate in MER tasks and the key factors such as modelling techniques, the number of features, or the inferential goal (explanation vs prediction) that might contribute to the prediction accuracy of the models.
+To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years, focusing on subgroup analyses capturing these differences (model type, feature N, journal type).
+Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model [@yang2018review].
+\
+<!-- yang et al. attribute this to fewer salient features, and individual differences, which I think is consistent with these descriptions -->\
+In terms of the modelling techniques and the number of features, a reasonable hypothesis is that advanced techniques (e.g., neural networks) and larger amount of features will lead to higher prediction rates than conventional techniques (e.g., logistic regression or linear regression) and smaller feature sets.
+However, this relationship might not be as straightforward as this due to the demands complex models place on dataset size \[@alwosheel2018; @sun2017revisiting\].
 
@@
 To capture key details of each study, we added extra fields to BibTeX entries for each study.
-Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM),[^2] Linear Methods (LM), Tree-based Methods (TM), KS, Add.
+Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM),[^1] Linear Methods (LM), Tree-based Methods (TM), KS, Add.
 and KNN Methods (KM) -- validation procedure and output measures.
@@
 
-[^2]: @chen2017co was the only study of those included to use Gaussian Mixture Models.
+[^1]: @chen2017co was the only study of those included to use Gaussian Mixture Models.
 We decided to group this with Support Vector Machines as they have been reported to perform similarly on mid-sized data sets [@mashao2003co].
@@
 |   | Regression | Classification | Total |
-|:-----------|:----------------------------|:--------------------------|:------|
+|:-------------|:----------------------|:--------------------|:-------------|
 | Study N | 22 | 12 | 34 |
@@
 <!-- numbers in the text updated up to here, CA 20/2/2025 -->
+
 <!-- I've removed the reference to the funnel plot, TE 19/3/2025 -->
@@
 To gain insights into the factors contributing to the wide range of model success, we explored several ways of splitting the data.
-Table 2 presents two key splits: one based on the number of features used, which we hypothesized might influence model performance, and another based on the modeling techniques employed.
+Table 2 presents two key splits: one based on the number of features used, which we hypothesized might influence model performance, and another based on the modelling techniques employed.
 In terms of feature sets, we categorized them into three groups: few features (\<30), a large number of features (30–300), and massive feature sets (300+).
@@
 
-When analyzing the studies across the four modeling techniques used, the prediction do differ significantly (*Q*(3) = 12.43, *p* = .0061).
+When analyzing the studies across the four modelling techniques used, the prediction do differ significantly (*Q*(3) = 12.43, *p* = .0061).
 Notably, linear models (LM) and neural networks (NN) were the most common, with 9 and 6 studies, respectively, allowing for more confident interpretations.
@@
 <!-- numbers in the text updated up to here, CA 20/2/2025 -->
+
 <!-- DISCUSS: we don't report journal type of explain/predict differences, although we do some of these in arousal, TE 19/3/2025 -->
@@
 Across studies, most operationalizations corresponded to either affective dimensions of the circumplex model or discrete emotion labels mapping to those dimensions [e.g., happy, sad, nervous, and calm and similar variants used in @agarwal2021an; @alvarez2023ri; @yeh2014po].
-Despite common adoption of the circumplex quadrants, studies differed in modeling decisions: one study predicted quadrants in a multi-class problem [@panda2020no], whereas another predicted them in a series of binary classification tasks [@bhuvanakumar2023em].
+Despite common adoption of the circumplex quadrants, studies differed in modelling decisions: one study predicted quadrants in a multi-class problem [@panda2020no], whereas another predicted them in a series of binary classification tasks [@bhuvanakumar2023em].
 Others predicted valence and arousal in separate tasks [@hu2022de; @zhang2016br], and some of the models analyzed only predicted arousal [e.g., all models in @zhang2017fe; the CART model in @zhang2016br].
@@
 In contrast, neural networks performed most accurately in classification studies ($MCC$ = 0.93), followed by SVMs ($MCC$ = 0.87) and tree-based models ($MCC$ = 0.85).
-Despite the high overall success of the research in this topic, the models exhibited several differences relating to (i) the scale and quantity of data sets employed, (ii) feature extraction methods, (iii) the number and types of features and reduction methods used, (iv) the actual modeling architecture, and (v) how model outcomes are cross-validated.
+Despite the high overall success of the research in this topic, the models exhibited several differences relating to (i) the scale and quantity of data sets employed, (ii) feature extraction methods, (iii) the number and types of features and reduction methods used, (iv) the actual modelling architecture, and (v) how model outcomes are cross-validated.
 
@@
 The results of the meta-analysis offer several important insights.
-First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from *r* = 0.51 to 0.67.[^3] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
+First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from *r* = 0.51 to 0.67.[^2] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
 For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is generally notably better, here $MCC$ = 0.87, albeit the differences in metrics.
 
-[^3]: Values reported as $R^2$ in original study.
+[^2]: Values reported as $R^2$ in original study.
 
@@
 
-One of the crucial aspects of modeling is the choice of features, their quantity, and their validation.
+One of the crucial aspects of modelling is the choice of features, their quantity, and their validation.
 In the present materials, we observe a continuum defined by two extremes: one approach relies on domain knowledge, starting with a limited number of features that are assumed to be perceptually relevant, while the other employs a large number of features, allowing the model to determine which are most relevant for prediction.
@@
 We believe that the relatively modest size of datasets available so far has prevented deep learning approaches from fully leveraging their potential to learn generalizable patterns in the data .
-For reference, the size of the datasets in MER are currently comparable to dataset sizes for modeling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
+For reference, the size of the datasets in MER are currently comparable to dataset sizes for modelling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
 However, annotated datasets for visual scenes and objects tend to be much larger, often exceeding 100,000 annotated examples [@deng2009imagenet; @krishna2017visual].
-Datasets of these magnitudes seem to be required for appropriate utilisation of deep learning algorithms [@alwosheel2018;@sun2017revisiting], which may explain the modest results observed in the music emotion recognition studies.
+Datasets of these magnitudes seem to be required for appropriate utilisation of deep learning algorithms [@alwosheel2018; @sun2017revisiting], which may explain the modest results observed in the music emotion recognition studies.
 

### 2025-04-02 manuscript/manuscript.qmd
added interpretation of the heatmap

@@
 
-To assess how the use of different model types affected performance, we prepared heatmap visualizations depicting differences in success across feature *n* categories.
+To assess how the use of different model types affected performance, we prepared heatmap visualizations depicting differences in success across feature *n* categories and algorithms.
 We collapsed SVM and Tree-Based categories due to their low representation in the model summary.
@@
 Overall, studies using smaller feature sets tend to perform best, whereas the best model type largely depends on the nature of the prediction task.
+For valence and arousal, linear models perform better than other model types, whereas for emotion classification, neural networks show the best overall performance.
+The overall pattern aligns with the analyses of the splits reported earlier concerning model types and feature counts, but the visualization also highlights concurrent information about the feature n, model types, study counts, and the average number of stimuli within each combination.
+For instance, studies with the lowest number of features (<30) also tend to have the highest mean number of stimuli (M = 749.5), while the poorest-performing feature count range (30–300) corresponds to the lowest mean number of stimuli (M = 522.5).
+It is also reassuring to observe that studies utilizing neural networks and other model types tend to use a higher number of features and stimuli than those employing linear models, as this reflects the capabilities and internal training requirements built into these models.
 

### 2025-04-02 manuscript/manuscript.qmd
added revisions to conclusions

@@
 Emotional engagement is a key reason why people engage with music in their everyday activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions; @agres2021music].
-In recent years, significant advances have been made in music information retrieval, particularly in music emotion recognition (MER) tasks [@gomez2021; @panda2020audio].
+In recent years, significant advances have been made in music information retrieval (MIR), particularly in music emotion recognition (MER) tasks [@gomez2021; @panda2020audio].
+Music Emotion Recognition (MER) is an interdisciplinary field that combines computer science, psychology, and musicology to identify the emotions conveyed by music.
+Research in this area involves developing computational models capable of recognizing emotions from musical content.
+The emotional attributions of music are based on various theoretical frameworks for emotion and require annotated datasets to build and train these models.
 Improvements to modelling techniques, datasets, and available features have created new opportunities to improve the accuracy and reliability of MER systems developed to predict emotion labels or ratings in music using audio features.
@@
 
+<!-- added a MER definition to 2nd sentence above -->
+
 Despite increased interest in MER studies, there is no consensus on the extent to which emotions can accurately be recognized by computational models.
-The current literature presents a diverse and mixed picture regarding the success of models in predicting emotions within the affective circumplex -- valence and arousal-- [@Russell1980] and in classifying distinct emotion categories [@fu2010survey].
+The current literature presents a diverse and mixed picture regarding the success of models in predicting emotions within the affective circumplex -- valence and arousal-- [@yang2011] and in classifying distinct emotion categories [@fu2010survey].
 
@@
 
+<!-- DISCUSS the interpretation above -->
+
 ![Heatmaps summarizing models.
@@
 
-<!-- first para is your text from ICMPC paper -->
-
 Research on Music Emotion Recognition has steadily increased in popularity since the early 2000s, with technological advancements facilitating sharing of data sets, analysis tools, and music stimuli.
-Public forums like the Music Information Retrieval Exchange (MIREX) have facilitated collaborations between computer scientists, musicologists, and psychologists alike—spurring improvements in performance.
-Despite increasing complexity in the types of models and data sets used, no extant study has evaluated the relative merits of the tools, stimuli, and feature sets employed in MER studies.
-The present study offers the first meta-analysis of music emotion recognition.
+Public forums like the Music Information Retrieval Exchange (MIREX) have facilitated collaborations between computer scientists, musicologists, and psychologists alike -- spurring improvements in performance.
+Despite the increasing complexity of models and datasets, no existing study has rigorously compared the overall success of Music Emotion Recognition research using standardized metrics, nor has there been an analysis of the relative merits of the model techniques and feature sets employed.
+This study presents the first meta-analysis of music emotion recognition.
 
@@
 We surmise that this might relate to disciplinary differences.
-For example, the smaller datasets often come from music psychology studies, which put a premium on data quality (quality control of the ground-truth data and features) rather than on data size and model techniques.
-Successful quality control is thought to decrease random errors inherent in human judgments.
+For example, the smaller datasets often come from music psychology studies, which put a premium on data quality (quality control of the ground-truth data and features) rather than on dataset size and model techniques.
 This argument is largely consistent with the analysis of the studies divided across journal types (psychology vs.
-engineering).
+engineering), even though the pattern is not well-defined.
+
+<!-- minor improvements to the ending of the paragraph above -->
 
 Third, there is little work on the relevance of the features and how these impact the accuracy of the models.
-Unfortunately, in many cases, it is impossible to attribute the sources of error to features (as opposed to target emotions obtained from participants or from the modelling architecture, cross-validation, or the size of data), as the studies so far have not compared the feature sets systematically, nor has a comparison of the datasets with identical features has been carried out.
+Unfortunately, in many cases, it is impossible to attribute the sources of error to features (as opposed to target emotions obtained from participants or from the modelling architecture, cross-validation, or the size of data), as the studies so far have not compared the feature sets systematically, nor has a comparison of the datasets with identical features has been carried out [@panda2020audio].
 In the future, it would be advantageous to systematically assess these sources of error in MER studies to allow us to focus on where and how significant improvements can be made.
+
+<!-- Added at least a reference to Pandas work on survey of features to para above -->
 
@@
 The modelling process should include a description of cross-validation, feature extraction technique, feature reduction (if used), and actual accuracy measures.
-We would recommend future studies to use Matthews correlation coefficient ($MCC$) for classification studies as currently there are numerous metrics (*F~1~*, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
+We would recommend future studies to use *Matthews correlation coefficient* ($MCC$) for classification studies, as currently there are numerous metrics (*F~1~*, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
 The situation for regression studies tends to be less volatile, but model accuracy may be reported with error measures (Mean Squared Error, Root Mean Squared Error, or Mean Absolute Error, or $MSE$, $RMSE$, $MAE$), which cannot be converted to relative measure such as $R^2$ without knowing the variance of the data.
+Again, we would recommend utilising $R^2$ due it being a relative measure and scale invarant to allow comparison across models, datasets, and studies.
+
+<!-- added a recommendation for regression study outputs as well to para above.
+We could add a mention about R2 adjusted to penalise complex models, but there are other ways to punish for model complexity as well.
+-->
 
@@
 If a study relies on published datasets, as most do, sharing the actual model (as code/notebooks) and features would allow for a more direct comparison of model techniques for the same dataset.
-Also, not all datasets are shared [@akiki2021; @santana2020; @hizlisoy2021mu; @zhang2017fe], or at least the sharing is only done partially.
+Also, not all datasets are shared [@akiki2021; @santana2020; @hizlisoy2021mu; @zhang2017fe].
 Standardizing reporting of datasets to include subsections explaining detailed information about stimuli (including genre, duration, sampling rate, and encoding format), features (types, extraction/analysis software, quantity of features, transformations, reduction methods), and models (types, tuning parameters, cross-validation) will enable more accurate comparisons between studies.
 The reporting in @grekow2018au serves as a useful example by providing enough detail in these areas to facilitate reproducibility.
-Although copyright restrictions may limit the sharing of some datasets, features and examples should be made available.
+Although copyright restrictions may limit the sharing of some datasets, features and examples should be made available through reliable external repositories (e.g., [Zenodo](https://zenodo.org/), [Open Science Framework](https://osf.io/), or [Kaggle datasets](https://osf.io/)).
+
+<!-- Added some examples of where the features/models can be shared -->
 

### 2025-04-02 manuscript/manuscript.qmd
added revisions to conclusions

@@
 The search yielded studies of variable (and occasionally questionable) quality.
-To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](include%20approx%20#%20for%20each?%20This%20would%20be%20good%20since%20the%20rest%20of%20this%20para%20already%20mentions%20counts.%20If%20this%20take%20a%20long%20time,%20we%20could%20save%20this%20for%20an%20additional%20analysis).
+To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](xxx).
 Finally, we excluded studies published in journals of questionable relevance/quality, (e.g., *Mathematical Problems in Engineering* ceased publication following 17 retractions published between July and September 2024).

### 2025-04-07 index.qmd
added links to data and code repositories, manuscript improvements

@@
 What is the evidence in the published literature for explaining what emotions the listeners can perceive in music when the source consists of audio examples.
-To what degree the results are dependent on the actual models, emotions, musical/acoustic features, or musical materials or participants?
+To what degree the results are dependent on the actual models, type of emotions predicted, musical/acoustic features, or musical materials?
 
 To obtain answers to these questions, we have set out to record and analyse the current state of the art from the literature using a meta-analysis paradigm.
-We focus on Music Emotion Recognition and hence the acronym `metaMER`.
+We focus on *Music Emotion Recognition* (MER) and hence the acronym `metaMER`.
 
@@
 The study report is available [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.
+
+### Common datasets
+
+Commonly used datasets [manuscript/datasets.qmd](manuscript/datasets.qmd).

### 2025-04-07 manuscript/datasets.qmd
added links to data and code repositories, manuscript improvements

--- 2025-02-18 manuscript/_datasets.qmd
@@
-```{r}
-#| label: datasets
-```
+---
+title             : "Datasets"
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+lineno            : no
+mask              : no
+csl: apa7.csl
+#class             : "man"
+#output            : papaja::apa6_pdf
+bibliography      : references.bib
+---
+
+The most frequently used 3 datasets are MediaEval [@soleymani2013], DEAM [@aljanaki2017developing], and AMG1608 [@chen2015amg1608].
+These datasets represent Western pop music, are moderate in terms of the size (containing from 744 to 1802 music excerpts) and have been manually annotated by relative large number of participants (either by experts, students, or crowdsourced workers).
+Two of the most popular datasets offer a large number (260 to 6669) features extracted with OpenSMILE [@eyben2010opensmile].
+Looking at the datasets more broadly, the diversity in the size and the features of the datasets is notable.
+Only two feature extraction tools are used across multiple datasets (OpenSMILE @eyben2010opensmile and MIR Toolbox, @lartillot2007matlab).
+However, despite this diversity, there does not seem to be a direct link between the model success rates and the features themselves, or at least separating the features from variation created by the dataset size, annotation accuracy and genre is not possible.
 

### 2025-04-07 manuscript/manuscript.qmd
added links to data and code repositories, manuscript improvements

@@
 
-In the search stage, we used three databases, *Web of Science*, *Scopus*, and *Open Alex* to identify journal articles published between 2014 and 2024 containing keywords/title `valence OR arousal OR classi* OR categor* OR algorithm AND music AND emotion AND recognition` (see specific search strings for each database in [SI](http://)).
+In the search stage, we used three databases, *Web of Science*, *Scopus*, and *Open Alex* to identify journal articles published between 2014 and 2024 containing keywords/title `valence OR arousal OR classi* OR categor* OR algorithm AND music AND emotion AND recognition` (see specific search strings for each database in [Study Data and Code Repository - Search Syntax](https://tuomaseerola.github.io/metaMER/studies/search_syntax.html)).
 All searches were done in May 2024.
@@
 The initial search yielded 553 potential studies after excluding duplicate entries.
-We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $r$ or $MCC$ values see [SI](http://) for a breakdown).
+We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $r$ or $MCC$ values see [Study Data and Code Repository - Extraction Details](https://tuomaseerola.github.io/metaMER/studies/extraction_details.html) for a breakdown).
 After the screening stage, we defined a set of entities to extract characterising (i) music (genre, stimulus number \[N\], duration), (ii) features extracted (number, type, source, defined by [@panda2020audio]), (iii) model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), (iv) model complexity (i.e., approximate number of features used to predict ratings), and (v) type of model cross-validation.
+Summary of the common datasets used in the studies in available at [Study Data and Code Repository - Datasets](https://tuomaseerola.github.io/metaMER/manuscript/datasets.html).
 
@@
 The search yielded studies of variable (and occasionally questionable) quality.
-To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](xxx).
+To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture [Study Data and Code Repository - Comparison](https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html).
 Finally, we excluded studies published in journals of questionable relevance/quality, (e.g., *Mathematical Problems in Engineering* ceased publication following 17 retractions published between July and September 2024).
@@
 Additionally, we included study results using executable *R* code containing custom functions for meta-analysis.
-For complete details about our encoding procedure, see `studies/extraction_details.qmd` .
+For complete details about our encoding procedure, see [Study Data and Code Repository - Extraction Details](https://tuomaseerola.github.io/metaMER/studies/extraction_details.html).
 
@@
 
-First we describe the overall pattern of data (regression vs. classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
+First we describe the overall pattern of data (regression vs.
+classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
+The analysis code is available at [Study Data and Code Repository - Analysis](https://tuomaseerola.github.io/metaMER/analysis/analysis.html).
 
@@
 
-These comparisons of sub-groupings are also influenced by other factors, such as the type of journal (psychology vs engineering) or whether the objective is to explain or predict emotions.
-Although the sub-groupings result in an uneven distribution of studies and observations, they still offer valuable insights.
-Despite these caveats, the two main sub-groupings portrayed in Table 2 enable us to identify valuable differences related to model success across the studies.
-
+These comparisons of sub-groupings may also be influenced by other factors, such as the aim of the study (i.e.
+whether it focused on prediction or explanation).
+To address this, we used the type of journal in which each study was published as a proxy indicator, classifying journals as either psychology or engineering.
+Of the 22 regression studies, 13 were published in engineering journals, yielding an average correlation of *r* = 0.656 (9% CI: 0.505–0.769).
+Studies published in psychology journals (9) showed a similar overall correlation of *r* = 0.688 (95% CI: 0.468–0.827).
+No significant difference in model accuracy was observed between the two types of study aims, *Q*(1) = 0.10, *p* = 0.748.
+More broadly, while the sub-groupings based on modelling techniques result in an uneven distribution of studies and observations, the two main sub-groupings presented in Table 2 highlight valuable differences in model performance across the studies.
 <!-- numbers in the text updated up to here, CA 20/2/2025 -->
 
-<!-- DISCUSS: we don't report journal type of explain/predict differences, although we do some of these in arousal, TE 19/3/2025 -->
+<!-- DISCUSS: we don't report journal type of explain/predict differences, although we do some of these in arousal, TE 19/3/2025: Now added! -->
 

### 2025-04-08 manuscript/manuscript.qmd
minor edits to text
fixed an error in sentence that should say all classification studies were published in engineering journals

@@
 To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years, focusing on subgroup analyses capturing these differences (model type, feature N, journal type).
-Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model [@yang2018review].
-\
+Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model [@yang2018review].\
 <!-- yang et al. attribute this to fewer salient features, and individual differences, which I think is consistent with these descriptions -->\
 In terms of the modelling techniques and the number of features, a reasonable hypothesis is that advanced techniques (e.g., neural networks) and larger amount of features will lead to higher prediction rates than conventional techniques (e.g., logistic regression or linear regression) and smaller feature sets.
-However, this relationship might not be as straightforward as this due to the demands complex models place on dataset size \[@alwosheel2018; @sun2017revisiting\].
+However, this relationship might not be as straightforward as this due to the demands complex models place on dataset size [@alwosheel2018; @sun2017revisiting].
 
@@
 |   | Regression | Classification | Total |
-|:-------------|:----------------------|:--------------------|:-------------|
+|:---------------|:--------------------|:------------------|:---------------|
 | Study N | 22 | 12 | 34 |
@@
 
-However, the indicators of heterogeneity are again high ($\tau^2$ = 0.141 and $I^2$=97.9%), which suggests that summary may be misleading.
+For arousal, the indicators of heterogeneity are again high ($\tau^2$ = 0.141 and $I^2$=97.9%), which suggests that summary may be misleading.
 However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.789 95%CI -4.87-6.45, *t* = 0.273, *p* = 0.788).
-If we remove the studies that are outside the 95%CI in heterogeneity, leaves this 13 studies in the summary that has *r* = 0.826 (95%CI 0.806-0.845) with $\tau^2$ = 0.0042 and $I^2$ = 76.8%.
-In other words, no material difference to the results obtained with all 22 studies.
+If we remove the studies that are outside the 95%CI in heterogeneity, this leaves 13 studies in the summary where *r* = 0.826 (95%CI 0.806-0.845), $\tau^2$ = 0.0042 and $I^2$ = 76.8%.
+In other words, we observed no material difference to the results obtained with all 22 studies.
 
@@
 The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (*Q*(2) = 5.20, *p* = .074) despite the differing means (*r* = 0.885 for studies with less than 30 features, *r* = 0.735 for 30 to 300 features, and *r* = 0.804 for studies utilising over 300 features).
-The differences in the techniques, however, does show statistically significant variance between subgroups (*Q*(3) = 10.83, *p* = .0127).
+The differences in the techniques, however, show statistically significant variance between subgroups (*Q*(3) = 10.83, *p* = .0127).
 The Neural Nets (NN) achieve poor prediction of arousal (*r* = 0.660) in comparison to other techniques.
@@
 Accounting for outliers among the classifications results removes 6 studies, affecting both performance ($MCC$ = 0.8941, 95%CI: 0.8282-0.9356) and heterogeneity scores ($\tau^2$ = 0.0569, $I^2$ = 97.7%).
-However, Eggers' test does not indicate an asymmetric funnel plot ($\beta$ = -19.769, 95%CI: -39.29--0.24).
+However, we observed no significant issues in analysis for asymmetry ($\beta$ = -19.769, 95%CI: -39.29--0.24).
 After aggregating across dimensions, some of the best models included only classified arousal [@zhang2016br; @zhang2017fe].
@@
 multi-class models (*Q*(1) = 0.03, *p* = 0.8694) differed significantly.
-Unlike regression, no classification studies were published in engineering journals.
+All classification studies were published in engineering journals.
 
@@
 The overall pattern aligns with the analyses of the splits reported earlier concerning model types and feature counts, but the visualization also highlights concurrent information about the feature n, model types, study counts, and the average number of stimuli within each combination.
-For instance, studies with the lowest number of features (<30) also tend to have the highest mean number of stimuli (M = 749.5), while the poorest-performing feature count range (30–300) corresponds to the lowest mean number of stimuli (M = 522.5).
+For instance, studies with the lowest number of features (\<30) also tend to have the highest mean number of stimuli (M = 749.5), while the poorest-performing feature count range (30–300) corresponds to the lowest mean number of stimuli (M = 522.5).
 It is also reassuring to observe that studies utilizing neural networks and other model types tend to use a higher number of features and stimuli than those employing linear models, as this reflects the capabilities and internal training requirements built into these models.

### 2025-04-08 manuscript/manuscript.qmd
add intro section on explanatory and predictive frameworks

@@
 
-Although training MER systems with a wide range of stimuli and features can be useful for generalizable and accurate modelling, smaller datasets can be more appropriate in studies requiring precise control over stimulus parameters.
-For example, @griffiths2021am tested multi-genre MER using multiple linear regression to predict emotion in 20 tracks from different genres (validating the model using a separate set of 40 tracks).
-@saizclar2022pr evaluated how 22 variables derived from an onset curves (changes in the energy of a note starting from its onset) can be used to predict valence and activation in 40 short (8-12s) piano excerpts.
-Smaller datasets are also useful in studies attempting to explain how stimulus qualities such as amplitude normalization [@gingras2014be] or different performers' interpretations [@battcock2021in] affect ratings of valence and arousal.
-Although predictive modelling is not always an explicit goal of these studies, they can be adapted to fit into a MER framework.
-For example, @chowdhury2021perceived adopted data from a previous psychological study of piano performances to compare sets of features analyzed from audio files, musical scores, or deep neural network feature extractors.
+Although training MER systems with a wide range of stimuli and features can be useful for generalizable modelling, smaller datasets can be more appropriate when greater control over stimuli or features is necessary.
+For example, @griffiths2021am conducted a study aiming to isolate features optimally predictive for evaluating emotion ratings of music from different genres.
+Using multiple linear regression, he predicted emotion in 20 tracks from different genres, and validated the model using a separate set of 40 tracks.
+By preparing the model for a specific predictive context, the study surpassed the performance accuracy of previous benchmark models.
+In another study, @saizclar2022pr evaluated novel audio-based features in a predictive context, extracting 22 variables derived from onset curves -- changes in the energy of a note starting from its onset -- to predict valence and activation in 40 short (8-12s) piano excerpts.
+These carefully-designed experiments evaluate specific questions, informing researchers about how models can be designed to perform accurately in diverse prediction tasks.
+
+Small, carefully-curated, datasets are also useful when attempting to *explain* how musical factors such as amplitude normalization [@gingras2014be] or different performers' interpretations [@battcock2021in], affect variance in emotion ratings.
+Psychological studies apply similar data collection and modelling procedures to the predictive MER studies summarized above.
+However, statistical models serve a distinct purpose.
+Instead of predicting emotion labels for new music, psychological studies on music emotion test causal theories about the relationship between musical predictors and emotion labels.
+Accurate modelling requires rigorous control of musical parameters and data collection procedures.
+
+The distinction between predictive and explanatory modelling frameworks is important, as it affects decisions about data curation and modelling, as well the predictive and explanatory power of models [@shmueli2010explain].
+However, the interdisciplinary nature of MER means these frameworks can be applied in complementary ways.
+Emotion constructs applied in predictive MER studies often originate from experimental psychology, such as Russell's circumplex model [@Russell1980] and Hevner's adjective circle [@hevner1936].
+Data collected through psychology experiments can also be applied in predictive contexts.
+For example, @chowdhury2021perceived used data from a previous psychological study of piano performances [@battcock2019ac] as a reference standard when comparing predictive accuracy of feature sets analyzed from audio files, musical scores, or deep neural network feature extractors.
+Insights from theoretical studies can inform predictive applications as scholars attempt to surpass existing benchmarks for predictive accuracy.
 

### 2025-04-08 manuscript/manuscript.qmd
changed journal splits to explanatory/predictive and added R2adjusted into the discussion

@@
 We focus on recent studies to identify the overall success rate in MER tasks and the key factors such as modelling techniques, the number of features, or the inferential goal (explanation vs prediction) that might contribute to the prediction accuracy of the models.
-To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years, focusing on subgroup analyses capturing these differences (model type, feature N, journal type).
+To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years, focusing on subgroup analyses capturing these differences (model type, feature N, and predictive vs explanatory modelling).
 Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model [@yang2018review].\
@@
 The number of stimuli is typically around 300-400 (with a median of 324 for regression and 300 for classification), though there is substantial variation, with the extremes from 20 stimuli in @beveridge2018po to 5192 stimuli in @alvarez2023ri.
-There are also additional dimensions to consider, such as the type of cross-validation used, the music genres analyzed (whether a single genre, multiple genres, or a mix), the type of journal in which the studies were published, and the extraction tool used to extract features.
+There are also additional dimensions to consider, such as the type of cross-validation used, the music genres analyzed (whether a single genre, multiple genres, or a mix), the type of modelling (predictive or explanatory) framework, and the extraction tool used to extract features.
 However, these variables do not lend themselves to a simple summary, so we will revisit them during the interpretation and discussion stages.
@@
 
-These comparisons of sub-groupings may also be influenced by other factors, such as the aim of the study (i.e.
-whether it focused on prediction or explanation).
-To address this, we used the type of journal in which each study was published as a proxy indicator, classifying journals as either psychology or engineering.
-Of the 22 regression studies, 13 were published in engineering journals, yielding an average correlation of *r* = 0.656 (9% CI: 0.505–0.769).
-Studies published in psychology journals (9) showed a similar overall correlation of *r* = 0.688 (95% CI: 0.468–0.827).
-No significant difference in model accuracy was observed between the two types of study aims, *Q*(1) = 0.10, *p* = 0.748.
+These comparisons of sub-groupings may also be influenced by other factors, such as whether the study utilised predictive or explanatory modelling framework.
+To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive.
+Of the 22 regression studies, 13 were classified into predictive frameworks, yielding an average correlation of *r* = 0.656 (9% CI: 0.505–0.769).
+Studies with explanatory frameworks (9 in total) showed a similar overall correlation of *r* = 0.688 (95% CI: 0.468–0.827).
+No significant difference in model accuracy was observed between the two types of frameworks, *Q*(1) = 0.10, *p* = 0.748.
 More broadly, while the sub-groupings based on modelling techniques result in an uneven distribution of studies and observations, the two main sub-groupings presented in Table 2 highlight valuable differences in model performance across the studies.
@@
 The caveat of this subgroup analysis is the small number of observations for four techniques.
-When other sub-groupings were explored, such as the type of journal (Engineering with 13 studies vs Psychology with 9 studies), no significant differences were observed (*Q*(1) = 0.94, *p* = .333).
+When other sub-groupings were explored, such as the type of framework utilised (predictive or explanatory), no significant differences were observed (*Q*(1) = 0.94, *p* = .333).
 
@@
 multi-class models (*Q*(1) = 0.03, *p* = 0.8694) differed significantly.
-All classification studies were published in engineering journals.
+All classification studies were published in engineering journals and thus represent predictive framework in our earlier typology.
 
@@
 For example, the smaller datasets often come from music psychology studies, which put a premium on data quality (quality control of the ground-truth data and features) rather than on dataset size and model techniques.
-This argument is largely consistent with the analysis of the studies divided across journal types (psychology vs.
-engineering), even though the pattern is not well-defined.
+This argument is largely consistent with the analysis of the studies divided across predictive and explanatory modelling frameworks (which we determined based on journals representing psychology or engineering discipline), even though the pattern is not well-defined.
 
@@
 Again, we would recommend utilising $R^2$ due it being a relative measure and scale invarant to allow comparison across models, datasets, and studies.
+There is potential confusion in using the $R^2$ measure since some studies report $R^2_{\text{adj}}$, which is a less biased estimate of the model's explanatory power as it incorporates the number of predictors as a penalty.
+However, since there are other measures that calculate penalties for complex models (like AIC or BIC), and the difference between the two measures is small in large datasets, we nevertheless recommend $R^2$ as the most transparent accuracy measure for regression studies.
 
@@
 We could add a mention about R2 adjusted to penalise complex models, but there are other ways to punish for model complexity as well.
--->
+This has now been added to the para above -->
 

### 2025-04-09 manuscript/manuscript.qmd
updates to manuscript
-updated new section on explanatory, predictive modeling
-reported regression for framework splits in arousal subsection of results
-added some citations to discussion section

@@
 
-Large datasets are needed to generalize predictions across diverse samples, especially for deep learning and complex machine-learning models that require extensive pre-training.
-However, the dataset sizes in MER tend to be modest in comparison, as direct annotation of music examples is resource-intensive.
-In contrast, datasets in the visual domain are often significantly larger (e.g., *EmoSet* with 118,102 images and *AffectNet* with 450,000, see @yang2023emoset;@mollahosseini2017affectnet).
+An important factor often affecting the size of datasets employed in MER concerns whether they use a *predictive* or *explanatory* modelling framework.
+Large datasets are necessary in predictive studies, where the predominant goal is to generalize predictions across diverse samples, especially for deep learning and complex machine-learning models that require extensive pre-training.
+Conversely, small, carefully-curated, datasets are useful when attempting to *explain* how musical factors such as amplitude normalization [@gingras2014be] or different performers' interpretations [@battcock2021in], affect variance in emotion ratings.
+In these studies, statistical models serve a different goal.
+Instead of predicting emotion labels for new music, psychological studies on music emotion test causal theories about the relationship between musical predictors and emotion labels.
+Whether models serve predictive or explanatory goals is important—affecting both decisions about data curation and modelling, and the models' resultant predictive and explanatory power [@shmueli2010explain].
+
+In predictive MER tasks, dataset sizes tend to be modest in comparison to other fields, as direct annotation of music examples is resource-intensive.
+For example, in the visual domain datasets are often significantly larger (e.g., *EmoSet* with 118,102 images and *AffectNet* with 450,000, see @yang2023emoset;@mollahosseini2017affectnet).
 Some efforts have been made to scale up MER datasets by inferring emotions from tags (*MTG-Jamendo* with 18,486 excerpts @bogdanov2019mtg and *Music4all* with 109,269 excerpts @santana2020), but these have not found their way into standard emotion prediction or classification tasks yet.
-
-Although training MER systems with a wide range of stimuli and features can be useful for generalizable modelling, smaller datasets can be more appropriate when greater control over stimuli or features is necessary.
-For example, @griffiths2021am conducted a study aiming to isolate features optimally predictive for evaluating emotion ratings of music from different genres.
-Using multiple linear regression, he predicted emotion in 20 tracks from different genres, and validated the model using a separate set of 40 tracks.
-By preparing the model for a specific predictive context, the study surpassed the performance accuracy of previous benchmark models.
-In another study, @saizclar2022pr evaluated novel audio-based features in a predictive context, extracting 22 variables derived from onset curves -- changes in the energy of a note starting from its onset -- to predict valence and activation in 40 short (8-12s) piano excerpts.
-These carefully-designed experiments evaluate specific questions, informing researchers about how models can be designed to perform accurately in diverse prediction tasks.
-
-Small, carefully-curated, datasets are also useful when attempting to *explain* how musical factors such as amplitude normalization [@gingras2014be] or different performers' interpretations [@battcock2021in], affect variance in emotion ratings.
-Psychological studies apply similar data collection and modelling procedures to the predictive MER studies summarized above.
-However, statistical models serve a distinct purpose.
-Instead of predicting emotion labels for new music, psychological studies on music emotion test causal theories about the relationship between musical predictors and emotion labels.
-Accurate modelling requires rigorous control of musical parameters and data collection procedures.
-
-The distinction between predictive and explanatory modelling frameworks is important, as it affects decisions about data curation and modelling, as well the predictive and explanatory power of models [@shmueli2010explain].
-However, the interdisciplinary nature of MER means these frameworks can be applied in complementary ways.
-Emotion constructs applied in predictive MER studies often originate from experimental psychology, such as Russell's circumplex model [@Russell1980] and Hevner's adjective circle [@hevner1936].
-Data collected through psychology experiments can also be applied in predictive contexts.
-For example, @chowdhury2021perceived used data from a previous psychological study of piano performances [@battcock2019ac] as a reference standard when comparing predictive accuracy of feature sets analyzed from audio files, musical scores, or deep neural network feature extractors.
-Insights from theoretical studies can inform predictive applications as scholars attempt to surpass existing benchmarks for predictive accuracy.
+However, small datasets can also be useful in predictive contexts when greater control over stimuli or features is necessary.
+These have been useful in applications testing new feature representations [@saizclar2022pr] or identifying relevant features for multi-genre predictions [@griffiths2021am], or as reference standards for comparison with novel feature sets [@chowdhury2021perceived].
+Findings from explanatory studies often inform theory-driven applications in predictive tasks, helping improve upon current benchmarks.
 
@@
 |   | Regression | Classification | Total |
-|:---------------|:--------------------|:------------------|:---------------|
+|:----------------|:-------------------|:-----------------|:----------------|
 | Study N | 22 | 12 | 34 |
@@
 
-When analyzing the studies across the four modelling techniques used, the prediction do differ significantly (*Q*(3) = 12.43, *p* = .0061).
+When analyzing the studies across the four modelling techniques used, the predictions differ significantly (*Q*(3) = 12.43, *p* = .0061).
 Notably, linear models (LM) and neural networks (NN) were the most common, with 9 and 6 studies, respectively, allowing for more confident interpretations.
@@
 To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive.
-Of the 22 regression studies, 13 were classified into predictive frameworks, yielding an average correlation of *r* = 0.656 (9% CI: 0.505–0.769).
+Of the 22 regression studies, 13 were classified into predictive frameworks, yielding an average correlation of *r* = 0.656 (95% CI: 0.505–0.769).
 Studies with explanatory frameworks (9 in total) showed a similar overall correlation of *r* = 0.688 (95% CI: 0.468–0.827).
@@
 Table 3 describes the broad pattern of results in tabular format, and Figure 3 illustrates the spread and heterogeneity of all studies for arousal.
-The overall correlation across the studies using the best performing model out of each study (Max) is 0.809 (CI95% 0.740-0.860).
-If we examine all the models reported in each study, the correlation drops marginally, to 0.791 (CI95% 0.770-0.810), despite this analysis including about four times as many models as taking the best model out of each study.
+The overall correlation across the studies using the best performing model out of each study (Max) is 0.809 (95% CI: 0.740-0.860).
+If we examine all the models reported in each study, the correlation drops marginally, to 0.791 (95% CI: 0.770-0.810), despite this analysis including about four times as many models as taking the best model out of each study.
 For arousal, even the baseline models seem to perform at a relatively high level.
@@
 For arousal, the indicators of heterogeneity are again high ($\tau^2$ = 0.141 and $I^2$=97.9%), which suggests that summary may be misleading.
-However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.789 95%CI -4.87-6.45, *t* = 0.273, *p* = 0.788).
-If we remove the studies that are outside the 95%CI in heterogeneity, this leaves 13 studies in the summary where *r* = 0.826 (95%CI 0.806-0.845), $\tau^2$ = 0.0042 and $I^2$ = 76.8%.
+However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.789 95% CI: -4.87-6.45, *t* = 0.273, *p* = 0.788).
+If we remove the studies that are outside the 95% CI in heterogeneity, this leaves 13 studies in the summary where *r* = 0.826 (95% CI: 0.806-0.845), $\tau^2$ = 0.0042 and $I^2$ = 76.8%.
 In other words, we observed no material difference to the results obtained with all 22 studies.
@@
 The caveat of this subgroup analysis is the small number of observations for four techniques.
-When other sub-groupings were explored, such as the type of framework utilised (predictive or explanatory), no significant differences were observed (*Q*(1) = 0.94, *p* = .333).
+We also found no difference between studies utilising predictive (*r* = 0.656, 95% CI: 0.505-0.769) or explanatory (*r* = 0.688, 95% CI: 0.468-0.828) frameworks (*Q*(1) = 0.94, *p* = .333).
 
@@
 Figure 4 shows forest plot visualization from the random-effects model of the best-performing models in classification studies.
-$MCC$s vary across a wide range, reporting $MCC$s between 0.55 to 0.98.
-Table 4 indicates that using the best model from each study increases performance relative to all models ($MCC$ = 0.8684 95%CI: 0.7475-0.9336), yet slightly increases heterogeneity ($\tau^2$ = 0.3180, $I^2$ = 99.8%).
+$MCC$s vary across a wide range, ranging from 0.55 to 0.98.
+Table 4 indicates that using the best model from each study increases performance relative to all models ($MCC$ = 0.868 95%CI: 0.748-0.934), yet slightly increases heterogeneity ($\tau^2$ = 0.318, $I^2$ = 99.8%).
 
@@
 
-Accounting for outliers among the classifications results removes 6 studies, affecting both performance ($MCC$ = 0.8941, 95%CI: 0.8282-0.9356) and heterogeneity scores ($\tau^2$ = 0.0569, $I^2$ = 97.7%).
-However, we observed no significant issues in analysis for asymmetry ($\beta$ = -19.769, 95%CI: -39.29--0.24).
-After aggregating across dimensions, some of the best models included only classified arousal [@zhang2016br; @zhang2017fe].
-To assess these studies' impact on overall performance, we conducted the same meta-analytic procedure after excluding them.
-Classification accuracy ($MCC$ = 0.8758, 95%CI: 0.7235-0.9468) does not change notably, nor does the rank order of model classes in terms of performance.
+Accounting for outliers among the classifications results removes 6 studies, affecting both performance ($MCC$ = 0.894, 95% CI: 0.828-0.936) and heterogeneity scores ($\tau^2$ = 0.057, $I^2$ = 97.7%).
+However, we observed no significant issues in analysis for asymmetry ($\beta$ = -19.769, 95% CI: -39.29-0.24).
+After aggregating across dimensions, we found that some studies with the best results only involved arousal classification [@zhang2016br; @zhang2017fe].
+To assess their impact on interpretations, we evaluated how their exclusion affected average classification accuracy.
+These analyses revealed that accuracy ($MCC$ = 0.8758, 95%CI: 0.7235-0.9468) did not change significantly, nor did the rank order of model classes in terms of performance.
 Consequently, we report on all 12 in subsequent analyses.
@@
 
-The number of features (as classified into under 30, between 30 and 300, and above 300 features; see Table 3 for actual ranges) analyzed does not significantly impact results (*Q*(2) = 3.91, *p* = 0.1419), despite $MCC$s showing average differences according to the number of features (\< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; \>300 F: $MCC$ = 0.7754).
-Similarly, the class of model did not differ significantly (*Q*(3) = 4.22, *p* = 0.239) despite neural networks attaining highest average performance ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728).
-Finally, neither single- vs.
-multigenre studies (*Q*(1) = 0.12, *p* = 0.7324), nor binary vs.
-multi-class models (*Q*(1) = 0.03, *p* = 0.8694) differed significantly.
+Analyzing subgroups revealed that the number of features (as classified into under 30, between 30 and 300, and above 300 features; see Table 3 for actual ranges) does not significantly impact results (*Q*(2) = 3.91, *p* = 0.1419), despite $MCC$s differing on average (\< 30 F: $MCC$ = 0.929; 30-300 F: $MCC$ = 0.846; \>300 F: $MCC$ = 0.775).
+Similarly, model classes did not differ significantly (*Q*(3) = 4.22, *p* = 0.239) although neural networks attained higher $MCCs$ (0.9307), followed by SVMs (0.870), tree-based methods (0.854), then linear methods (0.728).
+Finally, neither single vs.
+multigenre (*Q*(1) = 0.12, *p* = 0.732), nor binary vs.
+multi-class models (*Q*(1) = 0.03, *p* = 0.869) differed significantly.
 All classification studies were published in engineering journals and thus represent predictive framework in our earlier typology.
@@
 Despite the increasing complexity of models and datasets, no existing study has rigorously compared the overall success of Music Emotion Recognition research using standardized metrics, nor has there been an analysis of the relative merits of the model techniques and feature sets employed.
-This study presents the first meta-analysis of music emotion recognition.
+This study presents the first meta-analysis of music emotion recognition, breaking down accuracy in terms of the model types, number of features, and empirical frameworks employed.
 
@@
 
-We initially identified 96 studies involving MER models, but narrowed our selection to 34 after filtering studies to ensure consistent quality, reporting standards, and a dedicated focus on music.
+We initially identified 96 studies involving MER models, but narrowed our selection to 34 after filtering studies to ensure consistent quality, reporting standards, and a specific focus on predicting emotions using music features.
 From these studies, we encoded accuracy scores for 290 models, with 204 related to regression and 86 to classification.
-Comparing the most accurate model in each study revealed reasonably accurate prediction of valence (*r* = 0.67 \[0.56, 0.76\]), and arousal (*r* = 0.81 \[0.74, 0.86\]) in regression studies.
-For both affective dimensions of the circumplex model, linear methods (valence *r* = 0.78, arousal *r* = 0.88) and tree-based models (valence *r* = 0.75, arousal *r* = 0.81) outperformed neural networks (valence = 0.47, arousal = 0.66) and support vector machines (SVMs) (valence *r* = 0.58, arousal *r* = 0.79).
-In contrast, neural networks performed most accurately in classification studies ($MCC$ = 0.93), followed by SVMs ($MCC$ = 0.87) and tree-based models ($MCC$ = 0.85).
+Comparing the most accurate model in each study revealed reasonably accurate prediction of valence (*r* = 0.669 \[0.560, 0.755\]), and arousal (*r* = 0.809 \[0.740, 0.860\]) in regression studies.
+For both affective dimensions of the circumplex model, linear methods (valence *r* = 0.784, arousal *r* = 0.882) and tree-based models (valence *r* = 0.750, arousal *r* = 0.809) outperformed support vector machines (SVMs) (valence *r* = 0.539, arousal *r* = 0.796) and neural networks (valence = 0.473, arousal = 0.660).
+In contrast, neural networks performed most accurately in classification studies ($MCC$ = 0.931), followed by SVMs ($MCC$ = 0.870) and tree-based models ($MCC$ = 0.853).
 Despite the high overall success of the research in this topic, the models exhibited several differences relating to (i) the scale and quantity of data sets employed, (ii) feature extraction methods, (iii) the number and types of features and reduction methods used, (iv) the actual modelling architecture, and (v) how model outcomes are cross-validated.
@@
 First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from *r* = 0.51 to 0.67.[^2] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
-For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas now the accuracy is generally notably better, here $MCC$ = 0.87, albeit the differences in metrics.
+For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas prediction rates have improved considerably, here $MCC$ = 0.87, albeit the differences in metrics.
 
@@
 
-Broadly speaking, the present study revealed an uncomfortably large variation in overall quality control and reporting in MER studies.
+Broadly speaking, the present study revealed uncomfortably large variability in overall quality control and reporting in MER studies.
 In many cases, the reporting was insufficient to determine the features used in the models or their sources.
@@
 Consequently, it is too early to generalize that models based on domain knowledge, with a limited number of features and classical techniques, will continue to outperform machine learning approaches that utilize a large (300+) feature sets.
-We believe that the relatively modest size of datasets available so far has prevented deep learning approaches from fully leveraging their potential to learn generalizable patterns in the data .
+We believe that the relatively modest size of datasets available so far has prevented deep learning approaches from fully leveraging their potential to learn generalizable patterns in the data.
 For reference, the size of the datasets in MER are currently comparable to dataset sizes for modelling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
@@
 This lack of diversity may contribute the success of the task but presents a significant limitation in our understanding of MER more broadly [@bornDiversifyingMIRKnowledge2020].
+Greater exploration of multi-genre MER [e.g., @griffiths2021am], and cross-cultural applications [@wang2022cr; wang2021ac; @hu2017cr; @agarwal2021an] will provide an important step toward establishing more generalizable models.
 
@@
 The majority of studies rely either on valence and arousal or some combination of basic emotion categories.
-However, these frameworks may have limited usefulness for some practical applications that aim to capture experiences with music that are more aligned with models of music-induced emotions such as GEMS by @zentner2008emotions or AESTHEMOS [@schindler2017me], or what emotions music are shown to be able to express [@eerola2025what], or what are assumed to be worthwhile clusters of concepts (moods, emotions, tags) from crowdsourced, non-theory driven data [@saari_et_al_2015].
+However, these frameworks may have limited usefulness in practical applications that aim to capture the diversity of emotion experiences with music.
+For example, some experiences align with models of music-induced emotions, such as GEMS by @zentner2008emotions or AESTHEMOS [@schindler2017me], whereas other explore what emotions can be expressed through music [@eerola2025what], or what are assumed to be worthwhile clusters of concepts (moods, emotions, tags) from crowdsourced, non-theory driven data [@saari_et_al_2015].
+Understanding the limitations of different emotion taxonomies can also help improve modelling practices.
+For example, some scholars have explored treating MER as a circular regression problem, which can help overcome practical challenges such as the difficulty of relating to the abstract dimensions of valence and arousal, as well as the modelling assumptions required when translating a circular affective space to regression problems [@dufour2021us].
 

### 2025-04-09 studies/pass3_comparison.qmd
remove excluded studies from bib template
rendered the html versions

@@
 bib_df_merged$NOTES_INDEX.TE <- NULL
-bib_df_merged$CATEGORY <- NULL
 ```
@@
 ```
-
-Notes:
-
-For Feature classification, use this one:
-
-https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9229494
-
-Insert the template the annotation fields from googledoc to the bibtex file.

### 2025-04-09 analysis/analysis.qmd
rendered the html versions

@@
 #m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
-print(funnel(m.cor.c.all, common = FALSE, studlab=TRUE,backtransf=TRUE))
+#print(funnel(m.cor.c.all, common = FALSE, studlab=TRUE,backtransf=TRUE))
 
@@
 
-```
-
-#### Custom plot
-
-```{r}
-tmpdata <- data.frame(SE = FisherZInv(m.cor.c$seTE), Zr = FisherZInv(m.cor.c$TE),studies=m.cor.c$studlab)
-
-tmpdata$citekey<-str_replace_all(tmpdata$studies,'-.*$','')
-tmpdata$citekey<-factor(tmpdata$citekey)
-
-g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
-  geom_point(show.legend = FALSE) +
-  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
-  ylab('Standard Error') + 
-  xlab('r')+
-  scale_y_reverse()+
-#  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
-#  coord_flip()+
-  theme_bw()
-print(g)
 ```

### 2025-04-09 index.qmd
rendered the html versions

@@
 
-We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has beeb preregistered at [https://osf.io/6y3dr/](https://osf.io/6y3dr/).
+We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has been preregistered at [https://osf.io/6y3dr/](https://osf.io/6y3dr/).
 

### 2025-04-09 index.qmd
rendered the html versions

@@
 
-The study report is available [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.
+The study report is available at [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.
 
@@
 
-Commonly used datasets [manuscript/datasets.qmd](manuscript/datasets.qmd).
+Commonly used datasets are available at [manuscript/datasets.qmd](manuscript/datasets.qmd).

### 2025-04-09 studies/search_syntax.qmd
rendered the html versions

@@
 
-Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established [link to prereg] was carried out.
+Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established in the [preregistration plan](preregistration/preregistration.qmd) was carried out.

### 2025-04-09 studies/search_syntax.qmd
rendered the html versions

--- 2024-10-04 studies/search_syntax.qmd
@@
 
-Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established [link to prereg] was carried out.
+Out of the studies identified in the first pass, a closer look at the priority 2 studies using the criteria established in the [preregistration plan](../preregistration/preregistration.qmd) was carried out.

### 2025-04-09 manuscript/manuscript-apaquarto.qmd
polished references and apa-quarto MS version

@@
 Using the best-performing model from each study, we found that valence and arousal were predicted with reasonable accuracy (r = 0.67 and r = 0.81, respectively), while classification models achieved an accuracy of 0.87 as measured with Matthews correlation coefficient.
-Across modeling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed highest performance in classification tasks.
+Across modelling approaches, linear and tree-based methods generally outperformed neural networks in regression tasks, whereas neural networks and support vector machines (SVMs) showed highest performance in classification tasks.
 We highlight key recommendations for future MER research, emphasizing the need for greater transparency, feature validation, and standardized reporting to improve comparability across studies."
@@
 
-Emotional engagement is a key reason why people engage with music in their every day activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions; @agres2021music].
+Emotional engagement is a key reason why people engage with music in their everyday activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions; @agres2021music].
+In recent years, significant advances have been made in music information retrieval (MIR), particularly in music emotion recognition (MER) tasks [@gomez2021; @panda2020audio].
+Music Emotion Recognition (MER) is an interdisciplinary field that combines computer science, psychology, and musicology to identify the emotions conveyed by music.
+Research in this area involves developing computational models capable of recognizing emotions from musical content.
+The emotional attributions of music are based on various theoretical frameworks for emotion and require annotated datasets to build and train these models.
+Improvements to modelling techniques, datasets, and available features have created new opportunities to improve the accuracy and reliability of MER systems developed to predict emotion labels or ratings in music using audio features.
+Over the past 25 years, these studies have established the types of emotions that listeners perceive and recognize in music.
+In the last 15 years, research has increasingly focused on tracing these recognized emotions back to specific musical components, such as expressive features [@lindstrom2003expressivity], structural aspects of music [@eerola_friberg_bresin_2013; @anderson2022ex; @grimaud_eerola_2022], acoustic features [@yang2008; @panda2013multi; @saari_et_al_2015; @eerola2011c; @panda2020audio], or emergent properties revealed through deep learning techniques [@er2019music; @sarkar2020recognition].
+
+<!-- added a MER definition to 2nd sentence above -->
+
+Despite increased interest in MER studies, there is no consensus on the extent to which emotions can accurately be recognized by computational models.
+The current literature presents a diverse and mixed picture regarding the success of models in predicting emotions within the affective circumplex -- valence and arousal-- [@yang2011] and in classifying distinct emotion categories [@fu2010survey].
+
+## A brief history of MER
+
+Music's capacity to convey emotions has been widely discussed since the earliest artificial intelligence (AI) applications in the 1950s.
+Whereas early discourse largely focused on generative composition using computers [@zaripov1969], attention later shifted to creating methods to predict emotion using music's structural cues.
+Novel techniques for information retrieval emerged in the 1950s and 1960s [@fairthorne1968], inspiring analogous developments for automated music analysis [@kassler1966toward; @mendel1969some].
+These developments would set the stage for early work in music emotion recognition (MER).
+@katayose_sentiment_1988 conducted the first study of this nature, creating an algorithm that associated emotions with analyzed chords to generate descriptions like "there is \[a\] hopeful mood on chord\[s\] 69 to 97." [@katayose_sentiment_1988, p.
+1087].
+
+## Classification and regression approaches
+
+In the early 2000s, several research groups conducted studies using regression [@friberg_automatic_2002; @liu_automatic_2003] and classification [@lu_automatic_2005; @feng_popular_2003; @mandel_support_2006] techniques to predict emotion in music audio or MIDI.
+Citing "MIR researchers' growing interest in classifying music by moods" [@downie_music_2008, p.
+1], the Music Information Retrieval EXchange (MIREX) introduced Audio Mood Classification (AMC) to their rotation of tasks in 2007.
+In the first year, nine systems classified mood labels in a common data set, reaching 52.65% in classification accuracy (SD = 11.19%).
+These annual events, along with growing interest in the burgeoning field of affective computing [@picard_affective_1997], would lead to an explosion of interest in MER research.
+
+<!--Paragraph on MER as regression task-->
+
+In the tenth annual AMC task, the highest performing model reached 69.83% accuracy [@park2017representation].
+In parallel, research groups began independently evaluating MER using regression algorithms.
+The first study to popularize this approach predicted valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) in 195 Chinese pop songs [@yang2008] using audio-extracted features represented in 114 dimensions.
+Applying support vector regression, the study achieved 58.3% accuracy in predicting arousal and 28.1% in predicting valence.
+This difference in prediction accuracy between dimensions has reappeared in several subsequent studies [e.g., @bai2016dimensional; @coutinho2013psychoacoustic], with some research suggesting this challenge reflects fewer well-established predictors and more individual differences for valence than arousal [@yang2007music; @eerola2011c].
+
+<!--paragraph on models used across regession & classification tasks-->
+
+Across regression and classification paradigms, a wide range of models have been employed, ranging from multiple linear regression (MLR) [@saizclar2022pr; @griffiths2021am; @yang2008] to deep neural networks [@orjesek2022en; @hizlisoy2021mu].
+In classification tasks, early studies commonly employed Gaussian mixture models [@lu_automatic_2005; @liu_automatic_2003] and support vector machines [@mandel2007labrosa; @lin2009eeg; @tzanetakis2007marsyas], whereas convolutional, recurrent, and fully-connected neural networks are increasingly popular in recent years [@grekow2021music; @song2018audio; @coutinho2017sh].
+In regression tasks, a wide range of algorithms have been tested, including partial least squares (PLS) [@gingras2014be; @wang2021ac], support vector machines (SVMs) [@grekow2018au; @hu2017cr; @agarwal2021an], random forests (RFs) [@beveridge2018po; @xu2021us], and convolutional neural networks [@orjesek2022en].
+
+## Dataset size and scope
+
+MER studies apply regression and classification techniques to predict emotion in diverse datasets, using features derived from both music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
+To facilitate model comparison, several databases have been shared publicly, including *MediaEval* [@soleymani2013], *DEAM* [@aljanaki2017developing], and *AMG1608* [@chen2015amg1608].
+These datasets predominately use Western pop music, are moderate in size (containing from 744 to 1802 music excerpts) and have been manually annotated by a variable numbers of participants (either by experts, students, or crowdsourced workers).
+Several publicly available datasets include features analyzed using audio software suites such as *OpenSMILE* [@eyben2010opensmile] and *MIRToolbox* [@lartillot2007matlab] -- enabling predictions from tens, or even hundreds, of audio features.
+
+An important factor often affecting the size of datasets employed in MER concerns whether they use a *predictive* or *explanatory* modelling framework.
+Large datasets are necessary in predictive studies, where the predominant goal is to generalize predictions across diverse samples, especially for deep learning and complex machine-learning models that require extensive pre-training.
+Conversely, small, carefully-curated, datasets are useful when attempting to *explain* how musical factors such as amplitude normalization [@gingras2014be] or different performers' interpretations [@battcock2021in], affect variance in emotion ratings.
+In these studies, statistical models serve a different goal.
+Instead of predicting emotion labels for new music, psychological studies on music emotion test causal theories about the relationship between musical predictors and emotion labels.
+Whether models serve predictive or explanatory goals is important—affecting both decisions about data curation and modelling, and the models' resultant predictive and explanatory power [@shmueli2010explain].
+
+In predictive MER tasks, dataset sizes tend to be modest in comparison to other fields, as direct annotation of music examples is resource-intensive.
+For example, in the visual domain datasets are often significantly larger (e.g., *EmoSet* with 118,102 images and *AffectNet* with 450,000, see @yang2023emoset;@mollahosseini2017affectnet).
+Some efforts have been made to scale up MER datasets by inferring emotions from tags (*MTG-Jamendo* with 18,486 excerpts @bogdanov2019mtg and *Music4all* with 109,269 excerpts @santana2020), but these have not found their way into standard emotion prediction or classification tasks yet.
+However, small datasets can also be useful in predictive contexts when greater control over stimuli or features is necessary.
+These have been useful in applications testing new feature representations [@saizclar2022pr] or identifying relevant features for multi-genre predictions [@griffiths2021am], or as reference standards for comparison with novel feature sets [@chowdhury2021perceived].
+Findings from explanatory studies often inform theory-driven applications in predictive tasks, helping improve upon current benchmarks.
+
+## The current benchmarks of MER
+
+```{=html}
+<!--
+- Wide range of MER models attempting to outperform previous benchmarks, comparing performance against baseline models [MENTIONED NOW]
+- Introduce ceilings for classification, valence, and arousal, citing Barthet study [MENTIONED]
+- Citing what some researchers attribute limitations to (e.g., lower valence than arousal) [MENTIONED]
+- MIR discussions of "semantic" challenge [LEFT OUT NOW, GLASS-CEILING]
+- inherent error in all stages (annotation, features, models) [MENTIONED]
+- Due to wide range of approaches, difficult to evaluate how successful attempts to raise glass ceiling have been
+- How do modelling techniques, and the number of features used affect performance? Which combinations perform best?
+
+-->
+```
+
+Predictive accuracy in MER tasks has improved as datasets and models have become more sophisticated; Regression models for arousal/valence have been reported to peak at 58%/28% accuracy in 2008 [@yang2008], 70%/26% in 2010 [@huq2010automated], and 67%/46% in 2021 [@yang2021an].
+In the same period, classification rates have increased from 53% [@downie_music_2008] to 70% [@park2017representation] to 83% [@sarkar2020recognition].
+Comparing these past efforts, however, is challenging due to inconsistencies between studies in metrics, modelling architectures, datasets, and evaluation criteria.
+Although we assume that overall accuracy has improved significantly over the past decade, valence remains more challenging to predict than arousal.
+
+Recent studies have sought to enhance emotion prediction by identifying more relevant feature sets [@panda2020audio; @chowdhury2021perceived], integrating low-, mid-, and high-level features through multimodal data [@celma_foafing_2006], and leveraging neural networks to learn features directly from audio [@zhang2016br; @alvarez2023ri; @agarwal2021an].
+These approaches aim to overcome ceiling effects in predictive accuracy [@downie_music_2008], which some scholars refer to as a *semantic gap* [@wiggins_semantic_2009; @celma_foafing_2006].
+However, this prediction ceiling may be better understood as an inherent *measurement error* arising from annotations, feature representations, and model limitations.
+Although isolating the sources of these errors remains infeasible at this stage, comparing success rates across modelling techniques, feature set sizes, and other meaningful factors offers a step toward addressing this challenge.
+To date, however, no study has systematically compared the results of the diverse approaches employed in MER research.
+
+## Aims
+
+<!--This paragraph now is somewhat inconsistent with the analyses we actually perform motivating the journal/feature N/model discussion-->
+
+Our aim is to evaluate the predictive accuracy of two types emotional expression in music: (a) models that predict track-specific coordinates in affective circumplex space (valence and arousal), and (b) models that classify discrete emotion categories.
+We focus on recent studies to identify the overall success rate in MER tasks and the key factors such as modelling techniques, the number of features, or the inferential goal (explanation vs prediction) that might contribute to the prediction accuracy of the models.
+To achieve this, we conduct a meta-analysis of journal articles published in the past 10 years, focusing on subgroup analyses capturing these differences (model type, feature N, and predictive vs explanatory modelling).
+Based on existing literature, we hypothesize that arousal will be predicted with higher accuracy than valence, as valence tends to be more context-dependent and challenging to model [@yang2018review].\
+<!-- yang et al. attribute this to fewer salient features, and individual differences, which I think is consistent with these descriptions -->\
+In terms of the modelling techniques and the number of features, a reasonable hypothesis is that advanced techniques (e.g., neural networks) and larger amount of features will lead to higher prediction rates than conventional techniques (e.g., logistic regression or linear regression) and smaller feature sets.
+However, this relationship might not be as straightforward as this due to the demands complex models place on dataset size [@alwosheel2018; @sun2017revisiting].
+
+<!-- incorporate splits into above? -->
 
@@
 
+We preregistered the meta-analysis plan on 21 June 2024 at OSF, <https://osf.io/c5wgd>, and the plan is also available at <https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html>).
+
+## Study identification
+
+In the search stage, we used three databases, *Web of Science*, *Scopus*, and *Open Alex* to identify journal articles published between 2014 and 2024 containing keywords/title `valence OR arousal OR classi* OR categor* OR algorithm AND music AND emotion AND recognition` (see specific search strings for each database in [Study Data and Code Repository - Search Syntax](https://tuomaseerola.github.io/metaMER/studies/search_syntax.html)).
+All searches were done in May 2024.
+
+The initial search yielded 553 potential studies after excluding duplicate entries.
+We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $r$ or $MCC$ values see [Study Data and Code Repository - Extraction Details](https://tuomaseerola.github.io/metaMER/studies/extraction_details.html) for a breakdown).
+After the screening stage, we defined a set of entities to extract characterising (i) music (genre, stimulus number \[N\], duration), (ii) features extracted (number, type, source, defined by [@panda2020audio]), (iii) model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), (iv) model complexity (i.e., approximate number of features used to predict ratings), and (v) type of model cross-validation.
+Summary of the common datasets used in the studies in available at [Study Data and Code Repository - Datasets](https://tuomaseerola.github.io/metaMER/manuscript/datasets.html).
+
+We converted all regression results from $R^2$ values into $r$ values for valence and arousal, and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].
+To increase consistency in our analyses, we excluded studies using incompatible features (e.g., spectrograms of audio files [@nag2022]), or dependent variables (e.g., one regression study analyzed valence and arousal together, but not separately [@chin2018]).
+
 ![Flowchart of the study inclusions/eliminations.](figure1.svg){width="580"}
 
+## Quality control
+
+The search yielded studies of variable (and occasionally questionable) quality.
+To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture [Study Data and Code Repository - Comparison](https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html).
+Finally, we excluded studies published in journals of questionable relevance/quality, (e.g., *Mathematical Problems in Engineering* ceased publication following 17 retractions published between July and September 2024).
+Overall this step eliminated 12 studies, leaving us with 34 studies in total.
+
+## Study encoding
+
+To capture key details of each study, we added extra fields to BibTeX entries for each study.
+Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM),[^1] Linear Methods (LM), Tree-based Methods (TM), KS, Add.
+and KNN Methods (KM) -- validation procedure and output measures.
+Additionally, we included study results using executable *R* code containing custom functions for meta-analysis.
+For complete details about our encoding procedure, see [Study Data and Code Repository - Extraction Details](https://tuomaseerola.github.io/metaMER/studies/extraction_details.html).
+
+[^1]: @chen2017co was the only study of those included to use Gaussian Mixture Models.
+We decided to group this with Support Vector Machines as they have been reported to perform similarly on mid-sized data sets [@mashao2003co].
+
 # Results
+
+First we describe the overall pattern of data (regression vs.
+classification, modelling techniques, feature numbers, stimulus numbers, datasets, and other details).
+The analysis code is available at [Study Data and Code Repository - Analysis](https://tuomaseerola.github.io/metaMER/analysis/analysis.html).
 
@@
 
+Although the total number of studies meeting the criteria described in the previous section is modest (34 in total), they encompass a large array of models (290 in total) with a relatively even distribution among the three most popular techniques: Neural Nets (85 models in total), SVMs (88), and Linear Methods (81).
+Tree-based models are less frequently used (30 in total), and there is a small number (6) of other model techniques such as kernel smoothing or K-nearest neighbors (KNN) techniques used in the models.
+However, these techniques will not be visible in the breakdown of the results as these models were not among the strongest models per study (see reporting principles in the results).
+The number of features and stimuli within these studies varies significantly, ranging from as few as three features [@battcock2021in] to a maximum of almost 14,500 features [@zhang2023mo].
+The median number of features differs between regression (653) and classification (98) studies, primarily reflecting the nature of the datasets used in each approach.
+The number of stimuli is typically around 300-400 (with a median of 324 for regression and 300 for classification), though there is substantial variation, with the extremes from 20 stimuli in @beveridge2018po to 5192 stimuli in @alvarez2023ri.
+There are also additional dimensions to consider, such as the type of cross-validation used, the music genres analyzed (whether a single genre, multiple genres, or a mix), the type of modelling (predictive or explanatory) framework, and the extraction tool used to extract features.
+However, these variables do not lend themselves to a simple summary, so we will revisit them during the interpretation and discussion stages.
+
+We first report regression studies that predict valence and arousal.
+
+## Results for regression studies
+
+Since there are many models contained within each of the studies, we will report the results in two parts; We first give an overview of the results for all models, and then we focus on the best performing models of each study.
+The best performing model is the model within each study with the highest correlation coefficient.
+This reduction is done to avoid the issue of multiple models from the same study deflating the results as majority of the models included are relative modest baseline or alternative models that do not represent the novelty or content of the article.
+We also provide a summary of the results with all models included in addition to the chosen strategy, where the best model of each study is considered.
+
+### Results for valence
+
+Table 2 summarises the results for all models (All) as well as best performing models (Max) for each study for valence.
+The summary includes the number of models and observations, the correlation coefficient and its 95% confidence interval, the t-value and p-value for the correlation, the heterogeneity statistics $\tau^2$ and $I^2$, calculated through appropriate transformations (Fisher's Z) for the correlation coefficient as part of a random-effects model using `meta` library [@balduzzi2019].
+We used Paule-Mandel estimator for between-study heterogeneity [@langan2019comparison] and Knapp-Hartung [@knapp2003improved] adjustments for confidence intervals.
+In this table we also report two subgroup analyses.
+One where we have divided the studies according to the number of features they contain (three categories based on quantiles to keep the group size comparable) and into four modelling techniques introduced earlier (Table 1).
+
+Table 2. Meta-analytic diagnostic for all regression studies predicting valence from audio. See Table 1 for the acronyms of the modelling techniques.
+
+| Concept | Models, obs | $r$ \[95%-CI\] | $t$ | $p$ | $\tau^2$ | $I^2$ |
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+| Valence All | 102,60017 | 0.583 \[0.541-0.623\] | 21.41 | .0001 | 0.094 | 97.7% |
+| Valence Max | 22,14172 | 0.669 \[0.560-0.755\] | 9.58 | .0001 | 0.148 | 98.4% |
+| *N Features* |  |  |  |  |  |  |
+| \<30 F | 6,3140 | 0.766 \[0.488-0.903\] | \- | \- | 0.198 | 98.6% |
+| (Range: 3-22; Mdn = 16.5; *M* = 15.7) |  |  |  |  |  |  |
+| 30-300 F | 8,4098 | 0.580 \[0.276-0.778\] | \- | \- | 0.188 | 97.4% |
+| (Range: 45-260; Mdn = 101; *M* = 136) |  |  |  |  |  |  |
+| 300+ F | 8,6934 | 0.666 \[0.531-0.767\] | \- | \- | 0.062 | 98.0% |
+| (Range: 388-14460; Mdn = 654; *M* = 3360) |  |  |  |  |  |  |
+| *Techniques* |  |  |  |  |  |  |
+| LM | 9,2457 | 0.784 \[0.652-0.870\] | \- | \- | 0.1194 | 96.3% |
+| SVM | 4,5068 | 0.539 \[0.171-0.774\] | \- | \- | 0.0702 | 97.1% |
+| NN | 6,3317 | 0.473 \[0.167-0.696\] | \- | \- | 0.1029 | 98.2% |
+| TM | 3,3330 | 0.750 \[0.292-0.928\] | \- | \- | 0.0740 | 98.8% |
+
+The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 22 studies achieving an average correlation of *r* = 0.669 (95% CI: 0.560-0.755), called "valence Max" in Table 2.
+However, when considering all models across these studies (n = 102), the overall prediction rate drops significantly to *r* = 0.583.
+We argue that this lower correlation is likely due to the inclusion of baseline models reported in these studies, which may not reflect the true success of the task for the purposes of our analysis.
+
+#### Quantifying study heterogeneity
+
+Further analysis of between-study heterogeneity, as indexed by the $\tau^2$ (0.148) and Higgins & Thompson's $I^2$ statistic [@higgins2002quantifying] at 98.4%, reveals substantial heterogeneity.
+Since $I^2$ is heavily influenced by study size (with larger N leading to lower sampling error), its value may be less insightful in this context.
+In contrast, $\tau^2$, which is less sensitive to the number of studies and directly linked to the outcome metric (*r*), provides a more reliable measure of heterogeneity in this case.
+Also, we note that because the overall heterogeneity in the data is high, we are cautious in our interpretation of the publication bias [@van-aertwicherts_2016].
+
+To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents a forest of the random-effects model, based on the best-performing models from all studies.
+In terms of the forest plot, the range of prediction values (correlations) is broad, spanning from 0.13 to 0.92, with all studies except Koh et al.
+(2023) demonstrating evidence of positive correlations.
+A mean estimate of 0.67 is achieved by 15 out of the 22 models.
+While the confidence intervals are generally narrow due to the large sample sizes in each study, there are exceptions, such as smaller sample sizes in @beveridge2018po (n = 20), and in @griffiths2021am (n = 40).
+If we explore the asymmetry of the model prediction rate across standard error, we do not observe particular asymmetries that would indicate particular bias in the reported studies.
+This is verified by non-significant Egger's test ($\beta$ = 5.05, CI95% -0.99-11.09, *t* = 1.64, *p* = 0.112, @eggersmith_1997).
+
+Coming back to the mean of valence correlation of 0.669 by all studies and the possible impact of study heterogeneity on this estimation, we also calculated the correlation without the studies that lie outside the 95% CI for pooled effect.
+This left 12 studies in the data and resulted in the meta-analytical pooled correlation of 0.686 (CI95% 0.635-0.731).
+In other words, despite the large variation in the correlations and standard errors across the studies, this variation in itself does not seem to be a significant driver behind the overall effect.
+
 {{< include _figure2.qmd >}}
+
+#### Reporting splits
+
+To gain insights into the factors contributing to the wide range of model success, we explored several ways of splitting the data.
+Table 2 presents two key splits: one based on the number of features used, which we hypothesized might influence model performance, and another based on the modelling techniques employed.
+In terms of feature sets, we categorized them into three groups: few features (\<30), a large number of features (30–300), and massive feature sets (300+).
+These splits produced reasonably comparable representations of regression and classification studies, though the actual ranges differed.
+For transparency, we report a summary of the actual feature counts in Table 2.
+Models (6 in total) using a relatively small number of features (\<30) performed best (*r* = 0.766, 95% CI: 0.488–0.903) compared to those utilizing larger feature sets.
+However, it is worth noting that the models using massive feature sets (300+, 8 studies in total) also performed reasonably well (*r* = 0.666), achieving more consistent results than the overall prediction rate (*r* = 0.669).
+This observation is supported by the lowest heterogeneity index for the massive feature set group ($\tau^2$ = 0.062), indicating more consistent results across studies.
+Studies with large number of features (30-300 features, 8 studies in total) delivered the worst results, *r* = 0.580 (95% CI: 0.276–0.778).
+Despite the fluctuation in the overall model accuracy between the number of features, the differences are not substantially large to pass the test of statistical significance (*Q*(2) = 2.03, *p*=.363).
+
+When analyzing the studies across the four modelling techniques used, the predictions differ significantly (*Q*(3) = 12.43, *p* = .0061).
+Notably, linear models (LM) and neural networks (NN) were the most common, with 9 and 6 studies, respectively, allowing for more confident interpretations.
+Linear models achieved the highest prediction rate (*r* = 0.784, 95% CI: 0.652–0.870), though this may be influenced by the smaller datasets typically used in these studies.
+These studies also exhibited higher heterogeneity ($\tau^2$ = 0.119) compared to other techniques.
+While there were only 3 studies involving tree-based model (TM), these performed well, achieving *r* = 0.750, 95% CI: 0.292–0.928), and the relatively poor performance of the neural network (NN) models represented in six studies (*r* = 0.473, 95% CI: 0.167–0.696) is difficult to explain without a deeper examination of the specific model architectures and the stimuli used in these studies.
+
+We also ran the sub-grouping analyses across stimulus genres (single vs mixed), finding no significant difference (*Q*(1) = 0.01, *p* = .9158).
+Both single-genre (*r* = 0.675 95% CI: 0.465, 0.813, *n* = 8) and multi-genre (*r* = 0.665, 95% CI: 0.508-0.779, *n* = 14) achieved similar results, although multi-genre studies exhibited slightly higher heterogeneity ($\tau^2$ = 0.167) than single-genre studies ($\tau^2$ = 0.137).
+
+These comparisons of sub-groupings may also be influenced by other factors, such as whether the study utilised predictive or explanatory modelling framework.
+To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive.
+Of the 22 regression studies, 13 were classified into predictive frameworks, yielding an average correlation of *r* = 0.656 (95% CI: 0.505–0.769).
+Studies with explanatory frameworks (9 in total) showed a similar overall correlation of *r* = 0.688 (95% CI: 0.468–0.827).
+No significant difference in model accuracy was observed between the two types of frameworks, *Q*(1) = 0.10, *p* = 0.748.
+More broadly, while the sub-groupings based on modelling techniques result in an uneven distribution of studies and observations, the two main sub-groupings presented in Table 2 highlight valuable differences in model performance across the studies.
+<!-- numbers in the text updated up to here, CA 20/2/2025 -->
+
+### Results for arousal
+
+Moving on the arousal, we carry out the same meta-analytical analysis applying the random-effects model to arousal.
+Table 3 describes the broad pattern of results in tabular format, and Figure 3 illustrates the spread and heterogeneity of all studies for arousal.
+The overall correlation across the studies using the best performing model out of each study (Max) is 0.809 (95% CI: 0.740-0.860).
+If we examine all the models reported in each study, the correlation drops marginally, to 0.791 (95% CI: 0.770-0.810), despite this analysis including about four times as many models as taking the best model out of each study.
+For arousal, even the baseline models seem to perform at a relatively high level.
+
+#### Quantifying study heterogeneity
+
+For arousal, the indicators of heterogeneity are again high ($\tau^2$ = 0.141 and $I^2$=97.9%), which suggests that summary may be misleading.
+However, the analysis of asymmetry does not reveal significant issues (Eggers test, $\beta$ = 0.789 95% CI: -4.87-6.45, *t* = 0.273, *p* = 0.788).
+If we remove the studies that are outside the 95% CI in heterogeneity, this leaves 13 studies in the summary where *r* = 0.826 (95% CI: 0.806-0.845), $\tau^2$ = 0.0042 and $I^2$ = 76.8%.
+In other words, we observed no material difference to the results obtained with all 22 studies.
+
+Table 3. Meta-analytic diagnostic for all regression studies predicting arousal from audio.
+
+| Concept | Models, obs | $r$ \[95%-CI\] | $t$ | $p$ | $\tau^2$ | $I^2$ |
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+| Arousal All | 102, 60017 | 0.791 \[0.770-0.810\] | 39.9 | 0.0001 | 0.069 | 96.2% |
+| Arousal Max | 22, 14172 | 0.809 \[0.740-0.860\] | 13.6 | 0.0001 | 0.141 | 97.9% |
+| *N Features* |  |  |  |  |  |  |
+| \<30 F | 6, 3140 | 0.885 \[0.782-0.940\] |  |  | 0.0948 | 93.5% |
+| (Range: 3-22; Mdn = 16.5; *M* = 15.7) |  |  |  |  |  |  |
+| 30-300 F | 8, 4098 | 0.735 \[0.501-0.868\] |  |  | 0.1971 | 98.2% |
+| (Range: 45-260; Mdn = 101; *M* = 136) |  |  |  |  |  |  |
+| 300+ F | 8, 6934 | 0.804 \[0.716-0.867\] |  |  | 0.0612 | 97.4% |
+| (Range: 388-14460; Mdn = 654; *M* = 3360) |  |  |  |  |  |  |
+| *Techniques* |  |  |  |  |  |  |
+| LM | 8, 1713 | 0.882 \[0.809-0.928\] |  |  | 0.0846 | 93.3% |
+| SVM | 5, 5812 | 0.796 \[0.559-0.913\] |  |  | 0.1325 | 98.3% |
+| NN | 6, 3317 | 0.660 \[0.395-0.823\] |  |  | 0.1209 | 98.1% |
+| TM | 3, 3330 | 0.809 \[0.733-0.864\] |  |  | 0.0025 | 65.4% |
+
+<!-- numbers in the text updated up to here, CA 20/2/2025 -->
+
+```{=html}
+<!-- Schwarzer and colleagues (Schwarzer, Carpenter, and Rücker 2015, chap. 4.3) mention, as a general rule of thumb, that subgroup analyses only make sense when your meta-analysis contains at least 
+K= 10 studies.-->
+```
+
+Figure 3 presents a forest plot of the random-effects model of the best-performing models from all studies.
+Similarly to valence, the range of correlations is also wide for arousal, ranging from 0.35 to 0.95, with all studies demonstrating evidence of positive correlations.
+A mean estimate of 0.81 or higher is achieved by the majority (14 out of the 22 models).
+Due to large sample in most studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am; @koh2023me; @saizclar2022pr; @wang2021ac].
+
+<!-- Removed reference to the funnel plot, TE 19/3/2025 -->
+
+#### Reporting splits
+
+The analysis of the subdivision of studies shows that there is no significant differences between the studies using different number of features (*Q*(2) = 5.20, *p* = .074) despite the differing means (*r* = 0.885 for studies with less than 30 features, *r* = 0.735 for 30 to 300 features, and *r* = 0.804 for studies utilising over 300 features).
+The differences in the techniques, however, show statistically significant variance between subgroups (*Q*(3) = 10.83, *p* = .0127).
+The Neural Nets (NN) achieve poor prediction of arousal (*r* = 0.660) in comparison to other techniques.
+The caveat of this subgroup analysis is the small number of observations for four techniques.
+We also found no difference between studies utilising predictive (*r* = 0.656, 95% CI: 0.505-0.769) or explanatory (*r* = 0.688, 95% CI: 0.468-0.828) frameworks (*Q*(1) = 0.94, *p* = .333).
 
@@
 
+## Results for classification studies
+
+We next evaluated classification studies.
+The number of emotion classes predicted varied between studies, ranging from two to eight.
+Across studies, most operationalizations corresponded to either affective dimensions of the circumplex model or discrete emotion labels mapping to those dimensions [e.g., happy, sad, nervous, and calm and similar variants used in @agarwal2021an; @alvarez2023ri; @yeh2014po].
+Despite common adoption of the circumplex quadrants, studies differed in modelling decisions: one study predicted quadrants in a multi-class problem [@panda2020no], whereas another predicted them in a series of binary classification tasks [@bhuvanakumar2023em].
+Others predicted valence and arousal in separate tasks [@hu2022de; @zhang2016br], and some of the models analyzed only predicted arousal [e.g., all models in @zhang2017fe; the CART model in @zhang2016br].
+Finally, some studies excluded specific quadrants [@hizlisoy2021mu] due to a lack of relevant stimuli, whereas others divided quadrants into multiple levels of valence and arousal [@nguyen2017an; @sorussa2020em].
+Because only a few studies separately reported valence and arousal or quadrant classification, we averaged prediction success across them for each model to increase comparability with other studies.
+
+Figure 4 shows forest plot visualization from the random-effects model of the best-performing models in classification studies.
+$MCC$s vary across a wide range, ranging from 0.55 to 0.98.
+Table 4 indicates that using the best model from each study increases performance relative to all models ($MCC$ = 0.868 95%CI: 0.748-0.934), yet slightly increases heterogeneity ($\tau^2$ = 0.318, $I^2$ = 99.8%).
+
 {{< include _figure4.qmd >}}
 
+Table 4. Meta-analytic diagnostic for all classification studies predicting emotion categories from audio.
+
+| Concept | Models, obs | $r$ \[95%-CI\] | $t$ | $p$ | $\tau^2$ | $I^2$ |
+|:----------|:----------|:----------|:----------|:----------|:----------|:----------|
+| All Models | 86, 80544 | 0.825 \[0.790-0.854\] | 23.7 | 0.0001 | 0.208 | 99.7% |
+| Best Models | 12, 15696 | 0.868 \[0.748-0.934\] | 8.13 | 0.0001 | 0.318 | 99.8% |
+| *N Features* |  |  |  |  |  |  |
+| \<30 F | 4, 6179 | 0.929 \[0.816-0.974\] |  |  | 0.098 | 96.2% |
+| (Range: 6-11; Mdn = 9; *M* = 8.75) |  |  |  |  |  |  |
+| 30-300 F | 5, 8193 | 0.846 \[0.361-0.971\] |  |  | 0.482 | 99.9% |
+| (Range: 98-231; Mdn = 122; *M* = 139) |  |  |  |  |  |  |
+| 300+ F | 3, 1324 | 0.775 \[-0.271-0.982\] |  |  | 0.272 | 97.7% |
+| (Range: 397-8904; Mdn = 1702; *M* = 3668) |  |  |  |  |  |  |
+| *Techniques* |  |  |  |  |  |  |
+| LM | 2, 735 | 0.728 \[-0.996-0.999\] |  |  | 0.194 | 98.0% |
+| SVM | 3, 6556 | 0.870 \[-0.727-0.999\] |  |  | 0.823 | 99.9% |
+| NN | 3, 2313 | 0.931 \[0.6523-0.988\] |  |  | 0.125 | 98.8% |
+| TM | 4, 6092 | 0.853 \[0.446-0.968\] |  |  | 0.243 | 99.1% |
+
+### Quantifying study heterogeneity
+
+Accounting for outliers among the classifications results removes 6 studies, affecting both performance ($MCC$ = 0.894, 95% CI: 0.828-0.936) and heterogeneity scores ($\tau^2$ = 0.057, $I^2$ = 97.7%).
+However, we observed no significant issues in analysis for asymmetry ($\beta$ = -19.769, 95% CI: -39.29-0.24).
+After aggregating across dimensions, we found that some studies with the best results only involved arousal classification [@zhang2016br; @zhang2017fe].
+To assess their impact on interpretations, we evaluated how their exclusion affected average classification accuracy.
+These analyses revealed that accuracy ($MCC$ = 0.8758, 95%CI: 0.7235-0.9468) did not change significantly, nor did the rank order of model classes in terms of performance.
+Consequently, we report on all 12 in subsequent analyses.
+
+### Reporting splits
+
+Analyzing subgroups revealed that the number of features (as classified into under 30, between 30 and 300, and above 300 features; see Table 3 for actual ranges) does not significantly impact results (*Q*(2) = 3.91, *p* = 0.1419), despite $MCC$s differing on average (\< 30 F: $MCC$ = 0.929; 30-300 F: $MCC$ = 0.846; \>300 F: $MCC$ = 0.775).
+Similarly, model classes did not differ significantly (*Q*(3) = 4.22, *p* = 0.239) although neural networks attained higher $MCCs$ (0.9307), followed by SVMs (0.870), tree-based methods (0.854), then linear methods (0.728).
+Finally, neither single vs.
+multigenre (*Q*(1) = 0.12, *p* = 0.732), nor binary vs.
+multi-class models (*Q*(1) = 0.03, *p* = 0.869) differed significantly.
+All classification studies were published in engineering journals and thus represent predictive framework in our earlier typology.
+
+### Model success across concepts, model types and feature counts
+
+To assess how the use of different model types affected performance, we prepared heatmap visualizations depicting differences in success across feature *n* categories and algorithms.
+We collapsed SVM and Tree-Based categories due to their low representation in the model summary.
+Figure 5 summarizes differences in success (a) across categories, as well as (b) the algorithms in each model class.
+Overall, studies using smaller feature sets tend to perform best, whereas the best model type largely depends on the nature of the prediction task.
+For valence and arousal, linear models perform better than other model types, whereas for emotion classification, neural networks show the best overall performance.
+The overall pattern aligns with the analyses of the splits reported earlier concerning model types and feature counts, but the visualization also highlights concurrent information about the feature n, model types, study counts, and the average number of stimuli within each combination.
+For instance, studies with the lowest number of features (\<30) also tend to have the highest mean number of stimuli (M = 749.5), while the poorest-performing feature count range (30–300) corresponds to the lowest mean number of stimuli (M = 522.5).
+It is also reassuring to observe that studies utilizing neural networks and other model types tend to use a higher number of features and stimuli than those employing linear models, as this reflects the capabilities and internal training requirements built into these models.
+
+![Heatmaps summarizing models.
+Panel a depicts overall success across tasks according to model type and feature *n* summaries.
+Text labels summarize the number of models belonging to each subgroup, whereas the numbers in parentheses summarize the median number of stimuli used.
+Panel b summarizes the algorithms pertaining to each class, colour-coded by frequency.
+Grey rectangles are visual aids aligning with *x*-axis groupings in panel a (white: LM; light grey: NN; dark grey: other).](model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="668"}
+
 # Discussion and conclusions
+
+Research on Music Emotion Recognition has steadily increased in popularity since the early 2000s, with technological advancements facilitating sharing of data sets, analysis tools, and music stimuli.
+Public forums like the Music Information Retrieval Exchange (MIREX) have facilitated collaborations between computer scientists, musicologists, and psychologists alike -- spurring improvements in performance.
+Despite the increasing complexity of models and datasets, no existing study has rigorously compared the overall success of Music Emotion Recognition research using standardized metrics, nor has there been an analysis of the relative merits of the model techniques and feature sets employed.
+This study presents the first meta-analysis of music emotion recognition, breaking down accuracy in terms of the model types, number of features, and empirical frameworks employed.
+
+We initially identified 96 studies involving MER models, but narrowed our selection to 34 after filtering studies to ensure consistent quality, reporting standards, and a specific focus on predicting emotions using music features.
+From these studies, we encoded accuracy scores for 290 models, with 204 related to regression and 86 to classification.
+Comparing the most accurate model in each study revealed reasonably accurate prediction of valence (*r* = 0.669 \[0.560, 0.755\]), and arousal (*r* = 0.809 \[0.740, 0.860\]) in regression studies.
+For both affective dimensions of the circumplex model, linear methods (valence *r* = 0.784, arousal *r* = 0.882) and tree-based models (valence *r* = 0.750, arousal *r* = 0.809) outperformed support vector machines (SVMs) (valence *r* = 0.539, arousal *r* = 0.796) and neural networks (valence = 0.473, arousal = 0.660).
+In contrast, neural networks performed most accurately in classification studies ($MCC$ = 0.931), followed by SVMs ($MCC$ = 0.870) and tree-based models ($MCC$ = 0.853).
+Despite the high overall success of the research in this topic, the models exhibited several differences relating to (i) the scale and quantity of data sets employed, (ii) feature extraction methods, (iii) the number and types of features and reduction methods used, (iv) the actual modelling architecture, and (v) how model outcomes are cross-validated.
+
+## Improvements to predictive accuracy
+
+The results of the meta-analysis offer several important insights.
+First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from *r* = 0.51 to 0.67.[^2] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
+For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas prediction rates have improved considerably, here $MCC$ = 0.87, albeit the differences in metrics.
+
+[^2]: Values reported as $R^2$ in original study.
+
+Second, there is no single modelling technique that seems to arise on top, although linear models and random forests perform best in regression studies, and neural networks and support vector machines excel in classification tasks.
+We note that the model accuracy is surprisingly little affected by the number of features or the dataset size—likely the result of cross-validation techniques used to avoid overfitting—but the heterogeneity of the materials used in different studies may also mask substantial differences.
+For instance, the smaller datasets tend to use linear models and deliver higher model accuracy than larger datasets and those with a large number of features.
+We surmise that this might relate to disciplinary differences.
+For example, the smaller datasets often come from music psychology studies, which put a premium on data quality (quality control of the ground-truth data and features) rather than on dataset size and model techniques.
+This argument is largely consistent with the analysis of the studies divided across predictive and explanatory modelling frameworks (which we determined based on journals representing psychology or engineering discipline), even though the pattern is not well-defined.
+
+Third, there is little work on the relevance of the features and how these impact the accuracy of the models.
+Unfortunately, in many cases, it is impossible to attribute the sources of error to features (as opposed to target emotions obtained from participants or from the modelling architecture, cross-validation, or the size of data), as the studies so far have not compared the feature sets systematically, nor has a comparison of the datasets with identical features has been carried out [@panda2020audio].
+In the future, it would be advantageous to systematically assess these sources of error in MER studies to allow us to focus on where and how significant improvements can be made.
+
+## Recommendations for future MER studies
+
+Broadly speaking, the present study revealed uncomfortably large variability in overall quality control and reporting in MER studies.
+In many cases, the reporting was insufficient to determine the features used in the models or their sources.
+Additionally, a significant number of studies had to be discarded due to a lack of information about the data, model architectures, or outcome measures.
+We summarize these issues below as recommendations for improving (1) reporting and transparency, (2) feature definition, (3) dataset scale and content, and (4) the selection of emotion frameworks.
+
+Future reports should contain viable information about the data, models, and success metrics.
+The modelling process should include a description of cross-validation, feature extraction technique, feature reduction (if used), and actual accuracy measures.
+We would recommend future studies to use *Matthews correlation coefficient* ($MCC$) for classification studies, as currently there are numerous metrics (*F~1~*, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
+The situation for regression studies tends to be less volatile, but model accuracy may be reported with error measures (Mean Squared Error, Root Mean Squared Error, or Mean Absolute Error, or $MSE$, $RMSE$, $MAE$), which cannot be converted to relative measure such as $R^2$ without knowing the variance of the data.
+Again, we would recommend utilising $R^2$ due it being a relative measure and scale invarant to allow comparison across models, datasets, and studies.
+There is potential confusion in using the $R^2$ measure since some studies report $R^2_{\text{adj}}$, which is a less biased estimate of the model's explanatory power as it incorporates the number of predictors as a penalty.
+However, since there are other measures that calculate penalties for complex models (like AIC or BIC), and the difference between the two measures is small in large datasets, we nevertheless recommend $R^2$ as the most transparent accuracy measure for regression studies.
+
+It would be also highly beneficial to share models and features transparently.
+If a study relies on published datasets, as most do, sharing the actual model (as code/notebooks) and features would allow for a more direct comparison of model techniques for the same dataset.
+Also, not all datasets are shared [@akiki2021; @santana2020; @hizlisoy2021mu; @zhang2017fe].
+Standardizing reporting of datasets to include subsections explaining detailed information about stimuli (including genre, duration, sampling rate, and encoding format), features (types, extraction/analysis software, quantity of features, transformations, reduction methods), and models (types, tuning parameters, cross-validation) will enable more accurate comparisons between studies.
+The reporting in @grekow2018au serves as a useful example by providing enough detail in these areas to facilitate reproducibility.
+Although copyright restrictions may limit the sharing of some datasets, features and examples should be made available through reliable external repositories (e.g., [Zenodo](https://zenodo.org/), [Open Science Framework](https://osf.io/), or [Kaggle datasets](https://osf.io/)).
+
+One of the crucial aspects of modelling is the choice of features, their quantity, and their validation.
+In the present materials, we observe a continuum defined by two extremes: one approach relies on domain knowledge, starting with a limited number of features that are assumed to be perceptually relevant, while the other employs a large number of features, allowing the model to determine which are most relevant for prediction.
+The former is typically favored in music psychology studies, whereas the latter is more common in engineering and machine learning fields.
+Our results suggest that the domain knowledge-driven approach leads to the highest model accuracy across all studies and techniques.
+However, as our sample includes studies from the past 10 years, it is important to note that deep learning models have only gained prominence in this field since 2021.
+Consequently, it is too early to generalize that models based on domain knowledge, with a limited number of features and classical techniques, will continue to outperform machine learning approaches that utilize a large (300+) feature sets.
+We believe that the relatively modest size of datasets available so far has prevented deep learning approaches from fully leveraging their potential to learn generalizable patterns in the data.
+For reference, the size of the datasets in MER are currently comparable to dataset sizes for modelling facial expressions (median N=502, @krumhuber2017) and speech expressions (median of 1287, @hashem2023).
+However, annotated datasets for visual scenes and objects tend to be much larger, often exceeding 100,000 annotated examples [@deng2009imagenet; @krishna2017visual].
+Datasets of these magnitudes seem to be required for appropriate utilisation of deep learning algorithms [@alwosheel2018; @sun2017revisiting], which may explain the modest results observed in the music emotion recognition studies.
+
+An encouraging finding is that \~94% of the studies analyzed here reported some form of model validation.
+The majority of studies validated models by splitting the dataset into separate sets for training and testing [e.g., @yang2021an], sometimes including an additional set for validation [@sorussa2020em].
+Most used some form of cross validation (CV), with the most common type being 10-fold CV.
+Other varieties included 3-fold, 5-fold, or 6-fold CV, as well as more complex variants like nested leave-one-out CV [@coutinho2017sh] and 20 x 10-fold CV [@panda2020no].
+Whereas many engineering studies performed model validation using one or more large databases, some psychological studies evaluating smaller datasets validated models by designing new experiments.
+Examples include comparing a model's performance on ground-truth data with annotations from a second experiment [@griffiths2021am; @beveridge2018po], or comparing a model's performance across different versions of the same music pieces [@battcock2021in].
+
+At present, the majority of the datasets are Western pop, which represent only a fraction of the musical styles consumed globally.
+Also, the annotators representing the Global North dominate the studies at the moment, with some exceptions [@gomez-canon2023; @zhangPMEmo2018].
+This lack of diversity may contribute the success of the task but presents a significant limitation in our understanding of MER more broadly [@bornDiversifyingMIRKnowledge2020].
+Greater exploration of multi-genre MER [e.g., @griffiths2021am], and cross-cultural applications [@wang2022cr; wang2021ac; @hu2017cr; @agarwal2021an] will provide an important step toward establishing more generalizable models.
+
+Finally, we note that the relevance of the emotion frameworks used in MER is not always explicitly discussed.
+The majority of studies rely either on valence and arousal or some combination of basic emotion categories.
+However, these frameworks may have limited usefulness in practical applications that aim to capture the diversity of emotion experiences with music.
+For example, some experiences align with models of music-induced emotions, such as GEMS by @zentner2008emotions or AESTHEMOS [@schindler2017me], whereas other explore what emotions can be expressed through music [@eerola2025what], or what are assumed to be worthwhile clusters of concepts (moods, emotions, tags) from crowdsourced, non-theory driven data [@saari_et_al_2015].
+Understanding the limitations of different emotion taxonomies can also help improve modelling practices.
+For example, some scholars have explored treating MER as a circular regression problem, which can help overcome practical challenges such as the difficulty of relating to the abstract dimensions of valence and arousal, as well as the modelling assumptions required when translating a circular affective space to regression problems [@dufour2021us].
+
+The present meta-analysis demonstrates that significant progress has been made toward developing accurate and scalable MER models over the past decade.
+Future efforts should prioritize feature validation, standardized reporting, the construction of larger and more diverse datasets, and the transparent sharing of research materials to ensure further consistent improvements in MER.
 

### 2025-04-11 index.qmd
web site improvements and folder clean

--- 2025-04-09 index.qmd
@@
-# README
+---
+title: "A Meta-Analysis of Music Emotion Recognition Studies"
+author:
+  - name: Tuomas Eerola
+    orcid: 0000-0002-2896-929X
+    email: tuomas.eerola@durham.ac.uk
+    affiliations:
+      - name: Durham University
+  - name: Cameron J. Anderson
+    orcid: 0000-0002-8737-2055
+    email: andersoc@mcmaster.ca
+    affiliations:
+      - name: McMaster University
+description: "A Meta-Analysis of Music Emotion Recognition Studies."
+date: 4-11-2025
+title-block-style: default
+---
 
@@
 
-## Plan
+### Plan
 
@@
 
-### Study Search and Selection
+#### Study Search and Selection
 
@@
 
-### Data Extraction and Coding
+#### Data Extraction and Coding
 
@@
 
-### Analysis
+#### Analysis
 
-Data analysis is covered in [analysis/analysis.qmd](analysis/analysis.qmd) document.
+Data analysis steps are covered in the [analysis/analysis.qmd](analysis/analysis.qmd) document.
 
-### Manuscript
+#### Manuscript
 
-The study report is available [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.
+The study report is available in [manuscript/manuscript.qmd](manuscript/manuscript.qmd) document.
 
-### Common datasets
+#### Common datasets
 
-Commonly used datasets [manuscript/datasets.qmd](manuscript/datasets.qmd).
+Commonly used datasets are available in [manuscript/datasets.qmd](manuscript/datasets.qmd).

### 2025-04-11 manuscript/_figure3.qmd
web site improvements and folder clean

@@
 ggarrange(fp1) #  
-ggsave(filename = 'figure3.pdf', width = 12, height = 6, units = 'in',fp1)
+#ggsave(filename = 'figure3.pdf', width = 12, height = 6, units = 'in',fp1)
 

### 2025-04-11 manuscript/_figure4.qmd
web site improvements and folder clean

@@
 ggarrange(fp1)
-ggsave(filename = 'figure4.pdf', width = 12, height = 6, units = 'in',fp1)
+#ggsave(filename = 'figure4.pdf', width = 12, height = 6, units = 'in',fp1)
 

### 2025-04-11 version.R
Remove unnecessary temp files

@@ -1,9 +1,0 @@
-# show package version (these are controlled by renv)
-print(paste("meta:",packageVersion("meta")))
-print(paste("metafor:",packageVersion("metafor")))
-print(paste("dmetar:",packageVersion("dmetar")))
-print(paste("knitr:",packageVersion("knitr")))
-
-print(sessionInfo())
-
-# run me in terminal: R -e 'source("version.R")'

### 2025-04-12 studies/feature_representation.qmd
feat(studies): add qmd tracking feature prevalence per study

---
title: "Feature Representation"
---

This notebook prepares a data frame tabulating the classes of features for each study included in the meta analysis. Feature categories come from Panda et al. (2020).

## Procedure

To tabulate feature classes, we perform the following steps: 1. Read in .bib file and select only relevant fields. 2. Create and clean a data frame containing citation keys and feature categories 3. Account for discrepancies in encoding of features 4. Populate columns for each category tracking whether it was examined in study

### 1. Reading in bib file

First we read in the bibtex file and do some preprocessing to identify `NA` rows, along with the ASCII fields of interest.

```{r}
# read study encodings
study_encodings <- read.delim(
  'bib/extractions.bib',
  sep = '@', 
  header = F,
  na.strings = c("NA", "")
)

# the citekeys appear in the second column

citekey <- study_encodings[,2]
citekey <- citekey[!is.na(citekey)]

# remove all but FEATURE_CATEGORIES ASCII field

feature_class <- study_encodings[,1]
feature_class <- feature_class[
  stringr::str_detect(
    feature_class,
    "FEATURE_CATEGORIES"
  )
]

feature_class <- na.omit(feature_class)

```

## 2. Prepare dataframe

Next we combine the feature categories and citation keys into a data frame. We clean columns to account for excess characters from the bib file.

```{r}
df_features <- data.frame(cbind(feature_class, citekey))

# remove additional characters from .bib file, add formatting

df_features[,1] <- stringr::str_extract(
  df_features[,1], 
  "(?<=\\{).+?(?=\\})"
) |> tolower()

df_features[,1] <- stringr::str_remove_all(
  df_features[,1], 
  ",|;"
)

df_features[,2] <- stringr::str_remove_all(
  df_features[,2], 
  "Article\\{|,"
)

```

### 3. Account for discrepancies

Now we remove studies with no feature categories included or those lacking sufficient detail.

```{r}
# remove unencoded studies
df_features <- subset(
  df_features,
  !feature_class %in% c("uncertain", "not specified")
)

df_features <- dplyr::filter(
  df_features,
  feature_class != " "
)

```

### Standardize feature categories

We'll format names so they're consistent when we tabulate feature categories in the next step. In some cases categories might be encoded as "melodic" and in others "melody", but these refer to the same class, so we need to standardize them.

```{r}
# simplify griffiths et al. (2021)

df_features[
  df_features$citekey == "griffiths2021am",
]$feature_class <- "dynamic timbre harmony rhythm"

# standardize names
df_features[,1] <- stringr::str_replace_all(df_features[,1], "pitch", "melodic")
df_features[,1] <- stringr::str_replace_all(df_features[,1], "melodic", "melody")
df_features[,1] <- stringr::str_replace_all(df_features[,1], "harmonic", "harmony")
df_features[,1] <- stringr::str_replace_all(df_features[,1], "dynamics", "dynamic")
```

### Populate columns

Now we'll create a column for each category and tabulate whether it was included for each study.

First we identify all unique category names:

```{r}
# split encoding into a vector of values delimited by a space
category_representation <- strsplit(df_features[,1], " ")
# identify unique values
categories <- unique(
  unlist(
    category_representation
  )
)
```

Next we populate empty columns for each category name and combine these with our existing dataframe.

```{r}
# populate a matrix of category names with zeroes
category_matrix <- matrix(
  ncol = length(categories),)

category_matrix[1:length(categories)] <- 0
colnames(category_matrix) <- categories

df_features <- data.frame(
  df_features,
  category_matrix
)

```

Now we'll loop through the names of each feature category and identify whether it's present in the "feature_class" column using the stringr package. This will add a "1" to the relevant column if the feature class is represented in a study.

```{r}

for(this_category in categories) {
  df_features[,this_category] <- stringr::str_count(
    df_features$feature_class,
    this_category
  )
}

```

After verifying this works, we no longer need the feature_class column, so we can remove it.

```{r}
df_features$feature_class <- NULL
```

We can also remove rows corresponding to studies not included in the final selection of the metaanalysis.

```{r}
# read in citekeys for included studies
included_citekeys <- c(
  unique(read.csv("../analysis/R_summary.csv")$citekey),
  unique(read.csv("../analysis/C_summary.csv")$citekey)
)

# subset only included studies
df_features <- subset(
  df_features,
  citekey %in% included_citekeys
)

```

Now we can see the common feature classes included in MER studies

```{r}
barplot(
  sapply(
    df_features[,-1],
    sum
  ),
  las = 2
)

```

# References

> Panda, R., Malheiro, R., & Paiva, R. P. (2020). Audio features for music emotion recognition: a survey. *IEEE Transactions on Affective Computing, 14*(1), 68-88.

### 2025-04-12 manuscript/manuscript.qmd
manuscript: add information about encoding exceptions
- moved classification paradigm explanations to methods
- added explanation of exceptions (e.g., activation/resonance/tension concepts)

@@
 We converted all regression results from $R^2$ values into $r$ values for valence and arousal, and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].
-To increase consistency in our analyses, we excluded studies using incompatible features (e.g., spectrograms of audio files [@nag2022]), or dependent variables (e.g., one regression study analyzed valence and arousal together, but not separately [@chin2018]).
+We excluded irrelevant emotion dimensions (e.g., resonance in @deng2015em) and re-coded analogous labels (e.g., *activation* in @saizclar2022pr).
+Some regression studies operationalized arousal using dimensions of energy and tension [@wang2022cr].
+For these studies, we excluded tension, as it has been shown to overlap considerably with valence, and with energy after partialling out the effect of valence [@eerola2011comparison].
+To increase consistency in our analyses, we excluded studies using incompatible features (e.g., spectrograms of audio files in @nag2022) or dependent variables (@chin2018 evaluates valence and arousal as a single dimension).
+
+For classification studies, the number of emotion classes ranged from two to eight.
+Most studies predicted classes corresponding to the affective dimensions of the circumplex model, or discrete emotion labels mapping onto them [e.g., happy, sad, nervous, and calm and similar variants used in @agarwal2021an; @alvarez2023ri; @yeh2014po].
+Despite the popularity of the circumplex, its treatment varied substantially between studies.
+Examples range from predicting quadrants in a multi-class problem [@panda2020no] or in a series of binary classification problems [@bhuvanakumar2023em], or dividing each quadrant into multiple sublevels [@nguyen2017an; @sorussa2020em].
+Some studies predicted valence and arousal separately [@hu2022de; @zhang2016br], whereas others excluded valence (e.g., all models in @zhang2017fe; the CART model in @zhang2016br) or specific quadrants (@hizlisoy2021mu excludes the bottom-right quadrant).
+Only a few studies classified valence and arousal separately; for these studies we averaged prediction success across both emotion concepts.
 
@@
 |   | Regression | Classification | Total |
-|:----------------|:-------------------|:-----------------|:----------------|
+|:-----------------|:-------------------|:-----------------|:-----------------|
 | Study N | 22 | 12 | 34 |
@@
 We next evaluated classification studies.
-The number of emotion classes predicted varied between studies, ranging from two to eight.
-Across studies, most operationalizations corresponded to either affective dimensions of the circumplex model or discrete emotion labels mapping to those dimensions [e.g., happy, sad, nervous, and calm and similar variants used in @agarwal2021an; @alvarez2023ri; @yeh2014po].
-Despite common adoption of the circumplex quadrants, studies differed in modelling decisions: one study predicted quadrants in a multi-class problem [@panda2020no], whereas another predicted them in a series of binary classification tasks [@bhuvanakumar2023em].
-Others predicted valence and arousal in separate tasks [@hu2022de; @zhang2016br], and some of the models analyzed only predicted arousal [e.g., all models in @zhang2017fe; the CART model in @zhang2016br].
-Finally, some studies excluded specific quadrants [@hizlisoy2021mu] due to a lack of relevant stimuli, whereas others divided quadrants into multiple levels of valence and arousal [@nguyen2017an; @sorussa2020em].
-Because only a few studies separately reported valence and arousal or quadrant classification, we averaged prediction success across them for each model to increase comparability with other studies.
-
 Figure 4 shows forest plot visualization from the random-effects model of the best-performing models in classification studies.

### 2025-04-14 manuscript/figures/figure2.R
made figures folder with ACM style figure versions

@@ -1,0 +1,91 @@
+library(metafor, warn.conflicts = FALSE)
+library(dmetar, warn.conflicts = FALSE)
+library(meta, warn.conflicts = FALSE)
+library(DescTools, warn.conflicts = FALSE)
+library(ggplot2, quietly = TRUE)
+library(ggrepel, quietly = TRUE)
+library(forestplot)
+library(ggpubr)
+R_summary <- read.csv("../analysis/R_summary.csv")
+tmp <- dplyr::filter(R_summary, dimension == "valence")
+tmp$studyREF[tmp$studyREF == "Wang et al 2022"] <- c("Wang et al 2022a", "Wang et al 2022b")
+
+# Max values
+m.cor <- metacor(
+  cor = valuesMax,
+  # values
+  n = stimulus_n,
+  studlab = studyREF,
+  #citekey, # unique_id
+  data = tmp,
+  common = FALSE,
+  random = TRUE,
+  prediction = TRUE,
+  #                 backtransf = TRUE,
+  #                 sm = "ZCOR",
+  method.tau = "REML",
+  # could be PM (Paule-Mandel) as well
+  method.random.ci = "HK",
+  title = "MER: Regression: Valence: Summary"
+)
+
+#### Forest plot using forestplot
+data <- tibble::tibble(
+  mean = m.cor$cor,
+  lower = DescTools::FisherZInv(m.cor$lower),
+  upper = DescTools::FisherZInv(m.cor$upper),
+  study = m.cor$studlab,
+  n = m.cor$n,
+  cor = format(round(m.cor$cor, digits = 3), nsmall = 3)
+)
+data <- dplyr::arrange(data, mean)
+
+fp1 <- grid.grabExpr(
+  print(
+    data |>
+      forestplot(
+        labeltext = c(study, n, cor),
+        xticks.digits = 2,
+        xlab = "Correlation",
+        xticks = seq(0,1,by=0.2),
+        clip = c(0, 1)
+      ) |>
+      fp_add_header(
+        study = "Study",
+        n = "N",
+        cor = expression(italic(r))
+      ) |>
+      fp_append_row(
+        mean  = FisherZInv(m.cor$TE.random),
+        lower = FisherZInv(m.cor$lower.random),
+        upper = FisherZInv(m.cor$upper.random),
+        study = "Summary",
+        n = sum(m.cor$n),
+        cor = round(FisherZInv(m.cor$TE.random), 3),
[…]

### 2025-04-14 manuscript/figures/figure3.R

@@ -1,0 +1,92 @@
+library(metafor, warn.conflicts = FALSE)
+library(dmetar, warn.conflicts = FALSE)
+library(meta, warn.conflicts = FALSE)
+library(DescTools, warn.conflicts = FALSE)
+library(ggplot2, quietly = TRUE)
+library(ggrepel, quietly = TRUE)
+library(forestplot)
+library(ggpubr)
+R_summary <- read.csv("../analysis/R_summary.csv")
+tmp <- dplyr::filter(R_summary, dimension == "arousal")
+tmp$studyREF[tmp$studyREF == "Wang et al 2022"] <- c("Wang et al 2022a", "Wang et al 2022b")
+
+# Max values
+m.cor <- metacor(
+  cor = valuesMax,
+  # values
+  n = stimulus_n,
+  studlab = studyREF,
+  #citekey, # unique_id
+  data = tmp,
+  common = FALSE,
+  random = TRUE,
+  prediction = TRUE,
+  #                 backtransf = TRUE,
+  #                 sm = "ZCOR",
+  method.tau = "REML",
+  # could be PM (Paule-Mandel) as well
+  method.random.ci = "HK",
+  title = "MER: Regression: Arousal: Summary"
+)
+
+#### Forest plot using forestplot
+data <- tibble::tibble(
+  mean = m.cor$cor,
+  lower = DescTools::FisherZInv(m.cor$lower),
+  upper = DescTools::FisherZInv(m.cor$upper),
+  study = m.cor$studlab,
+  n = m.cor$n,
+  cor = format(round(m.cor$cor, digits = 3), nsmall = 3)
+)
+data <- dplyr::arrange(data, mean)
+
+fp1 <- grid.grabExpr(
+  print(
+    data |>
+      forestplot(
+        labeltext = c(study, n, cor),
+        xticks.digits = 2,
+        xlab = "Correlation",
+        xticks = seq(0,1,by=0.2),
+        clip = c(0, 1)
+      ) |>
+      fp_add_header(
+        study = "Study",
+        n = "N",
+        cor = expression(italic(r))
+      ) |>
+      fp_append_row(
+        mean  = FisherZInv(m.cor$TE.random),
+        lower = FisherZInv(m.cor$lower.random),
+        upper = FisherZInv(m.cor$upper.random),
+        study = "Summary",
+        n = sum(m.cor$n),
+        cor = round(FisherZInv(m.cor$TE.random), 3),
[…]

### 2025-04-14 manuscript/figures/figure4.R

@@ -1,0 +1,84 @@
+library(metafor, warn.conflicts = FALSE)
+library(dmetar, warn.conflicts = FALSE)
+library(meta, warn.conflicts = FALSE)
+library(DescTools, warn.conflicts = FALSE)
+library(ggplot2, quietly = TRUE)
+library(ggrepel, quietly = TRUE)
+library(forestplot)
+library(ggpubr)
+
+C_summary <- read.csv("../analysis/C_summary.csv")
+tmp <- C_summary
+
+# Max values
+m.cor <- metacor(cor = valuesMax,     # values 
+                 n = stimulus_n,
+                 studlab = studyREF, # unique_id
+                 data = C_summary,
+                 common = FALSE,
+                 random = TRUE,
+                 prediction = TRUE,
+                 backtransf = TRUE,
+                 sm = "ZCOR",
+                 method.tau = "REML",# could be PM (Paule-Mandel) as well
+                 method.random.ci = "HK", 
+                 title = "MER: Classification: Summary")
+
+#### Forest plot using forestplot
+data<-tibble::tibble(mean=m.cor$cor,lower=DescTools::FisherZInv(m.cor$lower),upper=DescTools::FisherZInv(m.cor$upper),study=m.cor$studlab,n=m.cor$n,cor=format(round(m.cor$cor, digits=3), nsmall = 3))
+data<-dplyr::arrange(data,mean)
+
+
+#extrafont::loadfonts()
+#extrafont::font_import()
+
+fp1 <- grid.grabExpr(
+  print(
+    data |>
+      forestplot(
+        labeltext = c(study, n, cor),
+        xticks.digits = 2,
+        xlab = "Matthews Correlation Coefficient",
+        xticks = seq(0,1,by=0.2),
+        clip = c(0, 1)
+      ) |>
+      fp_add_header(
+        study = "Study",
+        n = "N",
+        cor = expression(italic(r))
+      ) |>
+      fp_append_row(
+        mean  = FisherZInv(m.cor$TE.random),
+        lower = FisherZInv(m.cor$lower.random),
+        upper = FisherZInv(m.cor$upper.random),
+        study = "Summary",
+        n = sum(m.cor$n),
+        cor = round(FisherZInv(m.cor$TE.random), 3),
+        is.summary = TRUE
+      ) |>
+      fp_set_style(
+        box = "grey50",
+        line = "grey20",
[…]

### 2025-04-14 manuscript/figures/heat_map_figure.R

@@ -1,0 +1,157 @@
+library(ggplot2)
+library(dplyr)
+library(ggpubr)
+
+# Read in best models ---------------------------------------------
+
+R_heatmap <- read.csv("../analysis/R_summary.csv")
+C_heatmap <- read.csv("../analysis/C_summary.csv")
+
+# Success Heatmap -------------------------------------------------
+
+
+Rtmp <- R_heatmap |> select(
+  model_class_id,
+  feature_n_complexity,
+  valuesMax,
+  dimension,
+  stimulus_n,
+  citekey
+)
+
+Ctmp <- C_heatmap |> select(
+  model_class_id,
+  feature_n_complexity,
+  valuesMax,
+  dimension,
+  stimulus_n,
+  citekey
+)
+
+
+tmp <- rbind(Rtmp, Ctmp)
+
+tmp$model_class_id
+
+tmp[tmp$model_class_id %in% 
+      c("Support Vector Machines",
+        "Tree-based Methods" ),]$model_class_id <-"SVM,TM"
+
+tmp <- tmp |> group_by(
+  dimension,
+  model_class_id,
+  feature_n_complexity
+)|>
+  mutate(
+    study_n = length(citekey),
+    stim_mid = median(stimulus_n),
+    label = paste0("n = ",study_n,"\n(", round(stim_mid), ")")
+  )
+
+# Combine C and R studies, then facet based on type.
+# Simplify labels for x and y axes
+# Median number of stimulus n
+tmp$dimension <- factor(tmp$dimension,
+                        levels = c("valence", 
+                                   "arousal", 
+                                   "classification"),
+                        labels = c("Valence", 
+                                   "Arousal", 
+                                   "Classification"))
+
+heatmap_facets <- tmp |>
+  ggplot(aes(x = model_class_id, 
+             y = feature_n_complexity,
+             fill = valuesMax
+         )) +
+  geom_raster()+
+  facet_wrap(facets = vars(dimension))+
+  scale_fill_distiller(name = "Accuracy", palette = "Spectral",breaks=seq(0,1,by=.20),limits=c(0,1))+
+#  scale_fill_gradient2(name = "Accuracy")+
+  scale_x_discrete(labels = c("LM", "NN", "Other"))+
+  scale_y_discrete(labels = c("<30", "30-300", "300+"))+
+  geom_text(aes(label = label),family='Linux Biolinum O')+
[…]

### 2025-04-14 manuscript/manuscript-apaquarto.qmd
polished manuscript and preprint

@@
 In parallel, research groups began independently evaluating MER using regression algorithms.
-The first study to popularize this approach predicted valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) in 195 Chinese pop songs [@yang2008] using audio-extracted features represented in 114 dimensions.
+The first study to popularize this approach predicted valence (i.e., the negative---positive emotional quality) and arousal (i.e., the calm---exciting quality) in 195 Chinese pop songs [@yang2008] using 114 audio-extracted features.
 Applying support vector regression, the study achieved 58.3% accuracy in predicting arousal and 28.1% in predicting valence.
@@
 
-We preregistered the meta-analysis plan on 21 June 2024 at OSF, <https://osf.io/c5wgd>, and the plan is also available at <https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html>).
+We preregistered the meta-analysis plan on 21 June 2024 at OSF, [https://osf.io/c5wgd](https://osf.io/c5wgd), and the plan is also available at [Study and Code Repository - Preregistration](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html).
 
@@
 The initial search yielded 553 potential studies after excluding duplicate entries.
-We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $r$ or $MCC$ values see [Study Data and Code Repository - Extraction Details](https://tuomaseerola.github.io/metaMER/studies/extraction_details.html) for a breakdown).
+We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $r$ or $MCC$ values (see [Study Data and Code Repository - Extraction Details](https://tuomaseerola.github.io/metaMER/studies/extraction_details.html) for a breakdown).
 After the screening stage, we defined a set of entities to extract characterising (i) music (genre, stimulus number \[N\], duration), (ii) features extracted (number, type, source, defined by [@panda2020audio]), (iii) model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), (iv) model complexity (i.e., approximate number of features used to predict ratings), and (v) type of model cross-validation.
@@
 We converted all regression results from $R^2$ values into $r$ values for valence and arousal, and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].
-To increase consistency in our analyses, we excluded studies using incompatible features (e.g., spectrograms of audio files [@nag2022]), or dependent variables (e.g., one regression study analyzed valence and arousal together, but not separately [@chin2018]).
+We excluded irrelevant emotion dimensions (e.g., resonance in @deng2015em) and re-coded analogous labels (e.g., *activation* in @saizclar2022pr).
+Some regression studies operationalized arousal using dimensions of energy and tension [@wang2022cr].
+For these studies, we excluded tension, as it has been shown to overlap considerably with valence, and with energy after partialling out the effect of valence [@eerola2011comparison].
+To increase consistency in our analyses, we excluded studies using incompatible features (e.g., spectrograms of audio files in @nag2022) or dependent variables (@chin2018 evaluates valence and arousal as a single dimension).
 
-![Flowchart of the study inclusions/eliminations.](figure1.svg){width="580"}
+For classification studies, the number of emotion classes ranged from two to eight.
+Most studies predicted classes corresponding to the affective dimensions of the circumplex model, or discrete emotion labels mapping onto them [e.g., happy, sad, nervous, and calm and similar variants used in @agarwal2021an; @alvarez2023ri; @yeh2014po].
+Despite the popularity of the circumplex, its treatment varied substantially between studies.
+Examples range from predicting quadrants in a multi-class problem [@panda2020no] or in a series of binary classification problems [@bhuvanakumar2023em], or dividing each quadrant into multiple sublevels [@nguyen2017an; @sorussa2020em].
+Some studies predicted valence and arousal separately [@hu2022de; @zhang2016br], whereas others excluded valence (e.g., all models in @zhang2017fe; the CART model in @zhang2016br) or specific quadrants (@hizlisoy2021mu excludes the bottom-right quadrant).
+Only a few studies classified valence and arousal separately; for these studies we averaged prediction success across both emotion concepts.
+
+![Flowchart of the study inclusions/eliminations.](figures/figure1.png){width="580"}
 
@@
 The search yielded studies of variable (and occasionally questionable) quality.
-To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture [Study Data and Code Repository - Comparison](https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html).
+To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture (see [Study Data and Code Repository - Comparison](https://tuomaseerola.github.io/metaMER/studies/pass3_comparison.html)).
 Finally, we excluded studies published in journals of questionable relevance/quality, (e.g., *Mathematical Problems in Engineering* ceased publication following 17 retractions published between July and September 2024).
@@
 To capture key details of each study, we added extra fields to BibTeX entries for each study.
-Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM),[^1] Linear Methods (LM), Tree-based Methods (TM), KS, Add.
-and KNN Methods (KM) -- validation procedure and output measures.
+Fields included information about the genre/type of stimuli employed, along with their duration and number; the number of analyzed features; and the model type -- Neural Nets (NN), Support Vector Machines (SVM),[^1] Linear Methods (LM), Tree-based Methods (TM), Kernel Smoothing, Additive and KNN Methods (KM) -- validation procedure and output measures.
 Additionally, we included study results using executable *R* code containing custom functions for meta-analysis.
@@
        Classification = c("12","86","21","26","19","16","4","Min=6, Md=98, Max=8904","Min=124, Md=300, Max=5192"),
-       Total = c("34","290","85","88","81","30","6","NA","NA")) 
+       Total = c("34","290","85","88","81","30","6"," "," ")) 
 print(knitr::kable(t,bookstabs=TRUE))
@@
 |:----------|:----------|:----------|:----------|:----------|:----------|:----------|
-| Valence All | 102,60017 | 0.583 \[0.541-0.623\] | 21.41 | .0001 | 0.094 | 97.7% |
-| Valence Max | 22,14172 | 0.669 \[0.560-0.755\] | 9.58 | .0001 | 0.148 | 98.4% |
+| Valence All | 102, 60017 | 0.583 \[0.541-0.623\] | 21.41 | .0001 | 0.094 | 97.7% |
+| Valence Max | 22, 14172 | 0.669 \[0.560-0.755\] | 9.58 | .0001 | 0.148 | 98.4% |
 | *N Features* |  |  |  |  |  |  |
-| \<30 F | 6,3140 | 0.766 \[0.488-0.903\] | \- | \- | 0.198 | 98.6% |
-| (Range: 3-22; Mdn = 16.5; *M* = 15.7) |  |  |  |  |  |  |
-| 30-300 F | 8,4098 | 0.580 \[0.276-0.778\] | \- | \- | 0.188 | 97.4% |
-| (Range: 45-260; Mdn = 101; *M* = 136) |  |  |  |  |  |  |
-| 300+ F | 8,6934 | 0.666 \[0.531-0.767\] | \- | \- | 0.062 | 98.0% |
-| (Range: 388-14460; Mdn = 654; *M* = 3360) |  |  |  |  |  |  |
+| \<30 | 6, 3140 | 0.766 \[0.488-0.903\] | \- | \- | 0.198 | 98.6% |
+| 30-300 | 8, 4098 | 0.580 \[0.276-0.778\] | \- | \- | 0.188 | 97.4% |
+| 300+ | 8, 6934 | 0.666 \[0.531-0.767\] | \- | \- | 0.062 | 98.0% |
 | *Techniques* |  |  |  |  |  |  |
-| LM | 9,2457 | 0.784 \[0.652-0.870\] | \- | \- | 0.1194 | 96.3% |
-| SVM | 4,5068 | 0.539 \[0.171-0.774\] | \- | \- | 0.0702 | 97.1% |
-| NN | 6,3317 | 0.473 \[0.167-0.696\] | \- | \- | 0.1029 | 98.2% |
-| TM | 3,3330 | 0.750 \[0.292-0.928\] | \- | \- | 0.0740 | 98.8% |
+| LM | 9, 2457 | 0.784 \[0.652-0.870\] | \- | \- | 0.1194 | 96.3% |
+| SVM | 4, 5068 | 0.539 \[0.171-0.774\] | \- | \- | 0.0702 | 97.1% |
+| NN | 6, 3317 | 0.473 \[0.167-0.696\] | \- | \- | 0.1029 | 98.2% |
+| TM | 3, 3330 | 0.750 \[0.292-0.928\] | \- | \- | 0.0740 | 98.8% |
 
-The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 22 studies achieving an average correlation of *r* = 0.669 (95% CI: 0.560-0.755), called "valence Max" in Table 2.
+The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 22 studies achieving an average correlation of *r* = 0.669 (95% CI: 0.560-0.755), called "Valence Max" in Table 2.
 However, when considering all models across these studies (n = 102), the overall prediction rate drops significantly to *r* = 0.583.
@@
 These splits produced reasonably comparable representations of regression and classification studies, though the actual ranges differed.
-For transparency, we report a summary of the actual feature counts in Table 2.
-Models (6 in total) using a relatively small number of features (\<30) performed best (*r* = 0.766, 95% CI: 0.488–0.903) compared to those utilizing larger feature sets.
+Models using a relatively small number of features (\<30, 6 in total) performed best (*r* = 0.766, 95% CI: 0.488–0.903) compared to those utilizing larger feature sets.
 However, it is worth noting that the models using massive feature sets (300+, 8 studies in total) also performed reasonably well (*r* = 0.666), achieving more consistent results than the overall prediction rate (*r* = 0.669).
@@
 These comparisons of sub-groupings may also be influenced by other factors, such as whether the study utilised predictive or explanatory modelling framework.
-To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive.
+To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive[^2].
 Of the 22 regression studies, 13 were classified into predictive frameworks, yielding an average correlation of *r* = 0.656 (95% CI: 0.505–0.769).
@@
 <!-- numbers in the text updated up to here, CA 20/2/2025 -->
+
+[^2]: ASJC journal classification by Scopus was used to determine the type of subject area.
 
@@
 | *N Features* |  |  |  |  |  |  |
-| \<30 F | 6, 3140 | 0.885 \[0.782-0.940\] |  |  | 0.0948 | 93.5% |
-| (Range: 3-22; Mdn = 16.5; *M* = 15.7) |  |  |  |  |  |  |
-| 30-300 F | 8, 4098 | 0.735 \[0.501-0.868\] |  |  | 0.1971 | 98.2% |
-| (Range: 45-260; Mdn = 101; *M* = 136) |  |  |  |  |  |  |
-| 300+ F | 8, 6934 | 0.804 \[0.716-0.867\] |  |  | 0.0612 | 97.4% |
-| (Range: 388-14460; Mdn = 654; *M* = 3360) |  |  |  |  |  |  |
+| \<30 | 6, 3140 | 0.885 \[0.782-0.940\] |  |  | 0.0948 | 93.5% |
+| 30-300 | 8, 4098 | 0.735 \[0.501-0.868\] |  |  | 0.1971 | 98.2% |
+| 300+ | 8, 6934 | 0.804 \[0.716-0.867\] |  |  | 0.0612 | 97.4% |
 | *Techniques* |  |  |  |  |  |  |
@@
 Similarly to valence, the range of correlations is also wide for arousal, ranging from 0.35 to 0.95, with all studies demonstrating evidence of positive correlations.
-A mean estimate of 0.81 or higher is achieved by the majority (14 out of the 22 models).
+A mean estimate of 0.809 or higher is achieved by the majority (14 out of the 22 models).
 Due to large sample in most studies, the confidence intervals are narrow, although the exceptions ($N < 55$) are clearly visible [@beveridge2018po; @griffiths2021am; @koh2023me; @saizclar2022pr; @wang2021ac].
@@
 | *N Features* |  |  |  |  |  |  |
-| \<30 F | 4, 6179 | 0.929 \[0.816-0.974\] |  |  | 0.098 | 96.2% |
-| (Range: 6-11; Mdn = 9; *M* = 8.75) |  |  |  |  |  |  |
-| 30-300 F | 5, 8193 | 0.846 \[0.361-0.971\] |  |  | 0.482 | 99.9% |
-| (Range: 98-231; Mdn = 122; *M* = 139) |  |  |  |  |  |  |
-| 300+ F | 3, 1324 | 0.775 \[-0.271-0.982\] |  |  | 0.272 | 97.7% |
-| (Range: 397-8904; Mdn = 1702; *M* = 3668) |  |  |  |  |  |  |
+| \<30 | 4, 6179 | 0.929 \[0.816-0.974\] |  |  | 0.098 | 96.2% |
+| 30-300 | 5, 8193 | 0.846 \[0.361-0.971\] |  |  | 0.482 | 99.9% |
+| 300+ | 3, 1324 | 0.775 \[-0.271-0.982\] |  |  | 0.272 | 97.7% |
 | *Techniques* |  |  |  |  |  |  |
@@
 Accounting for outliers among the classifications results removes 6 studies, affecting both performance ($MCC$ = 0.894, 95% CI: 0.828-0.936) and heterogeneity scores ($\tau^2$ = 0.057, $I^2$ = 97.7%).
-However, we observed no significant issues in analysis for asymmetry ($\beta$ = -19.769, 95% CI: -39.29-0.24).
+However, we observed no significant issues in analysis for asymmetry ($\beta$ = -19.77, 95% CI: -39.29-0.24).
 After aggregating across dimensions, we found that some studies with the best results only involved arousal classification [@zhang2016br; @zhang2017fe].
@@
 
-Analyzing subgroups revealed that the number of features (as classified into under 30, between 30 and 300, and above 300 features; see Table 3 for actual ranges) does not significantly impact results (*Q*(2) = 3.91, *p* = 0.1419), despite $MCC$s differing on average (\< 30 F: $MCC$ = 0.929; 30-300 F: $MCC$ = 0.846; \>300 F: $MCC$ = 0.775).
+Analyzing subgroups revealed that the number of features (as classified into under 30, between 30 and 300, and above 300 features; see Table 3 for actual ranges) does not significantly impact results (*Q*(2) = 3.91, *p* = 0.1419), despite $MCC$s differing on average (\< 30: $MCC$ = 0.929; 30-300: $MCC$ = 0.846; 300+: $MCC$ = 0.775).
 Similarly, model classes did not differ significantly (*Q*(3) = 4.22, *p* = 0.239) although neural networks attained higher $MCCs$ (0.9307), followed by SVMs (0.870), tree-based methods (0.854), then linear methods (0.728).
@@
 
-To assess how the use of different model types affected performance, we prepared heatmap visualizations depicting differences in success across feature *n* categories and algorithms.
+To assess how the use of different model types affected performance, we prepared heatmap visualizations (Figure 5)depicting differences in success across feature *n* categories and algorithms.
 We collapsed SVM and Tree-Based categories due to their low representation in the model summary.
@@
 Text labels summarize the number of models belonging to each subgroup, whereas the numbers in parentheses summarize the median number of stimuli used.
-Panel b summarizes the algorithms pertaining to each class, colour-coded by frequency.
-Grey rectangles are visual aids aligning with *x*-axis groupings in panel a (white: LM; light grey: NN; dark grey: other).](model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Panel b summarizes the algorithms pertaining to each class, colour-coded by success rate and the numbers in parenthesis refer to number of studies.](model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
 Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="668"}
@@
 In contrast, neural networks performed most accurately in classification studies ($MCC$ = 0.931), followed by SVMs ($MCC$ = 0.870) and tree-based models ($MCC$ = 0.853).
-Despite the high overall success of the research in this topic, the models exhibited several differences relating to (i) the scale and quantity of data sets employed, (ii) feature extraction methods, (iii) the number and types of features and reduction methods used, (iv) the actual modelling architecture, and (v) how model outcomes are cross-validated.
+Despite the high overall success of the research in this topic, the models exhibited several differences relating to (i) the scale and quantity of data sets employed, (ii) feature extraction methods, (iii) the number and types of features and reduction methods used, (iv) the actual modelling architecture, and (v) how model outcomes were cross-validated.
 
@@
 The results of the meta-analysis offer several important insights.
-First, compared to a 2013 report by @barthet2013, the glass ceiling for valence has risen from *r* = 0.51 to 0.67.[^2] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
+First, compared to a 2013 report by @barthet2013, the prediction ceiling for valence has risen from *r* = 0.51 to 0.67.[^3] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
 For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas prediction rates have improved considerably, here $MCC$ = 0.87, albeit the differences in metrics.
 
-[^2]: Values reported as $R^2$ in original study.
+[^3]: Values reported as $R^2$ in original study.
 
@@
 
-Broadly speaking, the present study revealed uncomfortably large variability in overall quality control and reporting in MER studies.
+Broadly speaking, the present study revealed uncomfortably large variability in overall quality control and reporting practices in MER studies.
 In many cases, the reporting was insufficient to determine the features used in the models or their sources.
@@
 The modelling process should include a description of cross-validation, feature extraction technique, feature reduction (if used), and actual accuracy measures.
-We would recommend future studies to use *Matthews correlation coefficient* ($MCC$) for classification studies, as currently there are numerous metrics (*F~1~*, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
+We would recommend future studies to use Matthews correlation coefficient ($MCC$) for classification studies, as currently there are numerous metrics (*F~1~*, precision, recall, balanced accuracy, etc.), which do not operate in the same range.
 The situation for regression studies tends to be less volatile, but model accuracy may be reported with error measures (Mean Squared Error, Root Mean Squared Error, or Mean Absolute Error, or $MSE$, $RMSE$, $MAE$), which cannot be converted to relative measure such as $R^2$ without knowing the variance of the data.

### 2025-04-14 manuscript/manuscript.qmd
polished manuscript and preprint

@@
 | Techniques | KS, Add. & KNN: 2 | 4 | 6 |
-| Feature N | Min=3, Md=653, Max=14460 | Min=6, Md=98, Max=8904 | NA |
-| Stimulus N | Min=20, Md=324, Max=2486 | Min=124, Md=300, Max=5192 | NA |
+| Feature N | Min=3, Md=653, Max=14460 | Min=6, Md=98, Max=8904 |   |
+| Stimulus N | Min=20, Md=324, Max=2486 | Min=124, Md=300, Max=5192 |   |
 
@@
 |:----------|:----------|:----------|:----------|:----------|:----------|:----------|
-| Valence All | 102,60017 | 0.583 \[0.541-0.623\] | 21.41 | .0001 | 0.094 | 97.7% |
-| Valence Max | 22,14172 | 0.669 \[0.560-0.755\] | 9.58 | .0001 | 0.148 | 98.4% |
+| Valence All | 102, 60017 | 0.583 \[0.541-0.623\] | 21.41 | .0001 | 0.094 | 97.7% |
+| Valence Max | 22, 14172 | 0.669 \[0.560-0.755\] | 9.58 | .0001 | 0.148 | 98.4% |
 | *N Features* |  |  |  |  |  |  |
-| \<30 F | 6,3140 | 0.766 \[0.488-0.903\] | \- | \- | 0.198 | 98.6% |
-| (Range: 3-22; Mdn = 16.5; *M* = 15.7) |  |  |  |  |  |  |
-| 30-300 F | 8,4098 | 0.580 \[0.276-0.778\] | \- | \- | 0.188 | 97.4% |
-| (Range: 45-260; Mdn = 101; *M* = 136) |  |  |  |  |  |  |
-| 300+ F | 8,6934 | 0.666 \[0.531-0.767\] | \- | \- | 0.062 | 98.0% |
-| (Range: 388-14460; Mdn = 654; *M* = 3360) |  |  |  |  |  |  |
+| \<30 | 6, 3140 | 0.766 \[0.488-0.903\] | \- | \- | 0.198 | 98.6% |
+| 30-300 | 8, 4098 | 0.580 \[0.276-0.778\] | \- | \- | 0.188 | 97.4% |
+| 300+ | 8, 6934 | 0.666 \[0.531-0.767\] | \- | \- | 0.062 | 98.0% |
 | *Techniques* |  |  |  |  |  |  |
-| LM | 9,2457 | 0.784 \[0.652-0.870\] | \- | \- | 0.1194 | 96.3% |
-| SVM | 4,5068 | 0.539 \[0.171-0.774\] | \- | \- | 0.0702 | 97.1% |
-| NN | 6,3317 | 0.473 \[0.167-0.696\] | \- | \- | 0.1029 | 98.2% |
-| TM | 3,3330 | 0.750 \[0.292-0.928\] | \- | \- | 0.0740 | 98.8% |
+| LM | 9, 2457 | 0.784 \[0.652-0.870\] | \- | \- | 0.1194 | 96.3% |
+| SVM | 4, 5068 | 0.539 \[0.171-0.774\] | \- | \- | 0.0702 | 97.1% |
+| NN | 6, 3317 | 0.473 \[0.167-0.696\] | \- | \- | 0.1029 | 98.2% |
+| TM | 3, 3330 | 0.750 \[0.292-0.928\] | \- | \- | 0.0740 | 98.8% |
 
@@
 
-The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 22 studies achieving an average correlation of *r* = 0.669 (95% CI: 0.560-0.755), called "valence Max" in Table 2.
+The results indicate that valence can generally be predicted with moderately accuracy, with the best model from each of the 22 studies achieving an average correlation of *r* = 0.669 (95% CI: 0.560-0.755), called "Valence Max" in Table 2.
 However, when considering all models across these studies (n = 102), the overall prediction rate drops significantly to *r* = 0.583.
@@
 | *N Features* |  |  |  |  |  |  |
-| \<30 F | 4, 6179 | 0.9293 \[0.8160-0.9738\] |  |  | 0.0978 | 96.2% |
-| (Range: 6-11; Mdn = 9; *M* = 8.75) |  |  |  |  |  |  |
-| 30-300 F | 5, 8193 | 0.8458 \[0.3613-0.9707\] |  |  | 0.4822 | 99.9% |
-| (Range: 98-231; Mdn = 122; *M* = 139) |  |  |  |  |  |  |
-| 300+ F | 3, 1324 | 0.7754 \[-0.2709-0.9818\] |  |  | 0.2724 | 97.7% |
-| (Range: 397-8904; Mdn = 1702; *M* = 3668) |  |  |  |  |  |  |
+| \<30 | 4, 6179 | 0.9293 \[0.8160-0.9738\] |  |  | 0.0978 | 96.2% |
+| 30-300 | 5, 8193 | 0.8458 \[0.3613-0.9707\] |  |  | 0.4822 | 99.9% |
+| 300+ | 3, 1324 | 0.7754 \[-0.2709-0.9818\] |  |  | 0.2724 | 97.7% |
 | *Techniques* |  |  |  |  |  |  |
@@
 
-To assess how the use of different model types affected performance, we prepared heatmap visualizations depicting differences in success across feature *n* categories and algorithms.
+To assess how the use of different model types affected performance, we prepared heatmap visualizations (Figure 5) depicting differences in success across feature *n* categories and algorithms.
 We collapsed SVM and Tree-Based categories due to their low representation in the model summary.
@@
 Text labels summarize the number of models belonging to each subgroup, whereas the numbers in parentheses summarize the median number of stimuli used.
-Panel b summarizes the algorithms pertaining to each class, colour-coded by frequency.
-Grey rectangles are visual aids aligning with *x*-axis groupings in panel a (white: LM; light grey: NN; dark grey: other).](../manuscript/model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Panel b summarizes the algorithms pertaining to each class, colour-coded by success rate and the numbers in parenthesis refer to number of studies.](../manuscript/model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
 Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="668"}

### 2025-04-14 manuscript/manuscript.qmd
polished manuscript and preprint

@@
 bibliography: references.bib
+sidebar: false
+page-navigation: true
 format:

### 2025-04-15 manuscript/manuscript.qmd
edits to manuscript
-updated manuscript to be consistent with overleaf version
- imported references from overleaf

@@
 Emotional engagement is a key reason why people engage with music in their everyday activities, and it is also why music is increasingly being used in various health applications [@juslin2022emotions; @agres2021music].
-In recent years, significant advances have been made in music information retrieval (MIR), particularly in music emotion recognition (MER) tasks [@gomez2021; @panda2020audio].
+In recent years, significant advances have been made in music information retrieval (MIR), particularly in emotion prediction tasks [@gomez2021; @panda2020audio].
 Music Emotion Recognition (MER) is an interdisciplinary field that combines computer science, psychology, and musicology to identify the emotions conveyed by music.
@@
 Novel techniques for information retrieval emerged in the 1950s and 1960s [@fairthorne1968], inspiring analogous developments for automated music analysis [@kassler1966toward; @mendel1969some].
-These developments would set the stage for early work in music emotion recognition (MER).
+These developments would set the stage for early work in MER.
 @katayose_sentiment_1988 conducted the first study of this nature, creating an algorithm that associated emotions with analyzed chords to generate descriptions like "there is \[a\] hopeful mood on chord\[s\] 69 to 97." [@katayose_sentiment_1988, p.
@@
 MER studies apply regression and classification techniques to predict emotion in diverse datasets, using features derived from both music (e.g., audio, MIDI, metadata) and participants (e.g., demographic information, survey responses, physiological signals, etc.).
-To facilitate model comparison, several databases have been shared publicly, including *MediaEval* [@soleymani2013], *DEAM* [@aljanaki2017developing], and *AMG1608* [@chen2015amg1608].
+To facilitate model comparison, several databases have been shared publicly, including *DEAM* [@aljanaki2017developing; @soleymani2013] and *AMG1608* [@chen2015amg1608].
 These datasets predominately use Western pop music, are moderate in size (containing from 744 to 1802 music excerpts) and have been manually annotated by a variable numbers of participants (either by experts, students, or crowdsourced workers).
-Several publicly available datasets include features analyzed using audio software suites such as *OpenSMILE* [@eyben2010opensmile] and *MIRToolbox* [@lartillot2007matlab] -- enabling predictions from tens, or even hundreds, of audio features.
+Several publicly available datasets include features analyzed using audio software suites such as *OpenSMILE* [@eyben2010opensmile] and *MIR Toolbox* [@lartillot2007matlab] -- enabling predictions from tens, or even hundreds, of audio features.
 
@@
 
-Recent studies have sought to enhance emotion prediction by identifying more relevant feature sets [@panda2020audio; @chowdhury2021perceived], integrating low-, mid-, and high-level features through multimodal data [@celma_foafing_2006], and leveraging neural networks to learn features directly from audio [@zhang2016br; @alvarez2023ri; @agarwal2021an].
+Recent studies have sought to enhance emotion prediction by identifying more relevant feature sets [@panda2020audio; @chowdhury2021perceived], integrating low-, mid-, and high-level features through multimodal data [@celma_foafing_2006], and leveraging neural networks to learn features directly from audio [@zhang2016br; @agarwal2021an].
 These approaches aim to overcome ceiling effects in predictive accuracy [@downie_music_2008], which some scholars refer to as a *semantic gap* [@wiggins_semantic_2009; @celma_foafing_2006].
@@
 
-We preregistered the meta-analysis plan on 21 June 2024 at OSF, [https://osf.io/c5wgd](https://osf.io/c5wgd), and the plan is also available at [Study and Code Repository - Preregistration](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html).
+We preregistered the meta-analysis plan on 21 June 2024 at OSF, <https://osf.io/c5wgd>, and the plan is also available at [Study Data and Code Repository - Preregistration](https://tuomaseerola.github.io/metaMER/preregistration/preregistration.html).
 
@@
 After the screening stage, we defined a set of entities to extract characterising (i) music (genre, stimulus number \[N\], duration), (ii) features extracted (number, type, source, defined by [@panda2020audio]), (iii) model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), (iv) model complexity (i.e., approximate number of features used to predict ratings), and (v) type of model cross-validation.
-Summary of the common datasets used in the studies in available at [Study Data and Code Repository - Datasets](https://tuomaseerola.github.io/metaMER/manuscript/datasets.html).
+Summary of the common datasets used in the studies is available at [Study Data and Code Repository - Datasets](https://tuomaseerola.github.io/metaMER/manuscript/datasets.html).
 
@@
 |   | Regression | Classification | Total |
-|:-----------------|:-------------------|:-----------------|:-----------------|
+|:-----------------|:------------------|:-----------------|:-----------------|
 | Study N | 22 | 12 | 34 |
@@
 
-These comparisons of sub-groupings may also be influenced by other factors, such as whether the study utilised predictive or explanatory modelling framework.
-To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive[^2].
+These comparisons of sub-groupings may also be influenced by other factors, such as whether the study utilised a predictive or explanatory modelling framework.
+To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive.
 Of the 22 regression studies, 13 were classified into predictive frameworks, yielding an average correlation of *r* = 0.656 (95% CI: 0.505–0.769).
@@
 <!-- numbers in the text updated up to here, CA 20/2/2025 -->
-
-[^2]: ASJC journal classification by Scopus was used to determine the type of subject area.
 
@@
 Text labels summarize the number of models belonging to each subgroup, whereas the numbers in parentheses summarize the median number of stimuli used.
-Panel b summarizes the algorithms pertaining to each class, colour-coded by success rate and the numbers in parenthesis refer to number of studies.](../manuscript/model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Panel b summarizes the algorithms pertaining to each class, colour-coded by success rate, and the numbers refer to how many studies used each model.](../manuscript/model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
 Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="668"}
@@
 
-We initially identified 96 studies involving MER models, but narrowed our selection to 34 after filtering studies to ensure consistent quality, reporting standards, and a specific focus on predicting emotions using music features.
+We initially identified 96 studies involving MER models, but narrowed our selection to 34 after filtering studies to ensure consistent quality, reporting standards, and a specific focus on evaluating emotions using music features.
 From these studies, we encoded accuracy scores for 290 models, with 204 related to regression and 86 to classification.
@@
 The results of the meta-analysis offer several important insights.
-First, compared to a 2013 report by @barthet2013, the prediction ceiling for valence has risen from *r* = 0.51 to 0.67.[^3] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
+First, compared to a 2013 report by @barthet2013, the prediction ceiling for valence has risen from *r* = 0.51 to 0.67.[^2] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
 For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas prediction rates have improved considerably, here $MCC$ = 0.87, albeit the differences in metrics.
 
-[^3]: Values reported as $R^2$ in original study.
+[^2]: Values reported as $R^2$ in original study.
 
@@
 
+### Acknowledgments
+
+We thank Prof. Michael Schutz for creating the opportunity for collaboration.
+
 ### Funding statement

### 2025-04-15 manuscript/manuscript-apaquarto.qmd
preprint version processed

@@
 
-![Flowchart of the study inclusions/eliminations.](figures/figure1.png){width="580"}
+{{< include _figure1.qmd >}}
 
@@
 
-```{r}
-#| id: table1
-#| output: asis
-#| error: false
-#| warning: false
-#| message: false
-#| tbl-cap: Summary of the models for regression and classification studies.
-knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
-suppressPackageStartupMessages(library(tidyverse))
-suppressPackageStartupMessages(library(kableExtra))
-#suppressPackageStartupMessages(library(flextable))
+<!-- table 1 is part of `analysis/preprocessing.qmd` updated 20/2/2025) -->
 
-t <- tibble(Info = c("Study N","Model N","Techniques","Techniques","Techniques","Techniques","Techniques","Feature N","Stimulus N"), 
-       Regression = c("22","204","Neural Nets: 64","Support Vector Machines: 62","Linear Methods: 62","Tree-based Methods: 14","KS, Add.
-& KNN: 2","Min=3, Md=653, Max=14460","Min=20, Md=324, Max=2486"),
-       Classification = c("12","86","21","26","19","16","4","Min=6, Md=98, Max=8904","Min=124, Md=300, Max=5192"),
-       Total = c("34","290","85","88","81","30","6"," "," ")) 
-print(knitr::kable(t,bookstabs=TRUE))
-#flextable(t) %>% theme_apa()
+TABLE 1: Summary of data
 
-```
+|   | Regression | Classification | Total |
+|:-----------------|:------------------|:-----------------|:-----------------|
+| Study N | 22 | 12 | 34 |
+| Model N | 204 | 86 | 290 |
+| Techniques | Neural Nets (NN): 64 | 21 | 85 |
+| Techniques | Support Vector Machines (SVM): 62 | 26 | 88 |
+| Techniques | Linear Methods (LM): 62 | 19 | 81 |
+| Techniques | Tree-based Methods (TM): 14 | 16 | 30 |
+| Techniques | KS, Add. & KNN: 2 | 4 | 6 |
+| Feature N | Min=3, Md=653, Max=14460 | Min=6, Md=98, Max=8904 |  |
+| Stimulus N | Min=20, Md=324, Max=2486 | Min=124, Md=300, Max=5192 |  |
 
@@
 
+<!-- See `analysis/analysis.qmd` (updated 17/1/2025) -->
+
 Since there are many models contained within each of the studies, we will report the results in two parts; We first give an overview of the results for all models, and then we focus on the best performing models of each study.
@@
 One where we have divided the studies according to the number of features they contain (three categories based on quantiles to keep the group size comparable) and into four modelling techniques introduced earlier (Table 1).
+
+<!-- DISCUSS: I have changed the modelling techniques into FOUR categories, TE 19/3/2025 -->
 
@@
 | TM           | 3, 3330     | 0.750 \[0.292-0.928\] | \-    | \-    | 0.0740   | 98.8% |
+
+<!-- table updated CA 20/2/2025, revised terms 28/1/2025 -->
 
@@
 
+<!-- numbers in the text updated up to here, CA 20/2/2025 -->
+
+<!-- I've removed the reference to the funnel plot, TE 19/3/2025 -->
+
 {{< include _figure2.qmd >}}
@@
 
+<!-- numbers in the text updated up to here, CA 20/2/2025 -->
+
 When analyzing the studies across the four modelling techniques used, the predictions differ significantly (*Q*(3) = 12.43, *p* = .0061).
@@
 
-These comparisons of sub-groupings may also be influenced by other factors, such as whether the study utilised predictive or explanatory modelling framework.
-To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive[^2].
+<!-- However, these analyses did not reveal any clear patterns, likely due to the small number of studies in each subgroup.  -->
+
+<!-- see this to ignore I\^2 and rely on prediction interval: https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678 -->
+
+These comparisons of sub-groupings may also be influenced by other factors, such as whether the study utilised a predictive or explanatory modelling framework.
+To address this, we used the type of journal in which each study was published as a proxy indicator for predictive or explanatory modelling, where we classified studies published in psychology journals as explanatory and those published in engineering journals as predictive.
 Of the 22 regression studies, 13 were classified into predictive frameworks, yielding an average correlation of *r* = 0.656 (95% CI: 0.505–0.769).
@@
 
-[^2]: ASJC journal classification by Scopus was used to determine the type of subject area.
+<!-- DISCUSS: we don't report journal type of explain/predict differences, although we do some of these in arousal, TE 19/3/2025: Now added! -->
 
@@
 |:----------|:----------|:----------|:----------|:----------|:----------|:----------|
-| All Models | 86, 80544 | 0.825 \[0.790-0.854\] | 23.7 | 0.0001 | 0.208 | 99.7% |
-| Best Models | 12, 15696 | 0.868 \[0.748-0.934\] | 8.13 | 0.0001 | 0.318 | 99.8% |
+| All Models   | 86, 80544   | 0.8245 \[0.7904-0.8535\]  | 23.7 | 0.0001 | 0.2082   | 99.7% |
+| Best Models  | 12, 15696   | 0.8684 \[0.7475-0.9336\]  | 8.13 | 0.0001 | 0.3180   | 99.8% |
 | *N Features* |             |                           |      |        |          |       |
-| \<30 | 4, 6179 | 0.929 \[0.816-0.974\] |  |  | 0.098 | 96.2% |
-| 30-300 | 5, 8193 | 0.846 \[0.361-0.971\] |  |  | 0.482 | 99.9% |
-| 300+ | 3, 1324 | 0.775 \[-0.271-0.982\] |  |  | 0.272 | 97.7% |
+| \<30         | 4, 6179     | 0.9293 \[0.8160-0.9738\]  |      |        | 0.0978   | 96.2% |
+| 30-300       | 5, 8193     | 0.8458 \[0.3613-0.9707\]  |      |        | 0.4822   | 99.9% |
+| 300+         | 3, 1324     | 0.7754 \[-0.2709-0.9818\] |      |        | 0.2724   | 97.7% |
 | *Techniques* |             |                           |      |        |          |       |
-| LM | 2, 735 | 0.728 \[-0.996-0.999\] |  |  | 0.194 | 98.0% |
-| SVM | 3, 6556 | 0.870 \[-0.727-0.999\] |  |  | 0.823 | 99.9% |
-| NN | 3, 2313 | 0.931 \[0.6523-0.988\] |  |  | 0.125 | 98.8% |
-| TM | 4, 6092 | 0.853 \[0.446-0.968\] |  |  | 0.243 | 99.1% |
+| LM           | 2, 735      | 0.7280 \[-0.9957-0.9999\] |      |        | 0.1935   | 98.0% |
+| SVM          | 3, 6556     | 0.8699 \[-0.7268-0.9985\] |      |        | 0.8233   | 99.9% |
+| NN           | 3, 2313     | 0.9307 \[0.6523-0.9878\]  |      |        | 0.1250   | 98.8% |
+| TM           | 4, 6092     | 0.8534 \[0.4464-0.9679\]  |      |        | 0.2430   | 99.1% |
+
+<!-- DISCUSS: 4 digits is too much, let's make this consistent, 2 in all places?, TE 19/3/2025 -->
 
@@
 
-To assess how the use of different model types affected performance, we prepared heatmap visualizations (Figure 5)depicting differences in success across feature *n* categories and algorithms.
+<!-- Changed the header slightly, TE 19/3/2025-->
+
+To assess how the use of different model types affected performance, we prepared heatmap visualizations (Figure 5) depicting differences in success across feature *n* categories and algorithms.
 We collapsed SVM and Tree-Based categories due to their low representation in the model summary.
@@
 Text labels summarize the number of models belonging to each subgroup, whereas the numbers in parentheses summarize the median number of stimuli used.
-Panel b summarizes the algorithms pertaining to each class, colour-coded by success rate and the numbers in parenthesis refer to number of studies.](model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
+Panel b summarizes the algorithms pertaining to each class, colour-coded by success rate, and the numbers refer to how many studies used each model.](../manuscript/model-summary-fig.png "Heatmap depicting success across tasks according to Feature N category and model class.
 Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="668"}
+
+```{=html}
+<!-- Notes to results: In the pre-registration, we promised the following:
+- groupings based on genre, model complexity (high, medium, low), model validation (exists or not)
+- we promised to carry out sensitivity analyses based on type of journal the studies were published in.
+
+CA: It looks like we've accounted for genre (single- vs.
+multi-genre), complexity (if feature n is a suitable substitute), and subgroup analyses for journal type (though this is not possible for classification studies).
+We have info on validation, though I'm not sure how this will play out depending on model type and whether cross-validation is necessary based on the algorithm.
+We might still be able to do a simple T/F encoding for cross-validation, and report the outcomes regardless of what the actual algorithm is.
+-->
+```
 
@@
 
-We initially identified 96 studies involving MER models, but narrowed our selection to 34 after filtering studies to ensure consistent quality, reporting standards, and a specific focus on predicting emotions using music features.
+<!-- Concise summary of what we did and found -->
+
+We initially identified 96 studies involving MER models, but narrowed our selection to 34 after filtering studies to ensure consistent quality, reporting standards, and a specific focus on evaluating emotions using music features.
 From these studies, we encoded accuracy scores for 290 models, with 204 related to regression and 86 to classification.
@@
 The results of the meta-analysis offer several important insights.
-First, compared to a 2013 report by @barthet2013, the prediction ceiling for valence has risen from *r* = 0.51 to 0.67.[^3] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
+First, compared to a 2013 report by @barthet2013, the prediction ceiling for valence has risen from *r* = 0.51 to 0.67.[^2] Conversely, predictive accuracy for arousal has shown no improvement (reported already in 2013 at *r* = 0.83).
 For classification, studies reached variable classification rates from 0.497 using *F~1~* score [@sanden2011empirical] to 79% average precision [@trohidis2008multi] in the past, whereas prediction rates have improved considerably, here $MCC$ = 0.87, albeit the differences in metrics.
 
-[^3]: Values reported as $R^2$ in original study.
+[^2]: Values reported as $R^2$ in original study.
+
+```{=html}
+<!-- Note.
+there is no clear conversion from Average precision to MCC, although we could estimate this from our data using regression?
+or to calculate both metrics from the confusion matrix.
+CA: this sounds like an interesting and achievable idea.
+The confusion matrices are encoded and then summarized with the caret and yardstick packages, and we can potentially extract many other useful measures from them with yardstick::summary(), demonstrated here: https://yardstick.tidymodels.org/reference/summary.conf_mat.html.
+
+TE: Interesting, it is a potential weakness and it would make our promotion of MCC more valuable when we could demonstrate how these two are linked, but perhaps to limit the workload, we could try identify a small subset to which to apply to this idea.
+-->
+```
 
@@
 
+<!-- minor improvements to the ending of the paragraph above -->
+
 Third, there is little work on the relevance of the features and how these impact the accuracy of the models.
@@
 In the future, it would be advantageous to systematically assess these sources of error in MER studies to allow us to focus on where and how significant improvements can be made.
+
+<!-- Added at least a reference to Pandas work on survey of features to para above -->
+
+```{=html}
+<!-- Question to @Cameron: We are a bit coy here as we don't really mention the tools by name (e.g.
+MIR toolbox, psysound, essentia, librosa, etc.).
+We have the information and should we write about them?
+Another gem to the supporting information as the space does not allow expansion.
+
+CA: This is a great idea, and reminds me we also have the Panda categories, which we have encoded, but haven't touched.
+We could explore whether we can find additional patterns about feature categories, and possibly libraries by extending out our new heat map visualization approach.
+
+TE: Or if we submit the meta-analysis soon and create a more pragmatic breakdown of what is the state of the art technologies in MER, this could be sufficient for a brief article separately.
+The selling point would not be the prediction rate, but quality control issues and the techniques/tools/crossvals/datasets chosen so far.
+-->
+```
 
@@
 We summarize these issues below as recommendations for improving (1) reporting and transparency, (2) feature definition, (3) dataset scale and content, and (4) the selection of emotion frameworks.
+
+<!-- ### Reporting and transparency -->
 
@@
 
+<!-- added a recommendation for regression study outputs as well to para above.
+We could add a mention about R2 adjusted to penalise complex models, but there are other ways to punish for model complexity as well.
+This has now been added to the para above -->
+
 It would be also highly beneficial to share models and features transparently.
@@
 Although copyright restrictions may limit the sharing of some datasets, features and examples should be made available through reliable external repositories (e.g., [Zenodo](https://zenodo.org/), [Open Science Framework](https://osf.io/), or [Kaggle datasets](https://osf.io/)).
+
+<!-- Added some examples of where the features/models can be shared -->
+
+<!-- ### Feature definition/validations -->
 
@@
 
+<!-- ### Validation -->
+
 An encouraging finding is that \~94% of the studies analyzed here reported some form of model validation.
@@
 
+<!-- Western bias -->
+
 At present, the majority of the datasets are Western pop, which represent only a fraction of the musical styles consumed globally.
@@
 Greater exploration of multi-genre MER [e.g., @griffiths2021am], and cross-cultural applications [@wang2022cr; wang2021ac; @hu2017cr; @agarwal2021an] will provide an important step toward establishing more generalizable models.
+
+<!-- ### Emotion frameworks chosen -->
 
@@
 Future efforts should prioritize feature validation, standardized reporting, the construction of larger and more diverse datasets, and the transparent sharing of research materials to ensure further consistent improvements in MER.
+
+### Acknowledgments
+
+We thank Prof. Michael Schutz for creating the opportunity for collaboration.
 

### 2025-11-28 analysis/supp_tables.qmd
Updated manuscript and bibtex file (R1)

# Supporting tables

Updated 28/11/2025

```{r}
#| warning: false
#| eval: true
#| echo: false
#library(dmetar,quietly = TRUE)
library(tidyverse,quietly = TRUE)
#library(meta)
#library(DescTools)
#library(ggrepel)
#library(forestplot)
```

#### Summarise all models

```{r}
#| warning: false
#| eval: true
#| id: table-summary1
#| output: asis

R_studies <- read.csv("R_studies.csv")
R_studies$unique_id_task <- paste(R_studies$unique_id,R_studies$dimension,sep="-")
#length(unique(R_studies$unique_id_task))
RS <- reframe(group_by(R_studies,model_class_id,),id=unique_id_task)
colnames(RS) <- c("Technique","Study-Model ID")

C_studies <- read.csv("C_studies.csv")
CS <- reframe(group_by(C_studies,model_class_id,),id=unique_id)
colnames(CS) <- c("Technique","Study-Model ID")

print(knitr::kable(RS,caption="Regression studies by model class"))
print(knitr::kable(CS,caption="Classification studies by model class"))
```

### 2025-11-28 manuscript/manuscript.qmd
Updated manuscript and bibtex file (R1)

@@
 A total of 553 studies were identified, of which 96 full-text articles were assessed, resulting in a final review of 34 studies.
-These studies reported 204 models, including 86 for emotion classification and 204 for regression.
+These studies reported 290 models, including 86 for emotion classification and 204 for regression.
 Using the best-performing model from each study, we found that valence and arousal were predicted with reasonable accuracy (r = 0.67 and r = 0.81, respectively), while classification models achieved an accuracy of 0.87 as measured with Matthews correlation coefficient.
@@
 Recent studies have sought to enhance emotion prediction by identifying more relevant feature sets [@panda2020audio; @chowdhury2021perceived], integrating low-, mid-, and high-level features through multimodal data [@celma_foafing_2006], and leveraging neural networks to learn features directly from audio [@zhang2016br; @agarwal2021an].
+Other efforts have attempted to improve the MER pipeline by accounting for differences between studies in how emotion constructs are represented [@kang2025], as well as how emotions are represented in different languages [@hu2025; @lee2025].
 These approaches aim to overcome ceiling effects in predictive accuracy [@downie_music_2008], which some scholars refer to as a *semantic gap* [@wiggins_semantic_2009; @celma_foafing_2006].
@@
 
-TABLE 1: Summary of data
+TABLE 1: Summary of data. To identify the studies and the models across techniques, see online materials.
 
@@
 To better understand the effects across studies and the nature of the observed heterogeneity, Figure 2 presents a forest of the random-effects model, based on the best-performing models from all studies.
+Effects of individual studies are represented by rectangles, with size reflecting the weight based on the sample size.
+Lines reflect 95% confidence intervals around study effects, and the summary effect appears at the bottom of the plot, represented as a dark diamond [@lewis2001].
 In terms of the forest plot, the range of prediction values (correlations) is broad, spanning from 0.13 to 0.92, with all studies except Koh et al.
@@
 
+## Limitations (in progress)
+
+(i) basing sample size on stimuli
+
+(ii) Limitations in the selection of databases and definition of search terms (how they might miss particular relevant studies)
+
+(iii) How quality issues led us to remove many papers that would otherwise be included based on the inclusion criteria
+
 ## Recommendations for future MER studies
@@
 However, annotated datasets for visual scenes and objects tend to be much larger, often exceeding 100,000 annotated examples [@deng2009imagenet; @krishna2017visual].
-Datasets of these magnitudes seem to be required for appropriate utilisation of deep learning algorithms [@alwosheel2018; @sun2017revisiting], which may explain the modest results observed in the music emotion recognition studies.
+In many applications, large datasets would be required for appropriate utilization of deep-learning algorithms, however, recent proposals to overcome the dataset-size limitation involve the use of pre-training and unsupervised techniques to learn general features (see MERT, @yizhi2023mert).
+While this approach has not yet fully resolved the issue, the bottleneck related to dataset size may be partially mitigated through the judicious use of self-supervised learning.
 
@@
 Understanding the limitations of different emotion taxonomies can also help improve modelling practices.
-For example, some scholars have explored treating MER as a circular regression problem, which can help overcome practical challenges such as the difficulty of relating to the abstract dimensions of valence and arousal, as well as the modelling assumptions required when translating a circular affective space to regression problems [@dufour2021us].
+For example, some scholars have explored treating MER as a circular regression problem, which can help overcome practical challenges such as the difficulty of relating to the abstract dimensions of valence and arousal, as well as the modelling assumptions required when translating a circular affective space to regression problems [@han2009smers; @dufour2021us].
 
